### 2014-08-04 experiment.Rmd
Initial exploration of matching using n-grams

---
title: "Experimenting with n-grams in Civil Procedure Codes"
author: "Kellen Funk and Lincoln Mullen"
date: "August 4, 2014"
output: html_document
---

Some preliminary experimentation with the OCR files from the Field Code and with
various text analysis packages.

```{r}
library(magrittr)
library(RWeka)
```

First we need to load the codes into a useable format and clean them up. Load each code as a character vector with just words converted to lowercase into a list, with the filenames as the names of the list objects

```{r}
files <- dir("txt", "*.txt")
raw <- file.path("txt", files) %>%
  lapply(., scan, "character", sep = "\n")
names(raw) <- files
codes_texts <- lapply(raw, paste, collapse = " ") %>%
  lapply(., tolower) %>%
  lapply(., WordTokenizer) %>%
  lapply(., paste, collapse = " ")
```

A helper function to create n-grams using the function provided in RWeka. Note that the documentation says that the maximum for an n-gram is 3, but apparently that is not the case.

```{r}
ngrammify <- function(data, n) { 
  NGramTokenizer(data, Weka_control(min = n, max = n))
  }
```

Create the n-grams, then create a list of all the unique n-grams. We're going to create just 5-grams on the suspicion that that is a good length.

```{r}
codes_grams <- lapply(codes_texts, ngrammify, 5)
every_grams <- codes_grams %>% unlist() %>% unique()
```

So far we have been comparing each code to the universe of codes, not one to another.
How many unique n-grams are there in total, and how many in each code?

```{r}
length_all_ngrams <- every_grams %>% length()
length_codes_ngrams <- codes_grams %>% lapply(., length)
```

How many fewer unique n-grams are there than the total of the n-grams in all the codes? I.e., how many matches are there?

```{r}
length_codes_ngrams %>% unlist %>% sum - length_all_ngrams
```

The n-grams in each code comprise what percentage of the total?

```{r}
length_codes_ngrams %>% lapply(., "/", length_all_ngrams)
```

Up till now we have been comparing codes with the total universe of codes. Now let's compare one code to another. The NC 1868 code is probably borrowed from the NY 1850 code. How many n-grams in the NC code are in the NY code? What is the percentage of matches to possible matches (i.e., the unique list of n-grams in both sets). What do these matches look like? (Save them to disk for Kellen to look at.)

```{r}
ny_to_nc_matches <- intersect(codes_grams$NC1868.txt, codes_grams$NY1850part2.txt) 
ny_to_nc_possible <- unique(c(codes_grams$NC1868.txt, codes_grams$NY1850part2.txt))

ny_to_nc_matches %>% length
ny_to_nc_matches %>% length / ny_to_nc_possible %>% length
ny_to_nc_matches %>% length / length_codes_ngrams$NC1868.txt

sample(ny_to_nc_matches, 10)
write.csv(ny_to_nc_matches, file = "out/ny_to_nc.matches.csv")
```

What if we do the same thing for New York to Michigan?

```{r}
ny_to_mi_matches <- intersect(codes_grams$MI1853.txt, codes_grams$NY1850part2.txt) 
ny_to_mi_possible <- unique(c(codes_grams$MI1853.txt, codes_grams$NY1850part2.txt))

ny_to_mi_matches %>% length
ny_to_mi_matches %>% length / ny_to_nc_possible %>% length
ny_to_mi_matches %>% length / length_codes_ngrams$MI1853.txt

sample(ny_to_mi_matches, 10)
write.csv(ny_to_mi_matches, file = "out/ny_to_mi.matches.csv")
```

That kind of analysis might be generally useful, so let's turn it into a function.

```{r}
#' Compare two codes using their list of n-grams.
#' @param orig_code A vector of n-grams representing a code.
#' @param dest_code A vectory of n-grams representing a code.
#' @return A list containing data that might help to identify whether codes
#'   match up.
compare_codes_by_shared_ngrams <- function(orig_code, dest_code) {
  require(magrittr)

  matches <- intersect(orig_code, dest_code)
  shared_ngrams <- unique(c(orig_code, dest_code))
  ratio_matches_to_possible <- length(matches) / length(shared_ngrams)
  ratio_matches_to_destination <- length(matches) / length(dest_code)
  list(matches = matches,
       shared_ngrams = shared_ngrams,
       ratio_matches_to_possible = ratio_matches_to_possible,
       ratio_matches_to_destination = ratio_matches_to_destination)
}
```

### 2014-08-04 experiment.Rmd
Added KWIC function

@@
 ```
+
+It sure would be nice to be able to take an n-gram that we know is a match and to find the context in two codes.
+I'm going to assume that you've found a interesting match elsewhere, probably using the `compare_codes_by_shared_ngrams()` function, and want to investigate it further.
+This function takes the n-gram as a string and the two codes to look for it in.
+(Technically, I suppose, we're just implementing a generic search function.)
+
+```{r}
+kwic_ngram_match <- function(ngram, code_1, code_2, disp_chars = 100) {
+  require(stringr)
+  # The fixed() function from stringr indicates that we are using literal
+  # characters rather than a regex.
+  match_code_1 <- str_locate_all(code_1, fixed(ngram))[[1]]
+  match_code_2 <- str_locate_all(code_2, fixed(ngram))[[1]]
+
+  match_code_1[,1] <- match_code_1[,1] - disp_chars
+  match_code_1[,2] <- match_code_1[,2] + disp_chars
+  match_code_2[,1] <- match_code_2[,1] - disp_chars
+  match_code_2[,2] <- match_code_2[,2] + disp_chars
+
+  extract_code_1 <- str_sub(code_1, match_code_1[,1], match_code_1[,2])
+  extract_code_2 <- str_sub(code_2, match_code_2[,1], match_code_2[,2])
+
+  data.frame(ngram = ngram,
+             orig_code = extract_code_1,
+             dest_code = extract_code_2)
+}
+```

### 2014-08-05 experiment.Rmd
Apply KWIC function to matches

@@
 ```
+
+Now that we've written a [KWIC](http://en.wikipedia.org/wiki/Key_Word_in_Context) function, we can apply it to the comparison of the NY and NC sample codes.
+
+First we get a comparison of the two codes:
+
+```{r}
+cf_ny_nc <- compare_codes_by_shared_ngrams(codes_grams$NY1850part2.txt,
+                                           codes_grams$NC1868.txt)
+str(cf_ny_nc)
+```
+
+Now let's get a random sample of matches:
+
+```{r}
+sample_matches <- sample(cf_ny_nc$matches, 20)
+sample_matches
+```
+
+Now let's apply our KWIC function to those sample matches and get a comparison of the two codes in tabular format.
+(If the length of this table is longer than the sample matches, it is because the match appears more than once in each code.)
+
+```{r}
+comparison_of_matches <- sample_matches %>% lapply(., kwic_ngram_match,
+                          codes_texts$NY1850part2.txt,
+                          codes_texts$NC1868.txt,
+                          disp_chars = 300) %>%
+                            do.call(rbind.data.frame, .)
+comparison_of_matches
+write.csv(comparison_of_matches, file = "out/matches_ny_nc_kwic.csv")
+```

### 2014-08-05 experiment.Rmd
Filter unreasonable n-grams

@@
 That kind of analysis might be generally useful, so let's turn it into a function.
+First a helper function that removes elements from the list of n-grams.
+A lot of the n-grams contain non-word characters, numbers, or gibberish from the OCR.
+We want to know the proportion of matches that could be reasonably matched, so we'll exclude n-grams containing any of those characters.
+
+```{r}
+#' Remove unreasonable n-grams containing characters other than letters and spaces
+#' @param ngrams A list of n-grams
+#' @return Returns a list of filtered n-grams
+filter_unreasonable_ngrams <- function(ngrams) {
+  require(stringr)
+  ngrams[!str_detect(ngrams, "[^a-z ]")]
+}
+```
+
+Now the main function for comparing two codes:
 
@@
   shared_ngrams <- unique(c(orig_code, dest_code))
-  ratio_matches_to_possible <- length(matches) / length(shared_ngrams)
-  ratio_matches_to_destination <- length(matches) / length(dest_code)
+  ratio_matches_to_possible <- length(matches) / length(filter_unreasonable_ngrams(shared_ngrams))
+  ratio_matches_to_destination <- length(matches) / length(filter_unreasonable_ngrams(dest_code))
   list(matches = matches,

### 2014-08-05 experiment.Rmd
Plot of matches in test codes

@@
 title: "Experimenting with n-grams in Civil Procedure Codes"
-author: "Kellen Funk and Lincoln Mullen"
+author: "Kellen Funk"
 date: "August 4, 2014"
@@
 ```
+
+Now let's create a density map of where the matching n-grams are in a code. Interesting that the beginning and end of the code have fewer matches.
+
+```{r, fig.height = 3, fig.width = 8}
+density_plot_color <- rgb(0.5, 0.5, 0.5, 0.1)
+nc_matches <- codes_grams$NC1868.txt %in% cf_ny_nc$matches  
+nc_matches %>% 
+  plot(type = "h",
+       col = density_plot_color,
+       ann = FALSE,
+       yaxt = "n",
+       xaxt = "n")
+title("Places in NC 1868 Code with Matches in NY 1850 Code",
+      xlab = "Position in code",
+      ylab = "")
+```
+
+We can do the same thing with the MI 1853 code and find that it's not a very good match to the NY 1850 code.
+The matches that are there are probably just noise or common legal terms and English phrases.
+
+```{r, fig.height = 3, fig.width = 8}
+cf_ny_mi <- compare_codes_by_shared_ngrams(codes_grams$NY1850part2.txt,
+                                           codes_grams$MI1853.txt)
+mi_matches <- codes_grams$MI1853.txt %in% cf_ny_mi$matches  
+mi_matches %>% 
+  plot(type = "h",
+       col = density_plot_color,
+       ann = FALSE,
+       yaxt = "n",
+       xaxt = "n")
+title("Places in MI 1853 Code with Matches in NY 1850 Code",
+      xlab = "Position in code",
+      ylab = "")
+```

### 2014-08-07 experiment.Rmd
Works with new codes

@@
 ```{r}
-files <- dir("txt", "*.txt")
-raw <- file.path("txt", files) %>%
+codes_dir <- "text"
+files <- dir(codes_dir, "*.txt")
+raw <- file.path(codes_dir, files) %>%
   lapply(., scan, "character", sep = "\n")
@@
 
-So far we have been comparing each code to the universe of codes, not one to another.
 How many unique n-grams are there in total, and how many in each code?
@@
 ```{r}
-ny_to_nc_matches <- intersect(codes_grams$NC1868.txt, codes_grams$NY1850part2.txt) 
-ny_to_nc_possible <- unique(c(codes_grams$NC1868.txt, codes_grams$NY1850part2.txt))
+ny_to_nc_matches <- intersect(codes_grams$NC1868.txt, codes_grams$NY1850c.txt) 
+ny_to_nc_possible <- unique(c(codes_grams$NC1868.txt, codes_grams$NY1850c.txt))
 
@@
 ```{r}
-ny_to_mi_matches <- intersect(codes_grams$MI1853.txt, codes_grams$NY1850part2.txt) 
-ny_to_mi_possible <- unique(c(codes_grams$MI1853.txt, codes_grams$NY1850part2.txt))
+ny_to_mi_matches <- intersect(codes_grams$MI1853.txt, codes_grams$NY1850c.txt) 
+ny_to_mi_possible <- unique(c(codes_grams$MI1853.txt, codes_grams$NY1850c.txt))
 
@@
 ```{r}
-cf_ny_nc <- compare_codes_by_shared_ngrams(codes_grams$NY1850part2.txt,
+cf_ny_nc <- compare_codes_by_shared_ngrams(codes_grams$NY1850c.txt,
                                            codes_grams$NC1868.txt)
@@
 comparison_of_matches <- sample_matches %>% lapply(., kwic_ngram_match,
-                          codes_texts$NY1850part2.txt,
+                          codes_texts$NY1850c.txt,
                           codes_texts$NC1868.txt,
@@
 
+Let's try this with the California 1851 code.
+
+```{r}
+cf_ny_ca <- compare_codes_by_shared_ngrams(codes_grams$NY1850c.txt,
+                                           codes_grams$CA1851.txt)
+str(cf_ny_ca)
+```
+
+And the plot comparing California and New York:
+
+```{r, fig.height = 3, fig.width = 8}
+density_plot_color <- rgb(0.5, 0.5, 0.5, 0.1)
+ca_matches <- codes_grams$NC1868.txt %in% cf_ny_nc$matches  
+ca_matches %>% 
+  plot(type = "h",
+       col = density_plot_color,
+       ann = FALSE,
+       yaxt = "n",
+       xaxt = "n")
+title("Places in CA 1851 Code with Matches in NY 1850 Code",
+      xlab = "Position in code",
+      ylab = "")
+```
+```
+
 We can do the same thing with the MI 1853 code and find that it's not a very good match to the NY 1850 code.
@@
 ```{r, fig.height = 3, fig.width = 8}
-cf_ny_mi <- compare_codes_by_shared_ngrams(codes_grams$NY1850part2.txt,
+cf_ny_mi <- compare_codes_by_shared_ngrams(codes_grams$NY1850c.txt,
                                            codes_grams$MI1853.txt)

### 2014-08-07 disregarding-ngrams.Rmd
Measure quality of OCR

---
title: "How many n-grams are we disregarding?"
output: html_document
---

```{r, echo=FALSE}
library(magrittr)
library(RWeka)
library(stringr)
```

```{r, echo=FALSE}
codes_dir <- "text"
files <- dir(codes_dir, "*.txt")
raw <- file.path(codes_dir, files) %>%
  lapply(., scan, "character", sep = "\n")
names(raw) <- files
codes_texts <- lapply(raw, paste, collapse = " ") %>%
  lapply(., tolower) %>%
  lapply(., WordTokenizer) %>%
  lapply(., paste, collapse = " ")
```

```{r, echo=FALSE}
ngrammify <- function(data, n) { 
  NGramTokenizer(data, Weka_control(min = n, max = n))
  }
```

```{r, echo=FALSE, cache=TRUE}
codes_grams <- lapply(codes_texts, ngrammify, 5)
```

```{r, echo=FALSE}
#' Remove unreasonable n-grams containing characters other than letters and spaces
#' @param ngrams A list of n-grams
#' @return Returns a list of filtered n-grams
filter_unreasonable_ngrams <- function(ngrams) {
  require(stringr)
  ngrams[!str_detect(ngrams, "[^a-z ]")]
}
```

We have a known problem of mistakes in the OCR coupled with section numbers, page numbers, and the occasional stray character. If we throw away any n-gram that includes a character outside the range of `a-z` (plus space), what proportion of the n-grams is left? This is a rough proxy for how good the OCR is.

```{r}
codes_grams %>% lapply(function(x) {
  (x %>% filter_unreasonable_ngrams %>% length) / (x %>% length)
}) 
```

Using tessaract instead of other OCR solutions, we're keeping about 80% of the NY 1850 code, instead of roughly 70% using our older method. Since that number is the denominator when we calculate the proportion of the code that has a match, this explains why the proportion grew less than we might have expected.

### 2014-08-12 experiment.Rmd
File name for NY 1850 has changed

@@
 ```{r}
-ny_to_nc_matches <- intersect(codes_grams$NC1868.txt, codes_grams$NY1850c.txt) 
-ny_to_nc_possible <- unique(c(codes_grams$NC1868.txt, codes_grams$NY1850c.txt))
+ny_to_nc_matches <- intersect(codes_grams$NC1868.txt, codes_grams$NY1850.txt) 
+ny_to_nc_possible <- unique(c(codes_grams$NC1868.txt, codes_grams$NY1850.txt))
 
@@
 ```{r}
-ny_to_mi_matches <- intersect(codes_grams$MI1853.txt, codes_grams$NY1850c.txt) 
-ny_to_mi_possible <- unique(c(codes_grams$MI1853.txt, codes_grams$NY1850c.txt))
+ny_to_mi_matches <- intersect(codes_grams$MI1853.txt, codes_grams$NY1850.txt) 
+ny_to_mi_possible <- unique(c(codes_grams$MI1853.txt, codes_grams$NY1850.txt))
 
@@
 ```{r}
-cf_ny_nc <- compare_codes_by_shared_ngrams(codes_grams$NY1850c.txt,
+cf_ny_nc <- compare_codes_by_shared_ngrams(codes_grams$NY1850.txt,
                                            codes_grams$NC1868.txt)
@@
 comparison_of_matches <- sample_matches %>% lapply(., kwic_ngram_match,
-                          codes_texts$NY1850c.txt,
+                          codes_texts$NY1850.txt,
                           codes_texts$NC1868.txt,
@@
 ```{r}
-cf_ny_ca <- compare_codes_by_shared_ngrams(codes_grams$NY1850c.txt,
+cf_ny_ca <- compare_codes_by_shared_ngrams(codes_grams$NY1850.txt,
                                            codes_grams$CA1851.txt)
@@
 ```{r, fig.height = 3, fig.width = 8}
-cf_ny_mi <- compare_codes_by_shared_ngrams(codes_grams$NY1850c.txt,
+cf_ny_mi <- compare_codes_by_shared_ngrams(codes_grams$NY1850.txt,
                                            codes_grams$MI1853.txt)

### 2014-08-14 experiment.Rmd
Omitting some unnecessary, buggy code

@@
 author: "Kellen Funk"
-date: "August 4, 2014"
 output: html_document
@@
 ```{r}
-comparison_of_matches <- sample_matches %>% lapply(., kwic_ngram_match,
-                          codes_texts$NY1850.txt,
-                          codes_texts$NC1868.txt,
-                          disp_chars = 300) %>%
-                            do.call(rbind.data.frame, .)
-comparison_of_matches
-write.csv(comparison_of_matches, file = "out/matches_ny_nc_kwic.csv")
+# TEMPORARILY REMOVED
+# comparison_of_matches <- sample_matches %>% lapply(., kwic_ngram_match,
+#                           codes_texts$NY1850.txt,
+#                           codes_texts$NC1868.txt,
+#                           disp_chars = 300) %>%
+#                             do.call(rbind.data.frame, .)
+# comparison_of_matches
+# write.csv(comparison_of_matches, file = "out/matches_ny_nc_kwic.csv")
 ```
@@
 density_plot_color <- rgb(0.5, 0.5, 0.5, 0.1)
-ca_matches <- codes_grams$NC1868.txt %in% cf_ny_nc$matches  
+ca_matches <- codes_grams$CA1851.txt %in% cf_ny_ca$matches  
 ca_matches %>% 
@@
       ylab = "")
-```
 ```

### 2014-08-14 setup.R
Necessary packages

@@ -1,0 +1,14 @@
+# Packages that we are using, listed in the likely order of easiest to most
+# difficult to install.
+install.packages("magrittr")
+install.packages("stringr")
+install.packages("dplyr")
+install.packages("tidyr")
+install.packages("rJava")
+install.packages("RWeka")
+
+# Packages we are not using yet but will likely use soon
+install.packages("ggplot2")
+install.packages("reshape2")
+install.packages("plyr")
+install.packages("lubridate")

### 2014-08-15 test-compare-codes.Rmd
Matrix of comparison with sample clustering plot

---
title: "First Attempt at a Comparison Matrix"
output: html_document
---

Let's do a quick and dirty test to see if we can get a comparison matrix.

```{r}
library(magrittr)
library(RWeka)
library(stringr)
```

Load the codes.

```{r, echo=FALSE}
codes_dir <- "text"
files <- dir(codes_dir, "*.txt")
raw <- file.path(codes_dir, files) %>%
  lapply(., scan, "character", sep = "\n")
names(raw) <- files
codes_texts <- lapply(raw, paste, collapse = " ") %>%
  lapply(., tolower) %>%
  lapply(., WordTokenizer) %>%
  lapply(., paste, collapse = " ")

```

Keep a random sample of three plus NY 1850 to keep computation time low for the test.

```{r}
codes_sample <- c(sample(codes_texts, 3), NY1850.txt = codes_texts[["NY1850.txt"]])
```

Function for n-grams:

```{r}
ngrammify <- function(data, n) { 
  NGramTokenizer(data, Weka_control(min = n, max = n))
  }
```

Create the n-grams:

```{r}
codes_grams <- lapply(codes_sample, ngrammify, 5)
```

Function to remove unreasonable n-grams:

```{r}
#' Remove unreasonable n-grams containing characters other than letters and spaces
#' @param ngrams A list of n-grams
#' @return Returns a list of filtered n-grams
filter_unreasonable_ngrams <- function(ngrams) {
  require(stringr)
  ngrams[!str_detect(ngrams, "[^a-z ]")]
}
```

Now apply that function to `codes_grams` so we get a list of clean n-grams. This might not be the best strategy: we'll think about that later.

```{r}
codes_grams <- lapply(codes_grams, filter_unreasonable_ngrams)
```

Function to compare two codes. Note that this function (unlike earlier versions and just for the purpose of this test) only returns one number for simplicity's sake instead of a list. (And it no longer applies the filter for unreasonable n-grams inside this function. Instead that is applied globally earlier.)

```{r}
#' Compare two codes using their list of n-grams.
#' @param orig_code A vector of n-grams representing a code.
#' @param dest_code A vectory of n-grams representing a code.
#' @return A list containing data that might help to identify whether codes
#'   match up.
compare_codes_by_shared_ngrams <- function(orig_code, dest_code) {
  require(magrittr)

  matches <- intersect(orig_code, dest_code)
  shared_ngrams <- unique(c(orig_code, dest_code))
  ratio_matches_to_possible <- length(matches) / length(shared_ngrams)
  ratio_matches_to_destination <- length(matches) / length(dest_code)
  return(ratio_matches_to_destination)
}
```

Now we use a function to create a matrix of comparisons (This is inefficient because it compares each code to itself. And for each possible pairing it does the comparison twice, swapping origin and destination codes. Good enough for now.)

This is to help us understand the comparisons (pretty sure I have the arrow pointing the right way!):

```{r}
code_names <- str_extract(names(codes_grams), "\\w+")
names_of_comparisons <- outer(code_names, code_names, function(x, y){
  paste(y, "from", x)
}) 
colnames(names_of_comparisons) <- code_names
rownames(names_of_comparisons) <- code_names
print(names_of_comparisons)
```

These are the comparisons themselves. The way to read this matrix is "the proportion of ngrams that COLUMN borrows from ROW." In other words the ROW is the origin code and the COLUMN is the destination code.

```{r}
# From http://stackoverflow.com/questions/1719447/outer-equivalent-for-non-vector-lists-in-r
outer_for_lists <- function(a,b, fun) {
  outer(a, b, function(x,y) vapply(seq_along(x), function(i) fun(x[[i]], y[[i]]), numeric(1)))
}
comparison_of_codes <- outer_for_lists(codes_grams, codes_grams, compare_codes_by_shared_ngrams)
colnames(comparison_of_codes) <- code_names
rownames(comparison_of_codes) <- code_names
print(comparison_of_codes)
```

A big surprise is why the diagonal is not all `1`, since presumably a code is perfectly derived for itself. The reason is that the `intersect` function that we use to find matches must return only unique matches not duplicated matches. In other words, the intersection of a vector with itself is the same thing as the unique values of the vector. Proof:

```{r}
identical(intersect(codes_grams$NY1850.txt, codes_grams$NY1850.txt),
          unique(codes_grams$NY1850.txt))
```

That's a useful thing to know: maybe there is a better way to find matches. But for now let's not get sidetracked. The important point is that we can compare all of the codes into a matrix, and that it's pretty fast. Now we can run this analysis on the whole shebang.

First we get all the codes as n-grams:

```{r}
codes_all_grams <- lapply(codes_texts, ngrammify, 5)
codes_all_grams <- lapply(codes_all_grams, filter_unreasonable_ngrams)
```

Here is the matrix of comparisons for all the codes:

```{r}
codes_all_names <- str_extract(names(codes_all_grams), "\\w+")
comparison_of_all_codes <- outer_for_lists(codes_all_grams, codes_all_grams, compare_codes_by_shared_ngrams)
colnames(comparison_of_all_codes) <- codes_all_names
rownames(comparison_of_all_codes) <- codes_all_names
print(comparison_of_all_codes)
```

What we really care about is just the triangular comparison.

```{r}
triangle <- comparison_of_all_codes
triangle[upper.tri(triangle, diag = TRUE)]  <- NA
print(triangle)
```

Let's write that file to disk for someone who know about the history of codes to make sense of it.

```{r}
write.csv(triangle, "out/comparison_of_all_codes.csv")
```

What is the distribution of comparisons?

```{r}
triangle %>% hist()
```

*********

Now this is more than we can figure out meaningfully today, but it's possible to run standard distance and clustering functions on that matrix. I'm not sure what this even means just yet.

Let's see the standard distance function:

```{r}
distance <- comparison_of_all_codes %>% dist
print(distance)
```

And we can then pass that distance matrix to hierarchical clustering or k-means clustering (obviously we need to read up on all these) and plot each.

```{r}
distance %>% hclust() %>% str()
distance %>% hclust() %>% plot()
```

I wouldn't put any stock in that chart, but it does show what should be possible. And apart from the problem of the chronological arrow, it is interesting that western states are close to one another, the New York codes are close together, the two Ohio codes are at least close together, etc. Time to learn some statistics.

And now for k-means with a plot that I kind of get. Obviously this would make more sense with names on the plot.

```{r}
cluster <- kmeans(comparison_of_all_codes, centers = 5)
library(cluster)
clusplot(comparison_of_all_codes, cluster$cluster)
```

### 2014-08-15 test-compare-codes.Rmd
Add labels to k-means plot

@@
 
-And now for k-means with a plot that I kind of get. Obviously this would make more sense with names on the plot.
+And now for k-means with a plot that I kind of get.
 
@@
 library(cluster)
-clusplot(comparison_of_all_codes, cluster$cluster)
+clusplot(comparison_of_all_codes, cluster$cluster, labels = 2)
 ```

### 2014-08-15 test-compare-codes.Rmd
Create sorted list of code similarity

@@
 
+Let's write that comparison to disk for someone who know about the history of codes to make sense of it.
+
+```{r}
+write.csv(comparison_of_all_codes, "out/comparison_of_all_codes.csv")
+```
+
 What we really care about is just the triangular comparison.
@@
 
-Let's write that file to disk for someone who know about the history of codes to make sense of it.
-
-```{r}
-write.csv(triangle, "out/comparison_of_all_codes.csv")
-```
-
 What is the distribution of comparisons?
@@
 triangle %>% hist()
+```
+
+For each code we can get a sorted list of the codes that it is most like.
+
+```{r}
+for(i in 1:ncol(comparison_of_all_codes)) {
+  x <- comparison_of_all_codes[,i]
+  title <- colnames(comparison_of_all_codes)[i]
+  cat("\n\n", title, " is most like:\n", sep = "")
+  cat("---------\n")
+  y <- sort(x, decreasing = TRUE)
+  for(j in 2:length(y)) {
+    cat(names(y)[j], y[j], "\n", sep = " ") 
+    }
+}
 ```

### 2014-08-15 test-compare-codes.Rmd
Use unique n-grams for the denominator
Since `intersect()` finds the unique n-grams that match, not all the
matches, it is necessary to use the unique n-grams in the denominator
too. This shows that the comparisons are more favorable than we thought.
And most important, in the diagonal of the comparison matrix, a code
compared to itself now has a value of 1.

@@
   shared_ngrams <- unique(c(orig_code, dest_code))
-  ratio_matches_to_possible <- length(matches) / length(shared_ngrams)
-  ratio_matches_to_destination <- length(matches) / length(dest_code)
+  ratio_matches_to_possible <- length(matches) / length(unique(shared_ngrams))
+  ratio_matches_to_destination <- length(matches) / length(unique(dest_code))
   return(ratio_matches_to_destination)
@@
 
-A big surprise is why the diagonal is not all `1`, since presumably a code is perfectly derived for itself.
-The reason is that the `intersect` function that we use to find matches must return only unique matches not duplicated matches.
-In other words, the intersection of a vector with itself is the same thing as the unique values of the vector.
-Proof:
-
-```{r}
-identical(intersect(codes_grams$NY1850.txt, codes_grams$NY1850.txt),
-          unique(codes_grams$NY1850.txt))
-```
-
-That's a useful thing to know: maybe there is a better way to find matches.
-But for now let's not get sidetracked.
-The important point is that we can compare all of the codes into a matrix, and that it's pretty fast.
-Now we can run this analysis on the whole shebang.
-
-First we get all the codes as n-grams:
+Now we can run this analysis on the whole shebang. First we get all the codes as n-grams:
 

### 2014-11-21 setup.R
Delete setup script

@@ -1,14 +1,0 @@
-# Packages that we are using, listed in the likely order of easiest to most
-# difficult to install.
-install.packages("magrittr")
-install.packages("stringr")
-install.packages("dplyr")
-install.packages("tidyr")
-install.packages("rJava")
-install.packages("RWeka")
-
-# Packages we are not using yet but will likely use soon
-install.packages("ggplot2")
-install.packages("reshape2")
-install.packages("plyr")
-install.packages("lubridate")

### 2014-11-21 R/helper.R
Separate helper functions into own file

@@ -1,0 +1,32 @@
+# Function to create ngrams
+ngrammify <- function(data, n) {
+  NGramTokenizer(data, Weka_control(min = n, max = n))
+}
+
+#' Remove unreasonable n-grams containing characters other than letters and spaces
+#' @param ngrams A list of n-grams
+#' @return Returns a list of filtered n-grams
+filter_unreasonable_ngrams <- function(ngrams) {
+  ngrams[!stringi::stri_detect_fixed(ngrams, "[^a-z ]")]
+}
+
+#' Compare two codes using their list of n-grams.
+#' @param orig_code A vector of n-grams representing a code.
+#' @param dest_code A vectory of n-grams representing a code.
+#' @return A list containing data that might help to identify whether codes
+#'   match up.
+compare_codes_by_shared_ngrams <- function(orig_code, dest_code) {
+  matches <- intersect(orig_code, dest_code)
+  shared_ngrams <- unique(c(orig_code, dest_code))
+  ratio_matches_to_possible <- length(matches) / length(unique(shared_ngrams))
+  ratio_matches_to_destination <- length(matches) / length(unique(dest_code))
+  return(ratio_matches_to_destination)
+}
+
+# From http://stackoverflow.com/questions/1719447/outer-equivalent-for-non-vector-lists-in-r
+outer_for_lists <- function(a,b, fun) {
+  mat <- outer(a, b, function(x,y) vapply(seq_along(x), function(i) fun(x[[i]], y[[i]]), numeric(1)))
+  rownames(mat) <- names(b)
+  colnames(mat) <- names(a)
+  return(mat)
+}

### 2014-11-21 R/helper.R
Use regex not fixed

@@ -7,7 +7,7 @@ ngrammify <- function(data, n) {
 #' @param ngrams A list of n-grams
 #' @return Returns a list of filtered n-grams
 filter_unreasonable_ngrams <- function(ngrams) {
-  ngrams[!stringi::stri_detect_fixed(ngrams, "[^a-z ]")]
+  ngrams[!stringi::stri_detect_regex(ngrams, "[^a-z ]")]
 }
 
 #' Compare two codes using their list of n-grams.

### 2014-11-21 R/load-data.R
Load the data in separate script

@@ -1,0 +1,16 @@
+codes_dir <- "text"
+files <- dir(codes_dir, "*.txt")
+
+raw <- file.path(codes_dir, files) %>%
+  lapply(., scan, "character", sep = "\n")
+names(raw) <-  stri_match_first_regex(files, "(.+).txt")[,2]
+
+codes <- raw %>%
+  lapply(paste, collapse = " ") %>%
+  lapply(tolower) %>%
+  lapply(WordTokenizer) %>%
+  lapply(paste, collapse = " ") %>%
+  lapply(ngrammify, 5) %>%
+  lapply(filter_unreasonable_ngrams)
+
+rm(raw, codes_dir, files)

### 2014-11-21 network-analysis.Rmd
Load data for network analysis

---
title: "Network Analysis of Code Similarity"
author: "Kellen Funk and Lincoln Mullen"
date: "November 21, 2014"
output: html_document
---

```{r echo=FALSE}
packrat::on()
library(magrittr)
library(RWeka)
library(stringi)
source("R/helper.R")

# Load the data if it doesn't exist already.
if(file.exists("out/codes.rda")) {
  load("out/codes.rda")
  } else {
  source("R/load-data.R")
  save(codes, file = "out/codes.rda")
  }
```

There are the codes that we currently have:

```{r}
names(codes)
```

Create the comparison matrix:

```{r}
cf <- outer_for_lists(codes, codes, compare_codes_by_shared_ngrams)
diag(cf) <- NA   # remove codes compared to themselves
```

### 2014-11-21 R/helper.R
Remove anachronisms

@@ -30,3 +30,22 @@ outer_for_lists <- function(a,b, fun) {
   colnames(mat) <- names(a)
   return(mat)
 }
+
+# Get the year from a code name
+get_year <- function(s) {
+  year <- stringi::stri_extract_first_regex(s, "\\d{4}")
+  as.integer(year)
+}
+# Remove anachronistic comparisons of earlier codes to later codes
+rm_anachronism <- function(m) {
+  rows <- rownames(m)
+  cols <- colnames(m)
+  for(i in seq_along(m)) {
+    ind <- arrayInd(i, dim(m))
+    row <-  rows[ind[1,1]]
+    col <-  cols[ind[1,2]]
+    test <- get_year(row) > get_year(col)
+    if(test) m[i] <- NA
+  }
+  return(m)
+}

### 2014-11-21 R/helper.R
Clean up code comparison function

@@ -17,8 +17,6 @@ filter_unreasonable_ngrams <- function(ngrams) {
 #'   match up.
 compare_codes_by_shared_ngrams <- function(orig_code, dest_code) {
   matches <- intersect(orig_code, dest_code)
-  shared_ngrams <- unique(c(orig_code, dest_code))
-  ratio_matches_to_possible <- length(matches) / length(unique(shared_ngrams))
   ratio_matches_to_destination <- length(matches) / length(unique(dest_code))
   return(ratio_matches_to_destination)
 }

### 2014-11-21 network-analysis.Rmd
Remove anachronistic comparisons

@@
 diag(cf) <- NA                 # remove codes compared to themselves
+cf <- rm_anachronism(cf)       # remove anachronistic comparisons
 ```

### 2014-11-21 network-analysis.Rmd
Basic network graph

--- 2014-11-21 network-analysis.Rmd
@@
 library(stringi)
+library(igraph)
 source("R/helper.R")
@@
 cf <- outer_for_lists(codes, codes, compare_codes_by_shared_ngrams)
-diag(cf) <- NA   # remove codes compared to themselves
 ```
+
+Remove obviously incorrect values:
+
+```{r}
+cf2  <- cf
+diag(cf2) <- NA                 # remove codes compared to themselves
+cf2 <- rm_anachronism(cf2)       # remove anachronistic comparisons
+
+significance_threshold <- 0.15
+cf2[cf2 < significance_threshold] <- NA
+cf2[is.na(cf2)] <- 0
+```
+
+Now we can create a graph object from the comparison matrix, which we will treat as an adjacency matrix.
+
+```{r}
+g <- graph.adjacency(cf2, mode = "directed", weighted = TRUE, diag = FALSE) 
+set.seed(4821)
+l <- layout.fruchterman.reingold(g, weights = E(g)$weight)
+par(mar=c(0,0,0,0))
+plot(g, edge.width = E(g)$weight * 12, layout = l, edge.arrow.size= 0.25, vertex.size = 5)
+```

### 2014-11-21 network-analysis.Rmd
Plot options and community detection

@@
 l <- layout.fruchterman.reingold(g, weights = E(g)$weight)
-par(mar=c(0,0,0,0))
-plot(g, edge.width = E(g)$weight * 12, layout = l, edge.arrow.size= 0.25, vertex.size = 5)
+par(mar=c(0,0,1,0))
+plot(g, edge.width = E(g)$weight * 10, layout = l,
+     edge.arrow.size= 0.15, vertex.size = 5)
+title("Codes of Civil Procedure")
 ```
+
+Community detection
+
+```{r}
+g %>%
+  walktrap.community() %>%
+  plot(., g, vertex.label = NA, layout = l, vertex.size = 3)
+```

### 2014-11-21 network-analysis.Rmd
Isolate subgraphs

@@
 ```
+
+Get just the component graphs
+
+```{r}
+sub <- decompose.graph(g, mode = "weak", min.vertices = 3)[[1]]
+l2 <- layout.fruchterman.reingold(sub, weights = E(sub)$weight)
+par(mar=c(0,0,1,0))
+plot(sub, edge.width = E(sub)$weight * 10, layout = l2,
+     edge.arrow.size= 0.15, vertex.size = 5)
+title("Largest family of codes")
+```
+
+Neighborhood of NY 1850
+
+```{r}
+ny <- which(V(g)$name == "NY1850")
+neighbors(g, ny)
+graph.neighborhood(g, order = 2, nodes = ny)[[1]] %>%
+  plot_graph()
+```

### 2014-11-21 R/helper.R

@@ -47,3 +47,8 @@ rm_anachronism <- function(m) {
   }
   return(m)
 }
+
+plot_graph <- function(g) {
+  plot(g, edge.width = E(g)$weight * 5, layout = layout.fruchterman.reingold,
+       edge.arrow.size= 0.25, vertex.size = 5)
+}

### 2014-11-21 network-analysis.Rmd
Get influences function

@@
 
-significance_threshold <- 0.15
+significance_threshold <- 0.03
 cf2[cf2 < significance_threshold] <- NA
@@
 ```{r}
-ny <- which(V(g)$name == "NY1850")
+ny <- which(V(g)$name == "IA851")
 neighbors(g, ny)
-graph.neighborhood(g, order = 2, nodes = ny)[[1]] %>%
+graph.neighborhood(g, order = 1, nodes = ny)[[1]] %>%
   plot_graph()
 ```
+
+Get all the influences for people who need words.
+
+```{r}
+influences <- colnames(cf2) %>%
+  lapply(., function(name) { get_influences(cf2, name, 10) })
+names(influences) <- colnames(cf2)
+print(influences)
+```

### 2014-11-21 R/helper.R

@@ -52,3 +52,12 @@ plot_graph <- function(g) {
   plot(g, edge.width = E(g)$weight * 5, layout = layout.fruchterman.reingold,
        edge.arrow.size= 0.25, vertex.size = 5)
 }
+
+# Given a comparison matrix, return the codes that most INFLUENCE
+get_influences <- function(m, state, n = NULL) {
+  influences <- sort(m[, state], decreasing = TRUE)
+  if(is.null(n))
+    return(influences)
+  else
+    return(influences[1:n])
+}

### 2015-02-07 network-analysis.Rmd
Fix NY
Minor changes to networks

@@
 library(igraph)
+library(d3Network)
 source("R/helper.R")
@@
 
-significance_threshold <- 0.03
+significance_threshold <- 0.25
 cf2[cf2 < significance_threshold] <- NA
@@
 
-```{r}
+```{r fig.width=10, fig.height=10}
 g <- graph.adjacency(cf2, mode = "directed", weighted = TRUE, diag = FALSE) 
@@
 par(mar=c(0,0,1,0))
-plot(g, edge.width = E(g)$weight * 10, layout = l,
+plot(g, edge.width = E(g)$weight * 8, layout = l,
      edge.arrow.size= 0.15, vertex.size = 5)
@@
 ```{r}
-ny <- which(V(g)$name == "IA851")
+ny <- which(V(g)$name == "NY1850")
 neighbors(g, ny)

### 2015-09-21 early-analysis/001-test-compare-codes.Rmd
Move early analyses into separate folder

--- 2014-08-15 test-compare-codes.Rmd
@@
 rownames(comparison_of_all_codes) <- codes_all_names
+
+# Normalize comparison of all codes to percentages
+comparison_of_all_codes <- round(comparison_of_all_codes * 100, digits = 1)
 print(comparison_of_all_codes)

### 2015-09-21 early-analysis/006-ocr-quality.Rmd
Move early analyses into separate folder

---
title: "Check OCR quality of specific codes"
author: "Lincoln Mullen"
date: "September 11, 2015"
output: html_document
---

We have multiple versions of several codes, so we want to see whether any of them have better quality than others. The codes we are interested in:

> For Iowa 1859, I have a, b, and c versions, and for New Mexico 1897 I have an a and b.

```{r, message=FALSE, warning=FALSE}
library(ocrquality)
library(stringr)
library(dplyr)
set.seed(33532)
```

Load the files.

```{r}
paths <- Sys.glob("legal-codes/*.txt")
docs <- paths %>% 
  lapply(readLines) %>% 
  lapply(str_c, collapse = " ")
```

Check the OCR quality:

```{r}
quality <- sapply(docs, ocr_dictionary, sample_size = 10e3)
```

Turn that into a data frame and print it.

```{r}
results <- data_frame(file = paths,
                      quality = quality) %>% 
  arrange(desc(quality))
relevant <- results %>% 
  filter(str_detect(file, "IA1859") | str_detect(file, "NM1897"))
relevant
```

Write to CSV.

```
write.csv(results, "out/ocr-quality.csv")
write.csv(relevant, "out/ocr-quality-relevant.csv")
```

### 2015-09-21 ocr-quality.R

@@ -1,20 +1,0 @@
-library(stringr)
-library(textreuse)
-library(dplyr)
-
-files <- Sys.glob("text/*")
-texts <- files %>%
-  lapply(readLines) %>%
-  lapply(str_c, collapse = " ")
-names(texts) <- files
-
-quality <- texts %>% sapply(ocr_quality, method = "dictionary")
-names(quality) <- names(texts)
-quality <- round(quality, 3)
-
-quality_df <- data_frame(code = names(quality), quality) %>%
-  arrange(desc(quality))
-write.csv(quality_df, "out/ocr-quality.csv")
-
-hist(quality, breaks = 25, xlim = c(0, 1),
-     main = "Histogram of Codes OCR Quality", labels = TRUE)

### 2015-09-21 007-load-corpus.Rmd
Load and tokenize the corpus

---
title: "Load and tokenize all codes"
author: "Lincoln Mullen"
date: "September 21, 2015"
output: html_document
---

We are going to tokenize the codes and save a cached version. For our initial analysis, we will use skip n-grams with a moderate value for `k` so that we have many features.

```{r}
library("textreuse")

cache <- "cache/corpus-skip-ngrams-n7k3.rds"
if (!file.exists(cache)) {
  description <- "General purpose tokenization of codes for comparing pairwise."
  corpus <- TextReuseCorpus(dir = "legal-codes/",
                            meta = list("description" = description,
                                        "title" = "Field codes"),
                            tokenizer = tokenize_skip_ngrams, n = 7 , k = 3,
                            hash_func = hash_string,
                            keep_tokens = TRUE)
  dir.create("cache", showWarnings = FALSE)
  corpus
  saveRDS(corpus, file = cache)
}
```

Session info:

```{r}
sessionInfo()
```

### 2015-09-21 008-pairwise-jaccard.Rmd
Pairwise with Jaccard similarity

---
title: "Compare pairwise with Jaccard similarity"
author: "Lincoln Mullen"
date: "September 21, 2015"
output: 
  html_document:
    keep_md: true
---

We are going to load the corpus from the cache, and create a comparison matrix with Jaccard similarity. (We will do other comparisons in different notebook so we can do this in parallel.) We will cache the matrix for use in later analyses.

```{r}
library("textreuse")

cache <- "cache/comparison-matrix-jaccard.rds"
if (!file.exists(cache)) {
  corpus <- readRDS("cache/corpus-skip-ngrams-n7k3.rds")
  m <- pairwise_compare(corpus, jaccard_similarity)
  saveRDS(m, cache)
} else {
  m <- readRDS(cache)
}
```

Here is the comparison matrix:

```{r}
m
```

Session info:

```{r}
sessionInfo()
```

### 2015-09-22 scripts/clean-text.R
Additional OCR corrections for sectioning codes

@@ -17,6 +17,7 @@ corrections <- read_csv("scripts/ocr-corrections.csv")
 cleaned <- text %>%
   stri_replace_all_fixed(corrections$pattern, corrections$replacement,
                          vectorize_all = FALSE) %>%
+  str_replace_all("\r", "") %>%
   str_replace_all("-\n+", "")
 
 write(cleaned, file = out_file)

### 2015-09-22 011-split-codes.Rmd
Initial splitting of codes

---
title: "Split codes into chunks"
author: "Lincoln Mullen"
date: "September 21, 2015"
output: 
  html_document:
    keep_md: true
---

The goal is to split codes into chunks, then identify candidates with minhash and LSH. (See the textreuse package documentation.)

```{r}
library(textreuse)
library(stringr)
source("R/split-doc.R")
dir.create("legal-codes-split", showWarnings = FALSE)
```

Create a regular expression to section the codes.

```{r}
ny_1850_pattern <- regex("(\n§((\\s+)?)\\d+((\\.)?)|\n\\$((\\s+)?)\\d+((\\.)?)|\nchapter|\ntitle|\narticle|\nt i t l e|\nRULE \\w+\\.|\n\\d{4,}\\.|\nSEC((\\.)?)\\s+\\d+((\\.)?)|\n8EC((\\.)?)\\s+\\d+((\\.)?)|\nSE0((\\.)?)\\s+\\d+((\\.)?)|\nSEO((\\.)?)\\s+\\d+((\\.)?)|\nSEQ((\\.)?)\\s+\\d+((\\.)?))", ignore_case = TRUE)
test <- str_detect(c("\n§ 1842 This should be true", "\nThis should be false §",
                     "\n§ 142. This should be true", "\nThis should be false §",
                     "\n§142. This should be true", "\nThis should be false §",
                     "\nchapter should be true", "\nThis chapter should be false",
                     "\nCHAPTER should be true", "\nthis CHAPTER should be false",
                     "\nT I T L E should be true", "false",
                     "\n$342. This should be true", "false",
                     "\n$ 323. This should be true", "false",
                     "\nRULE XVI. This should be true", "This rule is false",
                     "\n3652. From AL1852 true", "232. False",
                     "\n3652. From AL1852 true", "Citation 232. False",
                     "\nSEC. 431. true", "This SEC 133 false",
                     "\n8EC. 3323. true", "false",
                     "\nSEC.   2545 true", "false"),
                   pattern = ny_1850_pattern)
all(test == c(TRUE, FALSE))
```

Split the codes.

```{r}
split_doc("legal-codes/NY1850.txt", ny_1850_pattern, "legal-codes-split/NY1850")
split_doc("legal-codes/CA1851.txt", ny_1850_pattern, "legal-codes-split/CA1851")
split_doc("legal-codes/NC1868.txt", ny_1850_pattern, "legal-codes-split/NC1868")
split_doc("legal-codes/AL1852.txt", ny_1850_pattern, "legal-codes-split/AL1852")
split_doc("legal-codes/OH1853.txt", ny_1850_pattern, "legal-codes-split/OH1853")
split_doc("legal-codes/OH1853extended.txt", ny_1850_pattern, "legal-codes-split/OH1853extended")
split_doc("legal-codes/CA1850.txt", ny_1850_pattern, "legal-codes-split/CA1850")
split_doc("legal-codes/GA1860.txt", ny_1850_pattern, "legal-codes-split/GA1860")
split_doc("legal-codes/CA1868.txt", ny_1850_pattern, "legal-codes-split/CA1868")
split_doc("legal-codes/AZ1865.txt", ny_1850_pattern, "legal-codes-split/AZ1865")
```

What are the mean, median, and mode lengths of sections in the NY 1850 code?

```{r}
ny_1850_code <- TextReuseCorpus(Sys.glob("legal-codes-split/NY1850*"),
                                tokenizer = tokenize_words)
ny_1850_wc <- wordcount(ny_1850_code)
mean(ny_1850_wc)
median(ny_1850_wc)
head(sort(-table(ny_1850_wc))) # mode
boxplot(ny_1850_wc, main = "Word counts of sections in NY1850")
```

## Known problems

- NC1868 has sections without section marks, so subsequent sections are joined together not split up.

### 2015-09-22 R/split-doc.R

@@ -1,0 +1,11 @@
+split_doc <- function(file, pattern, out_file_stem) {
+  require(stringr)
+  doc <- readLines(file)
+  doc <- str_c(doc, collapse = "\n")
+  chunks <- str_split(doc, pattern)[[1]]
+  chunks <- str_trim(chunks)
+  for (i in seq_along(chunks)) {
+    filename <- str_c(out_file_stem, "-", str_pad(i * 10, 8, pad = "0"), ".txt")
+    writeLines(chunks[[i]], filename)
+  }
+}

### 2015-09-22 008-pairwise-jaccard-bag.Rmd
Pairwise comparisons

---
title: "Compare pairwise with Jaccard bag similarity"
author: "Lincoln Mullen"
date: "September 21, 2015"
output: 
  html_document:
    keep_md: true
---

```{r}
library("textreuse")
```

We are going to load the corpus from the cache, and create a comparison matrix with Jaccard bag similarity. (We will do other comparisons in different notebook so we can do this in parallel.) We will cache the matrix for use in later analyses.

We are going to test this with both shingled and skip n-grams. Here are skip n-grams.

```{r}
cache_skip <- "cache/comparison-matrix-skip-jaccard-bag.rds"
if (!file.exists(cache_skip)) {
  corpus_skip <- readRDS("cache/corpus-skip-ngrams-n7k3.rds")
  m_skip <- pairwise_compare(corpus_skip, jaccard_bag_similarity)
  saveRDS(m_skip, cache_skip)
} else {
  m_skip <- readRDS(cache_skip)
}
```

Here are shingled n-grams.

```{r}
cache_shingles <- "cache/comparison-matrix-shingles-jaccard-bag.rds"
if (!file.exists(cache_shingles)) {
  corpus_shingles <- readRDS("cache/corpus-shingle-ngrams-n7.rds")
  m_shingles <- pairwise_compare(corpus_shingles, jaccard_similarity)
  saveRDS(m_shingles, cache_shingles)
} else {
  m_shingles <- readRDS(cache_shingles)
}
```

Here is the comparison matrix for the skip n-grams.

```{r}
round(m_skip, digits = 4)
```

Here is the comparison matrix for the shingled n-grams.

```{r}
round(m_shingles, digits = 4)
```

Session info:

```{r}
sessionInfo()
```

### 2015-09-22 008-pairwise-ratio-of-matches.Rmd
Pairwise comparisons

---
title: "Compare pairwise with ratio-of-matches similarity"
author: "Lincoln Mullen"
date: "September 21, 2015"
output: 
  html_document:
    keep_md: true
---

```{r}
library("textreuse")
```

We are going to load the corpus from the cache, and create a comparison matrix with ratio-of-matches similarity. (We will do other comparisons in different notebook so we can do this in parallel.) We will cache the matrix for use in later analyses. Note that ratio of matches is directional when the other comparisons are not.

We are going to test this with both shingled and skip n-grams. Here are skip n-grams.

```{r}
cache_skip <- "cache/comparison-matrix-skip-ratio-of-matches.rds"
if (!file.exists(cache_skip)) {
  corpus_skip <- readRDS("cache/corpus-skip-ngrams-n7k3.rds")
  m_skip <- pairwise_compare(corpus_skip, ratio_of_matches, directional = TRUE)
  saveRDS(m_skip, cache_skip)
} else {
  m_skip <- readRDS(cache_skip)
}
```

Here are shingled n-grams.

```{r}
cache_shingles <- "cache/comparison-matrix-shingles-ratio-of-matches.rds"
if (!file.exists(cache_shingles)) {
  corpus_shingles <- readRDS("cache/corpus-shingle-ngrams-n7.rds")
  m_shingles <- pairwise_compare(corpus_shingles, ratio_of_matches, 
                                 directional = TRUE)
  saveRDS(m_shingles, cache_shingles)
} else {
  m_shingles <- readRDS(cache_shingles)
}
```

Here is the comparison matrix for the skip n-grams.

```{r}
round(m_skip, digits = 4)
```

Here is the comparison matrix for the shingled n-grams.

```{r}
round(m_shingles, digits = 4)
```

Session info:

```{r}
sessionInfo()
```

### 2015-09-22 scripts/clean-text.R
Additional OCR corrections

@@ -18,7 +18,8 @@ cleaned <- text %>%
   stri_replace_all_fixed(corrections$pattern, corrections$replacement,
                          vectorize_all = FALSE) %>%
   str_replace_all("\r", "") %>%
-  str_replace_all("-\n+", "")
+  str_replace_all("-\n+", "") %>%
+  str_replace_all(regex("\\uFFFD((\\s)?)"), "")
 
 write(cleaned, file = out_file)
 

### 2015-09-22 011-split-codes.Rmd
Testing split codes

@@
 ```{r}
-ny_1850_pattern <- regex("(\n§((\\s+)?)\\d+((\\.)?)|\n\\$((\\s+)?)\\d+((\\.)?)|\nchapter|\ntitle|\narticle|\nt i t l e|\nRULE \\w+\\.|\n\\d{4,}\\.|\nSEC((\\.)?)\\s+\\d+((\\.)?)|\n8EC((\\.)?)\\s+\\d+((\\.)?)|\nSE0((\\.)?)\\s+\\d+((\\.)?)|\nSEO((\\.)?)\\s+\\d+((\\.)?)|\nSEQ((\\.)?)\\s+\\d+((\\.)?))", ignore_case = TRUE)
+ny_1850_pattern <- regex("(\n§((\\s+)?)\\d+((\\.)?)|\n\\$((\\s+)?)\\d+((\\.)?)|\nchapter|\ntitle|\narticle|\nSUBDIVISION|\nt i t l e|\nRULE \\w+\\.|\n\\d{4,}\\.|\nSEC((\\.)?)\\s+\\d+((\\.)?)|\nSECTION((\\.)?)\\s+\\d+((\\.)?)|\nSECT((\\.)?)\\s+\\d+((\\.)?)|\n8EC((\\.)?)\\s+\\d+((\\.)?)|\nSE0((\\.)?)\\s+\\d+((\\.)?)|\nSEO((\\.)?)\\s+\\d+((\\.)?)|\nS((\\.)?)\\s+\\d+((\\.)?)|\nSEQ((\\.)?)\\s+\\d+((\\.)?)|\nArt((\\.)?)\\s+\\d+((\\.)?)|\nAn((\\.)?)\\s+\\d+((\\.)?)|\nAm((\\.)?)\\s+\\d+((\\.)?))", ignore_case = TRUE)
 test <- str_detect(c("\n§ 1842 This should be true", "\nThis should be false §",
@@
                      "\n8EC. 3323. true", "false",
-                     "\nSEC.   2545 true", "false"),
+                     "\nSEC.   2545 true", "false",
+                     "\nSECTION 143. true", "false"),
                    pattern = ny_1850_pattern)
@@
 split_doc("legal-codes/AZ1865.txt", ny_1850_pattern, "legal-codes-split/AZ1865")
+split_doc("legal-codes/DT1887.txt", ny_1850_pattern, "legal-codes-split/DT1887")
+split_doc("legal-codes/LA1825.txt", ny_1850_pattern, "legal-codes-split/LA1825")
+split_doc("legal-codes/MA1858.txt", ny_1850_pattern, "legal-codes-split/MA1858")
+split_doc("legal-codes/AR1868.txt", ny_1850_pattern, "legal-codes-split/AR1868")
 ```

### 2015-09-22 R/split-doc.R
Script/Make task to split codes

@@ -1,11 +1,0 @@
-split_doc <- function(file, pattern, out_file_stem) {
-  require(stringr)
-  doc <- readLines(file)
-  doc <- str_c(doc, collapse = "\n")
-  chunks <- str_split(doc, pattern)[[1]]
-  chunks <- str_trim(chunks)
-  for (i in seq_along(chunks)) {
-    filename <- str_c(out_file_stem, "-", str_pad(i * 10, 8, pad = "0"), ".txt")
-    writeLines(chunks[[i]], filename)
-  }
-}

### 2015-09-22 scripts/split-code.R

@@ -1,0 +1,20 @@
+# Split a code into chunks
+library(readr)
+library(stringr)
+
+dir.create("legal-codes-split", showWarnings = FALSE)
+args <- commandArgs(trailingOnly = TRUE)
+in_file <- args[1]
+stem <- in_file %>%
+  basename() %>%
+  str_replace("\\.txt", "")
+out_file_stem <- str_c("legal-codes-split/", stem)
+doc <- read_file(in_file)
+doc <- str_c(doc, collapse = "\n")
+pattern <- regex("(\n§((\\s+)?)\\d+((\\.)?)|\n\\$((\\s+)?)\\d+((\\.)?)|\nchapter|\ntitle|\narticle|\nSUBDIVISION|\nt i t l e|\nRULE \\w+\\.|\n\\d{4,}\\.|\nSEC((\\.)?)\\s+\\d+((\\.)?)|\nSECTION((\\.)?)\\s+\\d+((\\.)?)|\nSECT((\\.)?)\\s+\\d+((\\.)?)|\n8EC((\\.)?)\\s+\\d+((\\.)?)|\nSE0((\\.)?)\\s+\\d+((\\.)?)|\nSEO((\\.)?)\\s+\\d+((\\.)?)|\nS((\\.)?)\\s+\\d+((\\.)?)|\nSEQ((\\.)?)\\s+\\d+((\\.)?)|\nArt((\\.)?)\\s+\\d+((\\.)?)|\nAn((\\.)?)\\s+\\d+((\\.)?)|\nAm((\\.)?)\\s+\\d+((\\.)?))", ignore_case = TRUE)
+chunks <- str_split(doc, pattern)[[1]]
+chunks <- str_trim(chunks)
+for (i in seq_along(chunks)) {
+  filename <- str_c(out_file_stem, "-", str_pad(i * 10, 8, pad = "0"), ".txt")
+  writeLines(chunks[[i]], filename)
+}

### 2015-09-22 scripts/split-code.R
Additional OCR/sectioning corrections

@@ -11,7 +11,7 @@ stem <- in_file %>%
 out_file_stem <- str_c("legal-codes-split/", stem)
 doc <- read_file(in_file)
 doc <- str_c(doc, collapse = "\n")
-pattern <- regex("(\n§((\\s+)?)\\d+((\\.)?)|\n\\$((\\s+)?)\\d+((\\.)?)|\nchapter|\ntitle|\narticle|\nSUBDIVISION|\nt i t l e|\nRULE \\w+\\.|\n\\d{4,}\\.|\nSEC((\\.)?)\\s+\\d+((\\.)?)|\nSECTION((\\.)?)\\s+\\d+((\\.)?)|\nSECT((\\.)?)\\s+\\d+((\\.)?)|\n8EC((\\.)?)\\s+\\d+((\\.)?)|\nSE0((\\.)?)\\s+\\d+((\\.)?)|\nSEO((\\.)?)\\s+\\d+((\\.)?)|\nS((\\.)?)\\s+\\d+((\\.)?)|\nSEQ((\\.)?)\\s+\\d+((\\.)?)|\nArt((\\.)?)\\s+\\d+((\\.)?)|\nAn((\\.)?)\\s+\\d+((\\.)?)|\nAm((\\.)?)\\s+\\d+((\\.)?))", ignore_case = TRUE)
+pattern <- regex("(\n§((\\s+)?)\\d+((\\.)?)|\n\\$((\\s+)?)\\d+((\\.)?)|\nchapter|\ntitle|\narticle|\nSUBDIVISION|\nt i t l e|\nRULE \\w+\\.|\n\\d{4,}\\.|\nSEC((\\.)?)\\s+\\d+((\\.)?)|\nSECTION((\\.)?)\\s+\\d+((\\.)?)|\nSECT((\\.)?)\\s+\\d+((\\.)?)|\n8EC((\\.)?)\\s+\\d+((\\.)?)|\nSE0((\\.)?)\\s+\\d+((\\.)?)|\nSEO((\\.)?)\\s+\\d+((\\.)?)|\nS((\\.)?)\\s+\\d+((\\.)?)|\nSEQ((\\.)?)\\s+\\d+((\\.)?)|\nArt((\\.)?)\\s+\\d+((\\.)?)|\nAn((\\.)?)\\s+\\d+((\\.)?)|\nAm((\\.)?)\\s+\\d+((\\.)?)|\nSec\\.\n\\d+\\.)", ignore_case = TRUE)
[…]

### 2015-09-22 009-lsh-all-codes.Rmd
LSH all the codes

---
title: "Candidates for whole codes"
author: "Lincoln Mullen"
date: "September 21, 2015"
output: 
  html_document:
    keep_md: true
---

The goal for this document is to decide on the comparison measure to be used.

We are going to use LSH to compute candidate matches, with a very low threshold for potential matches.

```{r}
library("textreuse")
library("dplyr")
lsh_threshold(h = 3000, b = 1500)
```

This threshold should identify most legitimate matches.

First we create the corpus, using a minhash function.

```{r}
minhash <- minhash_generator(n = 3000, seed = 34235)
cache <- "cache/corpus-minhash-n7.rds"
if (!file.exists(cache)) {
  corpus_shingles <- TextReuseCorpus(dir = "legal-codes", 
                                    tokenizer = tokenize_ngrams, n = 7,
                                    hash_func = minhash,
                                    keep_tokens = TRUE)
  saveRDS(corpus_shingles, cache)
} else {
  corpus_shingles <- readRDS(cache)
}
```

Now we will use minhash/LSH to identify the candidates and rehash the relevant subset.

```{r}
buckets_shingles <- lsh(corpus_shingles, bands = 1500)
candidates <- lsh_candidates(buckets_shingles)
candidates_reversed <- candidates
colnames(candidates_reversed) <- c("b", "a", "score")
candidates_both <- bind_rows(candidates, candidates_reversed)
candidates_subset <- lsh_subset(candidates)
corpus_subset <- corpus_shingles[candidates_subset]
corpus_subset <- rehash(corpus_subset, hash_string)
```

Now we will compute scores for the candidates. We have to do it both ways for the `ratio_of_matches()` function since it is directional.

```{r}
scores_jaccard <- lsh_compare(candidates, corpus_subset, jaccard_similarity)
scores_ratio <- lsh_compare(candidates_both, corpus_subset, ratio_of_matches)
range01 <- function(x) { (x - min(x)) / (max(x) - min(x)) }
cf_scores <-  scores_ratio %>% left_join(scores_jaccard, by = c("a", "b"))  %>% 
  rename(ratio = score.x, jaccard = score.y)  %>% 
  filter(!is.na(jaccard)) %>% 
  mutate(jaccard_scaled = range01(jaccard), 
         ratio_scaled = range01(ratio),
         diff = jaccard_scaled - ratio_scaled) %>% 
  arrange(desc(diff))
cf_scores
```

Since there are no obvious distortions to be corrected for, and since `ratio_of_matches()` can account for texts of different length and directionality, we will use that measure for comparing entire codes to entire codes. For comparing chunks of codes, we will use the Jaccard similarity measure.

Session info:

```{r}
sessionInfo()
```

### 2015-09-22 010-compare-code-sections.Rmd
Decide on threshold for LSH

---
title: "Test comparing sections of codes"
author: "Lincoln Mullen"
date: "September 22, 2015"
output: 
  html_document:
    keep_md: true
---

```{r}
library("textreuse")
library("stringr")
library("dplyr")
```

Now we want to compare the sections of the codes to one another. Our hypothesis is that codes are borrowed section by section, so treating individual sections of codes as their own documents means that we should find higher similarities between two borrowed sections of a code than between codes as a whole. Since the sections will be of similar length, we can use the Jaccard similarity measure rather than the ratio-of-matches measure.

We will begin by figuring out the Jaccard similarity scores of a single section that we know to be borrowed, though we do not know all the borrowings. The section involves people who are disqualified from being witnesses, most notably "Indians, or persons having one fourth or more of Indian blood" or "Negroes, or persons having one half or more Negro blood," both "in an action or proceeding to which a white person is a party" (CA 1851). We have identified obvious borrowings by searching the sections. We will create a small corpus of those borrowings and do a pairwise measure of the Jaccard similarity to figure out a good threshold for borrowings. To be clear, all of these sections disallow witnesses, but several of them are clearly not direct borrowings.

## Comparing the sections

Load the sections.

```{r}
witness_files <- c("NV1861-00003640.txt", "WOOD1857-00004280.txt",
                   "CA1851-00004310.txt", "NV1861-00003900.txt", 
                   "MT1865-00003240.txt", "IN1843-00002520.txt",
                   "IL1866-00003330.txt", "CA1858-00000450.txt", 
                   "CA1850-00003110.txt", "AZ1865-00003640.txt")
witness_paths <- str_c("legal-codes-split/", witness_files)
```

We will load these as a corpus, tokenizing them with 4-grams.

```{r}
witness_corpus <- TextReuseCorpus(paths = witness_paths, 
                                  tokenizer = tokenize_ngrams, n = 4)
```

Now we will do a pairwise comparison with Jaccard similarity.

```{r}
witness_comparison <- pairwise_compare(witness_corpus, jaccard_similarity)
```

What are the mean and median values for comparison, as well as the range?

```{r}
mean(witness_comparison, na.rm = TRUE)
median(witness_comparison, na.rm = TRUE)
range(witness_comparison, na.rm = TRUE)
```

## Matches

Let's examine the highest and lowest scores, starting with the highest.

```{r}
witness_candidates <- pairwise_candidates(witness_comparison) %>% 
  arrange(desc(score))
head(witness_candidates, 10)
```

We can check the text of some of these codes to see that they are in fact matches.

```{r}
content(witness_corpus[["CA1851-00004310"]])
content(witness_corpus[["AZ1865-00003640"]])
content(witness_corpus[["NV1861-00003640"]])
content(witness_corpus[["WOOD1857-00004280"]])
content(witness_corpus[["CA1858-00000450"]])
content(witness_corpus[["MT1865-00003240"]])
```

These are all valid matches, despite the presence in some cases of extraneous texts, such as tables of contents. Ideally this extra text would be removed by sectioning the codes, but since sectioning is an inexact process, it is good that we can detect matches even with OCR and sectioning problems.

## Mismatches

The mismatches are either matches with a score of `0`, or very low scores.

```{r}
tail(witness_candidates, 5)
```

Are these documents with a score of zero actually different documents?

```{r}
content(witness_corpus[["IL1866-00003330"]])
content(witness_corpus[["IN1843-00002520"]])
content(witness_corpus[["NV1861-00003900"]])
content(witness_corpus[["WOOD1857-00004280"]])
```

While these sections do all disqualify witnesses on the basis of race, they are clearly not word-for-word borrowings. So we would not expect to detect them as borrowings.

What about borrowings with low scores?

```{r}
witness_candidates %>% 
  filter(score > 0) %>% 
  tail()
```

```{r}
content(witness_corpus[["NV1861-00003900"]])
content(witness_corpus[["MT1865-00003240"]])
content(witness_corpus[["IN1843-00002520"]])
```

These are also not borrowings from one another, as expected.

## Conclusion

We can conclude that measures of Jaccard similarity do work for detecting actual borrowings. We will want to set the threshold for LSH detection relatively low, but above about `0.1`.

### 2015-09-23 011-sections-ny-ca.Rmd
Testing LSH on sectioned codes

---
title: "LSH for sections of CA and NY"
author: "Lincoln Mullen"
date: "September 22, 2015"
output: 
  html_document:
    keep_md: true
---

```{r, message=FALSE}
library("textreuse")
library("stringr")
library("dplyr")
source("R/extract_code_names.R")
```

As a test run for using LSH on all the codes, we are going to run this on just NY1850 and CA1851 and see if we can detect matches between sections of that code.

We begin by identifying all of the sections of those two codes:

```{r}
paths <- c(Sys.glob("legal-codes-split/NY1850*"), 
           Sys.glob("legal-codes-split/CA1851*"))
```

That is `r prettyNum(length(paths), big.mark = ",")` sections. We want to eliminate extremely small sections. So we are going to check the sizes of all of the files. Since we know that a file with five words has 32 bytes (using `du -b`) we will remove all files with fewer than 32 bytes. This will also take care of the empty `-SPLIT` files that we use for Make tasks. (Addendum, in the future we will do this by checking the word count directly.)

```{r}
sizes <- file.size(paths)
paths <- paths[sizes >= 34]
```

Now we have `r prettyNum(length(paths), big.mark = ",")` sections.

## Loading, tokenizing, and minhashing

We need an appropriate threshold for LSH. We are aiming for greater than `0.1`. So these values seem give us a slightly higher threshold.

```{r}
lsh_threshold(1500, 500)
```

We load and tokenize those files with 4-grams.

```{r}
minhash <- minhash_generator(1500, seed = 343653)
corpus <- TextReuseCorpus(paths = paths, 
                          tokenizer = tokenize_ngrams, n = 4,
                          hash_func = minhash,
                          keep_tokens = TRUE)
```

Now we can run LSH on the corpus to find the matches.

```{r}
buckets <- lsh(corpus, bands = 500)
candidates <- lsh_candidates(buckets) 
corpus <- rehash(corpus, hash_string)
scores <- lsh_compare(candidates, corpus, jaccard_similarity)
scores_filtered <- scores %>% 
  mutate(code_a = extract_code_names(a),
         code_b = extract_code_names(b)) %>% 
  filter(code_a != code_b)
```

We have `r nrow(scores_filtered)` matches between the two codes. If we filter so that we only keep track of matches with a similarity of `0.1`, there are `r nrow(filter(scores_filtered, score >= 0.1))`. For comparison, there are 691 sections in the split CA1851 code.

## Conclusions

We have genuine matches, even on the low Jaccard scores. 4-grams are too short because phrases like "in the same manner" and "in a civil action" are very common. We think 5-grams are the best length to avoid common phrases. The best threshold for distinguishing genuine matches from false positives is `0.1`.

### 2015-09-23 R/extract_code_names.R

@@ -1,0 +1,4 @@
+extract_code_names <- function(section_names) {
+  splits <- str_split(section_names, "-")
+  vapply(splits, `[`, character(1), 1)
+}

### 2015-09-24 014-network-analysis-code-to-code.Rmd
Network graphs of code to code comparions

---
title: "Network analysis of code to code comparison"
author: "Lincoln Mullen"
date: "September 24, 2015"
output: 
  html_document:
    keep_md: true
---

```{r warning=FALSE}
library("textreuse")
library("stringr")
library("dplyr")
library("igraph")
source("R/extract-date.R")
source("R/plot_network.R")
```

Load the corpus previously created and hashed. We won't compare the extended codes.

```{r}
cache <- "cache/corpus-shingle-ngrams-n7.rds"
corpus_shingles <- readRDS(cache)
corpus_shingles <- corpus_shingles[!str_detect(names(corpus_shingles), "extended")]
```

Now we will do the pairwise comparison of the codes.

```{r}
cache_pairwise <- "cache/comparison-matrix-pairwise-n7-ratio.rds"
if (!file.exists(cache_pairwise)) {
  comparisons <- pairwise_compare(corpus_shingles, ratio_of_matches,
                                  directional = TRUE)
  saveRDS(comparisons, cache_pairwise)
} else {
  comparisons <- readRDS(cache_pairwise)
}
```

Now we need to filter the obviously anachronistic comparisons. The way to read the directional matrix is "column borrows from row." Therefore we want to give a cell in the matrix an `NA` value if the year in the column is greater than the year in the row.

```{r}
indices <- arrayInd(1:length(comparisons), dim(comparisons), useNames = TRUE)
check_anachronism <- function(x) {
  row <- x["row"]
  col <- x["col"]
  row_date <- extract_date(rownames(comparisons)[row])
  col_date <- extract_date(colnames(comparisons)[col])
  if (col_date < row_date) comparisons[row, col] <<- NA
}
throwaway <- apply(indices, MARGIN = 1, check_anachronism)
rm(throwaway)
```

Now we are going to remove matches below a threshold. Also, we have to make `NA` values into `0` values so that there are no edges drawn in igraph.

```{r}
comparisons_filtered <- comparisons
match_threshold <- 0.05
comparisons_filtered[comparisons_filtered < match_threshold] <- NA
comparisons_filtered[is.na(comparisons_filtered)] <- 0
```

Let's make a network graph, using this matrix as an adjacency matrix.

```{r}
g <- graph.adjacency(comparisons_filtered, mode = "directed", weighted = TRUE,
                     diag = FALSE) 
set.seed(4821)
l <- layout.fruchterman.reingold(g, weights = E(g)$weight)
par(mar = c(0,0,1,0))
plot(g, edge.width = E(g)$weight * 8, layout = l,
     edge.arrow.size = 0.15, vertex.size = 5)
title("Codes of Civil Procedure")
```

Using a 5% threshold seems to deliver the appropriate clusters. There is a clear Field Code cluster, and the laws on the periphery make sense. Most legislation from the South, Mid-Atlantic, and New England was not directly related to the Field text, and the periphery comprises most of that legislation. Morever, the lines of connection in the periphery make sense. We know from independent sources that Maryland looked to English reforms, and there is indeed a cluster connecting Maryland to British reform acts. Florida enacted the Field Code as a Reconstruction measure in 1870, but then repealed it entirely at the end of the decade. This graph shows a connection between late- and early-century Florida with no connection to FL1870, which will be found in the Field Code cluster. This is all what we would expect, given information in independent sources.

Next we want to get the families of codes. We will decompose the main graph into its components, then plot a network graph of each.

```{r}
families <- decompose(g, min.vertices = 2)
```

Plot the biggest family.

```{r}
plot_network(families[[1]], graph_title = "Field codes")
```

This is still a bit of a hairball, even when zoomed in quite a bit. The difficulty is this. Suppose California borrows from New York, and Nevada borrows from California. We still detect the borrowings of Nevada from New York, even though they are not direct. So let's make a network of only the biggest borrowings for each code, i.e., the maximum value in each column.

```{r}
comparisons_max <- comparisons_filtered
col_max_index <- apply(comparisons_max, MARGIN = 2, max, na.rm = TRUE)
throwaway <- lapply(names(col_max_index), function(n) {
  subset <- comparisons_max[,n] != col_max_index[n]
  comparisons_max[subset, n] <<- 0
})
```

Now make a network graph of just those biggest comparions.

```{r}
g_max <- graph.adjacency(comparisons_max, mode = "directed", weighted = TRUE,
                         diag = FALSE) 
plot_network(g_max, "Biggest borrowings")
```

That is a far better picture of what is going on, because we can actually see the family tree effect. There are some problems, e.g., NC1868 is most like DT1868, but it should actually be connected to NY 1850 (which is close in value). Including two connections, or just removing known incorrect values, would make the graph better for communicating.

Let's get just the main family.

```{r}
plot_network(decompose(g_max)[[1]],
             graph_title = "Field codes, biggest borrowings")
```

It is difficult to filter the matrix of scores. Let's turn that into a data frame of pairs of nodes with edge weights (i.e., the scores), and then manipulate that with dplyr's richer vocabulary.

```{r}
borrowings <- pairwise_candidates(comparisons, directional = TRUE) %>% 
  filter(score >= 0.05) %>% 
  rename(origin = a, destination = b) %>% 
  mutate(origin_date = extract_date(origin),
         destination_date = extract_date(destination)) %>% 
  filter(destination_date >= origin_date)
borrowings
```

Let's keep only the top two borrowings for each code and turn that into a graph.

```{r}
g_top2 <- borrowings %>% 
  group_by(destination) %>% 
  top_n(2, score) %>% 
  graph.data.frame(directed = TRUE)
E(g_top2)$weight <- E(g_top2)$score
plot_network(decompose(g_top2)[[1]], "Top 2 borrowings")
```

We will have to decide if the top 1 connections chart with corrections or the top 2 connections is better. But for now these seem like accurate results.

### 2015-09-24 R/extract-date.R

@@ -1,0 +1,4 @@
+extract_date <- function(x) {
+  require(stringr)
+  as.integer(str_extract(x, "\\d{4}"))
+}

### 2015-09-24 R/plot_network.R

@@ -1,0 +1,12 @@
+plot_network <- function(g, graph_title = "Network graph") {
+  require("igraph")
+  l <- layout.fruchterman.reingold(g, weights = E(g)$weight) * 10
+  # http://stackoverflow.com/questions/5968612/how-do-i-lengthen-edges-in-an-igraph-network-plot-layout-fruchterman-reingold
+#   l <- layout.fruchterman.reingold(g, niter = 500,
+#                                    area = vcount(g) ^ 2.3,
+#                                    repulserad = vcount(g) ^ 2.8)
+  par(mar = c(0,0,1,0))
+  plot(g, edge.width = E(g)$weight * 12, layout = l,
+       edge.arrow.size = 0.15, vertex.size = 5)
+  title(graph_title)
+}

### 2015-09-24 014-network-analysis-code-to-code.Rmd
Don't like package loading messages

@@
 
-```{r warning=FALSE}
+```{r message=FALSE}
 library("textreuse")

### 2015-09-25 016-manual-lsh.Rmd
Manual LSH

---
title: "Calculate minhash pairs manually"
author: "Lincoln Mullen"
date: "September 25, 2015"
output: 
  html_document:
    keep_md: true
---

As the textreuse package is currently implemented, the `lsh()` function gets bogged down with large numbers of documents. The implementation with the hash package is probably unneccessary; we can do it a lot faster with dplyr. So we will implement a specific solution here before revising the textreuse package. (Thanks for an assist from [Stack Overflow](http://stackoverflow.com/questions/32783727/turn-ordered-pairs-into-unordered-pairs-in-a-data-frame-with-dplyr/32784685#32784685).)

```{r message=FALSE}
library("textreuse")
library("dplyr")
library("digest")
library("stringr")
library("tidyr")
library("readr")
```

Load the corpus.

```{r}
corpus <- readRDS("cache/corpus-n5-minhash-h1500-seed623.rds")
```

```{r}
bands <- 500
hashes <- 1500
rows <- hashes / bands
docs <- length(corpus)
bands_vec <- rep(vapply(1:bands, function(i) rep(i, rows), integer(rows)), docs)

buckets_cache <- "cache/buckets-dplyr-lsh.rds"
if (!file.exists(buckets_cache)) {
  buckets <-  corpus %>%
    hashes() %>%
    as_data_frame() %>%
    gather(doc, hash) %>%
    mutate(doc = as.character(doc),
           band = bands_vec) %>%
    group_by(doc, band) %>%
    summarize(buckets = digest(hash)) %>%
    select(-band)
  rm(bands_vec)
  saveRDS(buckets, file = buckets_cache)
} else {
  buckets <- readRDS(buckets_cache)
}
```

Now find the ordered pairs of matches:

```{r}
ordered <- buckets %>% 
  ungroup() %>%
  left_join(buckets, by = "buckets") %>%
  select(-buckets) %>%
  distinct() %>% 
  filter(doc.x != doc.y) %>%
  arrange(doc.x, doc.y)
```

Now remove the duplicate pairs.

```{r}
unordered <- ordered %>% 
  distinct(dn = pmin(doc.x, doc.y), up = pmax(doc.x, doc.y)) %>%
  select(-up, -dn) %>%
  rename(a = doc.x, b = doc.y) %>%
  arrange(a, b) %>% 
  mutate(score = NA_real_) 
```

Save the results.

```{r}
write_csv(ordered, path = "out/all-sections-unordered-pairs.csv")
```

Rehash the corpus to use for Jaccard similarity.

```{r}
corpus_rehashed <- rehash(corpus, hash_string)
```

Compute the Jaccard similarity scores and save the results.

```{r}
scores <- unordered %>% 
  lsh_compare(corpus_rehashed, jaccard_similarity) %>% 
  rename(similarity = score) %>% 
  mutate(dissimilarity = 1 - similarity)
write_csv(scores, path = "out/scores-all-sections-pairs.csv")
scores
```

### 2015-09-25 017-best-section-matches.Rmd
Investigate section matches by code

---
title: "Best matches for code sections"
author: "Lincoln Mullen"
date: "September 25, 2015"
output: 
  html_document:
    keep_md: true
---

```{r message=FALSE}
library("dplyr")
library("stringr")
library("readr")
library("ggplot2")
library("RColorBrewer")
source("R/extract-date.R")
source("R/extract_code_names.R")
```

The aim of this notebook is to create a function that takes a code's abbreviation (e.g., `NY1850`) and creates a data frame with each of the sections in that code with the best match to a non-anachronistic code.

Read in the data.

```{r}
scores <- read_csv("out/scores-all-sections-pairs.csv")
scores <- scores %>% 
  rename(section_a = a, section_b = b) %>% 
  mutate(code_a = extract_code_names(section_a),
         code_b = extract_code_names(section_b),
         year_a = extract_date(code_a),
         year_b = extract_date(code_b))
scores
```

```{r}
best_section_matches <- function(code_name, scores, threshold = 0.1, top = 1) {
  require("dplyr")
  require("stringr")
  matches <- scores %>% 
    filter(code_a == code_name | code_b == code_name) %>% 
    mutate(match_code = ifelse(code_a == code_name, code_b, code_a),
           code_of_interest = ifelse(code_a == code_name, code_a, code_b),
           match_section = ifelse(code_a == code_name, section_b, section_a),
           section_of_interest = ifelse(code_a == code_name, section_a, section_b),
           match_year = ifelse(code_a == code_name, year_b, year_a)) %>% 
    filter(match_code != code_of_interest,
           match_year <= extract_date(code_name),
           similarity >= threshold) %>% 
    select(code_of_interest, section_of_interest, match_code, match_section,
           similarity, dissimilarity) %>% 
    group_by(section_of_interest) %>%
    arrange(desc(similarity)) %>% 
    top_n(top, similarity)

  all_sections <- Sys.glob(str_c("legal-codes-split/", code_name, "-0*")) %>% 
    str_replace("legal-codes-split/", "") %>% 
    str_replace("\\.txt", "")
  all <- data_frame(all_sections)

  all %>% 
    left_join(matches, by = c("all_sections" = "section_of_interest")) %>% 
    select(-code_of_interest)
} 
```

Also a function to calculate summary statistics.

```{r}
summarize_borrowings <- function(section_list) {
  section_list %>% 
    group_by(match_code) %>% 
    summarize(mean_similarity = mean(similarity),
              n = n()) %>% 
    mutate(percentage_sections = n / nrow(section_list)) %>% 
    arrange(desc(n))
}
```

Apply this to three codes:

```{r}
CA1851 <- best_section_matches("CA1851", scores, threshold = 0.2)
CA1851
summarize_borrowings(CA1851)
IA1859 <- best_section_matches("IA1859", scores, threshold = 0.2)
IA1859
summarize_borrowings(IA1859)
UT1870 <- best_section_matches("UT1870", scores, threshold = 0.2)
UT1870
summarize_borrowings(UT1870)
```

Make a plot of code borrowings.

```{r}
plot_borrowings <- function(state_borrowings) {
  state_borrowings %>% 
    mutate(state = str_extract(match_code, "\\w\\w")) %>% 
    ggplot(aes(x = as.factor(all_sections), y = similarity, fill = state)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    scale_x_discrete(labels = NULL) +
    scale_y_continuous(limits = c(0, 1)) +
    scale_fill_brewer(palette = "Dark2")
}
```

Plot some borrowings:

```{r}
plot_borrowings(CA1851)
plot_borrowings(UT1870)
```

### 2015-09-26 018-families-of-sections.Rmd
Families of sections

---
title: "Clustering"
author: "Lincoln Mullen"
date: "September 25, 2015"
output: 
  html_document:
    keep_md: true
---

```{r, message = FALSE}
library("readr")
library("dplyr")
library("igraph")
```

How are all of the sections related to one another? We can think of this as a network problem. Sections that are similar have a relationship, but are very unlikely to have relationships to every other section. So we can use our comparisons then decompose that big network graph into families of codes.

Read the data.

```{r}
comparisons <- read_csv("out/scores-all-sections-pairs.csv") %>% 
  select(-dissimilarity) %>% 
  rename(weight = similarity) %>% 
  filter(weight > 0.1)
```

```{r}
g <- graph.data.frame(comparisons, directed = "FALSE")
families <- decompose(g, min.vertices = 2)
num_sections <- vapply(families, function(x) { length(V(x))}, integer(1))
head(sort(-num_sections), 20)
which(num_sections > 10 & num_sections < 15)
```

Plot those and look at their vertices.

```{r}
V(families[[4]])
plot(families[[4]])
V(families[[1084]])
plot(families[[1084]])
V(families[[4635]])
plot(families[[4635]])
```

### 2015-09-26 019-section-based-code-network.Rmd
Section based codes network

---
title: "Network of all codes based on sections borrowed"
author: "Lincoln Mullen"
date: "September 26, 2015"
output: 
  html_document:
    keep_md: true
---

Earlier we made a network graph of all codes using ratio of matches in a code to code comparison. Now lets make a network graph based on sections borrowed.

```{r message=FALSE}
library("readr")
library("igraph")
library("dplyr")
library("textreuse")
library("stringr")
source("R/best-section-matches.R")
source("R/summarize-borrowings.R")
source("R/extract-date.R")
source("R/extract_code_names.R")
```

Read the data.

```{r}
borrowings <- read_csv("out/scores-all-sections-pairs.csv") %>% 
  rename(section_a = a, section_b = b) %>% 
  mutate(code_a = extract_code_names(section_a),
         code_b = extract_code_names(section_b),
         year_a = extract_date(code_a),
         year_b = extract_date(code_b))
borrowings
```

All the codes in our corpus. Which codes aren't included?

```{r}
codes <- c(borrowings$code_a, borrowings$code_b) %>% unique
all_codes <- Sys.glob("legal-codes/*") %>% 
  str_replace("legal-codes/", "") %>% 
  str_replace("\\.txt", "") %>% 
  extract_code_names()
setdiff(all_codes, codes)
```

All the codes that aren't included are plausibly not connected to the corpus.

Calculate section matches and summarize them for a single code.

```{r}
CA1851 <- best_section_matches("CA1851", scores = borrowings, threshold = 0.2)
CA1851
summarize_borrowings(CA1851)
```

Apply that to all the codes.

```{r}
section_pct <- codes %>% 
  lapply(best_section_matches, scores = borrowings, threshold = 0.2) %>% 
  lapply(summarize_borrowings) %>% 
  bind_rows()
section_pct
```

Do some filtering and munge into an edge list.

```{r}
edges <- section_pct %>% 
  filter(percentage_sections >= 0.05,
         !is.na(match_code)) %>% 
  select(original_code, match_code, weight = percentage_sections)
edges
```

Turn that into a graph.

```{r}
g <- graph.data.frame(edges, directed = TRUE)
set.seed(4821)
l <- layout.fruchterman.reingold(g, weights = E(g)$weight)
par(mar = c(0,0,1,0))
plot(g, edge.width = E(g)$weight * 8, layout = l,
     edge.arrow.size = 0.15, vertex.size = 5)
title("Codes of Civil Procedure by percentage of sections")
```

### 2015-09-26 R/best-section-matches.R

@@ -1,0 +1,29 @@
+best_section_matches <- function(code_name, scores, threshold = 0.1, top = 1) {
+  require("dplyr")
+  require("stringr")
+  matches <- scores %>%
+    filter(code_a == code_name | code_b == code_name) %>%
+    mutate(match_code = ifelse(code_a == code_name, code_b, code_a),
+           code_of_interest = ifelse(code_a == code_name, code_a, code_b),
+           match_section = ifelse(code_a == code_name, section_b, section_a),
+           section_of_interest = ifelse(code_a == code_name, section_a, section_b),
+           match_year = ifelse(code_a == code_name, year_b, year_a)) %>%
+    filter(match_code != code_of_interest,
+           match_year <= extract_date(code_name),
+           similarity >= threshold) %>%
+    select(code_of_interest, section_of_interest, match_code, match_section,
+           similarity, dissimilarity) %>%
+    group_by(section_of_interest) %>%
+    arrange(desc(similarity)) %>%
+    top_n(top, similarity) %>%
+    mutate(original_code = code_name)
+
+  all_sections <- Sys.glob(str_c("legal-codes-split/", code_name, "-0*")) %>%
+    str_replace("legal-codes-split/", "") %>%
+    str_replace("\\.txt", "")
+  all <- data_frame(all_sections)
+
+  all %>%
+    left_join(matches, by = c("all_sections" = "section_of_interest")) %>%
+    select(-code_of_interest)
+}

### 2015-09-26 R/summarize-borrowings.R

@@ -1,0 +1,10 @@
+summarize_borrowings <- function(section_list) {
+  section_list %>%
+    group_by(match_code) %>%
+    summarize(original_code = unique(original_code),
+              mean_similarity = mean(similarity),
+              n = n()) %>%
+    mutate(percentage_sections = n / nrow(section_list)) %>%
+    arrange(desc(n)) %>%
+    select(original_code, match_code, mean_similarity, n, percentage_sections)
+}

### 2015-10-08 008-pairwise-jaccard.Rmd
Round matrix
Simplify notebook generation, improve figures

@@
 date: "September 21, 2015"
-output: 
-  html_document:
-    keep_md: true
 ---
+
+```{r}
+library("textreuse")
+```
 
@@
 
+We are going to test this with both shingled and skip n-grams. Here are skip n-grams.
+
 ```{r}
-library("textreuse")
-
-cache <- "cache/comparison-matrix-jaccard.rds"
-if (!file.exists(cache)) {
-  corpus <- readRDS("cache/corpus-skip-ngrams-n7k3.rds")
-  m <- pairwise_compare(corpus, jaccard_similarity)
-  saveRDS(m, cache)
+cache_skip <- "cache/comparison-matrix-skip-jaccard.rds"
+if (!file.exists(cache_skip)) {
+  corpus_skip <- readRDS("cache/corpus-skip-ngrams-n7k3.rds")
+  m_skip <- pairwise_compare(corpus_skip, jaccard_similarity)
+  saveRDS(m_skip, cache_skip)
 } else {
-  m <- readRDS(cache)
+  m_skip <- readRDS(cache_skip)
 }
@@
 
-Here is the comparison matrix:
+Here are shingled n-grams.
 
 ```{r}
-m
+cache_shingles <- "cache/comparison-matrix-shingles-jaccard.rds"
+if (!file.exists(cache_shingles)) {
+  corpus_shingles <- readRDS("cache/corpus-shingle-ngrams-n7.rds")
+  m_shingles <- pairwise_compare(corpus_shingles, jaccard_similarity)
+  saveRDS(m_shingles, cache_shingles)
+} else {
+  m_shingles <- readRDS(cache_shingles)
+}
+```
+
+Here is the comparison matrix for the skip n-grams.
+
+```{r}
+round(m_skip, digits = 4)
+```
+
+Here is the comparison matrix for the shingled n-grams.
+
+```{r}
+round(m_shingles, digits = 4)
 ```

### 2015-10-08 016-manual-lsh.Rmd
Simplify notebook generation, improve figures

@@
 date: "September 25, 2015"
-output: 
-  html_document:
-    keep_md: true
 ---
@@
 ```{r message=FALSE}
+library("readr")
 library("textreuse")
@@
 library("tidyr")
-library("readr")
 ```
@@
 ```{r}
-corpus <- readRDS("cache/corpus-n5-minhash-h1500-seed623.rds")
+cache <- "cache/corpus-n5-minhash-h1500-seed623.rds"
+if (!file.exists(cache)) {
+  corpus <- TextReuseCorpus(dir = "legal-codes-split", tokenizer = NULL)
+  wc <- wordcount(corpus)
+  corpus <- corpus[wc > 5]
+  minhash <- minhash_generator(n = 1500, seed = 623)
+  corpus <- tokenize(corpus, tokenizer = tokenize_ngrams, n = 5,
+                     hash_func = minhash, keep_tokens = TRUE)
+  saveRDS(corpus, file = cache)
+} else {
+  corpus <- readRDS(cache)
+}
 ```

### 2015-10-28 scripts/split-code.R
Less padding of split filenames

@@ -15,6 +15,6 @@ pattern <- regex("(\n§((\\s+)?)\\d+((\\.)?)|\n\\$((\\s+)?)\\d+((\\.)?)|\nchapte
 chunks <- str_split(doc, pattern)[[1]]
 chunks <- str_trim(chunks)
 for (i in seq_along(chunks)) {
-  filename <- str_c(out_file_stem, "-", str_pad(i * 10, 8, pad = "0"), ".txt")
+  filename <- str_c(out_file_stem, "-", str_pad(i * 10, 6, pad = "0"), ".txt")
   writeLines(chunks[[i]], filename)
 }

### 2015-10-28 scripts/split-code.R
Modify splitting code for different files

@@ -1,6 +1,6 @@
 # Split a code into chunks
-library(readr)
-library(stringr)
+library("readr")
+library("stringr")
 
 dir.create("legal-codes-split", showWarnings = FALSE)
 args <- commandArgs(trailingOnly = TRUE)
@@ -11,8 +11,26 @@ stem <- in_file %>%
 out_file_stem <- str_c("legal-codes-split/", stem)
 doc <- read_file(in_file)
 doc <- str_c(doc, collapse = "\n")
-pattern <- regex("(\n§((\\s+)?)\\d+((\\.)?)|\n\\$((\\s+)?)\\d+((\\.)?)|\nchapter|\ntitle|\narticle|\nSUBDIVISION|\nt i t l e|\nRULE \\w+\\.|\n\\d{4,}\\.|\nSEC((\\.)?)\\s+\\d+((\\.)?)|\nSECTION((\\.)?)\\s+\\d+((\\.)?)|\nSECT((\\.)?)\\s+\\d+((\\.)?)|\n8EC((\\.)?)\\s+\\d+((\\.)?)|\nSE0((\\.)?)\\s+\\d+((\\.)?)|\nSEO((\\.)?)\\s+\\d+((\\.)?)|\nS((\\.)?)\\s+\\d+((\\.)?)|\nSEQ((\\.)?)\\s+\\d+((\\.)?)|\nArt((\\.)?)\\s+\\d+((\\.)?)|\nAn((\\.)?)\\s+\\d+((\\.)?)|\nAm((\\.)?)\\s+\\d+((\\.)?)|\nSec\\.\n\\d+\\.)", ignore_case = TRUE)
-chunks <- str_split(doc, pattern)[[1]]
+
+# Use pattern_clean on files we have cleaned up; otherwise use pattern_fuzzy. We will assume that a file has been cleaned up unless it matches a black list.
[…]

### 2015-10-29 scripts/split-code.R
Rerun splits for newly sectioned codes

@@ -23,7 +23,7 @@ uncleaned_files <- c("BI1859", "CA1868short", "CO1858", "CT1854", "CT1879",
                      "MA1836", "MA1851", "MA1858", "ME1840", "MI1853", "MO1835",
                      "MS1848", "ND1877short", "NH1842", "NJ1847", "NM1865",
                      "OH1853short", "OH1879", "UT1884", "VA1841", "VA1860",
-                     "WA1873", "WI1849", "WI1858", "WV1868")
+                     "WI1849", "WV1868")
 
 if (any(str_detect(out_file_stem, uncleaned_files))) {
   chunks <- str_split(doc, pattern_fuzzy)[[1]]

### 2015-10-30 020-lsh-with-package.Rmd
LSH the corpus

---
title: "Use package"
author: "Lincoln Mullen"
date: "October 19, 2015"
output: html_document
---

We have refined our technique for extracting matches. So the work in the document supercedes all previous work. The aim is to create the data frame of matches and other results and cache them for future use.

```{r}
library("textreuse")
library("dplyr")
options("mc.cores" = 6L)
```

Create the corpus.

```{r}
cache_corpus <- "cache/corpus-sections-minash-n1500-seed623.rda"
if (!file.exists(cache_corpus)) {
  message("Creating the corpus")
  minhash <- minhash_generator(n = 1500, seed = 623)
  sections <- TextReuseCorpus(dir = "legal-codes-split/",
                              tokenizer = tokenize_ngrams, n = 5,
                              keep_tokens = FALSE,
                              minhash_func = minhash)
  save(sections, minhash, file = cache_corpus)
} else {
  message("Loading corpus from cache")
  load(file = cache_corpus)
}
```

Compute the LSH candidates, then compare them.

```{r}
cache_lsh <- "cache/lsh-sections.rda"
if (!file.exists(cache_lsh)) {
  message("Running LSH analysis")
  section_buckets <- lsh(sections, bands = 500)
  section_candidates <- lsh_candidates(section_buckets)
  section_scores <- lsh_compare(section_candidates, sections, jaccard_similarity)
  save(section_buckets, section_candidates, section_scores, file = cache_lsh)
  saveRDS(section_scores, "cache/section-scores.rds")
} else {
  message("Loading LSH objects from cache")
  load(file = cache_lsh)
}
```

How many pairs of matches do we have above `0.1` Jaccard score?

```{r}
section_scores %>% 
  filter(score > 0.1) %>% 
  nrow()
```

### 2015-10-31 020-lsh-with-package.Rmd
Redo the LSH with new sections and smarter minhashes/bands

@@
 
-```{r}
+```{r message=FALSE}
 library("textreuse")
@@
 
+We want to have the smallest number of hashes and bands while still detecting all reasonable matchs. We will set the bands and number of minhashes as follows.
+
+```{r}
+h <- 120
+b <- 60
+lsh_threshold(h, b)
+```
+
 Create the corpus.
@@
 ```{r}
-cache_corpus <- "cache/corpus-sections-minash-n1500-seed623.rda"
+cache_corpus <- "cache/corpus-sections-minash-n120-seed623.rda"
 if (!file.exists(cache_corpus)) {
-  message("Creating the corpus")
-  minhash <- minhash_generator(n = 1500, seed = 623)
+  message("Creating the corpus.")
+  minhash <- minhash_generator(n = h, seed = 623)
   sections <- TextReuseCorpus(dir = "legal-codes-split/",
@@
 } else {
-  message("Loading corpus from cache")
+  message("Loading corpus from cache.")
   load(file = cache_corpus)
@@
 if (!file.exists(cache_lsh)) {
-  message("Running LSH analysis")
-  section_buckets <- lsh(sections, bands = 500)
+  message("Running LSH analysis.")
+  section_buckets <- lsh(sections, bands = b)
   section_candidates <- lsh_candidates(section_buckets)
@@
 } else {
-  message("Loading LSH objects from cache")
+  message("Loading LSH objects from cache.")
   load(file = cache_lsh)

### 2015-11-04 022-visualizations-for-article.Rmd
Network graph with revised data

---
title: "Visualizations for article"
author: "Lincoln Mullen"
date: "November 3, 2015"
output: html_document
---

```{r message=FALSE}
library("readr")
library("igraph")
library("dplyr")
library("stringr")
library("parallel")
library("textreuse")
source("R/best-section-matches.R")
source("R/summarize-borrowings.R")
source("R/extract-date.R")
source("R/extract_code_names.R")
options("mc.cores" = 6L)
```

Read the data.

```{r}
cache_corpus <- "cache/corpus-sections-minash-n120-seed623.rda"
load(file = cache_corpus)
cache_lsh <- "cache/lsh-sections.rda"
load(file = cache_lsh)
borrowings <- section_scores %>% 
  rename(section_a = a, section_b = b, similarity = score) %>% 
  mutate(dissimilarity = 1 - similarity,
         code_a = extract_code_names(section_a),
         code_b = extract_code_names(section_b),
         year_a = extract_date(code_a),
         year_b = extract_date(code_b))
codes <- c(borrowings$code_a, borrowings$code_b) %>% unique()
```

Calculate section matches and summarize them for a single code.

```{r}
CA1851 <- best_section_matches("CA1851", borrowings, threshold = 0.2)
CA1851
summarize_borrowings(CA1851)
```

Apply that to all the codes.

```{r}
section_pct <- codes %>% 
  mclapply(best_section_matches, scores = borrowings, threshold = 0.2)  %>% 
  mclapply(summarize_borrowings) %>% 
  bind_rows()
section_pct
```

Do some filtering and munge into an edge list.

```{r}
# Note that original code is a misnomer here
edges <- section_pct %>% 
  mutate(original_date = extract_date(original_code),
         match_date = extract_date(match_code)) %>% 
  filter(percentage_sections >= 0.05,
         !is.na(match_code),
         original_code >= match_code) %>% 
  select(original_code, match_code, weight = percentage_sections)
edges
```

Turn that into a graph.

```{r}
g <- graph_from_data_frame(edges, directed = TRUE)
set.seed(4821)
l <- layout.fruchterman.reingold(g, weights = E(g)$weight)
par(mar = c(0,0,1,0))
plot(g, edge.width = E(g)$weight * 8, layout = l,
     edge.arrow.size = 0.65, vertex.size = 5)
title("Codes of Civil Procedure by percentage of sections")
```

### 2015-11-06 023-sparse-matrix.Rmd
Clustering of sections with affinity propagation

---
title: "Sparse matrix of comparisons"
author: "Lincoln Mullen"
date: "November 5, 2015"
output: html_document
---

Our data is bigger than anticipated when the number of section by section comparisons is stored as a non-sparse matrix. So we are going to read in the section comparisons and convert them to a sparse matrix.

```{r, message=FALSE}
library("Matrix")
library("dplyr")
library("readr")
library("textreuse")
source("R/extract-date.R")
source("R/extract_code_names.R")
cache_lsh <- "cache/lsh-sections.rda"
load(file = cache_lsh)
cache_corpus <- "cache/corpus-sections-minash-n120-seed623.rda"
load(file = cache_corpus)
```

Filter the sections down to a meaningful value.

```{r}
scores <- section_scores %>% 
  filter(score >= 0.1)
scores
nrow(scores)
```

Get the sections involved:

```{r}
section_names <- lsh_subset(scores)
head(section_names, 10)
length(section_names)
```

Create a look up data frame of index positions

```{r}
lookup <- data_frame(section_names, index = 1:length(section_names))
lookup
scores <- scores %>% 
  left_join(lookup, by = c("a" = "section_names")) %>% 
  left_join(lookup, by = c("b" = "section_names")) 
scores
```

Create the sparse matrix.

```{r}
n <- length(section_names)
m <- sparseMatrix(i = scores$index.x, j = scores$index.y, x = scores$score,
                  dims = c(n, n), symmetric = TRUE)
colnames(m) <- section_names
rownames(m) <- section_names
```

And write it to a file.

```{r}
writeMM(m, file = "out/sparse-section-similarity-matrix.MM")
write_csv(scores, "out/section-scores.csv")
```

Now use affinity propagation clustering to create clusters.

```{r}
library("apcluster")
clu <- apcluster(s = m,
                 # maxits = 10e3, convits = 1e3,
                 q = 0,
                 seed = 2828, 
                 includeSim = TRUE,
                 # details = TRUE
                 )
```

Get the top clusters

```{r}
clusters <- clu@clusters 
names(clusters) <- names(clu@exemplars)
clusters <- lapply(clusters, function(x) names(x))
min_cluster_length <- 5
selected_clusters <- clusters[sapply(clusters, length) >= min_cluster_length]
head(selected_clusters)
clusters_df <- selected_clusters %>% 
  seq_along() %>% 
  lapply(function(i) {
    exemplar <- names(selected_clusters)[i]
    doc <- selected_clusters[[i]]
    data_frame(exemplar, doc, cluster_id = i)
  }) %>% 
  bind_rows() %>% 
  mutate(exemplar_year = extract_date(exemplar),
         doc_date = extract_date(doc)) %>% 
  group_by(cluster_id) %>% 
  mutate(earliest_date = min(doc_date),
         earliest = doc[which.min(doc_date)]) %>% 
  select(cluster_id, exemplar, exemplar_year, earliest, earliest_date,
         doc, doc_date) %>% 
  arrange(doc_date) %>% 
  mutate(n = n()) %>% 
  ungroup() %>% 
  arrange(desc(n))
clusters_df
```

That data frame has the following properties. It is sorted so that the clusters with the most documents appear first. Within each cluster, documents appear chronologically. Each cluster contains three columns for documents (with another three columns corresponding to years). One column is the "examplar" document identified by the affinity propagation clustering. The next is the earliest document in the cluster. If there are multiple documents from the earliest year, then only one is listed. The third is a list of all the documents in the cluster. The column `n` is the number of documents in the cluster. Only clusters with `r min_cluster_length` documents or more are included.

Write that to disk:

```{r}
write_csv(clusters_df, "out/clusters.csv")
```

Some summary statistics about the borrowings.

The codes which most frequently provide exemplars, weighted by the size of the clusters for which they are exemplars.

```{r}
exemplars_summary <- clusters_df$exemplar %>% 
  extract_code_names() %>% 
  table() %>% 
  as.data.frame() %>% as_data_frame() %>% 
  rename(., code = `.`) %>% 
  arrange(desc(Freq))
write_csv(exemplars_summary, "out/clusters-exemplars-summary.csv")
exemplars_summary %>% head(20)
```

The codes which most frequently provide the earliest documents in the clusters, weighted by the size of the clusters for which they are the earliest.

```{r}
earliest_summary <- clusters_df$earliest %>% 
  extract_code_names() %>% 
  table() %>% 
  as.data.frame() %>% as_data_frame() %>% 
  rename(., code = `.`) %>% 
  arrange(desc(Freq)) 
write_csv(earliest_summary, "out/clusters-earliest-summary.csv")
earliest_summary %>% head(20)
```

Now let's write out the clusters to disk.

```{r, message=FALSE}
get_printable_code <- function(doc_id) {
  require("stringr")
  content <- str_wrap(content(sections[[doc_id]]))
  str_c(doc_id, content, "-----------------------------------------------\n\n", 
        sep = "\n\n")
}

get_cluster_header <- function(exemplar, earliest, n, cluster_id) {
  require("stringr")
  str_c("Exemplar: ", exemplar, "\n",
        "Earliest: ", earliest, "\n",
        "Documents in cluster: ", n, "\n",
        "Cluster ID: ", cluster_id, "\n",
        "\n",
        "-----------------------------------------------\n\n")
}

write_cluster <- function(df) {
  require("stringr")
  exemplar <- unique(df$exemplar)
  earliest <- unique(df$earliest)
  n <- unique(df$n)
  cluster_id <- unique(df$cluster_id)
  header <- get_cluster_header(exemplar, earliest, n, cluster_id)
  docs <- df$doc %>% sapply(get_printable_code) 
  text <- str_c(header, docs, collapse = "\n") %>% 
    str_split("\n") %>% 
    unlist()
  dir.create("clusters", showWarnings = FALSE)
  filename <- str_c("clusters/", exemplar, ".txt")
  message("Writing ", filename)
  writeLines(text, filename)
  df
}

clusters_df %>% 
  group_by(cluster_id) %>% 
  do(write_cluster(.))
```

### 2015-11-23 decompose-graph.R
Graph analysis for Tyrus

@@ -1,0 +1,35 @@
+library("textreuse")
+library("dplyr")
+library("igraph")
+library("Matrix")
+load(file = "cache/lsh-sections.rda")
+load(file = "cache/corpus-sections-minash-n120-seed623.rda")
+
+g <- section_scores %>%
+  # filter(score > 0.05) %>%
+  rename(weight = score) %>%
+  graph_from_data_frame()
+d <- decompose(g, min.vertices = 2)
+
+l <- sapply(d, function(x) length(V(x)))
+
+which.max(l)
+
+m <- d[[1]] %>% as_adjacency_matrix(attr = "weight")
+writeMM(m, file = "out/adjacency-matrix-biggest-subgraph.MM")
+
+library("readr")
+cluster2 <- read_csv("~/Dropbox/DocumentCluster/cluster2.csv")
+
+docids <- cluster2$`1050`
+
+cluster2docs <- sections[docids]
+docs <- lapply(cluster2docs$doc, content)
+
+length(docs)
+docs[[4]]
+
+m2[docids,docids] %>% as.matrix() %>% heatmap()
+library(igraph)
+g <- m[docids, docids] %>% as.matrix() %>% graph_from_adjacency_matrix(mode = "upper", weighted = TRUE)
+plot(g)

### 2015-11-23 017-best-section-matches.Rmd
Simplify notebook generation, improve figures
Updates to analysis

@@
 library("readr")
+library("tidyr")
 library("ggplot2")
@@
 ```{r}
-scores <- read_csv("out/scores-all-sections-pairs.csv")
-scores <- scores %>% 
+load("cache/lsh-sections.rda")
+scores <- section_scores %>% 
   rename(section_a = a, section_b = b) %>% 
@@
          year_a = extract_date(code_a),
-         year_b = extract_date(code_b))
+         year_b = extract_date(code_b)) %>% 
+  rename(similarity = score) %>% 
+  mutate(dissimilarity = 1 - similarity)
 scores
@@
 ```{r}
-best_section_matches <- function(code_name, scores, threshold = 0.1, top = 1) {
-  require("dplyr")
-  require("stringr")
-  matches <- scores %>% 
-    filter(code_a == code_name | code_b == code_name) %>% 
-    mutate(match_code = ifelse(code_a == code_name, code_b, code_a),
-           code_of_interest = ifelse(code_a == code_name, code_a, code_b),
-           match_section = ifelse(code_a == code_name, section_b, section_a),
-           section_of_interest = ifelse(code_a == code_name, section_a, section_b),
-           match_year = ifelse(code_a == code_name, year_b, year_a)) %>% 
-    filter(match_code != code_of_interest,
-           match_year <= extract_date(code_name),
-           similarity >= threshold) %>% 
-    select(code_of_interest, section_of_interest, match_code, match_section,
-           similarity, dissimilarity) %>% 
-    group_by(section_of_interest) %>%
-    arrange(desc(similarity)) %>% 
-    top_n(top, similarity)
-
-  all_sections <- Sys.glob(str_c("legal-codes-split/", code_name, "-0*")) %>% 
-    str_replace("legal-codes-split/", "") %>% 
-    str_replace("\\.txt", "")
-  all <- data_frame(all_sections)
-
-  all %>% 
-    left_join(matches, by = c("all_sections" = "section_of_interest")) %>% 
-    select(-code_of_interest)
-} 
-```
-
-Also a function to calculate summary statistics.
-
-```{r}
-summarize_borrowings <- function(section_list) {
-  section_list %>% 
-    group_by(match_code) %>% 
-    summarize(mean_similarity = mean(similarity),
-              n = n()) %>% 
-    mutate(percentage_sections = n / nrow(section_list)) %>% 
-    arrange(desc(n))
-}
+source("R/summarize-borrowings.R")
+source("R/best-section-matches.R")
 ```
@@
 ```
+
+Heatmaps of borrowings:
+
+```{r}
+col_vector <- function(n, cols) {
+  r <- trunc(n / cols)
+  remainder <- n %% cols
+  if (remainder > 0)
+    c(rep(1:cols, r), 1:remainder)
+  else
+    c(rep(1:cols, r))
+} 
+row_vector <- function(n, cols) {
+  out <- NULL
+  for (i in seq_len((n / cols) + 1)) {
+     out <- c(out, rep(i, cols))
+  }
+  out[1:n]
+}
+n_columns <- 40
+```
+
+Plot CA
+
+```{r}
+other <- c("MN1851", "IA1851", "KY1851", "MO1849")
+best_section_matches("CA1851", scores, threshold = 0.3) %>% 
+  mutate(match_code = ifelse(match_code %in% other,
+                             "Other", match_code)) %>% 
+  mutate(., 
+         column = col_vector(nrow(.), n_columns),
+         row = row_vector(nrow(.), n_columns),
+         match_code = as.factor(match_code)) %>% 
+  ggplot(aes(x = column, y = -row, fill = match_code, alpha)) +
+  geom_tile(color = "lightgray") + 
+  theme_minimal(base_size = 16) +
+  coord_equal() +
+  labs(x = NULL, y = NULL, title = "Borrowed sections in CA1851",
+       fill = "Section borrowed from") + 
+  theme(legend.position = "bottom", 
+        axis.ticks = element_blank(),
+        axis.line = element_blank(), axis.text = element_blank(),
+        panel.background = element_blank(), panel.grid = element_blank()) +
+  scale_fill_brewer(type = "qual", na.value = "gray", palette = 6)
+```
+
+Plot UT1859
+
+```{r}
+other <- c("NY1848", "WI1849", "CA1850", "NY1849", "IA1851", "NY1851", "WI1856",
+           "WI1858", "NY1853", "CA1851", "CA1858", "IA1859", "IN1852", "MA1858",
+           "MN1851", "TN1858", "KY1851", "MA1836", "MO1856", "NE1857", "OH1853",
+           "TX1855", "KS1859", "NE1859")
+best_section_matches("UT1859", scores, threshold = 0.3) %>% 
+  mutate(match_code = ifelse(match_code %in% other,
+                             "Other", match_code)) %>% 
+  mutate(., 
+         column = col_vector(nrow(.), n_columns),
+         row = row_vector(nrow(.), n_columns),
+         match_code = as.factor(match_code)) %>% 
+  ggplot(aes(x = column, y = -row, fill = match_code)) +
+  geom_tile(color = "lightgray") + 
+  theme_minimal(base_size = 16) +
+  coord_equal() +
+  labs(x = NULL, y = NULL, title = "Borrowed sections in UT1859",
+       fill = "Section borrowed from") + 
+  theme(legend.position = "bottom", 
+        axis.ticks = element_blank(),
+        axis.line = element_blank(), axis.text = element_blank(),
+        panel.background = element_blank(), panel.grid = element_blank()) +
+  scale_fill_brewer(type = "qual", na.value = "gray", palette = 6)
+```
+
+Plot WA1855
+
+```{r}
+white_list <- c("CA1850", "NY1850", "WI1849", "CA1851", "OR1854", "IN1852")
+other_maker <- function(x, white_list) {
+  ifelse(is.na(x), NA, ifelse(x %in% white_list, x, "Other"))
+}
+best_section_matches("WA1855", scores, threshold = 0.3) %>% 
+  mutate(match_code = other_maker(match_code, white_list)) %>% 
+  mutate(., 
+         column = col_vector(nrow(.), n_columns),
+         row = row_vector(nrow(.), n_columns),
+         match_code = as.factor(match_code)) %>% 
+  ggplot(aes(x = column, y = -row, fill = match_code)) +
+  geom_tile(color = "lightgray") + 
+  theme_minimal(base_size = 16) +
+  coord_equal() +
+  labs(x = NULL, y = NULL, title = "Borrowed sections in WA1855",
+       fill = "Section borrowed from") + 
+  theme(legend.position = "bottom", 
+        axis.ticks = element_blank(),
+        axis.line = element_blank(), axis.text = element_blank(),
+        panel.background = element_blank(), panel.grid = element_blank()) +
+  scale_fill_brewer(type = "qual", na.value = "gray", palette = 6)
+```
+
+OR 1854
+
+```{r}
+white_list <- c("CA1850", "NY1853", "NY1851", "WI1849", "MN1851", "NY1850", "CA1851")
+other_maker <- function(x, white_list) {
+  ifelse(is.na(x), NA, ifelse(x %in% white_list, x, "Other"))
+}
+best_section_matches("OR1854", scores, threshold = 0.15) %>% 
+  mutate(match_code = other_maker(match_code, white_list)) %>% 
+  mutate(., 
+         column = col_vector(nrow(.), n_columns),
+         row = row_vector(nrow(.), n_columns),
+         match_code = as.factor(match_code)) %>% 
+  ggplot(aes(x = column, y = -row, fill = match_code)) +
+  geom_tile(color = "lightgray") + 
+  theme_minimal(base_size = 16) +
+  coord_equal() +
+  labs(x = NULL, y = NULL, title = "Borrowed sections in OR1854",
+       fill = "Section borrowed from") + 
+  theme(legend.position = "bottom", 
+        axis.ticks = element_blank(),
+        axis.line = element_blank(), axis.text = element_blank(),
+        panel.background = element_blank(), panel.grid = element_blank()) +
+  scale_fill_brewer(type = "qual", na.value = "gray", palette = 6)
+```
+
+NC1868
+
+```{r}
+white_list <- c("DT1668", "NY1851", "NY1849", "NY1850", "WI1858", "WI1856")
+other_maker <- function(x, white_list) {
+  ifelse(is.na(x), NA, ifelse(x %in% white_list, x, "Other"))
+}
+best_section_matches("NC1868", scores, threshold = 0.3) %>% 
+  mutate(match_code = other_maker(match_code, white_list)) %>% 
+  mutate(., 
+         column = col_vector(nrow(.), n_columns),
+         row = row_vector(nrow(.), n_columns),
+         match_code = as.factor(match_code)) %>% 
+  ggplot(aes(x = column, y = -row, fill = match_code)) +
+  geom_tile(color = "lightgray") + 
+  theme_minimal(base_size = 16) +
+  coord_equal() +
+  labs(x = NULL, y = NULL, title = "Borrowed sections in NC1868",
+       fill = "Section borrowed from") + 
+  theme(legend.position = "bottom", 
+        axis.ticks = element_blank(),
+        axis.line = element_blank(), axis.text = element_blank(),
+        panel.background = element_blank(), panel.grid = element_blank()) +
+  scale_fill_brewer(type = "qual", na.value = "gray", palette = 6)
+```
+
+IA1859
+
+```{r}
+white_list <- c("IA1851", "NE1857", "KY1854")
+other_maker <- function(x, white_list) {
+  ifelse(is.na(x), NA, ifelse(x %in% white_list, x, "Other"))
+}
+best_section_matches("IA1859", scores, threshold = 0.3) %>% 
+  mutate(match_code = other_maker(match_code, white_list)) %>% 
+  mutate(., 
+         column = col_vector(nrow(.), n_columns),
+         row = row_vector(nrow(.), n_columns),
+         match_code = as.factor(match_code)) %>% 
+  ggplot(aes(x = column, y = -row, fill = match_code)) +
+  geom_tile(color = "lightgray") + 
+  theme_minimal(base_size = 16) +
+  coord_equal() +
+  labs(x = NULL, y = NULL, title = "Borrowed sections in IA1859",
+       fill = "Section borrowed from") + 
+  theme(legend.position = "bottom", 
+        axis.ticks = element_blank(),
+        axis.line = element_blank(), axis.text = element_blank(),
+        panel.background = element_blank(), panel.grid = element_blank()) +
+  scale_fill_brewer(type = "qual", na.value = "gray", palette = 6)
+```
+
+NM1897
+
+```{r}
+white_list <- c("MO", "NM", "IA", "NY", "MN", "WI")
+other_maker <- function(x, white_list) {
+  ifelse(is.na(x), NA, ifelse(x %in% white_list, x, "Other"))
+}
+best_section_matches("NM1897", scores, threshold = 0.15) %>% 
+  mutate(match_state = str_sub(match_code, start = 1, end = 2)) %>% 
+  mutate(match_state = other_maker(match_state, white_list)) %>% 
+  mutate(., 
+         column = col_vector(nrow(.), n_columns),
+         row = row_vector(nrow(.), n_columns),
+         match_code = as.factor(match_code)) %>% 
+  ggplot(aes(x = column, y = -row, fill = match_state)) +
+  geom_tile(color = "lightgray") + 
+  theme_minimal(base_size = 16) +
+  coord_equal() +
+  labs(x = NULL, y = NULL, title = "Borrowed sections in NM1897",
+       fill = "Section borrowed from") + 
+  theme(legend.position = "bottom", 
+        axis.ticks = element_blank(),
+        axis.line = element_blank(), axis.text = element_blank(),
+        panel.background = element_blank(), panel.grid = element_blank()) +
+  scale_fill_brewer(type = "qual", na.value = "gray", palette = 6)
+```
+
+Summarize by state
+
+```{r}
+summarize_by_state <- function(section_list) {
+  section_list %>% 
+    mutate(match_state = str_sub(match_code, start = 1, end = 2)) %>% 
+    group_by(match_state) %>% 
+    summarize(original_code = unique(original_code),
+              mean_similarity = mean(similarity),
+              n = n()) %>% 
+    mutate(percentage_sections = n / nrow(section_list)) %>% 
+    arrange(desc(n)) %>% 
+    select(original_code, match_state, mean_similarity, n, percentage_sections)
+}
+```

### 2015-11-23 022-visualizations-for-article.Rmd
Updates to analysis

@@
 ```{r}
-CA1851 <- best_section_matches("CA1851", borrowings, threshold = 0.2)
+CA1851 <- best_section_matches("CA1851", borrowings, threshold = 0.15)
 CA1851
@@
 section_pct <- codes %>% 
-  mclapply(best_section_matches, scores = borrowings, threshold = 0.2)  %>% 
+  mclapply(best_section_matches, scores = borrowings, threshold = 0.15)  %>% 
   mclapply(summarize_borrowings) %>% 
@@
 # Note that original code is a misnomer here
-edges <- section_pct %>% 
+edges <-
+  section_pct %>% 
   mutate(original_date = extract_date(original_code),
@@
          !is.na(match_code),
-         original_code >= match_code) %>% 
-  select(original_code, match_code, weight = percentage_sections)
+         original_date >= match_date) %>% 
+  select(original_code, match_code, weight = percentage_sections) %>% 
+  group_by(original_code) %>% 
+  top_n(2, weight)
 edges
@@
 g <- graph_from_data_frame(edges, directed = TRUE) 
-set.seed(4821)
-l <- layout.fruchterman.reingold(g, weights = E(g)$weight)
+nodes <- distances(g, to = "NY1850", algorithm = "unweighted") %>% as.data.frame() %>% 
+  add_rownames() %>% 
+  rename(name = rowname, distance = NY1850) %>% 
+  mutate(color = ifelse(distance == 0, "red",
+                        ifelse(distance == 1, "green",
+                               ifelse(distance == 2, "yellow", "lightblue"))))
+
+nodes[nodes$name == "NY1848", "color"] <- "red"
+nodes[nodes$name == "NY1849", "color"] <- "red"
+nodes[nodes$name == "NY1850", "color"] <- "red"
+nodes[nodes$name == "NY1851", "color"] <- "red"
+g <- graph_from_data_frame(edges, directed = TRUE, vertices = nodes) 
+V(g)$year <- V(g)$name %>% extract_date()
+set.seed(4221)
+
+# g <- g %>% decompose() %>% `[[`(1)
+
+g <- add_layout_(g, with_graphopt(niter = 4000, spring.length = 25), normalize())
+
+plot_before_year <- function(x, year) {
+  x_before <- induced.subgraph(x, which(V(x)$year <= year))
+  n <- V(x)$name
+  n_before <- V(x_before)$name
+  filter <- n %in% n_before
+  x_before$layout <- x_before$layout[filter, ]
   par(mar = c(0,0,1,0))
-plot(g, edge.width = E(g)$weight * 8, layout = l,
-     edge.arrow.size = 0.65, vertex.size = 5)
-title("Codes of Civil Procedure by percentage of sections")
+  plot(x_before, edge.width = E(x_before)$weight * 8,
+       edge.arrow.size = 0.0, vertex.size = 5)
+  title(paste0("Codes of Civil Procedure before ", year))
+}
+
+for (i in seq(1850, 1900, 5)) {
+  png(filename = paste0("out/field-code-network-ALL", i, ".png"), width = 1200,
+      height = 900)
+  plot_before_year(g, i)
+  dev.off()
+}
 ```

### 2015-11-23 scripts/split-code.R
Change which codes get fuzzy matching for splitting

@@ -21,8 +21,8 @@ uncleaned_files <- c("BI1859", "CA1868short", "CO1858", "CT1854", "CT1879",
                      "GA1851", "GB1873", "GB1875", "HI1859", "IA1839", "IL1866",
                      "IN1843", "LA1825", "LA1825french", "LC1867", "LC1867french",
                      "MA1836", "MA1851", "MA1858", "ME1840", "MI1853", "MO1835",
-                     "MS1848", "ND1877short", "NH1842", "NJ1847", "NM1865",
-                     "OH1853short", "OH1879", "UT1884", "VA1841", "VA1860",
+                     "MS1848", "ND1877short", "NH1842", "NY1829", "NJ1847", "NM1865",
+                     "OH1853short", "VA1841", "VA1860",
                      "WI1849", "WV1868")
 
 if (any(str_detect(out_file_stem, uncleaned_files))) {

### 2015-11-23 024-comparison-NY.Rmd
Compare NY codes using NY1829

---
title: "Comparison of New York codes"
date: "November 23, 2015"
output: html_document
---

```{r}
library("textreuse")
library("dplyr")
library("readr")
library("stringr")
source("R/best-section-matches.R")
source("R/summarize-borrowings.R")
source("R/extract_code_names.R")
source("R/extract-date.R")
options("mc.cores" = 6L)
h <- 120
b <- 60
minhash <- minhash_generator(n = h, seed = 623)
ny_paths <- Sys.glob("legal-codes-split/NY*")
```

Create the corpus:

```{r}
ny_sections <- TextReuseCorpus(paths = ny_paths,
                               tokenizer = tokenize_ngrams, n = 5,
                               keep_tokens = FALSE,
                               minhash_func = minhash)
```

Do the LSH for New York:

```{r}
ny_buckets <- lsh(ny_sections, bands = b)
ny_scores <- ny_buckets %>% 
  lsh_candidates() %>% 
  lsh_compare(ny_sections, jaccard_similarity) %>% 
  rename(section_a = a, section_b = b, similarity = score) %>% 
  mutate(dissimilarity = 1 - similarity,
         code_a = extract_code_names(section_a),
         code_b = extract_code_names(section_b),
         year_a = extract_date(code_a),
         year_b = extract_date(code_b))
```

Write out the best section matches to disk.

```{r}
ny_codes <- c(ny_scores$code_a, ny_scores$code_b) %>% unique %>% sort

lapply(ny_codes, function(x) {
  best_section_matches(x, ny_scores, threshold = 0.15) %>% 
    write_csv(str_c("out/NY-comparisons-", x, ".csv"))
})
```

Summaries of matches.

```{r}
ny_codes %>% 
  lapply(function(x) {
    best_section_matches(x, ny_scores, threshold = 0.15) %>% 
      summarize_borrowings()
  })
```

### 2015-11-23 024-comparison-NY.Rmd
Rerun analyses

@@
 ```{r}
-ny_codes %>% 
+intra_code_network <- ny_codes %>% 
   lapply(function(x) {
@@
       summarize_borrowings()
-  })
+  }) %>% 
+  bind_rows()
 ```
+
+```{r}
+library("igraph")
+g <- intra_code_network %>% 
+  select(original_code, match_code, weight = percentage_sections) %>% 
+  filter(!is.na(match_code)) %>%
+  filter(weight >= 0.02) %>% 
+  graph_from_data_frame() %>% 
+  add_layout_(with_graphopt()) 
+plot(g, edge.width = E(g)$weight * 10)
+```

### 2015-12-01 scripts/corpus-lsh.R
Separate corpus generation/lsh into script

@@ -1,0 +1,26 @@
+library("textreuse")
+library("dplyr")
+library("stringr")
+source("R/extract_code_names.R")
+source("R/extract-date.R")
+options("mc.cores" = 6L)
+
+h <- 120
+b <- 60
+minhash <- minhash_generator(n = h, seed = 623)
+
+sections <- TextReuseCorpus(dir = "legal-codes-split",
+                            tokenizer = tokenize_ngrams, n = 5,
+                            keep_tokens = FALSE,
+                            minhash_func = minhash)
+
+buckets <- lsh(sections, bands = b)
+scores <- buckets %>%
+  lsh_candidates() %>%
+  lsh_compare(sections, jaccard_similarity) %>%
+  rename(section_a = a, section_b = b, similarity = score) %>%
+  mutate(code_a = extract_code_names(section_a),
+         code_b = extract_code_names(section_b),
+         year_a = extract_date(code_a),
+         year_b = extract_date(code_b))
+save(sections, buckets, scores, file = "cache/lsh-corpus.rda")

### 2015-12-01 early-analysis/007-load-corpus.Rmd
Move old analysis into subdirectory

---
title: "Load and tokenize all codes"
author: "Lincoln Mullen"
date: "September 21, 2015"
---

```{r}
library("textreuse")
```

We are going to tokenize the codes and save cached versions. For our initial analysis, we will use skip n-grams with a moderate value for `k` so that we have many features.

```{r}
cache_skip <- "cache/corpus-skip-ngrams-n7k3.rds"
if (!file.exists(cache_skip)) {
  description <- "General purpose tokenization of codes for comparing pairwise."
  corpus_skip <- TextReuseCorpus(dir = "legal-codes/",
                                 meta = list("description" = description,
                                             "title" = "Field codes"),
                                 tokenizer = tokenize_skip_ngrams, n = 7, k = 3,
                                 hash_func = hash_string,
                                 keep_tokens = FALSE)
  dir.create("cache", showWarnings = FALSE)
  corpus_skip
  saveRDS(corpus_skip, file = cache_skip)
}
```

```{r}
cache_shingle <- "cache/corpus-shingle-ngrams-n7.rds"
if (!file.exists(cache_shingle)) {
  description <- "General purpose tokenization of codes for comparing pairwise."
  corpus_shingle <- TextReuseCorpus(dir = "legal-codes/",
                                    meta = list("description" = description,
                                                "title" = "Field codes"),
                                    tokenizer = tokenize_ngrams, n = 7,
                                    hash_func = hash_string,
                                    keep_tokens = FALSE)
  dir.create("cache", showWarnings = FALSE)
  corpus_shingle
  saveRDS(corpus_shingle, file = cache_shingle)
}
```

Session info:

```{r}
sessionInfo()
```

### 2015-12-01 early-analysis/021-check-sectioning.Rmd
Move old analysis into subdirectory

---
title: "Checking Sectioning of Codes"
author: "Lincoln Mullen"
date: "October 28, 2015"
output: html_document
---

Create a corpus of the sections.

```{r}
library("textreuse")
library("dplyr")
library("stringr")
library("readr")
options("mc.cores" = 6L)
sections <- TextReuseCorpus(dir = "legal-codes-split/", tokenizer = NULL)
```

Get the word counts of each section and turn that into a data frame.

```{r}
wc_raw <- wordcount(sections)
wc <- data_frame(section = names(wc_raw), words = wc_raw)
wc
```

Now detect the code name and calculate some summary statistics.

```{r}
wc_summary <- wc %>% 
  mutate(code = str_replace(section, "-\\d+", "")) %>% 
  group_by(code) %>% 
  summarize(n_sections = n(),
            total_words = sum(words),
            min_words = min(words),
            max_words = max(words),
            mean_words = mean(words),
            median_words = median(words)) %>% 
  arrange(code)

wc_summary %>% arrange(desc(n_sections))
wc_summary %>% arrange(n_sections)
```

And write that file to disk.

```{r}
write_csv(wc_summary, "out/section-wordcounts-summary.csv")
```

### 2015-12-01 scripts/corpus-lsh.R
Fix name of cache file

@@ -23,4 +23,4 @@ scores <- buckets %>%
          code_b = extract_code_names(section_b),
          year_a = extract_date(code_a),
          year_b = extract_date(code_b))
-save(sections, buckets, scores, file = "cache/lsh-corpus.rda")
+save(sections, buckets, scores, file = "cache/corpus-lsh.rda")

### 2015-12-01 102-clustering.Rmd
Rename current analysis files

--- 2015-11-06 023-sparse-matrix.Rmd
@@
 library("Matrix")
+library("apcluster")
 library("dplyr")
@@
 
-Create a look up data frame of index positions
+Create a look up data frame of matrix index positions.
 
@@
 
-And write it to a file.
-
-```{r}
-writeMM(m, file = "out/sparse-section-similarity-matrix.MM")
-write_csv(scores, "out/section-scores.csv")
-```
-
 Now use affinity propagation clustering to create clusters.
@@
 ```{r}
-library("apcluster")
+cluster_cache <- "cache/clusters.rds"
+if (!file.exists(cluster_cache)) {
+  timing <- system.time(
     clu <- apcluster(s = m,
-                 # maxits = 10e3, convits = 1e3,
+                     maxits = 100e3, convits = 10e3,
                      q = 0,
-                 seed = 2828, 
+                     lam = 0.975,
+                     seed = 42325, 
                      includeSim = TRUE,
-                 # details = TRUE
                      )
+  )
+  require("RPushbullet")
+  pbPost(title = "Clustering finished",
+         body = paste0("Finished in ", timing[["elapsed"]], "."))
+  saveRDS(clu, cluster_cache)
+} else {
+  clu <- readRDS(cluster_cache)
+}
 ```
 
-Get the top clusters
+Get the clusters in a slightly easier format to work with.
 
@@
 names(clusters) <- names(clu@exemplars)
-clusters <- lapply(clusters, function(x) names(x))
-min_cluster_length <- 5
-selected_clusters <- clusters[sapply(clusters, length) >= min_cluster_length]
-head(selected_clusters)
-clusters_df <- selected_clusters %>% 
+clusters <- lapply(clusters, names)
+```
+
+Now the problem is that some clusters have been inadequately joined together.
+We will compute simiarities on the examplars.
+If any of them have a high Jaccard similarity, we will join those clusters together.
+
+```{r}
+exemplars_corpus <- sections[names(clusters)]
+exemplars_scores <- exemplars_corpus %>% 
+  lsh(bands = 60) %>% 
+  lsh_candidates() %>% 
+  lsh_compare(exemplars_corpus, jaccard_similarity) %>% 
+  arrange(desc(score))
+```
+
+Here is a box plot of those scores:
+
+```{r}
+boxplot(exemplars_scores$score)
+```
+
+What is a good minimum match?
+Looking at the sections, `0.2` is clearly a match, while `0.1` is clearly not.
+An important observation is that the exemplars for the blood quantum sections have a Jaccard similarity of `0.15`.
+We will use that as the threshold.
+
+```{r}
+join_threshold <- 0.15
+exemplars_scores <- exemplars_scores %>% 
+  filter(score >= 0.15)
+```
+
+Now a function to iterate over that data frame. If the Jaccard score is sufficiently high, combine the two clusters.
+
+```{r}
+join_clusters <- function(row) {
+  exs <- c(row$a, row$b)
+  minval <- which.min(extract_date(exs))
+  exemplar <- exs[minval]
+  duplicate <- exs[ifelse(minval == 1, 2, 1)]
+  clusters[[exemplar]] <<- c(clusters[[exemplar]], clusters[[duplicate]])
+  clusters[[duplicate]] <<- NULL
+  dplyr::as_data_frame(row)
+}
+
+exemplars_scores %>% 
+  rowwise() %>% 
+  do(join_clusters(.))
+```
+
+Now convert the clusters into a data frame.
+
+```{r}
+clusters_df <- clusters %>% 
   seq_along() %>% 
   lapply(function(i) {
-    exemplar <- names(selected_clusters)[i]
-    doc <- selected_clusters[[i]]
+    exemplar <- names(clusters)[i]
+    doc <- clusters[[i]]
     data_frame(exemplar, doc, cluster_id = i)
@@
 The column `n` is the number of documents in the cluster.
-Only clusters with `r min_cluster_length` documents or more are included.
+All clusters regardless of length have been included.
 
@@
 
-Now let's write out the clusters to disk.
+Now let's write out the clusters with a certain minimum number of documents to disk.
 
 ```{r, message=FALSE}
+dir.create("clusters", showWarnings = FALSE)
+
 get_printable_code <- function(doc_id) {
@@
   docs <- df$doc %>% sapply(get_printable_code) 
-  text <- str_c(header, docs, collapse = "\n") %>% 
+  text <- str_c(docs, collapse = "\n") %>% 
+    str_c(header, .) %>% 
     str_split("\n") %>% 
     unlist()
-  dir.create("clusters", showWarnings = FALSE)
-  filename <- str_c("clusters/", exemplar, ".txt")
+  filename <- str_c("clusters/", earliest, ".txt")
   message("Writing ", filename)
@@
 clusters_df %>% 
+  filter(n >= 5) %>% 
   group_by(cluster_id) %>% 

### 2015-12-01 101-visualizations-for-article.Rmd
Refactor to use cached LSH objects

--- 2015-11-23 022-visualizations-for-article.Rmd
@@
 ```{r}
-cache_corpus <- "cache/corpus-sections-minash-n120-seed623.rda"
-load(file = cache_corpus)
-cache_lsh <- "cache/lsh-sections.rda"
-load(file = cache_lsh)
-borrowings <- section_scores %>% 
-  rename(section_a = a, section_b = b, similarity = score) %>% 
-  mutate(dissimilarity = 1 - similarity,
-         code_a = extract_code_names(section_a),
-         code_b = extract_code_names(section_b),
-         year_a = extract_date(code_a),
-         year_b = extract_date(code_b))
-codes <- c(borrowings$code_a, borrowings$code_b) %>% unique()
+load("cache/corpus-lsh.rda")
+codes <- c(scores$code_a, scores$code_b) %>% unique()
 ```
@@
 ```{r}
-CA1851 <- best_section_matches("CA1851", borrowings, threshold = 0.15)
+CA1851 <- best_section_matches("CA1851", scores, threshold = 0.15)
 CA1851
@@
 section_pct <- codes %>% 
-  mclapply(best_section_matches, scores = borrowings, threshold = 0.15)  %>% 
+  mclapply(best_section_matches, scores = scores, threshold = 0.15)  %>% 
   mclapply(summarize_borrowings) %>% 

### 2015-12-01 R/best-section-matches.R

@@ -12,7 +12,7 @@ best_section_matches <- function(code_name, scores, threshold = 0.1, top = 1) {
            match_year <= extract_date(code_name),
            similarity >= threshold) %>%
     select(code_of_interest, section_of_interest, match_code, match_section,
-           similarity, dissimilarity) %>%
+           similarity) %>%
     group_by(section_of_interest) %>%
     arrange(desc(similarity)) %>%
     top_n(top, similarity) %>%

### 2015-12-01 101-visualizations-for-article.Rmd
Fix some bad variable names

@@
 ```{r}
-section_pct <- codes %>% 
+code_match_summary <- codes %>% 
   mclapply(best_section_matches, scores = scores, threshold = 0.15)  %>% 
@@
   bind_rows()
-section_pct
+code_match_summary
 ```
 
-Do some filtering and munge into an edge list.
+Create a network graph based on section percentages.
 
 ```{r}
-# Note that original code is a misnomer here
-edges <-
-  section_pct %>% 
-  mutate(original_date = extract_date(original_code),
+edges_pct <-
+  code_match_summary %>% 
+  mutate(borrower_date = extract_date(borrower_code),
          match_date = extract_date(match_code)) %>% 
@@
          !is.na(match_code),
-         original_date >= match_date) %>% 
-  select(original_code, match_code, weight = percentage_sections) %>% 
-  group_by(original_code) %>% 
+         borrower_date >= match_date) %>% 
+  select(borrower_code, match_code, weight = percentage_sections) %>% 
+  group_by(borrower_code) %>% 
   top_n(2, weight)
-edges
-```
+edges_pct
 
-Turn that into a graph.
-
-```{r}
-g <- graph_from_data_frame(edges, directed = TRUE) 
+g <- graph_from_data_frame(edges_pct, directed = TRUE) 
 nodes <- distances(g, to = "NY1850", algorithm = "unweighted") %>% as.data.frame() %>% 
@@
 nodes[nodes$name == "NY1851", "color"] <- "red"
-g <- graph_from_data_frame(edges, directed = TRUE, vertices = nodes) 
+g <- graph_from_data_frame(edges_pct, directed = TRUE, vertices = nodes) 
 V(g)$year <- V(g)$name %>% extract_date()
 set.seed(4221)
-
-# g <- g %>% decompose() %>% `[[`(1)
 

### 2015-12-01 R/best-section-matches.R

@@ -16,7 +16,7 @@ best_section_matches <- function(code_name, scores, threshold = 0.1, top = 1) {
     group_by(section_of_interest) %>%
     arrange(desc(similarity)) %>%
     top_n(top, similarity) %>%
-    mutate(original_code = code_name)
+    mutate(borrower_code = code_name)
 
   all_sections <- Sys.glob(str_c("legal-codes-split/", code_name, "-0*")) %>%
     str_replace("legal-codes-split/", "") %>%

### 2015-12-01 R/summarize-borrowings.R

@@ -1,10 +1,10 @@
 summarize_borrowings <- function(section_list) {
   section_list %>%
     group_by(match_code) %>%
-    summarize(original_code = unique(original_code),
+    summarize(borrower_code = unique(borrower_code),
               mean_similarity = mean(similarity),
               n = n()) %>%
     mutate(percentage_sections = n / nrow(section_list)) %>%
     arrange(desc(n)) %>%
-    select(original_code, match_code, mean_similarity, n, percentage_sections)
+    select(borrower_code, match_code, mean_similarity, n, percentage_sections)
 }

### 2015-12-01 101-visualizations-for-article.Rmd
Network based on sections borrowed

@@
 library("parallel")
+library("scales")
 library("textreuse")
@@
 ```
+
+Create a graph based on numbers (not percentages) of sections shared.
+Notice that we are keeping only code to code matches that share a certain number of sections (`minimum_n`), we are keeping only a certain number of matches for each code (`top_matches`), and we are omitting codes that aren't part of the main network.
+
+```{r}
+minimum_n <- 3
+top_matches <- 2
+codes_not_to_plot <- c("LA1825", "LA1844")
+
+edges_n <- code_match_summary %>% 
+  mutate(borrower_date = extract_date(borrower_code),
+         match_date = extract_date(match_code)) %>% 
+  filter(!is.na(match_code),
+         borrower_date >= match_date,
+         n >= minimum_n) %>%  
+  select(borrower_code, match_code, weight = n) %>% 
+  group_by(borrower_code) %>% 
+  top_n(top_matches, weight) %>% 
+  ungroup() %>% 
+  mutate(weight = rescale(weight)) %>% 
+  filter(!borrower_code %in% codes_not_to_plot,
+         !match_code %in% codes_not_to_plot)
+edges_n
+
+g_n <- graph_from_data_frame(edges_n, directed = TRUE) 
+node_distances <- distances(g_n, to = c("NY1848", "NY1849", "NY1850", "NY1851"),
+                     algorithm = "unweighted") %>% 
+                     apply(1, min, na.rm = TRUE)
+nodes_n <- data_frame(name = names(node_distances), distance = node_distances) %>% 
+  mutate(color = ifelse(distance == 0, "red",
+                        ifelse(distance == 1, "green",
+                               ifelse(distance == 2, "yellow", "lightblue"))))
+
+g_n <- graph_from_data_frame(edges_n, directed = TRUE, vertices = nodes_n) 
+V(g_n)$year <- V(g_n)$name %>% extract_date()
+
+edge_size_clamp <- function(g, multiplier = 20, max_val = 6, min_val = 0.5) {
+  w <- E(g)$weight * multiplier
+  w[w > max_val] <- max_val
+  w[w < min_val] <- min_val
+  w
+}
+
+set.seed(4221)
+g_n <- g_n %>% add_layout_(with_graphopt(niter = 4000, spring.length = 45),
+                           normalize())
+par(mar = c(0,0,1,0))
+plot(g_n, edge.width = edge_size_clamp(g_n), edge.arrow.size = 0, vertex.size = 5)
+```

### 2015-12-02 101-visualizations-for-article.Rmd
Pruned version of section by section network graph

@@
 ```{r}
-minimum_n <- 3
-top_matches <- 2
-codes_not_to_plot <- c("LA1825", "LA1844")
+minimum_n <- 50
+top_matches <- 4
+codes_not_to_plot <- c(
+  "CO868", 
+#   "CT1879", 
+  "FL1847", 
+  "FL1892", 
+  "GA1851",
+  "GA1860", 
+#   "HI1859", 
+#   "HI1897", 
+  "IL1866", 
+#   "LA1825", 
+#   "LA1844", 
+#   "MS1848", 
+#   "MS1857", 
+  "NY1876", 
+  "NY1879",
+  "VA1860", 
+#   "VA1893", 
+  "WV1868" 
+  )
+# codes_not_to_plot <- NULL
 
@@
 set.seed(4221)
-g_n <- g_n %>% add_layout_(with_graphopt(niter = 4000, spring.length = 45),
+g_n <- g_n %>% add_layout_(with_graphopt(niter = 4000, spring.length = 25),
                            normalize())
@@
 plot(g_n, edge.width = edge_size_clamp(g_n), edge.arrow.size = 0, vertex.size = 5)
+title("Borrowings between codes, number of sections borrowed")
 ```

### 2015-12-02 101-visualizations-for-article.Rmd
Midway point in big graph of section borrowings

@@
 date: "November 3, 2015"
-output: html_document
 ---
@@
 ```{r}
-minimum_n <- 50
-top_matches <- 4
+minimum_n <- 20
+top_matches <- 3
 codes_not_to_plot <- c(
-  "CO868", 
+  # "CO868", 
 #   "CT1879", 
-  "FL1847", 
-  "FL1892", 
+  # "FL1847", 
+  # "FL1892", 
   "GA1851",
   "GA1860", 
-#   "HI1859", 
-#   "HI1897", 
-  "IL1866", 
-#   "LA1825", 
-#   "LA1844", 
+  "HI1859", 
+  "HI1897", 
+  # "IL1866", 
+  "LA1825", 
+  "LA1844", 
 #   "MS1848", 
 #   "MS1857", 
-  "NY1876", 
-  "NY1879",
-  "VA1860", 
-#   "VA1893", 
+  # "NY1876", 
+  # "NY1879",
+  # "VA1860", 
+  "VA1893", 
   "WV1868" 
@@
 
-edge_size_clamp <- function(g, multiplier = 20, max_val = 6, min_val = 0.5) {
+edge_size_clamp <- function(g, multiplier = 20, max_val = 6, min_val = 1) {
   w <- E(g)$weight * multiplier

### 2015-12-02 101-visualizations-for-article.Rmd
State to state network visualization

@@
 source("R/extract_code_names.R")
+source("R/extract-state.R")
 options("mc.cores" = 6L)
@@
 ```
+
+Now do a state to state network:
+
+```{r}
+min_state_borrowings <- 100
+top_matches <- 3
+edges_states <- code_match_summary %>% 
+  mutate(borrower_date = extract_date(borrower_code),
+         match_date = extract_date(match_code),
+         borrower_state = extract_state(borrower_code),
+         match_state = extract_state(match_code)) %>% 
+  filter(!is.na(match_code),
+         borrower_date >= match_date,
+         borrower_state != match_state) %>% 
+  group_by(borrower_state, match_state) %>% 
+  summarize(n = sum(n)) %>% 
+  filter(n >= min_state_borrowings) %>% 
+  select(borrower_state, match_state, weight = n) %>% 
+  group_by(borrower_state) %>% 
+  top_n(top_matches, weight) %>% 
+  ungroup() %>% 
+  mutate(weight = rescale(weight))
+
+edges_states
+
+g_states <- graph_from_data_frame(edges_states, directed = TRUE)
+
+state_distances <- distances(g_states, to = "NY", algorithm = "unweighted") 
+nodes_states <- data_frame(name = rownames(state_distances),
+                           distance = state_distances[, 1]) %>% 
+  mutate(color = ifelse(distance == 0, "red",
+                        ifelse(distance == 1, "green",
+                               ifelse(distance == 2, "yellow", "lightblue"))))
+
+g_states <- graph_from_data_frame(edges_states, directed = TRUE,
+                                  vertices = nodes_states) %>% 
+  decompose(min.vertices = 3) %>% 
+  `[[`(1)
+
+set.seed(4221)
+g_states <- g_states %>% add_layout_(with_graphopt(niter = 4000,
+                                                   spring.length = 25),
+                                     normalize())
+par(mar = c(0,0,1,0))
+plot(g_states, 
+     edge.width = edge_size_clamp(g_n), edge.arrow.size = 0.5,
+     edge.arrow.mode = 1,
+     vertex.size = 5, vertex.label.dist = 0.85, vertex.label.degree = pi)
+title("Borrowings between states, number of sections borrowed")
+```

### 2015-12-02 R/extract-state.R

@@ -1,0 +1,2 @@
+# CA1851 goes in, CA comes out
+extract_state <- function(x) str_sub(x, 1, 2)

### 2015-12-02 031-count-sections.Rmd
Count sections in each code

---
title: "Number of actual sections"
author: "Lincoln Mullen"
date: "December 2, 2015"
---

Count the number of sections in each code.

```{r}
library("magrittr")
library("readr")
library("dplyr")
library("stringr")
library("knitr")
code_files <- Sys.glob("legal-codes/*")
codes <- lapply(code_files, read_lines)
names(codes) <- code_files %>% basename() %>% str_replace_all("\\.txt", "")
code_info <- read_csv("codes/code-generations.csv")
```

A section is a line with `§` or `SEC.` at the very beginning.

```{r}
pattern_clean <- regex("(^§|^SEC\\.)", ignore_case = FALSE)
counts <- codes %>% 
  lapply(str_detect, pattern_clean) %>% 
  sapply(sum, na.rm = TRUE)
section_counts <- data_frame(code = names(counts), sections = counts) %>% 
  left_join(code_info)
```

The number of sections in each generation.

```{r}
section_counts %>% 
  group_by(generation) %>% 
  summarise(sections = sum(sections)) %>% 
  kable()
```

The number of sections in each code.

```{r}
section_counts %>% 
  kable()
```

### 2015-12-02 R/extract-date.R
Consolidate helper functions

@@ -1,4 +1,0 @@
-extract_date <- function(x) {
-  require(stringr)
-  as.integer(str_extract(x, "\\d{4}"))
-}

### 2015-12-02 R/extract-state.R

@@ -1,2 +1,0 @@
-# CA1851 goes in, CA comes out
-extract_state <- function(x) str_sub(x, 1, 2)

### 2015-12-02 R/extract_code_names.R

@@ -1,4 +1,0 @@
-extract_code_names <- function(section_names) {
-  splits <- str_split(section_names, "-")
-  vapply(splits, `[`, character(1), 1)
-}

### 2015-12-02 R/helper.R

@@ -1,63 +1,18 @@
-# Function to create ngrams
-ngrammify <- function(data, n) {
-  NGramTokenizer(data, Weka_control(min = n, max = n))
-}
-
-#' Remove unreasonable n-grams containing characters other than letters and spaces
-#' @param ngrams A list of n-grams
-#' @return Returns a list of filtered n-grams
-filter_unreasonable_ngrams <- function(ngrams) {
-  ngrams[!stringi::stri_detect_regex(ngrams, "[^a-z ]")]
-}
-
-#' Compare two codes using their list of n-grams.
-#' @param orig_code A vector of n-grams representing a code.
-#' @param dest_code A vectory of n-grams representing a code.
-#' @return A list containing data that might help to identify whether codes
-#'   match up.
-compare_codes_by_shared_ngrams <- function(orig_code, dest_code) {
-  matches <- intersect(orig_code, dest_code)
-  ratio_matches_to_destination <- length(matches) / length(unique(dest_code))
-  return(ratio_matches_to_destination)
-}
-
-# From http://stackoverflow.com/questions/1719447/outer-equivalent-for-non-vector-lists-in-r
-outer_for_lists <- function(a,b, fun) {
-  mat <- outer(a, b, function(x,y) vapply(seq_along(x), function(i) fun(x[[i]], y[[i]]), numeric(1)))
-  rownames(mat) <- names(b)
-  colnames(mat) <- names(a)
-  return(mat)
-}
-
-# Get the year from a code name
-get_year <- function(s) {
-  year <- stringi::stri_extract_first_regex(s, "\\d{4}")
-  as.integer(year)
-}
-# Remove anachronistic comparisons of earlier codes to later codes
-rm_anachronism <- function(m) {
-  rows <- rownames(m)
-  cols <- colnames(m)
-  for(i in seq_along(m)) {
-    ind <- arrayInd(i, dim(m))
-    row <-  rows[ind[1,1]]
-    col <-  cols[ind[1,2]]
-    test <- get_year(row) > get_year(col)
-    if(test) m[i] <- NA
-  }
-  return(m)
-}
-
 plot_graph <- function(g) {
   plot(g, edge.width = E(g)$weight * 5, layout = layout.fruchterman.reingold,
        edge.arrow.size= 0.25, vertex.size = 5)
 }
 
-# Given a comparison matrix, return the codes that most INFLUENCE
-get_influences <- function(m, state, n = NULL) {
[…]

### 2015-12-02 R/load-data.R

@@ -1,16 +1,0 @@
-codes_dir <- "text"
-files <- dir(codes_dir, "*.txt")
-
-raw <- file.path(codes_dir, files) %>%
-  lapply(., scan, "character", sep = "\n")
-names(raw) <-  stri_match_first_regex(files, "(.+).txt")[,2]
-
-codes <- raw %>%
-  lapply(paste, collapse = " ") %>%
-  lapply(tolower) %>%
-  lapply(WordTokenizer) %>%
-  lapply(paste, collapse = " ") %>%
-  lapply(ngrammify, 5) %>%
-  lapply(filter_unreasonable_ngrams)
-
-rm(raw, codes_dir, files)

### 2015-12-02 R/plot_network.R

@@ -1,12 +1,0 @@
-plot_network <- function(g, graph_title = "Network graph") {
-  require("igraph")
-  l <- layout.fruchterman.reingold(g, weights = E(g)$weight) * 10
-  # http://stackoverflow.com/questions/5968612/how-do-i-lengthen-edges-in-an-igraph-network-plot-layout-fruchterman-reingold
-#   l <- layout.fruchterman.reingold(g, niter = 500,
-#                                    area = vcount(g) ^ 2.3,
-#                                    repulserad = vcount(g) ^ 2.8)
-  par(mar = c(0,0,1,0))
-  plot(g, edge.width = E(g)$weight * 12, layout = l,
-       edge.arrow.size = 0.15, vertex.size = 5)
-  title(graph_title)
-}

### 2015-12-02 R/section-matches.R
Consolidate matching functions

@@ -27,3 +27,14 @@ best_section_matches <- function(code_name, scores, threshold = 0.1, top = 1) {
     left_join(matches, by = c("all_sections" = "section_of_interest")) %>%
     select(-code_of_interest)
 }
+
+summarize_borrowings <- function(section_list) {
+  section_list %>%
+    group_by(match_code) %>%
+    summarize(borrower_code = unique(borrower_code),
+              mean_similarity = mean(similarity),
+              n = n()) %>%
+    mutate(percentage_sections = n / nrow(section_list)) %>%
+    arrange(desc(n)) %>%
+    select(borrower_code, match_code, mean_similarity, n, percentage_sections)
+}

### 2015-12-02 R/summarize-borrowings.R

@@ -1,10 +1,0 @@
-summarize_borrowings <- function(section_list) {
-  section_list %>%
-    group_by(match_code) %>%
-    summarize(borrower_code = unique(borrower_code),
-              mean_similarity = mean(similarity),
-              n = n()) %>%
-    mutate(percentage_sections = n / nrow(section_list)) %>%
-    arrange(desc(n)) %>%
-    select(borrower_code, match_code, mean_similarity, n, percentage_sections)
-}

### 2015-12-03 scripts/corpus-lsh.R
Cache munging of data to section to section matches

@@ -1,8 +1,7 @@
 library("textreuse")
 library("dplyr")
 library("stringr")
-source("R/extract_code_names.R")
-source("R/extract-date.R")
+source("R/helper.R")
 options("mc.cores" = 6L)
 
 h <- 120
@@ -15,12 +14,27 @@ sections <- TextReuseCorpus(dir = "legal-codes-split",
                             minhash_func = minhash)
 
 buckets <- lsh(sections, bands = b)
+
 scores <- buckets %>%
   lsh_candidates() %>%
-  lsh_compare(sections, jaccard_similarity) %>%
-  rename(section_a = a, section_b = b, similarity = score) %>%
-  mutate(code_a = extract_code_names(section_a),
-         code_b = extract_code_names(section_b),
-         year_a = extract_date(code_a),
-         year_b = extract_date(code_b))
-save(sections, buckets, scores, file = "cache/corpus-lsh.rda")
+  lsh_compare(sections, jaccard_similarity)
+
+scores_swapped <- scores %>%
+  rename(b2 = a, a2 = b) %>%
+  rename(a = a2, b = b2)
+
+scores_for_join <- bind_rows(scores, scores_swapped) %>%
+  rename(borrower_section = a,
+         match_section = b)
+
+matches <- data_frame(borrower_section = names(sections)) %>%
+  left_join(scores_for_join, by = "borrower_section") %>%
+  mutate(borrower_code = extract_code_names(borrower_section),
+         borrower_year = extract_date(borrower_section),
+         borrower_state = extract_state(borrower_section),
+         match_code = extract_code_names(match_section),
+         match_year = extract_date(match_section),
+         match_state = extract_state(match_section)) %>%
+  arrange(borrower_section, match_section)
+
+save(sections, buckets, scores, matches, file = "cache/corpus-lsh.rda")

### 2015-12-03 scripts/corpus-lsh.R
Save matches as a CSV for good measure

@@ -1,6 +1,7 @@
 library("textreuse")
 library("dplyr")
 library("stringr")
+library("readr")
 source("R/helper.R")
 options("mc.cores" = 6L)
 
@@ -38,3 +39,4 @@ matches <- data_frame(borrower_section = names(sections)) %>%
   arrange(borrower_section, match_section)
 
 save(sections, buckets, scores, matches, file = "cache/corpus-lsh.rda")
+write_csv(matches, "cache/matches.csv")

### 2015-12-03 R/helper.R
Pretty number helper

@@ -16,3 +16,5 @@ extract_code_names <- function(section_names) {
   splits <- str_split(section_names, "-")
   vapply(splits, `[`, character(1), 1)
 }
+
+pnum <- function(x) prettyNum(x, big.mark = ",")

### 2015-12-03 R/section-matches.R
Rewrite best matches according to explicit and flawless logic

@@ -1,31 +1,70 @@
-best_section_matches <- function(code_name, scores, threshold = 0.1, top = 1) {
+best_matches <- function(matches, threshold = 0.1, tolerance = 0.1) {
+
   require("dplyr")
-  require("stringr")
-  matches <- scores %>%
-    filter(code_a == code_name | code_b == code_name) %>%
-    mutate(match_code = ifelse(code_a == code_name, code_b, code_a),
-           code_of_interest = ifelse(code_a == code_name, code_a, code_b),
-           match_section = ifelse(code_a == code_name, section_b, section_a),
-           section_of_interest = ifelse(code_a == code_name, section_a, section_b),
-           match_year = ifelse(code_a == code_name, year_b, year_a)) %>%
-    filter(match_code != code_of_interest,
-           match_year <= extract_date(code_name),
-           similarity >= threshold) %>%
-    select(code_of_interest, section_of_interest, match_code, match_section,
-           similarity) %>%
-    group_by(section_of_interest) %>%
-    arrange(desc(similarity)) %>%
-    top_n(top, similarity) %>%
-    mutate(borrower_code = code_name)
+  # message("Start: ", pnum(nrow(matches)))
 
-  all_sections <- Sys.glob(str_c("legal-codes-split/", code_name, "-0*")) %>%
-    str_replace("legal-codes-split/", "") %>%
-    str_replace("\\.txt", "")
-  all <- data_frame(all_sections)
+  # Remove matches from the same code
+  matches <- matches %>%
+    filter(borrower_code != match_code)
+  # message("Same code: ", pnum(nrow(matches)))
 
-  all %>%
-    left_join(matches, by = c("all_sections" = "section_of_interest")) %>%
-    select(-code_of_interest)
+  # Remove anachronistic matches
+  matches <- matches %>%
+    filter(borrower_year >= match_year)
+  # message("Anachronistic: ", pnum(nrow(matches)))
+
+  # Remove matches below threshold
+  matches <- matches %>%
+    filter(score >= threshold)
+  # message("Threshold: ", pnum(nrow(matches)))
+
+  # Keep matches within the tolerance
+  matches <- matches %>%
+    group_by(borrower_section) %>%
+    filter(score >= max(score) - tolerance)
+  # message("Tolerance: ", pnum(nrow(matches)))
+
+  # Keep matches within the same state, if there is one from the same state
+  matches <- matches %>%
+    group_by(borrower_section) %>%
[…]

### 2015-12-03 R/section-matches.R
Rewrite summarize borrowings

@@ -67,13 +67,12 @@ best_matches <- function(matches, threshold = 0.1, tolerance = 0.1) {
 
 }
 
-summarize_borrowings <- function(section_list) {
-  section_list %>%
-    group_by(match_code) %>%
-    summarize(borrower_code = unique(borrower_code),
-              mean_similarity = mean(similarity),
-              n = n()) %>%
-    mutate(percentage_sections = n / nrow(section_list)) %>%
-    arrange(desc(n)) %>%
-    select(borrower_code, match_code, mean_similarity, n, percentage_sections)
+summarize_borrowings <- function(matches) {
+  matches %>%
+    group_by(borrower_code, match_code) %>%
+    summarize(mean_score = mean(score, na.rm = TRUE),
+              sections_borrowed = n()) %>%
+    group_by(borrower_code) %>%
+    mutate(percent_borrowed = sections_borrowed / sum(sections_borrowed)) %>%
+    arrange(desc(sections_borrowed))
 }

### 2015-12-03 R/section-matches.R
Put best matches in the cache

@@ -1,4 +1,4 @@
-best_matches <- function(matches, threshold = 0.1, tolerance = 0.1) {
+get_best_matches <- function(matches, threshold = 0.1, tolerance = 0.1) {
 
   require("dplyr")
   # message("Start: ", pnum(nrow(matches)))

### 2015-12-03 scripts/corpus-lsh.R

@@ -1,8 +1,10 @@
-library("textreuse")
+library("readr")
+library("plyr")
 library("dplyr")
 library("stringr")
-library("readr")
+library("textreuse")
 source("R/helper.R")
+source("R/section-matches.R")
 options("mc.cores" = 6L)
 
 h <- 120
@@ -28,7 +30,7 @@ scores_for_join <- bind_rows(scores, scores_swapped) %>%
   rename(borrower_section = a,
          match_section = b)
 
-matches <- data_frame(borrower_section = names(sections)) %>%
+all_matches <- data_frame(borrower_section = names(sections)) %>%
   left_join(scores_for_join, by = "borrower_section") %>%
   mutate(borrower_code = extract_code_names(borrower_section),
          borrower_year = extract_date(borrower_section),
@@ -38,5 +40,25 @@ matches <- data_frame(borrower_section = names(sections)) %>%
          match_state = extract_state(match_section)) %>%
   arrange(borrower_section, match_section)
 
-save(sections, buckets, scores, matches, file = "cache/corpus-lsh.rda")
-write_csv(matches, "cache/matches.csv")
+best_matches <- data_frame(borrower_section = names(sections)) %>%
+  left_join(get_best_matches(all_matches), by = "borrower_section") %>%
+  mutate(borrower_code = extract_code_names(borrower_section),
+         borrower_year = extract_date(borrower_section),
+         borrower_state = extract_state(borrower_section),
+         match_code = extract_code_names(match_section),
+         match_year = extract_date(match_section),
+         match_state = extract_state(match_section)) %>%
+  arrange(borrower_section, match_section)
+
+split_matches <- dlply(best_matches, "borrower_code", identity)
+
+save(sections, buckets, scores, all_matches, best_matches,
+     file = "cache/corpus-lsh.rda")
+
+dir.create("out/matches", showWarnings = FALSE)
+write_csv(all_matches, "out/matches/all_matches.csv")
+write_csv(best_matches, "out/matches/best_matches.csv")
+lapply(names(split_matches), function(x) {
+  write_csv(split_matches[[x]], str_c("out/matches/", x, "-best-matches.csv"))
+}) %>% invisible
+

### 2015-12-03 R/section-matches.R
Add summary of matches to cache

@@ -74,5 +74,7 @@ summarize_borrowings <- function(matches) {
               sections_borrowed = n()) %>%
     group_by(borrower_code) %>%
     mutate(percent_borrowed = sections_borrowed / sum(sections_borrowed)) %>%
+    mutate(mean_score = ifelse(is.nan(mean_score), NA_real_, mean_score),
+           percent_borrowed = round(percent_borrowed, 4)) %>%
     arrange(desc(sections_borrowed))
 }

### 2015-12-03 scripts/corpus-lsh.R

@@ -52,12 +52,15 @@ best_matches <- data_frame(borrower_section = names(sections)) %>%
 
 split_matches <- dlply(best_matches, "borrower_code", identity)
 
-save(sections, buckets, scores, all_matches, best_matches,
+summary_matches <- summarize_borrowings(best_matches)
+
+save(sections, buckets, scores, all_matches, best_matches, summary_matches,
      file = "cache/corpus-lsh.rda")
 
 dir.create("out/matches", showWarnings = FALSE)
 write_csv(all_matches, "out/matches/all_matches.csv")
 write_csv(best_matches, "out/matches/best_matches.csv")
+write_csv(summary_matches, "out/matches/summary_matches.csv")
 lapply(names(split_matches), function(x) {
   write_csv(split_matches[[x]], str_c("out/matches/", x, "-best-matches.csv"))
 }) %>% invisible

### 2015-12-03 index.Rmd
Index

---
title: "Field Code Analysis"
author: "Lincoln Mullen and Kellen Funk"
output: html_document
---

```{r echo=FALSE, results='asis'}
rmd <- Sys.glob("*.Rmd")
html <- sub(".Rmd", ".html", rmd)
lines <- lapply(rmd, readLines)
yaml <- lapply(lines, rmarkdown:::parse_yaml_front_matter)
cat("<ul>")
for (i in seq_along(rmd)) {
  cat(paste0("<li><a href='", html[i], "'>", yaml[[i]]$title, "</a></li>"))
}
cat("</ul>")
```

### 2015-12-03 index.Rmd
Add filename to index

@@
 for (i in seq_along(rmd)) {
-  cat(paste0("<li><a href='", html[i], "'>", yaml[[i]]$title, "</a></li>"))
+  cat(paste0("<li><a href='", html[i], "'>", yaml[[i]]$title, "</a><br/>",
+             "<code>", html[i], "</code>", "</li>"))
 }

### 2015-12-03 index.Rmd
Show Rmd file name, filter index

--- 2015-12-03 index.Rmd
@@
 rmd <- Sys.glob("*.Rmd")
+rmd <- rmd[rmd != "index.Rmd"]
 html <- sub(".Rmd", ".html", rmd)
@@
 for (i in seq_along(rmd)) {
-  cat(paste0("<li><a href='", html[i], "'>", yaml[[i]]$title, "</a></li>"))
+  cat(paste0("<li><a href='", html[i], "'>", yaml[[i]]$title, "</a><br/>",
+             "<code>", rmd[i], "</code>", "</li>"))
 }

### 2015-12-03 index.Rmd
Infrastructure for web notebook

@@
 ---
-title: "Field Code Analysis"
+title: "Analysis of Text Reuse in the Field Code"
 author: "Lincoln Mullen and Kellen Funk"
-output: html_document
 ---
+
+This is an analysis notebook for detecting text reuse in codes of civil procedure---the "Field codes"---in the nineteenth-century United States.
+It is a collaboration between [Kellen Funk](http://kellenfunk.org/) and [Lincoln Mullen](http://lincolnmullen.com).
+
+See these links for more details:
+
+- [Kellen's posts about the project](http://kellenfunk.org/field-code/)
+- [An Introduction to the textreuse Package, with Suggested Applications](http://lincolnmullen.com/blog/an-introduction-to-the-textreuse-package/)
+- [Detecting Text Reuse in Nineteenth-Century Legal Documents](http://lincolnmullen.com/blog/detecting-text-reuse-in-legal-documents/)
+
+This notebook contains our work in progress. This is the most recent analysis in progress. There is more in the [repository](https://github.com/lmullen/civil-procedure-codes).
 

### 2015-12-03 101-visualizations-for-article.Rmd
Rerun visualizations

@@
 library("stringr")
-library("parallel")
 library("scales")
 library("textreuse")
-source("R/best-section-matches.R")
-source("R/summarize-borrowings.R")
-source("R/extract-date.R")
-source("R/extract_code_names.R")
-source("R/extract-state.R")
-options("mc.cores" = 6L)
+source("R/helper.R")
+source("R/section-matches.R")
 ```
@@
 load("cache/corpus-lsh.rda")
-codes <- c(scores$code_a, scores$code_b) %>% unique()
-```
-
-Calculate section matches and summarize them for a single code.
-
-```{r}
-CA1851 <- best_section_matches("CA1851", scores, threshold = 0.15)
-CA1851
-summarize_borrowings(CA1851)
-```
-
-Apply that to all the codes.
-
-```{r}
-code_match_summary <- codes %>% 
-  mclapply(best_section_matches, scores = scores, threshold = 0.15)  %>% 
-  mclapply(summarize_borrowings) %>% 
-  bind_rows()
-code_match_summary
 ```
@@
 ```{r}
-edges_pct <-
-  code_match_summary %>% 
-  mutate(borrower_date = extract_date(borrower_code),
-         match_date = extract_date(match_code)) %>% 
-  filter(percentage_sections >= 0.05,
-         !is.na(match_code),
-         borrower_date >= match_date) %>% 
-  select(borrower_code, match_code, weight = percentage_sections) %>% 
+edges_pct <- summary_matches %>% 
+  filter(percent_borrowed >= 0.05,
+         !is.na(match_code)) %>% 
+  select(borrower_code, match_code, weight = percent_borrowed) %>% 
   group_by(borrower_code) %>% 
@@
 for (i in seq(1850, 1900, 5)) {
-  png(filename = paste0("out/field-code-network-ALL", i, ".png"), width = 1200,
-      height = 900)
   plot_before_year(g, i)
-  dev.off()
 }
@@
 minimum_n <- 20
-top_matches <- 3
+top_matches <- 2
 codes_not_to_plot <- c(
@@
   "LA1825", 
-  "LA1844", 
+  "LA1844" 
 #   "MS1848", 
@@
   # "VA1860", 
-  "VA1893", 
-  "WV1868" 
+  # "VA1893", 
+  # "WV1868" 
   )
@@
 
-edges_n <- code_match_summary %>% 
-  mutate(borrower_date = extract_date(borrower_code),
-         match_date = extract_date(match_code)) %>% 
+edges_n <- summary_matches %>% 
   filter(!is.na(match_code),
-         borrower_date >= match_date,
-         n >= minimum_n) %>%  
-  select(borrower_code, match_code, weight = n) %>% 
+         sections_borrowed >= minimum_n) %>%  
+  select(borrower_code, match_code, weight = sections_borrowed) %>% 
   group_by(borrower_code) %>% 
@@
 min_state_borrowings <- 100
-top_matches <- 3
-edges_states <- code_match_summary %>% 
+top_matches <- 2
+edges_states <- summary_matches %>% 
   mutate(borrower_date = extract_date(borrower_code),
@@
   group_by(borrower_state, match_state) %>% 
-  summarize(n = sum(n)) %>% 
+  summarize(n = sum(sections_borrowed)) %>% 
   filter(n >= min_state_borrowings) %>% 

### 2016-01-05 R/spectrogram.R
Isolate function for creating a spectrogram

@@ -1,0 +1,39 @@
+col_vector <- function(n, cols) {
+  r <- trunc(n / cols)
+  remainder <- n %% cols
+  if (remainder > 0)
+    c(rep(1:cols, r), 1:remainder)
+  else
+    c(rep(1:cols, r))
+}
+row_vector <- function(n, cols) {
+  out <- NULL
+  for (i in seq_len((n / cols) + 1)) {
+    out <- c(out, rep(i, cols))
+  }
+  out[1:n]
+}
+n_columns <- 40
+
+white_list <- c("CA1850", "NY1850", "WI1849", "CA1851", "OR1854", "IN1852")
+other_maker <- function(x, white_list) {
+  ifelse(is.na(x), NA, ifelse(x %in% white_list, x, "Other"))
+}
+best_section_matches("WA1855", scores, threshold = 0.3) %>%
+  mutate(match_code = other_maker(match_code, white_list)) %>%
+  mutate(.,
+         column = col_vector(nrow(.), n_columns),
+         row = row_vector(nrow(.), n_columns),
+         match_code = as.factor(match_code)) %>%
+  ggplot(aes(x = column, y = -row, fill = match_code)) +
+  geom_tile(color = "lightgray") +
+  theme_minimal(base_size = 16) +
+  coord_equal() +
+  labs(x = NULL, y = NULL, title = "Borrowed sections in WA1855",
+       fill = "Section borrowed from") +
+  theme(legend.position = "bottom",
+        axis.ticks = element_blank(),
+        axis.line = element_blank(), axis.text = element_blank(),
+        panel.background = element_blank(), panel.grid = element_blank()) +
+  scale_fill_brewer(type = "qual", na.value = "gray", palette = 6)
+

### 2016-01-05 R/spectrogram.R
Refactor, with function to white list code names

@@ -1,3 +1,21 @@
+
+# Threshold is set to 0 because in `get_best_matches()` we already applied a
+# threshold of `0.1`: in other words, if it didn't meet that minimum, we don't
+# consider it a match at all. Here we will have the option to increase the limit
+# but won't exercise it by default.
+spectrogram <- function(code, matches_df, num_cols = 40, threshold = 0.0,
+                        white_list = NULL) {
+  require(dplyr)
+
+  # Get just the genuine matches for the code of interest
+  matches_df <- matches_df %>%
+    filter(borrower_code == code) %>%
+    filter(score >= threshold)
+
+  # Create the white list of codes that we want to explicitly name in the viz.
+
+}
+
 col_vector <- function(n, cols) {
   r <- trunc(n / cols)
   remainder <- n %% cols
@@ -6,6 +24,7 @@ col_vector <- function(n, cols) {
   else
     c(rep(1:cols, r))
 }
+
 row_vector <- function(n, cols) {
   out <- NULL
   for (i in seq_len((n / cols) + 1)) {
@@ -13,12 +32,22 @@ row_vector <- function(n, cols) {
   }
   out[1:n]
 }
-n_columns <- 40
 
-white_list <- c("CA1850", "NY1850", "WI1849", "CA1851", "OR1854", "IN1852")
 other_maker <- function(x, white_list) {
   ifelse(is.na(x), NA, ifelse(x %in% white_list, x, "Other"))
 }
+
+white_list_maker <- function(df, n = 5) {
+  df %>%
+    count(match_code) %>%
+    top_n(n, n) %>%
+    arrange(desc(n)) %>%
+    filter(!is.na(match_code)) %>%
+    `$`("match_code")
+}
+
+white_list <- c("CA1850", "NY1850", "WI1849", "CA1851", "OR1854", "IN1852")
+
 best_section_matches("WA1855", scores, threshold = 0.3) %>%
   mutate(match_code = other_maker(match_code, white_list)) %>%
   mutate(.,

### 2016-01-05 R/spectrogram.R
Make codes the other

@@ -3,6 +3,10 @@
 # threshold of `0.1`: in other words, if it didn't meet that minimum, we don't
 # consider it a match at all. Here we will have the option to increase the limit
 # but won't exercise it by default.
+#
+# The `white_list` argument takes either a count numeric, in which case it
+# white lists at most that number of codes to be explicitly named in the viz,
+# or a character vector of codes to white list.
 spectrogram <- function(code, matches_df, num_cols = 40, threshold = 0.0,
                         white_list = NULL) {
   require(dplyr)
@@ -13,6 +17,15 @@ spectrogram <- function(code, matches_df, num_cols = 40, threshold = 0.0,
     filter(score >= threshold)
 
   # Create the white list of codes that we want to explicitly name in the viz.
+  if (is.null(white_list)) {
+    white_list <- white_list_maker(matches_df)
+  } else if (is.numeric(white_list)) {
+    white_list <- white_list_maker(matches_df, n = white_list)
+  }
+
+  # Make all other codes "other"
+  match_df <- match_df %>%
+    mutate(match_code = other_maker(code_code, white_list))
 
 }
 
@@ -46,7 +59,6 @@ white_list_maker <- function(df, n = 5) {
     `$`("match_code")
 }
 
-white_list <- c("CA1850", "NY1850", "WI1849", "CA1851", "OR1854", "IN1852")
 
 best_section_matches("WA1855", scores, threshold = 0.3) %>%
   mutate(match_code = other_maker(match_code, white_list)) %>%

### 2016-01-05 R/spectrogram.R
Working version of spectrogram function

@@ -1,31 +1,49 @@
-
-# Threshold is set to 0 because in `get_best_matches()` we already applied a
-# threshold of `0.1`: in other words, if it didn't meet that minimum, we don't
-# consider it a match at all. Here we will have the option to increase the limit
-# but won't exercise it by default.
-#
 # The `white_list` argument takes either a count numeric, in which case it
 # white lists at most that number of codes to be explicitly named in the viz,
 # or a character vector of codes to white list.
-spectrogram <- function(code, matches_df, num_cols = 40, threshold = 0.0,
-                        white_list = NULL) {
+spectrogram <- function(code, matches_df, num_cols = 40, white_list = NULL) {
   require(dplyr)
+  require(stringr)
+  require(ggplot2)
 
   # Get just the genuine matches for the code of interest
   matches_df <- matches_df %>%
-    filter(borrower_code == code) %>%
-    filter(score >= threshold)
+    filter(borrower_code == code)
 
   # Create the white list of codes that we want to explicitly name in the viz.
   if (is.null(white_list)) {
     white_list <- white_list_maker(matches_df)
   } else if (is.numeric(white_list)) {
-    white_list <- white_list_maker(matches_df, n = white_list)
+    white_list <- white_list_maker(matches_df, num_codes = white_list)
   }
 
   # Make all other codes "other"
-  match_df <- match_df %>%
-    mutate(match_code = other_maker(code_code, white_list))
+  matches_df <- matches_df %>%
+    mutate(match_code = other_maker(match_code, white_list))
+
+  # Assign the positions in the heatmap
+  matches_df <- matches_df %>%
+    mutate(.,
+           column = col_vector(nrow(.), num_cols),
+           row = row_vector(nrow(.), num_cols),
+           match_code = as.factor(match_code))
+
+  # Create the title
+  title <- str_c("Borrowed sections in ", code)
+
+  # Make the plot
+  matches_df %>%
+  ggplot(aes(x = column, y = -row, fill = match_code)) +
+  geom_tile(color = "lightgray") +
+  theme_minimal(base_size = 16) +
+  coord_equal() +
+  labs(x = NULL, y = NULL, title = title,
+       fill = "Section borrowed from") +
+  theme(legend.position = "bottom",
+        axis.ticks = element_blank(),
[…]

### 2016-01-05 R/spectrogram.R
Able to specify title in spectrogram

@@ -1,7 +1,8 @@
 # The `white_list` argument takes either a count numeric, in which case it
 # white lists at most that number of codes to be explicitly named in the viz,
 # or a character vector of codes to white list.
-spectrogram <- function(code, matches_df, num_cols = 40, white_list = NULL) {
+spectrogram <- function(code, matches_df, num_cols = 40,
+                        white_list = NULL, title = NULL) {
   require(dplyr)
   require(stringr)
   require(ggplot2)
@@ -29,7 +30,8 @@ spectrogram <- function(code, matches_df, num_cols = 40, white_list = NULL) {
            match_code = as.factor(match_code))
 
   # Create the title
-  title <- str_c("Borrowed sections in ", code)
+  if (is.null(title))
+    title <- str_c("Borrowed sections in ", code)
 
   # Make the plot
   matches_df %>%

### 2016-01-05 101-visualizations-for-article.Rmd
Separate out the network graph
Working on #19.
Working on #20.
Isolate function for creating a spectrogram
Straightforward spectrograms and to NY spectrograms
Working on #17, #18, #21, #25, #26, #28, #29

@@
 ---
+
+## Data loading
 
@@
 ```
+
+## Spectrograms
+
+```{r}
+source("R/spectrogram.R")
+```
+
+Spectrogram of borrowings in CA1850. I expect it will show heavily reliance on NY1849 amidst original material.
+
+```{r}
+spectrogram("CA1850", best_matches, white_list = 7)
+```
+
+Spectrogram of borrowings in MD1855. I expect to see reliance on English legislation (GB1852 and GB1854), amidst original material.
+
+```{r}
+spectrogram("MD1855", best_matches, white_list = 7)
+```
+
+Spectrogram of borrowings in WA1855.
+An earlier version show two long runs of borrowings from Oregon and Indiana.
+If the latest data, still visualizes that kind of splicing, I think it's a great illustration.
+
+```{r}
+spectrogram("WA1855", best_matches, white_list = 8)
+```
+
+The point of this and the next exercise is not to show borrowings from all sources, but similarity between two sources.
+Our normal spectrogram of NV1861 will show heavy reliance on California.
+I want this to show that even though Nevada is two steps away from New York, it's text is still very similar to New York throughout.
+
+```{r}
+all_NV1861 <- data_frame(borrower_code = "NV1861",
+                         borrower_section = all_matches %>% 
+                           filter(borrower_code == "NV1861") %>% 
+                           `$`("borrower_section") %>%
+                           unique() %>%
+                           sort()
+                        )
+
+matches_to_NY <- all_matches %>% 
+  filter(borrower_code == "NV1861",
+         str_detect(match_code, "NY"),
+         score >= 0.1,
+         match_year <= 1861) %>% 
+  group_by(borrower_section) %>% 
+  arrange(desc(score)) %>% 
+  slice(1) %>% 
+  ungroup()
+
+NV1861toNY <- all_NV1861 %>% left_join(matches_to_NY) %>% 
+  arrange(borrower_section)
+
+spectrogram("NV1861", NV1861toNY, white_list = 5,
+            title = "Sections in NV1861 with high similarity to NY codes")
+```
+
+Like the previous query for NV1861, Iowa is two steps away from New York.
+This time, however, the text is much less similar to New York.
+I only want one visualization for this, but I'm not sure if IA1851 or the revision IA1859 will be better, so can we do both?
+
+IA1851
+
+```{r}
+all_IA1851 <- data_frame(borrower_code = "IA1851",
+                         borrower_section = all_matches %>% 
+                           filter(borrower_code == "IA1851") %>% 
+                           `$`("borrower_section") %>%
+                           unique() %>%
+                           sort()
+                        )
+
+matches_to_NY <- all_matches %>% 
+  filter(borrower_code == "IA1851",
+         str_detect(match_code, "NY"),
+         score >= 0.1,
+         match_year <= 1851) %>% 
+  group_by(borrower_section) %>% 
+  arrange(desc(score)) %>% 
+  slice(1) %>% 
+  ungroup()
+
+IA1851toNY <- all_IA1851 %>% left_join(matches_to_NY) %>% 
+  arrange(borrower_section)
+
+spectrogram("IA1851", IA1851toNY, white_list = 10,
+            title = "Sections in IA1851 with matches to NY codes")
+```
+
+IA1859
+
+```{r}
+all_IA1859 <- data_frame(borrower_code = "IA1859",
+                         borrower_section = all_matches %>% 
+                           filter(borrower_code == "IA1859") %>% 
+                           `$`("borrower_section") %>%
+                           unique() %>%
+                           sort()
+                        )
+
+matches_to_NY <- all_matches %>% 
+  filter(borrower_code == "IA1859",
+         str_detect(match_code, "NY"),
+         score >= 0.1,
+         match_year <= 1859) %>% 
+  group_by(borrower_section) %>% 
+  arrange(desc(score)) %>% 
+  slice(1) %>% 
+  ungroup()
+
+IA1859toNY <- all_IA1859 %>% left_join(matches_to_NY) %>% 
+  arrange(borrower_section)
+
+spectrogram("IA1859", IA1859toNY, white_list = 10,
+            title = "Sections in IA1859 with matches to NY codes")
+```
+
+Spectrogram of borrowings in NC1868. Should show heavy reliance on one or another New York Code, with scattered provisions coming from elsewhere.
+
+```{r}
+spectrogram("NC1868", best_matches, white_list = 8)
+```
+
+Spectrogram of borrowings in CO1868. Should show heavy reliance on Illinois law.
+
+```{r}
+spectrogram("CO1868", best_matches, white_list = 8)
+```
+
+## Network graphs
 

### 2016-01-05 R/spectrogram.R
Double check correct ordering, and eliminate message about top_n

@@ -24,6 +24,7 @@ spectrogram <- function(code, matches_df, num_cols = 40,
 
   # Assign the positions in the heatmap
   matches_df <- matches_df %>%
+    arrange(borrower_section) %>%
     mutate(.,
            column = col_vector(nrow(.), num_cols),
            row = row_vector(nrow(.), num_cols),
@@ -73,7 +74,7 @@ other_maker <- function(x, white_list) {
 white_list_maker <- function(df, num_codes = 5) {
   df %>%
     count(match_code) %>%
-    top_n(num_codes) %>%
+    top_n(num_codes, n) %>%
     arrange(desc(n)) %>%
     filter(!is.na(match_code)) %>%
     `$`("match_code")

### 2016-01-05 101-visualizations-for-article.Rmd
A few more spectrograms, mostly of NY

@@
 ```
+
+Same query as number 6 and 7, but like Louisiana, the point is to show that no one borrows the later New York Code, the one that departs from the Field tradition.
+
+```{r}
+spectrogram("NY1876", best_matches, white_list = 8)
+```
+
+```{r}
+spectrogram("NY1879", best_matches, white_list = 8)
+```
+
+Here I'm looking for the reverse of the previous spectrograms.
+Rather than illustrate sections BORROWED FROM elsewhere, can we illustrate sections in the original Field Code that GET BORROWED elsewhere, and instead of coloring by where they end up, color based on how many times a particular section appears throughout the corpus?
+
+I expect the beginning of the code will be grey--no one has New York's particular court system, so no one copies the jurisdictional texts, then high heat at the heart of the Code with the Field reforms, slackening off around particular proceedings, some of which will be New York specific, then heating up again towards the end with the code of evidence.
 

### 2016-01-30 103-racial-exclusions.Rmd
Sections with racial exclusions

---
title: "Sections with Racial Exclusions"
author: "Lincoln Mullen"
output: html_document
---

I used `ag` to search the split sections for `negro OR indian OR china OR chinese OR mongol OR blood`. We are going to load the corpus and that list of files, the create a chronological list of those sections.

```{r}
library(readr)
library(textreuse)
library(stringr)
library(dplyr)
source("R/helper.R")
load("cache/corpus-lsh.rda")
```

Load the matching sections.

```{r}
exclusions <- read_lines("racial-exclusions/list-of-racial-sections.txt") %>% 
  str_sub(end = -5)
```

Get those sections in the right order.

```{r}
ordered_sections <- data_frame(section = exclusions,
                               year = extract_date(exclusions),
                               code = extract_code_names(exclusions)) %>% 
  arrange(year, code)
```

Print the sections to a file.

```{r}
get_printable_code <- function(doc_id) {
  require("stringr")
  content <- str_wrap(content(sections[[doc_id]]))
  str_c(doc_id, content, "-----------------------------------------------\n\n", 
        sep = "\n\n")
}

write_sections <- function(df) {
  require("stringr")
  docs <- df$section %>% sapply(get_printable_code) 
  text <- str_c(docs, collapse = "\n") %>% 
    str_split("\n") %>% 
    unlist()
  filename <- "racial-exclusions/exclusion-sections.txt"
  writeLines(text, filename)
  df
}

write_sections(ordered_sections)
```

### 2016-02-06 talks/aha2016/aha2016.Rmd
Move AHA talk to subdirectory

---
title: "Tracking the Migration of the Field Code"
author: "Lincoln Mullen and Kellen Funk"
date: "http://lincolnmullen.com"
output: 
  revealjs::revealjs_presentation:
    theme: white
    css: talks.css
    transition: slide
    fig_width: 9
    fig_height: 6
    fig_caption: true
    pandoc_args: [
      "--slide-level=2",
      "--metadata=history:true",
      "--metadata=margin:0.05",
      "--metadata=center:false",
      "--variable=width:1200",
      "--variable=height:700"
    ]
    mathjax: null
    self_contained: true
    center: false
---

## The New York "Field Code"

<div class="left">
![David Dudley Field.](field.jpg)
</div>
<div class="right">
![Title page of the 1850 Field Code.](field-code.jpg)
</div>

## Code commissioners

![The 1868 North Carolina code commission: Victor Barringer, William Rodman, Albion Tourgee.](nc-commission.jpg)

## {data-background="field-code-states-map.jpeg"}

## "Paste-pot" procedure codes

![The 1861 Morris bill, which adapted California's code for Nevada.](morris-bill.jpg)

## {data-background="WA1855.png"}

## {data-background="NV1861.png"}

## {data-background="code-to-code.png"}

## {data-background="state-to-state.png"}

### 2016-02-12 talks/dh-working-group/dh-working-group.Rmd
Introduction to DH working group talk

---
title: "The Migration of the Field Code"
author: "Kellen Funk and Lincoln Mullen"
date: "February 17, 2016"
output: tufte::tufte_handout
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tufte)
library(textreuse)
```

# The Field Code

After the American Revolution, most states were common law jurisdictions, sometimes with courts of chancery. These courts had a complex system of pleading defined mostly be case law. By the 1840s, lawyers and the mercantile classes called for the codification of civil procedure. At stake in the ensuing debates were the rationality of the law a science, or the purity of Anglo-Saxon civilization. New York was the first state to codify its procedure, thanks to the efforts of David Dudly Field. New York's 1848 Field code became by the end of the century the model for the procedural codes in state jurisdiction.

\begin{figure}
\includegraphics{../aha2016/field-code-states-map.jpeg}
\caption{Field Code states by date of enactment. Many states subsequently revised their codes of civil procedure.}
\end{figure}

Legal historians have long known that the Field code spread to other jurisdictions. Beyond the mere fact of its adoption, however, no one has studied the content of the borrowings. Which codes borrowed from each other? Which sections were borrowed, and which were modified? What were the patterns of borrowings and of innovations?

To answer these questions we have gathered a corpus of 115 codes of civil procedure containing about 7.6 million words, and detected the borrowings algorithmically. Our approach is one of two common approaches. We have gathered a dataset of sources to answer a given set of questions; the other option is to take the sources as given and explore the data to see what questions it raises.

```{marginfigure}
Against the buzzword "big data," I call this "middle data", which we might define as data that is too small for distributed computation but too big for naive algorithms. Alternatively, it is data where the size of the sample approaches the size of the population, but where the population is strictly constrained by the research problem. Against big data, middle data offers the most promising way to combine traditional and digital history methods.
```

# How we found the borrowings

## Preparing the corpus

Having identified all of the relevant codes of civil procedure in the nineteenth-century, including separately published codes, session laws, and statutes, we used OCR software to create plain-text versions of the codes. These OCR files received only a light cleaning: we edited the section markers by hand as necessary, and wrote a script to fix the most obvious OCR errors.

We then split each section of each code into its own text file.

```{marginnote}
A sample file:
```

This.^[The data and code to re-run our analyses are available in a GitHub repository: <https://github.com/lmullen/civil-procedure-codes>.]

### 2016-02-12 talks/dh-working-group/dh-working-group.Rmd
Finished description of the methods

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE, comment = NA)
 library(tufte)
 library(textreuse)
+library(dplyr)
+library(ggplot2)
+library(ggthemes)
+library(readr)
+library(knitr)
+source("../../R/helper.R")
+source("../../R/section-matches.R")
+load("../../cache/corpus-lsh.rda")
+clusters <- read_csv("../../out/clusters.csv")
 ```
@@
 Our approach is one of two common approaches.
-We have gathered a dataset of sources to answer a given set of questions; the other option is to take the sources as given and explore the data to see what questions it raises.
-
-```{marginfigure}
-Against the buzzword "big data," I call this "middle data", which we might define as data that is too small for distributed computation but too big for naive algorithms.
+We have gathered a dataset of sources to answer a given set of questions; the other option is to take the sources as given and explore the data to see what questions it raises.^[Against the buzzword "big data," I call this "middle data", which we might define as data that is too small for distributed computation but too big for naive algorithms.
 Alternatively, it is data where the size of the sample approaches the size of the population, but where the population is strictly constrained by the research problem.
-Against big data, middle data offers the most promising way to combine traditional and digital history methods.
-```
+Against big data, middle data offers the most promising way to combine traditional and digital history methods.]
 
@@
 
-Having identified all of the relevant codes of civil procedure in the nineteenth-century, including separately published codes, session laws, and statutes, we used OCR software to create plain-text versions of the codes.
-These OCR files received only a light cleaning: we edited the section markers by hand as necessary, and wrote a script to fix the most obvious OCR errors.
+Having identified all of the relevant codes of civil procedure in the nineteenth-century, including separately published codes, session laws, and statutes, we used OCR software to create plain-text versions of the codes.^[The data and code to re-run our analyses are available in a GitHub repository: <https://github.com/lmullen/civil-procedure-codes>.] These OCR files received only a light cleaning: we edited the section markers by hand as necessary, and wrote a script to fix the most obvious OCR errors.
 
 We then split each section of each code into its own text file.
+The corpus contains nearly 98,000 sections.
+Below is a sample file containing a single section from a single code.^[Section 151 of the California's 1851 code of civil procedures from the file `CA1851-001660.txt`.]
 
-```{marginnote}
-A sample file:
+```
+151. An issue arises when a fact or conclusion of law 
+is maintained by the one party, and is controverted 
+by theothsr. Issues are of two kinds: lst. Of law: 
+and,  _ 2d. or fact. if?
 ```
 
-This.^[The data and code to re-run our analyses are available in a GitHub repository: <https://github.com/lmullen/civil-procedure-codes>.]
+## Tokenizing and measuring similarity
+
+The next stage in our process was to measure the similarity of the sections one to another.
+^[This stage of our process was embedded in the [textreuse package](https://github.com/ropensci/textreuse) for R, which was peer-reviewed by rOpenSci: <https://github.com/ropensci/textreuse>.
+See also my blog post, "[An Introduction to the textreuse Package, with Suggested Applications](http://lincolnmullen.com/blog/an-introduction-to-the-textreuse-package/)": <http://lincolnmullen.com/blog/an-introduction-to-the-textreuse-package/>.
+] We first had to tokenize the text, meaning that  After experimenting we found that five-grams worked well.^[We also hashed the tokens, meaning that we converted them to integer representations which permits considerable savings of memory.]  The use of n-grams, which is a ubiquitious technique, permits redudancy of phrasing, intentional word changes, and OCR errors.
+Below are the first five tokens from the section above.
+
+```{r}
+tokenize_ngrams("151. An issue arises when a fact or conclusion of law 
+is maintained by the one party, and is controverted 
+by theothsr. Issues are of two kinds: lst. Of law: 
+and,  _ 2d. or fact. if?", n = 5) %>% head(5)
+```
+
+Next we used the Jaccard similarity score for measuring document similarity.
+That measure, treating the tokens as a set, is the ratio of shared tokens to the ratio of total tokens in two documents.
+The result is a single number ranging from 0 (complete dissimilarity) to 1 (complete similarity).^[From MMDS.
+Formally, the definition of the Jaccard similarity score is $$J(A, B) = \frac{ | A \cap B| }{ | A \cup B|}$$] For instance, the section from the California 1851 code above was derived from section 756 of the New York 1850 code (`NY1850-008350.txt`).
+Because of changes to the wording and OCR errors, the Jaccard similarity between the two sections was `r jaccard_similarity(sections[["NY1850-008350"]], sections[["CA1851-001660"]]) %>% round(3)`.
+By carefully checking matching sections versus scores, we arrived at a rule of thumb that a Jaccard similarity score greater than 0.15 likely indicated a match, and a score greater than 0.2 almost certainly indicated a match.
+
+## Computing similarity for the entire corpus
+
+```{r}
+num_comparisons <- function(n) { ((n * (n - 1)) / 2) }
+billionize <- function(x) { round(x / 1e9, 1)}
+```
+
+The next step was to compute similarity for every section in the corpus.
+The difficulty is that to compare every section to every other section would require an enormous number of comparisons: approximately `r length(sections) %>% num_comparisons() %>% billionize()` billion for our corpus.^[Assuming that the similarity measure is bi-directional, the number of pairwise comparisons in a corpus is given by $(n^2-n) / {2}$.] Most of these comparisons would be wasted, since most sections have zero relationship to most other sections.
+
+```{r, fig.margin = TRUE, fig.cap = "This chart shows the threshold S-curves for various settings of the minhash/LSH algorithm.
+The x-axis shows the actual measured Jaccard similarity of the two documents; the y-axis shows the probability that they will be marked as a match.
+We used the settings for the leftmost curve, guaranteeing that we detected all matches above a similarity of 0.2."}
+prob_for_graph1 <- Vectorize(function(x) lsh_probability(120, 60, x))
+prob_for_graph3 <- Vectorize(function(x) lsh_probability(120, 30, x))
+prob_for_graph5 <- Vectorize(function(x) lsh_probability(120, 10, x))
+input <- data_frame(x = seq(0, 1, 0.001))
+ggplot(input, aes(x = x)) + 
+  stat_function(fun = prob_for_graph1, linetype = 1) +
+  stat_function(fun = prob_for_graph3, linetype = 2) +
+  stat_function(fun = prob_for_graph5, linetype = 5) +
+  theme_tufte() +
+  labs(x = "Jaccard similarity",
+       y = "Probability",
+       title = "Probability of detecting a match given real similarity") +
+  scale_x_continuous(breaks = seq(0, 1, .2))
+```
+
+We implemented the minhash/locality sensitive hashing (LSH) algorithm to detect candidate pairs, i.e., documents which were likely to be matches.
+This algorithm works by extracting a set number of random tokens from each document, allowing the documents to be represented uniformly and compactly.
+Then those random tokens are grouped into subsets.
+If any two documents have a matching subset, then they are considered a candidate pair.
+This algorithm has several useful properties.
+It approximates the Jaccard similarity of the two documents.
+The algorithm requires a computation for each document, not each pair of documents, so the compute time grows linearly not geometrically.
+And by controlling various parameters, one can determine a threshold similarity score above which one is likely to find a match and unlikely to find an inaccurate match.
+
+Once we had detected the candidate pairs, we measured the actual Jaccard similarity for those pairs.
+The result was a sparse matrix of similarity scores, with rows and columns for each section in the corpus.
+A tiny subset is shown below.
+
+```{r, fig.fullwidth = TRUE}
+a_cluster <- clusters %>% filter(cluster_id == 676) %>% `$`("doc")
+sample_matrix <- sections[a_cluster] %>% 
+  pairwise_compare(jaccard_similarity, progress = FALSE, directional = TRUE) %>% 
+  round(2) 
+sample_matrix[is.na(sample_matrix)] <- ""
+knitr::kable(sample_matrix, align = "c", caption = "A sample similarity matrix")
+```
+
+This matrix, however, required further filtering based on what we knew about the process of borrowing from other methods.
+For instance, a code from 1851 could obviously not have borrowed from a code from 1877.
+Furthermore, in chains of borrowing (e.g., MT1895 $\rightarrow$ CA1868 $\rightarrow$ CA1851 $\rightarrow$ NY1850) the latest section might have a high similarity to all of its parents, but was in fact borrowed only from the most recent parent.
+We therefore filtered the similarity matrix to remove (1) matches within the same code; (2) anachronistic matches; (3) spurious matches beneath a certain threshold.
+Then if a section had multiple matches, we kept the match from (5) the chronologically closest code from the same state unless (6) there was a substantially higher match from a different code.
+The results was a sparse matrix of the most likely matches for each section.

### 2016-02-12 talks/dh-working-group/dh-working-group.Rmd
Paragraph on harmony of the method

@@
 author: "Kellen Funk and Lincoln Mullen"
-date: "February 17, 2016"
 output: tufte::tufte_handout
@@
 # How we found the borrowings
+
+We found out how the codes borrowed from one another by breaking the codes up into sections and comparing each section to every other section.
+We were justified in this approach because what we were doing was in essence repeating the process that nineteenth-century codifiers had taken.
+Newspapers and other observers mentioned the "the scissors and paste-pot " codes, and we have found in the archives codes which were marked up and edited by hand to be adopted for a different state.
+We think our method is successful because it mimics what we know to have happened by other historical methods.
 
@@
 sample_matrix[is.na(sample_matrix)] <- ""
-knitr::kable(sample_matrix, align = "c", caption = "A sample similarity matrix")
+knitr::kable(sample_matrix, align = "c", 
+             caption = "A subset of the similarity matrix")
 ```

### 2016-02-15 talks/dh-working-group/dh-working-group.Rmd
Beginnings of clustering

@@
   stat_function(fun = prob_for_graph3, linetype = 2) +
-  stat_function(fun = prob_for_graph5, linetype = 5) +
+  stat_function(fun = prob_for_graph5, linetype = 2) +
   theme_tufte() +
@@
        y = "Probability",
-       title = "Probability of detecting a match given real similarity") +
+       title = "Probability of a match for a given similarity") +
   scale_x_continuous(breaks = seq(0, 1, .2))
@@
 Then if a section had multiple matches, we kept the match from (5) the chronologically closest code from the same state unless (6) there was a substantially higher match from a different code.
-The results was a sparse matrix of the most likely matches for each section.
+The result was a sparse matrix of the most likely matches for each section.
+
+# Learning from the borrowings
+
+A similarity matrix is a common input to many other visualizations and algorithms. We used the matrix of best borrowings to learn how the codes were borrowed in several ways.
+
+## Clustering the borrowings
+
+We used a clustering algorithm to group similar sections together.
+There are innumerable clustering algorithms, but we needed one that could work with a sparse matrix and one whose assumptions aligned with the problem we were working on.
+We used the affinity propagation clustering algorithm.^[Brendan J.
+Frey and Delbert Dueck, "Clustering by Passing Messages Between Data Points," *Science* 315 (2007): 972--976.] That algorithm assumes that there is an "exemplar" item in each cluster.
+That assumption exactly matches the case with the Field code, where a single section (likely from NY1850) had many borrowings.
+Furthermore, even though the affinity propagation clustering algorithm did not fully converge on our peculiar dataset, it did do an adequate job of clustering the documents initially.
+Because there was an exemplar section for each cluster, we were able to merge clusters where the exemplar sections had a high Jaccard similarity score.
+
+The result was a set of approximately 2,900 clusters which contained at least five sections.
+This probably overstates the number of ur-sections in the corpus.
+Each cluster contained a list of the section IDs that belonged to it.
+The biggest cluster, for instance, contained
+
+# Takeaways
+
+Methodological:
+
+- harmony of methods
+- applicability to future

### 2016-02-15 104-network-graphs-in-ggraph.Rmd
Network graph in ggraph

---
title: "Network graphs in ggraph"
author: "Lincoln Mullen"
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(igraph)
library(ggplot2)
library(ggraph)
load("cache/corpus-lsh.rda")
```

The network graphs aren't very pretty so far, so we are going to see if we can do better in [ggraph](https://github.com/thomasp85/ggraph).

Create an edge list based on numbers (not percentages) of sections shared. Notice that we are keeping only code to code matches that share a certain number of sections (`minimum_n`), we are keeping only a certain number of matches for each code (`top_matches`), and we are omitting codes that aren't part of the main network.

```{r}
minimum_n <- 50
top_matches <- 2

edges_n <- summary_matches %>% 
  filter(!is.na(match_code),
         sections_borrowed >= minimum_n) %>%  
  select(borrower_code, match_code, sections_borrowed) %>% 
  group_by(borrower_code) %>% 
  top_n(top_matches, sections_borrowed) %>% 
  ungroup() 
```

Now create a graph object of code to codes based on sections borrowed.

```{r}
codes_g <- graph_from_data_frame(edges_n, directed = TRUE) 
node_distances <- distances(codes_g,
                            mode = "out",
                            to = c("NY1848", "NY1849", "NY1850",
                                   "NY1851", "NY1853"),
                            algorithm = "unweighted") %>% 
                    apply(1, min, na.rm = TRUE)
nodes_n <- data_frame(name = names(node_distances),
                      distance = node_distances)

nodes_n <- nodes_n %>% 
  filter(distance != Inf)
edges_n <- edges_n %>% 
  filter(borrower_code %in% nodes_n$name,
         match_code %in% nodes_n$name)

codes_g <- graph_from_data_frame(edges_n, directed = TRUE, vertices = nodes_n) 
```

Now use ggraph to plot it:

```{r}
ggraph(codes_g, "igraph", algorithm = "kk") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed)) +
  geom_node_point(aes(colour = as.factor(distance)), size = 6) +
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") + 
  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +
  scale_color_discrete("Distance from a NY code") +
  ggforce::theme_no_axes() +
  geom_node_text(aes(label = name)) +
  labs(title = "Code to code borrowings") +
  theme(legend.position = "bottom")
```

### 2016-02-15 104-network-graphs-in-ggraph.Rmd
State to state network graph

@@
 library(ggraph)
+library(stringr)
 load("cache/corpus-lsh.rda")
+source("R/helper.R")
+set.seed(82892)
 ```
@@
   geom_edge_fan(aes(edge_width = sections_borrowed, 
-                    alpha = sections_borrowed)) +
+                    alpha = sections_borrowed),
+                arrow = arrow(type = "closed", ends = "first",
+                              length = unit(0.20, "inches"),
+                              angle = 15)) +
   geom_node_point(aes(colour = as.factor(distance)), size = 6) +
@@
 ```
+
+Now make a plot of state to state borrowings.
+
+```{r}
+min_state_sections <- 100
+max_state_connections <- 2
+
+states_edges <- summary_matches %>% 
+  mutate(borrower_state = extract_state(borrower_code),
+         match_state = extract_state(match_code),
+         borrower_date = extract_date(borrower_code),
+         match_date = extract_date(match_code)) %>% 
+  filter(!is.na(match_code),
+         borrower_date >= match_date,
+         borrower_state != match_state) %>% 
+  group_by(borrower_state, match_state) %>% 
+  summarize(sections_borrowed = sum(sections_borrowed)) %>% 
+  filter(sections_borrowed >= 100) %>% 
+  top_n(max_state_connections, sections_borrowed)
+
+state_nodes <- read.csv("regions.csv")
+
+states_g <- graph_from_data_frame(states_edges, directed = TRUE,
+                                  vertices = state_nodes) 
+```
+
+Now plot it.
+
+```{r}
+ggraph(states_g, "igraph", algorithm = "graphopt") +
+  geom_edge_fan(aes(edge_width = sections_borrowed, 
+                    alpha = sections_borrowed),
+                arrow = arrow(type = "closed", ends = "first",
+                              length = unit(0.20, "inches"),
+                              angle = 15)) +
+  geom_node_point(size = 6, alpha = 0.75, aes(color = region)) +
+  geom_node_text(aes(label = name)) +
+  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") + 
+  scale_edge_alpha(range = c(0.3, 0.4), guide = "none") +
+  ggforce::theme_no_axes() +
+  labs(title = "State to state borrowings") +
+  theme(legend.position = "bottom")
+```

### 2016-02-16 101-visualizations-for-article.Rmd
Move network logic into its own script

@@
 I expect the beginning of the code will be grey--no one has New York's particular court system, so no one copies the jurisdictional texts, then high heat at the heart of the Code with the Field reforms, slackening off around particular proceedings, some of which will be New York specific, then heating up again towards the end with the code of evidence.
-
-## Network graphs
-
-Create a network graph based on section percentages.
-
-```{r}
-edges_pct <- summary_matches %>% 
-  filter(percent_borrowed >= 0.05,
-         !is.na(match_code)) %>% 
-  select(borrower_code, match_code, weight = percent_borrowed) %>% 
-  group_by(borrower_code) %>% 
-  top_n(2, weight)
-edges_pct
-
-g <- graph_from_data_frame(edges_pct, directed = TRUE) 
-nodes <- distances(g, to = "NY1850", algorithm = "unweighted") %>% as.data.frame() %>% 
-  add_rownames() %>% 
-  rename(name = rowname, distance = NY1850) %>% 
-  mutate(color = ifelse(distance == 0, "red",
-                        ifelse(distance == 1, "green",
-                               ifelse(distance == 2, "yellow", "lightblue"))))
-
-nodes[nodes$name == "NY1848", "color"] <- "red"
-nodes[nodes$name == "NY1849", "color"] <- "red"
-nodes[nodes$name == "NY1850", "color"] <- "red"
-nodes[nodes$name == "NY1851", "color"] <- "red"
-g <- graph_from_data_frame(edges_pct, directed = TRUE, vertices = nodes) 
-V(g)$year <- V(g)$name %>% extract_date()
-set.seed(4221)
-
-g <- add_layout_(g, with_graphopt(niter = 4000, spring.length = 25), normalize())
-
-plot_before_year <- function(x, year) {
-  x_before <- induced.subgraph(x, which(V(x)$year <= year))
-  n <- V(x)$name
-  n_before <- V(x_before)$name
-  filter <- n %in% n_before
-  x_before$layout <- x_before$layout[filter, ]
-  par(mar = c(0,0,1,0))
-  plot(x_before, edge.width = E(x_before)$weight * 8,
-       edge.arrow.size = 0.0, vertex.size = 5)
-  title(paste0("Codes of Civil Procedure before ", year))
-}
-
-for (i in seq(1850, 1900, 5)) {
-  plot_before_year(g, i)
-}
-```
-
-Create a graph based on numbers (not percentages) of sections shared.
-Notice that we are keeping only code to code matches that share a certain number of sections (`minimum_n`), we are keeping only a certain number of matches for each code (`top_matches`), and we are omitting codes that aren't part of the main network.
-
-```{r}
-minimum_n <- 20
-top_matches <- 2
-codes_not_to_plot <- c(
-  # "CO868", 
-  # "CT1879", 
-  # "FL1847", 
-  # "FL1892", 
-  "GA1851",
-  "GA1860", 
-  "HI1859", 
-  "HI1897",
-  # "IL1866", 
-  "LA1825", 
-  "LA1844" 
-#   "MS1848", 
-#   "MS1857", 
-  # "NY1876", 
-  # "NY1879",
-  # "VA1860", 
-  # "VA1893", 
-  # "WV1868" 
-  )
-# codes_not_to_plot <- NULL
-
-edges_n <- summary_matches %>% 
-  filter(!is.na(match_code),
-         sections_borrowed >= minimum_n) %>%  
-  select(borrower_code, match_code, weight = sections_borrowed) %>% 
-  group_by(borrower_code) %>% 
-  top_n(top_matches, weight) %>% 
-  ungroup() %>% 
-  mutate(weight = rescale(weight)) %>% 
-  filter(!borrower_code %in% codes_not_to_plot,
-         !match_code %in% codes_not_to_plot)
-edges_n
-
-g_n <- graph_from_data_frame(edges_n, directed = TRUE) 
-node_distances <- distances(g_n, to = c("NY1848", "NY1849", "NY1850", "NY1851"),
-                     algorithm = "unweighted") %>% 
-                     apply(1, min, na.rm = TRUE)
-nodes_n <- data_frame(name = names(node_distances), distance = node_distances) %>% 
-  mutate(color = ifelse(distance == 0, "red",
-                        ifelse(distance == 1, "green",
-                               ifelse(distance == 2, "yellow", "lightblue"))))
-
-g_n <- graph_from_data_frame(edges_n, directed = TRUE, vertices = nodes_n) 
-V(g_n)$year <- V(g_n)$name %>% extract_date()
-
-edge_size_clamp <- function(g, multiplier = 20, max_val = 6, min_val = 1) {
-  w <- E(g)$weight * multiplier
-  w[w > max_val] <- max_val
-  w[w < min_val] <- min_val
-  w
-}
-
-set.seed(4221)
-g_n <- g_n %>% add_layout_(with_graphopt(niter = 4000, spring.length = 25),
-                           normalize())
-par(mar = c(0,0,1,0))
-plot(g_n, edge.width = edge_size_clamp(g_n), edge.arrow.size = 0, vertex.size = 5)
-title("Borrowings between codes, number of sections borrowed")
-```
-
-Now do a state to state network:
-
-```{r}
-min_state_borrowings <- 100
-top_matches <- 2
-edges_states <- summary_matches %>% 
-  mutate(borrower_date = extract_date(borrower_code),
-         match_date = extract_date(match_code),
-         borrower_state = extract_state(borrower_code),
-         match_state = extract_state(match_code)) %>% 
-  filter(!is.na(match_code),
-         borrower_date >= match_date,
-         borrower_state != match_state) %>% 
-  group_by(borrower_state, match_state) %>% 
-  summarize(n = sum(sections_borrowed)) %>% 
-  filter(n >= min_state_borrowings) %>% 
-  select(borrower_state, match_state, weight = n) %>% 
-  group_by(borrower_state) %>% 
-  top_n(top_matches, weight) %>% 
-  ungroup() %>% 
-  mutate(weight = rescale(weight))
-
-edges_states
-
-g_states <- graph_from_data_frame(edges_states, directed = TRUE)
-
-state_distances <- distances(g_states, to = "NY", algorithm = "unweighted") 
-nodes_states <- data_frame(name = rownames(state_distances),
-                           distance = state_distances[, 1]) %>% 
-  mutate(color = ifelse(distance == 0, "red",
-                        ifelse(distance == 1, "green",
-                               ifelse(distance == 2, "yellow", "lightblue"))))
-
-g_states <- graph_from_data_frame(edges_states, directed = TRUE,
-                                  vertices = nodes_states) %>% 
-  decompose(min.vertices = 3) %>% 
-  `[[`(1)
-
-set.seed(4221)
-g_states <- g_states %>% add_layout_(with_graphopt(niter = 4000,
-                                                   spring.length = 25),
-                                     normalize())
-par(mar = c(0,0,1,0))
-plot(g_states, 
-     edge.width = edge_size_clamp(g_n), edge.arrow.size = 0.5,
-     edge.arrow.mode = 1,
-     vertex.size = 5, vertex.label.dist = 0.85, vertex.label.degree = pi)
-title("Borrowings between states, number of sections borrowed")
-```

### 2016-02-16 scripts/network-graphs.R

@@ -1,0 +1,60 @@
+library(dplyr)
+library(igraph)
+library(ggplot2)
+library(ggraph)
+library(stringr)
+load("cache/corpus-lsh.rda")
+source("R/helper.R")
+set.seed(82892)
+
+minimum_n <- 50
+top_matches <- 2
+
+edges_n <- summary_matches %>%
+  filter(!is.na(match_code),
+         sections_borrowed >= minimum_n) %>%
+  select(borrower_code, match_code, sections_borrowed) %>%
+  group_by(borrower_code) %>%
+  top_n(top_matches, sections_borrowed) %>%
+  ungroup()
+
+codes_g <- graph_from_data_frame(edges_n, directed = TRUE)
+node_distances <- distances(codes_g,
+                            mode = "out",
+                            to = c("NY1848", "NY1849", "NY1850",
+                                   "NY1851", "NY1853"),
+                            algorithm = "unweighted") %>%
+                    apply(1, min, na.rm = TRUE)
+nodes_n <- data_frame(name = names(node_distances),
+                      distance = node_distances)
+
+nodes_n <- nodes_n %>%
+  filter(distance != Inf)
+edges_n <- edges_n %>%
+  filter(borrower_code %in% nodes_n$name,
+         match_code %in% nodes_n$name)
+
+codes_g <- graph_from_data_frame(edges_n, directed = TRUE, vertices = nodes_n)
+
+min_state_sections <- 100
+max_state_connections <- 2
+
+states_edges <- summary_matches %>%
+  mutate(borrower_state = extract_state(borrower_code),
+         match_state = extract_state(match_code),
+         borrower_date = extract_date(borrower_code),
+         match_date = extract_date(match_code)) %>%
+  filter(!is.na(match_code),
+         borrower_date >= match_date,
+         borrower_state != match_state) %>%
+  group_by(borrower_state, match_state) %>%
+  summarize(sections_borrowed = sum(sections_borrowed)) %>%
+  filter(sections_borrowed >= 100) %>%
+  top_n(max_state_connections, sections_borrowed)
+
+state_nodes <- read.csv("regions.csv")
+
+states_g <- graph_from_data_frame(states_edges, directed = TRUE,
+                                  vertices = state_nodes)
+
+save(codes_g, states_g, file = "cache/network-graphs.rda")

### 2016-02-16 R/section-matches.R
Change the logic for out-of-state matches

@@ -49,12 +49,18 @@ get_best_matches <- function(matches, threshold = 0.1, tolerance = 0.1) {
     ungroup()
   # message("Within state sliced: ", pnum(nrow(matches_within_state)))
 
-  # Outside of state matches, take the highest ranked match
+  # Outside of state matches, take the match from the code with the newest date
+  # as long as it is from the same state as the match that has the highest
+  # score
   matches_outside_state <- matches_outside_state %>%
     group_by(borrower_section) %>%
     arrange(desc(score)) %>%
+    mutate(matches_state_of_best_match = match_state == head(match_state, 1)) %>%
+    filter(matches_state_of_best_match) %>%
+    arrange(desc(match_year), desc(score)) %>%
     slice(1) %>%
-    ungroup()
+    ungroup() %>%
+    select(-matches_state_of_best_match)
   # message("Outside state sliced: ", pnum(nrow(matches_outside_state)))
 
   # Final cleanup

### 2016-02-16 R/section-matches.R
Give a slightly wider tolerance for matches

@@ -1,4 +1,4 @@
-get_best_matches <- function(matches, threshold = 0.1, tolerance = 0.1) {
+get_best_matches <- function(matches, threshold = 0.1, tolerance = 0.15) {
 
   require("dplyr")
   # message("Start: ", pnum(nrow(matches)))

### 2016-02-16 104-network-graphs-in-ggraph.Rmd
Depend on script for network analysis

@@
 load("cache/corpus-lsh.rda")
+load("cache/network-graphs.rda")
 source("R/helper.R")
@@
 The network graphs aren't very pretty so far, so we are going to see if we can do better in [ggraph](https://github.com/thomasp85/ggraph).
-
-Create an edge list based on numbers (not percentages) of sections shared.
-Notice that we are keeping only code to code matches that share a certain number of sections (`minimum_n`), we are keeping only a certain number of matches for each code (`top_matches`), and we are omitting codes that aren't part of the main network.
-
-```{r}
-minimum_n <- 50
-top_matches <- 2
-
-edges_n <- summary_matches %>% 
-  filter(!is.na(match_code),
-         sections_borrowed >= minimum_n) %>%  
-  select(borrower_code, match_code, sections_borrowed) %>% 
-  group_by(borrower_code) %>% 
-  top_n(top_matches, sections_borrowed) %>% 
-  ungroup() 
-```
-
-Now create a graph object of code to codes based on sections borrowed.
-
-```{r}
-codes_g <- graph_from_data_frame(edges_n, directed = TRUE) 
-node_distances <- distances(codes_g,
-                            mode = "out",
-                            to = c("NY1848", "NY1849", "NY1850",
-                                   "NY1851", "NY1853"),
-                            algorithm = "unweighted") %>% 
-                    apply(1, min, na.rm = TRUE)
-nodes_n <- data_frame(name = names(node_distances),
-                      distance = node_distances)
-
-nodes_n <- nodes_n %>% 
-  filter(distance != Inf)
-edges_n <- edges_n %>% 
-  filter(borrower_code %in% nodes_n$name,
-         match_code %in% nodes_n$name)
-
-codes_g <- graph_from_data_frame(edges_n, directed = TRUE, vertices = nodes_n) 
-```
-
-Now use ggraph to plot it:
 
@@
 ```{r}
-min_state_sections <- 100
-max_state_connections <- 2
-
-states_edges <- summary_matches %>% 
-  mutate(borrower_state = extract_state(borrower_code),
-         match_state = extract_state(match_code),
-         borrower_date = extract_date(borrower_code),
-         match_date = extract_date(match_code)) %>% 
-  filter(!is.na(match_code),
-         borrower_date >= match_date,
-         borrower_state != match_state) %>% 
-  group_by(borrower_state, match_state) %>% 
-  summarize(sections_borrowed = sum(sections_borrowed)) %>% 
-  filter(sections_borrowed >= 100) %>% 
-  top_n(max_state_connections, sections_borrowed)
-
-state_nodes <- read.csv("regions.csv")
-
-states_g <- graph_from_data_frame(states_edges, directed = TRUE,
-                                  vertices = state_nodes) 
-```
-
-Now plot it.
-
-```{r}
 ggraph(states_g, "igraph", algorithm = "graphopt") +

### 2016-02-16 104-network-graphs-in-ggraph.Rmd
Try the "nicely" layout for now

@@
 ```{r}
-ggraph(codes_g, "igraph", algorithm = "kk") +
+ggraph(codes_g, "igraph", algorithm = "nicely") +
   geom_edge_fan(aes(edge_width = sections_borrowed, 
@@
 ```{r}
-ggraph(states_g, "igraph", algorithm = "graphopt") +
+ggraph(states_g, "igraph", algorithm = "nicely") +
   geom_edge_fan(aes(edge_width = sections_borrowed, 

### 2016-02-16 talks/dh-working-group/dh-working-group.Rmd
Most of the methods part of the working group talk

@@
 library(knitr)
+library(igraph)
+library(ggraph)
+library(stringr)
 source("../../R/helper.R")
 source("../../R/section-matches.R")
+source("../../R/spectrogram.R")
 load("../../cache/corpus-lsh.rda")
+load("../../cache/network-graphs.rda")
 clusters <- read_csv("../../out/clusters.csv")
@@
 Each cluster contained a list of the section IDs that belonged to it.
-The biggest cluster, for instance, contained
+The biggest cluster, for instance, contained 103 sections, which concerned the use of affidavits in pleading.
+Scholars in digital literary studies often speak of "deformance" of texts.^[Stephen Ramsay, *Reading Machines: Toward an Algorithmic Criticism* (University of Illinois Press, 2011), ch.
+3.] Clustering the sections of the codes deformed them because it pulled the sections out of the codes from which they had been embedded in, and placed them in chronological order.
+This allowed us to see the development and spread of the law.
+You might consider this a method of distant reading which then permits a kind of close reading.
+Consider this (admittedly more important than usual) excerpt from one of the clusters which concerned the competence of witnesses:
+
+```
+Cluster ID: 10382          Documents in cluster: 20
+Exemplar: OR1854-003380    Earliest: NY1850-018680
+
+NY1850-018680 ------------------------------------------------------------------
+1709. The following persons are not admissible: 1. Those who are of unsound mind
+at the time of their production for examination: 2. Children under ten years of
+age, who appear incapable of receiving just impressions of the facts, respecting
+which they are examined, or of relating them truly.
+
+CA1851-004380 ------------------------------------------------------------------
+394. The following persons shall not be witnesses: ‘ lst. Those who areof
+unsound mind at the time of their production for examination: 2d. Children under
+ten years of age, who appear incapable of receiving just impressions of the
+facts respecting which they are examined, or of relating them truly: and, 3d.
+Indians, or persons having one fourth or more of Indian blood, in an action or
+proceeding to which a white person is a party: 4th. Negroes, or persons having
+one half or more Negro blood, in an action or proceeding to which a white person
+is a party.
+
+OR1854-003380 ------------------------------------------------------------------
+6. The following persons shall not be competent to testify 1. Those who are of
+unsound mind, or intoxicated at the time of their production for examination ;
+2. Children under ten years of age, who appear incapable of receiving just
+impressions of the facts respecting which they are examined, or of relating them
+truly; 4. Negroes, mulattocs and Indians, or persons one half or more of Indian
+blood, in an action or proceeding to which a white person is a party.
+```
+
+## Networks of borrowings
+
+A matrix of similarities can be thought of as an adjacency matrix to a network graph.
+We created network graph of the code to code borrowings.
+In an effort not to make this a typical hairball, we filtered the edges so that each code was connected to another code only if it borrowed at least fifty sections.
+
+```{r, fig.fullwidth=TRUE, fig.cap="Code to code borrowings.", fig.height=3}
+set.seed(21000)
+ggraph(codes_g, "igraph", algorithm = "nicely") +
+  geom_edge_fan(aes(edge_width = sections_borrowed, 
+                    alpha = sections_borrowed),
+                arrow = arrow(type = "closed", ends = "first",
+                              length = unit(0.10, "inches"),
+                              angle = 15)) +
+  geom_node_point(aes(color = as.factor(distance)), size = 2) +
+  scale_edge_width("Sections borrowed", range = c(0.25, 1), guide = "none") + 
+  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +
+  scale_color_brewer(palette = "Set1", "Distance from a NY code") +
+  ggforce::theme_no_axes(base_size = 4, base_family = "serif") +
+  geom_node_text(aes(label = name), size = 1.5) +
+  theme(legend.position = "bottom", 
+        panel.border = element_blank())
+```
+
+This network shows the structure of the borrowings.
+In particular, it demonstrates the centrality of New York's code, especially the eponymous Field Code of 1850.
+The New York code then became the basis of other families of codes.
+Those codes heavily edited NY1850, but within the families (which were often based on the proximity of states) the borrowings tended to be much more close.
+Yet states could and did sometimes borrow from multiple states.
+Notice that this network graph moves both geographically an chronologically.
+It is later codes which tend to be on the outside of the network diagram, and they are the most distant from the original Field Code in both time and borrowings.^[If we move up a level of abstraction we can consider not code to code but state to state borrowings.
+This shows us the pattern of borrowings more clearly, albeit at a considerable loss of detail.
+While that is a constant challenge in any kind of visualization work, it is especially a challenge here where we know that our measures of borrowings can be inaccurate for individual sections, though they are reliable on the whole.]
+
+```{r, eval=FALSE, fig.fullwidth=TRUE, fig.cap="State to state borrowings.", fig.height=3}
+set.seed(210)
+ggraph(states_g, "igraph", algorithm = "graphopt") +
+  geom_edge_fan(aes(edge_width = sections_borrowed, 
+                    alpha = sections_borrowed),
+                arrow = arrow(type = "closed", ends = "first",
+                              length = unit(0.10, "inches"),
+                              angle = 15)) +
+  geom_node_point(size = 3, aes(color = region)) +
+  scale_edge_width("Sections borrowed", range = c(0.25, 1), guide = "none") + 
+  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +
+  scale_color_brewer(palette = "Dark2", "Region") +
+  ggforce::theme_no_axes(base_size = 4, base_family = "serif") +
+  geom_node_text(aes(label = name), size = 1.5) +
+  theme(legend.position = "bottom", 
+        panel.border = element_blank())
+```
+
+## Borrowings within each code
+
+Finally, each of those nodes on the network diagram can be individualy investigated to get a more detailed perspective on how the codes were borrowed.
+We did this by creating a kind of "spectrograph" or fingerprint of which sections in a code were borrowed from which other codes.
+Take the case of Washington state's 1855 code.
+
+```{r, fig.cap="Borrowed sections in Washington's 1855 code. Each section in the code is represented by a square, the color of which indicates where it was borrowed from."}
+spectrogram("WA1855", best_matches, white_list = 4)
+```
+
+We can observe that most of the code is borrowed from some source or another.
+While there is a fair bit of "other" which are probably sections which we cannot adequately attribute, the pattern of borrowing is clear: IN1852 and OR1854 provide the majority of the borrowings, and they do so in two bands.
+This pattern is curious, because one might expect Washington to borrow from Oregon and California but Indiana is not an obvious choice.
+And why do the borrowings fall into these bands?
+Regulations on judgment were borrowed from Oregon, while enforcement provisions came from Indiana.
+We think this is because one of the Washington code commissioners, Edward Lander, was an Indiana appelate judge from 1850 to 1853, while another commissioner, William Strong, was a justice of the Oregon Supreme Court in the same years.
+In other words, the law in this case moved with judges and lawyers who picked the parts they knew best.
+
+Of course we can also demonstrate in an obvious way when codes were borrwed heavily from one source:
+
+```{r}
+spectrogram("NV1861", best_matches, white_list = 4)
+```
 

### 2016-02-16 scripts/network-graphs.R
Don't remove codes an Inf distance from New York
This was a bad error because it removed dead end codes like NM1865 which weren't derived from NY but which contributed to other codes.

@@ -28,12 +28,6 @@ node_distances <- distances(codes_g,
 nodes_n <- data_frame(name = names(node_distances),
                       distance = node_distances)
 
-nodes_n <- nodes_n %>%
-  filter(distance != Inf)
-edges_n <- edges_n %>%
-  filter(borrower_code %in% nodes_n$name,
-         match_code %in% nodes_n$name)
-
 codes_g <- graph_from_data_frame(edges_n, directed = TRUE, vertices = nodes_n)
 
 min_state_sections <- 100

### 2016-02-16 scripts/network-graphs.R
Keep edges with a minimum sections OR a minimum percentage

@@ -7,12 +7,16 @@ load("cache/corpus-lsh.rda")
 source("R/helper.R")
 set.seed(82892)
 
+# We will keep edges that have at least a certain number of shared connections
+# OR a percentage of borrowings that is greater than than a set percentage, but
+# we will keep at most a certain number of edges per code.
 minimum_n <- 50
+minimum_percent <- 0.20
 top_matches <- 2
 
 edges_n <- summary_matches %>%
   filter(!is.na(match_code),
-         sections_borrowed >= minimum_n) %>%
+         sections_borrowed >= minimum_n | percent_borrowed >= minimum_percent) %>%
   select(borrower_code, match_code, sections_borrowed) %>%
   group_by(borrower_code) %>%
   top_n(top_matches, sections_borrowed) %>%

### 2016-02-16 R/section-matches.R
White list within-the-same year matches

@@ -11,6 +11,24 @@ get_best_matches <- function(matches, threshold = 0.1, tolerance = 0.15) {
   # Remove anachronistic matches
   matches <- matches %>%
     filter(borrower_year >= match_year)
+
+  # White list matches within the same year; otherwise remove them
+  matches <- matches %>%
+    filter(
+      (borrower_year != match_year) | (borrower_code == "MO1849" & match_code == "NY1849"),
+      (borrower_year != match_year) | (borrower_code == "WI1849" & match_code == "NY1849"),
+      (borrower_year != match_year) | (borrower_code == "IA1851" & match_code == "KY1851"),
+      (borrower_year != match_year) | (borrower_code == "DC1857" & match_code == "NE1857"),
+      (borrower_year != match_year) | (borrower_code == "IA1859" & match_code == "KS1859"),
+      (borrower_year != match_year) | (borrower_code == "IA1859" & match_code == "NE1859"),
+      (borrower_year != match_year) | (borrower_code == "IA1859" & match_code == "MN1859"),
+      (borrower_year != match_year) | (borrower_code == "KS1859" & match_code == "NE1859"),
+      (borrower_year != match_year) | (borrower_code == "NC1868" & match_code == "DT1868"),
+      (borrower_year != match_year) | (borrower_code == "NC1868" & match_code == "ND1868"),
+      (borrower_year != match_year) | (borrower_code == "DT1887" & match_code == "AZ1887"),
+      (borrower_year != match_year) | (borrower_code == "ND1887" & match_code == "AZ1887")
+    )
+
   # message("Anachronistic: ", pnum(nrow(matches)))
 
   # Remove matches below threshold

### 2016-02-16 scripts/network-graphs.R
Rely on the variable not a hardcoded value

@@ -47,7 +47,7 @@ states_edges <- summary_matches %>%
          borrower_state != match_state) %>%
   group_by(borrower_state, match_state) %>%
   summarize(sections_borrowed = sum(sections_borrowed)) %>%
-  filter(sections_borrowed >= 100) %>%
+  filter(sections_borrowed >= min_state_sections) %>%
   top_n(max_state_connections, sections_borrowed)
 
 state_nodes <- read.csv("regions.csv")

### 2016-02-16 scripts/network-graphs.R
Prune multiple out of state edges

@@ -10,16 +10,24 @@ set.seed(82892)
 # We will keep edges that have at least a certain number of shared connections
 # OR a percentage of borrowings that is greater than than a set percentage, but
 # we will keep at most a certain number of edges per code.
+#
+# We will also prune second edges if they come from a different state than the
+# borrowing code AND are from the same state as a stronger borrowing.
 minimum_n <- 50
 minimum_percent <- 0.20
 top_matches <- 2
 
 edges_n <- summary_matches %>%
   filter(!is.na(match_code),
-         sections_borrowed >= minimum_n | percent_borrowed >= minimum_percent) %>%
+         sections_borrowed >= minimum_n |
+           percent_borrowed >= minimum_percent) %>%
   select(borrower_code, match_code, sections_borrowed) %>%
   group_by(borrower_code) %>%
   top_n(top_matches, sections_borrowed) %>%
+  arrange(desc(sections_borrowed)) %>%
+  filter(!(extract_state(match_code) == head(extract_state(match_code), 1) &
+             match_code != head(match_code, 1) &
+             extract_state(match_code) != extract_state(borrower_code))) %>%
   ungroup()
 
 codes_g <- graph_from_data_frame(edges_n, directed = TRUE)

### 2016-02-16 104-network-graphs-in-ggraph.Rmd
Rerun analysis with new sections and edges

--- 2016-02-16 104-network-graphs-in-ggraph.Rmd
@@
 ```{r}
-ggraph(codes_g, "igraph", algorithm = "kk") +
+ggraph(codes_g, "igraph", algorithm = "fr") +
   geom_edge_fan(aes(edge_width = sections_borrowed, 
@@
   labs(title = "Code to code borrowings") +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom",
+        panel.border = element_blank())
 ```
@@
   labs(title = "State to state borrowings") +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom",
+        panel.border = element_blank())
 ```

### 2016-02-16 talks/dh-working-group/dh-working-group.Rmd
Revise the first third or so of the handout

@@
 output: tufte::tufte_handout
+date: "February 17, 2016"
 ---
+
+\begin{abstract}
+This handout describes our work in progress for the Digital Humanities Working Group at George Mason University.\\
+E-mail: \url{lincoln@lincolnmullen.com}, \url{kfunk@princeton.edu}
+\end{abstract}
 
@@
 
+\begin{marginfigure}
+\includegraphics{../aha2016/field.jpg}
+\caption{David Dudley Field II (1805--1894).}
+\end{marginfigure}
+
 After the American Revolution, most states were common law jurisdictions, sometimes with courts of chancery.
-These courts had a complex system of pleading defined mostly be case law.
-By the 1840s, lawyers and the mercantile classes called for the codification of civil procedure.
-At stake in the ensuing debates were the rationality of the law a science, or the purity of Anglo-Saxon civilization.
-New York was the first state to codify its procedure, thanks to the efforts of David Dudly Field.
-New York's 1848 Field code became by the end of the century the model for the procedural codes in state jurisdiction.
+These courts had a complex system of pleading defined by case law.
+By the 1840s, lawyers and the mercantile classes called for the simplification and rationalization of civil procedure through codification.
+Factions for and against codification debated about whether codes were laws passed by democratic legislatures or anti-democratic legal elites, whether codification served only the needs of wealthy capitalists, and whether the purity of Anglo-Saxon civilization derived from the common law would be maintained.
+The economic capital New York was the first state to codify its procedure in 1848, thanks to the efforts of David Dudly Field.
+By the end of the century, New York's Field Code became the model for the codes of civil procedure in most states.
 
@@
 \includegraphics{../aha2016/field-code-states-map.jpeg}
-\caption{Field Code states by date of enactment. Many states subsequently revised their codes of civil procedure.}
+\caption{Field Code states by date of first enactment. Many states subsequently revised their codes of civil procedure.}
 \end{figure}
@@
 Which codes borrowed from each other?
-Which sections were borrowed, and which were modified?
-What were the patterns of borrowings and of innovations?
+Which sections were borrowed, and howe were they modified?
+What were the patterns and structures of borrowings and of innovations?
+To answer these questions we gathered a corpus of 115 codes and statutes of civil procedure from 1806 to 1933 containing about 7.6 million words, then algorithmically detected the borrowings within that corpus.
 
-To answer these questions we have gathered a corpus of 115 codes of civil procedure containing about 7.6 million words, and detected the borrowings algorithmically.
-Our approach is one of two common approaches.
-We have gathered a dataset of sources to answer a given set of questions; the other option is to take the sources as given and explore the data to see what questions it raises.^[Against the buzzword "big data," I call this "middle data", which we might define as data that is too small for distributed computation but too big for naive algorithms.
-Alternatively, it is data where the size of the sample approaches the size of the population, but where the population is strictly constrained by the research problem.
-Against big data, middle data offers the most promising way to combine traditional and digital history methods.]
+The aim of this handout is to describe our contributions to digital methods in legal history (and other fields), and to outline the interpretations we have drawn about the migration of the Field Code.
+Our method is one of two common approaches in computational history.
+We created a dataset to answer a given set of questions; a different approach is to take the sources as given and explore the data to see what questions it raises.^[This approach features "middle data" (not "big data") which we might define as data that is too small for distributed computation but too big for naive algorithms.
+Alternatively, it is data where the size of the sample approaches the size of the population, but where the population is strictly constrained by the research problem.] Our historical findings describe how American legal practice became standardized around a New York code yet varied by region.
 
@@
 
-We found out how the codes borrowed from one another by breaking the codes up into sections and comparing each section to every other section.
-We were justified in this approach because what we were doing was in essence repeating the process that nineteenth-century codifiers had taken.
-Newspapers and other observers mentioned the "the scissors and paste-pot " codes, and we have found in the archives codes which were marked up and edited by hand to be adopted for a different state.
-We think our method is successful because it mimics what we know to have happened by other historical methods.
+We found out how the codes borrowed from one another by splitting the codes into sections and comparing each section to every other section.^[The data and code to re-run our analyses are available in a GitHub repository: <https://github.com/lmullen/civil-procedure-codes>.
+We generalized our method in Lincoln Mullen, "textreuse: Detect Text Reuse and Document Similarity," R package version 0.1.2 (2015): <https://github.com/ropensci/textreuse>, which was peer-reviewed by rOpenSci.] This process in essence mimicked the way that nineteenth-century code commissioners literally cut and pasted sections from other jurisidictions.
 
@@
 
-Having identified all of the relevant codes of civil procedure in the nineteenth-century, including separately published codes, session laws, and statutes, we used OCR software to create plain-text versions of the codes.^[The data and code to re-run our analyses are available in a GitHub repository: <https://github.com/lmullen/civil-procedure-codes>.] These OCR files received only a light cleaning: we edited the section markers by hand as necessary, and wrote a script to fix the most obvious OCR errors.
+Having identified all of the relevant laws of civil procedure in the nineteenth-century, including codes, session laws, and statutes, we used OCR software to create plain-text versions of the codes.
+These OCR files received only a light cleaning: we edited the section markers by hand as necessary, and wrote a script to fix the most obvious OCR errors.
 
@@
 The corpus contains nearly 98,000 sections.
-Below is a sample file containing a single section from a single code.^[Section 151 of the California's 1851 code of civil procedures from the file `CA1851-001660.txt`.]
+Below is a sample file containing a single section from a single code.^[1851 California Laws 74, §151.
+This corresponds to our file `CA1851-001660.txt`.
+Notice the minor OCR errors.]
 
@@
 The next stage in our process was to measure the similarity of the sections one to another.
-^[This stage of our process was embedded in the [textreuse package](https://github.com/ropensci/textreuse) for R, which was peer-reviewed by rOpenSci: <https://github.com/ropensci/textreuse>.
-See also my blog post, "[An Introduction to the textreuse Package, with Suggested Applications](http://lincolnmullen.com/blog/an-introduction-to-the-textreuse-package/)": <http://lincolnmullen.com/blog/an-introduction-to-the-textreuse-package/>.
-] We first had to tokenize the text, meaning that  After experimenting we found that five-grams worked well.^[We also hashed the tokens, meaning that we converted them to integer representations which permits considerable savings of memory.]  The use of n-grams, which is a ubiquitious technique, permits redudancy of phrasing, intentional word changes, and OCR errors.
+We first had to tokenize the text, meaning that  After experimenting we found that five-grams worked well.^[We also hashed the tokens, meaning that we converted them to integer representations which permits considerable savings of memory.]  The use of n-grams, which is a ubiquitious technique, permits redudancy of phrasing, intentional word changes, and OCR errors.
 Below are the first five tokens from the section above.
@@
 The result was a sparse matrix of similarity scores, with rows and columns for each section in the corpus.
-A tiny subset is shown below.
+A tiny subset is shown below.^[Notice that all of the examples given from here on relate to the same set of codes from California, Oregon, and Washington, in order to demonstrate how the different parts of our method work together.]
 
@@
 
-Of course we can also demonstrate in an obvious way when codes were borrwed heavily from one source:
+Of course we can also demonstrate in an obvious way when codes were borrwed heavily from one source, yet we can also note the unusual places in the code where apparently later innovations from Oregon were borrowed, or where the California codes were not strictly borrowed.
 
@@
 spectrogram("NV1861", best_matches, white_list = 4)
+
+spectrogram("NM1865", best_matches, white_list = 8)
 ```
 
-# Takeaways
+# Conclusions
 
-Methodological:
+There are two sets of conclusions, or at least observations, which can be drawn from this work in progress.
 
-- harmony of methods
-- applicability to future
+We think that the methodology of this kind of work has a number of applications to historical problems.
+First, question framing.
+One very useful thing to do when framing a digital historical problem is to begin with exploratory data analysis of a large corpus---to let the sources drive the questions.
+We have modeled an approach that is at the opposite side of the interpretative spiral, by forming a corpus to answer an already formed historical question.
+The use of *medium data* permits us a close relationship between traditional and digital historical methods, which is our second point.
+Our methods produced useful historical knowledge because the digital methods were closely connected to assumptions we knew to be true about the data from our traditional historical work.
+To give a brief list of those harmonies: we knew that code commissioners worked with "the scissors and paste-pot," as political debates about the codes frequently complained, and we knew from examining codes in thea archives that commisions literally marked up the legislation of other states.^[*Rocky Mountain News*, January 20, 1877.] That knowledge, particularly the knowledge that the borrowings happened at the level of the section, justified our use of the minhash/LSH algorithm.
+Our knowledge that particular sections were frequently borrowed and thus were exemplars justified our use of the affinity propagration algorithm.
+And our assumptions about how codes were passed from state to state made network analysis an obvious fit.^[We might call these an example of the "no free lunch theorem" in action.
+See David Robinson, "K-means clustering is not a free lunch," *Variance Explained*, January 16, 2015: <http://varianceexplained.org/r/kmeans-free-lunch/>.] And third, we think that this method is widely applicable to different historical questions and sources, almost without modification in the case of corpora where the documents can be readily divided into sections.
+This method could be pursued in other legal documents such as treatises or statutes; it could also be pursued in sources of other domains, such as hymnbooks or tracts.
+
+Finally, the article that we are writing about the Field code will bring together what we have learned through traditional historical work and the digital methods described above.
+But we can sum up what we have learned primarily from the digital methods.
+This study is significant because it gets at the heart of lawmaking in U.S.
+history.
+Lawyers and judges, politicians and newspaper editors warred over whether codes that were drafted by commissioners and borrowed wholesale from one another were actually democratic laws or the imposition of a legal elite.
+Furthermore, these borrowings called into question the extent to which the United States was actually a federal system of laws.
+We have documented the scope and content of the exact borrowings.
+We have shown the dominance of New York's laws in a supposedly federal system, and shown exactly the extent to which code commissioners borrowed from that code and its descendants.
+Economic centers, which needed certain kinds of laws tied up with the expansion of markets and American capitalism, were in fact legal centers.
+But we have also demonstrated that regional distinctions were also significant, so that regional economic centers like California and Ohio generated separate Western and Midwestern families of codes.
+Finally we have shown how haphazard the process of codification could be, as in the case of the Washington code cited above where judges from jurisdictions borrowed laws that they were familiar with, and in the case of New Mexico, which borrowed Missouri's laws because those were the law books which were actually available.
+
+The specific provisions of the Field code aren't in continued use in every jurisdiction, (though in states like Missouri the Field Code provisions survive virtually unchanged) but the basic ideas embedded in the Field Code are standard practice which have spread throughout the entire country.
+Without too much exaggeration we might say that our method has revealed the spine of modern American legal practice.

### 2016-02-16 talks/dh-working-group/dh-working-group.Rmd
Revise section on Jaccard similarity

@@
 
-The next stage in our process was to measure the similarity of the sections one to another.
-We first had to tokenize the text, meaning that  After experimenting we found that five-grams worked well.^[We also hashed the tokens, meaning that we converted them to integer representations which permits considerable savings of memory.]  The use of n-grams, which is a ubiquitious technique, permits redudancy of phrasing, intentional word changes, and OCR errors.
+Next we tokenized the text into shingled n-grams.^[We also hashed the tokens, meaning that we converted them to integer representations.] After experimenting we found that five-grams worked best for detecting similarity despite intentional word changes and OCR errors.
 Below are the first five tokens from the section above.
@@
 That measure, treating the tokens as a set, is the ratio of shared tokens to the ratio of total tokens in two documents.
-The result is a single number ranging from 0 (complete dissimilarity) to 1 (complete similarity).^[From MMDS.
-Formally, the definition of the Jaccard similarity score is $$J(A, B) = \frac{ | A \cap B| }{ | A \cup B|}$$] For instance, the section from the California 1851 code above was derived from section 756 of the New York 1850 code (`NY1850-008350.txt`).
-Because of changes to the wording and OCR errors, the Jaccard similarity between the two sections was `r jaccard_similarity(sections[["NY1850-008350"]], sections[["CA1851-001660"]]) %>% round(3)`.
+That ration can range from 0 (complete dissimilarity) to 1 (complete similarity).^[Jure Leskovec, Anand Rajaraman, and Jeff Ullman, *Mining of Massive Datasets*, 2nd ed.
+(Cambridge University Press, 2014), ch.
+3, <http://www.mmds.org>.
+The formal definition of the Jaccard similarity score is $$J(A, B) = \frac{ | A \cap B| }{ | A \cup B|}$$] For instance, the section from the 1851 California code above was derived from the 1850 New York code.^[*Final Report of the Commission on Practice and Pleadings*, 2 *Documents of the Assembly of New York*, 73rd session, No.
+16 (1850), 317, §756.
+This corresponds to our file `NY1850-008350.txt`.] Because of changes to the wording and OCR errors, the Jaccard similarity between the two sections was `r jaccard_similarity(sections[["NY1850-008350"]], sections[["CA1851-001660"]]) %>% round(3)`.
 By carefully checking matching sections versus scores, we arrived at a rule of thumb that a Jaccard similarity score greater than 0.15 likely indicated a match, and a score greater than 0.2 almost certainly indicated a match.
+Most matching sections had scores much higher that 0.2.
 

### 2016-02-16 talks/dh-working-group/dh-working-group.Rmd
Revise section on determining best matches

@@
 load("../../cache/network-graphs.rda")
-clusters <- read_csv("../../out/clusters.csv")
+clusters <- read_csv("../../out/clusters/clusters.csv")
 ```
@@
 This corresponds to our file `NY1850-008350.txt`.] Because of changes to the wording and OCR errors, the Jaccard similarity between the two sections was `r jaccard_similarity(sections[["NY1850-008350"]], sections[["CA1851-001660"]]) %>% round(3)`.
-By carefully checking matching sections versus scores, we arrived at a rule of thumb that a Jaccard similarity score greater than 0.15 likely indicated a match, and a score greater than 0.2 almost certainly indicated a match.
-Most matching sections had scores much higher that 0.2.
+By carefully checking matching sections versus scores, we arrived at a rule of thumb that a Jaccard similarity score greater than 0.15 likely indicated a match, and a score greater than 0.2 almost certainly indicated a match.^[The mean score for the best section matches was `r best_matches$score %>% mean(na.rm = TRUE) %>% round(2)`.]
 
@@
 
-The next step was to compute similarity for every section in the corpus.
-The difficulty is that to compare every section to every other section would require an enormous number of comparisons: approximately `r length(sections) %>% num_comparisons() %>% billionize()` billion for our corpus.^[Assuming that the similarity measure is bi-directional, the number of pairwise comparisons in a corpus is given by $(n^2-n) / {2}$.] Most of these comparisons would be wasted, since most sections have zero relationship to most other sections.
+The next step was to compute the similarity of every section in the corpus to every other section.
+That posed a problem: doing so would require an enormous number of comparisons, approximately `r length(sections) %>% num_comparisons() %>% billionize()` billion for our corpus.^[Assuming that the similarity measure is bi-directional, the number of pairwise comparisons in a corpus is given by $(n^2-n) / {2}$.] Most of these comparisons would be unnecessary, since each section has no relationship to most other sections.
 
@@
 It approximates the Jaccard similarity of the two documents.
-The algorithm requires a computation for each document, not each pair of documents, so the compute time grows linearly not geometrically.
-And by controlling various parameters, one can determine a threshold similarity score above which one is likely to find a match and unlikely to find an inaccurate match.
+It requires a computation for each document rather than each pair of documents, so the computation time grows linearly not geometrically.
+And by controlling various parameters, one can set a threshold similarity score above which one is likely to find a genuine match and unlikely to find a spurious match.
 
-Once we had detected the candidate pairs, we measured the actual Jaccard similarity for those pairs.
+Once we detected the candidate pairs, we measured the actual Jaccard similarity of those pairs.
 The result was a sparse matrix of similarity scores, with rows and columns for each section in the corpus.
-A tiny subset is shown below.^[Notice that all of the examples given from here on relate to the same set of codes from California, Oregon, and Washington, in order to demonstrate how the different parts of our method work together.]
 
 ```{r, fig.fullwidth = TRUE}
-a_cluster <- clusters %>% filter(cluster_id == 676) %>% `$`("doc")
+a_cluster <- clusters %>%
+  filter(cluster_id == 10382) %>%
+  `$`("doc") %>% 
+  head(5)
 sample_matrix <- sections[a_cluster] %>% 
@@
   round(2) 
+sample_matrix[upper.tri(sample_matrix)] <- NA
+sample_matrix[3, 2] <- NA
+sample_matrix[4, 2:3] <- NA
+sample_matrix[5, 1:3] <- NA
 sample_matrix[is.na(sample_matrix)] <- ""
 knitr::kable(sample_matrix, align = "c", 
-             caption = "A subset of the similarity matrix")
+             caption = "A subset of the filtered similarity matrix.")
 ```
 
-This matrix, however, required further filtering based on what we knew about the process of borrowing from other methods.
-For instance, a code from 1851 could obviously not have borrowed from a code from 1877.
-Furthermore, in chains of borrowing (e.g., MT1895 $\rightarrow$ CA1868 $\rightarrow$ CA1851 $\rightarrow$ NY1850) the latest section might have a high similarity to all of its parents, but was in fact borrowed only from the most recent parent.
+This matrix required filtering based on what we knew about the process of borrowing.
+For instance, a code from 1851 obviously did not borrow from a code from 1877.
+Furthermore, in chains of borrowing (e.g., NY1850 $\rightarrow$ CA1851 $\rightarrow$ CA1868 $\rightarrow$ CA1872 $\rightarrow$ MT1895) the latest section might have a high similarity to all of its parents, but it was in fact borrowed only from the most recent parent.
 We therefore filtered the similarity matrix to remove (1) matches within the same code; (2) anachronistic matches; (3) spurious matches beneath a certain threshold.
-Then if a section had multiple matches, we kept the match from (5) the chronologically closest code from the same state unless (6) there was a substantially higher match from a different code.
-The result was a sparse matrix of the most likely matches for each section.
+Then if a section had multiple matches, we kept the match from (5) the chronologically closest code, (6) giving preference to codes from the same state, unless (7) there was a substantially higher match from a different code.
+The result was a sparse matrix of the most likely matches for each section, with at most one match for each section.
 
@@
 
-A similarity matrix is a common input to many other visualizations and algorithms. We used the matrix of best borrowings to learn how the codes were borrowed in several ways.
+A similarity matrix is a common input to many algorithms and visualizations. From that matrix, we built several means of understanding how the codes borrowed from one another.
 

### 2016-02-17 talks/dh-working-group/dh-working-group.Rmd
Revise the network section

@@
 
-We used a clustering algorithm to group similar sections together.
-There are innumerable clustering algorithms, but we needed one that could work with a sparse matrix and one whose assumptions aligned with the problem we were working on.
-We used the affinity propagation clustering algorithm.^[Brendan J.
-Frey and Delbert Dueck, "Clustering by Passing Messages Between Data Points," *Science* 315 (2007): 972--976.] That algorithm assumes that there is an "exemplar" item in each cluster.
-That assumption exactly matches the case with the Field code, where a single section (likely from NY1850) had many borrowings.
-Furthermore, even though the affinity propagation clustering algorithm did not fully converge on our peculiar dataset, it did do an adequate job of clustering the documents initially.
-Because there was an exemplar section for each cluster, we were able to merge clusters where the exemplar sections had a high Jaccard similarity score.
+We used a clustering algorithm to group related sections together.
+There are innumerable clustering algorithms, but we needed one that could work with a sparse matrix and one whose assumptions matched the characteristics of our problem.
+We decided to use affinity propagation clustering.^[Brendan J.
+Frey and Delbert Dueck, "Clustering by Passing Messages Between Data Points," *Science* 315 (2007): 972--976.] That algorithm assumes that each cluster has an "exemplar" item which the other items are similar to.
+That assumption fits nicely with borrowings from the Field Code, where a single section (likely from the 1850 New York code) had many borrowings.
+Furthermore, even though the affinity propagation clustering algorithm did not fully converge with our peculiar dataset, it did an adequate job clustering the documents.
+Because there was an exemplar section for each cluster, we were able to merge clusters whose exemplars had a high Jaccard similarity score.
 
-The result was a set of approximately 2,900 clusters which contained at least five sections.
-This probably overstates the number of ur-sections in the corpus.
-Each cluster contained a list of the section IDs that belonged to it.
-The biggest cluster, for instance, contained 103 sections, which concerned the use of affidavits in pleading.
-Scholars in digital literary studies often speak of "deformance" of texts.^[Stephen Ramsay, *Reading Machines: Toward an Algorithmic Criticism* (University of Illinois Press, 2011), ch.
-3.] Clustering the sections of the codes deformed them because it pulled the sections out of the codes from which they had been embedded in, and placed them in chronological order.
-This allowed us to see the development and spread of the law.
-You might consider this a method of distant reading which then permits a kind of close reading.
-Consider this (admittedly more important than usual) excerpt from one of the clusters which concerned the competence of witnesses:
+The result was a set of approximately 2,900 clusters which contained at least five sections, though this probably overstates the number of ur-sections in the corpus.
+Each cluster contained a list of the section that belonged to it.
+The biggest cluster, for instance, which concerned the use of affidavits in pleading, contained 103 sections.
+Scholars in digital literary studies often speak of the "deformance" of texts.^[Stephen Ramsay, *Reading Machines: Toward an Algorithmic Criticism* (University of Illinois Press, 2011), ch.
+3.] Clustering the sections of the codes deformed them by pulling the sections out of their context within specific codes and by arranging them by topic in chronological order.
+Deforming the codes allowed us to see the development and spread of the law.
+Consider this (admittedly more significant than typical) excerpt from a cluster of sections about the competence of witnesses:
 
@@
 
+Reading through those chronologically arranged sections, it became apparent how the original New York section was borrowed but adapted to include several different versions of a racial exclusion based on blood quantum.
+
 ## Networks of borrowings
 
-A matrix of similarities can be thought of as an adjacency matrix to a network graph.
-We created network graph of the code to code borrowings.
-In an effort not to make this a typical hairball, we filtered the edges so that each code was connected to another code only if it borrowed at least fifty sections.
+A matrix of similarities can also be thought of as the adjacency matrix of a network graph.
+Instead of creating a network graph of section to section borrowings (which would be practically the same thing as clustering), we moved up a level of abstraction to create a network graph of code to code borrowings.
+Because even our efforts at determining the best match for each section sometimes attributed a section to an incorrect code, we pruned the edges of the graph so that each code was connected to another code only if it borrowed at least fifty sections or twenty percent of its sections.
 
-```{r, fig.fullwidth=TRUE, fig.cap="Code to code borrowings.", fig.height=3}
+```{r, fig.fullwidth=TRUE, fig.cap="Code to code borrowings.
+The arrows indicate that a code contributed sections to another code.
+The color of the nodes indicates the number of steps to get to one of the New York codes.
+We could move up a further level of abstraction to consider state to state borrowings, which would show us the structure more clearly, albeit at a considerable loss of detail.", fig.height=3}
 set.seed(21000)
@@
   geom_edge_fan(aes(edge_width = sections_borrowed, 
-                    alpha = sections_borrowed),
+                    alpha = sections_borrowed,
+                    color = as.factor(sections_borrowed)),
                 arrow = arrow(type = "closed", ends = "first",
@@
                               angle = 15)) +
-  geom_node_point(aes(color = as.factor(distance)), size = 2) +
+  geom_node_point(alpha = 0.95, aes(color = as.factor(distance)), size = 2) +
+  geom_node_text(aes(label = name), size = 1.5, family = "serif") +
   scale_edge_width("Sections borrowed", range = c(0.25, 1), guide = "none") + 
-  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +
-  scale_color_brewer(palette = "Set1", "Distance from a NY code") +
-  ggforce::theme_no_axes(base_size = 4, base_family = "serif") +
-  geom_node_text(aes(label = name), size = 1.5) +
+  scale_edge_color_grey(start = 0.5, end = 0.6, guide = "none") +
+  scale_edge_alpha(range = c(0.98, 0.99), guide = "none") +
+  scale_color_brewer(palette = "Dark2", "Distance from a NY code") +
+  ggforce::theme_no_axes(base_size = 5, base_family = "serif") +
   theme(legend.position = "bottom", 
@@
 
-This network shows the structure of the borrowings.
-In particular, it demonstrates the centrality of New York's code, especially the eponymous Field Code of 1850.
-The New York code then became the basis of other families of codes.
-Those codes heavily edited NY1850, but within the families (which were often based on the proximity of states) the borrowings tended to be much more close.
-Yet states could and did sometimes borrow from multiple states.
-Notice that this network graph moves both geographically an chronologically.
-It is later codes which tend to be on the outside of the network diagram, and they are the most distant from the original Field Code in both time and borrowings.^[If we move up a level of abstraction we can consider not code to code but state to state borrowings.
-This shows us the pattern of borrowings more clearly, albeit at a considerable loss of detail.
-While that is a constant challenge in any kind of visualization work, it is especially a challenge here where we know that our measures of borrowings can be inaccurate for individual sections, though they are reliable on the whole.]
+This network shows the structure of borrowings within the corpus.
+This network graph expands both geographically an chronologically.
+Later codes tend to be on the outside of the diagram, and they are the most distant from the original Field Code in both time and similarity.
+The New York codes, especially the eponymous Field Code of 1850, are central to the entire network.
+The Field Code became the basis of other families of codes, which adapted it to different circumstances.
+Those families of codes tended to be regional, and the ties within the families of codes are somewhat tighter than the ties of the regional exemplar to the Field Code.
+Yet state code commissioners could and did sometimes borrow from multiple states.
 

### 2016-02-17 R/spectrogram.R
Permit controlling font size and family from spectrogram()

@@ -2,7 +2,8 @@
 # white lists at most that number of codes to be explicitly named in the viz,
 # or a character vector of codes to white list.
 spectrogram <- function(code, matches_df, num_cols = 40,
-                        white_list = NULL, title = NULL) {
+                        white_list = NULL, title = NULL,
+                        base_size = 16, base_family = "") {
   require(dplyr)
   require(stringr)
   require(ggplot2)
@@ -38,7 +39,7 @@ spectrogram <- function(code, matches_df, num_cols = 40,
   matches_df %>%
   ggplot(aes(x = column, y = -row, fill = match_code)) +
   geom_tile(color = "lightgray") +
-  theme_minimal(base_size = 16) +
+  theme_minimal(base_size = base_size, base_family = base_family) +
   coord_equal() +
   labs(x = NULL, y = NULL, title = title,
        fill = "Section borrowed from") +

### 2016-02-17 R/spectrogram.R
Control legend key size in spectrogram

@@ -3,7 +3,8 @@
 # or a character vector of codes to white list.
 spectrogram <- function(code, matches_df, num_cols = 40,
                         white_list = NULL, title = NULL,
-                        base_size = 16, base_family = "") {
+                        base_size = 16, base_family = "",
+                        legend_size = 0.5) {
   require(dplyr)
   require(stringr)
   require(ggplot2)
@@ -46,7 +47,8 @@ spectrogram <- function(code, matches_df, num_cols = 40,
   theme(legend.position = "bottom",
         axis.ticks = element_blank(),
         axis.line = element_blank(), axis.text = element_blank(),
-        panel.background = element_blank(), panel.grid = element_blank()) +
+        panel.background = element_blank(), panel.grid = element_blank(),
+        legend.key.size = unit(legend_size, "cm")) +
   scale_fill_brewer(type = "qual", na.value = "gray", palette = 6)
 
 }

### 2016-02-17 talks/dh-working-group/dh-working-group.Rmd
Complete second draft of DH working talk

@@
 \includegraphics{../aha2016/field.jpg}
-\caption{David Dudley Field II (1805--1894).}
+\caption{David Dudley Field II (1805--1894).
+Daguerreotype by Matthew Brady, circa 1844 to 1860, DAG no.
+084, Library of Congress, Prints and Photographs Division, Washington, DC: \url{http://www.loc.gov/pictures/item/2004663945/
+}.}
 \end{marginfigure}
@@
 
-This matrix required filtering based on what we knew about the process of borrowing.
-For instance, a code from 1851 obviously did not borrow from a code from 1877.
+This matrix required filtering based on what we knew about the process of borrowing.\marginnote{Read this table as \texttt{row} borrows from \texttt{column}.} For instance, a code from 1851 obviously did not borrow from a code from 1877.
 Furthermore, in chains of borrowing (e.g., NY1850 $\rightarrow$ CA1851 $\rightarrow$ CA1868 $\rightarrow$ CA1872 $\rightarrow$ MT1895) the latest section might have a high similarity to all of its parents, but it was in fact borrowed only from the most recent parent.
@@
   theme(legend.position = "bottom", 
-        panel.border = element_blank())
+        panel.border = element_blank(),
+        legend.key.size = unit(0.30, "cm"))
 ```
@@
 
-```{r, eval=FALSE, fig.fullwidth=TRUE, fig.cap="State to state borrowings.", fig.height=3}
-set.seed(210)
-ggraph(states_g, "igraph", algorithm = "graphopt") +
-  geom_edge_fan(aes(edge_width = sections_borrowed, 
-                    alpha = sections_borrowed),
-                arrow = arrow(type = "closed", ends = "first",
-                              length = unit(0.10, "inches"),
-                              angle = 15)) +
-  geom_node_point(size = 3, aes(color = region)) +
-  scale_edge_width("Sections borrowed", range = c(0.25, 1), guide = "none") + 
-  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +
-  scale_color_brewer(palette = "Dark2", "Region") +
-  ggforce::theme_no_axes(base_size = 4, base_family = "serif") +
-  geom_node_text(aes(label = name), size = 1.5) +
-  theme(legend.position = "bottom", 
-        panel.border = element_blank())
+## Borrowings within each code
+
+Finally, we created a "spectrograph" visualization in order to get a fuller picture of how each code compiled sections from other codes.
+These visualizations showed the origin of each section of a code.
+We can use these spectrographs to follow the some of the connected nodes on the network diagram.
+Take Washington's 1855 code.
+
+```{r, fig.margin=FALSE, fig.cap="Borrowed sections in Washington's 1855 code. Each section in the code is represented by a square, the color of which indicates where it was borrowed from."}
+spectrogram("WA1855", best_matches, white_list = 4, 
+            base_size = 6, base_family = "serif", legend_size = 0.3)
 ```
 
-## Borrowings within each code
-
-Finally, each of those nodes on the network diagram can be individualy investigated to get a more detailed perspective on how the codes were borrowed.
-We did this by creating a kind of "spectrograph" or fingerprint of which sections in a code were borrowed from which other codes.
-Take the case of Washington state's 1855 code.
-
-```{r, fig.cap="Borrowed sections in Washington's 1855 code. Each section in the code is represented by a square, the color of which indicates where it was borrowed from."}
-spectrogram("WA1855", best_matches, white_list = 4)
+```{r, fig.margin=TRUE, fig.cap="Borrowed sections in California's 1851 code.
+This code, which is the regional exemplar for much of the western codes, is almost entirely derived from the Field Code, with the exception of sections modified for California in its 1850 code.
+Those too were ultimately derived from New York."}
+spectrogram("CA1851", best_matches, white_list = 3, 
+            base_size = 12, base_family = "serif", legend_size = 0.3)
 ```
 
-We can observe that most of the code is borrowed from some source or another.
-While there is a fair bit of "other" which are probably sections which we cannot adequately attribute, the pattern of borrowing is clear: IN1852 and OR1854 provide the majority of the borrowings, and they do so in two bands.
-This pattern is curious, because one might expect Washington to borrow from Oregon and California but Indiana is not an obvious choice.
-And why do the borrowings fall into these bands?
-Regulations on judgment were borrowed from Oregon, while enforcement provisions came from Indiana.
-We think this is because one of the Washington code commissioners, Edward Lander, was an Indiana appelate judge from 1850 to 1853, while another commissioner, William Strong, was a justice of the Oregon Supreme Court in the same years.
-In other words, the law in this case moved with judges and lawyers who picked the parts they knew best.
+While there are a number of "other" sections, the pattern of borrowing is clear: Indiana's 1852 code and Oregon's 1854 code provide the majority of the borrowings.
+Those two bands of borrowings correspond to regulations on judgement from Oregon and enforcement provisions from Indiana.
+We think this pattern is because one of the Washington code commissioners, Edward Lander, was an Indiana appelate judge from 1850 to 1853, while another commissioner, William Strong, was a justice of the Oregon Supreme Court in the same years.
+The law was created by the commissioners, and they picked the laws that they knew best.
 
-Of course we can also demonstrate in an obvious way when codes were borrwed heavily from one source, yet we can also note the unusual places in the code where apparently later innovations from Oregon were borrowed, or where the California codes were not strictly borrowed.
+# Conclusions about method and interpretation
 
-```{r}
-spectrogram("NV1861", best_matches, white_list = 4)
+By framing our historical questions around "medium data" we enjoyed a useful symbiosis of traditional and digital historical methods.
+Our computational methods produced useful historical knowledge they were justified by what we knew about the data from traditional historical work.
+We knew that code commissioners worked with "the scissors and paste-pot,"^[*Rocky Mountain News*, January 20, 1877.] as political debates from the era frequently complained, and we knew codes in the archives that commisions literally marked up the legislation of other states.^[The Nevada code was created by marking up a printed copy of California's code.
+Detail from Council Bill 21, First Territorial Legislative Session (1861), Nevada State Library, Archives and Public Records.] Knowing that borrowings happened section by section justified our use of the minhash/LSH algorithm, and the nature of the borrowings justified our use of affinity propagration clustering.
+And knowing how codes passed from state to state made network analysis an obvious fit.^[This is an example of the "no free lunch theorem" in action.
+See David Robinson, "K-means clustering is not a free lunch," *Variance Explained*, January 16, 2015: <http://varianceexplained.org/r/kmeans-free-lunch/>, citing David H.
+Wolpert and William G.
+Macready, "No Free Lunch Theorems for Optimization" *IEEE Transactions on Evolutionary Computation* 1, no.
+1 (April 1997): 67--82, <http://ti.arc.nasa.gov/m/profile/dhw/papers/78.pdf>.]
 
-spectrogram("NM1865", best_matches, white_list = 8)
-```
+Our method is applicable to many historical questions and sources, especially corpora where the documents can be readily divided into sections.
+We may pursue it with other legal documents, such as treatises or statutes, or with sources for religious history, such as hymnbooks or tracts.
 
-# Conclusions
-
-There are two sets of conclusions, or at least observations, which can be drawn from this work in progress.
-
-We think that the methodology of this kind of work has a number of applications to historical problems.
-First, question framing.
-One very useful thing to do when framing a digital historical problem is to begin with exploratory data analysis of a large corpus---to let the sources drive the questions.
-We have modeled an approach that is at the opposite side of the interpretative spiral, by forming a corpus to answer an already formed historical question.
-The use of *medium data* permits us a close relationship between traditional and digital historical methods, which is our second point.
-Our methods produced useful historical knowledge because the digital methods were closely connected to assumptions we knew to be true about the data from our traditional historical work.
-To give a brief list of those harmonies: we knew that code commissioners worked with "the scissors and paste-pot," as political debates about the codes frequently complained, and we knew from examining codes in thea archives that commisions literally marked up the legislation of other states.^[*Rocky Mountain News*, January 20, 1877.] That knowledge, particularly the knowledge that the borrowings happened at the level of the section, justified our use of the minhash/LSH algorithm.
-Our knowledge that particular sections were frequently borrowed and thus were exemplars justified our use of the affinity propagration algorithm.
-And our assumptions about how codes were passed from state to state made network analysis an obvious fit.^[We might call these an example of the "no free lunch theorem" in action.
-See David Robinson, "K-means clustering is not a free lunch," *Variance Explained*, January 16, 2015: <http://varianceexplained.org/r/kmeans-free-lunch/>.] And third, we think that this method is widely applicable to different historical questions and sources, almost without modification in the case of corpora where the documents can be readily divided into sections.
-This method could be pursued in other legal documents such as treatises or statutes; it could also be pursued in sources of other domains, such as hymnbooks or tracts.
-
-Finally, the article that we are writing about the Field code will bring together what we have learned through traditional historical work and the digital methods described above.
-But we can sum up what we have learned primarily from the digital methods.
-This study is significant because it gets at the heart of lawmaking in U.S.
+We are writing an article with a fuller statement of our historical interpretations, but to sum up what we learned from the computational methods: This study is significant because it gets at the heart of lawmaking in U.S.
 history.
@@
 Furthermore, these borrowings called into question the extent to which the United States was actually a federal system of laws.
-We have documented the scope and content of the exact borrowings.
-We have shown the dominance of New York's laws in a supposedly federal system, and shown exactly the extent to which code commissioners borrowed from that code and its descendants.
-Economic centers, which needed certain kinds of laws tied up with the expansion of markets and American capitalism, were in fact legal centers.
-But we have also demonstrated that regional distinctions were also significant, so that regional economic centers like California and Ohio generated separate Western and Midwestern families of codes.
-Finally we have shown how haphazard the process of codification could be, as in the case of the Washington code cited above where judges from jurisdictions borrowed laws that they were familiar with, and in the case of New Mexico, which borrowed Missouri's laws because those were the law books which were actually available.
-
-The specific provisions of the Field code aren't in continued use in every jurisdiction, (though in states like Missouri the Field Code provisions survive virtually unchanged) but the basic ideas embedded in the Field Code are standard practice which have spread throughout the entire country.
-Without too much exaggeration we might say that our method has revealed the spine of modern American legal practice.
+We have shown the dominance of New York's laws in a supposedly federal system, and demonstrated the extent to which code commissioners borrowed from the Field Code and its descendants.
+Despite the notion that states were equal and soverign, economic centers were in fact legal centers.
+But we have also demonstrated that regional distinctions were also significant, with states like California and Ohio creating separate Western and Midwestern families of codes.
+Finally we have shown how haphazard the process of codification could be, as in the case of the 1855 Washington code cited above, or in the case of New Mexico, which borrowed Missouri's laws because those were the law books available to the commissioners.
+In most jurisdictions the exact language of the Field Code is not currently on the books, but its basic provisions for civil procedure are in force throughout the United States.^[But in some states such as Missouri the Field Code provisions survive nearly unchanged.] Without too much exaggeration we might say that our method has revealed the spine of modern American legal practice.

### 2016-02-17 R/spectrogram.R
Make spectrograph's transparent based on score

@@ -38,7 +38,7 @@ spectrogram <- function(code, matches_df, num_cols = 40,
 
   # Make the plot
   matches_df %>%
-  ggplot(aes(x = column, y = -row, fill = match_code)) +
+  ggplot(aes(x = column, y = -row, fill = match_code, alpha = score)) +
   geom_tile(color = "lightgray") +
   theme_minimal(base_size = base_size, base_family = base_family) +
   coord_equal() +
@@ -49,7 +49,8 @@ spectrogram <- function(code, matches_df, num_cols = 40,
         axis.line = element_blank(), axis.text = element_blank(),
         panel.background = element_blank(), panel.grid = element_blank(),
         legend.key.size = unit(legend_size, "cm")) +
-  scale_fill_brewer(type = "qual", na.value = "gray", palette = 6)
+  scale_fill_brewer(type = "qual", na.value = "lightgray", palette = 6) +
+  scale_alpha(range = c(0.6, 1), guide = FALSE)
 
 }
 

### 2016-02-17 talks/dh-working-group/dh-working-group.Rmd
Corrections from Kellen and Abby and additional citations

@@
 Factions for and against codification debated about whether codes were laws passed by democratic legislatures or anti-democratic legal elites, whether codification served only the needs of wealthy capitalists, and whether the purity of Anglo-Saxon civilization derived from the common law would be maintained.
-The economic capital New York was the first state to codify its procedure in 1848, thanks to the efforts of David Dudly Field.
+The economic capital New York was the first state to codify its procedure in 1848, thanks to the efforts of David Dudley Field.
 By the end of the century, New York's Field Code became the model for the codes of civil procedure in most states.
@@
 
-Legal historians have long known that the Field code spread to other jurisdictions.
+Legal historians have long known that the Field Code spread to other jurisdictions.
 Beyond the mere fact of its adoption, however, no one has studied the content of the borrowings.
 Which codes borrowed from each other?
-Which sections were borrowed, and howe were they modified?
+Which sections were borrowed, and how were they modified?
 What were the patterns and structures of borrowings and of innovations?
@@
 We found out how the codes borrowed from one another by splitting the codes into sections and comparing each section to every other section.^[The data and code to re-run our analyses are available in a GitHub repository: <https://github.com/lmullen/civil-procedure-codes>.
-We generalized our method in Lincoln Mullen, "textreuse: Detect Text Reuse and Document Similarity," R package version 0.1.2 (2015): <https://github.com/ropensci/textreuse>, which was peer-reviewed by rOpenSci.] This process in essence mimicked the way that nineteenth-century code commissioners literally cut and pasted sections from other jurisidictions.
+We generalized our method in Lincoln Mullen, "textreuse: Detect Text Reuse and Document Similarity," R package version 0.1.2 (2015): <https://github.com/ropensci/textreuse>, which was peer-reviewed by rOpenSci.
+We benefitted a great deal from  David A.
+Smith, Ryan Cordell, and Elizabeth Maddock Dillon, "Infectious Texts: Modeling Text Reuse in Nineteenth-Century Newspapers," in *2013 IEEE International Conference on Big Data*, 2013, 86–94, doi:10.1109/BigData.2013.6691675; David A.
+Smith et al., "Detecting and Modeling Local Text Reuse," in *Proceedings of the 14th ACM/IEEE-CS Joint Conference on Digital Libraries* (IEEE Press, 2014), 183–92, <http://dl.acm.org/citation.cfm?id=2740800>.] This process in essence mimicked the way that nineteenth-century code commissioners literally cut and pasted sections from other jurisidictions.
 
@@
 
-Having identified all of the relevant laws of civil procedure in the nineteenth-century, including codes, session laws, and statutes, we used OCR software to create plain-text versions of the codes.
+Having identified all of the relevant laws of civil procedure in the nineteenth century, including codes, session laws, and statutory compilations, we used OCR software to create plain-text versions of the codes.
 These OCR files received only a light cleaning: we edited the section markers by hand as necessary, and wrote a script to fix the most obvious OCR errors.
 
-We then split each section of each code into its own text file.
-The corpus contains nearly 98,000 sections.
+We then split each section of each code into its own text file.^[While all statutes are divided into chapters, articles, and titles, specific regulations appear within these as sequentially numbered sections.] The corpus contains nearly 98,000 sections.
 Below is a sample file containing a single section from a single code.^[1851 California Laws 74, §151.
@@
 That measure, treating the tokens as a set, is the ratio of shared tokens to the ratio of total tokens in two documents.
-That ration can range from 0 (complete dissimilarity) to 1 (complete similarity).^[Jure Leskovec, Anand Rajaraman, and Jeff Ullman, *Mining of Massive Datasets*, 2nd ed.
+That ratio can range from 0 (complete dissimilarity) to 1 (complete similarity).^[Jure Leskovec, Anand Rajaraman, and Jeff Ullman, *Mining of Massive Datasets*, 2nd ed.
 (Cambridge University Press, 2014), ch.
@@
 
-This matrix required filtering based on what we knew about the process of borrowing.\marginnote{Read this table as \texttt{row} borrows from \texttt{column}.} For instance, a code from 1851 obviously did not borrow from a code from 1877.
+This matrix required filtering based on what we knew about the process of borrowing.\marginnote{Read this table as \texttt{row} borrows from \texttt{column}, e.g., \texttt{CA1851-004380} borrows from \texttt{NY1850-018680}.} For instance, a code from 1851 obviously did not borrow from a code from 1877.
 Furthermore, in chains of borrowing (e.g., NY1850 $\rightarrow$ CA1851 $\rightarrow$ CA1868 $\rightarrow$ CA1872 $\rightarrow$ MT1895) the latest section might have a high similarity to all of its parents, but it was in fact borrowed only from the most recent parent.
-We therefore filtered the similarity matrix to remove (1) matches within the same code; (2) anachronistic matches; (3) spurious matches beneath a certain threshold.
-Then if a section had multiple matches, we kept the match from (5) the chronologically closest code, (6) giving preference to codes from the same state, unless (7) there was a substantially higher match from a different code.
+We therefore filtered the similarity matrix to remove matches within the same code; anachronistic matches; spurious matches beneath a certain threshold.
+Then if a section had multiple matches, we kept the match from the chronologically closest code, giving preference to codes from the same state, unless there was a substantially higher match from a different code.
 The result was a sparse matrix of the most likely matches for each section, with at most one match for each section.
@@
 Deforming the codes allowed us to see the development and spread of the law.
-Consider this (admittedly more significant than typical) excerpt from a cluster of sections about the competence of witnesses:
+Consider this excerpt from a cluster of sections about the competence of witnesses:
 
@@
 By framing our historical questions around "medium data" we enjoyed a useful symbiosis of traditional and digital historical methods.
-Our computational methods produced useful historical knowledge they were justified by what we knew about the data from traditional historical work.
-We knew that code commissioners worked with "the scissors and paste-pot,"^[*Rocky Mountain News*, January 20, 1877.] as political debates from the era frequently complained, and we knew codes in the archives that commisions literally marked up the legislation of other states.^[The Nevada code was created by marking up a printed copy of California's code.
+Our computational methods produced useful historical knowledge because they were justified by what we knew about the data from traditional historical work.
+We knew that code commissioners worked with "the scissors and paste-pot,"^[*Rocky Mountain News*, January 20, 1877.] as political debates from the era frequently complained, and we knew of codes in the archives that commisions literally marked up the legislation of other states.^[The Nevada code was created by marking up a printed copy of California's code.
 Detail from Council Bill 21, First Territorial Legislative Session (1861), Nevada State Library, Archives and Public Records.] Knowing that borrowings happened section by section justified our use of the minhash/LSH algorithm, and the nature of the borrowings justified our use of affinity propagration clustering.
@@
 We have shown the dominance of New York's laws in a supposedly federal system, and demonstrated the extent to which code commissioners borrowed from the Field Code and its descendants.
-Despite the notion that states were equal and soverign, economic centers were in fact legal centers.
+Despite the notion that states were equal and sovereign, economic centers were in fact legal centers.
 But we have also demonstrated that regional distinctions were also significant, with states like California and Ohio creating separate Western and Midwestern families of codes.

### 2016-02-17 talks/dh-working-group/dh-working-group.Rmd
Back to eight pages

@@
 Macready, "No Free Lunch Theorems for Optimization" *IEEE Transactions on Evolutionary Computation* 1, no.
-1 (April 1997): 67--82, <http://ti.arc.nasa.gov/m/profile/dhw/papers/78.pdf>.]
-
-Our method is applicable to many historical questions and sources, especially corpora where the documents can be readily divided into sections.
+1 (April 1997): 67--82, <http://ti.arc.nasa.gov/m/profile/dhw/papers/78.pdf>.]  Our method is applicable to many historical questions and sources, especially corpora where the documents can be readily divided into sections.
 We may pursue it with other legal documents, such as treatises or statutes, or with sources for religious history, such as hymnbooks or tracts.

### 2016-02-17 talks/dh-working-group/dh-working-group.Rmd
No date; better citation

@@
 output: tufte::tufte_handout
-date: "February 17, 2016"
 ---
@@
 \begin{abstract}
-This handout describes our work in progress for the Digital Humanities Working Group at George Mason University.\\
+This paper describes our work in progress for the Digital Humanities Working Group at George Mason University on February 17, 2016.\\
 E-mail: \url{lincoln@lincolnmullen.com}, \url{kfunk@princeton.edu}
@@
 We benefitted a great deal from  David A.
-Smith, Ryan Cordell, and Elizabeth Maddock Dillon, "Infectious Texts: Modeling Text Reuse in Nineteenth-Century Newspapers," in *2013 IEEE International Conference on Big Data*, 2013, 86–94, doi:10.1109/BigData.2013.6691675; David A.
-Smith et al., "Detecting and Modeling Local Text Reuse," in *Proceedings of the 14th ACM/IEEE-CS Joint Conference on Digital Libraries* (IEEE Press, 2014), 183–92, <http://dl.acm.org/citation.cfm?id=2740800>.] This process in essence mimicked the way that nineteenth-century code commissioners literally cut and pasted sections from other jurisidictions.
+Smith, Ryan Cordell, and Elizabeth Maddock Dillon, "Infectious Texts: Modeling Text Reuse in Nineteenth-Century Newspapers," in *2013 IEEE International Conference on Big Data*, 2013, 86–94, doi:10.1109/BigData.2013.6691675, and the other publications of the Viral Texts team.] This process in essence mimicked the way that nineteenth-century code commissioners literally cut and pasted sections from other jurisidictions.
 

### 2016-02-17 index.Rmd
Link to slides
Add working group to the index
Updated slides for DH working group

@@
 ```
+
+You may also be interested in the materials for various talks we have given about this project.
+
+- [AHA 2016 lightening talk slides](talks/aha2016/aha2016.html)
+- Digital Humanities Working Group, George Mason University: [paper](talks/dh-working-group/dh-working-group.pdf), [slides](talks/dh-working-group-slides/dh-working-group-slides.html)

### 2016-02-17 talks/dh-working-group-slides/dh-working-group-slides.Rmd
Updated slides for DH working group

--- 2016-02-06 talks/aha2016/aha2016.Rmd
@@
 ---
-title: "Tracking the Migration of the Field Code"
+title: "The Migration of the Field Code"
 author: "Lincoln Mullen and Kellen Funk"
@@
 
+## {data-background="code-to-code2.png"}
+
+## {data-background="state-to-state2.png"}
+
 ## {data-background="WA1855.png"}
+
+## {data-background="CA1851.png"}
 
@@
 
-## {data-background="code-to-code.png"}
-
-## {data-background="state-to-state.png"}
+## {data-background="NY1879.png"}

### 2016-02-19 index.Rmd
Update project hub

@@
 ---
-title: "Analysis of Text Reuse in the Field Code"
-author: "Lincoln Mullen and Kellen Funk"
+title: "The Migration of the Field Code"
+author: "Kellen Funk and Lincoln Mullen"
 ---
 
-This is an analysis notebook for detecting text reuse in codes of civil procedure---the "Field codes"---in the nineteenth-century United States.
+This is an analysis notebook for detecting text reuse in legal codes of civil procedure---the "Field codes"---in the nineteenth-century United States.
 It is a collaboration between [Kellen Funk](http://kellenfunk.org/) and [Lincoln Mullen](http://lincolnmullen.com).
+This [working paper](talks/dh-working-group/dh-working-group.pdf) has the most up-to-date summary of what we are doing.
 
@@
 - [Detecting Text Reuse in Nineteenth-Century Legal Documents](http://lincolnmullen.com/blog/detecting-text-reuse-in-legal-documents/)
+
+You may also be interested in the materials for various talks we have given about this project.
+
+- [AHA 2016 lightening talk slides](talks/aha2016/aha2016.html)
+- Digital Humanities Working Group, George Mason University: [paper](talks/dh-working-group/dh-working-group.pdf), [slides](talks/dh-working-group-slides/dh-working-group-slides.html)
 
@@
 ```
-
-You may also be interested in the materials for various talks we have given about this project.
-
-- [AHA 2016 lightening talk slides](talks/aha2016/aha2016.html)
-- Digital Humanities Working Group, George Mason University: [paper](talks/dh-working-group/dh-working-group.pdf), [slides](talks/dh-working-group-slides/dh-working-group-slides.html)

### 2016-02-19 index.Rmd
Rename working paper

@@
 It is a collaboration between [Kellen Funk](http://kellenfunk.org/) and [Lincoln Mullen](http://lincolnmullen.com).
-This [working paper](talks/dh-working-group/dh-working-group.pdf) has the most up-to-date summary of what we are doing.
+This [working paper](talks/dh-working-group/Funk-Mullen.Migration-Field-Code.working-paper.pdf) has the most up-to-date summary of what we are doing.
 
@@
 - [AHA 2016 lightening talk slides](talks/aha2016/aha2016.html)
-- Digital Humanities Working Group, George Mason University: [paper](talks/dh-working-group/dh-working-group.pdf), [slides](talks/dh-working-group-slides/dh-working-group-slides.html)
+- Digital Humanities Working Group, George Mason University: [paper](talks/dh-working-group/Funk-Mullen.Migration-Field-Code.working-paper.pdf), [slides](talks/dh-working-group-slides/dh-working-group-slides.html)
 

### 2016-02-19 article/article.Rmd
Placeholder for template draft

---
title: 'The “Paste-Pot” Field Code: The Migration of Law in the Nineteenth-Century
  United States'
author: "Kellen Funk and Lincoln Mullen"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### 2016-02-19 article.Rmd
Move article template

---
title: 'The “Paste-Pot” Field Code: The Migration of Law in the Nineteenth-Century
  United States'
author: "Kellen Funk and Lincoln Mullen"
output: pdf_document
---

```{r setup, include=FALSE}
library(textreuse)
library(dplyr)
library(readr)
library(ggplot2)
library(ggraph)
knitr::opts_chunk$set(echo = FALSE)
# load("cache/corpus-lsh.rda")
# load("cache/network-graphs.rda")
# clusters <- read_csv("out/clusters/clusters.csv")
```

### 2016-02-19 index.Rmd
Move article template

@@
 rmd <- Sys.glob("*.Rmd")
-rmd <- rmd[rmd != "index.Rmd"]
+rmd <- rmd[!rmd %in% c("index.Rmd", "article.Rmd")]
 html <- sub(".Rmd", ".html", rmd)

### 2016-02-19 105-most-borrowed-sections.Rmd
Most borrowed sections attempt

---
title: "Most Borrowed Sections"
author: "Kellen Funk and Lincoln Mullen"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Which sections of the Field Code were most borrowed? By borrowed we mean both directly and also several generations down the tree.

```{r, message=FALSE}
library(dplyr)
load("cache/corpus-lsh.rda")
source("R/helper.R")
source("R/spectrogram.R")
```

This is a hacky way of solving it. (The hackiness mostly comes from bending things to fit the spectrogram function.)
```{r}
borrowed_from <- function(code, matches_df = all_matches, threshold = 0.2) {
  require(dplyr)
  matches_df %>% 
    filter(match_code == code,
           borrower_year > extract_date(code),
           score >= threshold)
}

most_borrowed <- function(matches_df, matching_code, weighted = FALSE) {
  if (weighted) {
    matches_df <- matches_df %>% 
      group_by(match_section) %>% 
      summarize(score = sum(score, na.rm = TRUE)) %>% 
      mutate(match_code = "All codes",
             score = scales::rescale(score, from = c(0, max(score, na.rm = TRUE)))) %>% 
      rename(borrower_section = match_section)
  } else {
    matches_df <- matches_df %>% 
      group_by(match_section) %>% 
      summarize(n = n()) %>% 
      mutate(match_code = "All codes",
             score = scales::rescale(n, from = c(0, max(n, na.rm = TRUE)))) %>% 
      rename(borrower_section = match_section)
  }

  all_sections <- best_matches %>% 
    filter(borrower_code == matching_code) %>% 
    select(borrower_section)

  all_sections %>% 
    left_join(matches_df, by = "borrower_section") %>% 
    mutate(borrower_code = matching_code)

}

borrowings_spectrogram <- function(code) {
  spectrogram(code, most_borrowed(borrowed_from(code), code, weighted = FALSE))
}
```

Most of New York 1850 is borrowed, but not the title sections as you would expect.

```{r}
borrowings_spectrogram("NY1850")
```

Some other codes:

```{r}
borrowings_spectrogram("NY1829")
borrowings_spectrogram("NY1848")
borrowings_spectrogram("MA1836")
borrowings_spectrogram("MD1855")
borrowings_spectrogram("CA1851")

```

### 2016-02-19 article.Rmd
Outline first half of article

@@
 knitr::opts_chunk$set(echo = FALSE)
-# load("cache/corpus-lsh.rda")
-# load("cache/network-graphs.rda")
-# clusters <- read_csv("out/clusters/clusters.csv")
+load("cache/corpus-lsh.rda")
+load("cache/network-graphs.rda")
+clusters <- read_csv("out/clusters/clusters.csv")
 ```
+
+# Introduction: "The scissors and the paste-pot"
+
+## Nevada's borrowings
+
+Vignette showing how Nevada borrowed from California.
+
+![The session bill for Nevada’s procedure acts consisted of actual pages from Wood’s Digest of California Law, 1857 edition.
+The sections have been renumbered by hand and references to California replaced with Nevada.
+Detail from Council Bill 21, First Territorial Legislative Session (1861), Nevada State Library, Archives and Public Records.](img/morris-bill.jpg)
+
+Nevada's code shows the pattern of borrowings, and also the pressures that led to those kinds of borrowings: statehood, economy.
+
+## Nevada to California to New York
+
+Nevada's code was borrowed from California, but California was borrowed from New York.
+
+Brief discussion of the stakes of these kinds of borrowings.
+
+Historians have long known that the borrowings dependent on New York happened.
+
+![Map of first instance of Field Codes.](img/field-code-states-map.jpeg)
+
+# The Problem Stated
+
+Merely noticing the borrowings does not do justice to the migration of the Field Code. We have to ask questions about what was borrowed, by whom, and how it was modified.
+
+Questions such as these make us reconsider the ways that we look at the Field Code.
+Since critical legal history [?] scholars have focused on the reception of the code.
+The presumed narrative is that "conservative" judges stood in the way of implementing the Field Code reforms.
+This question misses the antecedent question of the coherence of the Field Code.
+On the one hand, the Field Code itself sometimes spoke at cross purposes.
+But we can further generalize to talk about "the Field Code" in terms of not just a single printed document from New York, though even New York revised its code year after year, but all the borrowings in the aggregate, and the pattern that they form.
+
+So we need to ask about the patterns of borrowings, the structure latent within them.
+We have already discussed the Nevada to California to New York connection.
+What were the family trees of the codes, and what kinds of borrowings were there within the different places?
+What reforms did states make?
+How did they innovate?
+
+These questions are fundamental to nineteenth century legal history and indeed, to U.S.
+history more generally.
+We want to demonstrate that the U.S., so far from being a place characterized by federalism, was a place where the fundamental laws of each state tended to be drawn from a single place, New York, because of its commercial power.
+OTHER BIG POINTS
+
+# How we did our work.
+
+We have to explain how we did our work first to lend credibility to the claims below, and also to make it clear exactly what the evidentiary basis of the visualizations is.
+
+Our methods work because we were reverse engineering the paste pot.
+Our methodological contributions are these: (1) starting with a problem rather than a source base.
+(2) Applying methods which have been used in computer science or literary history to legal history.
+(3) Being explicit about the process of working in different scales.
+(4) Deforming the text.
+
+Gathering a corpus and OCRing it
+
+Minhash/LSH.
+
+Finding the best borrowings.
+
+Learning from the code: clusters, networks, spectrographs, most frequent borrowings from New York.
+
+Having described our methods, now we are going to walk you through the process that we used to generate historical knowledge from our computations.

### 2016-03-11 talks/dh-working-group/Funk-Mullen.Migration-Field-Code.working-paper.Rmd
Fix typo

--- 2016-02-17 talks/dh-working-group/dh-working-group.Rmd
@@
 Our computational methods produced useful historical knowledge because they were justified by what we knew about the data from traditional historical work.
-We knew that code commissioners worked with "the scissors and paste-pot,"^[*Rocky Mountain News*, January 20, 1877.] as political debates from the era frequently complained, and we knew of codes in the archives that commisions literally marked up the legislation of other states.^[The Nevada code was created by marking up a printed copy of California's code.
-Detail from Council Bill 21, First Territorial Legislative Session (1861), Nevada State Library, Archives and Public Records.] Knowing that borrowings happened section by section justified our use of the minhash/LSH algorithm, and the nature of the borrowings justified our use of affinity propagration clustering.
+We knew that code commissioners worked with "the scissors and paste-pot,"^[*Rocky Mountain News*, January 20, 1877.] as political debates from the era frequently complained, and we knew of codes in the archives that commissions literally marked up the legislation of other states.^[The Nevada code was created by marking up a printed copy of California's code.
+Detail from Council Bill 21, First Territorial Legislative Session (1861), Nevada State Library, Archives and Public Records.] Knowing that borrowings happened section by section justified our use of the minhash/LSH algorithm, and the nature of the borrowings justified our use of affinity propagation clustering.
 And knowing how codes passed from state to state made network analysis an obvious fit.^[This is an example of the "no free lunch theorem" in action.

### 2016-03-11 scripts/best_matches_for_tyrus.R
Write out matches for Tyrus's clustering algorithm

@@ -1,0 +1,33 @@
+library(dplyr)
+library(r)
+load("cache/corpus-lsh.rda")
+
+all_sections <- data_frame(
+  section_id = c(best_matches$borrower_section, best_matches$match_section) %>%
+    unique() %>%
+    sort(),
+  index = 1:length(section_id)
+)
+
+best_matches_with_index <- best_matches %>%
+  select(1:3) %>%
+  filter(!is.na(match_section)) %>%
+  left_join(all_sections, by = c("borrower_section" = "section_id")) %>%
+  left_join(all_sections, by = c("match_section" = "section_id"))
+
+write_csv(best_matches_with_index, "~/Dropbox/DocumentCluster/best-section-scores.csv")
+
+all_sections2 <- data_frame(
+  section_id = c(all_matches$borrower_section, all_matches$match_section) %>%
+    unique() %>%
+    sort(),
+  index = 1:length(section_id)
+)
+
+all_matches_with_index <- all_matches %>%
+  select(1:3) %>%
+  filter(!is.na(match_section)) %>%
+  left_join(all_sections2, by = c("borrower_section" = "section_id")) %>%
+  left_join(all_sections2, by = c("match_section" = "section_id"))
+
+write_csv(all_matches_with_index, "~/Dropbox/DocumentCluster/all-section-scores.csv")

### 2016-03-15 106-innovative-sections.Rmd
Find innovative sections

---
title: "Innovations in codes"
author: "Lincoln Mullen"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The aim of this document is to figure out which sections were innovative (or at least, not borrowed) in a code.

```{r}
library(textreuse)
library(purrr)
library(dplyr)
library(readr)
load("cache/corpus-lsh.rda")
source("R/helper.R")
```

Function to get the non-matching sections.

```{r}
innovative_sections <- function(code_id, matches_df = best_matches) {
  require(dplyr)
  matches_df %>% 
    filter(borrower_code == code_id,
           is.na(match_section))
}
```

Test on a single code.

```{r}
innovative_sections("CA1851")
```

Functions to write the innovative sections to disk.

```{r}
write_sections <- function(sections_df, corpus = sections, filename = NULL) {
  require(stringr)
  if (nrow(sections_df) == 0) return(NA)
  corpus <- corpus[sections_df$borrower_section]

  texts <- lapply(corpus$documents, content) %>% 
    vapply(str_wrap, character(1))

  num_sections <- length(texts)
  code_name <- texts %>% names %>% extract_code_names() %>% unique %>% `[`(1)

  separator <- "------------------------------------------------------------\n"

  output_header <- str_c("Innovative sections (i.e., sections without best matches)\n",
                         "Code name: ", code_name, "\n",
                         "Number of sections: ", num_sections, "\n\n"
                         )

  output <- map2(names(texts), texts, function(name, text) {
    str_c("\n", separator, "\n\n",
          "Section ID: ", name, "\n\n",
          text, "\n\n")
  })

  output <- str_c(output, collapse = "")
  output <- str_c(output_header, output, collapse = "")

  if (is.null(filename)) filename <- str_c("innovations/", code_name, ".txt")

  message("Writing ", filename)
  writeLines(output, filename)

}
```

Write all the innovative sections to disk:

```{r}
unlink("innovations", recursive = TRUE)
dir.create("innovations", showWarnings = FALSE)
all_codes <- best_matches$borrower_code %>% unique %>% sort
all_codes %>% map(innovative_sections) %>% walk(write_sections)
```

### 2016-03-15 talks/dh-working-group/Funk-Mullen.Migration-Field-Code.working-paper.Rmd
Typo

@@
 Those two bands of borrowings correspond to regulations on judgement from Oregon and enforcement provisions from Indiana.
-We think this pattern is because one of the Washington code commissioners, Edward Lander, was an Indiana appelate judge from 1850 to 1853, while another commissioner, William Strong, was a justice of the Oregon Supreme Court in the same years.
+We think this pattern is because one of the Washington code commissioners, Edward Lander, was an Indiana appellate judge from 1850 to 1853, while another commissioner, William Strong, was a justice of the Oregon Supreme Court in the same years.
 The law was created by the commissioners, and they picked the laws that they knew best.

### 2016-03-16 107-test-values-of-n-k.Rmd
Test which values of n and k are best for tokenizing

---
title: "Testing values of n-grams and similarity scores"
author: "Lincoln Mullen"
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
load("cache/corpus-lsh.rda")
library(dplyr)
library(textreuse)
library(ggplot2)
library(ggrepel)
library(tidyr)
```

We are using n-grams as the tokens for detecting document similarity. We want to know for n-grams or skip n-grams, which values of `n` and `k` are optimal. To test these we are going to use four sections from the codes of civil procedure. They all have the same legal effect of abolishing the distinction between law and equity and creating the form of civil action. But they do with this with more or less linguistic similarity to the original New York provision. WA1855 has the same structure but nearly completely changes the wording. CA1851 has only the second half of the provision. FL1870 borrows the provision mostly unchanged. And as a kind of a control, we will include a random section from TX1855 with no connection to the original provision.

The text of the sections.

```{r}
NY <- sections[["NY1850-006060"]] %>% content()
NY
WA <- sections[["WA1855-000020"]] %>% content()
WA
CA <- sections[["CA1851-000030"]] %>% content()
CA
FL <- sections[["FL1870-000600"]] %>% content()
FL
control <- sections[["TX1855-005820"]] %>% content()
control
```

Now a comparison of the similarity among the sections using 5-grams.

```{r}
id <- c("NY1850-006060", "WA1855-000020", "CA1851-000030", "FL1870-000600",
        "TX1855-005820")
sections_subset <- sections[id]
m <- pairwise_compare(sections_subset, jaccard_similarity) %>% round(2)
m[-5 , -1]
```

Just to be sure, verify that tokenizing with skip n-grams for a value of `k = 0` is the same thing as tokenizing with just n-grams.

```{r}
all(tokenize_ngrams(WA, n = 5) ==  tokenize_skip_ngrams(WA, n = 5, k = 0))
```

A function to calculate the Jaccard similarity for arbitrary values of `n` and `k`.

```{r}
similarity <- function(x, y, n, k) {
  jaccard_similarity(tokenize_skip_ngrams(x, n = n, k = k),
                     tokenize_skip_ngrams(y, n = n, k = k))
}
similarity_safe <- failwith(NA_real_, f = similarity, quiet = TRUE)
```

The current similarity scores we are working with for `n = 5`, `k = 0`.

```{r}
current_values <- data_frame(
  cf = c("WA", "CA", "FL", "control"),
  current = c(
    similarity(WA, NY, n = 5, k = 0),
    similarity(CA, NY, n = 5, k = 0),
    similarity(FL, NY, n = 5, k = 0),
    similarity(control, NY, n = 5, k = 0)
  )
)
```

Calculate the similarity scores for all combinations of `n` and `k`.

```{r}
comparisons <-  expand.grid(n = 2:8, k = 0:4,
                                   cf = c("WA", "CA", "FL", "control"),
                                   stringsAsFactors = FALSE) %>% 
  rowwise() %>% 
  mutate(score = similarity_safe(NY, get(cf), n = n, k = k)) %>% 
  left_join(current_values) %>% 
  mutate(ratio = score / current,
         score = round(score, 3),
         current = round(current, 3),
         ratio = round(ratio, 3),
         cf = factor(cf, levels = c("WA", "CA", "FL", "control"))) %>% 
  ungroup()
```

Make a plot of the similarity scores. (Note that the y-axes vary.)

```{r}
ggplot(comparisons, aes(x = n, y = score, color = as.factor(k))) +
  geom_line() +
  facet_grid(cf ~ k, labeller = label_both, scales = "free_y") +
  theme_bw() +
  guides(color = FALSE) +
  ggtitle("Similarity scores for values of n and k")
```

This is basically what we would expect. Increasing values of `n` and increasing values of `k` both decrease the Jaccard score. It is not simply the case that a high Jaccard similarity score is a good thing, because that creates more false positives. We can rule out any value of `n` or `k` which creates a similarity score for the control which is appreciably above 0. So we can immediately rule out values of `n` that are less than 3 when `k` is 0. The question is which values of `n` and `k` create the highest value for the WA section that is better than the current Jaccard similarity score (approx. 0.01) without creating more false positives.

To put that logic into a table, these are the mostly likely to be useful settings of `n` and `k`. First the most useful settings optimizing for the highest values for WA.

```{r}
valid_params <- comparisons %>% 
  select(-current, -ratio) %>% 
  spread(cf, score) %>% 
  filter(control < 0.02,
         WA > 0.01) 
valid_params %>% 
  arrange(desc(WA))
```

Now optimizing for the highest ratio between WA and the control.

```{r}
valid_params %>% 
  mutate(ratio_WA_to_control = WA / control) %>% 
  arrange(desc(ratio_WA_to_control), desc(WA))
```

We can try to plot that relationship between the control and WA for different values of `n` and `k`.

```{r}
comparisons %>% 
  select(-current, -ratio) %>% 
  spread(cf, score) %>% 
  filter(WA > 0.01) %>% 
  ggplot(aes(x = control, label = paste0("n:", n, ",k:", k))) +
  geom_point(aes(y = WA, color = "WA")) +
  geom_point(aes(y = CA, color = "CA")) +
  geom_text_repel(aes(y = WA)) +
  geom_text_repel(aes(y = CA)) +
  labs(title = "Similarity scores for control vs WA and CA for values of n and k",
       x = "Similarity score for control",
       y = "Similarity score for matching section")
```

It would seem like there are several choices that can increase the similarity score of Washington. The safest choice is `n = 3, k = 0`. The riskiest choice is probably `n = 2, k = 0`, though `n = 2, k = 3` might also work. We can discard the option of `n = 2, k = 3` since that will create many more tokens than `n = 2, k = 0` (about 4 times as many) for not much gain. We might be best off using tri-grams.

### 2016-03-20 108-mapping.Rmd
Proof of concept for the map

---
title: "Maps"
author: "Lincoln Mullen"
date: "March 19, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Make

```{r}
library(dplyr)
library(stringr)
library(textreuse)
library(readr)
load("cache/corpus-lsh.rda")
source("R/helper.R")
```

```{r}
ny_codes <- c("NY1848", "NY1849", "NY1850", "NY1851", "NY1853")
map_matches <- all_matches %>% 
  filter(xor(borrower_code %in% ny_codes, match_code %in% ny_codes))

map_matches_ny_borrower <- map_matches %>% 
  filter(borrower_code %in% ny_codes) %>% 
  select(-borrower_state) %>% 
  mutate(match_section2 = borrower_section,
         borrower_section2 = match_section) %>% 
  select(-match_section, -borrower_section) %>% 
  rename(borrower_section = borrower_section2, match_section = match_section2) %>%
  select(borrower_section, match_section, score)

map_matches_not_ny <- map_matches %>% 
  filter(!(borrower_code %in% ny_codes)) %>% 
  select(borrower_section, match_section, score)

map_matches <- bind_rows(map_matches_ny_borrower, map_matches_not_ny) %>% 
  mutate(borrower_code = extract_code_names(borrower_section),
         borrower_year = extract_date(borrower_section),
         borrower_state = extract_state(borrower_section),
         match_code = extract_code_names(match_section),
         match_year = extract_date(match_section),
         match_state = extract_state(match_section))

map_matches <- map_matches %>% 
  filter(borrower_year >= match_year) %>% 
  group_by(borrower_section) %>% 
  arrange(desc(score)) %>% 
  slice(1) %>% 
  ungroup() %>%  
  filter(score >= 0.2)

map_matches <- data_frame(borrower_section = names(sections)) %>% 
  left_join(map_matches, by = "borrower_section") %>% 
  mutate(score = ifelse(is.na(score), 0, score))

map_summary <- map_matches %>% 
  group_by(borrower_state) %>% 
  summarize(score = mean(score)) %>% 
  arrange(desc(score)) 
```

```{r}
library(ggplot2)
library(broom)
library(USAboundaries)
library(rgeos)
library(maptools)
library(scales)
us <- us_states()
us_fortified <- tidy(us, region = "stusps") %>% 
  left_join(map_summary, by = c("id" = "borrower_state")) %>% 
  filter(id != "AK",
         id != "HI",
         id != "PR")

ggplot() +
  geom_polygon(data = us_fortified,
               aes(x = long, y = lat, group = group, fill = 1 - score),
               color = "black", size = 0.25) +
  scale_fill_distiller(name = "Avg. dissimilarity score", palette = "YlGn",
                       breaks = pretty_breaks(n = 5)) +
  coord_map("albers", lat0=30, lat1=40) +
  theme_classic() +
  labs(title = "Strength of borrowings from Field Code",
       x = NULL, y = NULL) +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        legend.position = "bottom")
```

```{r}
ggplot(map_summary, aes(x = borrower_state, y = score)) +
  geom_bar(stat = "identity") +
  theme_classic() +
  coord_flip()
```

### 2016-03-21 108-mapping.Rmd
Count number of sections for comparison to NY

@@
 source("R/helper.R")
+list1 <- read_lines("compare-to-NY-list-1.txt")
+list2 <- read_lines("compare-to-NY-list-2.txt")
+library(classInt)
 ```
@@
 
-map_matches <- map_matches %>% 
+regions <- read_csv("regions.csv")
+
+map_matches_sections <- map_matches %>% 
   filter(borrower_year >= match_year) %>% 
@@
   ungroup() %>%  
-  filter(score >= 0.2)
+  filter(score >= 0.2) %>% 
+  count(borrower_code) %>% 
+  mutate(year = extract_date(borrower_code)) %>% 
+  mutate(state = extract_state(borrower_code)) %>% 
+  left_join(regions)
 
@@
 map_summary <- map_matches %>% 
+  # filter(borrower_code %in% list2) %>% # Just the codes Kellen picked
   group_by(borrower_state) %>%
-  summarize(score = mean(score)) %>% 
+  summarize(score = sum(score)) %>% 
   arrange(desc(score))
+
+intervals <- classIntervals(map_summary$score, n = 5, style = "jenks")
+map_summary$score <- cut(map_summary$score, breaks = intervals$brks)
 ```
@@
 library(scales)
+library(RColorBrewer)
 us <- us_states()
@@
   geom_polygon(data = us_fortified,
-               aes(x = long, y = lat, group = group, fill = 1 - score),
+               aes(x = long, y = lat, group = group, fill = score),
                color = "black", size = 0.25) +
-  scale_fill_distiller(name = "Avg. dissimilarity score", palette = "YlGn",
-                       breaks = pretty_breaks(n = 5)) +
+  scale_fill_manual("Avg. dissimilarity score", values = brewer.pal(5, "YlGn")) +
   coord_map("albers", lat0=30, lat1=40) +
   theme_classic() +
-  labs(title = "Strength of borrowings from Field Code",
+  labs(title = "Strength of borrowings from Field Code (List 2)",
        x = NULL, y = NULL) +
@@
 ```
+
+```{r}
+library(ggrepel)
+ggplot(map_matches_sections, aes(x = year, y = n, color = region, group = state)) +
+  geom_point() +
+  geom_line() 
+    # geom_label_repel(aes(label = state))
+```

### 2016-03-21 108-mapping.Rmd
Revert "Count number of sections for comparison to NY"
This reverts commit 04e65feb331d6ff53c08180debbcdb255e4a7cd2.

@@
 
-regions <- read_csv("regions.csv")
-
-map_matches_sections <- map_matches %>% 
+map_matches <- map_matches %>% 
   filter(borrower_year >= match_year) %>% 
@@
   ungroup() %>%  
-  filter(score >= 0.2) %>% 
-  count(borrower_code) %>% 
-  mutate(year = extract_date(borrower_code)) %>% 
-  mutate(state = extract_state(borrower_code)) %>% 
-  left_join(regions)
+  filter(score >= 0.2)
 
@@
 map_summary <- map_matches %>% 
-  # filter(borrower_code %in% list2) %>% # Just the codes Kellen picked
+  filter(borrower_code %in% list2) %>% # Just the codes Kellen picked
   group_by(borrower_state) %>% 
-  summarize(score = sum(score)) %>% 
+  summarize(score = mean(score)) %>% 
   arrange(desc(score))
@@
 ```
-
-```{r}
-library(ggrepel)
-ggplot(map_matches_sections, aes(x = year, y = n, color = region, group = state)) +
-  geom_point() +
-  geom_line() 
-    # geom_label_repel(aes(label = state))
-```

### 2016-05-25 101-visualizations-for-article.Rmd
Add a couple spectrographs
Fix widths/heights of spectrograms

@@
 ---
+
+```{r setup,}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+```
 
@@
 
+CA1851
+
+```{r}
+spectrogram("CA1851", best_matches, white_list = 3)
+```
+
 Spectrogram of borrowings in MD1855. I expect to see reliance on English legislation (GB1852 and GB1854), amidst original material.
 
-```{r}
+```{r, fig.height=3}
 spectrogram("MD1855", best_matches, white_list = 7)
@@
 spectrogram("WA1855", best_matches, white_list = 8)
+```
+
+NV1861
+
+```{r}
+spectrogram("NV1861", best_matches, white_list = 4)
 ```
@@
 
-```{r}
+```{r, fig.height=6.5}
 spectrogram("NY1876", best_matches, white_list = 8)
@@
 
-```{r}
-spectrogram("NY1879", best_matches, white_list = 8)
+```{r, fig.height=7.75}
+spectrogram("NY1879", best_matches, white_list = 3)
 ```

### 2016-05-25 R/spectrogram.R

@@ -1,9 +1,9 @@
 # The `white_list` argument takes either a count numeric, in which case it
 # white lists at most that number of codes to be explicitly named in the viz,
 # or a character vector of codes to white list.
-spectrogram <- function(code, matches_df, num_cols = 40,
+spectrogram <- function(code, matches_df, num_cols = 50,
                         white_list = NULL, title = NULL,
-                        base_size = 16, base_family = "",
+                        base_size = 12, base_family = "",
                         legend_size = 0.5) {
   require(dplyr)
   require(stringr)
@@ -42,16 +42,18 @@ spectrogram <- function(code, matches_df, num_cols = 40,
   geom_tile(color = "lightgray") +
   theme_minimal(base_size = base_size, base_family = base_family) +
   coord_equal() +
-  labs(x = NULL, y = NULL, title = title,
-       fill = "Section borrowed from") +
+  labs(x = NULL, y = NULL, fill = "Section borrowed from") +
+  ggtitle(label = title) +
   theme(legend.position = "bottom",
         axis.ticks = element_blank(),
         axis.line = element_blank(), axis.text = element_blank(),
         panel.background = element_blank(), panel.grid = element_blank(),
-        legend.key.size = unit(legend_size, "cm")) +
+        legend.key.size = unit(legend_size, "cm"),
+        plot.margin = unit(c(0, 0, 0, 0), "cm"),
+        plot.title = element_text(hjust = 0.5)) +
   scale_fill_brewer(type = "qual", na.value = "lightgray", palette = 6) +
+  scale_fill_manual(na.value = "lightgray")
   scale_alpha(range = c(0.6, 1), guide = FALSE)
-
 }
 
 col_vector <- function(n, cols) {

### 2016-05-25 101-visualizations-for-article.Rmd
Wouldn't it be nice if things worked the first time?

@@
 
-```{r}
+```{r fig.height=3}
 spectrogram("CA1850", best_matches, white_list = 7)
@@
 
-```{r}
+```{r fig.height=4}
 spectrogram("CA1851", best_matches, white_list = 3)
@@
 
-```{r, fig.height=3}
+```{r, fig.height=2.5}
 spectrogram("MD1855", best_matches, white_list = 7)
@@
 
-```{r}
+```{r fig.height=4.5}
 spectrogram("NV1861", best_matches, white_list = 4)
@@
 ```
-
-Here I'm looking for the reverse of the previous spectrograms.
-Rather than illustrate sections BORROWED FROM elsewhere, can we illustrate sections in the original Field Code that GET BORROWED elsewhere, and instead of coloring by where they end up, color based on how many times a particular section appears throughout the corpus?
-
-I expect the beginning of the code will be grey--no one has New York's particular court system, so no one copies the jurisdictional texts, then high heat at the heart of the Code with the Field reforms, slackening off around particular proceedings, some of which will be New York specific, then heating up again towards the end with the code of evidence.

### 2016-05-25 R/spectrogram.R

@@ -52,7 +52,6 @@ spectrogram <- function(code, matches_df, num_cols = 50,
         plot.margin = unit(c(0, 0, 0, 0), "cm"),
         plot.title = element_text(hjust = 0.5)) +
   scale_fill_brewer(type = "qual", na.value = "lightgray", palette = 6) +
-  scale_fill_manual(na.value = "lightgray")
   scale_alpha(range = c(0.6, 1), guide = FALSE)
 }
 

### 2016-05-26 R/spectrogram.R
First attempt at setting consistent color scheme

@@ -38,7 +38,7 @@ spectrogram <- function(code, matches_df, num_cols = 50,
 
   # Make the plot
   matches_df %>%
-  ggplot(aes(x = column, y = -row, fill = match_code, alpha = score)) +
+  ggplot(aes(x = column, y = -row, fill = match_code)) +
   geom_tile(color = "lightgray") +
   theme_minimal(base_size = base_size, base_family = base_family) +
   coord_equal() +
@@ -51,8 +51,37 @@ spectrogram <- function(code, matches_df, num_cols = 50,
         legend.key.size = unit(legend_size, "cm"),
         plot.margin = unit(c(0, 0, 0, 0), "cm"),
         plot.title = element_text(hjust = 0.5)) +
-  scale_fill_brewer(type = "qual", na.value = "lightgray", palette = 6) +
-  scale_alpha(range = c(0.6, 1), guide = FALSE)
+  scale_fill_manual(na.value = "lightgray",
+                    values = c(
+                      CA1850 = "firebrick1",
+                      CA1851 = "firebrick2",
+                      CA1858 = "firebrick3",
+                      CA1872 = "darkred",
+                      DC1857 = "mediumorchid",
+                      GB1852 = "mediumorchid",
+                      IA1839 = "mediumorchid",
+                      IL1866 = "mediumorchid",
+                      IN1843 = "mediumorchid",
+                      IN1852 = "darkolivegreen4",
+                      LA1844 = "mediumorchid",
+                      MA1858 = "mediumorchid",
+                      MN1859 = "mediumorchid",
+                      MO1849 = "gold3",
+                      NE1866 = "mediumorchid",
+                      NY1829 = "darkorchid1",
+                      NY1848 = "gold1",
+                      NY1849 = "goldenrod1",
+                      NY1850 = "orange1",
+                      NY1851 = "goldenrod4",
+                      NY1853 = "orange3",
+                      NY1876 = "mediumorchid",
+                      OR1854 = "coral2",
+                      Other  = "mediumorchid",
+                      TX1855 = "mediumorchid",
+                      WI1849 = "deepskyblue1",
+                      WI1856 = "deepskyblue3",
+                      WI1858 = "deepskyblue4"
+                    ))
 }
 
 col_vector <- function(n, cols) {

### 2016-05-26 101-visualizations-for-article.Rmd
Changes to NA color plus new spectrograms

@@
 ```{r}
-spectrogram("CO1868", best_matches, white_list = 8)
+spectrogram("CO1868", best_matches, white_list = c("IL1866", "IN1843", "IA1839"))
+```
+
+CO1877: companion visualization of Colorado under the Field code
+
+```{r}
+spectrogram("CO1877", best_matches, white_list = 8) 
+```
+
+MT 1895
+
+```{r}
+spectrogram("MT1895", best_matches, white_list = 8)
 ```

### 2016-05-26 R/spectrogram.R

@@ -51,7 +51,7 @@ spectrogram <- function(code, matches_df, num_cols = 50,
         legend.key.size = unit(legend_size, "cm"),
         plot.margin = unit(c(0, 0, 0, 0), "cm"),
         plot.title = element_text(hjust = 0.5)) +
-  scale_fill_manual(na.value = "lightgray",
+  scale_fill_manual(na.value = "white",
                     values = c(
                       CA1850 = "firebrick1",
                       CA1851 = "firebrick2",
@@ -76,7 +76,7 @@ spectrogram <- function(code, matches_df, num_cols = 50,
                       NY1853 = "orange3",
                       NY1876 = "mediumorchid",
                       OR1854 = "coral2",
-                      Other  = "mediumorchid",
+                      Other  = "lightgray",
                       TX1855 = "mediumorchid",
                       WI1849 = "deepskyblue1",
                       WI1856 = "deepskyblue3",

### 2016-05-26 101-visualizations-for-article.Rmd
Fix colors, heights and selected codes

--- 2016-05-25 101-visualizations-for-article.Rmd
@@
 
-```{r setup,}
+```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
@@
 
-```{r fig.height=3}
-spectrogram("CA1850", best_matches, white_list = 7)
+```{r ca1850-borrowings, fig.height=3}
+spectrogram("CA1850", best_matches, white_list = c("LA1844", "NY1829", "NY1849",
+                                                   "NY1848"))
 ```
@@
 
-```{r fig.height=4}
+```{r CA1851-borrowings, fig.height=3.5}
 spectrogram("CA1851", best_matches, white_list = 3)
@@
 
-```{r, fig.height=2.5}
-spectrogram("MD1855", best_matches, white_list = 7)
+```{r MD1855-borrowings, fig.height=2.5}
+spectrogram("MD1855", best_matches, white_list = c("GB1852"))
 ```
@@
 
-```{r}
-spectrogram("WA1855", best_matches, white_list = 8)
+```{r WA1855-borrowings, fig.height=4.5}
+spectrogram("WA1855", best_matches, white_list = c("CA1850", "CA1851", "IN1852",
+                                                   "NY1853", "OR1854", "WI1849"))
 ```
@@
 
-```{r fig.height=4.5}
-spectrogram("NV1861", best_matches, white_list = 4)
+```{r NV1861-borrowings, fig.height=4.5}
+spectrogram("NV1861", best_matches, white_list = 5)
 ```
@@
 
-```{r}
+```{r NV1861-to-NY, fig.height=4.5}
 all_NV1861 <- data_frame(borrower_code = "NV1861",
@@
          str_detect(match_code, "NY"),
+         match_code != "NY1829",
          score >= 0.1,
@@
 
-spectrogram("NV1861", NV1861toNY, white_list = 5,
+spectrogram("NV1861", NV1861toNY, white_list = 7,
             title = "Sections in NV1861 with high similarity to NY codes")
-```
-
-Like the previous query for NV1861, Iowa is two steps away from New York.
-This time, however, the text is much less similar to New York.
-I only want one visualization for this, but I'm not sure if IA1851 or the revision IA1859 will be better, so can we do both?
-
-IA1851
-
-```{r}
-all_IA1851 <- data_frame(borrower_code = "IA1851",
-                         borrower_section = all_matches %>% 
-                           filter(borrower_code == "IA1851") %>% 
-                           `$`("borrower_section") %>%
-                           unique() %>%
-                           sort()
-                        )
-
-matches_to_NY <- all_matches %>% 
-  filter(borrower_code == "IA1851",
-         str_detect(match_code, "NY"),
-         score >= 0.1,
-         match_year <= 1851) %>% 
-  group_by(borrower_section) %>% 
-  arrange(desc(score)) %>% 
-  slice(1) %>% 
-  ungroup()
-
-IA1851toNY <- all_IA1851 %>% left_join(matches_to_NY) %>% 
-  arrange(borrower_section)
-
-spectrogram("IA1851", IA1851toNY, white_list = 10,
-            title = "Sections in IA1851 with matches to NY codes")
 ```
@@
 
-```{r}
+```{r IA1859-to-NY}
 all_IA1859 <- data_frame(borrower_code = "IA1859",
@@
 
-```{r}
-spectrogram("NC1868", best_matches, white_list = 8)
+```{r NC1868-matches}
+spectrogram("NC1868", best_matches, white_list = c("CA1858", "OR1862", "MN1859",
+                                                   "NY1849", "CA1850", "WI1858",
+                                                   "NY1853", "NY1851", "NY1850",
+                                                   "WI1856"))
 ```
@@
 
-```{r}
-spectrogram("CO1868", best_matches, white_list = 8)
+```{r CO1868-matches, fig.height=3.5}
+spectrogram("CO1868", best_matches, white_list = c("IL1866"))
 ```
 
-Same query as number 6 and 7, but like Louisiana, the point is to show that no one borrows the later New York Code, the one that departs from the Field tradition.
+CO1877: companion visualization of Colorado under the Field code
 
-```{r, fig.height=6.5}
-spectrogram("NY1876", best_matches, white_list = 8)
+```{r CO1877-matches, fig.height=4}
+spectrogram("CO1877", best_matches, white_list = 8) 
 ```
 
-```{r, fig.height=7.75}
-spectrogram("NY1879", best_matches, white_list = 3)
+MT 1895
+
+```{r MT1895-matches, fig.height=7.5}
+spectrogram("MT1895", best_matches, white_list = 8)
 ```
+
+NY1876
+
+```{r NY1876-matches, fig.height=6.5}
+spectrogram("NY1876", best_matches, white_list = c("NY1829", "NY1850", "NY1853",
+                                                   "NY1848", "NY1849", "NY1851"))
+```
+
+NY1879
+
+```{r NY1879-matches, fig.height=7}
+spectrogram("NY1879", best_matches, white_list = c("NY1853", "NY1876"))
+```

### 2016-05-26 R/spectrogram.R

@@ -53,29 +53,38 @@ spectrogram <- function(code, matches_df, num_cols = 50,
         plot.title = element_text(hjust = 0.5)) +
   scale_fill_manual(na.value = "white",
                     values = c(
-                      CA1850 = "firebrick1",
+                      AZ1865 = "lightpink3",
+                      AZ1887 = "lightpink3",
+                      CA1850 = "palevioletred1",
                       CA1851 = "firebrick2",
                       CA1858 = "firebrick3",
+                      CA1868 = "indianred1",
                       CA1872 = "darkred",
                       DC1857 = "mediumorchid",
                       GB1852 = "mediumorchid",
                       IA1839 = "mediumorchid",
+                      ID1881 = "mediumorchid4",
                       IL1866 = "mediumorchid",
                       IN1843 = "mediumorchid",
-                      IN1852 = "darkolivegreen4",
-                      LA1844 = "mediumorchid",
+                      IN1852 = "chartreuse3",
+                      LA1844 = "purple4",
                       MA1858 = "mediumorchid",
-                      MN1859 = "mediumorchid",
+                      MN1859 = "lightblue2",
                       MO1849 = "gold3",
+                      MT1865 = "maroon3",
                       NE1866 = "mediumorchid",
+                      NV1861 = "mediumpurple4",
+                      NV1869 = "mediumorchid4",
                       NY1829 = "darkorchid1",
-                      NY1848 = "gold1",
+                      NY1848 = "darkorange",
                       NY1849 = "goldenrod1",
-                      NY1850 = "orange1",
+                      NY1850 = "khaki3",
                       NY1851 = "goldenrod4",
                       NY1853 = "orange3",
                       NY1876 = "mediumorchid",
-                      OR1854 = "coral2",
+                      NY1879 = "mediumpurple1",
+                      OR1854 = "chocolate1",
+                      OR1862 = "chocolate1",
                       Other  = "lightgray",
                       TX1855 = "mediumorchid",
                       WI1849 = "deepskyblue1",

### 2016-05-26 101-visualizations-for-article.Rmd
Minor tweaks to colors and sizes

@@
 
-```{r NV1861-borrowings, fig.height=4.5}
+```{r NV1861-borrowings, fig.height=4}
 spectrogram("NV1861", best_matches, white_list = 5)
@@
 
-```{r NV1861-to-NY, fig.height=4.5}
+```{r NV1861-to-NY, fig.height=4}
 all_NV1861 <- data_frame(borrower_code = "NV1861",
@@
 
-```{r NY1879-matches, fig.height=7}
+```{r NY1879-matches, fig.height=6.5}
 spectrogram("NY1879", best_matches, white_list = c("NY1853", "NY1876"))

### 2016-05-26 R/spectrogram.R

@@ -66,7 +66,7 @@ spectrogram <- function(code, matches_df, num_cols = 50,
                       ID1881 = "mediumorchid4",
                       IL1866 = "mediumorchid",
                       IN1843 = "mediumorchid",
-                      IN1852 = "chartreuse3",
+                      IN1852 = "chartreuse4",
                       LA1844 = "purple4",
                       MA1858 = "mediumorchid",
                       MN1859 = "lightblue2",
@@ -78,7 +78,7 @@ spectrogram <- function(code, matches_df, num_cols = 50,
                       NY1829 = "darkorchid1",
                       NY1848 = "darkorange",
                       NY1849 = "goldenrod1",
-                      NY1850 = "khaki3",
+                      NY1850 = "khaki1",
                       NY1851 = "goldenrod4",
                       NY1853 = "orange3",
                       NY1876 = "mediumorchid",

### 2016-05-26 104-network-graphs-in-ggraph.Rmd
Update network graphs

@@
 library(stringr)
+library(purrr)
 load("cache/corpus-lsh.rda")
@@
 ```
+
+Get section-to-section network graphs.
+
+```{r}
+library(igraph)
+sections_edge_list <- best_matches %>% 
+  select(borrower_section, match_section, score) %>% 
+  filter(!is.na(match_section))
+sections_g <- graph_from_data_frame(sections_edge_list, directed = TRUE)
+sections_g <- decompose(sections_g, min.vertices = 5)
+sections_v_count <- sapply(sections_g, vcount) 
+hist(sections_v_count,main = "Number of vertices in section to section graphs")
+
+section_of_interest <- "NY1850-006060"
+has_section <- function(x, section) section %in% x
+sections_g %>% 
+  lapply(vertex_attr, "name") %>% 
+  sapply(has_section, section_of_interest) %>% 
+  which()
+
+# 484 for witness testimony
+# 1 for abolishing chancery
+```
+
+```{r}
+plot_graph <- function(g, title = "A cluster of borrowings", subtitle = NULL) {
+plot <- ggraph(g, "igraph", algorithm = "nicely") +
+  geom_edge_fan(aes(edge_width = score, 
+                    alpha = score),
+                arrow = arrow(type = "closed", ends = "first",
+                              length = unit(0.10, "inches"),
+                              angle = 15)) +
+  geom_node_point(size = 6, alpha = 0.5, color = "lightblue") +
+  geom_node_text(aes(label = name)) +
+  scale_edge_width("Similarity score", range = c(1, 2), guide = "none") + 
+  scale_edge_alpha(range = c(0.3, 0.4), guide = "none") +
+  ggforce::theme_no_axes() +
+  labs(title = title,
+       subtitle = subtitle) +
+  theme(legend.position = "bottom",
+        panel.border = element_blank())
+}
+
+set.seed(100)
+abolish_chancery <- sections_g[[1]]
+V(abolish_chancery)$name <- str_replace_all(V(abolish_chancery)$name, "-\\d+", "")
+civil_action <- plot_graph(abolish_chancery, title = 'The Creation of "A Civil Action"')
+ggsave("out/civil-action-sections-network.png", civil_action, width = 8, height = 6)
+```

### 2016-05-26 R/spectrogram.R
Just say no to khaki

@@ -78,7 +78,7 @@ spectrogram <- function(code, matches_df, num_cols = 50,
                       NY1829 = "darkorchid1",
                       NY1848 = "darkorange",
                       NY1849 = "goldenrod1",
-                      NY1850 = "khaki1",
+                      NY1850 = "peru",
                       NY1851 = "goldenrod4",
                       NY1853 = "orange3",
                       NY1876 = "mediumorchid",

### 2016-05-26 101-visualizations-for-article.Rmd
Yet more color updates

@@
   group_by(borrower_section) %>% 
-  arrange(desc(score)) %>% 
+  filter(score >= max(score) - 0.1) %>% 
+  arrange(desc(match_code)) %>% 
   slice(1) %>% 

### 2016-05-26 R/spectrogram.R

@@ -55,7 +55,7 @@ spectrogram <- function(code, matches_df, num_cols = 50,
                     values = c(
                       AZ1865 = "lightpink3",
                       AZ1887 = "lightpink3",
-                      CA1850 = "palevioletred1",
+                      CA1850 = "indianred4",
                       CA1851 = "firebrick2",
                       CA1858 = "firebrick3",
                       CA1868 = "indianred1",
@@ -80,7 +80,7 @@ spectrogram <- function(code, matches_df, num_cols = 50,
                       NY1849 = "goldenrod1",
                       NY1850 = "peru",
                       NY1851 = "goldenrod4",
-                      NY1853 = "orange3",
+                      NY1853 = "tan4",
                       NY1876 = "mediumorchid",
                       NY1879 = "mediumpurple1",
                       OR1854 = "chocolate1",

### 2016-05-26 scripts/network-graphs.R
Fix regions and Dakotas

@@ -50,6 +50,7 @@ states_edges <- summary_matches %>%
          match_state = extract_state(match_code),
          borrower_date = extract_date(borrower_code),
          match_date = extract_date(match_code)) %>%
+  mutate(borrower_state = ifelse(borrower_state == "DT", "SD", borrower_state)) %>%
   filter(!is.na(match_code),
          borrower_date >= match_date,
          borrower_state != match_state) %>%

### 2016-05-27 104-network-graphs-in-ggraph.Rmd
Updates to network graph

@@
 
-```{r}
+```{r fig.width=12, fig.height=12}
 ggraph(codes_g, "igraph", algorithm = "fr") +
@@
   scale_edge_alpha(range = c(0.3, 0.4), guide = "none") +
+  scale_color_manual(values = c("South" = "steelblue1",
+                                "West" = "coral2",
+                                "Atlantic" = "darkgoldenrod2",
+                                "New England" = "mediumorchid2",
+                                "Midwest" = "palegreen2",
+                                "New York" = "peru")) + 
   ggforce::theme_no_axes() +

### 2016-05-27 101-visualizations-for-article.Rmd
Push heatmap of NY1850

@@
 ```
+
+```{r NY-most-borrowed, fig.height=8}
+all_NY1850 <- data_frame(borrower_code = "NY1850",
+                         borrower_section = all_matches %>% 
+                           filter(borrower_code == "NY1850") %>% 
+                           `$`("borrower_section") %>%
+                           unique() %>%
+                           sort()
+                        )
+
+NY1850_match_counts <- all_matches %>% 
+  filter(match_code == "NY1850",
+         borrower_year > 1850,
+         score >= 0.1) %>% 
+  count(match_section)
+
+left_join(all_NY1850, NY1850_match_counts, 
+          by = c("borrower_section" = "match_section")) %>% 
+  select(section = borrower_section, n) %>% 
+  mutate(n = ifelse(n < 6, NA, n)) %>% 
+  mutate(n = cut(n, c(seq(0, 40, 5), 85))) %>% 
+  mutate(.,
+         column = col_vector(nrow(.), 50),
+         row = row_vector(nrow(.), 50)) %>% 
+  ggplot(aes(x = column, y = -row, fill = n)) +
+  geom_tile(color = "lightgray") +
+  scale_fill_brewer(palette = "YlOrBr", na.value = "white", 
+                    labels = c("6-10", "11-15", "16-20", "21-25", "26-30",
+                               "31-35", "36-40", "40+")) +
+  labs(x = NULL, y = NULL, fill = "Number of time borrowed") + 
+  coord_equal() + 
+  theme_minimal() + 
+  theme(legend.position = "bottom",
+      axis.ticks = element_blank(),
+      axis.line = element_blank(), axis.text = element_blank(),
+      panel.background = element_blank(), panel.grid = element_blank(),
+      legend.key.size = unit(0.5, "cm"),
+      plot.margin = unit(c(0, 0, 0, 0), "cm"),
+      plot.title = element_text(hjust = 0.5)) +
+  ggtitle("Most frequently borrowed sections in NY1850")
+
+```

### 2016-05-27 104-network-graphs-in-ggraph.Rmd
Updates to network graph

@@
 source("R/helper.R")
-set.seed(82892)
+set.seed(82893)
 ```
@@
 ```{r fig.width=12, fig.height=12}
-ggraph(codes_g, "igraph", algorithm = "fr") +
+ggraph(codes_g, "igraph", algorithm = "nicely") +
   geom_edge_fan(aes(edge_width = sections_borrowed, 

### 2016-05-27 scripts/network-graphs.R

@@ -31,6 +31,8 @@ edges_n <- summary_matches %>%
   ungroup()
 
 codes_g <- graph_from_data_frame(edges_n, directed = TRUE)
+
+
 node_distances <- distances(codes_g,
                             mode = "out",
                             to = c("NY1848", "NY1849", "NY1850",
@@ -41,6 +43,12 @@ nodes_n <- data_frame(name = names(node_distances),
                       distance = node_distances)
 
 codes_g <- graph_from_data_frame(edges_n, directed = TRUE, vertices = nodes_n)
+
+g_ids <- V(codes_g)$name
+g_ids <- ifelse(g_ids == "DT1862", "ND1862", g_ids)
+g_ids <- ifelse(g_ids == "DT1868", "ND1868", g_ids)
+g_ids <- ifelse(g_ids == "DT1887", "SD1887", g_ids)
+V(codes_g)$name <- g_ids
 
 min_state_sections <- 100
 max_state_connections <- 2

### 2016-06-18 article/article.Rmd
Import from Google Docs

@@
 ---
-title: 'The “Paste-Pot” Field Code: The Migration of Law in the Nineteenth-Century
-  United States'
-author: "Kellen Funk and Lincoln Mullen"
+title: The Spine of American Legal Practice
+author:
+- Kellen Funk
+- Lincoln Mullen
 output: pdf_document
----
+...
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
-```
+At the opening of the first Nevada legislature in 1861, Territorial Governor James W.
+Nye, a former New York lawyer, instructed the assembly that they would have to forsake the Mormon statutes of Utah Territory from which Nevada had been carved.
+Those laws were ill adapted to "the mining interests" of the new territory, but "happily for us, a neighboring State whose interests are similar to ours, has established a code of laws" sufficiently attractive to "capital from abroad." That neighbor, of course, was California, and Nye urged that California's code of civil practice be enacted in Nevada, as far as it could "be made applicable."[^1] Territorial Senator William Morris Stewart, the famed silver-mining lawyer who would become a leading U.S.
+Senator of Reconstruction, followed the instructions perhaps too well.
+Stewart literally cut and pasted the latest *Wood's Digest* of the California Practice Act into the session bill, crossing out *state* and *California* and substituting *territory* and *Nevada* where necessary.
+Stewart copied not just California's code but also its method of codification---California too had borrowed its code in a similar manner from New York.
+
+Nye wrote back to the assembly in disgust.
+The bill---of 715 sections---had reached him late the night before the legislative session was to close.
+Even in the few hours he had to read it, Nye counted "so many errors in the enrolling of it, numbering probably more than three hundred." Some errors were severe.
+Nevada's Organic Act specified the jurisdiction of the district courts and justices of the peace, but the code overwrote these limitations by copying California's arrangements.
+Error-riddled and unconstitutional as the bill was, Nye believed a civil practice code was a "universal necessity and public need," concluding that "without some legislation in providing a code of procedure in civil cases, it may be a matter of grave question whether your courts would be able to fulfill the purpose of their creation."[^2] Nye signed the Code into law.
+Strikingly, nothing like this "universal necessity" had existed when Nye began his legal career in New York in the 1840s.
+
+By the end of the nineteenth-century, thirty-one American states and territories had adapted the text of a New York Code of Civil Procedure first promulgated in 1848.
+The Code colloquially became known as the Field Code, named for its chief draftsman David Dudley Field, a famed Manhattan trial lawyer.[^3] When Field's Code appeared in the Colorado assembly in 1876, a Denver newspaper wryly commented that "the scissors and paste-pot we had heretofore confidently believed were implements peculiar to the newspaper sanctum." But to the editor, the cut-and-paste code was not just a humorous curiosity of legislative history.
+Rather, the extensive copying of Field's Code threatened the foundations of American popular sovereignty.
+"The bill is a long one; the assembly has not the time to devote to it and to give it the scrutiny that a measure of such importance demands," the editor explained.
+But blind approval "would be an injustice to themselves and a greater wrong and injustice to the people who have a right to demand that their public servants legislate for the public good." The Code "has been 'assimilated,' as we are informed, 'to the character and requirements of our people,' whatever that may mean," but the editor feared the legislation was the product of "men who have the welfare of the 'dear people' at their tongue's end always, but never in their hearts."[^4]
+
+The migration of the Field Code was a central event in Anglo-American legal history, but no modern historian has traced the extensive borrowings of the Field text nor recognized the political furor that greeted the Code outside New York.[^5] Every aspect of a civil justice system, the rules granting access to courts, to lawyers, to remedies (whether damages, injunctions, or seizure of property) was covered by the Code, making its New York-specific rules politically contentious both in- and outside the Empire State.
+As the Field Code migrated around the country, commentators in each jurisdiction raised the same complaint: How could legislation borrowed from another state represent the popular will and bests interests of *this* state?
+
+Exploring this history is a daunting task, however.
+Procedure codes were long, technical documents, and although each jurisdiction copied large swaths of text, each also modified the text along the way, sometimes with a simple *Nevada* for *California*, sometimes with more foundational changes to the remedial system.
+Although Stewart's cut-and-paste code found its way into the archives, most draft legislation did not, and few codifiers explained in detail how they produced their texts.
+
+Innovative techniques in digital analysis of texts can resolve some of these difficulties.
+Within a corpus of legislation, digital programming can essentially reverse engineer and visualize what the archive revealed in Figure 1: which texts were borrowed, which modified, and how extensively.
+Our method works especially well for legal texts, for reasons we will explain.
+However, we designed a replicable method that can offer similar results on any other kind of curated collection of texts, from church hymns to medical treatises.
+
+The first contribution of this Article is the demonstration of our methods, applied to the Field Code.
+The second contribution is the integration of these methods with more conventional approaches of social and cultural history.
+On the national level the extent of legislative borrowing followed a pattern American historians have described as "Greater Reconstruction"---the former Confederate South and the Far West show a remarkable kinship.
+Scholars have typically described Greater Reconstruction as a *federal* development: the creation of national citizenship, a national economy, and a larger state apparatus centered in Washington, D.C.
+This Article shows that Greater Reconstruction had its state-level dimensions as well.
+The uniform practice of law and adjudication of civil remedies was not structured by Washington mandates, however, but by the anxiety that New York capital would follow only New York civil remedies.
+At the more local level, our digital computations can trace modifications within code traditions, for instance, the ways western and midwestern codifiers altered New York's law to accommodate hardening conceptions of racial competencies in the civil courts.
+To see these developments, one needs a tool that can canvass all the states at once across broad swaths of civil law.
+
+**Part 1.**
+
+Until 1848, civil remedies and trial practice in New York were largely governed by common law traditions loosely categorized as "practice and pleadings."[^6] To understand how to file a civil claim or to enforce a judgment, a lawyer had to consult ad hoc statutes from colonial times to the present as well as precedents reported from cases litigated at common law and chancery.
+By the 1840s, enterprising practitioners had collated these materials into a half dozen marketable treatises, but these remained works of private opinion---no court was bound to agree with the treatise writers as to the weight, relevance, or proper interpretation of a legal statement.[^7] The common law was accordingly known as "unwritten law" despite the proliferation of published texts.
+The point was that common law was not precisely determined until a particular case drawn from the messy facts of life demanded resolution.[^8] Statutes, on the other hand, were "written law," prescribing or reforming the rules even before a case put the precise question in issue.
+And within the realm of written law, codes were the ultimate statutes.[^9]
+
+Codification is, as Lawrence Friedman has written, "one of the set pieces of American legal history." Law reformers advocated for a codification of the common law from the earliest days of the Republic up into the Gilded Age, from Massachusetts down to South Carolina.
+Efforts ranged from mere compilations of existing statutes in each state to a full European-style codification meant to be an entirely comprehensive and systematic statement of the law.[^10] At its most basic level, codification proposed that legislative policy ought to be the sole source of law.
+Law was to be made by democratically responsible legislators---in terse, unambiguous statements---not discovered through application and analogy in particular cases by the judges.
+Codification debates thus ranged over the metaphysics of law to the political theories of separation of powers and institutional competency.[^11]
+
+At New York's constitutional convention in 1846, "the conquerors took all," as the ambivalent Jacksonian James Fenimore Cooper complained.[^12] Law reformers abolished the court of chancery, made judges to stand for popular election, and required the legislature to appoint a commission to reform the "practice and pleadings" of the civil courts.[^13] New Yorkers had two models of legislative commissions on which they could draw for their own law reforms.
+The French government under Napoleon had appointed five-member commissions to codify the law of France.
+When the New York law reformer William Sampson called for codification in a widely noted address to the New York historical society, one of the members of the French commission was living in exile in upstate New York at the time and wrote to Sampson to advise him on the mechanics of codification:
+
+&gt;&gt;Courage; persevere in the support of written reason against precedents and vague traditions.
+.
+.
+.
+Let four or five good heads be united in a commission, to frame in silence the project of a code.
+It is not so difficult a task.
+It is only to consult together, and to select.
+Do so with your best authors as we did with ours, and principally with Pothier's treatise on Obligations, which we simply converted into articles of our code.&lt;&lt;
+
+Tellingly, the French commissioner took it as granted that the commission's code would automatically be promulgated as law.[^14]
+
+The other model came from England.
+Royal commissions had been employed since before the Revolution of 1688 to advise on a variety of matters.
+After the Revolution, royal commissions became disfavored while Parliament undertook many of the same functions through "committees of enquiry" to which only members of Parliament were appointed.
+By the nineteenth century, the use of royal commissions was again reviving.
+Royal commissioners were usually not legislators.
+On the one hand, that meant commissioners were not bound to the rhythms of Parliament's schedule---they could continue their work even as Parliament adjourned.
+On the other hand, the recommendations of royal commissioners were a further remove from actual legislation.
+Although by the mid-nineteenth century royal commissions sometimes offered model statutes, their advised legislation still had to pass through the normal politicking and drafting processes of Parliament.[^15]
+
+After David Dudley Field and two other lawyers were appointed to the procedural commission, their reports made clear that they favored the French model but understood political realities would hold them to the English model.
+From 1847 to 1850, the commissioners made five reports to the legislature knowing they had no power to keep legislators from amending their code or even defeating it altogether.
+Each time they reminded legislators that "public opinion had issued its mandate in the most imposing form" of a constitutional decree.
+The constitution, together with the legislative act appointing the commission "gave the commissioners instructions so precise, as to leave them no discretion, if they had desired it, \[and\] promised them therefore in advance, so long as they obeyed those instructions, the concurrence and co-operation of all departments of the government."[^16] Although the theory of codification made it a democratic enterprise, in practice Field---an ardent Jacksonian---insisted the democratic legislature ought to defer to the expertise of the commissioners.
+
+The Field commission sought to blunt criticism by insisting that political concerns about lawmaking did not apply to mere *procedure*.
+"The system of procedure by which law is administered, differs from the law itself in this," the commissioners explained: "the latter is a body of elementary rules founded in the immutable principles of justice, drawing their origin from the obligations which divine wisdom has imposed .
+.
+.
+; while the former consists, in its very nature, but of a body of prescribed rules, having no source but the will of those by whom they are laid down." Substantive law was universal, natural, grounded in divine justice, and therefore entitled to respect and protection from change.
+But God cared nothing of the "the mere machinery by which law is to be administered," and thus, the commissioners argued, procedure was trivial enough for legislative experimentation but complicated enough that only master practitioners like themselves could run the experiment.[^17]
+
+The scope of the Code tended to belie the idea that procedure included only the "mere machinery" of a lawsuit.[^18] The final draft of the Code, printed in 1850, spanned nearly 800 pages of 1,885 regulations.
+The first third of the Code covered constitutional topics, specifying the jurisdiction of all state courts and the duties of all state officers (and liabilities for violating those duties).
+The Code deregulated attorney compensation, introducing novel structures of retainers and contingency fees.[^19] It created summary procedures meant to accelerate debt collections while simultaneously carving out "homestead" exemptions from the sheriff's reach.[^20] The Code concluded by defining who could be an attorney, a juror, and a witness, drawing racial and gendered distinctions over who could speak in court.[^21]
+
+Most importantly, the Code defined all the remedies that a civil court could order---from money damages, to partition of property, to injunctive decrees and contempts--and made those remedies available in every lawsuit.
+In many cases, a legal right was indistinguishable from the remedy that secured that right: The right to possess a particular piece of property and the remedy that seized and delivered that property were, in effect, the same thing.
+Remedies were thus intimately connected to substantive law.
+For that reason, neither the French *code de procédure civile* (1806) nor Blackstone's or Bentham's writings conceived of remedies as purely procedural.[^22] By codifying remedies, Field invited continual expansion of the category of "procedure." As other states adopted the procedure code, they sometimes included other fields of law that seemed paradigmatically "substantive" yet had such specific procedures or remedies that they too were placed in a "code of procedure," including the law of wills, corporations, or mortgages.[^23] And after all, argued procedural codifiers in Iowa, what did the famed Married Women's Property Acts offer besides procedural reform?
+These acts gave women *standing* to litigate in their own name and seek *remedies* in claims of property and contract, and they abolished mandatory rules of *joinder* (of husbands).
+Thus, one of the most significant changes to the law of property and domestic relations in the century went into the state's Code of Civil Procedure.[^24]
+
+Despite Field's arguments that a mere procedure code was democratically unproblematic, his efforts were not entirely successful in New York.
+The commission submitted a draft of its main reforms in 1848, emphasizing that this first code was "but a report in part." New York's legislators enacted the partial code with little amendment, some legislators repeating Field's view that the constitution obligated them to accept the code.[^25] But when the commissioners submitted their final draft, the Assembly judiciary committee balked, directly disputing the commissioners' claims that procedure was merely the machinery of the law.
+They wrote that "provisions for rights and for the mode of pursuing remedies, insensibly run into each other," and distinctions between substance and procedure were difficult to draw in practice.
+In fact, "the parts of a system of law are more dependent on each other, and run into and affect each other, infinitely more than any machine of human contrivance." Procedure, at least in the common law tradition, was no mere machinery---it involved the entire legal apparatus.
+They therefore suspected the commissioners' forthcoming code of criminal procedure would include all of the criminal law as well, "as they seem to understand practice and pleadings to include all the law upon a given subject." That being the case, the committee wondered whether, "responsible as the Commissioners undoubtedly are, should we place in them a blind and implicit confidence that shall commit to their discretion the peace and property, the personal liberty and the lives of those who sent *us* here to make laws for them?"[^26]
+
+The Code would encounter similar difficulties in each jurisdiction that adopted it.
+Even the shortest version of the Field Code was significantly longer than any other state statute before the Progressive legislation of the twentieth century.
+And unlike statutory complilations that sometimes took the name of a "code" but made no changes to existing law, the Field Code opened with a declaration of novelty, abolishing the hallmarks of prior practice and instituting "hereafter" a new form of action with substantial revisions to basic matters of standing, remedy, and enforcement of civil judgments.[^27] In the states where it was imported, there could be no getting around the fact that the Code introduced extensive, new law, yet legislators were unable to read, critique, and amend the Code within the short time horizons of a legislative session.
+"It is folly to undertake to pass a code in a sixty day session," wrote the *Montana Post*, "and the best way would be for the Assembly to select one from a State or Territory which would come near meeting our wants, and slide it through with the fewest changes possible."[^28] Sliding the Code through eased the problem of time but exacerbated the problem of local sovereignty.
+"To be governed by a foreign law, especially when that law is not preknown to the people whose conduct is to be regulated thereby .
+.
+.
+is something repugnant to the idea of Democratic Republican government," complained the *The Miner's Express*.[^29]
+
+How, then, did states and territories achieve a politically acceptable balance between efficiency and sovereignty, borrowing law for sake of time but endowing it with popular legitimacy in each locale?
+Quite apart from the technicalities of legal practice, answering that question historically is daunting.
+The American federation of civil government into (depending on the period) more than thirty or forty separate jurisdictions creates significant difficulties for describing a phenomenon that was truly national despite its state-centered enactments.
+It requires some sense of how much law was borrowed in each locality and to what degree and significance innovations were introduced.
+But precisely because these questions concern codes---texts that comprehensively and systematically cover a given subject---they are ideal for innovative techniques in digital history.
+
+**Part 2.**
+
+Although the amount of legislation that governed American civil practice is impressive---even if uncodified, every state had procedure statutes that were amended and re-enacted nearly every decade---a corpus of procedural legislation would not even count among digital historians as "big data." Our collection of relevant (or possibly relevant) laws comprise 135 statutes from the nineteenth century.
+It includes separately bound codes of civil procedure as well as codes or regulations appearing session laws and statutory compilations.[^30] It comprises some **\[NUMBER\]** pages, **\[NUMBER\]** words, organized into 98,000 regulations.
+The corpus is not exhaustive.
+It includes the initial enactment of every code of civil procedure, as well as a sampling of procedure statutes and re-enacted codes from states reputed to have been legally influential, but it does not include every known statute of American procedural law.
+While a comprehensive project may be illuminating in its own ways, our specific question of how New York legislation influenced other states permits a more curated corpus.
+
+Curating a corpus to answer a question is an important difference from the way that digital history work often describes itself.
+Speaking in broad terms, digital historical work---like all historical work---can either begin with a set of sources or a question.[^31] Digital history often emphasizes that it can begin with large datasets---the so-called "big data" which recently achieved the level of buzzword---such as the Google Books or Hathi Trust corpora.[^32] We think that this is indeed a worthwhile endeavor, and salutary for historians to have their questions shaped by the sources.[^33] But it is less apparent that historians can apply digital history methods to questions that they have already formed, or that the only thing that these methods, most notably of "distant reading" can do is to work at the absolute largest scales.
+Our method, which might unimaginatively named "medium data" is a useful way for historians to proceed, by finding a corpus which is bounded by a particular problem.
+
+Because most codes were public statutes, they were widely printed and distributed and therefore found their way into libraries digitized by Google Books.
+Where possible, we collected our corpus from Google's publicly accessible database.
+We used optical character recognition software (OCR) to create plain-text versions of the codes, which we edited lightly---we corrected section markers by hand as necessary and wrote a script to fix the most common OCR errors.[^34]
+
+The most important step we took in processing the files was to split each section of the code into its own text file.
+Codes varied in their organizations, but they universally divided specific regulations into *sections* (or, on occasion, *articles*).
+The discursive formation of these texts not only provides a handy organizational scheme for digital approaches, sections were historically the way legislators borrowed their texts.[^35] Codifiers took their sources apart by sections, rearranging here, editing, drafting, and then re-combining there.
+Despite the fact that states differed widely on what topics they included in "civil procedure," sectioning the codes allowed us to assess similarity even among codes of quite different lengths and coverage.
+For instance, we know from historical evidence that California's 1851 code was derived from New York's 1850 code.
+(Stephen Johnson Field, David Dudley's brother, was the lawyer who imported New York's code into California.[^36]) But the New York code is over 150,000 words long, where was California's code was just over 50,000 words long.
+Those rather disparate lengths mean that comparing all of the California code to all of the New York code is a less meaningful comparison that than comparing each section in the California code to each section in the New York code, where matching sections will be a similar length.
+
+The next step was to compare sections to one another and measure the similarity between them.
+To continue the New York-to-California example, consider the following pairs of sections.
+The first pair is from the final draft of the New York Field Code.
+These sections completely abolish prior practice and begin to rebuild the procedure system from the ground up:
+
+&gt;&gt;§ 554.
+The distinction between actions at law and suits in equity, and the forms of all such actions and suits, heretofore existing, are abolished; and, there shall be in this state, hereafter, but one form of civil action, for the enforcement or protection of private rights and the redress or prevention of private wrongs, which shall be denominated a civil action.
+§ 555.
+In such action, the party complaining is known as the plaintiff, and the adverse party as the defendant.&lt;&lt;
+
+In the theory of Euro-American lawyers, California had no prior practice to abolish, so the code began more simply:
+
+&gt;&gt;§ 1.
+There shall be in this State but one form of Civil Action, for the enforcement or protection of private rights, and the redress or prevention of private wrongs.
+§2.
+In such action the party complaining shall be known as the plaintiff, and the adverse party as the defendant.&lt;&lt;
+
+The pairs are obviously related to one another, both in terms of their legal force and in terms of the actual words used.[^37]
+
+A well-known method for measuring the similarity of two documents involves dividing texts up into "tokens" of consecutive words and calculating a Jaccard score, defined as ratio between the number of tokens that the two document have in common to the total number of tokens that appear in both documents.
+We used five-word tokens and "shingled" them, meaning that for the New York sections above, the first token was "the distinction between actions at," the second token was "distinction between actions at law," and so on.
+These tokens each contain more meaning than a single word, yet because they are shingled they are robust to changes in the text or noisy OCR.
+A Jaccard score (in set notation, EQUATION) will always produce a number between 0 (complete dissimilarity) and 1 (complete similarity).
+
+Comparing the section pairs above produces the following matrix of scores.
+
+| NY1850-554 | NY1850-555 | CA1851-001 | CA1851-002 |
+
+|:----------|:----------:|:----------:|:----------:|:----------:|
+
+|NY1850-554 | | 0 | 0.14 | 0 |
+
+|NY1850-555 | | | 0 | 0.41 |
+
+|CA1851-001 | | | | 0 |
+
+|CA1851-002 | | | | |
+
+As we would expect the first respective sections (New York § 554 and California § 1) have a score of 0.14, which indicates that they are similar but have significant differences, while the second sections (New York § 555 to California § 2) have a much higher similarity score since only a few words were changed.
+Just as important when we compare the first section in New York to the second section in California, we get a score of 0; the two sections are nothing like each other.
+
+The aim, then, was to create a triangular matrix like the one above, but with approximately 98,000 rows and 98,000 columns, containing the similarity scores for each possible pair of sections.
+While this is easy enough to conceptualize, such a matrix is actually quite large, containing about 4.8 billion comparisons.
+This would take an unreasonable amount of computation time, and most of these comparisons would be unnecessary, since each section has no relationship to most other sections (like the matrix above, most scores will be zero).
+We therefore implemented the minhash/locality sensitive hashing (LSH) algorithm to detect candidate pairs, that is, documents which were likely to be matches, and then we measured the Jaccard score for only those candidate pairs.[^38]
+
+The result was a matrix of matches, with over 45,000 genuine matches.
+For each section in the corpus, after making some adjustments to remove anachronisms and spurious matches,[^39] we were able to identify the section from which it was most likely borrowed.
+In other words, we had traced the work of the commissioners' scissors and paste-pots through the course of their codes.
+
+**Part 3.**
+
+Having developed a method for finding legislative borrowings, we next sought to visualize the broader patterns revealed by the those borrowings.
+We did this first by aggregating the section to section borrowings into code to code borrowings.
+By counting how many sections each code borrowed from each other code, we were able to show the connections from one code to another.
+
+The resulting network graph (**Figure X: Network Graph**) tells the genealogy of civil procedure in the United States.
+The New York codes, especially the finished draft of 1850, are central to the entire network.[^40] Yet it is important to note that New York spurred different traditions within the procedural network.
+Variations in the Field drafts meant that different states could borrow different versions of the Field Code.
+The 1850 New York code was the primary progenitor of several families of codes in California, Kentucky, Iowa, and Ohio, each of which in turn became major contributors to the law of neighboring states.
+The 1851 New York code became the progenitor of codes for Wisconsin, Florida, North Carolina, and South Carolina.
+Mississippi and Missouri borrowed from the New York 1849 code.
+These variations point out how the Field Code was always a moving target.
+While Field considered the 1850 New York code to be the definitive, ideal version of the code, it was really all of the New York codes from 1848 to 1853 that became models for other jurisdictions, likely due to whatever material a given commission had on hand.
+The Field Code was not a single volume on the shelf, but a series of volumes any one of which might be more accessible in different regions and different eras.
+
+Even later New York codes can be considered a separate family.
+In 1876 a New York commission produced a new code attempting to consolidate all the statutory amendments subsequent to the 1851 Field Code.
+David Dudley Field was upset by the changes introduced in this revised code, called the Throop Code.
+A count by a "friend" of Field's found that only three sentences of the Field Code had carried over word-for-word into the Throop Code.
+Nevertheless, many of the changes were purely formal, and Field speculated that these changes had been made only "so that \[the Code\] should not appear to be the same thing as before." With respect to Mr.
+Field or his "friend," we were able to find that the connection was between the Throop Code and the Field Code was somewhat stronger than he thought, and the Throop Code was indeed a descendant, if much revised, from the Field Code.
+
+Finally, our corpus included a number of statutes which stood outside the Field Code tradition, such as Virginia and West Virginia regulations, statutes from Massachusetts and Maine, and southern codes from Georgia to Louisiana.
+These statutes show that the dominance of the Field Code was not total, and a number of older jurisdictions remained outside of its ambit.[^41] But virtually every jurisdiction established or reconstructed after 1850 became a part of the the Field Code network, and no other tradition achieved anywhere near the same coherence across state lines.
+
+We have so far discussed code to code borrowings which give us a macroscopic view of the corpus as a whole.
+But because the fundamental unit of comparison is section to section, it is possible to get a more detailed look at the kinds of borrowings that codes made of one another, by looking at each section in a code and seeing which other code it was borrowed from.
+These visualizations show how each code was put together.
+Codes at different removes from New York tended to have different patterns of borrowing.
+To illustrate this, we will follow one branch of the Field Code network, beginning with the family started by California's 1851 code.
+
+<!-- ![](media/image04.png){width="6.5in" height="3.7916666666666665in"} -->
+California's 1851 code borrowed heavily from two sources.
+The bulk of the code was taken directly from New York's 1849 or 1850 codes (which are difficult to distinguish exactly from one another.[^42] The remainder of the code was borrowed from California's 1850 code.
+The 1850 version was in turn borrowed from the New York codes \[**might as well show this, esp.
+since CA1850 is so impressive**\].
+As we would expect, the bulk of the borrowings that come from California instead of directly from New York are at the beginning of the code, where the 1850 code had made amendments specific to the borrowing from California.
+(Many of the non-matching sections are tables of contents.) The main point is that that the majority of the code was lifted more or less directly from New York, with minor amendments specific to California.
+California made few to no innovations to the Field Code beyond a rearrangement of its provisions.
+
+<!-- ![](media/image05.png){width="6.5in" height="4.291666666666667in"} -->
+The pattern of borrowings in the Washington 1855 code was a rather different case.
+The Washington code was definitely in the lineage of the 1851 California code, since it borrowed sections from both California directly and from Oregon, which was derived from California.
+While there are a number of "other" sections, the pattern of borrowing is clear: Indiana's 1852 code and Oregon's 1854 code provide the majority of the borrowings.
+Those two contiguous bands of borrowings correspond to regulations on judgement from Oregon and enforcement provisions from Indiana.
+This pattern likely came about because one of the Washington code commissioners, Edward Lander, was an Indiana appellate judge from 1850 to 1853, while another commissioner, William Strong, was a justice of the Oregon Supreme Court in the same years.
+While working on the Washington code, they must have each used the law (and the law books) that they knew best.
+As a second generation variation on a regional code, the Washington code drew from different sources.
+
+Finally, we can consider the case of Washington's revised 1873 code as an example of one of the last "leaves" on the family tree of the Field Code.
+The bulk of this code was lifted from the Washington 1855 code with only small amendments.
+The main exception was a probate code drawn from California's 1872 code.[^43] Like many of the last generation codes, the text of the procedure code had stabilized in a local manifestation of a regional tradition.
+The code was still genuinely a Field Code, with a great deal of similarity to the original New York Field Codes, but its specific form depended on the many edits and rearrangements that state code commissioners had made to the text.
+
+<!-- ![](media/image03.png){width="6.5in" height="4.666666666666667in"} -->
+So far we have retained the context of the surrounding sections within a particular code.
+But since our fundamental unit of comparison is section to section, we can use a technique called clustering to deform the texts (as a literary scholar might say) in order to see the textual history of how particular regulations embedded in individual sections changed over time.[^44]
+
+We used a clustering algorithm to group related sections together.
+Clustering is the process of taking a set of objects (in this case, sections of the field codes) which have distances between one another (in this case, the Jaccard similarity is easily converted into a distance measure), and grouping items which are are most alike together.
+There are innumerable clustering algorithms, but we needed one that could work with a sparse matrix and one whose assumptions matched the characteristics of our problem.
+We decided to use affinity propagation clustering.[^45] That algorithm assumes that each cluster has an "exemplar" item which the other items are similar to.
+That assumption fits nicely with borrowings from the Field Code, where a single section (likely from the 1850 New York code) had many borrowings, but where there could also be innovative sections in other stages.[^46]
+
+The result was a set of approximately 2,900 clusters which contained at least five sections, though this probably overstates the number of innovative, *ur*-sections in the corpus.
+Each cluster contained a list of the section that belonged to it.
+The biggest cluster, for instance, which concerned the use of affidavits in pleading, contained 103 sections.
+With those clusters, we were able to organize the documents chronologically.[^47] This method is particularly useful when tracking the variations in in the law from jurisdiction to jurisdiction.
+It provides historians with a way of noticing small changes in the wording and substance of the law.
+Most discussions of algorithmic reading have focused on "distant reading,"[^48] or have balanced the claims of distant reading by using it as a means to enable close reading.
+This method of clustering, however, is a kind of algorithmic close reading.
+By deforming the texts---taking them out of the context of the codes and putting them in the context of their particular variations---we are able to pay attention to those variations.[^49]
+
+Take for instance, provisions regulating witness testimony.
+At common law, parties and interested witnesses were not permitted to testify in their own causes.
+Field's Code reversed this rule, expanding witness competency as widely as possible: any person "having organs of sense" could now be admitted as a witness in New York, with only the insane and very young children exempted from the rule.
+As the Code migrated West, however, legislators added racial exclusions to Field's list.
+The following cluster documents how California's codifiers engrafted earlier prohibitions from midwestern states into Field's Code.
+Many other codes then evidence a remarkable uniformity with California's text (which later changed only to add "Mongolian" to the list of races).
+Iowa's Code had much more minor influence, and Wyoming developed the only truly original section which made clear the link to a racist assumption of infantilization of non-white peoples.
+\[**Figure: Cluster from Kellen**\]
+
+As these clusters illustrate, uniformity can be just as instructive as variation.
+On the point, the most significant clusters that we investigated related to the collection of debts.
+These were clusters which went against the typical pattern that we observed.
+While many clusters exhibited regional variation as they grew more distant from the Field Code, clusters having to do with creditors' remedies were almost completely uniform across the American West and South.
+No single section of the Code announced its preference for creditors' rights; rather, the acceleration of creditors' remedies resulted from the combination of several sections.
+In the original enacted Code, § 107 required a defendant to answer the complaint within twenty days, instead of at the next court session (which in some cases could have been as far as three months away); § 202 provided for default judgment as a matter of course, issued by a clerk without a judicial order if no adequate answer was received within the twenty days; §§ 128-133 abolished fictitious pleadings and required answers to state true facts verified by a defendant's oath, all so that no trial would delay the enforcement of uncontestable obligations; finally, the Code abolished a traditional thirty-day waiting period between issue of judgment and commencement of execution (see First Report (New York 1848), 197).
+These provisions dealt with what merchants and capitalists perceived as an abuse of the common law system, where defendants in cases of debt could stretch out enforcement of debt collection for as long as two years.
+The Field code's summary judgment brought down the time of debt collection to a matter of weeks.
+Effectively, the Code traded the rhythms of agriculture for the rhythms of merchant finance.[^50]
+
+Clustering each of these sections reveals that western states along with the former Confederate states of South Carolina, North Carolina, and Florida copied each provision almost exactly.
+Midwestern and Upper South states that had already developed by 1850 and maintained commercial ties to Chicago and New Orleans varied the New York rules, sometimes by requiring answers only in term time, or permitting only a judge to decree default judgment rather than a clerk, in either case effectively stretching out enforcement and making a formal trial more likely.
+But in the Reconstruction South, and in the West over the same period, regardless of whether a jurisdiction abolished chancery or not, regardless of the racial exclusions it may have placed on witness testimony, the provisions on debt collection remained unchanged.
+When it came to creditors' remedies, the law of New York became the law of the land.
+
+**Part 4**.
+
+Alerted by these clustering patterns to the significance of creditors' remedies in the developing West and re-developing South, it was not difficult to find evidence of westerners and southerners commenting on these features of the Code or its connections to New York capital.
+Twelve of the states and territories that copied the Field Code mostly closely did so during the Civil War and Reconstruction era---four states in the former Confederacy and eight jurisdictions in the Far West.[^51] As with other areas of postbellum historiography, it turns out one may learn a lot by holding the postellum American South and American West together.
+
+In the last decade, scholars of Reconstruction have broadened the scope of their study to include both the South and the West as two sites in one "Greater Reconstruction." These studies have illustrated the ways that military conquest, rapid industrialization, and the resettlement and education of ethnic minorities developed similarly in each region, guided by economic elites in New York and political administrators in Washington.[^52] In tracing the legal aspects of this Greater Reconstruction, scholars have focused almost entirely on constitutional rights of citizenship and civil equality or the expansion of federal power.[^53] While the 1860s and 1870s were of course a transformative period in the history of civil rights and the creation of a national state, they were also the decades in which many local legal institutions and practices were transformed not by federal power but by state codification.
+Naomi Lamoreaux and John Joseph Wallis have recently argued that in the creation of a modern American economy, "the federal government played *no* role in this process until the Civil War, and even then it played only a bit part." The history of the Field Code's migration helps to substantiate this claim.
+While Lamoreaux and Wallis focus on the development of banking, transportation, and incorporation at the state level, it was the Procedure Code that provided the structure of civil remedies that protected these state institutions.
+And procedure codes were, of course, the creatures of state governance.[^54]
+
+With the universal complaints that time was too short or commissioners too democratically irresponsible, one might expect the Code to have faced more competition from other workable statutes.
+Southern states that drew more on the civilian code tradition such as Louisiana and Alabama offered other options for states desiring to reform common law practice.[^55] And if Euro-Americans believed law had to be imported into the West, Colorado immigrants proved that the common law of Illinois was just as amenable to statutory importation as New York law.[^56] But what codifiers saw when they looked at New York, more so than Louisiana, Alabama, or Illinois, was the Empire State of commercial capital.
+And the putative fears, demands, and desires of a personified Capital continually wielded promises---and threats---in the debates over procedural codification.
+The early Mormon settlers of Utah persistently avoided the mining frenzy as well as codification.
+By 1870, however, the territory's governor directed the legislature's attention to the recent Code of Nevada, a code "for a people whose interests in many respects are similar to our own." Of course, standing behind the Nevada Code was "the State of New York---a State which is an empire in itself and whose commercial transactions are far greater than those of any other State in the Union." By copying its code, Utah too could be "rewarded by equal advantages."[^57] Code proponents in Colorado similarly parried arguments that a code would be a "foreign" imposition by pointing to the fact that it has been "adopted twenty-nine years ago by the Empire state of the Union" and they promised that the code of the nation's uniquely commercial empire could bring wealth in its wake.[^58]
+
+When a Colorado legislator scoffed at the idea that capitalists could possibly care about the difference between old common law and modern code remedies, his adversaries rebuked him.
+"Mr.
+Hamill replied that he knew of one California company of capitalists who were deterred from investing in mining property here wholly on account of the practice of the courts in mining cases.
+If we had had this code years ago, Colorado would now have a larger amount of California capital in her mines."[^59] Codifiers argued that, in attracting capital, procedure was at least as important as the substantive rules of property and contract, because procedure secured the remedies that actually protected investments.
+"Men of capital and enterprise will not make investments and devote their time and energies to those works of internal improvement so necessary for the speedy development of our natural resources, and for the settlement and building up the country," Nebraska's governor reasoned, "unless ample protection is afforded them, by legal enactment, for the capital invested and labor employed." And he therefore urged swift passage of the Field Code.[^60]
+
+Receiving innumerable letters complaining that under the Code, "no one will be benefited, except perhaps some Northern Capitalists," a North Carolina commissioner undertook an anonymous defense of the new Code in the *Weekly Standard*.
+He encouraged the bar to accommodate themselves to change, for "the New York system .
+.
+.
+bids fair to become national." Putatively offering an overview of the Code, the articles were almost entirely about credit.
+"How can we create credit?
+By punctuality," the commissioner wrote.
+"And how create punctuality?
+by law, and by law alone.
+Let the law enforce punctuality; let the people of North Carolina learn that the great law of business is, that 'time is of the essence of the contract,' and incur no debt that they do not expect to meet at maturity." Under the more certain and speedy remedies of the Code, "we may expect that the secret hoards of the frugal among ourselves will be offered to loan, and even that the vaults of the banks of New-York .
+.
+.
+will be open to our industry."[^61]
+
+As in postbellum North Carolina, establishing a flow of credit through the remedial system became a leading priority of western lawyers.
+While the so-called new western history has shed significant light on neglected topics of Indian dispossession and environmental management, it has often done so by leaving out of view matters of political economy, a staple of the old western history.
+As one work in that older tradition argued, "Debt collection was the central part of law practice for the \[western\] bar and remained a key part of private practice throughout the century."[^62] On that understanding, one western lawyer succinctly summarized the difference between the Code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, .
+.
+.
+that he did not also break out somewhere with 'take for instance the case of an action on a promissory note,' as though the collection of notes was about all there could be any law needed for."[^63]
+
+The creditors' remedies in the Code gave the codifiers their leading argument against criticisms rooted in the ideology of popular sovereignty.
+"There is no doubt but the people are in favor of anything that promises to hurry up that proverbially slow and blind old female called Justice, and they will go for the old code," one Colorado newspaper announced.[^64] New York's "code practice is the best in excellence," stated another, "and when I say *best* I do not mean best for lawyers only, but best for the people---the commonwealth."[^65] If the People favored economic progress, certainty of remedy, and efficiency in proceedings, then they favored the New York Code, no matter whether they understood or cared about technical rules of pleading and joinder.
+Thus, in their arguments the codifiers imagined themselves the champions of popular sovereignty, for it was they who accomplished what the People actually desired.
+
+Thus by the end of Reconstruction, New York's domestic empire of capital and creditors' remedies bore a remarkable resemblance to the international empire administered by England.
+Both jurisdictions, while reforming the practice of law, largely rejected codification within their own borders but encouraged it among their economic dependents.
+The English commissioned a full codification of law for India and colonies in Singapore, while further codifications produced by Field in New York covering civil and penal law were adopted in California and other western jurisdictions.[^66] In both places, leading arguments against codification carried a civilizational logic of empire: Advanced societies could not codify their law, for to do so would be to freeze the progress of legal science.
+What appeared to some to be a hopeless mass of confusion was to common law defenders the sign of true legal sophistication.
+Science was, after all, sophisticated.[^67] The Throop Code came in for censure, both in its first year and in following decades, precisely for trying to capture all the sophistication of the New York legal system within an unwieldy 3,300 rules.[^68] Codification, however, could help developing societies along law's frontier take a progressive leap forward.
+As India's chief codifier Thomas Macaulay explained, codification "cannot be well performed in an age of barbarism," but also "cannot without great difficulty be performed in an age of freedom." As India balanced between the two, however, "it is the work which especially belongs to a government like that of India---to an enlightened and paternal despotism."[^69]
+
+In America, Macaulay's tool of enlightened despotism spread with the anxiety that capital from the nation's economic center would remain scarce without a Code of remedies that, if not in fact the law of New York, was at least prescribed by New York lawyers and their corporate clients.
+In the two most populous and commercially advanced western states, Texas and Illinois, the need for New York capital failed to move state legislators to adopt the Code at the expense of popular sovereignty (although there were concerted efforts in both jurisdictions).[^70] Lacking the self-sufficiency of those two jurisdictions, the other states of the Greater Reconstruction in America adopted a foreign Code, but lawyers, legislators, and their supporters claimed the endorsement of popular sovereignty in doing so.
+Even in North Carolina, whose Democratic newspapers daily called for the repeal "this child of the carpet baggers," Republican editors proclaimed that "the movement" towards procedural codification "comes from the people, from the instinctive logic by which an unprejudiced mind grasps the advantages of the system."[^71]
+
+**Conclusion**
+
+By framing our historical questions around "medium data" we enjoyed a useful symbiosis of traditional and digital historical methods.
+Our computational methods produced useful historical knowledge because they were justified by what we knew about the data from traditional historical work.
+We knew that code commissioners worked with "the scissors and paste-pot," as critics complained, and we knew of codes in the archives that commissions literally marked up the legislation of other states.
+While we think that one of the most useful things about digital history is its ability to start with large corpora and then figure out what was interesting from the past, we have shown how digital history can function by starting with particular questions rather than particular sources.
+We have shown how a collection of methods from computer science, including minhash/locality-sensitive hashing, affinity propagation clustering, and network analysis, along with the concept of text deformance from literary history, can be used to good effect in tracking the changes in the law, as well as any other discursive field whose texts can be readily divided into sectional units.
+Finally we have shown how it is possible to work on different scales, using network analysis and algorithmic close reading, and thus to get both a macroscopic picture of the law's migration, as well as a highly detailed view of the changes in the law.
+
+The history of codification on the American periphery troubles cherished notions of American federalism.
+On the one hand, those suspicious of centralized power and critical of national governance since the New Deal have relied on narratives that tout the equality of sovereign states to set their own policies, foster local diversity, and "experiment" with legislative solutions to local issues.[^72] But the history of legal practice and civil remedies is one in which the localism fostered by common law practice rapidly gave way to uniform regulations transmitted by a network of New York lawyers without the slightest interference of the federal government.
+On the other hand, scholars who support the legitimacy of New Deal governance have recently produced an abundant literature unearthing a long tradition of "administrative" law at the state level well before the twentieth century.
+These accounts have focused on administrative adjudication or discretionary regulation within a narrow domain, such as customs houses.[^73] These histories have so far neglected the most widespread and significant instance of nineteenth-century administrative lawmaking in America---the spread of the Field Code through extra-legislative commissions.
+While these histories have sought to demonstrate that Americans from early on could be quite comfortable with administrative law and accepted it as a normal part of the constitutional order, this chapter has shown how lawmaking by commission generated significant political controversy and raised grave questions about popular sovereignty under such delegations, questions that over time were merely dodged rather than answered.
+
+In the economically developing West and re-developing South, anxieties over the lack of capital---both among the bar as well as lay voters---joined with arguments of civilization and progress to spur many jurisdictions to copy the text of the Code of New York, the Empire State of capital.
+The short time horizons of American lawmaking limited the options available for reimagining or recrafting what could become the law of remedies and legal practice.
+And in the economically underdeveloped parts of the country, time horizons could be short indeed.
+Capital might quickly pass over one region and favor another, and each month more lawyers arrived hoping to make a start in a jurisdiction where economic progress was just about to take off.
+
+This study thus gets at the heart of lawmaking in U.S.
+history.
+Lawyers and judges, politicians and newspaper editors warred over whether codes that were drafted by commissioners and borrowed wholesale from beyond a jurisdiction's borders were actually democratic.
+Codifiers responded by transmuting democratic theory into support for a remedial code elected legislators had neither the time nor inclination to read.
+Popular support for commercial development was taken to indicate popular support for New York's civil remedies, especially the cheapened and accelerated collection of debts.
+In many jurisdictions the exact language of the Field Code remains on the books, and its basic provisions for civil procedure are in force throughout the United States.
+Without too much exaggeration we might say that our method has revealed the spine of modern American legal practice.
+
+[^1]: Message of the Governor, in Journal of the Council for the Territory of Nevada (1862), 21.
+
+[^2]: Nevada Council Journal (1862), 261-62. Act of Congress (1861) Organizing the Territory of Nevada, 12 U.S. Statutes at Large 209-14 (1863). 1861 Nevada Laws 314.
+
+[^3]: Besides his work on codification, which extended to civil, penal, and even international codes of law, Field became renown for his trial advocacy.
+Field argued the winning side in major Reconstruction cases such as *Ex Parte Milligan*, 71 U.S.
+(4 Wall.) 2 (1866) (holding the trial of civilians by military commission unconstitutional), *Cummings v.
+Missouri*, 71 U.S.
+(4 Wall.) 277 (1867) (striking a loyalty oath as unconstitutional), and *United States v.
+Cruikshank*, 92 U.S.
+542 (1875) (enforcing the Fourteenth Amendment only against "state action").
+Field came under heavy censure for his representation of Gilded Age robber barons like Jay Gould, Jim Fisk, and William "Boss" Tweed, but even Tweed's chief adversary Samuel Tilden retained Field's services for the disputed election of 1876.
+See Henry Martyn Field, *The Life of David Dudley Field* (1898); Philip J.
+Bergan, "David Dudley Field: A Lawyer's Life," in *The Fields and the Law* (New York: Federal Bar Council, 1986).
+
+[^4]: *Rocky Mountain News*, January 20, 1877.
+
+[^5]: Roscoe Pound, "David Dudley Field: An Appraisal," and Alison Reppy, "The Field Codification Concept," in Alison Reppy, ed., *David Dudley Field: Centenary Essays* (New York University School of Law, 1949); Stephen Subrin, "David Dudley Field and the Field Code: A Historical Analysis of an Earlier Procedural Vision," 6 *Law & Hist.
+Rev*.
+311 (1988); Robert G.
+Bone, "Mapping the Boundaries of a Dispute: Conceptions of Ideal Lawsuit Structure from the Field Code to the Federal Rules," 89 *Colum.
+L.
+Rev*.
+1 (1989).
+See also the literature on procedure and codification cited below.
+
+[^6]: When law professors such as New York's David Graham Jr.
+(a collaborator on the Field Code) began to be appointed to university positions, the chair for instruction in legal practice or procedure carried this designation of "practice and pleadings." Today that field is described as "civil procedure" a field that grew out of David Dudley Field's codification, as described below.
+The history of practice and procedure is a staple of general legal history.
+See Frederick Pollock and Frederick Maitland, *The History of English Law Before the Time of Edward I* (2d.
+ed., Cambridge, 1898), 2 vols.; Theodore Plucknett, *A Concise History of the Common Law* (5th ed.
+2010); Lawrence M.
+Friedman, *A History of American Law* (3d.
+ed.
+2005).
+Few book-length works have been dedicated to the subject, however.
+The exceptions are Robert Wyness Millar, *Civil Procedure of the Trial Court in Historical Perspective* (New York University School of Law 1952); Edward Purcell, *Litigation and Inequality: Federal Diversity Jurisdiction in Industrial America, 1870-1958* (Oxford 1992); John H.
+Langbein et al., *History of the Common Law: The Development of Anglo-American Legal Institutions* (Aspen 2009); and to some extent, William E.
+Nelson, *The Americanization of the Common Law: The Impact of Legal Change on Massachusetts Society, 1760-1830* (2d.
+ed., University of Georgia Press 1994).
+
+[^7]: For the rise of treatises in America generally, see G.
+Edward White, *The Marshall Court and Cultural Change, 1815-1835* (1988) and A.W.B.
+Simpson, "The Rise and Fall of the Legal Treatise: Legal Principles and the Forms of Legal Literature," in *Legal Theory and Legal History: Essays on the Common Law* (1984), 273.
+The most instructive treatises for New York practice in the 1840s were Oliver L.
+Barbour, *A Treatise on the Practice of the Court of Chancery* (1844); Alexander M.
+Burrill, *Treatise on the Practice of the Supreme Court of the State of New York* (1846), 2 vols.; David Graham, *A Treatise on on the Practice of the Supreme Court of the State of New York* (3d.
+ed.
+1847); David Graham, *A Treatise on the Organization and Jurisdiction of the Courts of Law and Equity in the State of New York* (1839); Claudius L.
+Monell, *A Treatise on the Practice of the Supreme Court of the State of New York* (1849); Joseph W.
+Moulton, *The Chancery Practice of the State of New York* (1829), 2 vols.; and as a general introduction to the field, the Englishman Henry John Stephen's *Treatise on the Principles of Pleading in Civil Actions* (2d.
+ed.
+1828).
+
+[^8]: See Michael Lobban, *The Common Law and English Jurisprudence 1760-1850* (Clarendon Press 1991); Kunal M.
+Parker, *Common Law, History, and Democracy in America, 1790-1900: Legal Thought before Modernism* (Cambridge: Cambridge University Press, 2011); David M.
+Rabban, *Law's History: American Legal Thought and the Transatlantic Turn to History* (Cambridge 2013).
+
+[^9]: Or, to use a term from contemporary analysis, "super statutes." William N.
+Eskridge and John Ferejohn, *A Republic of Statutes: The New American Constitution* (New Haven: Yale University Press, 2010).
+See also David Lieberman, *The Province of Legislation Determined: Legal Theory in Eighteenth-century Britain* (Cambridge 1989); Farah Peterson, Statutory Interpretation and Judicial Authority, 1776-1860 (Ph.D.
+dissertation, Princeton University, September 2015).
+
+[^10]: Friedman, *A History of American Law*, 302.
+When the intellectual historian Perry Miller developed a reader surveying *The Legal Mind in America*, codification was its only central theme, as Miller argued it was the one intellectual topic that attracted lawyers away from their practices long enough to debate.
+Perry Miller, ed., *The Legal Mind in America: From Independence to the Civil War* (Anchor 1962).
+See also Charles M.
+Cook, *The American Codification Movement: A Study in Antebellum Legal Reform* (1983); Robert W.
+Gordon, "The American Codification Movement," 36 *Vanderbilt Law Review* 431 (1983); Maurice Eugen Lang, *Codification in the British Empire and America* (Lawbook Exchange 1924).
+On common theories of codification that transcended jurisdictional boundaries, see Csaba Varga, *Codification as a Socio-Historical Phenomenon* (Budapest, 2d.
+ed.
+2011 \[1991\]); Roger Berkowitz, *The Gift of Science: Leibniz and the Modern Legal Tradition* (Fordham 2010).
+
+[^11]: The most influential account has been Morton Horwitz's, which declares that "the desire to separate law and politics has always been a central aspiration of the American legal profession" in order to protect elite interests against popular democracy.
+Horwitz identifies "orthodox legal thought" and "orthodox lawyers" with the elite of the American bar who sought to shield the law from political interference, which above all meant crusading against legislation and especially codification.
+Morton J.
+Horwitz, *The Transformation of American Law, 1780-1850* (Oxford University Press, 1977), 258-59.
+Recent work has challenged Horwitz's account by showing how elite common law lawyers, particularly Horwitz's main target James Coolidge Carter, were actually political progressives who supported redistributive legislation such as the income tax.
+See, for instance, Rabban, *Law's History*, 322-77; Parker, *Common Law, History, and Democracy*, 230-41; Lewis A.
+Grossman, "James Coolidge Carter and Mugwump Jurisprudence," *Law & History Review* 20 (2002).
+These accounts follow Horwitz, however, in focusing on the few outspoken opponents of codification, rather than the elite lawyers who sponsored the procedure codes.
+Among the latter group could be found some of the most devout theorists of laissez faire economics in nineteenth-century America, including David Dudley Field and his brother, the Supreme Court Justice Stephen Johnson Field.
+
+[^12]: James Fenimore Cooper, *The Ways of the Hour: A Tale* (1850), 84.
+For an analysis of Cooper's philosophy of law and his critique of the New York constitution, see Charles Hansford Adams, *"The Guardian of the Law": Authority and Identity in James Fenimore Cooper* (Penn State University Press (1990), 135-48.
+See also Marvin Meyers, *The Jacksonian Persuasion: Politics and Belief* (Stanford 1957), 57-100.
+
+[^13]: On the politics and reforms of the New York Convention of 1846, see Charles Z.
+Lincoln, *The Constitutional History of New York from the Beginning of the Colonial Period to the Year 1905* (Rochester 1905), 2:10-101; Charles McCurdy, *The Anti-Rent Era in New York Law and Politics, 1839-1865* (University of North Carolina 2001); Jed Shugerman, *The People's Courts: The Rise of Judicial Elections and Judicial Power in America* (Harvard University Press 2012).
+
+[^14]: Count Pierre François Réal to William Sampson, October 27, 1824, in Sampson's Discourse and Correspondence with Various Learned Jurists Upon the History of the Law (1826), 191; Maxwell Bloomfield, "William Sampson and the Codifiers: The Roots of American Legal Reform," 11 *American Journal of Legal History* 234 (1967); Walter J.
+Walsh, "William Sampson, a Republican Constitution, and the Conundrum of Orangeism on American Soil, 1824-1831," 5/7 *Radharc* 1 (2006); William Sampson, *Memoirs* (2d.
+ed., 1817).
+On French-style codifications, see Robert B.
+Holtman, *The Napoleonic Revolution* (Louisiana State 1981); R.
+H.
+Kilbourne, *A History of the Louisiana Civil Code* (Paul M.
+Herbert Law Center 1987); Brian Young, *The Politics of Codification: The Lower Canadian Civil Code of 1866* (Osgoode Society 1994); John W.
+Cairns, *Codification, Transplants, and History: Law Reform in Louisiana (1808) and Quebec (1866)* (Talbot 2015); Roscoe Pound, "The French Civil Code and the Spirit of Nineteenth Century Law," 35 *Boston Law Review* 79 (1955).
+
+[^15]: Thomas J.
+Lockwood, "A History of Royal Commissions," 5 *Osgoode Hall Law Journal* 172 (1967); Barbara Lauriat, "'The Examination of Everything': Royal Commissions in British Legal History," 31 *Statute Law Review* 24 (2010); Joanna Innes, *Inferior Politics: Social Problems and Social Policies in Eighteenth-century Britain* (Oxford 2009).
+
+[^16]: Second Report of the Commissioners on Practice and Pleading (New York 1849), 3-4.
+See also, First Report of the Commissioners on Practice and Pleadings (New York 1848), iii-iv; Third Report of the Commissioners on Practice and Pleadings (New York 1849), 3, Lillian Goldman Law Library Rare Books Collection; Final Report of the Commissioners on Practice and Pleadings, in Documents of the Assembly of the State of New York, 73d sess., vol.
+2, no.
+16 (New York 1850), viii.
+
+[^17]: Report of the Commissioners on Practice and Pleadings, in New York Assembly Documents, 70th sess., vol. 2, no. 202 (1847), 3-4.
+
+[^18]: Working under this theory, the Field commission defined the content of the modern field of *civil procedure*.
+While western legal systems had long distinguished between the law of persons and things on the one hand, and the law of actions (the rules of litigation) on the other, in the Anglo-American tradition, the categories remained intermixed into the nineteenth century.
+Whether one had a substantive legal right (to property, to marry, to an office, etc.) depended upon whether and how one would sue for a remedy to vindicate that right.
+Blackstone's *Commentaries* attempted to describe English law in the more European terms of persons/things/actions, and Jeremy Bentham offered a more refined terminology of "substantive" law and "procedural" or "adjective" law, but until the Field Code no Anglo-American jurist had specified with precision where the line lay between substantive and procedural law.
+See Lobban, *The Common Law and English Jurisprudence*, 127-131, 146-151.
+As Amalia Kessler notes, *Bouvier's Law Dictionary* did not even define *civil procedure* until its 1897 edition, describing the term as "rather a modern one." Amalia Kessler, "Deciding Against Conciliation: The Nineteenth-Century Rejection of a European Transplant and the Rise of a Distinctively American Ideal of Adversarial Adjudication, 10 *Theoretical Inquiries in Law* 423 (2009), 481-482; *Bouvier's Law Dictionary* (1897), 2:764.
+Before 1848, the term was largely restricted to French usage, and American remedial law had carried the typical designation---as it did both in Graham's treatise and professorial title---of "practice and pleadings," the name likewise given to the reform commission.
+When the commission designated its final draft a "Code of Civil Procedure," it marked the first American attempt to give content to this category.
+
+[^19]: Final Report of the Commissioners, 368-378, tit.
+10.
+See also Peter Karsten, "Enabling the Poor to Have Their Day in Court: The Sanctioning of Contingency Fee Contracts, A History to 1940," 47 *DePaul Law Review* 231 (1998); Norman Spaulding, "The Luxury of the Law: The Codification Movement and the Right to Counsel," 73 *Fordham Law Review* 983 (2004) John Leubsdorf, "Toward a History of the American Rule on Attorney Fee Recovery," 47 *Law and Contemporary Problems* 9 (1984).
+
+[^20]: On debt collection, see Part 4 below.
+On homestead exemptions, see Final Report of the Commissioners, 353-354, § 839; James W.
+Ely, "Homestead Exemption and Southern Legal Culture," in Sally Hadden & Patricia Minter eds., *Signposts: New Directions in Southern Legal History* (University of Georgia 2013), 289-314; Paul Goodman, "The Emergence of Homestead Exemption in the United States: Accommodation and Resistance to the Market Revolution, 1840-1880," 80 *Journal of American History* 470 (1993).
+
+[^21]: Final Report of the Commissioners, 202-203, § 506 (restricting admission as an attorney to male citizens), 110, § 251 (restricting jury service to white male citizens), 714-715, § 1708 (permitting "all persons, without exceptions" to be witnesses in civil cases).
+
+[^22]: On the French procedure code, see C.H.
+van Rhee, *European Traditions in Civil Procedure* (Antwerp 2005).
+Bentham, the leading proponent of codification in England, argued that procedure was the one department of the law that ought to remain *un*codified.
+So long as the law of civil and criminal obligations and the law of property were sufficiently codified, a "natural procedure" arising from judicial discretion and flexibility would be superior to "technical" written rules.
+Later in his career Bentham produced the "Outlines of a Procedure Code" as a "provisional" remedy, but he insisted that a procedure code on its own could not be "invested with the form of law" without "reference to the codes of law, penal and non-penal, to which it has for its object and purpose the giving execution and effect." Although it spanned nearly 200 pages, Bentham's code favored general moral maxims over precise details, for instance: "On each occasion, have constant regard for all the several ends of justice; that is to say, minimize the sum, or the balance of evil." Jeremy Bentham, Principles of Judicial Procedure with the Outline of a Procedure Code, in John Bowring, ed., *Works of Jeremy Bentham* (2d.
+ed.
+1843 \[1839\]), 1-189, preface and 28, ch.
+7 § 1.
+See Lobban, *The Common Law*, 127-131.
+
+[^23]: See Revised Statutes of the State of Indiana (1852), 2:245-320 (wills); Public Statutes of the State of Minnesota (1859), 643-647, ch.
+75 (mortgages); The Code of Civil Procedure of the State of California (1880), 419-420, tit.
+6, 657-659, art.
+5 (corporations).
+
+[^24]: Report of the Code Commissioners to the Eighth General Assembly of the State of Iowa (1859), 296, note to § 172 ("The right to sue, follows necessarily from the right of property.") On the significance of the Married Women's Property Acts, see, e.g., Hendrik Hartog, *Man and Wife in America: A History* (Harvard 2000), 111-113, 187-192, 290-292.
+
+[^25]: First Report of the Commissioners, iv. For legislative debates on the Code, see "Legislative Acts and Proceedings," *Albany Evening Journal*, Mar. 31, 1848.
+
+[^26]: Report of the Committee on the Judiciary on the Bill to Continue in Office the Commissioners on Practice and Pleadings, in New York Assembly Documents, 72d sess., vol.
+3, no.
+47, (New York 1849), 2, 12-15.
+
+[^27]: Final Report of the Commissioners, 225-226, § 554.
+For examples of "codes" that did not alter previously enacted statutes, see, for instance, Report, Appendix to the Journals of the Senate and Assembly of the State of Tennessee (1857), 191 ("The digest presents the law substantially as it now exists in the State.
+I have neither felt at liberty nor deemed it advisable to innovate largely upon the established system."); 1897 New Mexico Compiled Laws 9 ("The commissioners were given no authority to revise."); 1866 Illinois Compiled Laws v ("We cannot change the text, but we can arrange and systematize the entire legislation of the state upon any given subject."); 1849 Wisconsin Revised Statutes, "Advertisement" (commission "directed the subscriber to arrange the chapters into parts and titles as he thought proper, re-arranging the order of the sections or transposing them from one chapter to another, whenever it would not alter the meaning of the law.").
+
+[^28]: *Montana Post*, January 21, 1865.
+
+[^29]: *The Miner's Express* (Dubuque), February 26, 1851.
+
+[^30]: Full citations to all of the codes that we used, plus links to electronic versions at the Hathi Trust, Google Books or other sources when available are available at Kellen Funk, \*American Legislation Project\*.
+
+[^31]: On this point, see Stephen Robertson, Debates in DH piece. As an example of digital historical work that is likewise aimed at exploring a dataset {RETHINK} see Cameron Blevins, spatial article.
+
+[^32]: Examples of big history include Historian's Macroscope. Cite Underwood fiction corpus; Jockers' on Macroanalysis and Moretti on Big Reading, Culturomics, Ben Schmidt.
+
+[^33]: Though somewhat overstated, see Cameron Blevins, Debates in DH.
+
+[^34]: **Note codes pulled from HeinOnline and three codes transcribed by hand**.We favored public domain sources where available both for reasons of efficiency (large statute books download much more quickly from Google's servers than from subscription databases) and reproducibility (most of this project can be replicated without subscription databases).
+In each instance we downloaded an entire volume of sessions laws, statutory compilations, or single-volume codes of procedure and then cropped out irrelevant pages, marginalia and footnoted commentary, leaving only the statutory text.
+After several trials of various implementations of Tesseract (open source) and I.R.I.S.
+(proprietary) OCR programs, we determined that Nitro Pro PDF, which relies on I.R.I.S.
+software, offered the best OCR tool for this project.
+I.R.I.S.
+provides slightly more accurate readings of nineteenth-century typefaces than Tesseract, and Nitro Pro's implementation makes words, not characters, the fundamental unit of output.
+The latter feature made cropping between marginalia and the statute more reliable.
+We programmatically removed hyphenated line breaks and standardized spelling for common terms that evolved over the nineteenth century (e.g., *indorsement*).
+
+[^35]: Cf. Hay & Craven, AJLH article
+
+[^36]:
+
+[^37]: **Code citations and literature on West as a legal void**.In practice, there are also variations in the texts due to numbering or minor OCR errors as well as actual changes. These differences
+
+[^38]: This algorithm works by extracting a set number of random tokens from each document, allowing the documents to be represented uniformly and compactly.
+Then those random tokens are grouped into subsets.
+If any two documents have a matching subset, then they are considered a candidate pair.
+\[**CLARIFY**\] This algorithm has several useful properties.
+It approximates the Jaccard similarity of the two documents.
+It requires a computation for each document rather than each pair of documents, so the computation time grows linearly not geometrically.
+And by controlling various parameters, one can set a threshold similarity score above which one is likely to find a genuine match and unlikely to find a spurious match.
+
+[^39]: This matrix required filtering based on what we knew about the process of borrowing.
+We removed any match below a threshold that we determined by reading pairs of matches.
+We had to remove anachronistic matches; for instance, a code from 1851 obviously did not borrow from a code from 1877.
+Furthermore, in chains of borrowing (e.g., NY1850 → CA1851 → CA1868 → CA1872 → MT1895) the latest section might have a high similarity to all of its parents, but it was in fact borrowed only from the most recent parent.
+We therefore filtered the similarity matrix to remove matches within the same code; anachronistic matches; spurious matches beneath a certain threshold.
+Then if a section had multiple matches, we kept the match from the chronologically closest code, giving preference to codes from the same state, unless there was a substantially higher match from a different code.
+
+[^40]: This is obvious from the visualization, but also confirmed by all measures of centrality used in network analysis.
+A network is simply a list of edges (in our case the number of sections borrowed) between nodes (in our case, the codes).
+Because even our efforts at determining the best match for each section sometimes attributed a section to an incorrect code, we pruned the edges of the graph so that each code was connected to another code only if it borrowed at least fifty sections or twenty percent of its sections.
+On networks see {CITATION}.
+
+    Within New York there was a definite chronological progression from the 1848, 1849, 1850, 1851, and 1853 versions of the code, but the development is not chronologically linear.
+The state legislature enacted the 1848, 1849, and 1851 codes, and these show stronger relational similarities.
+The 1850 and 1853 were David Dudley Field's ideal drafts of the code which were never enacted.
+They were, however, printed with wide margins, quality typesetting, and---in the 1850 draft---extensive explanatory notes, all with an eye towards other jurisdictions copying them as a model.
+Those two codes show stronger similarity to one another than to the enacted drafts.
+
+[^41]: Non-Field jurisdictions occasionally exhibited a borrowing relationship within a state or across two states.
+In in a few unusual instances they contributed to codes which were derived from the Field Code.
+For example, Alabama's 1852 Code provided a few sections to Tennessee's 1858 code, and some states like Wisconsin copied, along with the Field Code, large passages of pre-code legislation from earlier in the state's history.
+
+[^42]: spectrogram("CA1851", mutate(best\_matches, match\_code = ifelse(match\_code %in% c("NY1848", "NY1849", "NY1850"), "New York 1849/50", match\_code)), white\_list = 3)
+
+[^43]: (The visualization here, because of difficulties in precisely matching sections, actually understates the extent of the borrowing.) **Explain** why our method errs on the side of undercounting.
+
+[^44]: Scholars in digital literary studies often speak of the "deformance" of texts.
+Clustering the sections of the codes deformed them by pulling the sections out of their context within specific codes and by arranging them by topic in chronological order.
+Deforming the codes allowed us to see the development and spread of the law.
+
+[^45]: Brendan J. Frey and Delbert Dueck, "Clustering by Passing Messages Between Data Points," *Science* 315 (2007): 972--976.
+
+[^46]: Furthermore, even though the affinity propagation clus- tering algorithm did not fully converge with our peculiar dataset, it did an adequate job clustering the documents.
+Because there was an exemplar section for each cluster, we were able to merge clusters whose exemplars had a high Jaccard similarity score.
+
+[^47]: We also implemented a method called the Smith Waterman algorithm, which is used for gene sequencing, but which we adapted for natural language.
+This is the method used by Smith et al for Viral Texts.
+This permits us to extract the longest matching string from two documents and so to see how the one document modified the other.
+
+[^48]: E.g., Moretti, Distant Reading; Jockers, Macroanalysis.
+
+[^49]: Samuels, Lisa, and Jerome McGann. "Deformance and Interpretation." *New Literary History* 30.1 (1999) : 25--56; *Stallybrass, Peter. "Against Thinking."* PMLA *122.5 (2007): 1580-1587.*
+
+[^50]:
+
+[^51]: Those jurisdictions were Nevada (1861), Dakota Territory---which retained the Code when split into North and South (1862), Idaho (1864), Arizona (1864), Montana (1865), Arkansas (1868), North Carolina (1868), Wyoming (1869), Florida (1870), South Carolina (1870), Utah (1870), and Colorado (1877).
+
+[^52]: Elliott West, "Reconstructing Race," 34 *Western Historical Quarterly* 6 (2003).
+See also Heather Cox Richardson, *West from Appomattox: The Reconstruction of America after the Civil War* (New Haven: Yale University Press, 2007); Sven Beckert, *Monied Metropolis: New York City and the Consolidation of the American Bourgeoisie, 1850-1896* (Harvard 2003); Mark Wahlgren Summers, *The Ordeal of the Reunion: A New History of Reconstruction* (Chapel Hill: University of North Carolina Press, 2014).
+The major application of the Greater Reconstruction idea to legal history has been Sarah Barringer Gordon, *The Mormon Question: Polygamy and Constitutional Conflict in Nineteenth-Century America* (Chapel Hill: University of North Carolina Press, 2003).
+
+[^53]: See, for instance, Rogers Smith, *Civic Ideals: Conflicting Visions of Citizenship in U.S.
+History* (Yale 1999); Meg Jacobs, William J.
+Novak, and Julian E.
+Zelizer, eds., *The Democratic Experiment: New Directions in American Political History* (Princeton 2003); Edward Purcell, *Litigation and Inequality: Federal Diversity Jurisdiction in Industrial America, 1870-1958* (Oxford 1992).
+
+[^54]: Naomi Lamoreaux and John Joseph Wallis, "States, Not Nation: The Sources of Political and Economic Development in the Early United States," Paper Presented at the Economic History Workshop, Harvard University, March 4, 2016.
+
+[^55]: For instance, although Tennessee in 1858 adapted nearly 225 sections of its code from Field codes, the state also incorporated nearly 50 sections of the 1852 Code of Alabama, one of the largest borrowings of southern legislation within the corpus we collected.
+
+[^56]: Illinois was a fiercely traditional anti-code state.
+In later decades, lawyers jokingly called it "the Yellowstone Park of common law pleading." See Charles E.
+Clark, "The New Illinois Civil Practice Act," 1 *University of Chicago Law Review* 209 (1933).
+Nevertheless, even Illinois had substantial legislation organizing the courts and prescribing certain common law processes for obtaining civil remedies, and Colorado adapted the bulk of this legislation when it organized as a territory, a full seventeen years before its legislature considered adopting the Field Code.
+
+[^57]: Journal of the Assembly of the Territory of Utah (1870), 15.
+
+[^58]: "The Code Again," *Pueblo Daily Chieftain*, February 25, 1877.
+
+[^59]: "The Legislature: The Senate Devotes Another Day to the Code," *Denver Daily Tribune*, February 17, 1877.
+
+[^60]: Governor's Message, in Journal of the House of Assembly of the Territory of Nebraska (1857), 12.
+
+[^61]: William A.
+Jenkins to William Blount Rodman, January 14, 1868, Rodman Papers.
+East Carolina University Library, Special Collections.
+Rodman's explication of the Code appeared in three sequentially numbered articles in the *Standard* on August 14, 15, and 16, 1868, under the title "The Code of Civil Procedure." Rodman disclosed his authorship in private correspondence with Barringer.
+See Barringer to Rodman, August 21, 1868, Rodman Papers.
+
+[^62]: Gordon Morris Bakken, *Practicing Law in Frontier California* (Nebraska 1991), 51-54.
+The new western history ushered in by Patricia Nelson Limerick, *The Legacy of Conquest: The Unbroken Past of the American West* (Norton 1987) and Richard White, *"It's Your Misfortune and None of My Own": A History of the American West* (Oklahoma 1991) is now returning to issues of political economy.
+See Patricia Nelson Limerick, *A Ditch in Time: The City, the West, and Water* (Fulcrum 2012); Richard White, *Railroaded: The Transcontinentals and the Making of Modern America* (Norton 2011).
+
+[^63]: "The Code," *Denver Daily Tribune*, January 10, 1877; "The Code," *Denver Daily Times*, January 27, 1877.
+
+[^64]: "A Code of Civil Procedure," *Denver Daily Times*, January 12, 1877.
+
+[^65]: "The Code," *Denver Daily Tribune*, January 31, 1877.
+
+[^66]: See Gunther A.
+Weiss, "The Enchantment of Codification in the Common-Law World," 25 *Yale Journal of International Law* 435 (2000).
+For a thorough study of the ideology of codification in India, see Robert A.
+Yelle, *The Language of Disenchantment: Protestant Literalism and Colonial Discourse in British India* (Oxford: Oxford University Press, 2012).
+
+[^67]: See, for instance, James C.
+Carter's classic defense of the common law against codification, The Ideal and the Actual in the Law, Address to the American Bar Association, August 21, 1890, at 28 ("the legislature should never attempt to perform the function of the judge, that of simply ascertaining and declaring existing customs.
+This is the work of experts who can qualify themselves only by the devotion of their lives.").
+
+[^68]: See, for instance, "Note," 29 *Albany Law Journal* 141, 142 (1884); Millar, *Civil Procedure of the Trial Court*, 55-56.
+
+[^69]: 19 *Hansard Parliamentary Debates* 531.
+
+[^70]: Texas commissioned the preparation of a code of civil procedure in 1855, and the legislature scheduled an extra session to consider it but ultimately never passed the law.
+21 *Texas Reports* (Hartley) xi (1882); *Texas State Times*, December 15, 1855.
+Reformers in the 1869 convention in Illinois attempted to pass a provision similar to the one in New York's 1846 constitution, which would have required the legislature to appoint a commission to revise practice and pleadings along the lines of the Field Code.
+See *Debates and Proceedings of the Constitutional Convention of the State of Illinois* (1870), 1496-1498.
+
+[^71]: "The Code," *Weekly Standard* (Raleigh), May 26, 1869.
+
+[^72]: See, for instance, the summary of the states-as-laboratories literature in Brian Galle & Joseph Leahy, "Laboratories of Democracy?
+Policy Innovation in Decentralized Governments," 58 *Emory Law Journal* 1333 (2009).
+
+[^73]: See Daniel Ernst, *Tocqueville's Nightmare: The Administrative State Emerges in America, 1900-1940* (Oxford: Oxford University Press, 2014); Jerry L.
+Mashaw, *Creating the Administrative Constitution: The Lost One Hundred Years of American Administrative Law* (Yale Law Library 2012); Gautham Rao, *National Duties: Custom Houses and the Making of the American State* (University of Chicago 2016).

### 2016-06-20 article/article.Rmd
Basic cleanup from Google Docs

@@
 - Lincoln Mullen
-output: pdf_document
+output: 
+  pdf_document:
+    number_sections: true
+    fig_caption: true
+fontsize: 12pt
+documentclass: article
 ...
@@
 Stewart copied not just California's code but also its method of codification---California too had borrowed its code in a similar manner from New York.
+
+![The 1861 Morris bill which adapted California's code for Nevada.](morris-bill.jpg)
 
@@
 
-**Part 1.**
+# Part 1
 
@@
 
-&gt;&gt;Courage; persevere in the support of written reason against precedents and vague traditions.
-.
-.
-.
+> Courage; persevere in the support of written reason against precedents and vague traditions.
+...
 Let four or five good heads be united in a commission, to frame in silence the project of a code.
@@
 It is only to consult together, and to select.
-Do so with your best authors as we did with ours, and principally with Pothier's treatise on Obligations, which we simply converted into articles of our code.&lt;&lt;
+Do so with your best authors as we did with ours, and principally with Pothier's treatise on Obligations, which we simply converted into articles of our code.
 
@@
 Each time they reminded legislators that "public opinion had issued its mandate in the most imposing form" of a constitutional decree.
-The constitution, together with the legislative act appointing the commission "gave the commissioners instructions so precise, as to leave them no discretion, if they had desired it, \[and\] promised them therefore in advance, so long as they obeyed those instructions, the concurrence and co-operation of all departments of the government."[^16] Although the theory of codification made it a democratic enterprise, in practice Field---an ardent Jacksonian---insisted the democratic legislature ought to defer to the expertise of the commissioners.
+The constitution, together with the legislative act appointing the commission "gave the commissioners instructions so precise, as to leave them no discretion, if they had desired it, [and] promised them therefore in advance, so long as they obeyed those instructions, the concurrence and co-operation of all departments of the government."[^16] Although the theory of codification made it a democratic enterprise, in practice Field---an ardent Jacksonian---insisted the democratic legislature ought to defer to the expertise of the commissioners.
 
@@
 
-**Part 2.**
+# Part 2
 
 Although the amount of legislation that governed American civil practice is impressive---even if uncodified, every state had procedure statutes that were amended and re-enacted nearly every decade---a corpus of procedural legislation would not even count among digital historians as "big data." Our collection of relevant (or possibly relevant) laws comprise 135 statutes from the nineteenth century.
-It includes separately bound codes of civil procedure as well as codes or regulations appearing session laws and statutory compilations.[^30] It comprises some **\[NUMBER\]** pages, **\[NUMBER\]** words, organized into 98,000 regulations.
+It includes separately bound codes of civil procedure as well as codes or regulations appearing session laws and statutory compilations.[^30] It comprises some TODO pages, TODO words, organized into 98,000 regulations.
 The corpus is not exhaustive.
@@
 
-&gt;&gt;§ 554.
+> § 554.
 The distinction between actions at law and suits in equity, and the forms of all such actions and suits, heretofore existing, are abolished; and, there shall be in this state, hereafter, but one form of civil action, for the enforcement or protection of private rights and the redress or prevention of private wrongs, which shall be denominated a civil action.
 § 555.
-In such action, the party complaining is known as the plaintiff, and the adverse party as the defendant.&lt;&lt;
+In such action, the party complaining is known as the plaintiff, and the adverse party as the defendant.
 
@@
 
-&gt;&gt;§ 1.
+> § 1.
 There shall be in this State but one form of Civil Action, for the enforcement or protection of private rights, and the redress or prevention of private wrongs.
 §2.
-In such action the party complaining shall be known as the plaintiff, and the adverse party as the defendant.&lt;&lt;
+In such action the party complaining shall be known as the plaintiff, and the adverse party as the defendant.
 
@@
 
-**Part 3.**
+# Part 3
 
@@
 A count by a "friend" of Field's found that only three sentences of the Field Code had carried over word-for-word into the Throop Code.
-Nevertheless, many of the changes were purely formal, and Field speculated that these changes had been made only "so that \[the Code\] should not appear to be the same thing as before." With respect to Mr.
+Nevertheless, many of the changes were purely formal, and Field speculated that these changes had been made only "so that [the Code] should not appear to be the same thing as before." With respect to Mr.
 Field or his "friend," we were able to find that the connection was between the Throop Code and the Field Code was somewhat stronger than he thought, and the Throop Code was indeed a descendant, if much revised, from the Field Code.
@@
 The bulk of the code was taken directly from New York's 1849 or 1850 codes (which are difficult to distinguish exactly from one another.[^42] The remainder of the code was borrowed from California's 1850 code.
-The 1850 version was in turn borrowed from the New York codes \[**might as well show this, esp.
-since CA1850 is so impressive**\].
+The 1850 version was in turn borrowed from the New York codes **TODO: might as well show this, esp.
+since CA1850 is so impressive**.
 As we would expect, the bulk of the borrowings that come from California instead of directly from New York are at the beginning of the code, where the 1850 code had made amendments specific to the borrowing from California.
@@
 Iowa's Code had much more minor influence, and Wyoming developed the only truly original section which made clear the link to a racist assumption of infantilization of non-white peoples.
-\[**Figure: Cluster from Kellen**\]
+
+**Figure: Cluster from Kellen**
 
@@
 
-**Part 4**.
+# Part 4
 
@@
 While the so-called new western history has shed significant light on neglected topics of Indian dispossession and environmental management, it has often done so by leaving out of view matters of political economy, a staple of the old western history.
-As one work in that older tradition argued, "Debt collection was the central part of law practice for the \[western\] bar and remained a key part of private practice throughout the century."[^62] On that understanding, one western lawyer succinctly summarized the difference between the Code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, .
+As one work in that older tradition argued, "Debt collection was the central part of law practice for the [western] bar and remained a key part of private practice throughout the century."[^62] On that understanding, one western lawyer succinctly summarized the difference between the Code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, .
 .
@@
 
-**Conclusion**
+# Conclusion
 
@@
 ed.
-2011 \[1991\]); Roger Berkowitz, *The Gift of Science: Leibniz and the Modern Legal Tradition* (Fordham 2010).
+2011 [1991]); Roger Berkowitz, *The Gift of Science: Leibniz and the Modern Legal Tradition* (Fordham 2010).
 
@@
 ed.
-1843 \[1839\]), 1-189, preface and 28, ch.
+1843 [1839]), 1-189, preface and 28, ch.
 7 § 1.
@@
 If any two documents have a matching subset, then they are considered a candidate pair.
-\[**CLARIFY**\] This algorithm has several useful properties.
+**TODO: CLARIFY** This algorithm has several useful properties.
 It approximates the Jaccard similarity of the two documents.

### 2016-06-23 article/article.Rmd
Revise introduction

@@
 Nye, a former New York lawyer, instructed the assembly that they would have to forsake the Mormon statutes of Utah Territory from which Nevada had been carved.
-Those laws were ill adapted to "the mining interests" of the new territory, but "happily for us, a neighboring State whose interests are similar to ours, has established a code of laws" sufficiently attractive to "capital from abroad." That neighbor, of course, was California, and Nye urged that California's code of civil practice be enacted in Nevada, as far as it could "be made applicable."[^1] Territorial Senator William Morris Stewart, the famed silver-mining lawyer who would become a leading U.S.
-Senator of Reconstruction, followed the instructions perhaps too well.
+Those laws were ill adapted to "the mining interests" of the new territory, but "happily for us, a neighboring State whose interests are similar to ours, has established a code of laws" sufficiently attractive to "capital from abroad." That neighbor, of course, was California, and Nye urged that California's code of civil practice be enacted in Nevada, as far as it could "be made applicable."[^1] Territorial Senator William Morris Stewart, a famed silver-mining lawyer who would become the leading U.S.
+senator of Reconstruction, followed the instructions perhaps too well.
 Stewart literally cut and pasted the latest *Wood's Digest* of the California Practice Act into the session bill, crossing out *state* and *California* and substituting *territory* and *Nevada* where necessary.
-Stewart copied not just California's code but also its method of codification---California too had borrowed its code in a similar manner from New York.
+Stewart copied not just California's procedure code but also its method of codification, for California had in turn borrowed its code by modifying New York's.
 
-![The 1861 Morris bill which adapted California's code for Nevada.](morris-bill.jpg)
+![Detail from Council Bill 21, First Territorial Legislative Session (1861), Nevada State Library, Archives and Public Records.](morris-bill.jpg)
 
@@
 The bill---of 715 sections---had reached him late the night before the legislative session was to close.
-Even in the few hours he had to read it, Nye counted "so many errors in the enrolling of it, numbering probably more than three hundred." Some errors were severe.
+Even in the few hours he had to read it, Nye counted "many errors in the enrolling of it, numbering probably more than three hundred." Some errors were severe.
 Nevada's Organic Act specified the jurisdiction of the district courts and justices of the peace, but the code overwrote these limitations by copying California's arrangements.
 Error-riddled and unconstitutional as the bill was, Nye believed a civil practice code was a "universal necessity and public need," concluding that "without some legislation in providing a code of procedure in civil cases, it may be a matter of grave question whether your courts would be able to fulfill the purpose of their creation."[^2] Nye signed the Code into law.
-Strikingly, nothing like this "universal necessity" had existed when Nye began his legal career in New York in the 1840s.
 
-By the end of the nineteenth-century, thirty-one American states and territories had adapted the text of a New York Code of Civil Procedure first promulgated in 1848.
-The Code colloquially became known as the Field Code, named for its chief draftsman David Dudley Field, a famed Manhattan trial lawyer.[^3] When Field's Code appeared in the Colorado assembly in 1876, a Denver newspaper wryly commented that "the scissors and paste-pot we had heretofore confidently believed were implements peculiar to the newspaper sanctum." But to the editor, the cut-and-paste code was not just a humorous curiosity of legislative history.
+Strikingly, nothing like this "universal necessity" for a code of practice existed when Nye began his legal career in New York in the 1840s; rather, it was one of the central developments of America law during the nineteenth-century.
+By the end of the nineteenth-century, thirty-one American states and territories had adapted the text of a New York code of civil procedure first promulgated in 1848.
+The code colloquially became known as the Field Code, named for its chief draftsman David Dudley Field, a famed Manhattan trial lawyer.[^3] When Field's code appeared in the Colorado assembly in 1876, a Denver newspaper wryly commented, "The scissors and paste-pot we had heretofore confidently believed were implements peculiar to the newspaper sanctum." To the editor, the cut-and-paste code was not just a humorous curiosity of legislative history.
 Rather, the extensive copying of Field's Code threatened the foundations of American popular sovereignty.
 "The bill is a long one; the assembly has not the time to devote to it and to give it the scrutiny that a measure of such importance demands," the editor explained.
-But blind approval "would be an injustice to themselves and a greater wrong and injustice to the people who have a right to demand that their public servants legislate for the public good." The Code "has been 'assimilated,' as we are informed, 'to the character and requirements of our people,' whatever that may mean," but the editor feared the legislation was the product of "men who have the welfare of the 'dear people' at their tongue's end always, but never in their hearts."[^4]
+Blind approval "would be an injustice to themselves and a greater wrong and injustice to the people who have a right to demand that their public servants legislate for the public good." The Code "has been 'assimilated,' as we are informed, 'to the character and requirements of our people,' whatever that may mean," but the editor feared the legislation was the product of "men who have the welfare of the 'dear people' at their tongue's end always, but never in their hearts."[^4]
 
-The migration of the Field Code was a central event in Anglo-American legal history, but no modern historian has traced the extensive borrowings of the Field text nor recognized the political furor that greeted the Code outside New York.[^5] Every aspect of a civil justice system, the rules granting access to courts, to lawyers, to remedies (whether damages, injunctions, or seizure of property) was covered by the Code, making its New York-specific rules politically contentious both in- and outside the Empire State.
-As the Field Code migrated around the country, commentators in each jurisdiction raised the same complaint: How could legislation borrowed from another state represent the popular will and bests interests of *this* state?
+The migration of the Field Code was a central event in Anglo-American legal history, but no modern historian has traced the extensive borrowings of the Field text nor recognized the political furor that greeted the Code outside New York.[^5] Every aspect of a civil justice system, from the rules granting access to courts, to lawyers, to remedies (whether damages, injunctions, or seizure of property) was covered by the Code, making its New York-specific rules politically contentious both inside and outside the Empire State.
+As the Field Code migrated around the country, commentators in each jurisdiction raised the same complaint: how could legislation borrowed from another state represent the popular will and bests interests of *this* state?
 
-Exploring this history is a daunting task, however.
+Understanding the history of the Field Code requires not only attention to its political context but also a detailed examination of the substance of what was borrowed and what was revised in each jurisdiction.
+Exploring these borrowings is a daunting task, however.
 Procedure codes were long, technical documents, and although each jurisdiction copied large swaths of text, each also modified the text along the way, sometimes with a simple *Nevada* for *California*, sometimes with more foundational changes to the remedial system.
 Although Stewart's cut-and-paste code found its way into the archives, most draft legislation did not, and few codifiers explained in detail how they produced their texts.
+Traditional reading or textual criticism of some 98,000 distinct sections of law comprising some 7.7 million words is simply not a feasible research task for a historian who wishes to track these borrowings.
 
-Innovative techniques in digital analysis of texts can resolve some of these difficulties.
-Within a corpus of legislation, digital programming can essentially reverse engineer and visualize what the archive revealed in Figure 1: which texts were borrowed, which modified, and how extensively.
+Yet by turning to the digital analysis of texts, we have resolved this difficulty and tracked the how the sections of the various codes of civil procedures were borrowed from one another.
+Within the corpus of legislation, algorithmic analysis of texts can essentially reverse engineer and visualize what the archive revealed in Figure 1: which texts were borrowed, which modified, and how extensively.
 Our method works especially well for legal texts, for reasons we will explain.
-However, we designed a replicable method that can offer similar results on any other kind of curated collection of texts, from church hymns to medical treatises.
+However, scholars can extend this method to other kinds of curated collection of texts, from church hymns to medical treatises.
 
-The first contribution of this Article is the demonstration of our methods, applied to the Field Code.
-The second contribution is the integration of these methods with more conventional approaches of social and cultural history.
-On the national level the extent of legislative borrowing followed a pattern American historians have described as "Greater Reconstruction"---the former Confederate South and the Far West show a remarkable kinship.
-Scholars have typically described Greater Reconstruction as a *federal* development: the creation of national citizenship, a national economy, and a larger state apparatus centered in Washington, D.C.
-This Article shows that Greater Reconstruction had its state-level dimensions as well.
-The uniform practice of law and adjudication of civil remedies was not structured by Washington mandates, however, but by the anxiety that New York capital would follow only New York civil remedies.
+The first contribution of this article is the demonstration of our methods as applied to the corpus of nineteenth-century state procedure codes.
+The second contribution is the integration of what we learned from the text analysis with more conventional approaches of political and cultural history to explain the importance of the migration of the Field Code.
+On the national level the extent of legislative borrowing followed a pattern American historians have described as a "Greater Reconstruction" in which the former Confederate South and the Far West showed a remarkable kinship.
+Scholars have typically described Greater Reconstruction as a federal development, featuring the creation of national citizenship, a national economy, and a larger state apparatus centered in Washington, D.C.
+This article shows that Greater Reconstruction had its state-level dimensions as well.
+The uniform practice of law and adjudication of civil remedies was not structured by Washington mandates, however, but by the anxiety that New York financial capital would follow only New York civil remedies.
 At the more local level, our digital computations can trace modifications within code traditions, for instance, the ways western and midwestern codifiers altered New York's law to accommodate hardening conceptions of racial competencies in the civil courts.

### 2016-06-23 article/article.Rmd
Correct citation

@@
 [^7]: For the rise of treatises in America generally, see G.
-Edward White, *The Marshall Court and Cultural Change, 1815-1835* (1988) and A.W.B.
-Simpson, "The Rise and Fall of the Legal Treatise: Legal Principles and the Forms of Legal Literature," in *Legal Theory and Legal History: Essays on the Common Law* (1984), 273.
+Edward White, *The Marshall Court and Cultural Change, 1815--1835* (1988) and A.
+W.
+B.
+Simpson, "The Rise and Fall of the Legal Treatise: Legal Principles and the Forms of Legal Literature," in *Legal Theory and Legal History: Essays on the Common Law* (London: Hambledon Press, 1987), 273--320.
 The most instructive treatises for New York practice in the 1840s were Oliver L.

### 2016-06-23 article/article.Rmd
Revisions to part 1

@@
 Law was to be made by democratically responsible legislators---in terse, unambiguous statements---not discovered through application and analogy in particular cases by the judges.
-Codification debates thus ranged over the metaphysics of law to the political theories of separation of powers and institutional competency.[^11]
+Debates over codification thus ranged from the metaphysics of law to political theories of separation of powers and institutional competency.[^11]
 
-At New York's constitutional convention in 1846, "the conquerors took all," as the ambivalent Jacksonian James Fenimore Cooper complained.[^12] Law reformers abolished the court of chancery, made judges to stand for popular election, and required the legislature to appoint a commission to reform the "practice and pleadings" of the civil courts.[^13] New Yorkers had two models of legislative commissions on which they could draw for their own law reforms.
+In New York, these codification debates came to a head at the 1846 constitutional convention, where "the conquerors took all," as the ambivalent Jacksonian James Fenimore Cooper complained.[^12] Law reformers abolished the court of chancery, made judges stand for popular election, and required the legislature to appoint a commission to reform the "practice and pleadings" of the civil courts.[^13] New Yorkers had two models of legislative commissions on which they could draw for their own law reforms.
 The French government under Napoleon had appointed five-member commissions to codify the law of France.

### 2016-06-23 article/article.Rmd
Trim Pierre François Réal quotation

@@
 The French government under Napoleon had appointed five-member commissions to codify the law of France.
-When the New York law reformer William Sampson called for codification in a widely noted address to the New York historical society, one of the members of the French commission was living in exile in upstate New York at the time and wrote to Sampson to advise him on the mechanics of codification:
-
-> Courage; persevere in the support of written reason against precedents and vague traditions.
-...
-Let four or five good heads be united in a commission, to frame in silence the project of a code.
+When the New York law reformer William Sampson called for codification in a widely noted address to the New York historical society, one of the members of the French commission was living in exile in upstate New York at the time and wrote to Sampson to advise him on the mechanics of codification:  "Let four or five good heads be united in a commission, to frame in silence the project of a code.
 It is not so difficult a task.
 It is only to consult together, and to select.
-Do so with your best authors as we did with ours, and principally with Pothier's treatise on Obligations, which we simply converted into articles of our code.
-
-Tellingly, the French commissioner took it as granted that the commission's code would automatically be promulgated as law.[^14]
+Do so with your best authors as we did with ours, ...
+which we simply converted into articles of our code." Tellingly, the French commissioner took it as granted that the commission's code would automatically be promulgated as law.[^14]
 

### 2016-06-23 article/article.Rmd
Revisions to part 1, plus standardize capitalization

@@
 Nevada's Organic Act specified the jurisdiction of the district courts and justices of the peace, but the code overwrote these limitations by copying California's arrangements.
-Error-riddled and unconstitutional as the bill was, Nye believed a civil practice code was a "universal necessity and public need," concluding that "without some legislation in providing a code of procedure in civil cases, it may be a matter of grave question whether your courts would be able to fulfill the purpose of their creation."[^2] Nye signed the Code into law.
+Error-riddled and unconstitutional as the bill was, Nye believed a civil practice code was a "universal necessity and public need," concluding that "without some legislation in providing a code of procedure in civil cases, it may be a matter of grave question whether your courts would be able to fulfill the purpose of their creation."[^2] Nye signed the code into law.
 
@@
 "The bill is a long one; the assembly has not the time to devote to it and to give it the scrutiny that a measure of such importance demands," the editor explained.
-Blind approval "would be an injustice to themselves and a greater wrong and injustice to the people who have a right to demand that their public servants legislate for the public good." The Code "has been 'assimilated,' as we are informed, 'to the character and requirements of our people,' whatever that may mean," but the editor feared the legislation was the product of "men who have the welfare of the 'dear people' at their tongue's end always, but never in their hearts."[^4]
+Blind approval "would be an injustice to themselves and a greater wrong and injustice to the people who have a right to demand that their public servants legislate for the public good." The code "has been 'assimilated,' as we are informed, 'to the character and requirements of our people,' whatever that may mean," but the editor feared the legislation was the product of "men who have the welfare of the 'dear people' at their tongue's end always, but never in their hearts."[^4]
 
-The migration of the Field Code was a central event in Anglo-American legal history, but no modern historian has traced the extensive borrowings of the Field text nor recognized the political furor that greeted the Code outside New York.[^5] Every aspect of a civil justice system, from the rules granting access to courts, to lawyers, to remedies (whether damages, injunctions, or seizure of property) was covered by the Code, making its New York-specific rules politically contentious both inside and outside the Empire State.
+The migration of the Field Code was a central event in Anglo-American legal history, but no modern historian has traced the extensive borrowings of the Field text nor recognized the political furor that greeted the code outside New York.[^5] Every aspect of a civil justice system, from the rules granting access to courts, to lawyers, to remedies (whether damages, injunctions, or seizure of property) was covered by the code, making its New York-specific rules politically contentious both inside and outside the Empire State.
 As the Field Code migrated around the country, commentators in each jurisdiction raised the same complaint: how could legislation borrowed from another state represent the popular will and bests interests of *this* state?
@@
 After the Revolution, royal commissions became disfavored while Parliament undertook many of the same functions through "committees of enquiry" to which only members of Parliament were appointed.
-By the nineteenth century, the use of royal commissions was again reviving.
+By the nineteenth century, royal commissions again became common.
 Royal commissioners were usually not legislators.
@@
 On the other hand, the recommendations of royal commissioners were a further remove from actual legislation.
-Although by the mid-nineteenth century royal commissions sometimes offered model statutes, their advised legislation still had to pass through the normal politicking and drafting processes of Parliament.[^15]
+Although by the mid-nineteenth century royal commissions sometimes offered model statutes, the legislation they advised still had to pass through the normal politicking and drafting processes of Parliament.[^15]
 
@@
 Each time they reminded legislators that "public opinion had issued its mandate in the most imposing form" of a constitutional decree.
-The constitution, together with the legislative act appointing the commission "gave the commissioners instructions so precise, as to leave them no discretion, if they had desired it, [and] promised them therefore in advance, so long as they obeyed those instructions, the concurrence and co-operation of all departments of the government."[^16] Although the theory of codification made it a democratic enterprise, in practice Field---an ardent Jacksonian---insisted the democratic legislature ought to defer to the expertise of the commissioners.
+The constitution, together with the legislative act appointing the commission, "gave the commissioners instructions so precise, as to leave them no discretion, if they had desired it, [and] promised them therefore in advance, so long as they obeyed those instructions, the concurrence and co-operation of all departments of the government."[^16] Although the theory of codification made it a democratic enterprise, in practice Field---an ardent Jacksonian---insisted the democratic legislature ought to defer to the expertise of the commissioners.
 
-The Field commission sought to blunt criticism by insisting that political concerns about lawmaking did not apply to mere *procedure*.
-"The system of procedure by which law is administered, differs from the law itself in this," the commissioners explained: "the latter is a body of elementary rules founded in the immutable principles of justice, drawing their origin from the obligations which divine wisdom has imposed .
-.
-.
-; while the former consists, in its very nature, but of a body of prescribed rules, having no source but the will of those by whom they are laid down." Substantive law was universal, natural, grounded in divine justice, and therefore entitled to respect and protection from change.
-But God cared nothing of the "the mere machinery by which law is to be administered," and thus, the commissioners argued, procedure was trivial enough for legislative experimentation but complicated enough that only master practitioners like themselves could run the experiment.[^17]
+The Field commission sought to blunt criticism by insisting that political concerns about lawmaking did not apply to mere procedure.
+"The system of procedure by which law is administered, differs from the law itself in this," the commissioners explained: "the latter is a body of elementary rules founded in the immutable principles of justice, drawing their origin from the obligations which divine wisdom has imposed ...; while the former consists, in its very nature, but of a body of prescribed rules, having no source but the will of those by whom they are laid down." Substantive law was universal, natural, grounded in divine justice, and therefore entitled to respect and protection from change.
+But God cared nothing of the "the mere machinery by which law is to be administered." Thus, the commissioners argued, procedure was trivial enough for legislative experimentation but complicated enough that only master practitioners like themselves could run the experiment.[^17]
 
-The scope of the Code tended to belie the idea that procedure included only the "mere machinery" of a lawsuit.[^18] The final draft of the Code, printed in 1850, spanned nearly 800 pages of 1,885 regulations.
-The first third of the Code covered constitutional topics, specifying the jurisdiction of all state courts and the duties of all state officers (and liabilities for violating those duties).
-The Code deregulated attorney compensation, introducing novel structures of retainers and contingency fees.[^19] It created summary procedures meant to accelerate debt collections while simultaneously carving out "homestead" exemptions from the sheriff's reach.[^20] The Code concluded by defining who could be an attorney, a juror, and a witness, drawing racial and gendered distinctions over who could speak in court.[^21]
+Yet the scope of the procedure Code included far more than the "mere machinery" of a lawsuit.[^18] The final draft of the code, printed in 1850, spanned nearly 800 pages of 1,885 regulations.
+The first third of the code covered constitutional topics, specifying the jurisdiction of all state courts and the duties of all state officers (and liabilities for violating those duties).
+The code deregulated attorney compensation, introducing novel structures of retainers and contingency fees.[^19] It created summary procedures meant to accelerate debt collections while simultaneously carving out "homestead" exemptions from the sheriff's reach.[^20] The code concluded by defining who could be an attorney, a juror, and a witness, drawing racial and gendered distinctions over who could speak in court.[^21]
 
-Most importantly, the Code defined all the remedies that a civil court could order---from money damages, to partition of property, to injunctive decrees and contempts--and made those remedies available in every lawsuit.
+Most importantly, the code defined all the remedies that a civil court could order---from money damages, to partition of property, to injunctive decrees and contempts--and made those remedies available in every lawsuit.
 In many cases, a legal right was indistinguishable from the remedy that secured that right: The right to possess a particular piece of property and the remedy that seized and delivered that property were, in effect, the same thing.
@@
 
-The Code would encounter similar difficulties in each jurisdiction that adopted it.
+The code would encounter similar difficulties in each jurisdiction that adopted it.
 Even the shortest version of the Field Code was significantly longer than any other state statute before the Progressive legislation of the twentieth century.
-And unlike statutory complilations that sometimes took the name of a "code" but made no changes to existing law, the Field Code opened with a declaration of novelty, abolishing the hallmarks of prior practice and instituting "hereafter" a new form of action with substantial revisions to basic matters of standing, remedy, and enforcement of civil judgments.[^27] In the states where it was imported, there could be no getting around the fact that the Code introduced extensive, new law, yet legislators were unable to read, critique, and amend the Code within the short time horizons of a legislative session.
-"It is folly to undertake to pass a code in a sixty day session," wrote the *Montana Post*, "and the best way would be for the Assembly to select one from a State or Territory which would come near meeting our wants, and slide it through with the fewest changes possible."[^28] Sliding the Code through eased the problem of time but exacerbated the problem of local sovereignty.
+And unlike statutory complilations that sometimes took the name of a "code" but made no changes to existing law, the Field Code opened with a declaration of novelty, abolishing the hallmarks of prior practice and instituting "hereafter" a new form of action with substantial revisions to basic matters of standing, remedy, and enforcement of civil judgments.[^27] In the states where it was imported, there could be no getting around the fact that the code introduced extensive, new law, yet legislators were unable to read, critique, and amend the code within the short time horizons of a legislative session.
+"It is folly to undertake to pass a code in a sixty day session," wrote the *Montana Post*, "and the best way would be for the Assembly to select one from a State or Territory which would come near meeting our wants, and slide it through with the fewest changes possible."[^28] Sliding the code through eased the problem of time but exacerbated the problem of local sovereignty.
 "To be governed by a foreign law, especially when that law is not preknown to the people whose conduct is to be regulated thereby .
@@
 These variations point out how the Field Code was always a moving target.
-While Field considered the 1850 New York code to be the definitive, ideal version of the code, it was really all of the New York codes from 1848 to 1853 that became models for other jurisdictions, likely due to whatever material a given commission had on hand.
+While Field considered the 1850 New York Code to be the definitive, ideal version of the code, it was really all of the New York codes from 1848 to 1853 that became models for other jurisdictions, likely due to whatever material a given commission had on hand.
 The Field Code was not a single volume on the shelf, but a series of volumes any one of which might be more accessible in different regions and different eras.
@@
 A count by a "friend" of Field's found that only three sentences of the Field Code had carried over word-for-word into the Throop Code.
-Nevertheless, many of the changes were purely formal, and Field speculated that these changes had been made only "so that [the Code] should not appear to be the same thing as before." With respect to Mr.
+Nevertheless, many of the changes were purely formal, and Field speculated that these changes had been made only "so that [the code] should not appear to be the same thing as before." With respect to Mr.
 Field or his "friend," we were able to find that the connection was between the Throop Code and the Field Code was somewhat stronger than he thought, and the Throop Code was indeed a descendant, if much revised, from the Field Code.
@@
 Field's Code reversed this rule, expanding witness competency as widely as possible: any person "having organs of sense" could now be admitted as a witness in New York, with only the insane and very young children exempted from the rule.
-As the Code migrated West, however, legislators added racial exclusions to Field's list.
+As the code migrated West, however, legislators added racial exclusions to Field's list.
 The following cluster documents how California's codifiers engrafted earlier prohibitions from midwestern states into Field's Code.
@@
 While many clusters exhibited regional variation as they grew more distant from the Field Code, clusters having to do with creditors' remedies were almost completely uniform across the American West and South.
-No single section of the Code announced its preference for creditors' rights; rather, the acceleration of creditors' remedies resulted from the combination of several sections.
-In the original enacted Code, § 107 required a defendant to answer the complaint within twenty days, instead of at the next court session (which in some cases could have been as far as three months away); § 202 provided for default judgment as a matter of course, issued by a clerk without a judicial order if no adequate answer was received within the twenty days; §§ 128-133 abolished fictitious pleadings and required answers to state true facts verified by a defendant's oath, all so that no trial would delay the enforcement of uncontestable obligations; finally, the Code abolished a traditional thirty-day waiting period between issue of judgment and commencement of execution (see First Report (New York 1848), 197).
+No single section of the code announced its preference for creditors' rights; rather, the acceleration of creditors' remedies resulted from the combination of several sections.
+In the original enacted Code, § 107 required a defendant to answer the complaint within twenty days, instead of at the next court session (which in some cases could have been as far as three months away); § 202 provided for default judgment as a matter of course, issued by a clerk without a judicial order if no adequate answer was received within the twenty days; §§ 128-133 abolished fictitious pleadings and required answers to state true facts verified by a defendant's oath, all so that no trial would delay the enforcement of uncontestable obligations; finally, the code abolished a traditional thirty-day waiting period between issue of judgment and commencement of execution (see First Report (New York 1848), 197).
 These provisions dealt with what merchants and capitalists perceived as an abuse of the common law system, where defendants in cases of debt could stretch out enforcement of debt collection for as long as two years.
 The Field code's summary judgment brought down the time of debt collection to a matter of weeks.
-Effectively, the Code traded the rhythms of agriculture for the rhythms of merchant finance.[^50]
+Effectively, the code traded the rhythms of agriculture for the rhythms of merchant finance.[^50]
 
@@
 
-Alerted by these clustering patterns to the significance of creditors' remedies in the developing West and re-developing South, it was not difficult to find evidence of westerners and southerners commenting on these features of the Code or its connections to New York capital.
+Alerted by these clustering patterns to the significance of creditors' remedies in the developing West and re-developing South, it was not difficult to find evidence of westerners and southerners commenting on these features of the code or its connections to New York capital.
 Twelve of the states and territories that copied the Field Code mostly closely did so during the Civil War and Reconstruction era---four states in the former Confederacy and eight jurisdictions in the Far West.[^51] As with other areas of postbellum historiography, it turns out one may learn a lot by holding the postellum American South and American West together.
@@
 
-With the universal complaints that time was too short or commissioners too democratically irresponsible, one might expect the Code to have faced more competition from other workable statutes.
+With the universal complaints that time was too short or commissioners too democratically irresponsible, one might expect the code to have faced more competition from other workable statutes.
 Southern states that drew more on the civilian code tradition such as Louisiana and Alabama offered other options for states desiring to reform common law practice.[^55] And if Euro-Americans believed law had to be imported into the West, Colorado immigrants proved that the common law of Illinois was just as amenable to statutory importation as New York law.[^56] But what codifiers saw when they looked at New York, more so than Louisiana, Alabama, or Illinois, was the Empire State of commercial capital.
@@
 
-Receiving innumerable letters complaining that under the Code, "no one will be benefited, except perhaps some Northern Capitalists," a North Carolina commissioner undertook an anonymous defense of the new Code in the *Weekly Standard*.
+Receiving innumerable letters complaining that under the code, "no one will be benefited, except perhaps some Northern Capitalists," a North Carolina commissioner undertook an anonymous defense of the new Code in the *Weekly Standard*.
 He encouraged the bar to accommodate themselves to change, for "the New York system .
@@
 .
-bids fair to become national." Putatively offering an overview of the Code, the articles were almost entirely about credit.
+bids fair to become national." Putatively offering an overview of the code, the articles were almost entirely about credit.
 "How can we create credit?
@@
 by law, and by law alone.
-Let the law enforce punctuality; let the people of North Carolina learn that the great law of business is, that 'time is of the essence of the contract,' and incur no debt that they do not expect to meet at maturity." Under the more certain and speedy remedies of the Code, "we may expect that the secret hoards of the frugal among ourselves will be offered to loan, and even that the vaults of the banks of New-York .
+Let the law enforce punctuality; let the people of North Carolina learn that the great law of business is, that 'time is of the essence of the contract,' and incur no debt that they do not expect to meet at maturity." Under the more certain and speedy remedies of the code, "we may expect that the secret hoards of the frugal among ourselves will be offered to loan, and even that the vaults of the banks of New-York .
 .
@@
 While the so-called new western history has shed significant light on neglected topics of Indian dispossession and environmental management, it has often done so by leaving out of view matters of political economy, a staple of the old western history.
-As one work in that older tradition argued, "Debt collection was the central part of law practice for the [western] bar and remained a key part of private practice throughout the century."[^62] On that understanding, one western lawyer succinctly summarized the difference between the Code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, .
+As one work in that older tradition argued, "Debt collection was the central part of law practice for the [western] bar and remained a key part of private practice throughout the century."[^62] On that understanding, one western lawyer succinctly summarized the difference between the code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, .
 .
@@
 
-The creditors' remedies in the Code gave the codifiers their leading argument against criticisms rooted in the ideology of popular sovereignty.
+The creditors' remedies in the code gave the codifiers their leading argument against criticisms rooted in the ideology of popular sovereignty.
 "There is no doubt but the people are in favor of anything that promises to hurry up that proverbially slow and blind old female called Justice, and they will go for the old code," one Colorado newspaper announced.[^64] New York's "code practice is the best in excellence," stated another, "and when I say *best* I do not mean best for lawyers only, but best for the people---the commonwealth."[^65] If the People favored economic progress, certainty of remedy, and efficiency in proceedings, then they favored the New York Code, no matter whether they understood or cared about technical rules of pleading and joinder.
@@
 In America, Macaulay's tool of enlightened despotism spread with the anxiety that capital from the nation's economic center would remain scarce without a Code of remedies that, if not in fact the law of New York, was at least prescribed by New York lawyers and their corporate clients.
-In the two most populous and commercially advanced western states, Texas and Illinois, the need for New York capital failed to move state legislators to adopt the Code at the expense of popular sovereignty (although there were concerted efforts in both jurisdictions).[^70] Lacking the self-sufficiency of those two jurisdictions, the other states of the Greater Reconstruction in America adopted a foreign Code, but lawyers, legislators, and their supporters claimed the endorsement of popular sovereignty in doing so.
+In the two most populous and commercially advanced western states, Texas and Illinois, the need for New York capital failed to move state legislators to adopt the code at the expense of popular sovereignty (although there were concerted efforts in both jurisdictions).[^70] Lacking the self-sufficiency of those two jurisdictions, the other states of the Greater Reconstruction in America adopted a foreign Code, but lawyers, legislators, and their supporters claimed the endorsement of popular sovereignty in doing so.
 Even in North Carolina, whose Democratic newspapers daily called for the repeal "this child of the carpet baggers," Republican editors proclaimed that "the movement" towards procedural codification "comes from the people, from the instinctive logic by which an unprejudiced mind grasps the advantages of the system."[^71]
@@
 
-In the economically developing West and re-developing South, anxieties over the lack of capital---both among the bar as well as lay voters---joined with arguments of civilization and progress to spur many jurisdictions to copy the text of the Code of New York, the Empire State of capital.
+In the economically developing West and re-developing South, anxieties over the lack of capital---both among the bar as well as lay voters---joined with arguments of civilization and progress to spur many jurisdictions to copy the text of the code of New York, the Empire State of capital.
 The short time horizons of American lawmaking limited the options available for reimagining or recrafting what could become the law of remedies and legal practice.

### 2016-06-24 article/article.Rmd
Give part 1 a title
Revisions to part 1

@@
 
-# Part 1
+# The origin and migration of the Field Code
 
@@
 
-Most importantly, the code defined all the remedies that a civil court could order---from money damages, to partition of property, to injunctive decrees and contempts--and made those remedies available in every lawsuit.
-In many cases, a legal right was indistinguishable from the remedy that secured that right: The right to possess a particular piece of property and the remedy that seized and delivered that property were, in effect, the same thing.
+Most important, the code defined all the remedies that a civil court could order---from money damages, to partition of property, to injunctive decrees and contempts---and made those remedies available in every lawsuit.
+In many cases, a legal right was indistinguishable from the remedy that secured that right: the right to possess a particular piece of property and the remedy that seized and delivered that property were, in effect, the same thing.
 Remedies were thus intimately connected to substantive law.
-For that reason, neither the French *code de procédure civile* (1806) nor Blackstone's or Bentham's writings conceived of remedies as purely procedural.[^22] By codifying remedies, Field invited continual expansion of the category of "procedure." As other states adopted the procedure code, they sometimes included other fields of law that seemed paradigmatically "substantive" yet had such specific procedures or remedies that they too were placed in a "code of procedure," including the law of wills, corporations, or mortgages.[^23] And after all, argued procedural codifiers in Iowa, what did the famed Married Women's Property Acts offer besides procedural reform?
+For that reason, neither the French *code de procédure civile* (1806) nor Blackstone's or Bentham's writings conceived of remedies as purely procedural.[^22] By codifying remedies, Field invited continual expansion of the category of "procedure." As other states adopted the procedure code, they sometimes included other fields of law that seemed obviously "substantive" yet had such specific procedures or remedies that they were placed in a "code of procedure," including the law of wills, corporations, and mortgages.[^23] After all, argued procedural codifiers in Iowa, what did the famed Married Women's Property Acts offer besides procedural reform?
 These acts gave women *standing* to litigate in their own name and seek *remedies* in claims of property and contract, and they abolished mandatory rules of *joinder* (of husbands).
@@
 Despite Field's arguments that a mere procedure code was democratically unproblematic, his efforts were not entirely successful in New York.
-The commission submitted a draft of its main reforms in 1848, emphasizing that this first code was "but a report in part." New York's legislators enacted the partial code with little amendment, some legislators repeating Field's view that the constitution obligated them to accept the code.[^25] But when the commissioners submitted their final draft, the Assembly judiciary committee balked, directly disputing the commissioners' claims that procedure was merely the machinery of the law.
-They wrote that "provisions for rights and for the mode of pursuing remedies, insensibly run into each other," and distinctions between substance and procedure were difficult to draw in practice.
-In fact, "the parts of a system of law are more dependent on each other, and run into and affect each other, infinitely more than any machine of human contrivance." Procedure, at least in the common law tradition, was no mere machinery---it involved the entire legal apparatus.
+The commission submitted a draft of its main reforms in 1848, emphasizing that this first code was "but a report in part." New York's legislators enacted the partial code with little amendment, some legislators repeating Field's view that the constitution obligated them to accept the code.[^25] But when the commissioners submitted their final draft in 1849, the Assembly judiciary committee balked, directly disputing the commissioners' claims that procedure was merely the machinery of the law.
+They wrote that "provisions for rights and for the mode of pursuing remedies, insensibly run into each other," and observed that distinctions between substance and procedure were difficult to draw in practice.
+In fact, "the parts of a system of law are more dependent on each other, and run into and affect each other, infinitely more than any machine of human contrivance." Procedure, at least in the common law tradition, was no mere machinery; it involved the entire legal apparatus.
 They therefore suspected the commissioners' forthcoming code of criminal procedure would include all of the criminal law as well, "as they seem to understand practice and pleadings to include all the law upon a given subject." That being the case, the committee wondered whether, "responsible as the Commissioners undoubtedly are, should we place in them a blind and implicit confidence that shall commit to their discretion the peace and property, the personal liberty and the lives of those who sent *us* here to make laws for them?"[^26]
@@
 See Lobban, *The Common Law and English Jurisprudence*, 127-131, 146-151.
-As Amalia Kessler notes, *Bouvier's Law Dictionary* did not even define *civil procedure* until its 1897 edition, describing the term as "rather a modern one." Amalia Kessler, "Deciding Against Conciliation: The Nineteenth-Century Rejection of a European Transplant and the Rise of a Distinctively American Ideal of Adversarial Adjudication, 10 *Theoretical Inquiries in Law* 423 (2009), 481-482; *Bouvier's Law Dictionary* (1897), 2:764.
+As Amalia Kessler notes, *Bouvier's Law Dictionary* did not even define *civil procedure* until its 1897 edition, describing the term as "rather a modern one." Amalia Kessler, "Deciding Against Conciliation: The Nineteenth-Century Rejection of a European Transplant and the Rise of a Distinctively American Ideal of Adversarial Adjudication," 10 *Theoretical Inquiries in Law* 423 (2009), 481-482; *Bouvier's Law Dictionary* (1897), 2:764.
 Before 1848, the term was largely restricted to French usage, and American remedial law had carried the typical designation---as it did both in Graham's treatise and professorial title---of "practice and pleadings," the name likewise given to the reform commission.

### 2016-06-24 article/article.Rmd
Remove point made in previous paragraph

@@
 They wrote that "provisions for rights and for the mode of pursuing remedies, insensibly run into each other," and observed that distinctions between substance and procedure were difficult to draw in practice.
-In fact, "the parts of a system of law are more dependent on each other, and run into and affect each other, infinitely more than any machine of human contrivance." Procedure, at least in the common law tradition, was no mere machinery; it involved the entire legal apparatus.
-They therefore suspected the commissioners' forthcoming code of criminal procedure would include all of the criminal law as well, "as they seem to understand practice and pleadings to include all the law upon a given subject." That being the case, the committee wondered whether, "responsible as the Commissioners undoubtedly are, should we place in them a blind and implicit confidence that shall commit to their discretion the peace and property, the personal liberty and the lives of those who sent *us* here to make laws for them?"[^26]
+In fact, "the parts of a system of law are more dependent on each other, and run into and affect each other, infinitely more than any machine of human contrivance." They therefore suspected the commissioners' forthcoming code of criminal procedure would include all of the criminal law as well, "as they seem to understand practice and pleadings to include all the law upon a given subject." That being the case, the committee wondered whether, "responsible as the Commissioners undoubtedly are, should we place in them a blind and implicit confidence that shall commit to their discretion the peace and property, the personal liberty and the lives of those who sent *us* here to make laws for them?"[^26]
 

### 2016-06-24 article/article.Rmd
Trim quotation

@@
 They wrote that "provisions for rights and for the mode of pursuing remedies, insensibly run into each other," and observed that distinctions between substance and procedure were difficult to draw in practice.
-In fact, "the parts of a system of law are more dependent on each other, and run into and affect each other, infinitely more than any machine of human contrivance." They therefore suspected the commissioners' forthcoming code of criminal procedure would include all of the criminal law as well, "as they seem to understand practice and pleadings to include all the law upon a given subject." That being the case, the committee wondered whether, "responsible as the Commissioners undoubtedly are, should we place in them a blind and implicit confidence that shall commit to their discretion the peace and property, the personal liberty and the lives of those who sent *us* here to make laws for them?"[^26]
+In fact, "the parts of a system of law are more dependent on each other, and run into and affect each other, infinitely more than any machine of human contrivance." They therefore suspected the commissioners' forthcoming code of criminal procedure would include all of the criminal law as well, "as they seem to understand practice and pleadings to include all the law upon a given subject." That being the case, the committee wondered whether they should "place in [the commissioners] a blind and implicit confidence that shall commit to their discretion the peace and property, the personal liberty and the lives of those who sent *us* here to make laws for them?"[^26]
 

### 2016-06-24 article/article.Rmd
Typos and other assorted changes

@@
 Even the shortest version of the Field Code was significantly longer than any other state statute before the Progressive legislation of the twentieth century.
-And unlike statutory complilations that sometimes took the name of a "code" but made no changes to existing law, the Field Code opened with a declaration of novelty, abolishing the hallmarks of prior practice and instituting "hereafter" a new form of action with substantial revisions to basic matters of standing, remedy, and enforcement of civil judgments.[^27] In the states where it was imported, there could be no getting around the fact that the code introduced extensive, new law, yet legislators were unable to read, critique, and amend the code within the short time horizons of a legislative session.
+And unlike statutory compilations that sometimes took the name of a "code" but made no changes to existing law, the Field Code opened with a declaration of novelty, abolishing the hallmarks of prior practice and instituting "hereafter" a new form of action with substantial revisions to basic matters of standing, remedy, and enforcement of civil judgments.[^27] In the states where it was imported, there could be no getting around the fact that the code introduced extensive, new law, yet legislators were unable to read, critique, and amend the code within the short time horizons of a legislative session.
 "It is folly to undertake to pass a code in a sixty day session," wrote the *Montana Post*, "and the best way would be for the Assembly to select one from a State or Territory which would come near meeting our wants, and slide it through with the fewest changes possible."[^28] Sliding the code through eased the problem of time but exacerbated the problem of local sovereignty.
-"To be governed by a foreign law, especially when that law is not preknown to the people whose conduct is to be regulated thereby .
-.
-.
+"To be governed by a foreign law, especially when that law is not preknown to the people whose conduct is to be regulated thereby ...
 is something repugnant to the idea of Democratic Republican government," complained the *The Miner's Express*.[^29]
@@
 Finally, our corpus included a number of statutes which stood outside the Field Code tradition, such as Virginia and West Virginia regulations, statutes from Massachusetts and Maine, and southern codes from Georgia to Louisiana.
-These statutes show that the dominance of the Field Code was not total, and a number of older jurisdictions remained outside of its ambit.[^41] But virtually every jurisdiction established or reconstructed after 1850 became a part of the the Field Code network, and no other tradition achieved anywhere near the same coherence across state lines.
+These statutes show that the dominance of the Field Code was not total, and a number of older jurisdictions remained outside of its ambit.[^41] But virtually every jurisdiction established or reconstructed after 1850 became a part of the Field Code network, and no other tradition achieved anywhere near the same coherence across state lines.
 
@@
 As the code migrated West, however, legislators added racial exclusions to Field's list.
-The following cluster documents how California's codifiers engrafted earlier prohibitions from midwestern states into Field's Code.
+The following cluster documents how California's codifiers grafted earlier prohibitions from midwestern states into Field's Code.
 Many other codes then evidence a remarkable uniformity with California's text (which later changed only to add "Mongolian" to the list of races).
@@
 Alerted by these clustering patterns to the significance of creditors' remedies in the developing West and re-developing South, it was not difficult to find evidence of westerners and southerners commenting on these features of the code or its connections to New York capital.
-Twelve of the states and territories that copied the Field Code mostly closely did so during the Civil War and Reconstruction era---four states in the former Confederacy and eight jurisdictions in the Far West.[^51] As with other areas of postbellum historiography, it turns out one may learn a lot by holding the postellum American South and American West together.
+Twelve of the states and territories that copied the Field Code mostly closely did so during the Civil War and Reconstruction era---four states in the former Confederacy and eight jurisdictions in the Far West.[^51] As with other areas of postbellum historiography, it turns out one may learn a lot by holding the postbellum American South and American West together.
 
@@
 Receiving innumerable letters complaining that under the code, "no one will be benefited, except perhaps some Northern Capitalists," a North Carolina commissioner undertook an anonymous defense of the new Code in the *Weekly Standard*.
-He encouraged the bar to accommodate themselves to change, for "the New York system .
-.
-.
+He encouraged the bar to accommodate themselves to change, for "the New York system ...
 bids fair to become national." Putatively offering an overview of the code, the articles were almost entirely about credit.
@@
 by law, and by law alone.
-Let the law enforce punctuality; let the people of North Carolina learn that the great law of business is, that 'time is of the essence of the contract,' and incur no debt that they do not expect to meet at maturity." Under the more certain and speedy remedies of the code, "we may expect that the secret hoards of the frugal among ourselves will be offered to loan, and even that the vaults of the banks of New-York .
-.
-.
+Let the law enforce punctuality; let the people of North Carolina learn that the great law of business is, that 'time is of the essence of the contract,' and incur no debt that they do not expect to meet at maturity." Under the more certain and speedy remedies of the code, "we may expect that the secret hoards of the frugal among ourselves will be offered to loan, and even that the vaults of the banks of New-York ...
 will be open to our industry."[^61]
@@
 While the so-called new western history has shed significant light on neglected topics of Indian dispossession and environmental management, it has often done so by leaving out of view matters of political economy, a staple of the old western history.
-As one work in that older tradition argued, "Debt collection was the central part of law practice for the [western] bar and remained a key part of private practice throughout the century."[^62] On that understanding, one western lawyer succinctly summarized the difference between the code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, .
-.
-.
+As one work in that older tradition argued, "Debt collection was the central part of law practice for the [western] bar and remained a key part of private practice throughout the century."[^62] On that understanding, one western lawyer succinctly summarized the difference between the code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, ...
 that he did not also break out somewhere with 'take for instance the case of an action on a promissory note,' as though the collection of notes was about all there could be any law needed for."[^63]
@@
 In the economically developing West and re-developing South, anxieties over the lack of capital---both among the bar as well as lay voters---joined with arguments of civilization and progress to spur many jurisdictions to copy the text of the code of New York, the Empire State of capital.
-The short time horizons of American lawmaking limited the options available for reimagining or recrafting what could become the law of remedies and legal practice.
+The short time horizons of American lawmaking limited the options available for re-imagining or re-crafting what could become the law of remedies and legal practice.
 And in the economically underdeveloped parts of the country, time horizons could be short indeed.

### 2016-06-24 article/article.Rmd
Revisions to part 1

@@
 Even the shortest version of the Field Code was significantly longer than any other state statute before the Progressive legislation of the twentieth century.
-And unlike statutory compilations that sometimes took the name of a "code" but made no changes to existing law, the Field Code opened with a declaration of novelty, abolishing the hallmarks of prior practice and instituting "hereafter" a new form of action with substantial revisions to basic matters of standing, remedy, and enforcement of civil judgments.[^27] In the states where it was imported, there could be no getting around the fact that the code introduced extensive, new law, yet legislators were unable to read, critique, and amend the code within the short time horizons of a legislative session.
+And unlike statutory compilations that sometimes took the name of a "code" but made no changes to existing law, the Field Code opened by abolishing the hallmarks of prior practice and instituting "hereafter" a new form of action with substantial revisions to basic matters of standing, remedy, and enforcement of civil judgments.[^27] In the states where it was imported, there was be no getting around the fact that the code introduced much new law, yet legislators were unable to read, critique, and amend the code within the brief period of a legislative session.
 "It is folly to undertake to pass a code in a sixty day session," wrote the *Montana Post*, "and the best way would be for the Assembly to select one from a State or Territory which would come near meeting our wants, and slide it through with the fewest changes possible."[^28] Sliding the code through eased the problem of time but exacerbated the problem of local sovereignty.
 "To be governed by a foreign law, especially when that law is not preknown to the people whose conduct is to be regulated thereby ...
-is something repugnant to the idea of Democratic Republican government," complained the *The Miner's Express*.[^29]
+is something repugnant to the idea of Democratic Republican government," complained the *The Miner's Express* in Iowa.[^29]
 
 How, then, did states and territories achieve a politically acceptable balance between efficiency and sovereignty, borrowing law for sake of time but endowing it with popular legitimacy in each locale?
-Quite apart from the technicalities of legal practice, answering that question historically is daunting.
-The American federation of civil government into (depending on the period) more than thirty or forty separate jurisdictions creates significant difficulties for describing a phenomenon that was truly national despite its state-centered enactments.
-It requires some sense of how much law was borrowed in each locality and to what degree and significance innovations were introduced.
-But precisely because these questions concern codes---texts that comprehensively and systematically cover a given subject---they are ideal for innovative techniques in digital history.
+Quite apart from the technicalities of legal practice, the American federation of civil government into (depending on the year) more than thirty or forty separate state jurisdictions makes it hard to  describe a phenomenon that was truly national despite its state-centered enactments.
+It requires a sense of how much law was borrowed in each location and to what degree innovations were introduced.
+But precisely because these questions concern codes---texts that comprehensively and systematically cover a given subject---they are ideal sources for the techniques of digital history.
 

### 2016-06-24 article/article.Rmd
Give part 2 a title

@@
   pdf_document:
-    number_sections: true
+    number_sections: false
     fig_caption: true
@@
 
-# The origin and migration of the Field Code
+# 1. The origin and migration of the Field Code
 
@@
 
-# Part 2
+# 2. Detecting borrowings among procedure codes
 

### 2016-06-24 article/article.Rmd
Delicate section on DH

@@
 ---
-title: The Spine of American Legal Practice
 author:
@@
 - Lincoln Mullen
+documentclass: article
+fontsize: 12pt
 output:
   pdf_document:
-    number_sections: false
-    fig_caption: true
-fontsize: 12pt
-documentclass: article
+    fig_caption: True
+    number_sections: False
+title: The Spine of American Legal Practice
 ...
@@
 Each time they reminded legislators that "public opinion had issued its mandate in the most imposing form" of a constitutional decree.
-The constitution, together with the legislative act appointing the commission, "gave the commissioners instructions so precise, as to leave them no discretion, if they had desired it, [and] promised them therefore in advance, so long as they obeyed those instructions, the concurrence and co-operation of all departments of the government."[^16] Although the theory of codification made it a democratic enterprise, in practice Field---an ardent Jacksonian---insisted the democratic legislature ought to defer to the expertise of the commissioners.
+The constitution, together with the legislative act appointing the commission, "gave the commissioners instructions so precise, as to leave them no discretion, if they had desired it, \[and\] promised them therefore in advance, so long as they obeyed those instructions, the concurrence and co-operation of all departments of the government."[^16] Although the theory of codification made it a democratic enterprise, in practice Field---an ardent Jacksonian---insisted the democratic legislature ought to defer to the expertise of the commissioners.
 
@@
 They wrote that "provisions for rights and for the mode of pursuing remedies, insensibly run into each other," and observed that distinctions between substance and procedure were difficult to draw in practice.
-In fact, "the parts of a system of law are more dependent on each other, and run into and affect each other, infinitely more than any machine of human contrivance." They therefore suspected the commissioners' forthcoming code of criminal procedure would include all of the criminal law as well, "as they seem to understand practice and pleadings to include all the law upon a given subject." That being the case, the committee wondered whether they should "place in [the commissioners] a blind and implicit confidence that shall commit to their discretion the peace and property, the personal liberty and the lives of those who sent *us* here to make laws for them?"[^26]
+In fact, "the parts of a system of law are more dependent on each other, and run into and affect each other, infinitely more than any machine of human contrivance." They therefore suspected the commissioners' forthcoming code of criminal procedure would include all of the criminal law as well, "as they seem to understand practice and pleadings to include all the law upon a given subject." That being the case, the committee wondered whether they should "place in \[the commissioners\] a blind and implicit confidence that shall commit to their discretion the peace and property, the personal liberty and the lives of those who sent *us* here to make laws for them?"[^26]
 
@@
 
-Although the amount of legislation that governed American civil practice is impressive---even if uncodified, every state had procedure statutes that were amended and re-enacted nearly every decade---a corpus of procedural legislation would not even count among digital historians as "big data." Our collection of relevant (or possibly relevant) laws comprise 135 statutes from the nineteenth century.
-It includes separately bound codes of civil procedure as well as codes or regulations appearing session laws and statutory compilations.[^30] It comprises some TODO pages, TODO words, organized into 98,000 regulations.
-The corpus is not exhaustive.
-It includes the initial enactment of every code of civil procedure, as well as a sampling of procedure statutes and re-enacted codes from states reputed to have been legally influential, but it does not include every known statute of American procedural law.
-While a comprehensive project may be illuminating in its own ways, our specific question of how New York legislation influenced other states permits a more curated corpus.
+To discover how the Field Code migrated to other jurisdictions, we compiled a corpus of relevant (or possibly relevant) laws, including separately bound codes of civil procedure as well as codes or regulations appearing as session laws and statutory compilations.
+The corpus comprises 135 statutes from the nineteenth century, which amounts to 7.7 million words organized into 98,000 regulations.
+It includes the initial enactment of every code of civil procedure, as well as procedure statutes and re-enacted codes from states reputed to have been legally influential, but it does not include every known statute of American procedural law.
+While a comprehensive project may be illuminating in its own ways, our specific question of how New York legislation influenced other states permits a more curated corpus.[^30]
 
-Curating a corpus to answer a question is an important difference from the way that digital history work often describes itself.
-Speaking in broad terms, digital historical work---like all historical work---can either begin with a set of sources or a question.[^31] Digital history often emphasizes that it can begin with large datasets---the so-called "big data" which recently achieved the level of buzzword---such as the Google Books or Hathi Trust corpora.[^32] We think that this is indeed a worthwhile endeavor, and salutary for historians to have their questions shaped by the sources.[^33] But it is less apparent that historians can apply digital history methods to questions that they have already formed, or that the only thing that these methods, most notably of "distant reading" can do is to work at the absolute largest scales.
-Our method, which might unimaginatively named "medium data" is a useful way for historians to proceed, by finding a corpus which is bounded by a particular problem.
+Curating a corpus to answer a specific question is an important difference from the way that digital history often describes itself.
+Speaking in broad terms, digital historical work---like all historical work---can begin either with a set of sources or a question.
+Digital history is often conceived of as working with very large datasets such as the Google Books or Hathi Trust corpora.
+These large corpora are sometimes called "big data"---though, it must be emphasized, almost never by digital historians who actually work with them---and are used as the basis of a "distant reading." We think that working with these large corpora is worthwhile because it is salutary for historians to have their research questions shaped by the broadest possible contexts.
+Nevertheless, it is not apparent that digital historians can readily move from these omnibus corpora to answering the specific research questions that animate historical fields.
+In this article we demonstrate an alternative approach, which we might unimaginatively label "medium data." Although the amount of legislation that governed American civil practice is impressive---every state amended and re-enacted procedure statutes nearly every decade---a corpus of procedural legislation requires some computational sophistication but is far from needing the computational techniques derived for truly big data.
+We have gathered a large but narrowly constrained corpus centered on solving a well-defined research question.
+This corpus is large enough that digital historical methods provide results that a scholar could not obtain through traditional methods, but sufficiently circumscribed so as to directly address a discipline- and field-specific question.[^31]
 
@@
 Where possible, we collected our corpus from Google's publicly accessible database.
-We used optical character recognition software (OCR) to create plain-text versions of the codes, which we edited lightly---we corrected section markers by hand as necessary and wrote a script to fix the most common OCR errors.[^34]
+We used optical character recognition software (OCR) to create plain-text versions of the codes, which we edited lightly---we corrected section markers by hand as necessary and wrote a script to fix the most common OCR errors.[^32]
 
@@
 Codes varied in their organizations, but they universally divided specific regulations into *sections* (or, on occasion, *articles*).
-The discursive formation of these texts not only provides a handy organizational scheme for digital approaches, sections were historically the way legislators borrowed their texts.[^35] Codifiers took their sources apart by sections, rearranging here, editing, drafting, and then re-combining there.
+The discursive formation of these texts not only provides a handy organizational scheme for digital approaches, sections were historically the way legislators borrowed their texts.[^33] Codifiers took their sources apart by sections, rearranging here, editing, drafting, and then re-combining there.
 Despite the fact that states differed widely on what topics they included in "civil procedure," sectioning the codes allowed us to assess similarity even among codes of quite different lengths and coverage.
 For instance, we know from historical evidence that California's 1851 code was derived from New York's 1850 code.
-(Stephen Johnson Field, David Dudley's brother, was the lawyer who imported New York's code into California.[^36]) But the New York code is over 150,000 words long, where was California's code was just over 50,000 words long.
+(Stephen Johnson Field, David Dudley's brother, was the lawyer who imported New York's code into California.[^34]) But the New York code is over 150,000 words long, where was California's code was just over 50,000 words long.
 Those rather disparate lengths mean that comparing all of the California code to all of the New York code is a less meaningful comparison that than comparing each section in the California code to each section in the New York code, where matching sections will be a similar length.
@@
 
-The pairs are obviously related to one another, both in terms of their legal force and in terms of the actual words used.[^37]
+The pairs are obviously related to one another, both in terms of their legal force and in terms of the actual words used.[^35]
 
@@
 
-| NY1850-554 | NY1850-555 | CA1851-001 | CA1851-002 |
+NY1850-554 | NY1850-555 | CA1851-001 | CA1851-002 |
 
@@
 This would take an unreasonable amount of computation time, and most of these comparisons would be unnecessary, since each section has no relationship to most other sections (like the matrix above, most scores will be zero).
-We therefore implemented the minhash/locality sensitive hashing (LSH) algorithm to detect candidate pairs, that is, documents which were likely to be matches, and then we measured the Jaccard score for only those candidate pairs.[^38]
+We therefore implemented the minhash/locality sensitive hashing (LSH) algorithm to detect candidate pairs, that is, documents which were likely to be matches, and then we measured the Jaccard score for only those candidate pairs.[^36]
 
 The result was a matrix of matches, with over 45,000 genuine matches.
-For each section in the corpus, after making some adjustments to remove anachronisms and spurious matches,[^39] we were able to identify the section from which it was most likely borrowed.
+For each section in the corpus, after making some adjustments to remove anachronisms and spurious matches,[^37] we were able to identify the section from which it was most likely borrowed.
 In other words, we had traced the work of the commissioners' scissors and paste-pots through the course of their codes.
@@
 The resulting network graph (**Figure X: Network Graph**) tells the genealogy of civil procedure in the United States.
-The New York codes, especially the finished draft of 1850, are central to the entire network.[^40] Yet it is important to note that New York spurred different traditions within the procedural network.
+The New York codes, especially the finished draft of 1850, are central to the entire network.[^38] Yet it is important to note that New York spurred different traditions within the procedural network.
 Variations in the Field drafts meant that different states could borrow different versions of the Field Code.
@@
 A count by a "friend" of Field's found that only three sentences of the Field Code had carried over word-for-word into the Throop Code.
-Nevertheless, many of the changes were purely formal, and Field speculated that these changes had been made only "so that [the code] should not appear to be the same thing as before." With respect to Mr.
+Nevertheless, many of the changes were purely formal, and Field speculated that these changes had been made only "so that \[the code\] should not appear to be the same thing as before." With respect to Mr.
 Field or his "friend," we were able to find that the connection was between the Throop Code and the Field Code was somewhat stronger than he thought, and the Throop Code was indeed a descendant, if much revised, from the Field Code.
@@
 Finally, our corpus included a number of statutes which stood outside the Field Code tradition, such as Virginia and West Virginia regulations, statutes from Massachusetts and Maine, and southern codes from Georgia to Louisiana.
-These statutes show that the dominance of the Field Code was not total, and a number of older jurisdictions remained outside of its ambit.[^41] But virtually every jurisdiction established or reconstructed after 1850 became a part of the Field Code network, and no other tradition achieved anywhere near the same coherence across state lines.
+These statutes show that the dominance of the Field Code was not total, and a number of older jurisdictions remained outside of its ambit.[^39] But virtually every jurisdiction established or reconstructed after 1850 became a part of the Field Code network, and no other tradition achieved anywhere near the same coherence across state lines.
 
@@
 California's 1851 code borrowed heavily from two sources.
-The bulk of the code was taken directly from New York's 1849 or 1850 codes (which are difficult to distinguish exactly from one another.[^42] The remainder of the code was borrowed from California's 1850 code.
+The bulk of the code was taken directly from New York's 1849 or 1850 codes (which are difficult to distinguish exactly from one another.[^40] The remainder of the code was borrowed from California's 1850 code.
 The 1850 version was in turn borrowed from the New York codes **TODO: might as well show this, esp.
@@
 The bulk of this code was lifted from the Washington 1855 code with only small amendments.
-The main exception was a probate code drawn from California's 1872 code.[^43] Like many of the last generation codes, the text of the procedure code had stabilized in a local manifestation of a regional tradition.
+The main exception was a probate code drawn from California's 1872 code.[^41] Like many of the last generation codes, the text of the procedure code had stabilized in a local manifestation of a regional tradition.
 The code was still genuinely a Field Code, with a great deal of similarity to the original New York Field Codes, but its specific form depended on the many edits and rearrangements that state code commissioners had made to the text.
@@
 So far we have retained the context of the surrounding sections within a particular code.
-But since our fundamental unit of comparison is section to section, we can use a technique called clustering to deform the texts (as a literary scholar might say) in order to see the textual history of how particular regulations embedded in individual sections changed over time.[^44]
+But since our fundamental unit of comparison is section to section, we can use a technique called clustering to deform the texts (as a literary scholar might say) in order to see the textual history of how particular regulations embedded in individual sections changed over time.[^42]
 
@@
 There are innumerable clustering algorithms, but we needed one that could work with a sparse matrix and one whose assumptions matched the characteristics of our problem.
-We decided to use affinity propagation clustering.[^45] That algorithm assumes that each cluster has an "exemplar" item which the other items are similar to.
-That assumption fits nicely with borrowings from the Field Code, where a single section (likely from the 1850 New York code) had many borrowings, but where there could also be innovative sections in other stages.[^46]
+We decided to use affinity propagation clustering.[^43] That algorithm assumes that each cluster has an "exemplar" item which the other items are similar to.
+That assumption fits nicely with borrowings from the Field Code, where a single section (likely from the 1850 New York code) had many borrowings, but where there could also be innovative sections in other stages.[^44]
 
@@
 The biggest cluster, for instance, which concerned the use of affidavits in pleading, contained 103 sections.
-With those clusters, we were able to organize the documents chronologically.[^47] This method is particularly useful when tracking the variations in in the law from jurisdiction to jurisdiction.
+With those clusters, we were able to organize the documents chronologically.[^45] This method is particularly useful when tracking the variations in in the law from jurisdiction to jurisdiction.
 It provides historians with a way of noticing small changes in the wording and substance of the law.
-Most discussions of algorithmic reading have focused on "distant reading,"[^48] or have balanced the claims of distant reading by using it as a means to enable close reading.
+Most discussions of algorithmic reading have focused on "distant reading,"[^46] or have balanced the claims of distant reading by using it as a means to enable close reading.
 This method of clustering, however, is a kind of algorithmic close reading.
-By deforming the texts---taking them out of the context of the codes and putting them in the context of their particular variations---we are able to pay attention to those variations.[^49]
+By deforming the texts---taking them out of the context of the codes and putting them in the context of their particular variations---we are able to pay attention to those variations.[^47]
 
@@
 The Field code's summary judgment brought down the time of debt collection to a matter of weeks.
-Effectively, the code traded the rhythms of agriculture for the rhythms of merchant finance.[^50]
+Effectively, the code traded the rhythms of agriculture for the rhythms of merchant finance.[^48]
 
@@
 Alerted by these clustering patterns to the significance of creditors' remedies in the developing West and re-developing South, it was not difficult to find evidence of westerners and southerners commenting on these features of the code or its connections to New York capital.
-Twelve of the states and territories that copied the Field Code mostly closely did so during the Civil War and Reconstruction era---four states in the former Confederacy and eight jurisdictions in the Far West.[^51] As with other areas of postbellum historiography, it turns out one may learn a lot by holding the postbellum American South and American West together.
+Twelve of the states and territories that copied the Field Code mostly closely did so during the Civil War and Reconstruction era---four states in the former Confederacy and eight jurisdictions in the Far West.[^49] As with other areas of postbellum historiography, it turns out one may learn a lot by holding the postbellum American South and American West together.
 
-In the last decade, scholars of Reconstruction have broadened the scope of their study to include both the South and the West as two sites in one "Greater Reconstruction." These studies have illustrated the ways that military conquest, rapid industrialization, and the resettlement and education of ethnic minorities developed similarly in each region, guided by economic elites in New York and political administrators in Washington.[^52] In tracing the legal aspects of this Greater Reconstruction, scholars have focused almost entirely on constitutional rights of citizenship and civil equality or the expansion of federal power.[^53] While the 1860s and 1870s were of course a transformative period in the history of civil rights and the creation of a national state, they were also the decades in which many local legal institutions and practices were transformed not by federal power but by state codification.
+In the last decade, scholars of Reconstruction have broadened the scope of their study to include both the South and the West as two sites in one "Greater Reconstruction." These studies have illustrated the ways that military conquest, rapid industrialization, and the resettlement and education of ethnic minorities developed similarly in each region, guided by economic elites in New York and political administrators in Washington.[^50] In tracing the legal aspects of this Greater Reconstruction, scholars have focused almost entirely on constitutional rights of citizenship and civil equality or the expansion of federal power.[^51] While the 1860s and 1870s were of course a transformative period in the history of civil rights and the creation of a national state, they were also the decades in which many local legal institutions and practices were transformed not by federal power but by state codification.
 Naomi Lamoreaux and John Joseph Wallis have recently argued that in the creation of a modern American economy, "the federal government played *no* role in this process until the Civil War, and even then it played only a bit part." The history of the Field Code's migration helps to substantiate this claim.
 While Lamoreaux and Wallis focus on the development of banking, transportation, and incorporation at the state level, it was the Procedure Code that provided the structure of civil remedies that protected these state institutions.
-And procedure codes were, of course, the creatures of state governance.[^54]
+And procedure codes were, of course, the creatures of state governance.[^52]
 
 With the universal complaints that time was too short or commissioners too democratically irresponsible, one might expect the code to have faced more competition from other workable statutes.
-Southern states that drew more on the civilian code tradition such as Louisiana and Alabama offered other options for states desiring to reform common law practice.[^55] And if Euro-Americans believed law had to be imported into the West, Colorado immigrants proved that the common law of Illinois was just as amenable to statutory importation as New York law.[^56] But what codifiers saw when they looked at New York, more so than Louisiana, Alabama, or Illinois, was the Empire State of commercial capital.
+Southern states that drew more on the civilian code tradition such as Louisiana and Alabama offered other options for states desiring to reform common law practice.[^53] And if Euro-Americans believed law had to be imported into the West, Colorado immigrants proved that the common law of Illinois was just as amenable to statutory importation as New York law.[^54] But what codifiers saw when they looked at New York, more so than Louisiana, Alabama, or Illinois, was the Empire State of commercial capital.
 And the putative fears, demands, and desires of a personified Capital continually wielded promises---and threats---in the debates over procedural codification.
 The early Mormon settlers of Utah persistently avoided the mining frenzy as well as codification.
-By 1870, however, the territory's governor directed the legislature's attention to the recent Code of Nevada, a code "for a people whose interests in many respects are similar to our own." Of course, standing behind the Nevada Code was "the State of New York---a State which is an empire in itself and whose commercial transactions are far greater than those of any other State in the Union." By copying its code, Utah too could be "rewarded by equal advantages."[^57] Code proponents in Colorado similarly parried arguments that a code would be a "foreign" imposition by pointing to the fact that it has been "adopted twenty-nine years ago by the Empire state of the Union" and they promised that the code of the nation's uniquely commercial empire could bring wealth in its wake.[^58]
+By 1870, however, the territory's governor directed the legislature's attention to the recent Code of Nevada, a code "for a people whose interests in many respects are similar to our own." Of course, standing behind the Nevada Code was "the State of New York---a State which is an empire in itself and whose commercial transactions are far greater than those of any other State in the Union." By copying its code, Utah too could be "rewarded by equal advantages."[^55] Code proponents in Colorado similarly parried arguments that a code would be a "foreign" imposition by pointing to the fact that it has been "adopted twenty-nine years ago by the Empire state of the Union" and they promised that the code of the nation's uniquely commercial empire could bring wealth in its wake.[^56]
 
@@
 Hamill replied that he knew of one California company of capitalists who were deterred from investing in mining property here wholly on account of the practice of the courts in mining cases.
-If we had had this code years ago, Colorado would now have a larger amount of California capital in her mines."[^59] Codifiers argued that, in attracting capital, procedure was at least as important as the substantive rules of property and contract, because procedure secured the remedies that actually protected investments.
-"Men of capital and enterprise will not make investments and devote their time and energies to those works of internal improvement so necessary for the speedy development of our natural resources, and for the settlement and building up the country," Nebraska's governor reasoned, "unless ample protection is afforded them, by legal enactment, for the capital invested and labor employed." And he therefore urged swift passage of the Field Code.[^60]
+If we had had this code years ago, Colorado would now have a larger amount of California capital in her mines."[^57] Codifiers argued that, in attracting capital, procedure was at least as important as the substantive rules of property and contract, because procedure secured the remedies that actually protected investments.
+"Men of capital and enterprise will not make investments and devote their time and energies to those works of internal improvement so necessary for the speedy development of our natural resources, and for the settlement and building up the country," Nebraska's governor reasoned, "unless ample protection is afforded them, by legal enactment, for the capital invested and labor employed." And he therefore urged swift passage of the Field Code.[^58]
 
@@
 Let the law enforce punctuality; let the people of North Carolina learn that the great law of business is, that 'time is of the essence of the contract,' and incur no debt that they do not expect to meet at maturity." Under the more certain and speedy remedies of the code, "we may expect that the secret hoards of the frugal among ourselves will be offered to loan, and even that the vaults of the banks of New-York ...
-will be open to our industry."[^61]
+will be open to our industry."[^59]
 
@@
 While the so-called new western history has shed significant light on neglected topics of Indian dispossession and environmental management, it has often done so by leaving out of view matters of political economy, a staple of the old western history.
-As one work in that older tradition argued, "Debt collection was the central part of law practice for the [western] bar and remained a key part of private practice throughout the century."[^62] On that understanding, one western lawyer succinctly summarized the difference between the code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, ...
-that he did not also break out somewhere with 'take for instance the case of an action on a promissory note,' as though the collection of notes was about all there could be any law needed for."[^63]
+As one work in that older tradition argued, "Debt collection was the central part of law practice for the \[western\] bar and remained a key part of private practice throughout the century."[^60] On that understanding, one western lawyer succinctly summarized the difference between the code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, ...
+that he did not also break out somewhere with 'take for instance the case of an action on a promissory note,' as though the collection of notes was about all there could be any law needed for."[^61]
 
 The creditors' remedies in the code gave the codifiers their leading argument against criticisms rooted in the ideology of popular sovereignty.
-"There is no doubt but the people are in favor of anything that promises to hurry up that proverbially slow and blind old female called Justice, and they will go for the old code," one Colorado newspaper announced.[^64] New York's "code practice is the best in excellence," stated another, "and when I say *best* I do not mean best for lawyers only, but best for the people---the commonwealth."[^65] If the People favored economic progress, certainty of remedy, and efficiency in proceedings, then they favored the New York Code, no matter whether they understood or cared about technical rules of pleading and joinder.
+"There is no doubt but the people are in favor of anything that promises to hurry up that proverbially slow and blind old female called Justice, and they will go for the old code," one Colorado newspaper announced.[^62] New York's "code practice is the best in excellence," stated another, "and when I say *best* I do not mean best for lawyers only, but best for the people---the commonwealth."[^63] If the People favored economic progress, certainty of remedy, and efficiency in proceedings, then they favored the New York Code, no matter whether they understood or cared about technical rules of pleading and joinder.
 Thus, in their arguments the codifiers imagined themselves the champions of popular sovereignty, for it was they who accomplished what the People actually desired.
@@
 Both jurisdictions, while reforming the practice of law, largely rejected codification within their own borders but encouraged it among their economic dependents.
-The English commissioned a full codification of law for India and colonies in Singapore, while further codifications produced by Field in New York covering civil and penal law were adopted in California and other western jurisdictions.[^66] In both places, leading arguments against codification carried a civilizational logic of empire: Advanced societies could not codify their law, for to do so would be to freeze the progress of legal science.
+The English commissioned a full codification of law for India and colonies in Singapore, while further codifications produced by Field in New York covering civil and penal law were adopted in California and other western jurisdictions.[^64] In both places, leading arguments against codification carried a civilizational logic of empire: Advanced societies could not codify their law, for to do so would be to freeze the progress of legal science.
 What appeared to some to be a hopeless mass of confusion was to common law defenders the sign of true legal sophistication.
-Science was, after all, sophisticated.[^67] The Throop Code came in for censure, both in its first year and in following decades, precisely for trying to capture all the sophistication of the New York legal system within an unwieldy 3,300 rules.[^68] Codification, however, could help developing societies along law's frontier take a progressive leap forward.
-As India's chief codifier Thomas Macaulay explained, codification "cannot be well performed in an age of barbarism," but also "cannot without great difficulty be performed in an age of freedom." As India balanced between the two, however, "it is the work which especially belongs to a government like that of India---to an enlightened and paternal despotism."[^69]
+Science was, after all, sophisticated.[^65] The Throop Code came in for censure, both in its first year and in following decades, precisely for trying to capture all the sophistication of the New York legal system within an unwieldy 3,300 rules.[^66] Codification, however, could help developing societies along law's frontier take a progressive leap forward.
+As India's chief codifier Thomas Macaulay explained, codification "cannot be well performed in an age of barbarism," but also "cannot without great difficulty be performed in an age of freedom." As India balanced between the two, however, "it is the work which especially belongs to a government like that of India---to an enlightened and paternal despotism."[^67]
 
 In America, Macaulay's tool of enlightened despotism spread with the anxiety that capital from the nation's economic center would remain scarce without a Code of remedies that, if not in fact the law of New York, was at least prescribed by New York lawyers and their corporate clients.
-In the two most populous and commercially advanced western states, Texas and Illinois, the need for New York capital failed to move state legislators to adopt the code at the expense of popular sovereignty (although there were concerted efforts in both jurisdictions).[^70] Lacking the self-sufficiency of those two jurisdictions, the other states of the Greater Reconstruction in America adopted a foreign Code, but lawyers, legislators, and their supporters claimed the endorsement of popular sovereignty in doing so.
-Even in North Carolina, whose Democratic newspapers daily called for the repeal "this child of the carpet baggers," Republican editors proclaimed that "the movement" towards procedural codification "comes from the people, from the instinctive logic by which an unprejudiced mind grasps the advantages of the system."[^71]
+In the two most populous and commercially advanced western states, Texas and Illinois, the need for New York capital failed to move state legislators to adopt the code at the expense of popular sovereignty (although there were concerted efforts in both jurisdictions).[^68] Lacking the self-sufficiency of those two jurisdictions, the other states of the Greater Reconstruction in America adopted a foreign Code, but lawyers, legislators, and their supporters claimed the endorsement of popular sovereignty in doing so.
+Even in North Carolina, whose Democratic newspapers daily called for the repeal "this child of the carpet baggers," Republican editors proclaimed that "the movement" towards procedural codification "comes from the people, from the instinctive logic by which an unprejudiced mind grasps the advantages of the system."[^69]
 
@@
 The history of codification on the American periphery troubles cherished notions of American federalism.
-On the one hand, those suspicious of centralized power and critical of national governance since the New Deal have relied on narratives that tout the equality of sovereign states to set their own policies, foster local diversity, and "experiment" with legislative solutions to local issues.[^72] But the history of legal practice and civil remedies is one in which the localism fostered by common law practice rapidly gave way to uniform regulations transmitted by a network of New York lawyers without the slightest interference of the federal government.
+On the one hand, those suspicious of centralized power and critical of national governance since the New Deal have relied on narratives that tout the equality of sovereign states to set their own policies, foster local diversity, and "experiment" with legislative solutions to local issues.[^70] But the history of legal practice and civil remedies is one in which the localism fostered by common law practice rapidly gave way to uniform regulations transmitted by a network of New York lawyers without the slightest interference of the federal government.
 On the other hand, scholars who support the legitimacy of New Deal governance have recently produced an abundant literature unearthing a long tradition of "administrative" law at the state level well before the twentieth century.
-These accounts have focused on administrative adjudication or discretionary regulation within a narrow domain, such as customs houses.[^73] These histories have so far neglected the most widespread and significant instance of nineteenth-century administrative lawmaking in America---the spread of the Field Code through extra-legislative commissions.
+These accounts have focused on administrative adjudication or discretionary regulation within a narrow domain, such as customs houses.[^71] These histories have so far neglected the most widespread and significant instance of nineteenth-century administrative lawmaking in America---the spread of the Field Code through extra-legislative commissions.
 While these histories have sought to demonstrate that Americans from early on could be quite comfortable with administrative law and accepted it as a normal part of the constitutional order, this chapter has shown how lawmaking by commission generated significant political controversy and raised grave questions about popular sovereignty under such delegations, questions that over time were merely dodged rather than answered.
@@
 ed.
-2011 [1991]); Roger Berkowitz, *The Gift of Science: Leibniz and the Modern Legal Tradition* (Fordham 2010).
+2011 \[1991\]); Roger Berkowitz, *The Gift of Science: Leibniz and the Modern Legal Tradition* (Fordham 2010).
 
@@
 ed.
-1843 [1839]), 1-189, preface and 28, ch.
+1843 \[1839\]), 1-189, preface and 28, ch.
 7 § 1.
@@
 
-[^30]: Full citations to all of the codes that we used, plus links to electronic versions at the Hathi Trust, Google Books or other sources when available are available at Kellen Funk, \*American Legislation Project\*.
+[^30]: Full citations to all of the codes that we used, plus links to electronic versions at the Hathi Trust, Google Books or other sources when available are available at Kellen Funk, *American Legislation Project* (2015--): <http://kellenfunk.org/legislation>.
 
-[^31]: On this point, see Stephen Robertson, Debates in DH piece. As an example of digital historical work that is likewise aimed at exploring a dataset {RETHINK} see Cameron Blevins, spatial article.
+[^31]: We have preferred to use the term "digital history" when referring to our own work, in part because the term "digital humanities" has largely come to refer to the work of digital literary and digital media scholars, but primarily because we wish to see digital scholars make disciplinary, rather than interdisciplinary contributions.
+On the role of disciplines and the importance of field specific argumentation, see, Stephen Robertson, "The Differences between Digital Humanities and Digital History," {PAGE}--{PAGE}, and Cameron Blevins, "Digital History's Perpetual Future Tense," {PAGE}--{PAGE}, both in *Debates in the Digital Humanities 2016*, ed.
+Matthew K.
+Gold and Lauren F.
+Klein (Minneapolis: University of Minnesota Press, 2016).
+Nevertheless, digital text analysis in the humanities has mostly been published by literary scholars, including Stephen Ramsay, *Reading Machines: Toward an Algorithmic Criticism* (Urbana: University of Illinois Press, 2011); Franco Moretti, *Distant Reading* (New York: Verso, 2013); Matthew L.
+Jockers, *Macroanalysis: Digital Methods and Literary History* (Urbana: University of Illinois Press, 2013); Ted Underwood, *Why Literary Periods Mattered: Historical Contrast and the Prestige of English Studies* (Stanford: Stanford University Press, 2013).
+Related but less well regarded by humanities scholars is work in "culturomics": see Jean-Baptiste Michel et al., "Quantitative Analysis of Culture Using Millions of Digitized Books", *Science* 331, no.
+6014 (2011), 176--182; doi:10.1126/science.1199644.
+On the uselessness of the term "big data," see Ted Underwood, "Against (Talking About) 'Big Data,'" *The Stone and the Shell*, blog post, 10 May 2013: <https://tedunderwood.com/2013/05/10/why-it-matters-that-we-dont-know-what-we-mean-by-big-data/>.
+For an example of forming a corpus, see Ted Underwood, Boris Capitanu, Peter Organisciak, Sayan Bhattacharyya, Loretta Auvil, Colleen Fallaw, J.
+Stephen Downie, "Word Frequencies in English-Language Literature, 1700-1922," dataset, v0.2 (HathiTrust Research Center, 2015) doi:10.13012/J8JW8BSJ.
 
-[^32]: Examples of big history include Historian's Macroscope. Cite Underwood fiction corpus; Jockers' on Macroanalysis and Moretti on Big Reading, Culturomics, Ben Schmidt.
-
-[^33]: Though somewhat overstated, see Cameron Blevins, Debates in DH.
-
-[^34]: **Note codes pulled from HeinOnline and three codes transcribed by hand**.We favored public domain sources where available both for reasons of efficiency (large statute books download much more quickly from Google's servers than from subscription databases) and reproducibility (most of this project can be replicated without subscription databases).
+[^32]: **Note codes pulled from HeinOnline and three codes transcribed by hand**.We favored public domain sources where available both for reasons of efficiency (large statute books download much more quickly from Google's servers than from subscription databases) and reproducibility (most of this project can be replicated without subscription databases).
 In each instance we downloaded an entire volume of sessions laws, statutory compilations, or single-volume codes of procedure and then cropped out irrelevant pages, marginalia and footnoted commentary, leaving only the statutory text.
@@
 
-[^35]: Cf. Hay & Craven, AJLH article
+[^33]: Cf. Hay & Craven, AJLH article
 
-[^36]:
+[^34]:
 
-[^37]: **Code citations and literature on West as a legal void**.In practice, there are also variations in the texts due to numbering or minor OCR errors as well as actual changes. These differences
+[^35]: **Code citations and literature on West as a legal void**.In practice, there are also variations in the texts due to numbering or minor OCR errors as well as actual changes. These differences
 
-[^38]: This algorithm works by extracting a set number of random tokens from each document, allowing the documents to be represented uniformly and compactly.
+[^36]: This algorithm works by extracting a set number of random tokens from each document, allowing the documents to be represented uniformly and compactly.
 Then those random tokens are grouped into subsets.
@@
 
-[^39]: This matrix required filtering based on what we knew about the process of borrowing.
+[^37]: This matrix required filtering based on what we knew about the process of borrowing.
 We removed any match below a threshold that we determined by reading pairs of matches.
@@
 
-[^40]: This is obvious from the visualization, but also confirmed by all measures of centrality used in network analysis.
+[^38]: This is obvious from the visualization, but also confirmed by all measures of centrality used in network analysis.
 A network is simply a list of edges (in our case the number of sections borrowed) between nodes (in our case, the codes).
@@
 
-[^41]: Non-Field jurisdictions occasionally exhibited a borrowing relationship within a state or across two states.
+[^39]: Non-Field jurisdictions occasionally exhibited a borrowing relationship within a state or across two states.
 In in a few unusual instances they contributed to codes which were derived from the Field Code.
@@
 
-[^42]: spectrogram("CA1851", mutate(best\_matches, match\_code = ifelse(match\_code %in% c("NY1848", "NY1849", "NY1850"), "New York 1849/50", match\_code)), white\_list = 3)
+[^40]: spectrogram("CA1851", mutate(best\_matches, match\_code = ifelse(match\_code %in% c("NY1848", "NY1849", "NY1850"), "New York 1849/50", match\_code)), white\_list = 3)
 
-[^43]: (The visualization here, because of difficulties in precisely matching sections, actually understates the extent of the borrowing.) **Explain** why our method errs on the side of undercounting.
+[^41]: (The visualization here, because of difficulties in precisely matching sections, actually understates the extent of the borrowing.) **Explain** why our method errs on the side of undercounting.
 
-[^44]: Scholars in digital literary studies often speak of the "deformance" of texts.
+[^42]: Scholars in digital literary studies often speak of the "deformance" of texts.
 Clustering the sections of the codes deformed them by pulling the sections out of their context within specific codes and by arranging them by topic in chronological order.
@@
 
-[^45]: Brendan J. Frey and Delbert Dueck, "Clustering by Passing Messages Between Data Points," *Science* 315 (2007): 972--976.
+[^43]: Brendan J. Frey and Delbert Dueck, "Clustering by Passing Messages Between Data Points," *Science* 315 (2007): 972--976.
 
-[^46]: Furthermore, even though the affinity propagation clus- tering algorithm did not fully converge with our peculiar dataset, it did an adequate job clustering the documents.
+[^44]: Furthermore, even though the affinity propagation clus- tering algorithm did not fully converge with our peculiar dataset, it did an adequate job clustering the documents.
 Because there was an exemplar section for each cluster, we were able to merge clusters whose exemplars had a high Jaccard similarity score.
 
-[^47]: We also implemented a method called the Smith Waterman algorithm, which is used for gene sequencing, but which we adapted for natural language.
+[^45]: We also implemented a method called the Smith Waterman algorithm, which is used for gene sequencing, but which we adapted for natural language.
 This is the method used by Smith et al for Viral Texts.
@@
 
-[^48]: E.g., Moretti, Distant Reading; Jockers, Macroanalysis.
+[^46]: E.g., Moretti, Distant Reading; Jockers, Macroanalysis.
 
-[^49]: Samuels, Lisa, and Jerome McGann. "Deformance and Interpretation." *New Literary History* 30.1 (1999) : 25--56; *Stallybrass, Peter. "Against Thinking."* PMLA *122.5 (2007): 1580-1587.*
+[^47]: Samuels, Lisa, and Jerome McGann. "Deformance and Interpretation." *New Literary History* 30.1 (1999) : 25--56; *Stallybrass, Peter. "Against Thinking."* PMLA *122.5 (2007): 1580-1587.*
 
-[^50]:
+[^48]:
 
-[^51]: Those jurisdictions were Nevada (1861), Dakota Territory---which retained the Code when split into North and South (1862), Idaho (1864), Arizona (1864), Montana (1865), Arkansas (1868), North Carolina (1868), Wyoming (1869), Florida (1870), South Carolina (1870), Utah (1870), and Colorado (1877).
+[^49]: Those jurisdictions were Nevada (1861), Dakota Territory---which retained the Code when split into North and South (1862), Idaho (1864), Arizona (1864), Montana (1865), Arkansas (1868), North Carolina (1868), Wyoming (1869), Florida (1870), South Carolina (1870), Utah (1870), and Colorado (1877).
 
-[^52]: Elliott West, "Reconstructing Race," 34 *Western Historical Quarterly* 6 (2003).
+[^50]: Elliott West, "Reconstructing Race," 34 *Western Historical Quarterly* 6 (2003).
 See also Heather Cox Richardson, *West from Appomattox: The Reconstruction of America after the Civil War* (New Haven: Yale University Press, 2007); Sven Beckert, *Monied Metropolis: New York City and the Consolidation of the American Bourgeoisie, 1850-1896* (Harvard 2003); Mark Wahlgren Summers, *The Ordeal of the Reunion: A New History of Reconstruction* (Chapel Hill: University of North Carolina Press, 2014).
@@
 
-[^53]: See, for instance, Rogers Smith, *Civic Ideals: Conflicting Visions of Citizenship in U.S.
+[^51]: See, for instance, Rogers Smith, *Civic Ideals: Conflicting Visions of Citizenship in U.S.
 History* (Yale 1999); Meg Jacobs, William J.
@@
 
-[^54]: Naomi Lamoreaux and John Joseph Wallis, "States, Not Nation: The Sources of Political and Economic Development in the Early United States," Paper Presented at the Economic History Workshop, Harvard University, March 4, 2016.
+[^52]: Naomi Lamoreaux and John Joseph Wallis, "States, Not Nation: The Sources of Political and Economic Development in the Early United States," Paper Presented at the Economic History Workshop, Harvard University, March 4, 2016.
 
-[^55]: For instance, although Tennessee in 1858 adapted nearly 225 sections of its code from Field codes, the state also incorporated nearly 50 sections of the 1852 Code of Alabama, one of the largest borrowings of southern legislation within the corpus we collected.
+[^53]: For instance, although Tennessee in 1858 adapted nearly 225 sections of its code from Field codes, the state also incorporated nearly 50 sections of the 1852 Code of Alabama, one of the largest borrowings of southern legislation within the corpus we collected.
 
-[^56]: Illinois was a fiercely traditional anti-code state.
+[^54]: Illinois was a fiercely traditional anti-code state.
 In later decades, lawyers jokingly called it "the Yellowstone Park of common law pleading." See Charles E.
@@
 
-[^57]: Journal of the Assembly of the Territory of Utah (1870), 15.
+[^55]: Journal of the Assembly of the Territory of Utah (1870), 15.
 
-[^58]: "The Code Again," *Pueblo Daily Chieftain*, February 25, 1877.
+[^56]: "The Code Again," *Pueblo Daily Chieftain*, February 25, 1877.
 
-[^59]: "The Legislature: The Senate Devotes Another Day to the Code," *Denver Daily Tribune*, February 17, 1877.
+[^57]: "The Legislature: The Senate Devotes Another Day to the Code," *Denver Daily Tribune*, February 17, 1877.
 
-[^60]: Governor's Message, in Journal of the House of Assembly of the Territory of Nebraska (1857), 12.
+[^58]: Governor's Message, in Journal of the House of Assembly of the Territory of Nebraska (1857), 12.
 
-[^61]: William A.
+[^59]: William A.
 Jenkins to William Blount Rodman, January 14, 1868, Rodman Papers.
@@
 
-[^62]: Gordon Morris Bakken, *Practicing Law in Frontier California* (Nebraska 1991), 51-54.
+[^60]: Gordon Morris Bakken, *Practicing Law in Frontier California* (Nebraska 1991), 51-54.
 The new western history ushered in by Patricia Nelson Limerick, *The Legacy of Conquest: The Unbroken Past of the American West* (Norton 1987) and Richard White, *"It's Your Misfortune and None of My Own": A History of the American West* (Oklahoma 1991) is now returning to issues of political economy.
@@
 
-[^63]: "The Code," *Denver Daily Tribune*, January 10, 1877; "The Code," *Denver Daily Times*, January 27, 1877.
+[^61]: "The Code," *Denver Daily Tribune*, January 10, 1877; "The Code," *Denver Daily Times*, January 27, 1877.
 
-[^64]: "A Code of Civil Procedure," *Denver Daily Times*, January 12, 1877.
+[^62]: "A Code of Civil Procedure," *Denver Daily Times*, January 12, 1877.
 
-[^65]: "The Code," *Denver Daily Tribune*, January 31, 1877.
+[^63]: "The Code," *Denver Daily Tribune*, January 31, 1877.
 
-[^66]: See Gunther A.
+[^64]: See Gunther A.
 Weiss, "The Enchantment of Codification in the Common-Law World," 25 *Yale Journal of International Law* 435 (2000).
@@
 
-[^67]: See, for instance, James C.
+[^65]: See, for instance, James C.
 Carter's classic defense of the common law against codification, The Ideal and the Actual in the Law, Address to the American Bar Association, August 21, 1890, at 28 ("the legislature should never attempt to perform the function of the judge, that of simply ascertaining and declaring existing customs.
@@
 
-[^68]: See, for instance, "Note," 29 *Albany Law Journal* 141, 142 (1884); Millar, *Civil Procedure of the Trial Court*, 55-56.
+[^66]: See, for instance, "Note," 29 *Albany Law Journal* 141, 142 (1884); Millar, *Civil Procedure of the Trial Court*, 55-56.
 
-[^69]: 19 *Hansard Parliamentary Debates* 531.
+[^67]: 19 *Hansard Parliamentary Debates* 531.
 
-[^70]: Texas commissioned the preparation of a code of civil procedure in 1855, and the legislature scheduled an extra session to consider it but ultimately never passed the law.
+[^68]: Texas commissioned the preparation of a code of civil procedure in 1855, and the legislature scheduled an extra session to consider it but ultimately never passed the law.
 21 *Texas Reports* (Hartley) xi (1882); *Texas State Times*, December 15, 1855.
@@
 
-[^71]: "The Code," *Weekly Standard* (Raleigh), May 26, 1869.
+[^69]: "The Code," *Weekly Standard* (Raleigh), May 26, 1869.
 
-[^72]: See, for instance, the summary of the states-as-laboratories literature in Brian Galle & Joseph Leahy, "Laboratories of Democracy?
+[^70]: See, for instance, the summary of the states-as-laboratories literature in Brian Galle & Joseph Leahy, "Laboratories of Democracy?
 Policy Innovation in Decentralized Governments," 58 *Emory Law Journal* 1333 (2009).
 
-[^73]: See Daniel Ernst, *Tocqueville's Nightmare: The Administrative State Emerges in America, 1900-1940* (Oxford: Oxford University Press, 2014); Jerry L.
+[^71]: See Daniel Ernst, *Tocqueville's Nightmare: The Administrative State Emerges in America, 1900-1940* (Oxford: Oxford University Press, 2014); Jerry L.
 Mashaw, *Creating the Administrative Constitution: The Lost One Hundred Years of American Administrative Law* (Yale Law Library 2012); Gautham Rao, *National Duties: Custom Houses and the Making of the American State* (University of Chicago 2016).

### 2016-06-25 article/article.Rmd
Minor fixes

@@
   pdf_document:
-    fig_caption: True
-    number_sections: False
+    fig_caption: true
+    number_sections: false
 title: The Spine of American Legal Practice
@@
 Each time they reminded legislators that "public opinion had issued its mandate in the most imposing form" of a constitutional decree.
-The constitution, together with the legislative act appointing the commission, "gave the commissioners instructions so precise, as to leave them no discretion, if they had desired it, \[and\] promised them therefore in advance, so long as they obeyed those instructions, the concurrence and co-operation of all departments of the government."[^16] Although the theory of codification made it a democratic enterprise, in practice Field---an ardent Jacksonian---insisted the democratic legislature ought to defer to the expertise of the commissioners.
+The constitution, together with the legislative act appointing the commission, "gave the commissioners instructions so precise, as to leave them no discretion, if they had desired it, [and] promised them therefore in advance, so long as they obeyed those instructions, the concurrence and co-operation of all departments of the government."[^16] Although the theory of codification made it a democratic enterprise, in practice Field---an ardent Jacksonian---insisted the democratic legislature ought to defer to the expertise of the commissioners.
 
@@
 They wrote that "provisions for rights and for the mode of pursuing remedies, insensibly run into each other," and observed that distinctions between substance and procedure were difficult to draw in practice.
-In fact, "the parts of a system of law are more dependent on each other, and run into and affect each other, infinitely more than any machine of human contrivance." They therefore suspected the commissioners' forthcoming code of criminal procedure would include all of the criminal law as well, "as they seem to understand practice and pleadings to include all the law upon a given subject." That being the case, the committee wondered whether they should "place in \[the commissioners\] a blind and implicit confidence that shall commit to their discretion the peace and property, the personal liberty and the lives of those who sent *us* here to make laws for them?"[^26]
+In fact, "the parts of a system of law are more dependent on each other, and run into and affect each other, infinitely more than any machine of human contrivance." They therefore suspected the commissioners' forthcoming code of criminal procedure would include all of the criminal law as well, "as they seem to understand practice and pleadings to include all the law upon a given subject." That being the case, the committee wondered whether they should "place in [the commissioners] a blind and implicit confidence that shall commit to their discretion the peace and property, the personal liberty and the lives of those who sent *us* here to make laws for them?"[^26]
 
@@
 Curating a corpus to answer a specific question is an important difference from the way that digital history often describes itself.
-Speaking in broad terms, digital historical work---like all historical work---can begin either with a set of sources or a question.
-Digital history is often conceived of as working with very large datasets such as the Google Books or Hathi Trust corpora.
+Speaking in broad terms, digital historical work---like all historical work---can begin either with a set of sources or with a question.
+Digital history is often conceived of as beginning with very large datasets such as the Google Books or Hathi Trust corpora.
 These large corpora are sometimes called "big data"---though, it must be emphasized, almost never by digital historians who actually work with them---and are used as the basis of a "distant reading." We think that working with these large corpora is worthwhile because it is salutary for historians to have their research questions shaped by the broadest possible contexts.
-Nevertheless, it is not apparent that digital historians can readily move from these omnibus corpora to answering the specific research questions that animate historical fields.
+Nevertheless, it is not apparent that digital historians can readily move from these omnibus corpora to answering the specific research questions that animate various historical fields.
 In this article we demonstrate an alternative approach, which we might unimaginatively label "medium data." Although the amount of legislation that governed American civil practice is impressive---every state amended and re-enacted procedure statutes nearly every decade---a corpus of procedural legislation requires some computational sophistication but is far from needing the computational techniques derived for truly big data.
@@
 A count by a "friend" of Field's found that only three sentences of the Field Code had carried over word-for-word into the Throop Code.
-Nevertheless, many of the changes were purely formal, and Field speculated that these changes had been made only "so that \[the code\] should not appear to be the same thing as before." With respect to Mr.
+Nevertheless, many of the changes were purely formal, and Field speculated that these changes had been made only "so that [the code] should not appear to be the same thing as before." With respect to Mr.
 Field or his "friend," we were able to find that the connection was between the Throop Code and the Field Code was somewhat stronger than he thought, and the Throop Code was indeed a descendant, if much revised, from the Field Code.
@@
 While the so-called new western history has shed significant light on neglected topics of Indian dispossession and environmental management, it has often done so by leaving out of view matters of political economy, a staple of the old western history.
-As one work in that older tradition argued, "Debt collection was the central part of law practice for the \[western\] bar and remained a key part of private practice throughout the century."[^60] On that understanding, one western lawyer succinctly summarized the difference between the code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, ...
+As one work in that older tradition argued, "Debt collection was the central part of law practice for the [western] bar and remained a key part of private practice throughout the century."[^60] On that understanding, one western lawyer succinctly summarized the difference between the code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, ...
 that he did not also break out somewhere with 'take for instance the case of an action on a promissory note,' as though the collection of notes was about all there could be any law needed for."[^61]

### 2016-06-25 article/article.Rmd
Fix problem with display math

--- 2016-06-24 article/article.Rmd
@@
 - Lincoln Mullen
-documentclass: article
 fontsize: 12pt
@@
     number_sections: False
+    md_extensions: -tex_math_single_backslash
 title: The Spine of American Legal Practice
-...
+---
 

### 2016-06-25 article/article.Rmd
Revise section on sectioning

@@
     fig_caption: True
+    md_extensions: '-tex\_math\_single\_backslash'
     number_sections: False
-    md_extensions: -tex_math_single_backslash
 title: The Spine of American Legal Practice
@@
 Because most codes were public statutes, they were widely printed and distributed and therefore found their way into libraries digitized by Google Books.
-Where possible, we collected our corpus from Google's publicly accessible database.
-We used optical character recognition software (OCR) to create plain-text versions of the codes, which we edited lightly---we corrected section markers by hand as necessary and wrote a script to fix the most common OCR errors.[^32]
+We drew primarily from the Google Books, filling in gaps from other databases as necessary.[^32] We used optical character recognition software (OCR) to create plain-text versions of the codes, which we edited lightly, correcting section markers by hand as necessary and writing a script to fix the most obvious OCR errors.[^33]
 
 The most important step we took in processing the files was to split each section of the code into its own text file.
-Codes varied in their organizations, but they universally divided specific regulations into *sections* (or, on occasion, *articles*).
-The discursive formation of these texts not only provides a handy organizational scheme for digital approaches, sections were historically the way legislators borrowed their texts.[^33] Codifiers took their sources apart by sections, rearranging here, editing, drafting, and then re-combining there.
+Codes varied in how they were organized, but they universally divided specific regulations into *sections* (or, on occasion, *articles*).
+Not only does the discursive form of these texts provide a handy organizational scheme for digital methods, but historically sections were also the way legislators borrowed their texts.[^34] Codifiers took their sources apart by sections, rearranging here, editing, drafting, and then re-combining there.
 Despite the fact that states differed widely on what topics they included in "civil procedure," sectioning the codes allowed us to assess similarity even among codes of quite different lengths and coverage.
-For instance, we know from historical evidence that California's 1851 code was derived from New York's 1850 code.
-(Stephen Johnson Field, David Dudley's brother, was the lawyer who imported New York's code into California.[^34]) But the New York code is over 150,000 words long, where was California's code was just over 50,000 words long.
-Those rather disparate lengths mean that comparing all of the California code to all of the New York code is a less meaningful comparison that than comparing each section in the California code to each section in the New York code, where matching sections will be a similar length.
+For instance, we know that California's 1851 code was derived from New York's 1850 code.
+(Stephen Johnson Field, David Dudley Field's brother, was the lawyer who imported New York's code into California.[^35]) But the New York code is over 150,000 words long, whereas California's code was just over 50,000 words long.
+Those disparate lengths mean that comparing all of the California code to all of the New York code is a less meaningful comparison that than comparing each section in the California code to each section in the New York code, where matching sections will have a similar length.
 
@@
 
-The pairs are obviously related to one another, both in terms of their legal force and in terms of the actual words used.[^35]
+The pairs are obviously related to one another, both in terms of their legal force and in terms of the actual words used.[^36]
 
@@
 This would take an unreasonable amount of computation time, and most of these comparisons would be unnecessary, since each section has no relationship to most other sections (like the matrix above, most scores will be zero).
-We therefore implemented the minhash/locality sensitive hashing (LSH) algorithm to detect candidate pairs, that is, documents which were likely to be matches, and then we measured the Jaccard score for only those candidate pairs.[^36]
+We therefore implemented the minhash/locality sensitive hashing (LSH) algorithm to detect candidate pairs, that is, documents which were likely to be matches, and then we measured the Jaccard score for only those candidate pairs.[^37]
 
 The result was a matrix of matches, with over 45,000 genuine matches.
-For each section in the corpus, after making some adjustments to remove anachronisms and spurious matches,[^37] we were able to identify the section from which it was most likely borrowed.
+For each section in the corpus, after making some adjustments to remove anachronisms and spurious matches,[^38] we were able to identify the section from which it was most likely borrowed.
 In other words, we had traced the work of the commissioners' scissors and paste-pots through the course of their codes.
@@
 The resulting network graph (**Figure X: Network Graph**) tells the genealogy of civil procedure in the United States.
-The New York codes, especially the finished draft of 1850, are central to the entire network.[^38] Yet it is important to note that New York spurred different traditions within the procedural network.
+The New York codes, especially the finished draft of 1850, are central to the entire network.[^39] Yet it is important to note that New York spurred different traditions within the procedural network.
 Variations in the Field drafts meant that different states could borrow different versions of the Field Code.
@@
 Finally, our corpus included a number of statutes which stood outside the Field Code tradition, such as Virginia and West Virginia regulations, statutes from Massachusetts and Maine, and southern codes from Georgia to Louisiana.
-These statutes show that the dominance of the Field Code was not total, and a number of older jurisdictions remained outside of its ambit.[^39] But virtually every jurisdiction established or reconstructed after 1850 became a part of the Field Code network, and no other tradition achieved anywhere near the same coherence across state lines.
+These statutes show that the dominance of the Field Code was not total, and a number of older jurisdictions remained outside of its ambit.[^40] But virtually every jurisdiction established or reconstructed after 1850 became a part of the Field Code network, and no other tradition achieved anywhere near the same coherence across state lines.
 
@@
 California's 1851 code borrowed heavily from two sources.
-The bulk of the code was taken directly from New York's 1849 or 1850 codes (which are difficult to distinguish exactly from one another.[^40] The remainder of the code was borrowed from California's 1850 code.
+The bulk of the code was taken directly from New York's 1849 or 1850 codes (which are difficult to distinguish exactly from one another.[^41] The remainder of the code was borrowed from California's 1850 code.
 The 1850 version was in turn borrowed from the New York codes **TODO: might as well show this, esp.
@@
 The bulk of this code was lifted from the Washington 1855 code with only small amendments.
-The main exception was a probate code drawn from California's 1872 code.[^41] Like many of the last generation codes, the text of the procedure code had stabilized in a local manifestation of a regional tradition.
+The main exception was a probate code drawn from California's 1872 code.[^42] Like many of the last generation codes, the text of the procedure code had stabilized in a local manifestation of a regional tradition.
 The code was still genuinely a Field Code, with a great deal of similarity to the original New York Field Codes, but its specific form depended on the many edits and rearrangements that state code commissioners had made to the text.
@@
 So far we have retained the context of the surrounding sections within a particular code.
-But since our fundamental unit of comparison is section to section, we can use a technique called clustering to deform the texts (as a literary scholar might say) in order to see the textual history of how particular regulations embedded in individual sections changed over time.[^42]
+But since our fundamental unit of comparison is section to section, we can use a technique called clustering to deform the texts (as a literary scholar might say) in order to see the textual history of how particular regulations embedded in individual sections changed over time.[^43]
 
@@
 There are innumerable clustering algorithms, but we needed one that could work with a sparse matrix and one whose assumptions matched the characteristics of our problem.
-We decided to use affinity propagation clustering.[^43] That algorithm assumes that each cluster has an "exemplar" item which the other items are similar to.
-That assumption fits nicely with borrowings from the Field Code, where a single section (likely from the 1850 New York code) had many borrowings, but where there could also be innovative sections in other stages.[^44]
+We decided to use affinity propagation clustering.[^44] That algorithm assumes that each cluster has an "exemplar" item which the other items are similar to.
+That assumption fits nicely with borrowings from the Field Code, where a single section (likely from the 1850 New York code) had many borrowings, but where there could also be innovative sections in other stages.[^45]
 
@@
 The biggest cluster, for instance, which concerned the use of affidavits in pleading, contained 103 sections.
-With those clusters, we were able to organize the documents chronologically.[^45] This method is particularly useful when tracking the variations in in the law from jurisdiction to jurisdiction.
+With those clusters, we were able to organize the documents chronologically.[^46] This method is particularly useful when tracking the variations in in the law from jurisdiction to jurisdiction.
 It provides historians with a way of noticing small changes in the wording and substance of the law.
-Most discussions of algorithmic reading have focused on "distant reading,"[^46] or have balanced the claims of distant reading by using it as a means to enable close reading.
+Most discussions of algorithmic reading have focused on "distant reading,"[^47] or have balanced the claims of distant reading by using it as a means to enable close reading.
 This method of clustering, however, is a kind of algorithmic close reading.
-By deforming the texts---taking them out of the context of the codes and putting them in the context of their particular variations---we are able to pay attention to those variations.[^47]
+By deforming the texts---taking them out of the context of the codes and putting them in the context of their particular variations---we are able to pay attention to those variations.[^48]
 
@@
 The Field code's summary judgment brought down the time of debt collection to a matter of weeks.
-Effectively, the code traded the rhythms of agriculture for the rhythms of merchant finance.[^48]
+Effectively, the code traded the rhythms of agriculture for the rhythms of merchant finance.[^49]
 
@@
 Alerted by these clustering patterns to the significance of creditors' remedies in the developing West and re-developing South, it was not difficult to find evidence of westerners and southerners commenting on these features of the code or its connections to New York capital.
-Twelve of the states and territories that copied the Field Code mostly closely did so during the Civil War and Reconstruction era---four states in the former Confederacy and eight jurisdictions in the Far West.[^49] As with other areas of postbellum historiography, it turns out one may learn a lot by holding the postbellum American South and American West together.
+Twelve of the states and territories that copied the Field Code mostly closely did so during the Civil War and Reconstruction era---four states in the former Confederacy and eight jurisdictions in the Far West.[^50] As with other areas of postbellum historiography, it turns out one may learn a lot by holding the postbellum American South and American West together.
 
-In the last decade, scholars of Reconstruction have broadened the scope of their study to include both the South and the West as two sites in one "Greater Reconstruction." These studies have illustrated the ways that military conquest, rapid industrialization, and the resettlement and education of ethnic minorities developed similarly in each region, guided by economic elites in New York and political administrators in Washington.[^50] In tracing the legal aspects of this Greater Reconstruction, scholars have focused almost entirely on constitutional rights of citizenship and civil equality or the expansion of federal power.[^51] While the 1860s and 1870s were of course a transformative period in the history of civil rights and the creation of a national state, they were also the decades in which many local legal institutions and practices were transformed not by federal power but by state codification.
+In the last decade, scholars of Reconstruction have broadened the scope of their study to include both the South and the West as two sites in one "Greater Reconstruction." These studies have illustrated the ways that military conquest, rapid industrialization, and the resettlement and education of ethnic minorities developed similarly in each region, guided by economic elites in New York and political administrators in Washington.[^51] In tracing the legal aspects of this Greater Reconstruction, scholars have focused almost entirely on constitutional rights of citizenship and civil equality or the expansion of federal power.[^52] While the 1860s and 1870s were of course a transformative period in the history of civil rights and the creation of a national state, they were also the decades in which many local legal institutions and practices were transformed not by federal power but by state codification.
 Naomi Lamoreaux and John Joseph Wallis have recently argued that in the creation of a modern American economy, "the federal government played *no* role in this process until the Civil War, and even then it played only a bit part." The history of the Field Code's migration helps to substantiate this claim.
 While Lamoreaux and Wallis focus on the development of banking, transportation, and incorporation at the state level, it was the Procedure Code that provided the structure of civil remedies that protected these state institutions.
-And procedure codes were, of course, the creatures of state governance.[^52]
+And procedure codes were, of course, the creatures of state governance.[^53]
 
 With the universal complaints that time was too short or commissioners too democratically irresponsible, one might expect the code to have faced more competition from other workable statutes.
-Southern states that drew more on the civilian code tradition such as Louisiana and Alabama offered other options for states desiring to reform common law practice.[^53] And if Euro-Americans believed law had to be imported into the West, Colorado immigrants proved that the common law of Illinois was just as amenable to statutory importation as New York law.[^54] But what codifiers saw when they looked at New York, more so than Louisiana, Alabama, or Illinois, was the Empire State of commercial capital.
+Southern states that drew more on the civilian code tradition such as Louisiana and Alabama offered other options for states desiring to reform common law practice.[^54] And if Euro-Americans believed law had to be imported into the West, Colorado immigrants proved that the common law of Illinois was just as amenable to statutory importation as New York law.[^55] But what codifiers saw when they looked at New York, more so than Louisiana, Alabama, or Illinois, was the Empire State of commercial capital.
 And the putative fears, demands, and desires of a personified Capital continually wielded promises---and threats---in the debates over procedural codification.
 The early Mormon settlers of Utah persistently avoided the mining frenzy as well as codification.
-By 1870, however, the territory's governor directed the legislature's attention to the recent Code of Nevada, a code "for a people whose interests in many respects are similar to our own." Of course, standing behind the Nevada Code was "the State of New York---a State which is an empire in itself and whose commercial transactions are far greater than those of any other State in the Union." By copying its code, Utah too could be "rewarded by equal advantages."[^55] Code proponents in Colorado similarly parried arguments that a code would be a "foreign" imposition by pointing to the fact that it has been "adopted twenty-nine years ago by the Empire state of the Union" and they promised that the code of the nation's uniquely commercial empire could bring wealth in its wake.[^56]
+By 1870, however, the territory's governor directed the legislature's attention to the recent Code of Nevada, a code "for a people whose interests in many respects are similar to our own." Of course, standing behind the Nevada Code was "the State of New York---a State which is an empire in itself and whose commercial transactions are far greater than those of any other State in the Union." By copying its code, Utah too could be "rewarded by equal advantages."[^56] Code proponents in Colorado similarly parried arguments that a code would be a "foreign" imposition by pointing to the fact that it has been "adopted twenty-nine years ago by the Empire state of the Union" and they promised that the code of the nation's uniquely commercial empire could bring wealth in its wake.[^57]
 
@@
 Hamill replied that he knew of one California company of capitalists who were deterred from investing in mining property here wholly on account of the practice of the courts in mining cases.
-If we had had this code years ago, Colorado would now have a larger amount of California capital in her mines."[^57] Codifiers argued that, in attracting capital, procedure was at least as important as the substantive rules of property and contract, because procedure secured the remedies that actually protected investments.
-"Men of capital and enterprise will not make investments and devote their time and energies to those works of internal improvement so necessary for the speedy development of our natural resources, and for the settlement and building up the country," Nebraska's governor reasoned, "unless ample protection is afforded them, by legal enactment, for the capital invested and labor employed." And he therefore urged swift passage of the Field Code.[^58]
+If we had had this code years ago, Colorado would now have a larger amount of California capital in her mines."[^58] Codifiers argued that, in attracting capital, procedure was at least as important as the substantive rules of property and contract, because procedure secured the remedies that actually protected investments.
+"Men of capital and enterprise will not make investments and devote their time and energies to those works of internal improvement so necessary for the speedy development of our natural resources, and for the settlement and building up the country," Nebraska's governor reasoned, "unless ample protection is afforded them, by legal enactment, for the capital invested and labor employed." And he therefore urged swift passage of the Field Code.[^59]
 
@@
 Let the law enforce punctuality; let the people of North Carolina learn that the great law of business is, that 'time is of the essence of the contract,' and incur no debt that they do not expect to meet at maturity." Under the more certain and speedy remedies of the code, "we may expect that the secret hoards of the frugal among ourselves will be offered to loan, and even that the vaults of the banks of New-York ...
-will be open to our industry."[^59]
+will be open to our industry."[^60]
 
@@
 While the so-called new western history has shed significant light on neglected topics of Indian dispossession and environmental management, it has often done so by leaving out of view matters of political economy, a staple of the old western history.
-As one work in that older tradition argued, "Debt collection was the central part of law practice for the \[western\] bar and remained a key part of private practice throughout the century."[^60] On that understanding, one western lawyer succinctly summarized the difference between the code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, ...
-that he did not also break out somewhere with 'take for instance the case of an action on a promissory note,' as though the collection of notes was about all there could be any law needed for."[^61]
+As one work in that older tradition argued, "Debt collection was the central part of law practice for the \[western\] bar and remained a key part of private practice throughout the century."[^61] On that understanding, one western lawyer succinctly summarized the difference between the code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, ...
+that he did not also break out somewhere with 'take for instance the case of an action on a promissory note,' as though the collection of notes was about all there could be any law needed for."[^62]
 
 The creditors' remedies in the code gave the codifiers their leading argument against criticisms rooted in the ideology of popular sovereignty.
-"There is no doubt but the people are in favor of anything that promises to hurry up that proverbially slow and blind old female called Justice, and they will go for the old code," one Colorado newspaper announced.[^62] New York's "code practice is the best in excellence," stated another, "and when I say *best* I do not mean best for lawyers only, but best for the people---the commonwealth."[^63] If the People favored economic progress, certainty of remedy, and efficiency in proceedings, then they favored the New York Code, no matter whether they understood or cared about technical rules of pleading and joinder.
+"There is no doubt but the people are in favor of anything that promises to hurry up that proverbially slow and blind old female called Justice, and they will go for the old code," one Colorado newspaper announced.[^63] New York's "code practice is the best in excellence," stated another, "and when I say *best* I do not mean best for lawyers only, but best for the people---the commonwealth."[^64] If the People favored economic progress, certainty of remedy, and efficiency in proceedings, then they favored the New York Code, no matter whether they understood or cared about technical rules of pleading and joinder.
 Thus, in their arguments the codifiers imagined themselves the champions of popular sovereignty, for it was they who accomplished what the People actually desired.
@@
 Both jurisdictions, while reforming the practice of law, largely rejected codification within their own borders but encouraged it among their economic dependents.
-The English commissioned a full codification of law for India and colonies in Singapore, while further codifications produced by Field in New York covering civil and penal law were adopted in California and other western jurisdictions.[^64] In both places, leading arguments against codification carried a civilizational logic of empire: Advanced societies could not codify their law, for to do so would be to freeze the progress of legal science.
+The English commissioned a full codification of law for India and colonies in Singapore, while further codifications produced by Field in New York covering civil and penal law were adopted in California and other western jurisdictions.[^65] In both places, leading arguments against codification carried a civilizational logic of empire: Advanced societies could not codify their law, for to do so would be to freeze the progress of legal science.
 What appeared to some to be a hopeless mass of confusion was to common law defenders the sign of true legal sophistication.
-Science was, after all, sophisticated.[^65] The Throop Code came in for censure, both in its first year and in following decades, precisely for trying to capture all the sophistication of the New York legal system within an unwieldy 3,300 rules.[^66] Codification, however, could help developing societies along law's frontier take a progressive leap forward.
-As India's chief codifier Thomas Macaulay explained, codification "cannot be well performed in an age of barbarism," but also "cannot without great difficulty be performed in an age of freedom." As India balanced between the two, however, "it is the work which especially belongs to a government like that of India---to an enlightened and paternal despotism."[^67]
+Science was, after all, sophisticated.[^66] The Throop Code came in for censure, both in its first year and in following decades, precisely for trying to capture all the sophistication of the New York legal system within an unwieldy 3,300 rules.[^67] Codification, however, could help developing societies along law's frontier take a progressive leap forward.
+As India's chief codifier Thomas Macaulay explained, codification "cannot be well performed in an age of barbarism," but also "cannot without great difficulty be performed in an age of freedom." As India balanced between the two, however, "it is the work which especially belongs to a government like that of India---to an enlightened and paternal despotism."[^68]
 
 In America, Macaulay's tool of enlightened despotism spread with the anxiety that capital from the nation's economic center would remain scarce without a Code of remedies that, if not in fact the law of New York, was at least prescribed by New York lawyers and their corporate clients.
-In the two most populous and commercially advanced western states, Texas and Illinois, the need for New York capital failed to move state legislators to adopt the code at the expense of popular sovereignty (although there were concerted efforts in both jurisdictions).[^68] Lacking the self-sufficiency of those two jurisdictions, the other states of the Greater Reconstruction in America adopted a foreign Code, but lawyers, legislators, and their supporters claimed the endorsement of popular sovereignty in doing so.
-Even in North Carolina, whose Democratic newspapers daily called for the repeal "this child of the carpet baggers," Republican editors proclaimed that "the movement" towards procedural codification "comes from the people, from the instinctive logic by which an unprejudiced mind grasps the advantages of the system."[^69]
+In the two most populous and commercially advanced western states, Texas and Illinois, the need for New York capital failed to move state legislators to adopt the code at the expense of popular sovereignty (although there were concerted efforts in both jurisdictions).[^69] Lacking the self-sufficiency of those two jurisdictions, the other states of the Greater Reconstruction in America adopted a foreign Code, but lawyers, legislators, and their supporters claimed the endorsement of popular sovereignty in doing so.
+Even in North Carolina, whose Democratic newspapers daily called for the repeal "this child of the carpet baggers," Republican editors proclaimed that "the movement" towards procedural codification "comes from the people, from the instinctive logic by which an unprejudiced mind grasps the advantages of the system."[^70]
 
@@
 The history of codification on the American periphery troubles cherished notions of American federalism.
-On the one hand, those suspicious of centralized power and critical of national governance since the New Deal have relied on narratives that tout the equality of sovereign states to set their own policies, foster local diversity, and "experiment" with legislative solutions to local issues.[^70] But the history of legal practice and civil remedies is one in which the localism fostered by common law practice rapidly gave way to uniform regulations transmitted by a network of New York lawyers without the slightest interference of the federal government.
+On the one hand, those suspicious of centralized power and critical of national governance since the New Deal have relied on narratives that tout the equality of sovereign states to set their own policies, foster local diversity, and "experiment" with legislative solutions to local issues.[^71] But the history of legal practice and civil remedies is one in which the localism fostered by common law practice rapidly gave way to uniform regulations transmitted by a network of New York lawyers without the slightest interference of the federal government.
 On the other hand, scholars who support the legitimacy of New Deal governance have recently produced an abundant literature unearthing a long tradition of "administrative" law at the state level well before the twentieth century.
-These accounts have focused on administrative adjudication or discretionary regulation within a narrow domain, such as customs houses.[^71] These histories have so far neglected the most widespread and significant instance of nineteenth-century administrative lawmaking in America---the spread of the Field Code through extra-legislative commissions.
+These accounts have focused on administrative adjudication or discretionary regulation within a narrow domain, such as customs houses.[^72] These histories have so far neglected the most widespread and significant instance of nineteenth-century administrative lawmaking in America---the spread of the Field Code through extra-legislative commissions.
 While these histories have sought to demonstrate that Americans from early on could be quite comfortable with administrative law and accepted it as a normal part of the constitutional order, this chapter has shown how lawmaking by commission generated significant political controversy and raised grave questions about popular sovereignty under such delegations, questions that over time were merely dodged rather than answered.
@@
 On the uselessness of the term "big data," see Ted Underwood, "Against (Talking About) 'Big Data,'" *The Stone and the Shell*, blog post, 10 May 2013: <https://tedunderwood.com/2013/05/10/why-it-matters-that-we-dont-know-what-we-mean-by-big-data/>.
-For an example of forming a corpus, see Ted Underwood, Boris Capitanu, Peter Organisciak, Sayan Bhattacharyya, Loretta Auvil, Colleen Fallaw, J.
+For an example of curating a corpus aimed at research questions, see Ted Underwood, Boris Capitanu, Peter Organisciak, Sayan Bhattacharyya, Loretta Auvil, Colleen Fallaw, J.
 Stephen Downie, "Word Frequencies in English-Language Literature, 1700-1922," dataset, v0.2 (HathiTrust Research Center, 2015) doi:10.13012/J8JW8BSJ.
 
-[^32]: **Note codes pulled from HeinOnline and three codes transcribed by hand**.We favored public domain sources where available both for reasons of efficiency (large statute books download much more quickly from Google's servers than from subscription databases) and reproducibility (most of this project can be replicated without subscription databases).
-In each instance we downloaded an entire volume of sessions laws, statutory compilations, or single-volume codes of procedure and then cropped out irrelevant pages, marginalia and footnoted commentary, leaving only the statutory text.
+[^32]: {TODO: list exceptions to Google Books}.
+
+[^33]: In each instance we downloaded an entire volume of sessions laws, statutory compilations, or single-volume codes of procedure and then cropped out irrelevant pages, marginalia and footnoted commentary, leaving only the statutory text.
 After several trials of various implementations of Tesseract (open source) and I.R.I.S.
@@
 The latter feature made cropping between marginalia and the statute more reliable.
-We programmatically removed hyphenated line breaks and standardized spelling for common terms that evolved over the nineteenth century (e.g., *indorsement*).
+We removed hyphenated line breaks and standardized spelling for common terms that evolved over the nineteenth century (e.g., *indorsement*).
 
-[^33]: Cf. Hay & Craven, AJLH article
+[^34]: Cf. Hay & Craven, AJLH article
 
-[^34]:
+[^35]:
 
-[^35]: **Code citations and literature on West as a legal void**.In practice, there are also variations in the texts due to numbering or minor OCR errors as well as actual changes. These differences
+[^36]: **Code citations and literature on West as a legal void**.In practice, there are also variations in the texts due to numbering or minor OCR errors as well as actual changes. These differences
 
-[^36]: This algorithm works by extracting a set number of random tokens from each document, allowing the documents to be represented uniformly and compactly.
+[^37]: This algorithm works by extracting a set number of random tokens from each document, allowing the documents to be represented uniformly and compactly.
 Then those random tokens are grouped into subsets.
@@
 
-[^37]: This matrix required filtering based on what we knew about the process of borrowing.
+[^38]: This matrix required filtering based on what we knew about the process of borrowing.
 We removed any match below a threshold that we determined by reading pairs of matches.
@@
 
-[^38]: This is obvious from the visualization, but also confirmed by all measures of centrality used in network analysis.
+[^39]: This is obvious from the visualization, but also confirmed by all measures of centrality used in network analysis.
 A network is simply a list of edges (in our case the number of sections borrowed) between nodes (in our case, the codes).
@@
 
-[^39]: Non-Field jurisdictions occasionally exhibited a borrowing relationship within a state or across two states.
+[^40]: Non-Field jurisdictions occasionally exhibited a borrowing relationship within a state or across two states.
 In in a few unusual instances they contributed to codes which were derived from the Field Code.
@@
 
-[^40]: spectrogram("CA1851", mutate(best\_matches, match\_code = ifelse(match\_code %in% c("NY1848", "NY1849", "NY1850"), "New York 1849/50", match\_code)), white\_list = 3)
+[^41]: spectrogram("CA1851", mutate(best\_matches, match\_code = ifelse(match\_code %in% c("NY1848", "NY1849", "NY1850"), "New York 1849/50", match\_code)), white\_list = 3)
 
-[^41]: (The visualization here, because of difficulties in precisely matching sections, actually understates the extent of the borrowing.) **Explain** why our method errs on the side of undercounting.
+[^42]: (The visualization here, because of difficulties in precisely matching sections, actually understates the extent of the borrowing.) **Explain** why our method errs on the side of undercounting.
 
-[^42]: Scholars in digital literary studies often speak of the "deformance" of texts.
+[^43]: Scholars in digital literary studies often speak of the "deformance" of texts.
 Clustering the sections of the codes deformed them by pulling the sections out of their context within specific codes and by arranging them by topic in chronological order.
@@
 
-[^43]: Brendan J. Frey and Delbert Dueck, "Clustering by Passing Messages Between Data Points," *Science* 315 (2007): 972--976.
+[^44]: Brendan J. Frey and Delbert Dueck, "Clustering by Passing Messages Between Data Points," *Science* 315 (2007): 972--976.
 
-[^44]: Furthermore, even though the affinity propagation clus- tering algorithm did not fully converge with our peculiar dataset, it did an adequate job clustering the documents.
+[^45]: Furthermore, even though the affinity propagation clus- tering algorithm did not fully converge with our peculiar dataset, it did an adequate job clustering the documents.
 Because there was an exemplar section for each cluster, we were able to merge clusters whose exemplars had a high Jaccard similarity score.
 
-[^45]: We also implemented a method called the Smith Waterman algorithm, which is used for gene sequencing, but which we adapted for natural language.
+[^46]: We also implemented a method called the Smith Waterman algorithm, which is used for gene sequencing, but which we adapted for natural language.
 This is the method used by Smith et al for Viral Texts.
@@
 
-[^46]: E.g., Moretti, Distant Reading; Jockers, Macroanalysis.
+[^47]: E.g., Moretti, Distant Reading; Jockers, Macroanalysis.
 
-[^47]: Samuels, Lisa, and Jerome McGann. "Deformance and Interpretation." *New Literary History* 30.1 (1999) : 25--56; *Stallybrass, Peter. "Against Thinking."* PMLA *122.5 (2007): 1580-1587.*
+[^48]: Samuels, Lisa, and Jerome McGann. "Deformance and Interpretation." *New Literary History* 30.1 (1999) : 25--56; *Stallybrass, Peter. "Against Thinking."* PMLA *122.5 (2007): 1580-1587.*
 
-[^48]:
+[^49]:
 
-[^49]: Those jurisdictions were Nevada (1861), Dakota Territory---which retained the Code when split into North and South (1862), Idaho (1864), Arizona (1864), Montana (1865), Arkansas (1868), North Carolina (1868), Wyoming (1869), Florida (1870), South Carolina (1870), Utah (1870), and Colorado (1877).
+[^50]: Those jurisdictions were Nevada (1861), Dakota Territory---which retained the Code when split into North and South (1862), Idaho (1864), Arizona (1864), Montana (1865), Arkansas (1868), North Carolina (1868), Wyoming (1869), Florida (1870), South Carolina (1870), Utah (1870), and Colorado (1877).
 
-[^50]: Elliott West, "Reconstructing Race," 34 *Western Historical Quarterly* 6 (2003).
+[^51]: Elliott West, "Reconstructing Race," 34 *Western Historical Quarterly* 6 (2003).
 See also Heather Cox Richardson, *West from Appomattox: The Reconstruction of America after the Civil War* (New Haven: Yale University Press, 2007); Sven Beckert, *Monied Metropolis: New York City and the Consolidation of the American Bourgeoisie, 1850-1896* (Harvard 2003); Mark Wahlgren Summers, *The Ordeal of the Reunion: A New History of Reconstruction* (Chapel Hill: University of North Carolina Press, 2014).
@@
 
-[^51]: See, for instance, Rogers Smith, *Civic Ideals: Conflicting Visions of Citizenship in U.S.
+[^52]: See, for instance, Rogers Smith, *Civic Ideals: Conflicting Visions of Citizenship in U.S.
 History* (Yale 1999); Meg Jacobs, William J.
@@
 
-[^52]: Naomi Lamoreaux and John Joseph Wallis, "States, Not Nation: The Sources of Political and Economic Development in the Early United States," Paper Presented at the Economic History Workshop, Harvard University, March 4, 2016.
+[^53]: Naomi Lamoreaux and John Joseph Wallis, "States, Not Nation: The Sources of Political and Economic Development in the Early United States," Paper Presented at the Economic History Workshop, Harvard University, March 4, 2016.
 
-[^53]: For instance, although Tennessee in 1858 adapted nearly 225 sections of its code from Field codes, the state also incorporated nearly 50 sections of the 1852 Code of Alabama, one of the largest borrowings of southern legislation within the corpus we collected.
+[^54]: For instance, although Tennessee in 1858 adapted nearly 225 sections of its code from Field codes, the state also incorporated nearly 50 sections of the 1852 Code of Alabama, one of the largest borrowings of southern legislation within the corpus we collected.
 
-[^54]: Illinois was a fiercely traditional anti-code state.
+[^55]: Illinois was a fiercely traditional anti-code state.
 In later decades, lawyers jokingly called it "the Yellowstone Park of common law pleading." See Charles E.
@@
 
-[^55]: Journal of the Assembly of the Territory of Utah (1870), 15.
+[^56]: Journal of the Assembly of the Territory of Utah (1870), 15.
 
-[^56]: "The Code Again," *Pueblo Daily Chieftain*, February 25, 1877.
+[^57]: "The Code Again," *Pueblo Daily Chieftain*, February 25, 1877.
 
-[^57]: "The Legislature: The Senate Devotes Another Day to the Code," *Denver Daily Tribune*, February 17, 1877.
+[^58]: "The Legislature: The Senate Devotes Another Day to the Code," *Denver Daily Tribune*, February 17, 1877.
 
-[^58]: Governor's Message, in Journal of the House of Assembly of the Territory of Nebraska (1857), 12.
+[^59]: Governor's Message, in Journal of the House of Assembly of the Territory of Nebraska (1857), 12.
 
-[^59]: William A.
+[^60]: William A.
 Jenkins to William Blount Rodman, January 14, 1868, Rodman Papers.
@@
 
-[^60]: Gordon Morris Bakken, *Practicing Law in Frontier California* (Nebraska 1991), 51-54.
+[^61]: Gordon Morris Bakken, *Practicing Law in Frontier California* (Nebraska 1991), 51-54.
 The new western history ushered in by Patricia Nelson Limerick, *The Legacy of Conquest: The Unbroken Past of the American West* (Norton 1987) and Richard White, *"It's Your Misfortune and None of My Own": A History of the American West* (Oklahoma 1991) is now returning to issues of political economy.
@@
 
-[^61]: "The Code," *Denver Daily Tribune*, January 10, 1877; "The Code," *Denver Daily Times*, January 27, 1877.
+[^62]: "The Code," *Denver Daily Tribune*, January 10, 1877; "The Code," *Denver Daily Times*, January 27, 1877.
 
-[^62]: "A Code of Civil Procedure," *Denver Daily Times*, January 12, 1877.
+[^63]: "A Code of Civil Procedure," *Denver Daily Times*, January 12, 1877.
 
-[^63]: "The Code," *Denver Daily Tribune*, January 31, 1877.
+[^64]: "The Code," *Denver Daily Tribune*, January 31, 1877.
 
-[^64]: See Gunther A.
+[^65]: See Gunther A.
 Weiss, "The Enchantment of Codification in the Common-Law World," 25 *Yale Journal of International Law* 435 (2000).
@@
 
-[^65]: See, for instance, James C.
+[^66]: See, for instance, James C.
 Carter's classic defense of the common law against codification, The Ideal and the Actual in the Law, Address to the American Bar Association, August 21, 1890, at 28 ("the legislature should never attempt to perform the function of the judge, that of simply ascertaining and declaring existing customs.
@@
 
-[^66]: See, for instance, "Note," 29 *Albany Law Journal* 141, 142 (1884); Millar, *Civil Procedure of the Trial Court*, 55-56.
+[^67]: See, for instance, "Note," 29 *Albany Law Journal* 141, 142 (1884); Millar, *Civil Procedure of the Trial Court*, 55-56.
 
-[^67]: 19 *Hansard Parliamentary Debates* 531.
+[^68]: 19 *Hansard Parliamentary Debates* 531.
 
-[^68]: Texas commissioned the preparation of a code of civil procedure in 1855, and the legislature scheduled an extra session to consider it but ultimately never passed the law.
+[^69]: Texas commissioned the preparation of a code of civil procedure in 1855, and the legislature scheduled an extra session to consider it but ultimately never passed the law.
 21 *Texas Reports* (Hartley) xi (1882); *Texas State Times*, December 15, 1855.
@@
 
-[^69]: "The Code," *Weekly Standard* (Raleigh), May 26, 1869.
+[^70]: "The Code," *Weekly Standard* (Raleigh), May 26, 1869.
 
-[^70]: See, for instance, the summary of the states-as-laboratories literature in Brian Galle & Joseph Leahy, "Laboratories of Democracy?
+[^71]: See, for instance, the summary of the states-as-laboratories literature in Brian Galle & Joseph Leahy, "Laboratories of Democracy?
 Policy Innovation in Decentralized Governments," 58 *Emory Law Journal* 1333 (2009).
 
-[^71]: See Daniel Ernst, *Tocqueville's Nightmare: The Administrative State Emerges in America, 1900-1940* (Oxford: Oxford University Press, 2014); Jerry L.
+[^72]: See Daniel Ernst, *Tocqueville's Nightmare: The Administrative State Emerges in America, 1900-1940* (Oxford: Oxford University Press, 2014); Jerry L.
 Mashaw, *Creating the Administrative Constitution: The Lost One Hundred Years of American Administrative Law* (Yale Law Library 2012); Gautham Rao, *National Duties: Custom Houses and the Making of the American State* (University of Chicago 2016).

### 2016-06-25 article/article.Rmd
Cite Viral Texts

@@
 Nevertheless, digital text analysis in the humanities has mostly been published by literary scholars, including Stephen Ramsay, *Reading Machines: Toward an Algorithmic Criticism* (Urbana: University of Illinois Press, 2011); Franco Moretti, *Distant Reading* (New York: Verso, 2013); Matthew L.
-Jockers, *Macroanalysis: Digital Methods and Literary History* (Urbana: University of Illinois Press, 2013); Ted Underwood, *Why Literary Periods Mattered: Historical Contrast and the Prestige of English Studies* (Stanford: Stanford University Press, 2013).
+Jockers, *Macroanalysis: Digital Methods and Literary History* (Urbana: University of Illinois Press, 2013); Ted Underwood, *Why Literary Periods Mattered: Historical Contrast and the Prestige of English Studies* (Stanford: Stanford University Press, 2013); Ryan Cordell and David A.
+Smith, *Viral Texts: Mapping Networks of Reprinting in 19th-Century Newspapers and Magazines*, NULab for Texts Maps and Networks, Northeastern University (2012--): <http://viraltexts.org>.
 Related but less well regarded by humanities scholars is work in "culturomics": see Jean-Baptiste Michel et al., "Quantitative Analysis of Culture Using Millions of Digitized Books", *Science* 331, no.

### 2016-06-25 article/article.Rmd
Cite digital legal history

--- 2016-06-25 article/article.Rmd
@@
     fig_caption: True
+    md_extensions: "-tex_math_single_backslash"
     number_sections: False
-    md_extensions: -tex_math_single_backslash
 title: The Spine of American Legal Practice
@@
 Because most codes were public statutes, they were widely printed and distributed and therefore found their way into libraries digitized by Google Books.
-Where possible, we collected our corpus from Google's publicly accessible database.
-We used optical character recognition software (OCR) to create plain-text versions of the codes, which we edited lightly---we corrected section markers by hand as necessary and wrote a script to fix the most common OCR errors.[^32]
+We drew primarily from the Google Books, filling in gaps from other databases as necessary.[^32] We used optical character recognition software (OCR) to create plain-text versions of the codes, which we edited lightly, correcting section markers by hand as necessary and writing a script to fix the most obvious OCR errors.[^33]
 
 The most important step we took in processing the files was to split each section of the code into its own text file.
-Codes varied in their organizations, but they universally divided specific regulations into *sections* (or, on occasion, *articles*).
-The discursive formation of these texts not only provides a handy organizational scheme for digital approaches, sections were historically the way legislators borrowed their texts.[^33] Codifiers took their sources apart by sections, rearranging here, editing, drafting, and then re-combining there.
+Codes varied in how they were organized, but they universally divided specific regulations into *sections* (or, on occasion, *articles*).
+Not only does the discursive form of these texts provide a handy organizational scheme for digital methods, but historically sections were also the way legislators borrowed their texts.
+Codifiers took their sources apart by sections, rearranging here, editing, drafting, and then re-combining there.
 Despite the fact that states differed widely on what topics they included in "civil procedure," sectioning the codes allowed us to assess similarity even among codes of quite different lengths and coverage.
-For instance, we know from historical evidence that California's 1851 code was derived from New York's 1850 code.
-(Stephen Johnson Field, David Dudley's brother, was the lawyer who imported New York's code into California.[^34]) But the New York code is over 150,000 words long, where was California's code was just over 50,000 words long.
-Those rather disparate lengths mean that comparing all of the California code to all of the New York code is a less meaningful comparison that than comparing each section in the California code to each section in the New York code, where matching sections will be a similar length.
+For instance, we know that California's 1851 code was derived from New York's 1850 code.
+(Stephen Johnson Field, David Dudley Field's brother, was the lawyer who imported New York's code into California.[^34]) But the New York code is over 150,000 words long, whereas California's code was just over 50,000 words long.
+Those disparate lengths mean that comparing all of the California code to all of the New York code is a less meaningful comparison that than comparing each section in the California code to each section in the New York code, where matching sections will have a similar length.
 
-The next step was to compare sections to one another and measure the similarity between them.
+Having divided the texts according to a historically justified pattern, our next step was to compare each section to every other section and measure the similarity between them.
 To continue the New York-to-California example, consider the following pairs of sections.
 The first pair is from the final draft of the New York Field Code.
-These sections completely abolish prior practice and begin to rebuild the procedure system from the ground up:
+These sections completely abolished prior practice and began to rebuild the procedure system from the ground up:
 
@@
 
-A well-known method for measuring the similarity of two documents involves dividing texts up into "tokens" of consecutive words and calculating a Jaccard score, defined as ratio between the number of tokens that the two document have in common to the total number of tokens that appear in both documents.
+A well-known method for measuring the similarity of two documents involves dividing texts up into tokens of consecutive words (called n-grams) and calculating a Jaccard similarity score, defined as ratio between the number of tokens that the two document have in common to the total number of tokens that appear in both documents.
 We used five-word tokens and "shingled" them, meaning that for the New York sections above, the first token was "the distinction between actions at," the second token was "distinction between actions at law," and so on.
 These tokens each contain more meaning than a single word, yet because they are shingled they are robust to changes in the text or noisy OCR.
-A Jaccard score (in set notation, EQUATION) will always produce a number between 0 (complete dissimilarity) and 1 (complete similarity).
+A Jaccard similarity score will always be in a range between 0 (complete dissimilarity) and 1 (complete similarity).
 
@@
 On the uselessness of the term "big data," see Ted Underwood, "Against (Talking About) 'Big Data,'" *The Stone and the Shell*, blog post, 10 May 2013: <https://tedunderwood.com/2013/05/10/why-it-matters-that-we-dont-know-what-we-mean-by-big-data/>.
-For an example of forming a corpus, see Ted Underwood, Boris Capitanu, Peter Organisciak, Sayan Bhattacharyya, Loretta Auvil, Colleen Fallaw, J.
+For an example of curating a corpus aimed at research questions, see Ted Underwood, Boris Capitanu, Peter Organisciak, Sayan Bhattacharyya, Loretta Auvil, Colleen Fallaw, J.
 Stephen Downie, "Word Frequencies in English-Language Literature, 1700-1922," dataset, v0.2 (HathiTrust Research Center, 2015) doi:10.13012/J8JW8BSJ.
 
-[^32]: **Note codes pulled from HeinOnline and three codes transcribed by hand**.We favored public domain sources where available both for reasons of efficiency (large statute books download much more quickly from Google's servers than from subscription databases) and reproducibility (most of this project can be replicated without subscription databases).
-In each instance we downloaded an entire volume of sessions laws, statutory compilations, or single-volume codes of procedure and then cropped out irrelevant pages, marginalia and footnoted commentary, leaving only the statutory text.
+    Only a few scholars have turned their attention to the computer analysis of legal texts for historical purposes, including Paul Craven, "Detección automática y visualización de dominios específicos similares en documentos: análisis DWIC y su aplicación en el Proyecto Master & Servant \[Automatic Detection and Visualization of Domain-Specific Similarities in Documents: DWIC Analysis and its Application in the Master & Servant Project\]," published on CD-ROM in F.
+J.
+A Perez et al., eds., *La Historia en una nueva frontera \[History in a New Frontier\]* (Digibis: Ediciones de la Universidad de Castilla-La Mancha, 1998); Paul Craven and Douglas Hay, "Computer Applications in Comparative Historical Research: The Master & Servant Project at York University, Canada," *History and Computing* 7, no.
+2 (1995); Paul Craven and W.
+Traves, "A General-Purpose Hierarchical Coding Engine and Its Application to Comparative Analysis of Statutes," *Literary and Linguistic Computing* 8, no.
+1 (1993): 27--32, doi:10.1093/llc/8.1.27; Eric C.
+Nystrom and David S.
+Tanenhaus, "The Future of Digital Legal History: No Magic, No Silver Bullets," *American Journal of Legal History* 56, no.
+1 (2016): 150--67, doi:10.1093/ajlh/njv017; Dan Cohen, Frederick Gibbs, Tim Hitchcock, Geoffrey Rockwell, et al., "Data Mining with Criminal Intent," white paper, 31 August 2011, <http://criminalintent.org>.
+
+[^32]: {TODO: list exceptions to Google Books}.
+
+[^33]: In each instance we downloaded an entire volume of sessions laws, statutory compilations, or single-volume codes of procedure and then cropped out irrelevant pages, marginalia and footnoted commentary, leaving only the statutory text.
 After several trials of various implementations of Tesseract (open source) and I.R.I.S.
@@
 The latter feature made cropping between marginalia and the statute more reliable.
-We programmatically removed hyphenated line breaks and standardized spelling for common terms that evolved over the nineteenth century (e.g., *indorsement*).
+We removed hyphenated line breaks and standardized spelling for common terms that evolved over the nineteenth century (e.g., *indorsement*).
 
-[^33]: Cf. Hay & Craven, AJLH article
-
-[^34]:
+[^34]: {TODO: citation on Stephen Johnson Field}
 

### 2016-06-25 article/article.Rmd
Define Jaccard similarity

@@
 
-A well-known method for measuring the similarity of two documents involves dividing texts up into tokens of consecutive words (called n-grams) and calculating a Jaccard similarity score, defined as ratio between the number of tokens that the two document have in common to the total number of tokens that appear in both documents.
+A common method for measuring the similarity of two documents involves dividing texts up into tokens of consecutive words (called n-grams) and calculating a Jaccard similarity score, defined as ratio between the number of tokens that the two document have in common to the total number of tokens that appear in both documents.
 We used five-word tokens and "shingled" them, meaning that for the New York sections above, the first token was "the distinction between actions at," the second token was "distinction between actions at law," and so on.
 These tokens each contain more meaning than a single word, yet because they are shingled they are robust to changes in the text or noisy OCR.
-A Jaccard similarity score will always be in a range between 0 (complete dissimilarity) and 1 (complete similarity).
+A Jaccard similarity score will always be in a range between 0 (complete dissimilarity) and 1 (complete similarity).^[The formal definition of the Jaccard similarity for two sets, $A$ and $B$, is $$J(A, B) = \frac{ | A \cap B | }{ | A \cup B | }$$]
 

### 2016-06-25 article/article.Rmd
Map with caption

@@
 
+![This map shows which states adopted codes of civil procedure based on the New York Field Code.
+The date shown is the date of the first enactment of a procedure code; most states subsequently revised their codes.
+Note that many southern states and western states came to adopt the Field Code during the period of Greater Reconstruction.
+By the end of the nineteenth-century, thirty-one jurisdictions (those displayed on the map, plus Alaska) had adopted a version of the Field Code.](field-code-states-map.jpeg)
+
 The code would encounter similar difficulties in each jurisdiction that adopted it.
@@
 
-NY1850-554 | NY1850-555 | CA1851-001 | CA1851-002 |
-
-|:----------|:----------:|:----------:|:----------:|:----------:|
-
+|            | NY1850-554 | NY1850-555 | CA1851-001 | CA1851-002 |
+|:-----------|:----------:|:----------:|:----------:|:----------:|
 |NY1850-554  |            |          0 |       0.14 |          0 |
-
 |NY1850-555  |            |            | 0          |       0.41 |
-
 |CA1851-001  |            |            |            |          0 |
-
 |CA1851-002  |            |            |            |            |
 
-As we would expect the first respective sections (New York § 554 and California § 1) have a score of 0.14, which indicates that they are similar but have significant differences, while the second sections (New York § 555 to California § 2) have a much higher similarity score since only a few words were changed.
-Just as important when we compare the first section in New York to the second section in California, we get a score of 0; the two sections are nothing like each other.
+As we would expect the first respective sections (New York §554 and California §1) have a score of 0.14, which indicates that they are similar but have significant differences, while the second sections (New York §555 to California §2) have a much higher similarity score since only a few words were changed.
+Just as important, when we compare the first section in New York to the second section in California, we get a score of 0; the two sections are nothing like each other.
 
@@
 While this is easy enough to conceptualize, such a matrix is actually quite large, containing about 4.8 billion comparisons.
-This would take an unreasonable amount of computation time, and most of these comparisons would be unnecessary, since each section has no relationship to most other sections (like the matrix above, most scores will be zero).
-We therefore implemented the minhash/locality sensitive hashing (LSH) algorithm to detect candidate pairs, that is, documents which were likely to be matches, and then we measured the Jaccard score for only those candidate pairs.[^36]
+This would take an unreasonable amount of computation time, and most of these comparisons would be unnecessary, since each section has no relationship to most other sections.
+
+We therefore implemented the minhash/locality sensitive hashing (LSH) algorithm to detect pairs of possible matches. This algorithm
+
+that is, documents which were likely to be matches, and then we measured the Jaccard score for only those candidate pairs.[^36]
 

### 2016-06-26 article/article.Rmd
Cite all the text reuse and repository things

@@
     fig_caption: True
-    md_extensions: "-tex_math_single_backslash"
+    md_extensions: '-tex_math_single_backslash'
     number_sections: False
@@
 
-In the theory of Euro-American lawyers, California had no prior practice to abolish, so the code began more simply:
+In the theory of Euro-American lawyers, California had no prior practice to abolish, so the code began more simply:[^35]
 
@@
 
-The pairs are obviously related to one another, both in terms of their legal force and in terms of the actual words used.[^35]
+The pairs are obviously related to one another, both in terms of their legal force and in terms of the actual words used.
 
@@
 These tokens each contain more meaning than a single word, yet because they are shingled they are robust to changes in the text or noisy OCR.
-A Jaccard similarity score will always be in a range between 0 (complete dissimilarity) and 1 (complete similarity).^[The formal definition of the Jaccard similarity for two sets, $A$ and $B$, is $$J(A, B) = \frac{ | A \cap B | }{ | A \cup B | }$$]
+A Jaccard similarity score will always be in a range between 0 (complete dissimilarity) and 1 (complete similarity).[^36]
 
@@
 
-|            | NY1850-554 | NY1850-555 | CA1851-001 | CA1851-002 |
-|:-----------|:----------:|:----------:|:----------:|:----------:|
-|NY1850-554  |            |          0 |       0.14 |          0 |
-|NY1850-555  |            |            | 0          |       0.41 |
-|CA1851-001  |            |            |            |          0 |
-|CA1851-002  |            |            |            |            |
+                NY1850-554   NY1850-555   CA1851-001   CA1851-002
+  ------------ ------------ ------------ ------------ ------------
+  NY1850-554                     0           0.14          0
+  NY1850-555                                  0           0.41
+  CA1851-001                                               0
+  CA1851-002
 
@@
 This would take an unreasonable amount of computation time, and most of these comparisons would be unnecessary, since each section has no relationship to most other sections.
+We therefore implemented the minhash/locality sensitive hashing (LSH) algorithm to detect pairs of possible matches quickly.This algorithm works by extracting a set number of random tokens from each document to create a document signature; this subset makes it possible to approximate the Jaccard similarity of two documents.
+These signatures can then be used to identify each of the billions of possible pairs of sections as likely to be matches or not.
+By setting parameters to the algorithm, one can control how sensitive the algorithm is in drawing the line between genuine and spurious matches.
+We then measured the actual Jaccard score for only those candidate pairs.[^37]
 
-We therefore implemented the minhash/locality sensitive hashing (LSH) algorithm to detect pairs of possible matches. This algorithm
-
-that is, documents which were likely to be matches, and then we measured the Jaccard score for only those candidate pairs.[^36]
-
-The result was a matrix of matches, with over 45,000 genuine matches.
-For each section in the corpus, after making some adjustments to remove anachronisms and spurious matches,[^37] we were able to identify the section from which it was most likely borrowed.
-In other words, we had traced the work of the commissioners' scissors and paste-pots through the course of their codes.
+The result was a matrix of similarity scores, with over 45,000 genuine matches.
+For each section in the corpus, after making some adjustments to remove anachronisms and spurious matches, we were able to identify the section from which it was most likely borrowed.[^38] In other words, we had traced the work of the commissioners' scissors and paste-pots through the course of their codes.[^39]
 
@@
 The resulting network graph (**Figure X: Network Graph**) tells the genealogy of civil procedure in the United States.
-The New York codes, especially the finished draft of 1850, are central to the entire network.[^38] Yet it is important to note that New York spurred different traditions within the procedural network.
+The New York codes, especially the finished draft of 1850, are central to the entire network.[^40] Yet it is important to note that New York spurred different traditions within the procedural network.
 Variations in the Field drafts meant that different states could borrow different versions of the Field Code.
@@
 Finally, our corpus included a number of statutes which stood outside the Field Code tradition, such as Virginia and West Virginia regulations, statutes from Massachusetts and Maine, and southern codes from Georgia to Louisiana.
-These statutes show that the dominance of the Field Code was not total, and a number of older jurisdictions remained outside of its ambit.[^39] But virtually every jurisdiction established or reconstructed after 1850 became a part of the Field Code network, and no other tradition achieved anywhere near the same coherence across state lines.
+These statutes show that the dominance of the Field Code was not total, and a number of older jurisdictions remained outside of its ambit.[^41] But virtually every jurisdiction established or reconstructed after 1850 became a part of the Field Code network, and no other tradition achieved anywhere near the same coherence across state lines.
 
@@
 California's 1851 code borrowed heavily from two sources.
-The bulk of the code was taken directly from New York's 1849 or 1850 codes (which are difficult to distinguish exactly from one another.[^40] The remainder of the code was borrowed from California's 1850 code.
+The bulk of the code was taken directly from New York's 1849 or 1850 codes (which are difficult to distinguish exactly from one another.[^42] The remainder of the code was borrowed from California's 1850 code.
 The 1850 version was in turn borrowed from the New York codes **TODO: might as well show this, esp.
@@
 The bulk of this code was lifted from the Washington 1855 code with only small amendments.
-The main exception was a probate code drawn from California's 1872 code.[^41] Like many of the last generation codes, the text of the procedure code had stabilized in a local manifestation of a regional tradition.
+The main exception was a probate code drawn from California's 1872 code.[^43] Like many of the last generation codes, the text of the procedure code had stabilized in a local manifestation of a regional tradition.
 The code was still genuinely a Field Code, with a great deal of similarity to the original New York Field Codes, but its specific form depended on the many edits and rearrangements that state code commissioners had made to the text.
@@
 So far we have retained the context of the surrounding sections within a particular code.
-But since our fundamental unit of comparison is section to section, we can use a technique called clustering to deform the texts (as a literary scholar might say) in order to see the textual history of how particular regulations embedded in individual sections changed over time.[^42]
+But since our fundamental unit of comparison is section to section, we can use a technique called clustering to deform the texts (as a literary scholar might say) in order to see the textual history of how particular regulations embedded in individual sections changed over time.[^44]
 
@@
 There are innumerable clustering algorithms, but we needed one that could work with a sparse matrix and one whose assumptions matched the characteristics of our problem.
-We decided to use affinity propagation clustering.[^43] That algorithm assumes that each cluster has an "exemplar" item which the other items are similar to.
-That assumption fits nicely with borrowings from the Field Code, where a single section (likely from the 1850 New York code) had many borrowings, but where there could also be innovative sections in other stages.[^44]
+We decided to use affinity propagation clustering.[^45] That algorithm assumes that each cluster has an "exemplar" item which the other items are similar to.
+That assumption fits nicely with borrowings from the Field Code, where a single section (likely from the 1850 New York code) had many borrowings, but where there could also be innovative sections in other stages.[^46]
 
@@
 The biggest cluster, for instance, which concerned the use of affidavits in pleading, contained 103 sections.
-With those clusters, we were able to organize the documents chronologically.[^45] This method is particularly useful when tracking the variations in in the law from jurisdiction to jurisdiction.
+With those clusters, we were able to organize the documents chronologically.[^47] This method is particularly useful when tracking the variations in in the law from jurisdiction to jurisdiction.
 It provides historians with a way of noticing small changes in the wording and substance of the law.
-Most discussions of algorithmic reading have focused on "distant reading,"[^46] or have balanced the claims of distant reading by using it as a means to enable close reading.
+Most discussions of algorithmic reading have focused on "distant reading,"[^48] or have balanced the claims of distant reading by using it as a means to enable close reading.
 This method of clustering, however, is a kind of algorithmic close reading.
-By deforming the texts---taking them out of the context of the codes and putting them in the context of their particular variations---we are able to pay attention to those variations.[^47]
+By deforming the texts---taking them out of the context of the codes and putting them in the context of their particular variations---we are able to pay attention to those variations.[^49]
 
@@
 The Field code's summary judgment brought down the time of debt collection to a matter of weeks.
-Effectively, the code traded the rhythms of agriculture for the rhythms of merchant finance.[^48]
+Effectively, the code traded the rhythms of agriculture for the rhythms of merchant finance.[^50]
 
@@
 Alerted by these clustering patterns to the significance of creditors' remedies in the developing West and re-developing South, it was not difficult to find evidence of westerners and southerners commenting on these features of the code or its connections to New York capital.
-Twelve of the states and territories that copied the Field Code mostly closely did so during the Civil War and Reconstruction era---four states in the former Confederacy and eight jurisdictions in the Far West.[^49] As with other areas of postbellum historiography, it turns out one may learn a lot by holding the postbellum American South and American West together.
+Twelve of the states and territories that copied the Field Code mostly closely did so during the Civil War and Reconstruction era---four states in the former Confederacy and eight jurisdictions in the Far West.[^51] As with other areas of postbellum historiography, it turns out one may learn a lot by holding the postbellum American South and American West together.
 
-In the last decade, scholars of Reconstruction have broadened the scope of their study to include both the South and the West as two sites in one "Greater Reconstruction." These studies have illustrated the ways that military conquest, rapid industrialization, and the resettlement and education of ethnic minorities developed similarly in each region, guided by economic elites in New York and political administrators in Washington.[^50] In tracing the legal aspects of this Greater Reconstruction, scholars have focused almost entirely on constitutional rights of citizenship and civil equality or the expansion of federal power.[^51] While the 1860s and 1870s were of course a transformative period in the history of civil rights and the creation of a national state, they were also the decades in which many local legal institutions and practices were transformed not by federal power but by state codification.
+In the last decade, scholars of Reconstruction have broadened the scope of their study to include both the South and the West as two sites in one "Greater Reconstruction." These studies have illustrated the ways that military conquest, rapid industrialization, and the resettlement and education of ethnic minorities developed similarly in each region, guided by economic elites in New York and political administrators in Washington.[^52] In tracing the legal aspects of this Greater Reconstruction, scholars have focused almost entirely on constitutional rights of citizenship and civil equality or the expansion of federal power.[^53] While the 1860s and 1870s were of course a transformative period in the history of civil rights and the creation of a national state, they were also the decades in which many local legal institutions and practices were transformed not by federal power but by state codification.
 Naomi Lamoreaux and John Joseph Wallis have recently argued that in the creation of a modern American economy, "the federal government played *no* role in this process until the Civil War, and even then it played only a bit part." The history of the Field Code's migration helps to substantiate this claim.
 While Lamoreaux and Wallis focus on the development of banking, transportation, and incorporation at the state level, it was the Procedure Code that provided the structure of civil remedies that protected these state institutions.
-And procedure codes were, of course, the creatures of state governance.[^52]
+And procedure codes were, of course, the creatures of state governance.[^54]
 
 With the universal complaints that time was too short or commissioners too democratically irresponsible, one might expect the code to have faced more competition from other workable statutes.
-Southern states that drew more on the civilian code tradition such as Louisiana and Alabama offered other options for states desiring to reform common law practice.[^53] And if Euro-Americans believed law had to be imported into the West, Colorado immigrants proved that the common law of Illinois was just as amenable to statutory importation as New York law.[^54] But what codifiers saw when they looked at New York, more so than Louisiana, Alabama, or Illinois, was the Empire State of commercial capital.
+Southern states that drew more on the civilian code tradition such as Louisiana and Alabama offered other options for states desiring to reform common law practice.[^55] And if Euro-Americans believed law had to be imported into the West, Colorado immigrants proved that the common law of Illinois was just as amenable to statutory importation as New York law.[^56] But what codifiers saw when they looked at New York, more so than Louisiana, Alabama, or Illinois, was the Empire State of commercial capital.
 And the putative fears, demands, and desires of a personified Capital continually wielded promises---and threats---in the debates over procedural codification.
 The early Mormon settlers of Utah persistently avoided the mining frenzy as well as codification.
-By 1870, however, the territory's governor directed the legislature's attention to the recent Code of Nevada, a code "for a people whose interests in many respects are similar to our own." Of course, standing behind the Nevada Code was "the State of New York---a State which is an empire in itself and whose commercial transactions are far greater than those of any other State in the Union." By copying its code, Utah too could be "rewarded by equal advantages."[^55] Code proponents in Colorado similarly parried arguments that a code would be a "foreign" imposition by pointing to the fact that it has been "adopted twenty-nine years ago by the Empire state of the Union" and they promised that the code of the nation's uniquely commercial empire could bring wealth in its wake.[^56]
+By 1870, however, the territory's governor directed the legislature's attention to the recent Code of Nevada, a code "for a people whose interests in many respects are similar to our own." Of course, standing behind the Nevada Code was "the State of New York---a State which is an empire in itself and whose commercial transactions are far greater than those of any other State in the Union." By copying its code, Utah too could be "rewarded by equal advantages."[^57] Code proponents in Colorado similarly parried arguments that a code would be a "foreign" imposition by pointing to the fact that it has been "adopted twenty-nine years ago by the Empire state of the Union" and they promised that the code of the nation's uniquely commercial empire could bring wealth in its wake.[^58]
 
@@
 Hamill replied that he knew of one California company of capitalists who were deterred from investing in mining property here wholly on account of the practice of the courts in mining cases.
-If we had had this code years ago, Colorado would now have a larger amount of California capital in her mines."[^57] Codifiers argued that, in attracting capital, procedure was at least as important as the substantive rules of property and contract, because procedure secured the remedies that actually protected investments.
-"Men of capital and enterprise will not make investments and devote their time and energies to those works of internal improvement so necessary for the speedy development of our natural resources, and for the settlement and building up the country," Nebraska's governor reasoned, "unless ample protection is afforded them, by legal enactment, for the capital invested and labor employed." And he therefore urged swift passage of the Field Code.[^58]
+If we had had this code years ago, Colorado would now have a larger amount of California capital in her mines."[^59] Codifiers argued that, in attracting capital, procedure was at least as important as the substantive rules of property and contract, because procedure secured the remedies that actually protected investments.
+"Men of capital and enterprise will not make investments and devote their time and energies to those works of internal improvement so necessary for the speedy development of our natural resources, and for the settlement and building up the country," Nebraska's governor reasoned, "unless ample protection is afforded them, by legal enactment, for the capital invested and labor employed." And he therefore urged swift passage of the Field Code.[^60]
 
@@
 Let the law enforce punctuality; let the people of North Carolina learn that the great law of business is, that 'time is of the essence of the contract,' and incur no debt that they do not expect to meet at maturity." Under the more certain and speedy remedies of the code, "we may expect that the secret hoards of the frugal among ourselves will be offered to loan, and even that the vaults of the banks of New-York ...
-will be open to our industry."[^59]
+will be open to our industry."[^61]
 
@@
 While the so-called new western history has shed significant light on neglected topics of Indian dispossession and environmental management, it has often done so by leaving out of view matters of political economy, a staple of the old western history.
-As one work in that older tradition argued, "Debt collection was the central part of law practice for the \[western\] bar and remained a key part of private practice throughout the century."[^60] On that understanding, one western lawyer succinctly summarized the difference between the code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, ...
-that he did not also break out somewhere with 'take for instance the case of an action on a promissory note,' as though the collection of notes was about all there could be any law needed for."[^61]
+As one work in that older tradition argued, "Debt collection was the central part of law practice for the \[western\] bar and remained a key part of private practice throughout the century."[^62] On that understanding, one western lawyer succinctly summarized the difference between the code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, ...
+that he did not also break out somewhere with 'take for instance the case of an action on a promissory note,' as though the collection of notes was about all there could be any law needed for."[^63]
 
 The creditors' remedies in the code gave the codifiers their leading argument against criticisms rooted in the ideology of popular sovereignty.
-"There is no doubt but the people are in favor of anything that promises to hurry up that proverbially slow and blind old female called Justice, and they will go for the old code," one Colorado newspaper announced.[^62] New York's "code practice is the best in excellence," stated another, "and when I say *best* I do not mean best for lawyers only, but best for the people---the commonwealth."[^63] If the People favored economic progress, certainty of remedy, and efficiency in proceedings, then they favored the New York Code, no matter whether they understood or cared about technical rules of pleading and joinder.
+"There is no doubt but the people are in favor of anything that promises to hurry up that proverbially slow and blind old female called Justice, and they will go for the old code," one Colorado newspaper announced.[^64] New York's "code practice is the best in excellence," stated another, "and when I say *best* I do not mean best for lawyers only, but best for the people---the commonwealth."[^65] If the People favored economic progress, certainty of remedy, and efficiency in proceedings, then they favored the New York Code, no matter whether they understood or cared about technical rules of pleading and joinder.
 Thus, in their arguments the codifiers imagined themselves the champions of popular sovereignty, for it was they who accomplished what the People actually desired.
@@
 Both jurisdictions, while reforming the practice of law, largely rejected codification within their own borders but encouraged it among their economic dependents.
-The English commissioned a full codification of law for India and colonies in Singapore, while further codifications produced by Field in New York covering civil and penal law were adopted in California and other western jurisdictions.[^64] In both places, leading arguments against codification carried a civilizational logic of empire: Advanced societies could not codify their law, for to do so would be to freeze the progress of legal science.
+The English commissioned a full codification of law for India and colonies in Singapore, while further codifications produced by Field in New York covering civil and penal law were adopted in California and other western jurisdictions.[^66] In both places, leading arguments against codification carried a civilizational logic of empire: Advanced societies could not codify their law, for to do so would be to freeze the progress of legal science.
 What appeared to some to be a hopeless mass of confusion was to common law defenders the sign of true legal sophistication.
-Science was, after all, sophisticated.[^65] The Throop Code came in for censure, both in its first year and in following decades, precisely for trying to capture all the sophistication of the New York legal system within an unwieldy 3,300 rules.[^66] Codification, however, could help developing societies along law's frontier take a progressive leap forward.
-As India's chief codifier Thomas Macaulay explained, codification "cannot be well performed in an age of barbarism," but also "cannot without great difficulty be performed in an age of freedom." As India balanced between the two, however, "it is the work which especially belongs to a government like that of India---to an enlightened and paternal despotism."[^67]
+Science was, after all, sophisticated.[^67] The Throop Code came in for censure, both in its first year and in following decades, precisely for trying to capture all the sophistication of the New York legal system within an unwieldy 3,300 rules.[^68] Codification, however, could help developing societies along law's frontier take a progressive leap forward.
+As India's chief codifier Thomas Macaulay explained, codification "cannot be well performed in an age of barbarism," but also "cannot without great difficulty be performed in an age of freedom." As India balanced between the two, however, "it is the work which especially belongs to a government like that of India---to an enlightened and paternal despotism."[^69]
 
 In America, Macaulay's tool of enlightened despotism spread with the anxiety that capital from the nation's economic center would remain scarce without a Code of remedies that, if not in fact the law of New York, was at least prescribed by New York lawyers and their corporate clients.
-In the two most populous and commercially advanced western states, Texas and Illinois, the need for New York capital failed to move state legislators to adopt the code at the expense of popular sovereignty (although there were concerted efforts in both jurisdictions).[^68] Lacking the self-sufficiency of those two jurisdictions, the other states of the Greater Reconstruction in America adopted a foreign Code, but lawyers, legislators, and their supporters claimed the endorsement of popular sovereignty in doing so.
-Even in North Carolina, whose Democratic newspapers daily called for the repeal "this child of the carpet baggers," Republican editors proclaimed that "the movement" towards procedural codification "comes from the people, from the instinctive logic by which an unprejudiced mind grasps the advantages of the system."[^69]
+In the two most populous and commercially advanced western states, Texas and Illinois, the need for New York capital failed to move state legislators to adopt the code at the expense of popular sovereignty (although there were concerted efforts in both jurisdictions).[^70] Lacking the self-sufficiency of those two jurisdictions, the other states of the Greater Reconstruction in America adopted a foreign Code, but lawyers, legislators, and their supporters claimed the endorsement of popular sovereignty in doing so.
+Even in North Carolina, whose Democratic newspapers daily called for the repeal "this child of the carpet baggers," Republican editors proclaimed that "the movement" towards procedural codification "comes from the people, from the instinctive logic by which an unprejudiced mind grasps the advantages of the system."[^71]
 
@@
 The history of codification on the American periphery troubles cherished notions of American federalism.
-On the one hand, those suspicious of centralized power and critical of national governance since the New Deal have relied on narratives that tout the equality of sovereign states to set their own policies, foster local diversity, and "experiment" with legislative solutions to local issues.[^70] But the history of legal practice and civil remedies is one in which the localism fostered by common law practice rapidly gave way to uniform regulations transmitted by a network of New York lawyers without the slightest interference of the federal government.
+On the one hand, those suspicious of centralized power and critical of national governance since the New Deal have relied on narratives that tout the equality of sovereign states to set their own policies, foster local diversity, and "experiment" with legislative solutions to local issues.[^72] But the history of legal practice and civil remedies is one in which the localism fostered by common law practice rapidly gave way to uniform regulations transmitted by a network of New York lawyers without the slightest interference of the federal government.
 On the other hand, scholars who support the legitimacy of New Deal governance have recently produced an abundant literature unearthing a long tradition of "administrative" law at the state level well before the twentieth century.
-These accounts have focused on administrative adjudication or discretionary regulation within a narrow domain, such as customs houses.[^71] These histories have so far neglected the most widespread and significant instance of nineteenth-century administrative lawmaking in America---the spread of the Field Code through extra-legislative commissions.
+These accounts have focused on administrative adjudication or discretionary regulation within a narrow domain, such as customs houses.[^73] These histories have so far neglected the most widespread and significant instance of nineteenth-century administrative lawmaking in America---the spread of the Field Code through extra-legislative commissions.
 While these histories have sought to demonstrate that Americans from early on could be quite comfortable with administrative law and accepted it as a normal part of the constitutional order, this chapter has shown how lawmaking by commission generated significant political controversy and raised grave questions about popular sovereignty under such delegations, questions that over time were merely dodged rather than answered.
@@
 
-[^35]: **Code citations and literature on West as a legal void**.In practice, there are also variations in the texts due to numbering or minor OCR errors as well as actual changes. These differences
+[^35]: {TODO: cite literature on West as legal void.}
 
-[^36]: This algorithm works by extracting a set number of random tokens from each document, allowing the documents to be represented uniformly and compactly.
-Then those random tokens are grouped into subsets.
-If any two documents have a matching subset, then they are considered a candidate pair.
-**TODO: CLARIFY** This algorithm has several useful properties.
-It approximates the Jaccard similarity of the two documents.
-It requires a computation for each document rather than each pair of documents, so the computation time grows linearly not geometrically.
-And by controlling various parameters, one can set a threshold similarity score above which one is likely to find a genuine match and unlikely to find a spurious match.
+[^36]: The formal definition of the Jaccard similarity for two sets, $A$ and $B$, is $$J(A, B) = \frac{ | A \cap B | }{ | A \cup B | }$$
 
-[^37]: This matrix required filtering based on what we knew about the process of borrowing.
+[^37]: We implemented LSH as described in Jure Leskovec, Anand Rajaraman, and Jeff Ullman, *Mining of Massive Datasets*, 2nd ed.
+(Cambridge University Press, 2014), ch.
+3, <http://www.mmds.org>; the algorithm was first described in Andrei Z.
+Broder, "On the Resemblance and Containment of Documents," in *Compression and Complexity of Sequences 1997: Proceedings*, (IEEE, 1997): 21--29, <http://gatekeeper.dec.com/ftp/pub/dec/SRC/publications/broder/positano-final-wpnums.pdf>.
+Other digital humanities projects, most notably *Viral Texts*, have used other means for detecting text reuse.
+The most prominent of these are algorithms for sequence alignment.
+(Our "textreuse" package for R also implements the Smith-Waterman local sequencing algorithm, derived from gene sequencing.) Yet the older and simpler LSH algorithm sufficed for our purposes because legal sources are easily divided into discrete sections which can be treated as independent documents.
+For other approaches, see David Bamman and Gregory Crane, "Discovering Multilingual Text Reuse in Literary Texts," white Paper, Perseus Digital Library (2009): <http://www.perseus.tufts.edu/publications/2009-Bamman.pdf>; Timothy Allen, Charles Cooney, Stéphane Douard, et al., "Plundering Philosophers: Identifying Sources of the Encyclopédie," *Journal of the Association for History and Computing* 13, no.
+1 (2010): <http://hdl.handle.net/2027/spo.3310410.0013.107>; Glenn Roe, Russell Horton, and Mark Olsen, "Something Borrowed: Sequence Alignment and the Identification of Similar Passages in Large Text Collections," *Digital Studies / Le Champ numérique* 2, no.
+1 (2010): <http://www.digitalstudies.org/ojs/index.php/digital_studies/article/view/190/235>; David A.
+Smith, Ryan Cordell, and Elizabeth Maddock Dillon, "Infectious Texts: Modeling Text Reuse in Nineteenth-Century Newspapers," in *2013 IEEE International Conference on Big Data*, 2013, 86--94, doi:10.1109/BigData.2013.6691675; David A.
+Smith, Ryan Cordell, Elizabeth Maddock Dillon, et al., "Detecting and Modeling Local Text Reuse," *Proceedings of IEEE/ACM Joint Conference on Digital Libraries* (IEEE Computer Society Press, 2014); Christopher Forstall, Neil Coffee, Thomas Buck, Katherine Roache, and Sarah Jacobson, "Modeling the scholars: Detecting Intertextuality through Enhanced Word-level N-gram Matching" *Digital Scholarship in the Humanities* 30, no.
+4 (2015): 503--515; Douglas Ernest Duhaime, "Textual Reuse in the Eighteenth Century: Mining Eliza Haywood's Quotations," *Digital Humanities Quarterly* 10, no.
+1 (2016): <http://www.digitalhumanities.org/dhq/vol/10/1/000229/000229.html>.
+
+[^38]: We filtered this matrix based on what we knew about the process of borrowing.
 We removed any match below a threshold that we determined by reading pairs of matches.
-We had to remove anachronistic matches; for instance, a code from 1851 obviously did not borrow from a code from 1877.
-Furthermore, in chains of borrowing (e.g., NY1850 → CA1851 → CA1868 → CA1872 → MT1895) the latest section might have a high similarity to all of its parents, but it was in fact borrowed only from the most recent parent.
+Because Jaccard similarity scores are symmetric, we also removed anachronistic matches.
+For instance, a code from 1851 obviously did not borrow from a code from 1877.
+Furthermore, in chains of borrowing (e.g., NY1850 → CA1851 → CA1868 → CA1872 → MT1895) the latest section might have a high similarity to all of its ancestors, but it was in fact borrowed only from the most recent parent.
 We therefore filtered the similarity matrix to remove matches within the same code; anachronistic matches; spurious matches beneath a certain threshold.
-Then if a section had multiple matches, we kept the match from the chronologically closest code, giving preference to codes from the same state, unless there was a substantially higher match from a different code.
+Then if a section had multiple matches, we kept the match from the chronologically closest code, giving preference to codes from the same state, unless there was a substantially closer match from a different code.
 
-[^38]: This is obvious from the visualization, but also confirmed by all measures of centrality used in network analysis.
+[^39]: We have released two repositories with all the code used for this project.
+Lincoln Mullen, "textreuse: Detect Text Reuse and Document Similarity," R package version 0.1.3 (2015--): <https://github.com/ropensci/textreuse>, includes the LSH and other algorithms that we used for general purpose application.
+(This package was peer-reviewed by rOpenSci, a collective of academic developers who use the R programming language.) A second repository contains all of our code specific to the migration of the Field Code: <https://github.com/lmullen/civil-procedure-codes/>.
+
+[^40]: This is obvious from the visualization, but also confirmed by all measures of centrality used in network analysis.
 A network is simply a list of edges (in our case the number of sections borrowed) between nodes (in our case, the codes).
@@
 
-[^39]: Non-Field jurisdictions occasionally exhibited a borrowing relationship within a state or across two states.
+[^41]: Non-Field jurisdictions occasionally exhibited a borrowing relationship within a state or across two states.
 In in a few unusual instances they contributed to codes which were derived from the Field Code.
@@
 
-[^40]: spectrogram("CA1851", mutate(best\_matches, match\_code = ifelse(match\_code %in% c("NY1848", "NY1849", "NY1850"), "New York 1849/50", match\_code)), white\_list = 3)
+[^42]: spectrogram("CA1851", mutate(best\_matches, match\_code = ifelse(match\_code %in% c("NY1848", "NY1849", "NY1850"), "New York 1849/50", match\_code)), white\_list = 3)
 
-[^41]: (The visualization here, because of difficulties in precisely matching sections, actually understates the extent of the borrowing.) **Explain** why our method errs on the side of undercounting.
+[^43]: (The visualization here, because of difficulties in precisely matching sections, actually understates the extent of the borrowing.) **Explain** why our method errs on the side of undercounting.
 
-[^42]: Scholars in digital literary studies often speak of the "deformance" of texts.
+[^44]: Scholars in digital literary studies often speak of the "deformance" of texts.
 Clustering the sections of the codes deformed them by pulling the sections out of their context within specific codes and by arranging them by topic in chronological order.
@@
 
-[^43]: Brendan J. Frey and Delbert Dueck, "Clustering by Passing Messages Between Data Points," *Science* 315 (2007): 972--976.
+[^45]: Brendan J. Frey and Delbert Dueck, "Clustering by Passing Messages Between Data Points," *Science* 315 (2007): 972--976.
 
-[^44]: Furthermore, even though the affinity propagation clus- tering algorithm did not fully converge with our peculiar dataset, it did an adequate job clustering the documents.
+[^46]: Furthermore, even though the affinity propagation clus- tering algorithm did not fully converge with our peculiar dataset, it did an adequate job clustering the documents.
 Because there was an exemplar section for each cluster, we were able to merge clusters whose exemplars had a high Jaccard similarity score.
 
-[^45]: We also implemented a method called the Smith Waterman algorithm, which is used for gene sequencing, but which we adapted for natural language.
+[^47]: We also implemented a method called the Smith Waterman algorithm, which is used for gene sequencing, but which we adapted for natural language.
 This is the method used by Smith et al for Viral Texts.
@@
 
-[^46]: E.g., Moretti, Distant Reading; Jockers, Macroanalysis.
+[^48]: E.g., Moretti, Distant Reading; Jockers, Macroanalysis.
 
-[^47]: Samuels, Lisa, and Jerome McGann. "Deformance and Interpretation." *New Literary History* 30.1 (1999) : 25--56; *Stallybrass, Peter. "Against Thinking."* PMLA *122.5 (2007): 1580-1587.*
+[^49]: Samuels, Lisa, and Jerome McGann. "Deformance and Interpretation." *New Literary History* 30.1 (1999) : 25--56; *Stallybrass, Peter. "Against Thinking."* PMLA *122.5 (2007): 1580-1587.*
 
-[^48]:
+[^50]:
 
-[^49]: Those jurisdictions were Nevada (1861), Dakota Territory---which retained the Code when split into North and South (1862), Idaho (1864), Arizona (1864), Montana (1865), Arkansas (1868), North Carolina (1868), Wyoming (1869), Florida (1870), South Carolina (1870), Utah (1870), and Colorado (1877).
+[^51]: Those jurisdictions were Nevada (1861), Dakota Territory---which retained the Code when split into North and South (1862), Idaho (1864), Arizona (1864), Montana (1865), Arkansas (1868), North Carolina (1868), Wyoming (1869), Florida (1870), South Carolina (1870), Utah (1870), and Colorado (1877).
 
-[^50]: Elliott West, "Reconstructing Race," 34 *Western Historical Quarterly* 6 (2003).
+[^52]: Elliott West, "Reconstructing Race," 34 *Western Historical Quarterly* 6 (2003).
 See also Heather Cox Richardson, *West from Appomattox: The Reconstruction of America after the Civil War* (New Haven: Yale University Press, 2007); Sven Beckert, *Monied Metropolis: New York City and the Consolidation of the American Bourgeoisie, 1850-1896* (Harvard 2003); Mark Wahlgren Summers, *The Ordeal of the Reunion: A New History of Reconstruction* (Chapel Hill: University of North Carolina Press, 2014).
@@
 
-[^51]: See, for instance, Rogers Smith, *Civic Ideals: Conflicting Visions of Citizenship in U.S.
+[^53]: See, for instance, Rogers Smith, *Civic Ideals: Conflicting Visions of Citizenship in U.S.
 History* (Yale 1999); Meg Jacobs, William J.
@@
 
-[^52]: Naomi Lamoreaux and John Joseph Wallis, "States, Not Nation: The Sources of Political and Economic Development in the Early United States," Paper Presented at the Economic History Workshop, Harvard University, March 4, 2016.
+[^54]: Naomi Lamoreaux and John Joseph Wallis, "States, Not Nation: The Sources of Political and Economic Development in the Early United States," Paper Presented at the Economic History Workshop, Harvard University, March 4, 2016.
 
-[^53]: For instance, although Tennessee in 1858 adapted nearly 225 sections of its code from Field codes, the state also incorporated nearly 50 sections of the 1852 Code of Alabama, one of the largest borrowings of southern legislation within the corpus we collected.
+[^55]: For instance, although Tennessee in 1858 adapted nearly 225 sections of its code from Field codes, the state also incorporated nearly 50 sections of the 1852 Code of Alabama, one of the largest borrowings of southern legislation within the corpus we collected.
 
-[^54]: Illinois was a fiercely traditional anti-code state.
+[^56]: Illinois was a fiercely traditional anti-code state.
 In later decades, lawyers jokingly called it "the Yellowstone Park of common law pleading." See Charles E.
@@
 
-[^55]: Journal of the Assembly of the Territory of Utah (1870), 15.
+[^57]: Journal of the Assembly of the Territory of Utah (1870), 15.
 
-[^56]: "The Code Again," *Pueblo Daily Chieftain*, February 25, 1877.
+[^58]: "The Code Again," *Pueblo Daily Chieftain*, February 25, 1877.
 
-[^57]: "The Legislature: The Senate Devotes Another Day to the Code," *Denver Daily Tribune*, February 17, 1877.
+[^59]: "The Legislature: The Senate Devotes Another Day to the Code," *Denver Daily Tribune*, February 17, 1877.
 
-[^58]: Governor's Message, in Journal of the House of Assembly of the Territory of Nebraska (1857), 12.
+[^60]: Governor's Message, in Journal of the House of Assembly of the Territory of Nebraska (1857), 12.
 
-[^59]: William A.
+[^61]: William A.
 Jenkins to William Blount Rodman, January 14, 1868, Rodman Papers.
@@
 
-[^60]: Gordon Morris Bakken, *Practicing Law in Frontier California* (Nebraska 1991), 51-54.
+[^62]: Gordon Morris Bakken, *Practicing Law in Frontier California* (Nebraska 1991), 51-54.
 The new western history ushered in by Patricia Nelson Limerick, *The Legacy of Conquest: The Unbroken Past of the American West* (Norton 1987) and Richard White, *"It's Your Misfortune and None of My Own": A History of the American West* (Oklahoma 1991) is now returning to issues of political economy.
@@
 
-[^61]: "The Code," *Denver Daily Tribune*, January 10, 1877; "The Code," *Denver Daily Times*, January 27, 1877.
+[^63]: "The Code," *Denver Daily Tribune*, January 10, 1877; "The Code," *Denver Daily Times*, January 27, 1877.
 
-[^62]: "A Code of Civil Procedure," *Denver Daily Times*, January 12, 1877.
+[^64]: "A Code of Civil Procedure," *Denver Daily Times*, January 12, 1877.
 
-[^63]: "The Code," *Denver Daily Tribune*, January 31, 1877.
+[^65]: "The Code," *Denver Daily Tribune*, January 31, 1877.
 
-[^64]: See Gunther A.
+[^66]: See Gunther A.
 Weiss, "The Enchantment of Codification in the Common-Law World," 25 *Yale Journal of International Law* 435 (2000).
@@
 
-[^65]: See, for instance, James C.
+[^67]: See, for instance, James C.
 Carter's classic defense of the common law against codification, The Ideal and the Actual in the Law, Address to the American Bar Association, August 21, 1890, at 28 ("the legislature should never attempt to perform the function of the judge, that of simply ascertaining and declaring existing customs.
@@
 
-[^66]: See, for instance, "Note," 29 *Albany Law Journal* 141, 142 (1884); Millar, *Civil Procedure of the Trial Court*, 55-56.
+[^68]: See, for instance, "Note," 29 *Albany Law Journal* 141, 142 (1884); Millar, *Civil Procedure of the Trial Court*, 55-56.
 
-[^67]: 19 *Hansard Parliamentary Debates* 531.
+[^69]: 19 *Hansard Parliamentary Debates* 531.
 
-[^68]: Texas commissioned the preparation of a code of civil procedure in 1855, and the legislature scheduled an extra session to consider it but ultimately never passed the law.
+[^70]: Texas commissioned the preparation of a code of civil procedure in 1855, and the legislature scheduled an extra session to consider it but ultimately never passed the law.
 21 *Texas Reports* (Hartley) xi (1882); *Texas State Times*, December 15, 1855.
@@
 
-[^69]: "The Code," *Weekly Standard* (Raleigh), May 26, 1869.
+[^71]: "The Code," *Weekly Standard* (Raleigh), May 26, 1869.
 
-[^70]: See, for instance, the summary of the states-as-laboratories literature in Brian Galle & Joseph Leahy, "Laboratories of Democracy?
+[^72]: See, for instance, the summary of the states-as-laboratories literature in Brian Galle & Joseph Leahy, "Laboratories of Democracy?
 Policy Innovation in Decentralized Governments," 58 *Emory Law Journal* 1333 (2009).
 
-[^71]: See Daniel Ernst, *Tocqueville's Nightmare: The Administrative State Emerges in America, 1900-1940* (Oxford: Oxford University Press, 2014); Jerry L.
+[^73]: See Daniel Ernst, *Tocqueville's Nightmare: The Administrative State Emerges in America, 1900-1940* (Oxford: Oxford University Press, 2014); Jerry L.
 Mashaw, *Creating the Administrative Constitution: The Lost One Hundred Years of American Administrative Law* (Yale Law Library 2012); Gautham Rao, *National Duties: Custom Houses and the Making of the American State* (University of Chicago 2016).

### 2016-06-26 article/article.Rmd
Page numbers for citations

@@
 [^31]: We have preferred to use the term "digital history" when referring to our own work, in part because the term "digital humanities" has largely come to refer to the work of digital literary and digital media scholars, but primarily because we wish to see digital scholars make disciplinary, rather than interdisciplinary contributions.
-On the role of disciplines and the importance of field specific argumentation, see, Stephen Robertson, "The Differences between Digital Humanities and Digital History," {PAGE}--{PAGE}, and Cameron Blevins, "Digital History's Perpetual Future Tense," {PAGE}--{PAGE}, both in *Debates in the Digital Humanities 2016*, ed.
+On the role of disciplines and the importance of field specific argumentation, see, Stephen Robertson, "The Differences between Digital Humanities and Digital History," 289--307, and Cameron Blevins, "Digital History's Perpetual Future Tense," 308--324, both in *Debates in the Digital Humanities 2016*, ed.
 Matthew K.

### 2016-06-26 article/article.Rmd
Give part 3 a title
Footnotes from Kellen

--- 2016-06-25 article/article.Rmd
@@
 
-# 1. The origin and migration of the Field Code
+## 1. The origin and migration of the Field Code
 
@@
 
-# 2. Detecting borrowings among procedure codes
+## 2. Detecting borrowings among procedure codes
 
@@
 Because most codes were public statutes, they were widely printed and distributed and therefore found their way into libraries digitized by Google Books.
-We drew primarily from the Google Books, filling in gaps from other databases as necessary.[^32] We used optical character recognition software (OCR) to create plain-text versions of the codes, which we edited lightly, correcting section markers by hand as necessary and writing a script to fix the most obvious OCR errors.[^33]
+We drew primarily from the Google Books, filling in gaps from other databases as necessary.
+We used optical character recognition software (OCR) to create plain-text versions of the codes, which we edited lightly, correcting section markers by hand as necessary and writing a script to fix the most obvious OCR errors.[^32]
 
@@
 For instance, we know that California's 1851 code was derived from New York's 1850 code.
-(Stephen Johnson Field, David Dudley Field's brother, was the lawyer who imported New York's code into California.[^34]) But the New York code is over 150,000 words long, whereas California's code was just over 50,000 words long.
+(Stephen Johnson Field, David Dudley Field's brother, was the lawyer who imported New York's code into California.[^33]) But the New York code is over 150,000 words long, whereas California's code was just over 50,000 words long.
 Those disparate lengths mean that comparing all of the California code to all of the New York code is a less meaningful comparison that than comparing each section in the California code to each section in the New York code, where matching sections will have a similar length.
@@
 These tokens each contain more meaning than a single word, yet because they are shingled they are robust to changes in the text or noisy OCR.
-A Jaccard similarity score will always be in a range between 0 (complete dissimilarity) and 1 (complete similarity).^[The formal definition of the Jaccard similarity for two sets, $A$ and $B$, is $$J(A, B) = \frac{ | A \cap B | }{ | A \cup B | }$$]
+A Jaccard similarity score will always be in a range between 0 (complete dissimilarity) and 1 (complete similarity).[^34]
 
@@
 This would take an unreasonable amount of computation time, and most of these comparisons would be unnecessary, since each section has no relationship to most other sections.
+We therefore implemented the minhash/locality sensitive hashing (LSH) algorithm to detect pairs of possible matches quickly.This algorithm works by extracting a set number of random tokens from each document to create a document signature; this subset makes it possible to approximate the Jaccard similarity of two documents.
+These signatures can then be used to identify each of the billions of possible pairs of sections as likely to be matches or not.
+By setting parameters to the algorithm, one can control how sensitive the algorithm is in drawing the line between genuine and spurious matches.
+We then measured the actual Jaccard score for only those candidate pairs.[^35]
 
-We therefore implemented the minhash/locality sensitive hashing (LSH) algorithm to detect pairs of possible matches. This algorithm
+The result was a matrix of similarity scores, with over 45,000 genuine matches.
+For each section in the corpus, after making some adjustments to remove anachronisms and spurious matches, we were able to identify the section from which it was most likely borrowed.[^36] In other words, we had traced the work of the commissioners' scissors and paste-pots through the course of their codes.[^37]
 
-that is, documents which were likely to be matches, and then we measured the Jaccard score for only those candidate pairs.[^36]
-
-The result was a matrix of matches, with over 45,000 genuine matches.
-For each section in the corpus, after making some adjustments to remove anachronisms and spurious matches,[^37] we were able to identify the section from which it was most likely borrowed.
-In other words, we had traced the work of the commissioners' scissors and paste-pots through the course of their codes.
-
-# Part 3
+## 3. Patterns of borrowing among Field Code jurisdictions
 
@@
 
-# Part 4
+## Part 4
 
@@
 
-# Conclusion
+## Conclusion
 
@@
 
-[^32]: {TODO: list exceptions to Google Books}.
-
-[^33]: In each instance we downloaded an entire volume of sessions laws, statutory compilations, or single-volume codes of procedure and then cropped out irrelevant pages, marginalia and footnoted commentary, leaving only the statutory text.
+[^32]: In each instance we downloaded an entire volume of sessions laws, statutory compilations, or single-volume codes of procedure and then cropped out irrelevant pages, marginalia and footnoted commentary, leaving only the statutory text.
 After several trials of various implementations of Tesseract (open source) and I.R.I.S.
@@
 
-[^34]: {TODO: citation on Stephen Johnson Field}
+[^33]: William Wirt Blume, "Adoption in California of the Field Code of Civil Procedure: A Chapter in American Legal History," 17 *Hastings Law Journal* 701 (1966); Stephen J.
+Field, *Personal Reminiscences of Early Days in California* (1893), 75-78.
 
-[^35]: **Code citations and literature on West as a legal void**.In practice, there are also variations in the texts due to numbering or minor OCR errors as well as actual changes. These differences
+[^34]: The formal definition of the Jaccard similarity for two sets, $A$ and $B$, is $$J(A, B) = \frac{ | A \cap B | }{ | A \cup B | }$$
 
-[^36]: This algorithm works by extracting a set number of random tokens from each document, allowing the documents to be represented uniformly and compactly.
-Then those random tokens are grouped into subsets.
-If any two documents have a matching subset, then they are considered a candidate pair.
-**TODO: CLARIFY** This algorithm has several useful properties.
-It approximates the Jaccard similarity of the two documents.
-It requires a computation for each document rather than each pair of documents, so the computation time grows linearly not geometrically.
-And by controlling various parameters, one can set a threshold similarity score above which one is likely to find a genuine match and unlikely to find a spurious match.
+[^35]: We implemented LSH as described in Jure Leskovec, Anand Rajaraman, and Jeff Ullman, *Mining of Massive Datasets*, 2nd ed.
+(Cambridge University Press, 2014), ch.
+3, <http://www.mmds.org>; the algorithm was first described in Andrei Z.
+Broder, "On the Resemblance and Containment of Documents," in *Compression and Complexity of Sequences 1997: Proceedings*, (IEEE, 1997): 21--29, <http://gatekeeper.dec.com/ftp/pub/dec/SRC/publications/broder/positano-final-wpnums.pdf>.
+Other digital humanities projects, most notably *Viral Texts*, have used other means for detecting text reuse.
+The most prominent of these are algorithms for sequence alignment.
+(Our "textreuse" package for R also implements the Smith-Waterman local sequencing algorithm, derived from gene sequencing.) Yet the older and simpler LSH algorithm sufficed for our purposes because legal sources are easily divided into discrete sections which can be treated as independent documents.
+For other approaches, see David Bamman and Gregory Crane, "Discovering Multilingual Text Reuse in Literary Texts," white Paper, Perseus Digital Library (2009): <http://www.perseus.tufts.edu/publications/2009-Bamman.pdf>; Timothy Allen, Charles Cooney, Stéphane Douard, et al., "Plundering Philosophers: Identifying Sources of the Encyclopédie," *Journal of the Association for History and Computing* 13, no.
+1 (2010): <http://hdl.handle.net/2027/spo.3310410.0013.107>; Glenn Roe, Russell Horton, and Mark Olsen, "Something Borrowed: Sequence Alignment and the Identification of Similar Passages in Large Text Collections," *Digital Studies / Le Champ numérique* 2, no.
+1 (2010): <http://www.digitalstudies.org/ojs/index.php/digital_studies/article/view/190/235>; David A.
+Smith, Ryan Cordell, and Elizabeth Maddock Dillon, "Infectious Texts: Modeling Text Reuse in Nineteenth-Century Newspapers," in *2013 IEEE International Conference on Big Data*, 2013, 86--94, doi:10.1109/BigData.2013.6691675; David A.
+Smith, Ryan Cordell, Elizabeth Maddock Dillon, et al., "Detecting and Modeling Local Text Reuse," *Proceedings of IEEE/ACM Joint Conference on Digital Libraries* (IEEE Computer Society Press, 2014); Christopher Forstall, Neil Coffee, Thomas Buck, Katherine Roache, and Sarah Jacobson, "Modeling the scholars: Detecting Intertextuality through Enhanced Word-level N-gram Matching" *Digital Scholarship in the Humanities* 30, no.
+4 (2015): 503--515; Douglas Ernest Duhaime, "Textual Reuse in the Eighteenth Century: Mining Eliza Haywood's Quotations," *Digital Humanities Quarterly* 10, no.
+1 (2016): <http://www.digitalhumanities.org/dhq/vol/10/1/000229/000229.html>.
 
-[^37]: This matrix required filtering based on what we knew about the process of borrowing.
+[^36]: We filtered this matrix based on what we knew about the process of borrowing.
 We removed any match below a threshold that we determined by reading pairs of matches.
-We had to remove anachronistic matches; for instance, a code from 1851 obviously did not borrow from a code from 1877.
-Furthermore, in chains of borrowing (e.g., NY1850 → CA1851 → CA1868 → CA1872 → MT1895) the latest section might have a high similarity to all of its parents, but it was in fact borrowed only from the most recent parent.
+Because Jaccard similarity scores are symmetric, we also removed anachronistic matches.
+For instance, a code from 1851 obviously did not borrow from a code from 1877.
+Furthermore, in chains of borrowing (e.g., NY1850 → CA1851 → CA1868 → CA1872 → MT1895) the latest section might have a high similarity to all of its ancestors, but it was in fact borrowed only from the most recent parent.
 We therefore filtered the similarity matrix to remove matches within the same code; anachronistic matches; spurious matches beneath a certain threshold.
-Then if a section had multiple matches, we kept the match from the chronologically closest code, giving preference to codes from the same state, unless there was a substantially higher match from a different code.
+Then if a section had multiple matches, we kept the match from the chronologically closest code, giving preference to codes from the same state, unless there was a substantially closer match from a different code.
+
+[^37]: We have released two repositories with all the code used for this project.
+Lincoln Mullen, "textreuse: Detect Text Reuse and Document Similarity," R package version 0.1.3 (2015--): <https://github.com/ropensci/textreuse>, includes the LSH and other algorithms that we used for general purpose application.
+(This package was peer-reviewed by rOpenSci, a collective of academic developers who use the R programming language.) A second repository contains all of our code specific to the migration of the Field Code: <https://github.com/lmullen/civil-procedure-codes/>.
 

### 2016-06-27 article/article.Rmd
Network graph and caption for the table

@@
 ---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+library(igraph)
+library(ggplot2)
+library(ggraph)
+load("../cache/network-graphs.rda")
+source("../R/helper.R")
+set.seed(82893)
+```
 
@@
 
-Comparing the section pairs above produces the following matrix of scores.
+Comparing the section pairs above produces the matrix of similarity scores in table 1.
 
@@
   CA1851-002
+
+  Table: A subset of the section to section similarity matrix.
 
@@
 
-Having developed a method for finding legislative borrowings, we next sought to visualize the broader patterns revealed by the those borrowings.
+Having developed a method for finding legislative borrowings, we next sought to visualize the broader patterns revealed by those borrowings.
 We did this first by aggregating the section to section borrowings into code to code borrowings.
 By counting how many sections each code borrowed from each other code, we were able to show the connections from one code to another.
+
+```{r code-to-code-network, fig.width=12, fig.height=12, fig.cap = "The structure of borrowings among nineteenth-century codes of civil procedure.
+Note that several versions of New York's Field Code were at the center of the network, while other states such as California and Ohio became centers of regional variations on the Field Code."}
+ggraph(codes_g, "igraph", algorithm = "nicely") +
+  geom_edge_fan(aes(edge_width = sections_borrowed, 
+                    alpha = sections_borrowed),
+                arrow = arrow(type = "closed", ends = "first",
+                              length = unit(0.20, "inches"),
+                              angle = 15)) +
+  geom_node_point(aes(colour = as.factor(distance)), size = 10) +
+  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") + 
+  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +
+  scale_color_discrete("Distance from a NY code") +
+  ggforce::theme_no_axes() +
+  geom_node_text(aes(label = name), size = 6) +
+  # labs(title = "Borrowings among nineteenth-century codes of civil procedure") +
+  theme(legend.position = "bottom",
+        panel.border = element_blank())
+```
 

### 2016-06-27 article/article.Rmd
Add table of racial exclusions

@@
 
+## Appendix: Clustering sections involving racial exclusions from witness testimony
+
+Disqualifying the testimony of racialized parties and witnesses was not new to the procedure codes.
+The following laws from midwestern states with large free black populations would be echoed in adaptations of the Field Code.
+
+Code       |  Section
+-----------|-------------------------------------------------
+OH 1807    | That no black or mulatto person or persons, shall hereafter be permitted to be sworn or give evidence in any court of record, or elsewhere in this state, in any cause depending, or matter of controversy, where either party to the same is a white person, or in any prosecution, which shall be instituted in behalf of this state, against any white person.
+           |
+IA 1839    | A negro, mulatto, or Indian, shall not be a witness in any court or in any case against a white person.
+           |
+IN 1843    | No negro, mulatto or Indian, shall be a witness, except in pleas of the state against negroes, mulattoes, or Indians, and in civil causes where negroes, mulattoes, or Indians alone are parties: every person other than a negro having one-fourth part of negro blood or more, or any one of whose grandfathers or grandmothers shall have been a negro, shall be deemed an incompetent witness, within the provisions of this article.
+
+Racial qualifications were introduced to the Field Code tradition in California, first in Elisha Crosby’s draft of 1850, then in Stephen J.
+Field’s draft of 1851.
+Many western states copied Stephen Field’s provision.
+
+Code       |  Section
+-----------|--------------------------------------------------
+CA 1850    | 306.
+No black, or mulatto person, or Indian, shall be permitted to give evidence in any action to which a white person is a party, in any Court of this State.
+Every person who shall have one eighth part or more of negro blood, shall be deemed a mulatto; and every person who shall have one half Indian blood, shall be deemed an Indian.
+           |
+CA 1851    | 394.
+The following persons shall not be witnesses: lst.
+Those who are of unsound mind at the time of their production for examination; 2d.
+Children under ten years of age, who appear incapable of receiving just impressions of the facts respecting which they are examined, or of relating them truly: and; 3d.
+Indians, or persons having one fourth or more of Indian blood, in an action or proceeding to which a white person is a party: 4th.
+Negroes, or persons having one half or more Negro blood, in an action or proceeding to which a white person is a party.
+           |
+CA 1868    | 394.
+The following persons shall not he witnesses: First.
+Those who are of unsound mind at the time of their production for examination.
+Second.
+Children under ten years of age, who, in the opinion of the court, appear incapable of receiving just impressions of the facts respecting which they are examined, or of relating them truly.
+Third.
+Mongolians, Chinese, or Indians, or persons having one-half or more of Indian blood, in an action or proceeding wherein a white person is a party.
+Fourth.
+Persons against whom judgment has been rendered upon a conviction for a felony, unless pardoned by the governor, or such judgment has been reversed on appeal.
+           | 
+OR 1854    | 6.
+The following persons shall not be competent to testify: 1.
+Those who are of unsound mind, or intoxicated at the time of their production for examination; 2.
+Children under ten years of age, who appear incapable of receiving just impressions of the facts respecting which they are examined, or of relating them truly; 3.
+Negroes, mulattoes and Indians, or persons one half or more of Indian blood, in an action or proceeding to which a white person is a party.
+           |
+WA 1855    | 293.
+The following persons shall not be competent to testify: 1st.
+Those who are of unsound mind, or intoxicated at the time of their production for examination.
+2d.
+Children under ten years of age, who appear incapable of receiving just impressions of the facts, respecting which they are examined, or of relating -them truly.
+3d.
+Indians, or persons having more than one half Indian blood, in an action or proceeding to which a white person is a party.
+           |
+UT 1859    | 215.
+The following persons shall not be competent to testify: 1.
+Those who are of unsound mind or intoxicated at the time of their production for examination.
+2.
+Children under ten years of age, who appear to be incapable of receiving just impressions of the facts respecting which they are examined or of relating them truly.
+Negroes, mulattos, and Indians, or persons having one fourth of negro or Indian blood, in an action or proceeding to which a white person is a party, but shall not be disqualified from testifying against another.
+           |
+NV 1861    | 342.
+The following persons shall not be witnesses: First.
+Those who are of unsound mind at the time of their production for examination.
+Second.
+Children under ten years of age, who, in the opinion of the court, appear incapable of receiving just impressions of the facts respecting which they are examined, or of relating them truly.
+Third.
+Indians, or persons having one half or more of Indian blood, and negroes, or persons having one half or more of negro blood, in an action or proceeding to which a white person is a party.
+Fourth.
+Persons against whom judgment as been rendered upon a conviction for a felony, unless pardoned by the governor, or such judgment has been reversed on appeal.
+           |
+ID 1864    | 352.
+The following persons shall not be witnesses: First.
+Those who are of unsound mind at the time of their production for examination.
+Second.
+Children under ten years of age, who, in the opinion of the court, appear incapable of receiving just impressions of the facts respecting which they are examined, or of relating them truly.
+Third.
+Chinamen or persons having one-half or more of China blood; Indians, or persons having one-half or more of Indian blood, and negroes, or persons having one-half or more of negro blood, in an action or proceeding to which a white person is a party.
+Fourth.
+Persons against whom judgment has been rendered upon a conviction or felony, unless pardoned by the governor, or such judgment has been reversed on appeal.
+           |
+AZ 1865    | 396.
+The following persons shall not be witnesses: 1.
+Those who are of unsound mind at the time of their production for examination.
+2.
+Children under ten years of age, who appear incapable of receiving just impressions of the facts respecting which they are examined, or of relating them truly; and, 3.
+Indiana or persons having one-half or more of Indian blood, in an action or proceeding to which a white person is a party.
+4.
+Negroes, or persons having one-half or more negro blood, in an action or, proceeding to which a white person is a party.
+
+Kentucky differed from other code states by making no distinction between incompetency (an absolute bar) and privilege (which might be waived).
+Kentucky also maintained a strict disqualification of parties and interested witnesses while other Field Code states made parties at least partially competent to stand examination.
+
+Code       | Section
+-----------|----------------------------------------
+KY 1851    | 568.
+The following persons shall be incompetent to testify: 1.
+Persons convicted of a capital offense, or of perjury, subornation of perjury; burglary, robbery, larceny, receiving stolen goods, forgery, or counterfeiting.
+2.
+Infants under the age of ten years, and over that age, if incapable of understanding the obligation of an oath.
+3.
+Persons who are of unsound mind at the time of being produced as witnesses.
+4.
+Husband and wife, for or against each other, or concerning any communication made by one to the other, during the marriage, whether called as a witness while that relation subsisted or afterwards.
+5.
+An attorney, concerning any communication made to him by his client in that relation, or his advice thereon, without the client’s consent.
+6.
+Persons interested in an issue, in behalf of themselves, and parties to an issue, in behalf of themselves or those united with them in the issue.
+7.
+Negroes, mulattoes, or Indians, in any action or proceeding where a white person, in his own right, or as representative of a white person, is a party, except in actions brought to recover a penalty or forfeiture for a violation of law, against a negro, mulatto, or Indian.
+           |
+MT 1865    | 320.
+The following persons shall be incompetent to testify: First, Persons who are of an unsound mind at the time of their production for examination.
+Second, Children under ten years of age who appear incapable of receiving just impressions of the facts respecting which they are examined or of relating them truly, but the court in its discretion may allow such children to testify, and the facts herein enumerated shall go to their credibility.
+Third, Husband or wife for or against each other, or concerning any communication made by one to the other during the marriage, whether called as a witness while that relation existed or afterwards.
+Fourth, An attorney concerning any communication made to him by his client in that relation, or his advice thereon, without the client’s consent.
+Fifth, A clergyman or priest concerning any confession made to him, in his professional character, in the course of discipline enjoined by the church to which he belongs, without the consent of the person making the confession.
+Sixth, A negro, Indian, or Chinaman, where the parties to the action are white persons, but if the parties to an action or either of the parties is an Indian, negro, or Chinaman, a negro may be introduced as a witness against such negro, an Indian against such Indian, or a Chinaman against such Chinaman.
+A negro within the meaning of this act is a person having one-eighth or more of negro blood, an Indian is a person having one-half or more of Indian blood, and a Chinaman is a person having one-half or more Chinese blood.
+
+Iowa's Code began by defining competency purely in terms of understanding the legal oath, and in the same section it barred racialized testimony (even if racialized actors could understand the oath).
+Wyoming followed the same tack, but softened the racial bar by adopting the same standard used for children: only those adjudged incapable of perceiving and relating facts were barred from testifying.
+
+Code       | Section
+-----------|----------------------------------------
+IA 1851    | 2388.
+Every human being of sufficient capacity to understand the obligation of an oath is a competent witness in all cases both civil and criminal except as herein otherwise declared.
+But an indian, a negro, a mulatto or black person shall not be allowed to give testimony in any cause wherein a white person is a party.
+           |
+NE 1855    | 2388.
+Every human being of sufficient capacity to understand the obligation of an oath is a competent witness in all cases both civil and criminal except as herein otherwise declared.
+But an indian, a negro, a mulatto or black person shall not be allowed to give testimony in any cause wherein a white person is a party.
+           |
+WY 1870    | 325.
+Every human being of sufficient capacity to understand the obligations of an oath, is a competent witness in all cases, civil and criminal, except as otherwise herein declared.
+The following persons shall be incompetent to testify: First, Persons of unsound mind at the time of their production.
+Second, Indians and negroes who appear incapable of receiving just impressions of the facts respecting which they are examined, or of relating them intelligently and truly.
+Third Husband and wife, concerning any communication made by one to the other during the marriage, whether called as a witness while that relation exists or afterwards.
+Fourth, An attorney, concerning any communication made to him by his client in that relation or his advice thereon, without the client’s consent in open court or in writing produced in court.
+Fifth, A clergyman or priest, concerning any confession made to him in his professional character in the course of discipline enjoined by the church to which he belongs, without the consent of the person making the confession.
+
+States that did not borrow Field's Evidence Code nevertheless borrowed prohibitions of racialized testimony.
+Two distinct strands emerge in legislation from the Deep South as well as the Upper South and Midwest.
+
+Code       | Section
+-----------|----------------------------------------
+MS 1848    | All negroes, mulattoes, Indians, and all persons of mixed blood, descended from negro or Indian ancestors, to the third generation, inclusive, though one ancestor of each generation may have been a white person, shall be incapable in law, to be witnesses in any case whatsoever, except for and against each other.
+           |
+AL 1852    | 2276.
+Negroes, mulattoes, Indians, and all persons of mixed blood, descended from negro or Indian ancestors, to the third generation inclusive, though one ancestor of each generation may have been a white person, whether bond or e, must not be Witnesses in any cause, civil or criminal, except for or against each other.
+           |
+TN 1858    | 3808.
+A negro, mulatto, Indian, or person of mixed blood, descended from negro or Indian ancestors, to the third generation inclusive, though one ancestor of each generation may have been a white person, whether bond or free, is incapable of being a witness in any cause, civil or criminal, except for or against each other.
+           |
+DC 1857    | A negro shall be a competent witness for or against a negro in any criminal proceeding, and shall be a competent witness in any civil case to which only negroes are parties, but not in any other case.
+           |
+VA 1860    | A negro or indian shall he a competent witness in a case of the commonwealth for or against a negro or indian, or in a civil ease to which only negroes or indians are parties, but not in any other case.
+           |
+IL 1866    | A negro, mulatto or Indian shall not be a witness in any court, or in any case, against a white person. Any person having one-fourth part negro blood shall be adjudged a mulatto.
+
 [^1]: Message of the Governor, in Journal of the Council for the Territory of Nevada (1862), 21.

### 2016-06-27 article/article.Rmd
Add the spectrograms

@@
 knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+library(dplyr)
 library(igraph)
@@
 library(ggraph)
+library(stringr)
+library(scales)
+library(textreuse)
+source("../R/helper.R")
+source("../R/section-matches.R")
+source("../R/spectrogram.R")
+load("../cache/corpus-lsh.rda")
 load("../cache/network-graphs.rda")
-source("../R/helper.R")
 set.seed(82893)
@@
 
-Having developed a method for finding legislative borrowings, we next sought to visualize the broader patterns revealed by those borrowings.
-We did this first by aggregating the section to section borrowings into code to code borrowings.
-By counting how many sections each code borrowed from each other code, we were able to show the connections from one code to another.
+The computational evidence that we assembled revealed patterns in how law migrated at several different scales of analysis.
 
@@
 
-The resulting network graph (**Figure X: Network Graph**) tells the genealogy of civil procedure in the United States.
-The New York codes, especially the finished draft of 1850, are central to the entire network.[^38] Yet it is important to note that New York spurred different traditions within the procedural network.
+At the broadest scale of analysis, we aggregated the section-to-section borrowings into a summary of how many sections each code (or statute) borrowed from each other code.
+We therefore can show the connections from one code to another.
+The resulting network graph reveals the genealogy of civil procedure in the United States.
+
+The New York Field Codes, especially the finished draft of 1850, are central to the entire network.[^38] New York gave rise to different regional traditions within the procedural network.
 Variations in the Field drafts meant that different states could borrow different versions of the Field Code.
@@
 Mississippi and Missouri borrowed from the New York 1849 code.
-These variations point out how the Field Code was always a moving target.
-While Field considered the 1850 New York Code to be the definitive, ideal version of the code, it was really all of the New York codes from 1848 to 1853 that became models for other jurisdictions, likely due to whatever material a given commission had on hand.
-The Field Code was not a single volume on the shelf, but a series of volumes any one of which might be more accessible in different regions and different eras.
+While Field considered the 1850 version to be the definitive, ideal version of the code, all of the New York codes from 1848 to 1853 became models for other jurisdictions.
+In many cases, the commissions likely used whatever version of the code they had at hand.
+The Field Code was not a single volume on the shelf, but a series of volumes, any of which might be more accessible in different regions and in different years.
 
@@
 In 1876 a New York commission produced a new code attempting to consolidate all the statutory amendments subsequent to the 1851 Field Code.
-David Dudley Field was upset by the changes introduced in this revised code, called the Throop Code.
+David Dudley Field was upset by the changes introduced in this revision, called the Throop Code.
 A count by a "friend" of Field's found that only three sentences of the Field Code had carried over word-for-word into the Throop Code.
-Nevertheless, many of the changes were purely formal, and Field speculated that these changes had been made only "so that \[the code\] should not appear to be the same thing as before." With respect to Mr.
-Field or his "friend," we were able to find that the connection was between the Throop Code and the Field Code was somewhat stronger than he thought, and the Throop Code was indeed a descendant, if much revised, from the Field Code.
+Nevertheless, many of the changes were purely formal, and Field speculated that these changes had been made only "so that \[the code\] should not appear to be the same thing as before."[^1] With respect to Mr.
+Field or his "friend," we found that the connection was between the Throop Code and the Field Code was somewhat stronger than he thought, and the Throop Code was indeed a descendant, if much revised, from the Field Code.
 
 Finally, our corpus included a number of statutes which stood outside the Field Code tradition, such as Virginia and West Virginia regulations, statutes from Massachusetts and Maine, and southern codes from Georgia to Louisiana.
-These statutes show that the dominance of the Field Code was not total, and a number of older jurisdictions remained outside of its ambit.[^39] But virtually every jurisdiction established or reconstructed after 1850 became a part of the Field Code network, and no other tradition achieved anywhere near the same coherence across state lines.
+These statutes show that the dominance of the Field Code was not total, and a number of older jurisdictions remained outside of its ambit.[^39] But nearly every jurisdiction established or reconstructed after 1850 became a part of the Field Code network, and no other tradition achieved anywhere near the same coherence across state lines.
 
-We have so far discussed code to code borrowings which give us a macroscopic view of the corpus as a whole.
-But because the fundamental unit of comparison is section to section, it is possible to get a more detailed look at the kinds of borrowings that codes made of one another, by looking at each section in a code and seeing which other code it was borrowed from.
+In addition to the overview of the pattern of borrowings between codes, we can also see the pattern of borrowings within each code.
+We can visualize where each section of a code was borrowed from.
 These visualizations show how each code was put together.
@@
 
-<!-- ![](media/image04.png){width="6.5in" height="3.7916666666666665in"} -->
+```{r ca1850-borrowings, fig.height=3, fig.width=6.5}
+spectrogram("CA1850", best_matches, white_list = c("LA1844", "NY1829", "NY1849",
+                                                   "NY1848"))
+```
+
 California's 1851 code borrowed heavily from two sources.
@@
 
-<!-- ![](media/image05.png){width="6.5in" height="4.291666666666667in"} -->
+```{r CA1851-borrowings, fig.height=3.5, fig.width=6.5}
+spectrogram("CA1851", best_matches, white_list = 3)
+```
+
 The pattern of borrowings in the Washington 1855 code was a rather different case.
@@
 
+```{r WA1855-borrowings, fig.height=4.5, fig.width=6.5}
+spectrogram("WA1855", best_matches, white_list = c("CA1850", "CA1851", "IN1852",
+                                                   "NY1853", "OR1854", "WI1849"))
+```
+
 Finally, we can consider the case of Washington's revised 1873 code as an example of one of the last "leaves" on the family tree of the Field Code.
@@
 
-<!-- ![](media/image03.png){width="6.5in" height="4.666666666666667in"} -->
+```{r WA1873-borrowings, fig.height=4.5, fig.width=6.5}
+spectrogram("WA1873", best_matches)
+```
+
 So far we have retained the context of the surrounding sections within a particular code.
@@
 
-[^38]: This is obvious from the visualization, but also confirmed by all measures of centrality used in network analysis.
+[^38]: That New York codes are central is obvious from the visualization, but we also confirmed this by formal measures of centrality used in network analysis.
 A network is simply a list of edges (in our case the number of sections borrowed) between nodes (in our case, the codes).
 Because even our efforts at determining the best match for each section sometimes attributed a section to an incorrect code, we pruned the edges of the graph so that each code was connected to another code only if it borrowed at least fifty sections or twenty percent of its sections.
-On networks see {CITATION}.
 
-    Within New York there was a definite chronological progression from the 1848, 1849, 1850, 1851, and 1853 versions of the code, but the development is not chronologically linear.
-The state legislature enacted the 1848, 1849, and 1851 codes, and these show stronger relational similarities.
-The 1850 and 1853 were David Dudley Field's ideal drafts of the code which were never enacted.
+    Within New York there was a definite chronological progression from the 1848, 1849, 1850, 1851, and 1853 versions of the code, but the development was not chronologically linear.
+The state legislature enacted the 1848, 1849, and 1851 codes, and these show strong similarities in their relationships.
+The 1850 and 1853 versions were David Dudley Field's ideal drafts of the code which were never enacted.
 They were, however, printed with wide margins, quality typesetting, and---in the 1850 draft---extensive explanatory notes, all with an eye towards other jurisdictions copying them as a model.
@@
 Mashaw, *Creating the Administrative Constitution: The Lost One Hundred Years of American Administrative Law* (Yale Law Library 2012); Gautham Rao, *National Duties: Custom Houses and the Making of the American State* (University of Chicago 2016).
+
+[^72]: David Dudley Field, The Latest Edition of the New York Code of Civil Procedure (1878), 21.

### 2016-06-27 R/spectrogram.R

@@ -87,6 +87,7 @@ spectrogram <- function(code, matches_df, num_cols = 50,
                       OR1862 = "chocolate1",
                       Other  = "lightgray",
                       TX1855 = "mediumorchid",
+                      WA1855 = "chocolate3",
                       WI1849 = "deepskyblue1",
                       WI1856 = "deepskyblue3",
                       WI1858 = "deepskyblue4"

### 2016-06-28 article/article.Rmd
Revise through the end of part 3

@@
 Note that many southern states and western states came to adopt the Field Code during the period of Greater Reconstruction.
-By the end of the nineteenth-century, thirty-one jurisdictions (those displayed on the map, plus Alaska) had adopted a version of the Field Code.](field-code-states-map.jpeg)
+By the end of the nineteenth-century, thirty-one jurisdictions (those displayed on the map, plus Alaska) had adopted a version of the Field Code.
+Data adapted from Charles McGuffey Hepburn, *The Historical Development of Code Pleading in America and England* (1897).](field-code-states-map.jpeg)
 
@@
 The computational evidence that we assembled revealed patterns in how law migrated at several different scales of analysis.
+We used the similarity matrix as the input to three different digital history techniques: network analysis, visualizations, and clustering.
+
+At the broadest scale of analysis, we aggregated the section-to-section borrowings into a summary of how many sections each code (or statute) borrowed from each other code.
+We therefore can show the connections from one code to another.
+The resulting network graph reveals the genealogy of civil procedure in the United States.
 
@@
   geom_node_text(aes(label = name), size = 6) +
-  # labs(title = "Borrowings among nineteenth-century codes of civil procedure") +
+  labs(title = "The migration of law through borrowings in nineteenth-century codes of civil procedure") +
   theme(legend.position = "bottom",
@@
 ```
-
-At the broadest scale of analysis, we aggregated the section-to-section borrowings into a summary of how many sections each code (or statute) borrowed from each other code.
-We therefore can show the connections from one code to another.
-The resulting network graph reveals the genealogy of civil procedure in the United States.
 
@@
 A count by a "friend" of Field's found that only three sentences of the Field Code had carried over word-for-word into the Throop Code.
-Nevertheless, many of the changes were purely formal, and Field speculated that these changes had been made only "so that \[the code\] should not appear to be the same thing as before."[^1] With respect to Mr.
+Nevertheless, many of the changes were purely formal, and Field speculated that these changes had been made only "so that \[the code\] should not appear to be the same thing as before."[^39] With respect to Mr.
 Field or his "friend," we found that the connection was between the Throop Code and the Field Code was somewhat stronger than he thought, and the Throop Code was indeed a descendant, if much revised, from the Field Code.
@@
 Finally, our corpus included a number of statutes which stood outside the Field Code tradition, such as Virginia and West Virginia regulations, statutes from Massachusetts and Maine, and southern codes from Georgia to Louisiana.
-These statutes show that the dominance of the Field Code was not total, and a number of older jurisdictions remained outside of its ambit.[^39] But nearly every jurisdiction established or reconstructed after 1850 became a part of the Field Code network, and no other tradition achieved anywhere near the same coherence across state lines.
+These statutes show that the dominance of the Field Code was not total, and a number of older jurisdictions remained outside of its ambit.[^40] But nearly every jurisdiction established or reconstructed after 1850 became a part of the Field Code network, and no other tradition achieved anywhere near the same coherence across state lines.
 
-In addition to the overview of the pattern of borrowings between codes, we can also see the pattern of borrowings within each code.
-We can visualize where each section of a code was borrowed from.
-These visualizations show how each code was put together.
-Codes at different removes from New York tended to have different patterns of borrowing.
-To illustrate this, we will follow one branch of the Field Code network, beginning with the family started by California's 1851 code.
+In addition to the overview of the relationship between codes, we can also see more detail by visualizing the pattern of borrowings within each code.
+We have visualized where each section of a code was borrowed from to see how each code was put together.
+To illustrate this, we will follow one branch of the Field Code network, beginning with the family started by California's 1850 and 1851 codes.
 
-```{r ca1850-borrowings, fig.height=3, fig.width=6.5}
+California's 1850 code, enacted in the period when California was entering the Union as a state, was borrowed almost entirely from New York's 1849 Field Code.
+The compiler Elisha Crosby did lift one significant section from the mixed civilian-common law code of Louisiana regulating when a judge could order a new trial.
+New trials were not provided for in the New York Code until the finished draft in 1850.
+Most of the sections that were not borrowed, as with many of the codes, have to do with parts that describe the system of courts or provide sample forms peculiar to that state.
+
+```{r ca1850-borrowings, fig.height=3, fig.align="center"}
 spectrogram("CA1850", best_matches, white_list = c("LA1844", "NY1829", "NY1849",
@@
 
-California's 1851 code borrowed heavily from two sources.
-The bulk of the code was taken directly from New York's 1849 or 1850 codes (which are difficult to distinguish exactly from one another.[^40] The remainder of the code was borrowed from California's 1850 code.
-The 1850 version was in turn borrowed from the New York codes **TODO: might as well show this, esp.
-since CA1850 is so impressive**.
-As we would expect, the bulk of the borrowings that come from California instead of directly from New York are at the beginning of the code, where the 1850 code had made amendments specific to the borrowing from California.
-(Many of the non-matching sections are tables of contents.) The main point is that that the majority of the code was lifted more or less directly from New York, with minor amendments specific to California.
+When California revised its procedure code in 1851, for the most part it did not use its own code from the previous year as the basis.
+Rather, the bulk of the 1851 California code came from the updated model code Field completed for New York in 1850.
+This includes the portion of the code on new trials previously borrowed from Louisiana.^[Final Report (New York, 1850), §§804-809, compared to 1851 California Laws 260, §§439-441.] The remainder of the code was borrowed from the 1850 California code.
+The bulk of the borrowings that come from California instead of directly from New York are at the beginning of the code, where the 1850 code had made amendments specific to California.
+(Many of the non-matching sections are tables of contents.) Thus California based the majority of its law of civil procedure entirely on New York's code not one, but twice.
 California made few to no innovations to the Field Code beyond a rearrangement of its provisions.
 
-```{r CA1851-borrowings, fig.height=3.5, fig.width=6.5}
+```{r CA1851-borrowings, fig.height=3.5, fig.align="center"}
 spectrogram("CA1851", best_matches, white_list = 3)
@@
 The pattern of borrowings in the Washington 1855 code was a rather different case.
-The Washington code was definitely in the lineage of the 1851 California code, since it borrowed sections from both California directly and from Oregon, which was derived from California.
-While there are a number of "other" sections, the pattern of borrowing is clear: Indiana's 1852 code and Oregon's 1854 code provide the majority of the borrowings.
+The Washington code was definitely in the lineage of the 1851 California code, since it borrowed sections from both California directly and more often from Oregon, which was also derived from California.
+Indiana's 1852 code and Oregon's 1854 code provide the majority of the borrowings.
 Those two contiguous bands of borrowings correspond to regulations on judgement from Oregon and enforcement provisions from Indiana.
@@
 While working on the Washington code, they must have each used the law (and the law books) that they knew best.
-As a second generation variation on a regional code, the Washington code drew from different sources.
+As a second generation variation on a regional code, the Washington code drew from a variety of sources.
 
-```{r WA1855-borrowings, fig.height=4.5, fig.width=6.5}
+```{r WA1855-borrowings, fig.height=4.5, fig.align="center"}
 spectrogram("WA1855", best_matches, white_list = c("CA1850", "CA1851", "IN1852",
@@
 
-Finally, we can consider the case of Washington's revised 1873 code as an example of one of the last "leaves" on the family tree of the Field Code.
-The bulk of this code was lifted from the Washington 1855 code with only small amendments.
-The main exception was a probate code drawn from California's 1872 code.[^41] Like many of the last generation codes, the text of the procedure code had stabilized in a local manifestation of a regional tradition.
+Finally, we can consider the case of Washington's revised 1873 code as an example of one of the outermost leaves on the family tree of the Field Code.
+The bulk of this code was taken from the Washington 1855 code with only small amendments.
+The main exception was lengthy set of sections on probate drawn from California's 1872 code.
+Like many of the last generation codes, the text of the procedure code had stabilized as a local manifestation of a regional tradition.
 The code was still genuinely a Field Code, with a great deal of similarity to the original New York Field Codes, but its specific form depended on the many edits and rearrangements that state code commissioners had made to the text.
 
-```{r WA1873-borrowings, fig.height=4.5, fig.width=6.5}
+```{r WA1873-borrowings, fig.height=4.5, fig.align="center"}
 spectrogram("WA1873", best_matches)
@@
 So far we have retained the context of the surrounding sections within a particular code.
-But since our fundamental unit of comparison is section to section, we can use a technique called clustering to deform the texts (as a literary scholar might say) in order to see the textual history of how particular regulations embedded in individual sections changed over time.[^42]
-
-We used a clustering algorithm to group related sections together.
-Clustering is the process of taking a set of objects (in this case, sections of the field codes) which have distances between one another (in this case, the Jaccard similarity is easily converted into a distance measure), and grouping items which are are most alike together.
-There are innumerable clustering algorithms, but we needed one that could work with a sparse matrix and one whose assumptions matched the characteristics of our problem.
-We decided to use affinity propagation clustering.[^43] That algorithm assumes that each cluster has an "exemplar" item which the other items are similar to.
-That assumption fits nicely with borrowings from the Field Code, where a single section (likely from the 1850 New York code) had many borrowings, but where there could also be innovative sections in other stages.[^44]
+But since our fundamental unit of comparison is section to section, we can use a technique called clustering to group sections based on their similarity to one another, regardless of which code they come from.
+In this case, clustering groups sections of the law which have a high similarity because of their direct textual relationship and which thus share the same topic.
+There are innumerable clustering algorithms, but we used the affinity propagation clustering algorithm because its assumptions aligned with the characteristics of our problem.
+That algorithm finds an "exemplar" item which is most characteristic of the other items in the cluster.
+That assumption fits nicely with borrowings from the Field Code, where a single section (likely from the 1850 New York code) had many borrowings, but where there could also be innovative sections in other stages that might be more influential.[^43]
 
 The result was a set of approximately 2,900 clusters which contained at least five sections, though this probably overstates the number of innovative, *ur*-sections in the corpus.
-Each cluster contained a list of the section that belonged to it.
 The biggest cluster, for instance, which concerned the use of affidavits in pleading, contained 103 sections.
-With those clusters, we were able to organize the documents chronologically.[^45] This method is particularly useful when tracking the variations in in the law from jurisdiction to jurisdiction.
-It provides historians with a way of noticing small changes in the wording and substance of the law.
-Most discussions of algorithmic reading have focused on "distant reading,"[^46] or have balanced the claims of distant reading by using it as a means to enable close reading.
+Within each cluster, we organized the sections chronologically.
+We were thus able to see the development of the law from jurisdiction to jurisdiction.
+This method provides historians with a way of noticing small changes in the wording and substance of the law.
+Most discussions of algorithmic reading have focused on "distant reading," or have balanced the claims of distant reading by using it as a means to enable close reading.
 This method of clustering, however, is a kind of algorithmic close reading.
@@
 
-Take for instance, provisions regulating witness testimony.
+Take provisions regulating witness testimony.
 At common law, parties and interested witnesses were not permitted to testify in their own causes.
@@
 As the code migrated West, however, legislators added racial exclusions to Field's list.
-The following cluster documents how California's codifiers grafted earlier prohibitions from midwestern states into Field's Code.
+The cluster of sections in the appendix documents how California's codifiers grafted earlier prohibitions from midwestern states into Field's Code.
 Many other codes then evidence a remarkable uniformity with California's text (which later changed only to add "Mongolian" to the list of races).
-Iowa's Code had much more minor influence, and Wyoming developed the only truly original section which made clear the link to a racist assumption of infantilization of non-white peoples.
+Iowa's Code had a more minor influence, and Wyoming developed the only truly original section which made explicit that the exclusion was based on the racist assumption that non-white peoples were infantilized, a connection only implicit in other jurisdictions.
 
-**Figure: Cluster from Kellen**
-
-As these clusters illustrate, uniformity can be just as instructive as variation.
-On the point, the most significant clusters that we investigated related to the collection of debts.
-These were clusters which went against the typical pattern that we observed.
-While many clusters exhibited regional variation as they grew more distant from the Field Code, clusters having to do with creditors' remedies were almost completely uniform across the American West and South.
+Uniformity in the law, as shown through these clusters, is just as instructive as variation.
+The most significant clusters that we investigated related to the collection of debts.
+These were clusters which went against the typical pattern we observed.
+While most clusters exhibited regional variation as they grew more distant from the Field Code, clusters having to do with creditors' remedies were almost completely uniform across the American West and South.
 No single section of the code announced its preference for creditors' rights; rather, the acceleration of creditors' remedies resulted from the combination of several sections.
-In the original enacted Code, § 107 required a defendant to answer the complaint within twenty days, instead of at the next court session (which in some cases could have been as far as three months away); § 202 provided for default judgment as a matter of course, issued by a clerk without a judicial order if no adequate answer was received within the twenty days; §§ 128-133 abolished fictitious pleadings and required answers to state true facts verified by a defendant's oath, all so that no trial would delay the enforcement of uncontestable obligations; finally, the code abolished a traditional thirty-day waiting period between issue of judgment and commencement of execution (see First Report (New York 1848), 197).
+In New York's original enacted code from 1848, §107 required a defendant to answer the complaint within twenty days, instead of at the next court session (which in some cases could have been as far as three months away); §202 provided for default judgment as a matter of course, issued by a clerk without a judicial order if no adequate answer was received within the twenty days; §§128--133 abolished fictitious pleadings and required answers to state true facts verified by a defendant's oath, all so that no trial would delay the enforcement of uncontestable obligations; finally, the code abolished a traditional thirty-day waiting period between issue of judgment and commencement of execution.
 These provisions dealt with what merchants and capitalists perceived as an abuse of the common law system, where defendants in cases of debt could stretch out enforcement of debt collection for as long as two years.
@@
 Clustering each of these sections reveals that western states along with the former Confederate states of South Carolina, North Carolina, and Florida copied each provision almost exactly.
-Midwestern and Upper South states that had already developed by 1850 and maintained commercial ties to Chicago and New Orleans varied the New York rules, sometimes by requiring answers only in term time, or permitting only a judge to decree default judgment rather than a clerk, in either case effectively stretching out enforcement and making a formal trial more likely.
+Midwestern and Upper South states that had already developed and maintained commercial ties to Chicago and New Orleans by 1850 varied the New York rules, sometimes by requiring answers only in term time, or permitting only a judge to decree default judgment rather than a clerk, in either case effectively stretching out enforcement and making a formal trial more likely.
 But in the Reconstruction South, and in the West over the same period, regardless of whether a jurisdiction abolished chancery or not, regardless of the racial exclusions it may have placed on witness testimony, the provisions on debt collection remained unchanged.
@@
 
-[^34]: The formal definition of the Jaccard similarity for two sets, $A$ and $B$, is $$J(A, B) = \frac{ | A \cap B | }{ | A \cup B | }$$
+[^34]: The formal definition of the Jaccard similarity for two sets, $A$ and $B$, is $J(A, B) = \frac{ | A \cap B | }{ | A \cup B | }$.
 
@@
 
-[^39]: Non-Field jurisdictions occasionally exhibited a borrowing relationship within a state or across two states.
+[^39]: David Dudley Field, The Latest Edition of the New York Code of Civil Procedure (1878), 21.
+
+[^40]: Non-Field jurisdictions occasionally exhibited a borrowing relationship within a state or across two states.
 In in a few unusual instances they contributed to codes which were derived from the Field Code.
@@
 
-[^40]: spectrogram("CA1851", mutate(best\_matches, match\_code = ifelse(match\_code %in% c("NY1848", "NY1849", "NY1850"), "New York 1849/50", match\_code)), white\_list = 3)
-
-[^41]: (The visualization here, because of difficulties in precisely matching sections, actually understates the extent of the borrowing.) **Explain** why our method errs on the side of undercounting.
-
-[^42]: Scholars in digital literary studies often speak of the "deformance" of texts.
-Clustering the sections of the codes deformed them by pulling the sections out of their context within specific codes and by arranging them by topic in chronological order.
-Deforming the codes allowed us to see the development and spread of the law.
-
-[^43]: Brendan J. Frey and Delbert Dueck, "Clustering by Passing Messages Between Data Points," *Science* 315 (2007): 972--976.
-
-[^44]: Furthermore, even though the affinity propagation clus- tering algorithm did not fully converge with our peculiar dataset, it did an adequate job clustering the documents.
+[^43]: Brendan J.
+Frey and Delbert Dueck, "Clustering by Passing Messages Between Data Points," *Science* 315 (2007): 972--976, doi: 10.1126/science.1136800; Ulrich Bodenhofer, Andreas Kothmeier, and Sepp Hochreiter, "APCluster: an R package for affinity propagation clustering," *Bioinformatics* 27 (2011): 2463-2464, doi:10.1093/bioinformatics/btr406.
+Even though the affinity propagation algorithm did not fully converge with our dataset, it did an adequate job clustering the documents.
 Because there was an exemplar section for each cluster, we were able to merge clusters whose exemplars had a high Jaccard similarity score.
 
-[^45]: We also implemented a method called the Smith Waterman algorithm, which is used for gene sequencing, but which we adapted for natural language.
-This is the method used by Smith et al for Viral Texts.
-This permits us to extract the longest matching string from two documents and so to see how the one document modified the other.
+[^47]: Samuels, Lisa, and Jerome McGann.
+"Deformance and Interpretation." *New Literary History* 30.1 (1999) : 25--56; Mark Sample, "Notes toward a Deformed Humanities," blog post, 2 May 2012: <http://www.samplereality.com/2012/05/02/notes-towards-a-deformed-humanities/>; Ramsay, *Reading Machines*, 32--57.
 
-[^46]: E.g., Moretti, Distant Reading; Jockers, Macroanalysis.
-
-[^47]: Samuels, Lisa, and Jerome McGann. "Deformance and Interpretation." *New Literary History* 30.1 (1999) : 25--56; *Stallybrass, Peter. "Against Thinking."* PMLA *122.5 (2007): 1580-1587.*
-
-[^48]:
+[^48]: First Report (New York, 1848), 197.
 
@@
 Mashaw, *Creating the Administrative Constitution: The Lost One Hundred Years of American Administrative Law* (Yale Law Library 2012); Gautham Rao, *National Duties: Custom Houses and the Making of the American State* (University of Chicago 2016).
-
-[^72]: David Dudley Field, The Latest Edition of the New York Code of Civil Procedure (1878), 21.

### 2016-06-28 article/article.Rmd
Make the network graph look better

@@
 
-```{r code-to-code-network, fig.width=12, fig.height=12, fig.cap = "The structure of borrowings among nineteenth-century codes of civil procedure.
+```{r code-to-code-network, fig.width=6.5, fig.height=7, fig.cap = "The structure of borrowings among nineteenth-century codes of civil procedure.
 Note that several versions of New York's Field Code were at the center of the network, while other states such as California and Ohio became centers of regional variations on the Field Code."}
+set.seed(3728)
 ggraph(codes_g, "igraph", algorithm = "nicely") +
@@
                               angle = 15)) +
-  geom_node_point(aes(colour = as.factor(distance)), size = 10) +
+  geom_node_point(aes(colour = as.factor(distance)), size = 5) +
   scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") + 
@@
   ggforce::theme_no_axes() +
-  geom_node_text(aes(label = name), size = 6) +
-  labs(title = "The migration of law through borrowings in nineteenth-century codes of civil procedure") +
+  geom_node_text(aes(label = name), size = 3, family = "Palatino") +
+  labs(title = "The migration of the Field Code",
+       subtitle = "Codes of civil procedure connected by borrowed sections") +
   theme(legend.position = "bottom",
-        panel.border = element_blank())
+        panel.border = element_blank(),
+        text = element_text(family = "Palatino"),
+        legend.title = element_text(size = 10),
+        legend.text = element_text(size = 8))
 ```

### 2016-06-28 article/article.Rmd
Standardize labels and legend sizes

@@
 fontsize: 12pt
+fontfamily: 
+  - mathpazo
 output:
@@
 spectrogram("CA1850", best_matches, white_list = c("LA1844", "NY1829", "NY1849",
-                                                   "NY1848"))
+                                                   "NY1848"),
+            base_size = 10)
 ```
@@
 ```{r CA1851-borrowings, fig.height=3.5, fig.align="center"}
-spectrogram("CA1851", best_matches, white_list = 3)
+spectrogram("CA1851", best_matches, white_list = 3,
+            base_size = 10)
 ```
@@
 spectrogram("WA1855", best_matches, white_list = c("CA1850", "CA1851", "IN1852",
-                                                   "NY1853", "OR1854", "WI1849"))
+                                                   "NY1853", "OR1854", "WI1849"),
+            base_size = 10)
 ```
@@
 ```{r WA1873-borrowings, fig.height=4.5, fig.align="center"}
-spectrogram("WA1873", best_matches)
+spectrogram("WA1873", best_matches,
+            base_size = 10)
 ```
@@
 The Field code's summary judgment brought down the time of debt collection to a matter of weeks.
-Effectively, the code traded the rhythms of agriculture for the rhythms of merchant finance.[^48]
+The code traded the rhythms of agriculture for the rhythms of merchant finance.[^48]
 
@@
 For instance, a code from 1851 obviously did not borrow from a code from 1877.
-Furthermore, in chains of borrowing (e.g., NY1850 → CA1851 → CA1868 → CA1872 → MT1895) the latest section might have a high similarity to all of its ancestors, but it was in fact borrowed only from the most recent parent.
+Furthermore, in chains of borrowing (e.g., NY1850 to CA1851 to CA1868 to CA1872 to MT1895) the latest section might have a high similarity to all of its ancestors, but it was in fact borrowed only from the most recent parent.
 We therefore filtered the similarity matrix to remove matches within the same code; anachronistic matches; spurious matches beneath a certain threshold.
@@
 [^47]: Samuels, Lisa, and Jerome McGann.
-"Deformance and Interpretation." *New Literary History* 30.1 (1999) : 25--56; Mark Sample, "Notes toward a Deformed Humanities," blog post, 2 May 2012: <http://www.samplereality.com/2012/05/02/notes-towards-a-deformed-humanities/>; Ramsay, *Reading Machines*, 32--57.
+"Deformance and Interpretation." *New Literary History* 30.1 (1999): 25--56; Mark Sample, "Notes toward a Deformed Humanities," blog post, 2 May 2012: <http://www.samplereality.com/2012/05/02/notes-towards-a-deformed-humanities/>; Ramsay, *Reading Machines*, 32--57.
 

### 2016-06-28 R/spectrogram.R

@@ -45,6 +45,7 @@ spectrogram <- function(code, matches_df, num_cols = 50,
   labs(x = NULL, y = NULL, fill = "Section borrowed from") +
   ggtitle(label = title) +
   theme(legend.position = "bottom",
+        text = element_text(family = "Palatino"),
         axis.ticks = element_blank(),
         axis.line = element_blank(), axis.text = element_blank(),
         panel.background = element_blank(), panel.grid = element_blank(),

### 2016-06-28 article/article.Rmd
Revise part 4

@@
 
-## Part 4
+## 4. Procedure codes and capitalism
 
-Alerted by these clustering patterns to the significance of creditors' remedies in the developing West and re-developing South, it was not difficult to find evidence of westerners and southerners commenting on these features of the code or its connections to New York capital.
-Twelve of the states and territories that copied the Field Code mostly closely did so during the Civil War and Reconstruction era---four states in the former Confederacy and eight jurisdictions in the Far West.[^49] As with other areas of postbellum historiography, it turns out one may learn a lot by holding the postbellum American South and American West together.
+The near uniformity of creditors' remedies in Field Code states, as demonstrated by clustering, points out the close link between the rise of civil procedure and capitalism.
+Westerners and southerners commented on these features of the code or its connections to New York capital.
+Twelve of the states and territories that copied the Field Code most closely did so during the Civil War and Reconstruction era---four states in the former Confederacy and eight jurisdictions in the Far West.[^49] As with other areas of postbellum history, it turns out one may learn a lot by holding the postbellum American South and American West together.
 
@@
 While Lamoreaux and Wallis focus on the development of banking, transportation, and incorporation at the state level, it was the Procedure Code that provided the structure of civil remedies that protected these state institutions.
-And procedure codes were, of course, the creatures of state governance.[^52]
+And procedure codes were the creatures of state governance.[^52]
 
-With the universal complaints that time was too short or commissioners too democratically irresponsible, one might expect the code to have faced more competition from other workable statutes.
-Southern states that drew more on the civilian code tradition such as Louisiana and Alabama offered other options for states desiring to reform common law practice.[^53] And if Euro-Americans believed law had to be imported into the West, Colorado immigrants proved that the common law of Illinois was just as amenable to statutory importation as New York law.[^54] But what codifiers saw when they looked at New York, more so than Louisiana, Alabama, or Illinois, was the Empire State of commercial capital.
-And the putative fears, demands, and desires of a personified Capital continually wielded promises---and threats---in the debates over procedural codification.
+The states that adopted the Field Code were never forced to, and they had other options available to them.
+Southern states that drew more on the civilian code tradition such as Louisiana and Alabama offered other options for states desiring to reform common law practice.[^53] Illinois long retained the common law---in later decades lawyers called it "the Yellowstone Park of common law pleading." When Colorado was a territory it imported the Illinois common law to the West via statute, a full fourteen years before its legislature considered the Field Code.
+[^54]
+
+But what codifiers saw when they looked at New York, more so than at Louisiana, Alabama, or Illinois, was the Empire State of commercial capital.
+The fears, demands, and desires of a personified Capital continually wielded promises---and threats---in the debates over procedural codification.
 The early Mormon settlers of Utah persistently avoided the mining frenzy as well as codification.
@@
 He encouraged the bar to accommodate themselves to change, for "the New York system ...
-bids fair to become national." Putatively offering an overview of the code, the articles were almost entirely about credit.
+bids fair to become national." Supposedly offering an overview of the code, the articles were almost entirely about credit.
 "How can we create credit?
@@
 As in postbellum North Carolina, establishing a flow of credit through the remedial system became a leading priority of western lawyers.
-While the so-called new western history has shed significant light on neglected topics of Indian dispossession and environmental management, it has often done so by leaving out of view matters of political economy, a staple of the old western history.
+While the new western history has shed significant light on neglected topics of Indian dispossession and environmental management, it has often done so by leaving out of view matters of political economy, a staple of the old western history.
 As one work in that older tradition argued, "Debt collection was the central part of law practice for the \[western\] bar and remained a key part of private practice throughout the century."[^60] On that understanding, one western lawyer succinctly summarized the difference between the code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, ...
@@
 Both jurisdictions, while reforming the practice of law, largely rejected codification within their own borders but encouraged it among their economic dependents.
-The English commissioned a full codification of law for India and colonies in Singapore, while further codifications produced by Field in New York covering civil and penal law were adopted in California and other western jurisdictions.[^64] In both places, leading arguments against codification carried a civilizational logic of empire: Advanced societies could not codify their law, for to do so would be to freeze the progress of legal science.
+The English commissioned a full codification of law for India and colonies in Singapore, while further codifications produced by Field in New York covering civil and penal law were adopted in California and other western jurisdictions.[^64] In both places, leading arguments against codification carried a civilizational logic of empire: advanced societies could not codify their law, for to do so would be to freeze the progress of legal science.
 What appeared to some to be a hopeless mass of confusion was to common law defenders the sign of true legal sophistication.
@@
 
-In America, Macaulay's tool of enlightened despotism spread with the anxiety that capital from the nation's economic center would remain scarce without a Code of remedies that, if not in fact the law of New York, was at least prescribed by New York lawyers and their corporate clients.
-In the two most populous and commercially advanced western states, Texas and Illinois, the need for New York capital failed to move state legislators to adopt the code at the expense of popular sovereignty (although there were concerted efforts in both jurisdictions).[^68] Lacking the self-sufficiency of those two jurisdictions, the other states of the Greater Reconstruction in America adopted a foreign Code, but lawyers, legislators, and their supporters claimed the endorsement of popular sovereignty in doing so.
+In America, Macaulay's tool of enlightened despotism spread with the anxiety that capital from the nation's economic center would remain scarce without a code of remedies that, if not in fact the law of New York, was at least prescribed by New York lawyers and their corporate clients.
+In the two most populous and commercially advanced western states, Texas and Illinois, the need for New York capital failed to move state legislators to adopt the code at the expense of popular sovereignty (although there were concerted efforts in both jurisdictions).[^68] Lacking the self-sufficiency of those two jurisdictions, the other states of the Greater Reconstruction in America adopted a foreign code, but lawyers, legislators, and their supporters claimed the endorsement of popular sovereignty in doing so.
 Even in North Carolina, whose Democratic newspapers daily called for the repeal "this child of the carpet baggers," Republican editors proclaimed that "the movement" towards procedural codification "comes from the people, from the instinctive logic by which an unprejudiced mind grasps the advantages of the system."[^69]
@@
 
-[^54]: Illinois was a fiercely traditional anti-code state.
-In later decades, lawyers jokingly called it "the Yellowstone Park of common law pleading." See Charles E.
-Clark, "The New Illinois Civil Practice Act," 1 *University of Chicago Law Review* 209 (1933).
+[^54]: See Charles E.
+Clark, "The New Illinois Civil Practice Act," *University of Chicago Law Review* 1 (1933): 209.
 Nevertheless, even Illinois had substantial legislation organizing the courts and prescribing certain common law processes for obtaining civil remedies, and Colorado adapted the bulk of this legislation when it organized as a territory, a full seventeen years before its legislature considered adopting the Field Code.
@@
 [^55]: Journal of the Assembly of the Territory of Utah (1870), 15.
+See also Leonard J.
+Arrington, *Great Basin Kingdom: An Economic History of the Latter-Day Saints, 1830--1900*, new edition (University of Illinois Press, 2004).
 

### 2016-06-28 article/article.Rmd
Fix conclusion

@@
 
-By framing our historical questions around "medium data" we enjoyed a useful symbiosis of traditional and digital historical methods.
-Our computational methods produced useful historical knowledge because they were justified by what we knew about the data from traditional historical work.
-We knew that code commissioners worked with "the scissors and paste-pot," as critics complained, and we knew of codes in the archives that commissions literally marked up the legislation of other states.
-While we think that one of the most useful things about digital history is its ability to start with large corpora and then figure out what was interesting from the past, we have shown how digital history can function by starting with particular questions rather than particular sources.
-We have shown how a collection of methods from computer science, including minhash/locality-sensitive hashing, affinity propagation clustering, and network analysis, along with the concept of text deformance from literary history, can be used to good effect in tracking the changes in the law, as well as any other discursive field whose texts can be readily divided into sectional units.
-Finally we have shown how it is possible to work on different scales, using network analysis and algorithmic close reading, and thus to get both a macroscopic picture of the law's migration, as well as a highly detailed view of the changes in the law.
+By framing addressing our historical questions to a sufficiently large but narrowly defined corpus of sources, we enjoyed a useful symbiosis of traditional and digital historical methods.
+Our computational methods produced useful historical knowledge because they were carefully tailored to what we knew about the data from traditional historical work.
+We knew that code commissioners worked with "the scissors and paste-pot," as critics complained, and we examined codes in the archives which showed how commissions literally marked up the legislation of other states.
+While we think that one of the most useful things about digital history is its ability to start with large corpora and then figure out what was interesting from the past, we have shown how digital history can also operate by starting with specific historical questions rather than particular sources.
+We have shown how a collection of methods from computer science, including minhash/locality-sensitive hashing, affinity propagation clustering, and network analysis, along with the concept of text deformance from literary history, can be used to good effect in tracking the changes in the law, as well as any other discursive field whose texts can be readily divided into sections.
+Finally we have shown how it is possible to work on different scales, using network analysis, visualization, and algorithmic close reading, and thus to gain both a broad overview of the law's migration, as well as a highly detailed view of the changes in the law.
 
@@
 
-In the economically developing West and re-developing South, anxieties over the lack of capital---both among the bar as well as lay voters---joined with arguments of civilization and progress to spur many jurisdictions to copy the text of the code of New York, the Empire State of capital.
+In the economically developing West and re-developing South, anxieties over the lack of capital---both among the bar as well as voters---joined with arguments of civilization and progress to spur many jurisdictions to copy the text of the code of New York, the Empire State of capital.
 The short time horizons of American lawmaking limited the options available for re-imagining or re-crafting what could become the law of remedies and legal practice.

### 2016-06-28 article/article.Rmd
Revisions to clustering sections
Cite the macroscope

@@
 
-The computational evidence that we assembled revealed patterns in how law migrated at several different scales of analysis.
-We used the similarity matrix as the input to three different digital history techniques: network analysis, visualizations, and clustering.
+The computational evidence that we assembled revealed patterns in how law migrated at several different scales of analysis.^[Our attention to big and small scales is the main aim described in Shawn Graham, Ian Milligan, and Scott Weingart, *Exploring Big Historical Data: The Historian’s Macroscope* (Imperial College Press, 2015).] We used the similarity matrix as the input to three different digital history techniques: network analysis, visualizations, and clustering.
 
@@
 
-## Appendix: Clustering sections involving racial exclusions from witness testimony
+## Appendix: Clustering sections involving witness exclusions
+
+This sample cluster brings together sections that involve racial exclusions from witness testimony in civil trials, with commentary.
 

### 2016-06-29 article/article.Rmd
Changes to formatting, cite the macroscope, etc

@@
 - Lincoln Mullen
-fontsize: 12pt
 fontfamily:
 - mathpazo
+fontsize: 12pt
 output:
@@
     number_sections: False
+  word_document: 
+    fig_caption: True
+    md_extensions: '-tex_math_single_backslash'
+    pandoc_args: ["--smart"]
 title: The Spine of American Legal Practice
@@
 
-  Table: A subset of the section to section similarity matrix.
+  : A subset of the section to section similarity matrix.
 
@@
 
-The computational evidence that we assembled revealed patterns in how law migrated at several different scales of analysis.^[Our attention to big and small scales is the main aim described in Shawn Graham, Ian Milligan, and Scott Weingart, *Exploring Big Historical Data: The Historian’s Macroscope* (Imperial College Press, 2015).] We used the similarity matrix as the input to three different digital history techniques: network analysis, visualizations, and clustering.
+The computational evidence that we assembled revealed patterns in how law migrated at several different scales of analysis.[^38] We used the similarity matrix as the input to three different digital history techniques: network analysis, visualizations, and clustering.
 
@@
 ```{r code-to-code-network, fig.width=6.5, fig.height=7, fig.cap = "The structure of borrowings among nineteenth-century codes of civil procedure.
-Note that several versions of New York's Field Code were at the center of the network, while other states such as California and Ohio became centers of regional variations on the Field Code."}
+Note that several versions of New York's Field Code were at the center of the network, while other states such as California and Ohio became centers of regional variations on the Field Code.
+States that adopted any of the variations on the Field Code became part of a network centered on New York capital."}
 set.seed(3728)
@@
                                angle = 15)) + 
-  geom_node_point(aes(colour = as.factor(distance)), size = 5) +
+  geom_node_point(aes(shape = as.factor(distance)), size = 5) +   
   scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") +    
   scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +   
-  scale_color_discrete("Distance from a NY code") +
+  scale_color_discrete("Distance from a Field Code") +
   ggforce::theme_no_axes() +  
@@
         legend.title = element_text(size = 10),
-        legend.text = element_text(size = 8))
+        legend.text = element_text(size = 8),
+        plot.title = element_text(face = "bold"))
 ```
 
-The New York Field Codes, especially the finished draft of 1850, are central to the entire network.[^38] New York gave rise to different regional traditions within the procedural network.
+The New York Field Codes, especially the finished draft of 1850, are central to the entire network.[^39] New York gave rise to different regional traditions within the procedural network.
 Variations in the Field drafts meant that different states could borrow different versions of the Field Code.
@@
 A count by a "friend" of Field's found that only three sentences of the Field Code had carried over word-for-word into the Throop Code.
-Nevertheless, many of the changes were purely formal, and Field speculated that these changes had been made only "so that \[the code\] should not appear to be the same thing as before."[^39] With respect to Mr.
+Nevertheless, many of the changes were purely formal, and Field speculated that these changes had been made only "so that \[the code\] should not appear to be the same thing as before."[^40] With respect to Mr.
 Field or his "friend," we found that the connection was between the Throop Code and the Field Code was somewhat stronger than he thought, and the Throop Code was indeed a descendant, if much revised, from the Field Code.
@@
 Finally, our corpus included a number of statutes which stood outside the Field Code tradition, such as Virginia and West Virginia regulations, statutes from Massachusetts and Maine, and southern codes from Georgia to Louisiana.
-These statutes show that the dominance of the Field Code was not total, and a number of older jurisdictions remained outside of its ambit.[^40] But nearly every jurisdiction established or reconstructed after 1850 became a part of the Field Code network, and no other tradition achieved anywhere near the same coherence across state lines.
+These statutes show that the dominance of the Field Code was not total, and a number of older jurisdictions remained outside of its ambit.[^41] But nearly every jurisdiction established or reconstructed after 1850 became a part of the Field Code network, and no other tradition achieved anywhere near the same coherence across state lines.
 
@@
 spectrogram("CA1850", best_matches, white_list = c("LA1844", "NY1829", "NY1849",
-                                                   "NY1848"),
-            base_size = 10)
+                                                   "NY1848"), base_size = 10)
 ```
@@
 Rather, the bulk of the 1851 California code came from the updated model code Field completed for New York in 1850.
-This includes the portion of the code on new trials previously borrowed from Louisiana.^[Final Report (New York, 1850), §§804-809, compared to 1851 California Laws 260, §§439-441.] The remainder of the code was borrowed from the 1850 California code.
+This includes the portion of the code on new trials previously borrowed from Louisiana.[^42] The remainder of the code was borrowed from the 1850 California code.
 The bulk of the borrowings that come from California instead of directly from New York are at the beginning of the code, where the 1850 code had made amendments specific to California.
@@
 ```{r CA1851-borrowings, fig.height=3.5, fig.align="center"}
-spectrogram("CA1851", best_matches, white_list = 3,
-            base_size = 10)
+spectrogram("CA1851", best_matches, white_list = 3, base_size = 10)
 ```
@@
 ```{r WA1873-borrowings, fig.height=4.5, fig.align="center"}
-spectrogram("WA1873", best_matches,
-            base_size = 10)
+spectrogram("WA1873", best_matches, base_size = 10)
 ```
@@
 This method of clustering, however, is a kind of algorithmic close reading.
-By deforming the texts---taking them out of the context of the codes and putting them in the context of their particular variations---we are able to pay attention to those variations.[^47]
+By deforming the texts---taking them out of the context of the codes and putting them in the context of their particular variations---we are able to pay attention to those variations.[^44]
 
@@
 The Field code's summary judgment brought down the time of debt collection to a matter of weeks.
-The code traded the rhythms of agriculture for the rhythms of merchant finance.[^48]
+The code traded the rhythms of agriculture for the rhythms of merchant finance.[^45]
 
@@
 Westerners and southerners commented on these features of the code or its connections to New York capital.
-Twelve of the states and territories that copied the Field Code most closely did so during the Civil War and Reconstruction era---four states in the former Confederacy and eight jurisdictions in the Far West.[^49] As with other areas of postbellum history, it turns out one may learn a lot by holding the postbellum American South and American West together.
+Twelve of the states and territories that copied the Field Code most closely did so during the Civil War and Reconstruction era---four states in the former Confederacy and eight jurisdictions in the Far West.[^46] As with other areas of postbellum history, it turns out one may learn a lot by holding the postbellum American South and American West together.
 
-In the last decade, scholars of Reconstruction have broadened the scope of their study to include both the South and the West as two sites in one "Greater Reconstruction." These studies have illustrated the ways that military conquest, rapid industrialization, and the resettlement and education of ethnic minorities developed similarly in each region, guided by economic elites in New York and political administrators in Washington.[^50] In tracing the legal aspects of this Greater Reconstruction, scholars have focused almost entirely on constitutional rights of citizenship and civil equality or the expansion of federal power.[^51] While the 1860s and 1870s were of course a transformative period in the history of civil rights and the creation of a national state, they were also the decades in which many local legal institutions and practices were transformed not by federal power but by state codification.
+In the last decade, scholars of Reconstruction have broadened the scope of their study to include both the South and the West as two sites in one "Greater Reconstruction." These studies have illustrated the ways that military conquest, rapid industrialization, and the resettlement and education of ethnic minorities developed similarly in each region, guided by economic elites in New York and political administrators in Washington.[^47] In tracing the legal aspects of this Greater Reconstruction, scholars have focused almost entirely on constitutional rights of citizenship and civil equality or the expansion of federal power.[^48] While the 1860s and 1870s were of course a transformative period in the history of civil rights and the creation of a national state, they were also the decades in which many local legal institutions and practices were transformed not by federal power but by state codification.
 Naomi Lamoreaux and John Joseph Wallis have recently argued that in the creation of a modern American economy, "the federal government played *no* role in this process until the Civil War, and even then it played only a bit part." The history of the Field Code's migration helps to substantiate this claim.
 While Lamoreaux and Wallis focus on the development of banking, transportation, and incorporation at the state level, it was the Procedure Code that provided the structure of civil remedies that protected these state institutions.
-And procedure codes were the creatures of state governance.[^52]
+And procedure codes were the creatures of state governance.[^49]
 
 The states that adopted the Field Code were never forced to, and they had other options available to them.
-Southern states that drew more on the civilian code tradition such as Louisiana and Alabama offered other options for states desiring to reform common law practice.[^53] Illinois long retained the common law---in later decades lawyers called it "the Yellowstone Park of common law pleading." When Colorado was a territory it imported the Illinois common law to the West via statute, a full fourteen years before its legislature considered the Field Code.
-[^54]
+Southern states that drew more on the civilian code tradition such as Louisiana and Alabama offered other options for states desiring to reform common law practice.[^50] Illinois long retained the common law---in later decades lawyers called it "the Yellowstone Park of common law pleading." When Colorado was a territory it imported the Illinois common law to the West via statute, a full fourteen years before its legislature considered the Field Code.
+[^51]
 
@@
 The early Mormon settlers of Utah persistently avoided the mining frenzy as well as codification.
-By 1870, however, the territory's governor directed the legislature's attention to the recent Code of Nevada, a code "for a people whose interests in many respects are similar to our own." Of course, standing behind the Nevada Code was "the State of New York---a State which is an empire in itself and whose commercial transactions are far greater than those of any other State in the Union." By copying its code, Utah too could be "rewarded by equal advantages."[^55] Code proponents in Colorado similarly parried arguments that a code would be a "foreign" imposition by pointing to the fact that it has been "adopted twenty-nine years ago by the Empire state of the Union" and they promised that the code of the nation's uniquely commercial empire could bring wealth in its wake.[^56]
+By 1870, however, the territory's governor directed the legislature's attention to the recent Code of Nevada, a code "for a people whose interests in many respects are similar to our own." Of course, standing behind the Nevada Code was "the State of New York---a State which is an empire in itself and whose commercial transactions are far greater than those of any other State in the Union." By copying its code, Utah too could be "rewarded by equal advantages."[^52] Code proponents in Colorado similarly parried arguments that a code would be a "foreign" imposition by pointing to the fact that it has been "adopted twenty-nine years ago by the Empire state of the Union" and they promised that the code of the nation's uniquely commercial empire could bring wealth in its wake.[^53]
 
@@
 Hamill replied that he knew of one California company of capitalists who were deterred from investing in mining property here wholly on account of the practice of the courts in mining cases.
-If we had had this code years ago, Colorado would now have a larger amount of California capital in her mines."[^57] Codifiers argued that, in attracting capital, procedure was at least as important as the substantive rules of property and contract, because procedure secured the remedies that actually protected investments.
-"Men of capital and enterprise will not make investments and devote their time and energies to those works of internal improvement so necessary for the speedy development of our natural resources, and for the settlement and building up the country," Nebraska's governor reasoned, "unless ample protection is afforded them, by legal enactment, for the capital invested and labor employed." And he therefore urged swift passage of the Field Code.[^58]
+If we had had this code years ago, Colorado would now have a larger amount of California capital in her mines."[^54] Codifiers argued that, in attracting capital, procedure was at least as important as the substantive rules of property and contract, because procedure secured the remedies that actually protected investments.
+"Men of capital and enterprise will not make investments and devote their time and energies to those works of internal improvement so necessary for the speedy development of our natural resources, and for the settlement and building up the country," Nebraska's governor reasoned, "unless ample protection is afforded them, by legal enactment, for the capital invested and labor employed." And he therefore urged swift passage of the Field Code.[^55]
 
@@
 Let the law enforce punctuality; let the people of North Carolina learn that the great law of business is, that 'time is of the essence of the contract,' and incur no debt that they do not expect to meet at maturity." Under the more certain and speedy remedies of the code, "we may expect that the secret hoards of the frugal among ourselves will be offered to loan, and even that the vaults of the banks of New-York ...
-will be open to our industry."[^59]
+will be open to our industry."[^56]
 
@@
 While the new western history has shed significant light on neglected topics of Indian dispossession and environmental management, it has often done so by leaving out of view matters of political economy, a staple of the old western history.
-As one work in that older tradition argued, "Debt collection was the central part of law practice for the \[western\] bar and remained a key part of private practice throughout the century."[^60] On that understanding, one western lawyer succinctly summarized the difference between the code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, ...
-that he did not also break out somewhere with 'take for instance the case of an action on a promissory note,' as though the collection of notes was about all there could be any law needed for."[^61]
+As one work in that older tradition argued, "Debt collection was the central part of law practice for the \[western\] bar and remained a key part of private practice throughout the century."[^57] On that understanding, one western lawyer succinctly summarized the difference between the code and the common law as "whether a merchant had better try to collect a \$500 note or burn it up." Tiring of all the focus on creditors' remedies, one legislator observed that he "never knew one of these professionals who undertook to write up the beauties of the New York code, ...
+that he did not also break out somewhere with 'take for instance the case of an action on a promissory note,' as though the collection of notes was about all there could be any law needed for."[^58]
 
 The creditors' remedies in the code gave the codifiers their leading argument against criticisms rooted in the ideology of popular sovereignty.
-"There is no doubt but the people are in favor of anything that promises to hurry up that proverbially slow and blind old female called Justice, and they will go for the old code," one Colorado newspaper announced.[^62] New York's "code practice is the best in excellence," stated another, "and when I say *best* I do not mean best for lawyers only, but best for the people---the commonwealth."[^63] If the People favored economic progress, certainty of remedy, and efficiency in proceedings, then they favored the New York Code, no matter whether they understood or cared about technical rules of pleading and joinder.
+"There is no doubt but the people are in favor of anything that promises to hurry up that proverbially slow and blind old female called Justice, and they will go for the old code," one Colorado newspaper announced.[^59] New York's "code practice is the best in excellence," stated another, "and when I say *best* I do not mean best for lawyers only, but best for the people---the commonwealth."[^60] If the People favored economic progress, certainty of remedy, and efficiency in proceedings, then they favored the New York Code, no matter whether they understood or cared about technical rules of pleading and joinder.
 Thus, in their arguments the codifiers imagined themselves the champions of popular sovereignty, for it was they who accomplished what the People actually desired.
@@
 Both jurisdictions, while reforming the practice of law, largely rejected codification within their own borders but encouraged it among their economic dependents.
-The English commissioned a full codification of law for India and colonies in Singapore, while further codifications produced by Field in New York covering civil and penal law were adopted in California and other western jurisdictions.[^64] In both places, leading arguments against codification carried a civilizational logic of empire: advanced societies could not codify their law, for to do so would be to freeze the progress of legal science.
+The English commissioned a full codification of law for India and colonies in Singapore, while further codifications produced by Field in New York covering civil and penal law were adopted in California and other western jurisdictions.[^61] In both places, leading arguments against codification carried a civilizational logic of empire: advanced societies could not codify their law, for to do so would be to freeze the progress of legal science.
 What appeared to some to be a hopeless mass of confusion was to common law defenders the sign of true legal sophistication.
-Science was, after all, sophisticated.[^65] The Throop Code came in for censure, both in its first year and in following decades, precisely for trying to capture all the sophistication of the New York legal system within an unwieldy 3,300 rules.[^66] Codification, however, could help developing societies along law's frontier take a progressive leap forward.
-As India's chief codifier Thomas Macaulay explained, codification "cannot be well performed in an age of barbarism," but also "cannot without great difficulty be performed in an age of freedom." As India balanced between the two, however, "it is the work which especially belongs to a government like that of India---to an enlightened and paternal despotism."[^67]
+Science was, after all, sophisticated.[^62] The Throop Code came in for censure, both in its first year and in following decades, precisely for trying to capture all the sophistication of the New York legal system within an unwieldy 3,300 rules.[^63] Codification, however, could help developing societies along law's frontier take a progressive leap forward.
+As India's chief codifier Thomas Macaulay explained, codification "cannot be well performed in an age of barbarism," but also "cannot without great difficulty be performed in an age of freedom." As India balanced between the two, however, "it is the work which especially belongs to a government like that of India---to an enlightened and paternal despotism."[^64]
 
 In America, Macaulay's tool of enlightened despotism spread with the anxiety that capital from the nation's economic center would remain scarce without a code of remedies that, if not in fact the law of New York, was at least prescribed by New York lawyers and their corporate clients.
-In the two most populous and commercially advanced western states, Texas and Illinois, the need for New York capital failed to move state legislators to adopt the code at the expense of popular sovereignty (although there were concerted efforts in both jurisdictions).[^68] Lacking the self-sufficiency of those two jurisdictions, the other states of the Greater Reconstruction in America adopted a foreign code, but lawyers, legislators, and their supporters claimed the endorsement of popular sovereignty in doing so.
-Even in North Carolina, whose Democratic newspapers daily called for the repeal "this child of the carpet baggers," Republican editors proclaimed that "the movement" towards procedural codification "comes from the people, from the instinctive logic by which an unprejudiced mind grasps the advantages of the system."[^69]
+In the two most populous and commercially advanced western states, Texas and Illinois, the need for New York capital failed to move state legislators to adopt the code at the expense of popular sovereignty (although there were concerted efforts in both jurisdictions).[^65] Lacking the self-sufficiency of those two jurisdictions, the other states of the Greater Reconstruction in America adopted a foreign code, but lawyers, legislators, and their supporters claimed the endorsement of popular sovereignty in doing so.
+Even in North Carolina, whose Democratic newspapers daily called for the repeal "this child of the carpet baggers," Republican editors proclaimed that "the movement" towards procedural codification "comes from the people, from the instinctive logic by which an unprejudiced mind grasps the advantages of the system."[^66]
 
@@
 The history of codification on the American periphery troubles cherished notions of American federalism.
-On the one hand, those suspicious of centralized power and critical of national governance since the New Deal have relied on narratives that tout the equality of sovereign states to set their own policies, foster local diversity, and "experiment" with legislative solutions to local issues.[^70] But the history of legal practice and civil remedies is one in which the localism fostered by common law practice rapidly gave way to uniform regulations transmitted by a network of New York lawyers without the slightest interference of the federal government.
+On the one hand, those suspicious of centralized power and critical of national governance since the New Deal have relied on narratives that tout the equality of sovereign states to set their own policies, foster local diversity, and "experiment" with legislative solutions to local issues.[^67] But the history of legal practice and civil remedies is one in which the localism fostered by common law practice rapidly gave way to uniform regulations transmitted by a network of New York lawyers without the slightest interference of the federal government.
 On the other hand, scholars who support the legitimacy of New Deal governance have recently produced an abundant literature unearthing a long tradition of "administrative" law at the state level well before the twentieth century.
-These accounts have focused on administrative adjudication or discretionary regulation within a narrow domain, such as customs houses.[^71] These histories have so far neglected the most widespread and significant instance of nineteenth-century administrative lawmaking in America---the spread of the Field Code through extra-legislative commissions.
+These accounts have focused on administrative adjudication or discretionary regulation within a narrow domain, such as customs houses.[^68] These histories have so far neglected the most widespread and significant instance of nineteenth-century administrative lawmaking in America---the spread of the Field Code through extra-legislative commissions.
 While these histories have sought to demonstrate that Americans from early on could be quite comfortable with administrative law and accepted it as a normal part of the constitutional order, this chapter has shown how lawmaking by commission generated significant political controversy and raised grave questions about popular sovereignty under such delegations, questions that over time were merely dodged rather than answered.
@@
 Without too much exaggeration we might say that our method has revealed the spine of modern American legal practice.
+
+[^1]: Message of the Governor, in Journal of the Council for the Territory of Nevada (1862), 21.
+
+[^2]: Nevada Council Journal (1862), 261--62. Act of Congress (1861) Organizing the Territory of Nevada, 12 U.S. Statutes at Large 209--14 (1863). 1861 Nevada Laws 314.
+
+[^3]: Besides his work on codification, which extended to civil, penal, and even international codes of law, Field became renown for his trial advocacy.
+Field argued the winning side in major Reconstruction cases such as *Ex Parte Milligan*, 71 U.S.
+(4 Wall.) 2 (1866) (holding the trial of civilians by military commission unconstitutional), *Cummings v.
+Missouri*, 71 U.S.
+(4 Wall.) 277 (1867) (striking a loyalty oath as unconstitutional), and *United States v.
+Cruikshank*, 92 U.S.
+542 (1875) (enforcing the Fourteenth Amendment only against "state action").
+Field came under heavy censure for his representation of Gilded Age robber barons like Jay Gould, Jim Fisk, and William "Boss" Tweed, but even Tweed's chief adversary Samuel Tilden retained Field's services for the disputed election of 1876.
+See Henry Martyn Field, *The Life of David Dudley Field* (1898); Philip J.
+Bergan, "David Dudley Field: A Lawyer's Life," in *The Fields and the Law* (New York: Federal Bar Council, 1986).
+
+[^4]: *Rocky Mountain News*, January 20, 1877.
+
+[^5]: Roscoe Pound, "David Dudley Field: An Appraisal," and Alison Reppy, "The Field Codification Concept," in Alison Reppy, ed., *David Dudley Field: Centenary Essays* (New York University School of Law, 1949); Stephen Subrin, "David Dudley Field and the Field Code: A Historical Analysis of an Earlier Procedural Vision," 6 *Law & Hist.
+Rev*.
+311 (1988); Robert G.
+Bone, "Mapping the Boundaries of a Dispute: Conceptions of Ideal Lawsuit Structure from the Field Code to the Federal Rules," 89 *Colum.
+L.
+Rev*.
+1 (1989).
+See also the literature on procedure and codification cited below.
+
+[^6]: When law professors such as New York's David Graham Jr.
+(a collaborator on the Field Code) began to be appointed to university positions, the chair for instruction in legal practice or procedure carried this designation of "practice and pleadings." Today that field is described as "civil procedure" a field that grew out of David Dudley Field's codification, as described below.
+The history of practice and procedure is a staple of general legal history.
+See Frederick Pollock and Frederick Maitland, *The History of English Law Before the Time of Edward I* (2d.
+ed., Cambridge, 1898), 2 vols.; Theodore Plucknett, *A Concise History of the Common Law* (5th ed.
+2010); Lawrence M.
+Friedman, *A History of American Law* (3d.
+ed.
+2005).
+Few book-length works have been dedicated to the subject, however.
+The exceptions are Robert Wyness Millar, *Civil Procedure of the Trial Court in Historical Perspective* (New York University School of Law 1952); Edward Purcell, *Litigation and Inequality: Federal Diversity Jurisdiction in Industrial America, 1870--1958* (Oxford 1992); John H.
+Langbein et al., *History of the Common Law: The Development of Anglo-American Legal Institutions* (Aspen 2009); and to some extent, William E.
+Nelson, *The Americanization of the Common Law: The Impact of Legal Change on Massachusetts Society, 1760--1830* (2d.
+ed., University of Georgia Press 1994).
+
+[^7]: For the rise of treatises in America generally, see G.
+Edward White, *The Marshall Court and Cultural Change, 1815--1835* (1988) and A.
+W.
+B.
+Simpson, "The Rise and Fall of the Legal Treatise: Legal Principles and the Forms of Legal Literature," in *Legal Theory and Legal History: Essays on the Common Law* (London: Hambledon Press, 1987), 273--320.
+The most instructive treatises for New York practice in the 1840s were Oliver L.
+Barbour, *A Treatise on the Practice of the Court of Chancery* (1844); Alexander M.
+Burrill, *Treatise on the Practice of the Supreme Court of the State of New York* (1846), 2 vols.; David Graham, *A Treatise on on the Practice of the Supreme Court of the State of New York* (3d.
+ed.
+1847); David Graham, *A Treatise on the Organization and Jurisdiction of the Courts of Law and Equity in the State of New York* (1839); Claudius L.
+Monell, *A Treatise on the Practice of the Supreme Court of the State of New York* (1849); Joseph W.
+Moulton, *The Chancery Practice of the State of New York* (1829), 2 vols.; and as a general introduction to the field, the Englishman Henry John Stephen's *Treatise on the Principles of Pleading in Civil Actions* (2d.
+ed.
+1828).
+
+[^8]: See Michael Lobban, *The Common Law and English Jurisprudence 1760--1850* (Clarendon Press 1991); Kunal M.
+Parker, *Common Law, History, and Democracy in America, 1790--1900: Legal Thought before Modernism* (Cambridge: Cambridge University Press, 2011); David M.
+Rabban, *Law's History: American Legal Thought and the Transatlantic Turn to History* (Cambridge 2013).
+
+[^9]: Or, to use a term from contemporary analysis, "super statutes." William N.
+Eskridge and John Ferejohn, *A Republic of Statutes: The New American Constitution* (New Haven: Yale University Press, 2010).
+See also David Lieberman, *The Province of Legislation Determined: Legal Theory in Eighteenth-century Britain* (Cambridge 1989); Farah Peterson, Statutory Interpretation and Judicial Authority, 1776--1860 (Ph.D.
+dissertation, Princeton University, September 2015).
+
+[^10]: Friedman, *A History of American Law*, 302.
+When the intellectual historian Perry Miller developed a reader surveying *The Legal Mind in America*, codification was its only central theme, as Miller argued it was the one intellectual topic that attracted lawyers away from their practices long enough to debate.
+Perry Miller, ed., *The Legal Mind in America: From Independence to the Civil War* (Anchor 1962).
+See also Charles M.
+Cook, *The American Codification Movement: A Study in Antebellum Legal Reform* (1983); Robert W.
+Gordon, "The American Codification Movement," 36 *Vanderbilt Law Review* 431 (1983); Maurice Eugen Lang, *Codification in the British Empire and America* (Lawbook Exchange 1924).
+On common theories of codification that transcended jurisdictional boundaries, see Csaba Varga, *Codification as a Socio-Historical Phenomenon* (Budapest, 2d.
+ed.
+2011 \[1991\]); Roger Berkowitz, *The Gift of Science: Leibniz and the Modern Legal Tradition* (Fordham 2010).
+
+[^11]: The most influential account has been Morton Horwitz's, which declares that "the desire to separate law and politics has always been a central aspiration of the American legal profession" in order to protect elite interests against popular democracy.
+Horwitz identifies "orthodox legal thought" and "orthodox lawyers" with the elite of the American bar who sought to shield the law from political interference, which above all meant crusading against legislation and especially codification.
+Morton J.
+Horwitz, *The Transformation of American Law, 1780--1850* (Oxford University Press, 1977), 258--59.
+Recent work has challenged Horwitz's account by showing how elite common law lawyers, particularly Horwitz's main target James Coolidge Carter, were actually political progressives who supported redistributive legislation such as the income tax.
+See, for instance, Rabban, *Law's History*, 322--77; Parker, *Common Law, History, and Democracy*, 230--41; Lewis A.
+Grossman, "James Coolidge Carter and Mugwump Jurisprudence," *Law & History Review* 20 (2002).
+These accounts follow Horwitz, however, in focusing on the few outspoken opponents of codification, rather than the elite lawyers who sponsored the procedure codes.
+Among the latter group could be found some of the most devout theorists of laissez faire economics in nineteenth-century America, including David Dudley Field and his brother, the Supreme Court Justice Stephen Johnson Field.
+
+[^12]: James Fenimore Cooper, *The Ways of the Hour: A Tale* (1850), 84.
+For an analysis of Cooper's philosophy of law and his critique of the New York constitution, see Charles Hansford Adams, *"The Guardian of the Law": Authority and Identity in James Fenimore Cooper* (Penn State University Press (1990), 135--48.
+See also Marvin Meyers, *The Jacksonian Persuasion: Politics and Belief* (Stanford 1957), 57--100.
+
+[^13]: On the politics and reforms of the New York Convention of 1846, see Charles Z.
+Lincoln, *The Constitutional History of New York from the Beginning of the Colonial Period to the Year 1905* (Rochester 1905), 2:10--101; Charles McCurdy, *The Anti-Rent Era in New York Law and Politics, 1839--1865* (University of North Carolina 2001); Jed Shugerman, *The People's Courts: The Rise of Judicial Elections and Judicial Power in America* (Harvard University Press 2012).
+
+[^14]: Count Pierre François Réal to William Sampson, October 27, 1824, in Sampson's Discourse and Correspondence with Various Learned Jurists Upon the History of the Law (1826), 191; Maxwell Bloomfield, "William Sampson and the Codifiers: The Roots of American Legal Reform," 11 *American Journal of Legal History* 234 (1967); Walter J.
+Walsh, "William Sampson, a Republican Constitution, and the Conundrum of Orangeism on American Soil, 1824--1831," 5/7 *Radharc* 1 (2006); William Sampson, *Memoirs* (2d.
+ed., 1817).
+On French-style codifications, see Robert B.
+Holtman, *The Napoleonic Revolution* (Louisiana State 1981); R.
+H.
+Kilbourne, *A History of the Louisiana Civil Code* (Paul M.
+Herbert Law Center 1987); Brian Young, *The Politics of Codification: The Lower Canadian Civil Code of 1866* (Osgoode Society 1994); John W.
+Cairns, *Codification, Transplants, and History: Law Reform in Louisiana (1808) and Quebec (1866)* (Talbot 2015); Roscoe Pound, "The French Civil Code and the Spirit of Nineteenth Century Law," 35 *Boston Law Review* 79 (1955).
+
+[^15]: Thomas J.
+Lockwood, "A History of Royal Commissions," 5 *Osgoode Hall Law Journal* 172 (1967); Barbara Lauriat, "'The Examination of Everything': Royal Commissions in British Legal History," 31 *Statute Law Review* 24 (2010); Joanna Innes, *Inferior Politics: Social Problems and Social Policies in Eighteenth-century Britain* (Oxford 2009).
+
+[^16]: Second Report of the Commissioners on Practice and Pleading (New York 1849), 3--4.
+See also, First Report of the Commissioners on Practice and Pleadings (New York 1848), iii-iv; Third Report of the Commissioners on Practice and Pleadings (New York 1849), 3, Lillian Goldman Law Library Rare Books Collection; Final Report of the Commissioners on Practice and Pleadings, in Documents of the Assembly of the State of New York, 73d sess., vol.
+2, no.
+16 (New York 1850), viii.
+
+[^17]: Report of the Commissioners on Practice and Pleadings, in New York Assembly Documents, 70th sess., vol. 2, no. 202 (1847), 3--4.
+
+[^18]: Working under this theory, the Field commission defined the content of the modern field of *civil procedure*.
+While western legal systems had long distinguished between the law of persons and things on the one hand, and the law of actions (the rules of litigation) on the other, in the Anglo-American tradition, the categories remained intermixed into the nineteenth century.
+Whether one had a substantive legal right (to property, to marry, to an office, etc.) depended upon whether and how one would sue for a remedy to vindicate that right.
+Blackstone's *Commentaries* attempted to describe English law in the more European terms of persons/things/actions, and Jeremy Bentham offered a more refined terminology of "substantive" law and "procedural" or "adjective" law, but until the Field Code no Anglo-American jurist had specified with precision where the line lay between substantive and procedural law.
+See Lobban, *The Common Law and English Jurisprudence*, 127--131, 146--151.
+As Amalia Kessler notes, *Bouvier's Law Dictionary* did not even define *civil procedure* until its 1897 edition, describing the term as "rather a modern one." Amalia Kessler, "Deciding Against Conciliation: The Nineteenth-Century Rejection of a European Transplant and the Rise of a Distinctively American Ideal of Adversarial Adjudication," 10 *Theoretical Inquiries in Law* 423 (2009), 481--482; *Bouvier's Law Dictionary* (1897), 2:764.
+Before 1848, the term was largely restricted to French usage, and American remedial law had carried the typical designation---as it did both in Graham's treatise and professorial title---of "practice and pleadings," the name likewise given to the reform commission.
+When the commission designated its final draft a "Code of Civil Procedure," it marked the first American attempt to give content to this category.
+
+[^19]: Final Report of the Commissioners, 368--378, tit.
+10.
+See also Peter Karsten, "Enabling the Poor to Have Their Day in Court: The Sanctioning of Contingency Fee Contracts, A History to 1940," 47 *DePaul Law Review* 231 (1998); Norman Spaulding, "The Luxury of the Law: The Codification Movement and the Right to Counsel," 73 *Fordham Law Review* 983 (2004) John Leubsdorf, "Toward a History of the American Rule on Attorney Fee Recovery," 47 *Law and Contemporary Problems* 9 (1984).
+
+[^20]: On debt collection, see Part 4 below.
+On homestead exemptions, see Final Report of the Commissioners, 353--354, § 839; James W.
+Ely, "Homestead Exemption and Southern Legal Culture," in Sally Hadden & Patricia Minter eds., *Signposts: New Directions in Southern Legal History* (University of Georgia 2013), 289--314; Paul Goodman, "The Emergence of Homestead Exemption in the United States: Accommodation and Resistance to the Market Revolution, 1840--1880," 80 *Journal of American History* 470 (1993).
+
+[^21]: Final Report of the Commissioners, 202--203, § 506 (restricting admission as an attorney to male citizens), 110, § 251 (restricting jury service to white male citizens), 714--715, § 1708 (permitting "all persons, without exceptions" to be witnesses in civil cases).
+
+[^22]: On the French procedure code, see C.H.
+van Rhee, *European Traditions in Civil Procedure* (Antwerp 2005).
+Bentham, the leading proponent of codification in England, argued that procedure was the one department of the law that ought to remain *un*codified.
+So long as the law of civil and criminal obligations and the law of property were sufficiently codified, a "natural procedure" arising from judicial discretion and flexibility would be superior to "technical" written rules.
+Later in his career Bentham produced the "Outlines of a Procedure Code" as a "provisional" remedy, but he insisted that a procedure code on its own could not be "invested with the form of law" without "reference to the codes of law, penal and non-penal, to which it has for its object and purpose the giving execution and effect." Although it spanned nearly 200 pages, Bentham's code favored general moral maxims over precise details, for instance: "On each occasion, have constant regard for all the several ends of justice; that is to say, minimize the sum, or the balance of evil." Jeremy Bentham, Principles of Judicial Procedure with the Outline of a Procedure Code, in John Bowring, ed., *Works of Jeremy Bentham* (2d.
+ed.
+1843 \[1839\]), 1--189, preface and 28, ch.
+7 § 1.
+See Lobban, *The Common Law*, 127--131.
+
+[^23]: See Revised Statutes of the State of Indiana (1852), 2:245--320 (wills); Public Statutes of the State of Minnesota (1859), 643--647, ch.
+75 (mortgages); The Code of Civil Procedure of the State of California (1880), 419--420, tit.
+6, 657--659, art.
+5 (corporations).
+
+[^24]: Report of the Code Commissioners to the Eighth General Assembly of the State of Iowa (1859), 296, note to § 172 ("The right to sue, follows necessarily from the right of property.") On the significance of the Married Women's Property Acts, see, e.g., Hendrik Hartog, *Man and Wife in America: A History* (Harvard 2000), 111--113, 187--192, 290--292.
+
+[^25]: First Report of the Commissioners, iv. For legislative debates on the Code, see "Legislative Acts and Proceedings," *Albany Evening Journal*, Mar. 31, 1848.
+
+[^26]: Report of the Committee on the Judiciary on the Bill to Continue in Office the Commissioners on Practice and Pleadings, in New York Assembly Documents, 72d sess., vol.
+3, no.
+47, (New York 1849), 2, 12--15.
+
+[^27]: Final Report of the Commissioners, 225--226, § 554.
+For examples of "codes" that did not alter previously enacted statutes, see, for instance, Report, Appendix to the Journals of the Senate and Assembly of the State of Tennessee (1857), 191 ("The digest presents the law substantially as it now exists in the State.
+I have neither felt at liberty nor deemed it advisable to innovate largely upon the established system."); 1897 New Mexico Compiled Laws 9 ("The commissioners were given no authority to revise."); 1866 Illinois Compiled Laws v ("We cannot change the text, but we can arrange and systematize the entire legislation of the state upon any given subject."); 1849 Wisconsin Revised Statutes, "Advertisement" (commission "directed the subscriber to arrange the chapters into parts and titles as he thought proper, re-arranging the order of the sections or transposing them from one chapter to another, whenever it would not alter the meaning of the law.").
+
+[^28]: *Montana Post*, January 21, 1865.
+
+[^29]: *The Miner's Express* (Dubuque), February 26, 1851.
+
+[^30]: Full citations to all of the codes that we used, plus links to electronic versions at the Hathi Trust, Google Books or other sources when available are available at Kellen Funk, *American Legislation Project* (2015--): <http://kellenfunk.org/legislation>.
+
+[^31]: We have preferred to use the term "digital history" when referring to our own work, in part because the term "digital humanities" has largely come to refer to the work of digital literary and digital media scholars, but primarily because we wish to see digital scholars make disciplinary, rather than interdisciplinary contributions.
+On the role of disciplines and the importance of field specific argumentation, see, Stephen Robertson, "The Differences between Digital Humanities and Digital History," 289--307, and Cameron Blevins, "Digital History's Perpetual Future Tense," 308--324, both in *Debates in the Digital Humanities 2016*, ed.
+Matthew K.
+Gold and Lauren F.
+Klein (Minneapolis: University of Minnesota Press, 2016).
+Nevertheless, digital text analysis in the humanities has mostly been published by literary scholars, including Stephen Ramsay, *Reading Machines: Toward an Algorithmic Criticism* (Urbana: University of Illinois Press, 2011); Franco Moretti, *Distant Reading* (New York: Verso, 2013); Matthew L.
+Jockers, *Macroanalysis: Digital Methods and Literary History* (Urbana: University of Illinois Press, 2013); Ted Underwood, *Why Literary Periods Mattered: Historical Contrast and the Prestige of English Studies* (Stanford: Stanford University Press, 2013); Ryan Cordell and David A.
+Smith, *Viral Texts: Mapping Networks of Reprinting in 19th-Century Newspapers and Magazines*, NULab for Texts Maps and Networks, Northeastern University (2012--): <http://viraltexts.org>.
+Related but less well regarded by humanities scholars is work in "culturomics": see Jean-Baptiste Michel et al., "Quantitative Analysis of Culture Using Millions of Digitized Books", *Science* 331, no.
+6014 (2011), 176--182; doi:10.1126/science.1199644.
+On the uselessness of the term "big data," see Ted Underwood, "Against (Talking About) 'Big Data,'" *The Stone and the Shell*, blog post, 10 May 2013: <https://tedunderwood.com/2013/05/10/why-it-matters-that-we-dont-know-what-we-mean-by-big-data/>.
+For an example of curating a corpus aimed at research questions, see Ted Underwood, Boris Capitanu, Peter Organisciak, Sayan Bhattacharyya, Loretta Auvil, Colleen Fallaw, J.
+Stephen Downie, "Word Frequencies in English-Language Literature, 1700--1922," dataset, v0.2 (HathiTrust Research Center, 2015) doi:10.13012/J8JW8BSJ.
+
+    Only a few scholars have turned their attention to the computer analysis of legal texts for historical purposes, including Paul Craven, "Detección automática y visualización de dominios específicos similares en documentos: análisis DWIC y su aplicación en el Proyecto Master & Servant \[Automatic Detection and Visualization of Domain-Specific Similarities in Documents: DWIC Analysis and its Application in the Master & Servant Project\]," published on CD-ROM in F.
+J.
+A Perez et al., eds., *La Historia en una nueva frontera \[History in a New Frontier\]* (Digibis: Ediciones de la Universidad de Castilla-La Mancha, 1998); Paul Craven and Douglas Hay, "Computer Applications in Comparative Historical Research: The Master & Servant Project at York University, Canada," *History and Computing* 7, no.
+2 (1995); Paul Craven and W.
+Traves, "A General-Purpose Hierarchical Coding Engine and Its Application to Comparative Analysis of Statutes," *Literary and Linguistic Computing* 8, no.
+1 (1993): 27--32, doi:10.1093/llc/8.1.27; Eric C.
+Nystrom and David S.
+Tanenhaus, "The Future of Digital Legal History: No Magic, No Silver Bullets," *American Journal of Legal History* 56, no.
+1 (2016): 150--67, doi:10.1093/ajlh/njv017; Dan Cohen, Frederick Gibbs, Tim Hitchcock, Geoffrey Rockwell, et al., "Data Mining with Criminal Intent," white paper, 31 August 2011, <http://criminalintent.org>.
+
+[^32]: In each instance we downloaded an entire volume of sessions laws, statutory compilations, or single-volume codes of procedure and then cropped out irrelevant pages, marginalia and footnoted commentary, leaving only the statutory text.
+After several trials of various implementations of Tesseract (open source) and I.R.I.S.
+(proprietary) OCR programs, we determined that Nitro Pro PDF, which relies on I.R.I.S.
+software, offered the best OCR tool for this project.
+I.R.I.S.
+provides slightly more accurate readings of nineteenth-century typefaces than Tesseract, and Nitro Pro's implementation makes words, not characters, the fundamental unit of output.
+The latter feature made cropping between marginalia and the statute more reliable.
+We removed hyphenated line breaks and standardized spelling for common terms that evolved over the nineteenth century (e.g., *indorsement*).
+
+[^33]: William Wirt Blume, "Adoption in California of the Field Code of Civil Procedure: A Chapter in American Legal History," 17 *Hastings Law Journal* 701 (1966); Stephen J.
+Field, *Personal Reminiscences of Early Days in California* (1893), 75--78.
+
+[^34]: The formal definition of the Jaccard similarity for two sets, $A$ and $B$, is $J(A, B) = \frac{ | A \cap B | }{ | A \cup B | }$.
+
+[^35]: We implemented LSH as described in Jure Leskovec, Anand Rajaraman, and Jeff Ullman, *Mining of Massive Datasets*, 2nd ed.
+(Cambridge University Press, 2014), ch.
+3, <http://www.mmds.org>; the algorithm was first described in Andrei Z.
+Broder, "On the Resemblance and Containment of Documents," in *Compression and Complexity of Sequences 1997: Proceedings*, (IEEE, 1997): 21--29, <http://gatekeeper.dec.com/ftp/pub/dec/SRC/publications/broder/positano-final-wpnums.pdf>.
+Other digital humanities projects, most notably *Viral Texts*, have used other means for detecting text reuse.
+The most prominent of these are algorithms for sequence alignment.
+(Our "textreuse" package for R also implements the Smith-Waterman local sequencing algorithm, derived from gene sequencing.) Yet the older and simpler LSH algorithm sufficed for our purposes because legal sources are easily divided into discrete sections which can be treated as independent documents.
+For other approaches, see David Bamman and Gregory Crane, "Discovering Multilingual Text Reuse in Literary Texts," white Paper, Perseus Digital Library (2009): <http://www.perseus.tufts.edu/publications/2009-Bamman.pdf>; Timothy Allen, Charles Cooney, Stéphane Douard, et al., "Plundering Philosophers: Identifying Sources of the Encyclopédie," *Journal of the Association for History and Computing* 13, no.
+1 (2010): <http://hdl.handle.net/2027/spo.3310410.0013.107>; Glenn Roe, Russell Horton, and Mark Olsen, "Something Borrowed: Sequence Alignment and the Identification of Similar Passages in Large Text Collections," *Digital Studies / Le Champ numérique* 2, no.
+1 (2010): <http://www.digitalstudies.org/ojs/index.php/digital_studies/article/view/190/235>; David A.
+Smith, Ryan Cordell, and Elizabeth Maddock Dillon, "Infectious Texts: Modeling Text Reuse in Nineteenth-Century Newspapers," in *2013 IEEE International Conference on Big Data*, 2013, 86--94, doi:10.1109/BigData.2013.6691675; David A.
+Smith, Ryan Cordell, Elizabeth Maddock Dillon, et al., "Detecting and Modeling Local Text Reuse," *Proceedings of IEEE/ACM Joint Conference on Digital Libraries* (IEEE Computer Society Press, 2014); Christopher Forstall, Neil Coffee, Thomas Buck, Katherine Roache, and Sarah Jacobson, "Modeling the scholars: Detecting Intertextuality through Enhanced Word-level N-gram Matching" *Digital Scholarship in the Humanities* 30, no.
+4 (2015): 503--515; Douglas Ernest Duhaime, "Textual Reuse in the Eighteenth Century: Mining Eliza Haywood's Quotations," *Digital Humanities Quarterly* 10, no.
+1 (2016): <http://www.digitalhumanities.org/dhq/vol/10/1/000229/000229.html>.
+
+[^36]: We filtered this matrix based on what we knew about the process of borrowing.
+We removed any match below a threshold that we determined by reading pairs of matches.
+Because Jaccard similarity scores are symmetric, we also removed anachronistic matches.
+For instance, a code from 1851 obviously did not borrow from a code from 1877.
+Furthermore, in chains of borrowing (e.g., NY1850 to CA1851 to CA1868 to CA1872 to MT1895) the latest section might have a high similarity to all of its ancestors, but it was in fact borrowed only from the most recent parent.
+We therefore filtered the similarity matrix to remove matches within the same code; anachronistic matches; spurious matches beneath a certain threshold.
+Then if a section had multiple matches, we kept the match from the chronologically closest code, giving preference to codes from the same state, unless there was a substantially closer match from a different code.
+
+[^37]: We have released two repositories with all the code used for this project.
+Lincoln Mullen, "textreuse: Detect Text Reuse and Document Similarity," R package version 0.1.3 (2015--): <https://github.com/ropensci/textreuse>, includes the LSH and other algorithms that we used for general purpose application.
+(This package was peer-reviewed by rOpenSci, a collective of academic developers who use the R programming language.) A second repository contains all of our code specific to the migration of the Field Code: <https://github.com/lmullen/civil-procedure-codes/>.
+
+[^38]: Our attention to big and small scales is the main aim described in Shawn Graham, Ian Milligan, and Scott Weingart, *Exploring Big Historical Data: The Historian’s Macroscope* (Imperial College Press, 2015).
+
+[^39]: That New York codes are central is obvious from the visualization, but we also confirmed this by formal measures of centrality used in network analysis.
+A network is simply a list of edges (in our case the number of sections borrowed) between nodes (in our case, the codes).
+Because even our efforts at determining the best match for each section sometimes attributed a section to an incorrect code, we pruned the edges of the graph so that each code was connected to another code only if it borrowed at least fifty sections or twenty percent of its sections.
+
+    Within New York there was a definite chronological progression from the 1848, 1849, 1850, 1851, and 1853 versions of the code, but the development was not chronologically linear.
+The state legislature enacted the 1848, 1849, and 1851 codes, and these show strong similarities in their relationships.
+The 1850 and 1853 versions were David Dudley Field's ideal drafts of the code which were never enacted.
+They were, however, printed with wide margins, quality typesetting, and---in the 1850 draft---extensive explanatory notes, all with an eye towards other jurisdictions copying them as a model.
+Those two codes show stronger similarity to one another than to the enacted drafts.
+
+[^40]: David Dudley Field, The Latest Edition of the New York Code of Civil Procedure (1878), 21.
+
+[^41]: Non-Field jurisdictions occasionally exhibited a borrowing relationship within a state or across two states.
+In in a few unusual instances they contributed to codes which were derived from the Field Code.
+For example, Alabama's 1852 Code provided a few sections to Tennessee's 1858 code, and some states like Wisconsin copied, along with the Field Code, large passages of pre-code legislation from earlier in the state's history.
+
+[^42]: Final Report (New York, 1850), §§ 804--809, compared to 1851 California Laws 260, §§ 439--441.
+
+[^43]: Brendan J.
+Frey and Delbert Dueck, "Clustering by Passing Messages Between Data Points," *Science* 315 (2007): 972--976, doi: 10.1126/science.1136800; Ulrich Bodenhofer, Andreas Kothmeier, and Sepp Hochreiter, "APCluster: an R package for affinity propagation clustering," *Bioinformatics* 27 (2011): 2463--2464, doi:10.1093/bioinformatics/btr406.
+Even though the affinity propagation algorithm did not fully converge with our dataset, it did an adequate job clustering the documents.
+Because there was an exemplar section for each cluster, we were able to merge clusters whose exemplars had a high Jaccard similarity score.
+
+[^44]: Samuels, Lisa, and Jerome McGann.
+"Deformance and Interpretation." *New Literary History* 30.1 (1999): 25--56; Mark Sample, "Notes toward a Deformed Humanities," blog post, 2 May 2012: <http://www.samplereality.com/2012/05/02/notes-towards-a-deformed-humanities/>; Ramsay, *Reading Machines*, 32--57.
+
+[^45]: First Report (New York, 1848), 197.
+
+[^46]: Those jurisdictions were Nevada (1861), Dakota Territory---which retained the Code when split into North and South (1862), Idaho (1864), Arizona (1864), Montana (1865), Arkansas (1868), North Carolina (1868), Wyoming (1869), Florida (1870), South Carolina (1870), Utah (1870), and Colorado (1877).
+
+[^47]: Elliott West, "Reconstructing Race," 34 *Western Historical Quarterly* 6 (2003).
+See also Heather Cox Richardson, *West from Appomattox: The Reconstruction of America after the Civil War* (New Haven: Yale University Press, 2007); Sven Beckert, *Monied Metropolis: New York City and the Consolidation of the American Bourgeoisie, 1850--1896* (Harvard 2003); Mark Wahlgren Summers, *The Ordeal of the Reunion: A New History of Reconstruction* (Chapel Hill: University of North Carolina Press, 2014).
+The major application of the Greater Reconstruction idea to legal history has been Sarah Barringer Gordon, *The Mormon Question: Polygamy and Constitutional Conflict in Nineteenth-Century America* (Chapel Hill: University of North Carolina Press, 2003).
+
+[^48]: See, for instance, Rogers Smith, *Civic Ideals: Conflicting Visions of Citizenship in U.S.
+History* (Yale 1999); Meg Jacobs, William J.
+Novak, and Julian E.
+Zelizer, eds., *The Democratic Experiment: New Directions in American Political History* (Princeton 2003); Edward Purcell, *Litigation and Inequality: Federal Diversity Jurisdiction in Industrial America, 1870--1958* (Oxford 1992).
+
+[^49]: Naomi Lamoreaux and John Joseph Wallis, "States, Not Nation: The Sources of Political and Economic Development in the Early United States," Paper Presented at the Economic History Workshop, Harvard University, March 4, 2016.
+
+[^50]: For instance, although Tennessee in 1858 adapted nearly 225 sections of its code from Field codes, the state also incorporated nearly 50 sections of the 1852 Code of Alabama, one of the largest borrowings of southern legislation within the corpus we collected.
+
+[^51]: See Charles E.
+Clark, "The New Illinois Civil Practice Act," *University of Chicago Law Review* 1 (1933): 209.
+Nevertheless, even Illinois had substantial legislation organizing the courts and prescribing certain common law processes for obtaining civil remedies, and Colorado adapted the bulk of this legislation when it organized as a territory, a full seventeen years before its legislature considered adopting the Field Code.
+
+[^52]: Journal of the Assembly of the Territory of Utah (1870), 15.
+See also Leonard J.
+Arrington, *Great Basin Kingdom: An Economic History of the Latter-Day Saints, 1830--1900*, new edition (University of Illinois Press, 2004).
+
+[^53]: "The Code Again," *Pueblo Daily Chieftain*, February 25, 1877.
+
+[^54]: "The Legislature: The Senate Devotes Another Day to the Code," *Denver Daily Tribune*, February 17, 1877.
+
+[^55]: Governor's Message, in Journal of the House of Assembly of the Territory of Nebraska (1857), 12.
+
+[^56]: William A.
+Jenkins to William Blount Rodman, January 14, 1868, Rodman Papers.
+East Carolina University Library, Special Collections.
+Rodman's explication of the Code appeared in three sequentially numbered articles in the *Standard* on August 14, 15, and 16, 1868, under the title "The Code of Civil Procedure." Rodman disclosed his authorship in private correspondence with Barringer.
+See Barringer to Rodman, August 21, 1868, Rodman Papers.
+
+[^57]: Gordon Morris Bakken, *Practicing Law in Frontier California* (Nebraska 1991), 51--54.
+The new western history ushered in by Patricia Nelson Limerick, *The Legacy of Conquest: The Unbroken Past of the American West* (Norton 1987) and Richard White, *"It's Your Misfortune and None of My Own": A History of the American West* (Oklahoma 1991) is now returning to issues of political economy.
+See Patricia Nelson Limerick, *A Ditch in Time: The City, the West, and Water* (Fulcrum 2012); Richard White, *Railroaded: The Transcontinentals and the Making of Modern America* (Norton 2011).
+
+[^58]: "The Code," *Denver Daily Tribune*, January 10, 1877; "The Code," *Denver Daily Times*, January 27, 1877.
+
+[^59]: "A Code of Civil Procedure," *Denver Daily Times*, January 12, 1877.
+
+[^60]: "The Code," *Denver Daily Tribune*, January 31, 1877.
+
+[^61]: See Gunther A.
+Weiss, "The Enchantment of Codification in the Common-Law World," 25 *Yale Journal of International Law* 435 (2000).
+For a thorough study of the ideology of codification in India, see Robert A.
+Yelle, *The Language of Disenchantment: Protestant Literalism and Colonial Discourse in British India* (Oxford: Oxford University Press, 2012).
+
+[^62]: See, for instance, James C.
+Carter's classic defense of the common law against codification, The Ideal and the Actual in the Law, Address to the American Bar Association, August 21, 1890, at 28 ("the legislature should never attempt to perform the function of the judge, that of simply ascertaining and declaring existing customs.
+This is the work of experts who can qualify themselves only by the devotion of their lives.").
+
+[^63]: See, for instance, "Note," 29 *Albany Law Journal* 141, 142 (1884); Millar, *Civil Procedure of the Trial Court*, 55--56.
+
+[^64]: 19 *Hansard Parliamentary Debates* 531.
+
+[^65]: Texas commissioned the preparation of a code of civil procedure in 1855, and the legislature scheduled an extra session to consider it but ultimately never passed the law.
+21 *Texas Reports* (Hartley) xi (1882); *Texas State Times*, December 15, 1855.
+Reformers in the 1869 convention in Illinois attempted to pass a provision similar to the one in New York's 1846 constitution, which would have required the legislature to appoint a commission to revise practice and pleadings along the lines of the Field Code.
+See *Debates and Proceedings of the Constitutional Convention of the State of Illinois* (1870), 1496--1498.
+
+[^66]: "The Code," *Weekly Standard* (Raleigh), May 26, 1869.
+
+[^67]: See, for instance, the summary of the states-as-laboratories literature in Brian Galle & Joseph Leahy, "Laboratories of Democracy?
+Policy Innovation in Decentralized Governments," 58 *Emory Law Journal* 1333 (2009).
+
+[^68]: See Daniel Ernst, *Tocqueville's Nightmare: The Administrative State Emerges in America, 1900--1940* (Oxford: Oxford University Press, 2014); Jerry L.
+Mashaw, *Creating the Administrative Constitution: The Lost One Hundred Years of American Administrative Law* (Yale Law Library 2012); Gautham Rao, *National Duties: Custom Houses and the Making of the American State* (University of Chicago 2016).
 
@@
 IL 1866    | A negro, mulatto or Indian shall not be a witness in any court, or in any case, against a white person. Any person having one-fourth part negro blood shall be adjudged a mulatto.
-
-[^1]: Message of the Governor, in Journal of the Council for the Territory of Nevada (1862), 21.
-
-[^2]: Nevada Council Journal (1862), 261-62. Act of Congress (1861) Organizing the Territory of Nevada, 12 U.S. Statutes at Large 209-14 (1863). 1861 Nevada Laws 314.
-
-[^3]: Besides his work on codification, which extended to civil, penal, and even international codes of law, Field became renown for his trial advocacy.
-Field argued the winning side in major Reconstruction cases such as *Ex Parte Milligan*, 71 U.S.
-(4 Wall.) 2 (1866) (holding the trial of civilians by military commission unconstitutional), *Cummings v.
-Missouri*, 71 U.S.
-(4 Wall.) 277 (1867) (striking a loyalty oath as unconstitutional), and *United States v.
-Cruikshank*, 92 U.S.
-542 (1875) (enforcing the Fourteenth Amendment only against "state action").
-Field came under heavy censure for his representation of Gilded Age robber barons like Jay Gould, Jim Fisk, and William "Boss" Tweed, but even Tweed's chief adversary Samuel Tilden retained Field's services for the disputed election of 1876.
-See Henry Martyn Field, *The Life of David Dudley Field* (1898); Philip J.
-Bergan, "David Dudley Field: A Lawyer's Life," in *The Fields and the Law* (New York: Federal Bar Council, 1986).
-
-[^4]: *Rocky Mountain News*, January 20, 1877.
-
-[^5]: Roscoe Pound, "David Dudley Field: An Appraisal," and Alison Reppy, "The Field Codification Concept," in Alison Reppy, ed., *David Dudley Field: Centenary Essays* (New York University School of Law, 1949); Stephen Subrin, "David Dudley Field and the Field Code: A Historical Analysis of an Earlier Procedural Vision," 6 *Law & Hist.
-Rev*.
-311 (1988); Robert G.
-Bone, "Mapping the Boundaries of a Dispute: Conceptions of Ideal Lawsuit Structure from the Field Code to the Federal Rules," 89 *Colum.
-L.
-Rev*.
-1 (1989).
-See also the literature on procedure and codification cited below.
-
-[^6]: When law professors such as New York's David Graham Jr.
-(a collaborator on the Field Code) began to be appointed to university positions, the chair for instruction in legal practice or procedure carried this designation of "practice and pleadings." Today that field is described as "civil procedure" a field that grew out of David Dudley Field's codification, as described below.
-The history of practice and procedure is a staple of general legal history.
-See Frederick Pollock and Frederick Maitland, *The History of English Law Before the Time of Edward I* (2d.
-ed., Cambridge, 1898), 2 vols.; Theodore Plucknett, *A Concise History of the Common Law* (5th ed.
-2010); Lawrence M.
-Friedman, *A History of American Law* (3d.
-ed.
-2005).
-Few book-length works have been dedicated to the subject, however.
-The exceptions are Robert Wyness Millar, *Civil Procedure of the Trial Court in Historical Perspective* (New York University School of Law 1952); Edward Purcell, *Litigation and Inequality: Federal Diversity Jurisdiction in Industrial America, 1870-1958* (Oxford 1992); John H.
-Langbein et al., *History of the Common Law: The Development of Anglo-American Legal Institutions* (Aspen 2009); and to some extent, William E.
-Nelson, *The Americanization of the Common Law: The Impact of Legal Change on Massachusetts Society, 1760-1830* (2d.
-ed., University of Georgia Press 1994).
-
-[^7]: For the rise of treatises in America generally, see G.
-Edward White, *The Marshall Court and Cultural Change, 1815--1835* (1988) and A.
-W.
-B.
-Simpson, "The Rise and Fall of the Legal Treatise: Legal Principles and the Forms of Legal Literature," in *Legal Theory and Legal History: Essays on the Common Law* (London: Hambledon Press, 1987), 273--320.
-The most instructive treatises for New York practice in the 1840s were Oliver L.
-Barbour, *A Treatise on the Practice of the Court of Chancery* (1844); Alexander M.
-Burrill, *Treatise on the Practice of the Supreme Court of the State of New York* (1846), 2 vols.; David Graham, *A Treatise on on the Practice of the Supreme Court of the State of New York* (3d.
-ed.
-1847); David Graham, *A Treatise on the Organization and Jurisdiction of the Courts of Law and Equity in the State of New York* (1839); Claudius L.
-Monell, *A Treatise on the Practice of the Supreme Court of the State of New York* (1849); Joseph W.
-Moulton, *The Chancery Practice of the State of New York* (1829), 2 vols.; and as a general introduction to the field, the Englishman Henry John Stephen's *Treatise on the Principles of Pleading in Civil Actions* (2d.
-ed.
-1828).
-
-[^8]: See Michael Lobban, *The Common Law and English Jurisprudence 1760-1850* (Clarendon Press 1991); Kunal M.
-Parker, *Common Law, History, and Democracy in America, 1790-1900: Legal Thought before Modernism* (Cambridge: Cambridge University Press, 2011); David M.
-Rabban, *Law's History: American Legal Thought and the Transatlantic Turn to History* (Cambridge 2013).
-
-[^9]: Or, to use a term from contemporary analysis, "super statutes." William N.
-Eskridge and John Ferejohn, *A Republic of Statutes: The New American Constitution* (New Haven: Yale University Press, 2010).
-See also David Lieberman, *The Province of Legislation Determined: Legal Theory in Eighteenth-century Britain* (Cambridge 1989); Farah Peterson, Statutory Interpretation and Judicial Authority, 1776-1860 (Ph.D.
-dissertation, Princeton University, September 2015).
-
-[^10]: Friedman, *A History of American Law*, 302.
-When the intellectual historian Perry Miller developed a reader surveying *The Legal Mind in America*, codification was its only central theme, as Miller argued it was the one intellectual topic that attracted lawyers away from their practices long enough to debate.
-Perry Miller, ed., *The Legal Mind in America: From Independence to the Civil War* (Anchor 1962).
-See also Charles M.
-Cook, *The American Codification Movement: A Study in Antebellum Legal Reform* (1983); Robert W.
-Gordon, "The American Codification Movement," 36 *Vanderbilt Law Review* 431 (1983); Maurice Eugen Lang, *Codification in the British Empire and America* (Lawbook Exchange 1924).
-On common theories of codification that transcended jurisdictional boundaries, see Csaba Varga, *Codification as a Socio-Historical Phenomenon* (Budapest, 2d.
-ed.
-2011 \[1991\]); Roger Berkowitz, *The Gift of Science: Leibniz and the Modern Legal Tradition* (Fordham 2010).
-
-[^11]: The most influential account has been Morton Horwitz's, which declares that "the desire to separate law and politics has always been a central aspiration of the American legal profession" in order to protect elite interests against popular democracy.
-Horwitz identifies "orthodox legal thought" and "orthodox lawyers" with the elite of the American bar who sought to shield the law from political interference, which above all meant crusading against legislation and especially codification.
-Morton J.
-Horwitz, *The Transformation of American Law, 1780-1850* (Oxford University Press, 1977), 258-59.
-Recent work has challenged Horwitz's account by showing how elite common law lawyers, particularly Horwitz's main target James Coolidge Carter, were actually political progressives who supported redistributive legislation such as the income tax.
-See, for instance, Rabban, *Law's History*, 322-77; Parker, *Common Law, History, and Democracy*, 230-41; Lewis A.
-Grossman, "James Coolidge Carter and Mugwump Jurisprudence," *Law & History Review* 20 (2002).
-These accounts follow Horwitz, however, in focusing on the few outspoken opponents of codification, rather than the elite lawyers who sponsored the procedure codes.
-Among the latter group could be found some of the most devout theorists of laissez faire economics in nineteenth-century America, including David Dudley Field and his brother, the Supreme Court Justice Stephen Johnson Field.
-
-[^12]: James Fenimore Cooper, *The Ways of the Hour: A Tale* (1850), 84.
-For an analysis of Cooper's philosophy of law and his critique of the New York constitution, see Charles Hansford Adams, *"The Guardian of the Law": Authority and Identity in James Fenimore Cooper* (Penn State University Press (1990), 135-48.
-See also Marvin Meyers, *The Jacksonian Persuasion: Politics and Belief* (Stanford 1957), 57-100.
-
-[^13]: On the politics and reforms of the New York Convention of 1846, see Charles Z.
-Lincoln, *The Constitutional History of New York from the Beginning of the Colonial Period to the Year 1905* (Rochester 1905), 2:10-101; Charles McCurdy, *The Anti-Rent Era in New York Law and Politics, 1839-1865* (University of North Carolina 2001); Jed Shugerman, *The People's Courts: The Rise of Judicial Elections and Judicial Power in America* (Harvard University Press 2012).
-
-[^14]: Count Pierre François Réal to William Sampson, October 27, 1824, in Sampson's Discourse and Correspondence with Various Learned Jurists Upon the History of the Law (1826), 191; Maxwell Bloomfield, "William Sampson and the Codifiers: The Roots of American Legal Reform," 11 *American Journal of Legal History* 234 (1967); Walter J.
-Walsh, "William Sampson, a Republican Constitution, and the Conundrum of Orangeism on American Soil, 1824-1831," 5/7 *Radharc* 1 (2006); William Sampson, *Memoirs* (2d.
-ed., 1817).
-On French-style codifications, see Robert B.
-Holtman, *The Napoleonic Revolution* (Louisiana State 1981); R.
-H.
-Kilbourne, *A History of the Louisiana Civil Code* (Paul M.
-Herbert Law Center 1987); Brian Young, *The Politics of Codification: The Lower Canadian Civil Code of 1866* (Osgoode Society 1994); John W.
-Cairns, *Codification, Transplants, and History: Law Reform in Louisiana (1808) and Quebec (1866)* (Talbot 2015); Roscoe Pound, "The French Civil Code and the Spirit of Nineteenth Century Law," 35 *Boston Law Review* 79 (1955).
-
-[^15]: Thomas J.
-Lockwood, "A History of Royal Commissions," 5 *Osgoode Hall Law Journal* 172 (1967); Barbara Lauriat, "'The Examination of Everything': Royal Commissions in British Legal History," 31 *Statute Law Review* 24 (2010); Joanna Innes, *Inferior Politics: Social Problems and Social Policies in Eighteenth-century Britain* (Oxford 2009).
-
-[^16]: Second Report of the Commissioners on Practice and Pleading (New York 1849), 3-4.
-See also, First Report of the Commissioners on Practice and Pleadings (New York 1848), iii-iv; Third Report of the Commissioners on Practice and Pleadings (New York 1849), 3, Lillian Goldman Law Library Rare Books Collection; Final Report of the Commissioners on Practice and Pleadings, in Documents of the Assembly of the State of New York, 73d sess., vol.
-2, no.
-16 (New York 1850), viii.
-
-[^17]: Report of the Commissioners on Practice and Pleadings, in New York Assembly Documents, 70th sess., vol. 2, no. 202 (1847), 3-4.
-
-[^18]: Working under this theory, the Field commission defined the content of the modern field of *civil procedure*.
-While western legal systems had long distinguished between the law of persons and things on the one hand, and the law of actions (the rules of litigation) on the other, in the Anglo-American tradition, the categories remained intermixed into the nineteenth century.
-Whether one had a substantive legal right (to property, to marry, to an office, etc.) depended upon whether and how one would sue for a remedy to vindicate that right.
-Blackstone's *Commentaries* attempted to describe English law in the more European terms of persons/things/actions, and Jeremy Bentham offered a more refined terminology of "substantive" law and "procedural" or "adjective" law, but until the Field Code no Anglo-American jurist had specified with precision where the line lay between substantive and procedural law.
-See Lobban, *The Common Law and English Jurisprudence*, 127-131, 146-151.
-As Amalia Kessler notes, *Bouvier's Law Dictionary* did not even define *civil procedure* until its 1897 edition, describing the term as "rather a modern one." Amalia Kessler, "Deciding Against Conciliation: The Nineteenth-Century Rejection of a European Transplant and the Rise of a Distinctively American Ideal of Adversarial Adjudication," 10 *Theoretical Inquiries in Law* 423 (2009), 481-482; *Bouvier's Law Dictionary* (1897), 2:764.
-Before 1848, the term was largely restricted to French usage, and American remedial law had carried the typical designation---as it did both in Graham's treatise and professorial title---of "practice and pleadings," the name likewise given to the reform commission.
-When the commission designated its final draft a "Code of Civil Procedure," it marked the first American attempt to give content to this category.
-
-[^19]: Final Report of the Commissioners, 368-378, tit.
-10.
-See also Peter Karsten, "Enabling the Poor to Have Their Day in Court: The Sanctioning of Contingency Fee Contracts, A History to 1940," 47 *DePaul Law Review* 231 (1998); Norman Spaulding, "The Luxury of the Law: The Codification Movement and the Right to Counsel," 73 *Fordham Law Review* 983 (2004) John Leubsdorf, "Toward a History of the American Rule on Attorney Fee Recovery," 47 *Law and Contemporary Problems* 9 (1984).
-
-[^20]: On debt collection, see Part 4 below.
-On homestead exemptions, see Final Report of the Commissioners, 353-354, § 839; James W.
-Ely, "Homestead Exemption and Southern Legal Culture," in Sally Hadden & Patricia Minter eds., *Signposts: New Directions in Southern Legal History* (University of Georgia 2013), 289-314; Paul Goodman, "The Emergence of Homestead Exemption in the United States: Accommodation and Resistance to the Market Revolution, 1840-1880," 80 *Journal of American History* 470 (1993).
-
-[^21]: Final Report of the Commissioners, 202-203, § 506 (restricting admission as an attorney to male citizens), 110, § 251 (restricting jury service to white male citizens), 714-715, § 1708 (permitting "all persons, without exceptions" to be witnesses in civil cases).
-
-[^22]: On the French procedure code, see C.H.
-van Rhee, *European Traditions in Civil Procedure* (Antwerp 2005).
-Bentham, the leading proponent of codification in England, argued that procedure was the one department of the law that ought to remain *un*codified.
-So long as the law of civil and criminal obligations and the law of property were sufficiently codified, a "natural procedure" arising from judicial discretion and flexibility would be superior to "technical" written rules.
-Later in his career Bentham produced the "Outlines of a Procedure Code" as a "provisional" remedy, but he insisted that a procedure code on its own could not be "invested with the form of law" without "reference to the codes of law, penal and non-penal, to which it has for its object and purpose the giving execution and effect." Although it spanned nearly 200 pages, Bentham's code favored general moral maxims over precise details, for instance: "On each occasion, have constant regard for all the several ends of justice; that is to say, minimize the sum, or the balance of evil." Jeremy Bentham, Principles of Judicial Procedure with the Outline of a Procedure Code, in John Bowring, ed., *Works of Jeremy Bentham* (2d.
-ed.
-1843 \[1839\]), 1-189, preface and 28, ch.
-7 § 1.
-See Lobban, *The Common Law*, 127-131.
-
-[^23]: See Revised Statutes of the State of Indiana (1852), 2:245-320 (wills); Public Statutes of the State of Minnesota (1859), 643-647, ch.
-75 (mortgages); The Code of Civil Procedure of the State of California (1880), 419-420, tit.
-6, 657-659, art.
-5 (corporations).
-
-[^24]: Report of the Code Commissioners to the Eighth General Assembly of the State of Iowa (1859), 296, note to § 172 ("The right to sue, follows necessarily from the right of property.") On the significance of the Married Women's Property Acts, see, e.g., Hendrik Hartog, *Man and Wife in America: A History* (Harvard 2000), 111-113, 187-192, 290-292.
-
-[^25]: First Report of the Commissioners, iv. For legislative debates on the Code, see "Legislative Acts and Proceedings," *Albany Evening Journal*, Mar. 31, 1848.
-
-[^26]: Report of the Committee on the Judiciary on the Bill to Continue in Office the Commissioners on Practice and Pleadings, in New York Assembly Documents, 72d sess., vol.
-3, no.
-47, (New York 1849), 2, 12-15.
-
-[^27]: Final Report of the Commissioners, 225-226, § 554.
-For examples of "codes" that did not alter previously enacted statutes, see, for instance, Report, Appendix to the Journals of the Senate and Assembly of the State of Tennessee (1857), 191 ("The digest presents the law substantially as it now exists in the State.
-I have neither felt at liberty nor deemed it advisable to innovate largely upon the established system."); 1897 New Mexico Compiled Laws 9 ("The commissioners were given no authority to revise."); 1866 Illinois Compiled Laws v ("We cannot change the text, but we can arrange and systematize the entire legislation of the state upon any given subject."); 1849 Wisconsin Revised Statutes, "Advertisement" (commission "directed the subscriber to arrange the chapters into parts and titles as he thought proper, re-arranging the order of the sections or transposing them from one chapter to another, whenever it would not alter the meaning of the law.").
-
-[^28]: *Montana Post*, January 21, 1865.
-
-[^29]: *The Miner's Express* (Dubuque), February 26, 1851.
-
-[^30]: Full citations to all of the codes that we used, plus links to electronic versions at the Hathi Trust, Google Books or other sources when available are available at Kellen Funk, *American Legislation Project* (2015--): <http://kellenfunk.org/legislation>.
-
-[^31]: We have preferred to use the term "digital history" when referring to our own work, in part because the term "digital humanities" has largely come to refer to the work of digital literary and digital media scholars, but primarily because we wish to see digital scholars make disciplinary, rather than interdisciplinary contributions.
-On the role of disciplines and the importance of field specific argumentation, see, Stephen Robertson, "The Differences between Digital Humanities and Digital History," 289--307, and Cameron Blevins, "Digital History's Perpetual Future Tense," 308--324, both in *Debates in the Digital Humanities 2016*, ed.
-Matthew K.
-Gold and Lauren F.
-Klein (Minneapolis: University of Minnesota Press, 2016).
-Nevertheless, digital text analysis in the humanities has mostly been published by literary scholars, including Stephen Ramsay, *Reading Machines: Toward an Algorithmic Criticism* (Urbana: University of Illinois Press, 2011); Franco Moretti, *Distant Reading* (New York: Verso, 2013); Matthew L.
-Jockers, *Macroanalysis: Digital Methods and Literary History* (Urbana: University of Illinois Press, 2013); Ted Underwood, *Why Literary Periods Mattered: Historical Contrast and the Prestige of English Studies* (Stanford: Stanford University Press, 2013); Ryan Cordell and David A.
-Smith, *Viral Texts: Mapping Networks of Reprinting in 19th-Century Newspapers and Magazines*, NULab for Texts Maps and Networks, Northeastern University (2012--): <http://viraltexts.org>.
-Related but less well regarded by humanities scholars is work in "culturomics": see Jean-Baptiste Michel et al., "Quantitative Analysis of Culture Using Millions of Digitized Books", *Science* 331, no.
-6014 (2011), 176--182; doi:10.1126/science.1199644.
-On the uselessness of the term "big data," see Ted Underwood, "Against (Talking About) 'Big Data,'" *The Stone and the Shell*, blog post, 10 May 2013: <https://tedunderwood.com/2013/05/10/why-it-matters-that-we-dont-know-what-we-mean-by-big-data/>.
-For an example of curating a corpus aimed at research questions, see Ted Underwood, Boris Capitanu, Peter Organisciak, Sayan Bhattacharyya, Loretta Auvil, Colleen Fallaw, J.
-Stephen Downie, "Word Frequencies in English-Language Literature, 1700-1922," dataset, v0.2 (HathiTrust Research Center, 2015) doi:10.13012/J8JW8BSJ.
-
-    Only a few scholars have turned their attention to the computer analysis of legal texts for historical purposes, including Paul Craven, "Detección automática y visualización de dominios específicos similares en documentos: análisis DWIC y su aplicación en el Proyecto Master & Servant \[Automatic Detection and Visualization of Domain-Specific Similarities in Documents: DWIC Analysis and its Application in the Master & Servant Project\]," published on CD-ROM in F.
-J.
-A Perez et al., eds., *La Historia en una nueva frontera \[History in a New Frontier\]* (Digibis: Ediciones de la Universidad de Castilla-La Mancha, 1998); Paul Craven and Douglas Hay, "Computer Applications in Comparative Historical Research: The Master & Servant Project at York University, Canada," *History and Computing* 7, no.
-2 (1995); Paul Craven and W.
-Traves, "A General-Purpose Hierarchical Coding Engine and Its Application to Comparative Analysis of Statutes," *Literary and Linguistic Computing* 8, no.
-1 (1993): 27--32, doi:10.1093/llc/8.1.27; Eric C.
-Nystrom and David S.
-Tanenhaus, "The Future of Digital Legal History: No Magic, No Silver Bullets," *American Journal of Legal History* 56, no.
-1 (2016): 150--67, doi:10.1093/ajlh/njv017; Dan Cohen, Frederick Gibbs, Tim Hitchcock, Geoffrey Rockwell, et al., "Data Mining with Criminal Intent," white paper, 31 August 2011, <http://criminalintent.org>.
-
-[^32]: In each instance we downloaded an entire volume of sessions laws, statutory compilations, or single-volume codes of procedure and then cropped out irrelevant pages, marginalia and footnoted commentary, leaving only the statutory text.
-After several trials of various implementations of Tesseract (open source) and I.R.I.S.
-(proprietary) OCR programs, we determined that Nitro Pro PDF, which relies on I.R.I.S.
-software, offered the best OCR tool for this project.
-I.R.I.S.
-provides slightly more accurate readings of nineteenth-century typefaces than Tesseract, and Nitro Pro's implementation makes words, not characters, the fundamental unit of output.
-The latter feature made cropping between marginalia and the statute more reliable.
-We removed hyphenated line breaks and standardized spelling for common terms that evolved over the nineteenth century (e.g., *indorsement*).
-
-[^33]: William Wirt Blume, "Adoption in California of the Field Code of Civil Procedure: A Chapter in American Legal History," 17 *Hastings Law Journal* 701 (1966); Stephen J.
-Field, *Personal Reminiscences of Early Days in California* (1893), 75-78.
-
-[^34]: The formal definition of the Jaccard similarity for two sets, $A$ and $B$, is $J(A, B) = \frac{ | A \cap B | }{ | A \cup B | }$.
-
-[^35]: We implemented LSH as described in Jure Leskovec, Anand Rajaraman, and Jeff Ullman, *Mining of Massive Datasets*, 2nd ed.
-(Cambridge University Press, 2014), ch.
-3, <http://www.mmds.org>; the algorithm was first described in Andrei Z.
-Broder, "On the Resemblance and Containment of Documents," in *Compression and Complexity of Sequences 1997: Proceedings*, (IEEE, 1997): 21--29, <http://gatekeeper.dec.com/ftp/pub/dec/SRC/publications/broder/positano-final-wpnums.pdf>.
-Other digital humanities projects, most notably *Viral Texts*, have used other means for detecting text reuse.
-The most prominent of these are algorithms for sequence alignment.
-(Our "textreuse" package for R also implements the Smith-Waterman local sequencing algorithm, derived from gene sequencing.) Yet the older and simpler LSH algorithm sufficed for our purposes because legal sources are easily divided into discrete sections which can be treated as independent documents.
-For other approaches, see David Bamman and Gregory Crane, "Discovering Multilingual Text Reuse in Literary Texts," white Paper, Perseus Digital Library (2009): <http://www.perseus.tufts.edu/publications/2009-Bamman.pdf>; Timothy Allen, Charles Cooney, Stéphane Douard, et al., "Plundering Philosophers: Identifying Sources of the Encyclopédie," *Journal of the Association for History and Computing* 13, no.
-1 (2010): <http://hdl.handle.net/2027/spo.3310410.0013.107>; Glenn Roe, Russell Horton, and Mark Olsen, "Something Borrowed: Sequence Alignment and the Identification of Similar Passages in Large Text Collections," *Digital Studies / Le Champ numérique* 2, no.
-1 (2010): <http://www.digitalstudies.org/ojs/index.php/digital_studies/article/view/190/235>; David A.
-Smith, Ryan Cordell, and Elizabeth Maddock Dillon, "Infectious Texts: Modeling Text Reuse in Nineteenth-Century Newspapers," in *2013 IEEE International Conference on Big Data*, 2013, 86--94, doi:10.1109/BigData.2013.6691675; David A.
-Smith, Ryan Cordell, Elizabeth Maddock Dillon, et al., "Detecting and Modeling Local Text Reuse," *Proceedings of IEEE/ACM Joint Conference on Digital Libraries* (IEEE Computer Society Press, 2014); Christopher Forstall, Neil Coffee, Thomas Buck, Katherine Roache, and Sarah Jacobson, "Modeling the scholars: Detecting Intertextuality through Enhanced Word-level N-gram Matching" *Digital Scholarship in the Humanities* 30, no.
-4 (2015): 503--515; Douglas Ernest Duhaime, "Textual Reuse in the Eighteenth Century: Mining Eliza Haywood's Quotations," *Digital Humanities Quarterly* 10, no.
-1 (2016): <http://www.digitalhumanities.org/dhq/vol/10/1/000229/000229.html>.
-
-[^36]: We filtered this matrix based on what we knew about the process of borrowing.
-We removed any match below a threshold that we determined by reading pairs of matches.
-Because Jaccard similarity scores are symmetric, we also removed anachronistic matches.
-For instance, a code from 1851 obviously did not borrow from a code from 1877.
-Furthermore, in chains of borrowing (e.g., NY1850 to CA1851 to CA1868 to CA1872 to MT1895) the latest section might have a high similarity to all of its ancestors, but it was in fact borrowed only from the most recent parent.
-We therefore filtered the similarity matrix to remove matches within the same code; anachronistic matches; spurious matches beneath a certain threshold.
-Then if a section had multiple matches, we kept the match from the chronologically closest code, giving preference to codes from the same state, unless there was a substantially closer match from a different code.
-
-[^37]: We have released two repositories with all the code used for this project.
-Lincoln Mullen, "textreuse: Detect Text Reuse and Document Similarity," R package version 0.1.3 (2015--): <https://github.com/ropensci/textreuse>, includes the LSH and other algorithms that we used for general purpose application.
-(This package was peer-reviewed by rOpenSci, a collective of academic developers who use the R programming language.) A second repository contains all of our code specific to the migration of the Field Code: <https://github.com/lmullen/civil-procedure-codes/>.
-
-[^38]: That New York codes are central is obvious from the visualization, but we also confirmed this by formal measures of centrality used in network analysis.
-A network is simply a list of edges (in our case the number of sections borrowed) between nodes (in our case, the codes).
-Because even our efforts at determining the best match for each section sometimes attributed a section to an incorrect code, we pruned the edges of the graph so that each code was connected to another code only if it borrowed at least fifty sections or twenty percent of its sections.
-
-    Within New York there was a definite chronological progression from the 1848, 1849, 1850, 1851, and 1853 versions of the code, but the development was not chronologically linear.
-The state legislature enacted the 1848, 1849, and 1851 codes, and these show strong similarities in their relationships.
-The 1850 and 1853 versions were David Dudley Field's ideal drafts of the code which were never enacted.
-They were, however, printed with wide margins, quality typesetting, and---in the 1850 draft---extensive explanatory notes, all with an eye towards other jurisdictions copying them as a model.
-Those two codes show stronger similarity to one another than to the enacted drafts.
-
-[^39]: David Dudley Field, The Latest Edition of the New York Code of Civil Procedure (1878), 21.
-
-[^40]: Non-Field jurisdictions occasionally exhibited a borrowing relationship within a state or across two states.
-In in a few unusual instances they contributed to codes which were derived from the Field Code.
-For example, Alabama's 1852 Code provided a few sections to Tennessee's 1858 code, and some states like Wisconsin copied, along with the Field Code, large passages of pre-code legislation from earlier in the state's history.
-
-[^43]: Brendan J.
-Frey and Delbert Dueck, "Clustering by Passing Messages Between Data Points," *Science* 315 (2007): 972--976, doi: 10.1126/science.1136800; Ulrich Bodenhofer, Andreas Kothmeier, and Sepp Hochreiter, "APCluster: an R package for affinity propagation clustering," *Bioinformatics* 27 (2011): 2463-2464, doi:10.1093/bioinformatics/btr406.
-Even though the affinity propagation algorithm did not fully converge with our dataset, it did an adequate job clustering the documents.
-Because there was an exemplar section for each cluster, we were able to merge clusters whose exemplars had a high Jaccard similarity score.
-
-[^47]: Samuels, Lisa, and Jerome McGann.
-"Deformance and Interpretation." *New Literary History* 30.1 (1999): 25--56; Mark Sample, "Notes toward a Deformed Humanities," blog post, 2 May 2012: <http://www.samplereality.com/2012/05/02/notes-towards-a-deformed-humanities/>; Ramsay, *Reading Machines*, 32--57.
-
-[^48]: First Report (New York, 1848), 197.
-
-[^49]: Those jurisdictions were Nevada (1861), Dakota Territory---which retained the Code when split into North and South (1862), Idaho (1864), Arizona (1864), Montana (1865), Arkansas (1868), North Carolina (1868), Wyoming (1869), Florida (1870), South Carolina (1870), Utah (1870), and Colorado (1877).
-
-[^50]: Elliott West, "Reconstructing Race," 34 *Western Historical Quarterly* 6 (2003).
-See also Heather Cox Richardson, *West from Appomattox: The Reconstruction of America after the Civil War* (New Haven: Yale University Press, 2007); Sven Beckert, *Monied Metropolis: New York City and the Consolidation of the American Bourgeoisie, 1850-1896* (Harvard 2003); Mark Wahlgren Summers, *The Ordeal of the Reunion: A New History of Reconstruction* (Chapel Hill: University of North Carolina Press, 2014).
-The major application of the Greater Reconstruction idea to legal history has been Sarah Barringer Gordon, *The Mormon Question: Polygamy and Constitutional Conflict in Nineteenth-Century America* (Chapel Hill: University of North Carolina Press, 2003).
-
-[^51]: See, for instance, Rogers Smith, *Civic Ideals: Conflicting Visions of Citizenship in U.S.
-History* (Yale 1999); Meg Jacobs, William J.
-Novak, and Julian E.
-Zelizer, eds., *The Democratic Experiment: New Directions in American Political History* (Princeton 2003); Edward Purcell, *Litigation and Inequality: Federal Diversity Jurisdiction in Industrial America, 1870-1958* (Oxford 1992).
-
-[^52]: Naomi Lamoreaux and John Joseph Wallis, "States, Not Nation: The Sources of Political and Economic Development in the Early United States," Paper Presented at the Economic History Workshop, Harvard University, March 4, 2016.
-
-[^53]: For instance, although Tennessee in 1858 adapted nearly 225 sections of its code from Field codes, the state also incorporated nearly 50 sections of the 1852 Code of Alabama, one of the largest borrowings of southern legislation within the corpus we collected.
-
-[^54]: See Charles E.
-Clark, "The New Illinois Civil Practice Act," *University of Chicago Law Review* 1 (1933): 209.
-Nevertheless, even Illinois had substantial legislation organizing the courts and prescribing certain common law processes for obtaining civil remedies, and Colorado adapted the bulk of this legislation when it organized as a territory, a full seventeen years before its legislature considered adopting the Field Code.
-
-[^55]: Journal of the Assembly of the Territory of Utah (1870), 15.
-See also Leonard J.
-Arrington, *Great Basin Kingdom: An Economic History of the Latter-Day Saints, 1830--1900*, new edition (University of Illinois Press, 2004).
-
-[^56]: "The Code Again," *Pueblo Daily Chieftain*, February 25, 1877.
-
-[^57]: "The Legislature: The Senate Devotes Another Day to the Code," *Denver Daily Tribune*, February 17, 1877.
-
-[^58]: Governor's Message, in Journal of the House of Assembly of the Territory of Nebraska (1857), 12.
-
-[^59]: William A.
-Jenkins to William Blount Rodman, January 14, 1868, Rodman Papers.
-East Carolina University Library, Special Collections.
-Rodman's explication of the Code appeared in three sequentially numbered articles in the *Standard* on August 14, 15, and 16, 1868, under the title "The Code of Civil Procedure." Rodman disclosed his authorship in private correspondence with Barringer.
-See Barringer to Rodman, August 21, 1868, Rodman Papers.
-
-[^60]: Gordon Morris Bakken, *Practicing Law in Frontier California* (Nebraska 1991), 51-54.
-The new western history ushered in by Patricia Nelson Limerick, *The Legacy of Conquest: The Unbroken Past of the American West* (Norton 1987) and Richard White, *"It's Your Misfortune and None of My Own": A History of the American West* (Oklahoma 1991) is now returning to issues of political economy.
-See Patricia Nelson Limerick, *A Ditch in Time: The City, the West, and Water* (Fulcrum 2012); Richard White, *Railroaded: The Transcontinentals and the Making of Modern America* (Norton 2011).
-
-[^61]: "The Code," *Denver Daily Tribune*, January 10, 1877; "The Code," *Denver Daily Times*, January 27, 1877.
-
-[^62]: "A Code of Civil Procedure," *Denver Daily Times*, January 12, 1877.
-
-[^63]: "The Code," *Denver Daily Tribune*, January 31, 1877.
-
-[^64]: See Gunther A.
-Weiss, "The Enchantment of Codification in the Common-Law World," 25 *Yale Journal of International Law* 435 (2000).
-For a thorough study of the ideology of codification in India, see Robert A.
-Yelle, *The Language of Disenchantment: Protestant Literalism and Colonial Discourse in British India* (Oxford: Oxford University Press, 2012).
-
-[^65]: See, for instance, James C.
-Carter's classic defense of the common law against codification, The Ideal and the Actual in the Law, Address to the American Bar Association, August 21, 1890, at 28 ("the legislature should never attempt to perform the function of the judge, that of simply ascertaining and declaring existing customs.
-This is the work of experts who can qualify themselves only by the devotion of their lives.").
-
-[^66]: See, for instance, "Note," 29 *Albany Law Journal* 141, 142 (1884); Millar, *Civil Procedure of the Trial Court*, 55-56.
-
-[^67]: 19 *Hansard Parliamentary Debates* 531.
-
-[^68]: Texas commissioned the preparation of a code of civil procedure in 1855, and the legislature scheduled an extra session to consider it but ultimately never passed the law.
-21 *Texas Reports* (Hartley) xi (1882); *Texas State Times*, December 15, 1855.
-Reformers in the 1869 convention in Illinois attempted to pass a provision similar to the one in New York's 1846 constitution, which would have required the legislature to appoint a commission to revise practice and pleadings along the lines of the Field Code.
-See *Debates and Proceedings of the Constitutional Convention of the State of Illinois* (1870), 1496-1498.
-
-[^69]: "The Code," *Weekly Standard* (Raleigh), May 26, 1869.
-
-[^70]: See, for instance, the summary of the states-as-laboratories literature in Brian Galle & Joseph Leahy, "Laboratories of Democracy?
-Policy Innovation in Decentralized Governments," 58 *Emory Law Journal* 1333 (2009).
-
-[^71]: See Daniel Ernst, *Tocqueville's Nightmare: The Administrative State Emerges in America, 1900-1940* (Oxford: Oxford University Press, 2014); Jerry L.
-Mashaw, *Creating the Administrative Constitution: The Lost One Hundred Years of American Administrative Law* (Yale Law Library 2012); Gautham Rao, *National Duties: Custom Houses and the Making of the American State* (University of Chicago 2016).

### 2016-06-29 article/article.Rmd
Proofreading

@@
 
-Strikingly, nothing like this "universal necessity" for a code of practice existed when Nye began his legal career in New York in the 1840s; rather, it was one of the central developments of America law during the nineteenth-century.
+Nothing like this "universal necessity" for a code of practice existed when Nye began his legal career in New York in the 1840s; rather, it was one of the central developments of America law during the nineteenth-century.
 By the end of the nineteenth-century, thirty-one American states and territories had adapted the text of a New York code of civil procedure first promulgated in 1848.
-The code colloquially became known as the Field Code, named for its chief draftsman David Dudley Field, a famed Manhattan trial lawyer.[^3] When Field's code appeared in the Colorado assembly in 1876, a Denver newspaper wryly commented, "The scissors and paste-pot we had heretofore confidently believed were implements peculiar to the newspaper sanctum." To the editor, the cut-and-paste code was not just a humorous curiosity of legislative history.
+The code became known as the Field Code, after its chief draftsman David Dudley Field, a famed Manhattan trial lawyer.[^3] When Field's code appeared in the Colorado assembly in 1876, a Denver newspaper wryly commented, "The scissors and paste-pot we had heretofore confidently believed were implements peculiar to the newspaper sanctum." To the editor, the cut-and-paste code was not just a curiosity of legislative history.
 Rather, the extensive copying of Field's Code threatened the foundations of American popular sovereignty.
-"The bill is a long one; the assembly has not the time to devote to it and to give it the scrutiny that a measure of such importance demands," the editor explained.
+"The bill is a long one; the assembly has not the time to devote to it and to give it the scrutiny that a measure of such importance demands," he explained.
 Blind approval "would be an injustice to themselves and a greater wrong and injustice to the people who have a right to demand that their public servants legislate for the public good." The code "has been 'assimilated,' as we are informed, 'to the character and requirements of our people,' whatever that may mean," but the editor feared the legislation was the product of "men who have the welfare of the 'dear people' at their tongue's end always, but never in their hearts."[^4]
 
-The migration of the Field Code was a central event in Anglo-American legal history, but no modern historian has traced the extensive borrowings of the Field text nor recognized the political furor that greeted the code outside New York.[^5] Every aspect of a civil justice system, from the rules granting access to courts, to lawyers, to remedies (whether damages, injunctions, or seizure of property) was covered by the code, making its New York-specific rules politically contentious both inside and outside the Empire State.
+The migration of the Field Code was a central event in Anglo-American legal history, but no historian has traced the extensive borrowings of the Field text nor recognized the political furor that greeted the code outside New York.[^5] Every aspect of a civil justice system, from the rules granting access to courts, to lawyers, to remedies (whether damages, injunctions, or seizure of property) was covered by the code, making its New York-specific rules politically contentious both inside and outside the Empire State.
 As the Field Code migrated around the country, commentators in each jurisdiction raised the same complaint: how could legislation borrowed from another state represent the popular will and bests interests of *this* state?
@@
 Although Stewart's cut-and-paste code found its way into the archives, most draft legislation did not, and few codifiers explained in detail how they produced their texts.
-Traditional reading or textual criticism of some 98,000 distinct sections of law comprising some 7.7 million words is simply not a feasible research task for a historian who wishes to track these borrowings.
+Traditional close reading or textual criticism of some 98,000 distinct sections of law comprising some 7.7 million words is simply not a feasible research task for a historian who wishes to track these borrowings.
 
-Yet by turning to the digital analysis of texts, we have resolved this difficulty and tracked the how the sections of the various codes of civil procedures were borrowed from one another.
-Within the corpus of legislation, algorithmic analysis of texts can essentially reverse engineer and visualize what the archive revealed in Figure 1: which texts were borrowed, which modified, and how extensively.
+Yet by turning to the digital analysis of texts, we have resolved this difficulty and tracked how states borrowed their codes of civil procedure from one another.
+Within the corpus of legislation, algorithmic analysis of texts can reverse engineer and visualize what the archive revealed in figure 1: which texts were borrowed, which modified, and how extensively.
 Our method works especially well for legal texts, for reasons we will explain.
@@
 
-The first contribution of this article is the demonstration of our methods as applied to the corpus of nineteenth-century state procedure codes.
-The second contribution is the integration of what we learned from the text analysis with more conventional approaches of political and cultural history to explain the importance of the migration of the Field Code.
+The first contribution of this article is to demonstrate our methods as applied to a corpus of nineteenth-century state procedure codes.
+The second contribution is to integrate what we learned from the text analysis with the more conventional approaches of political and cultural history to explain why the migration of the Field Code mattered.
 On the national level the extent of legislative borrowing followed a pattern American historians have described as a "Greater Reconstruction" in which the former Confederate South and the Far West showed a remarkable kinship.
@@
 At the more local level, our digital computations can trace modifications within code traditions, for instance, the ways western and midwestern codifiers altered New York's law to accommodate hardening conceptions of racial competencies in the civil courts.
-To see these developments, one needs a tool that can canvass all the states at once across broad swaths of civil law.
 
@@
 Until 1848, civil remedies and trial practice in New York were largely governed by common law traditions loosely categorized as "practice and pleadings."[^6] To understand how to file a civil claim or to enforce a judgment, a lawyer had to consult ad hoc statutes from colonial times to the present as well as precedents reported from cases litigated at common law and chancery.
-By the 1840s, enterprising practitioners had collated these materials into a half dozen marketable treatises, but these remained works of private opinion---no court was bound to agree with the treatise writers as to the weight, relevance, or proper interpretation of a legal statement.[^7] The common law was accordingly known as "unwritten law" despite the proliferation of published texts.
-The point was that common law was not precisely determined until a particular case drawn from the messy facts of life demanded resolution.[^8] Statutes, on the other hand, were "written law," prescribing or reforming the rules even before a case put the precise question in issue.
-And within the realm of written law, codes were the ultimate statutes.[^9]
+By the 1840s, enterprising practitioners had collated these materials into a half dozen marketable treatises, but these remained works of private opinion---no court was bound to agree with the treatise writers as to the weight, relevance, or proper interpretation of a legal statement.[^7] The common law was accordingly known as "unwritten law" despite the proliferation of published texts, because the common law was not precisely determined until a particular case drawn from the messy facts of life demanded resolution.[^8] Statutes, on the other hand, were "written law," prescribing or reforming the rules even before a case put the precise question in issue.
+Within the realm of written law, codes were the ultimate statutes.[^9]
 
-Codification is, as Lawrence Friedman has written, "one of the set pieces of American legal history." Law reformers advocated for a codification of the common law from the earliest days of the Republic up into the Gilded Age, from Massachusetts down to South Carolina.
+Codification is, as Lawrence Friedman has written, "one of the set pieces of American legal history." Law reformers advocated for a codification of the common law from the earliest days of the Republic through the Gilded Age, from Massachusetts down to South Carolina.
 Efforts ranged from mere compilations of existing statutes in each state to a full European-style codification meant to be an entirely comprehensive and systematic statement of the law.[^10] At its most basic level, codification proposed that legislative policy ought to be the sole source of law.
-Law was to be made by democratically responsible legislators---in terse, unambiguous statements---not discovered through application and analogy in particular cases by the judges.
-Debates over codification thus ranged from the metaphysics of law to political theories of separation of powers and institutional competency.[^11]
+Law was to be made by democratically responsible legislators in terse, unambiguous statements, not discovered through application and analogy in particular cases by the judges.
+Debates over codification thus ranged from the metaphysics of law to political theories of institutional competency and the separation of powers.[^11]
 
-In New York, these codification debates came to a head at the 1846 constitutional convention, where "the conquerors took all," as the ambivalent Jacksonian James Fenimore Cooper complained.[^12] Law reformers abolished the court of chancery, made judges stand for popular election, and required the legislature to appoint a commission to reform the "practice and pleadings" of the civil courts.[^13] New Yorkers had two models of legislative commissions on which they could draw for their own law reforms.
+In New York, these codification debates came to a head at the 1846 constitutional convention, where "the conquerors took all," as the ambivalent Jacksonian James Fenimore Cooper complained.[^12] Law reformers abolished the court of chancery, made judges stand for popular election, and required the legislature to appoint a commission to reform the "practice and pleadings" of the civil courts.[^13]
+
+New Yorkers had two models of legislative commissions on which they could draw for their own law reforms.
 The French government under Napoleon had appointed five-member commissions to codify the law of France.
@@
 Royal commissioners were usually not legislators.
-On the one hand, that meant commissioners were not bound to the rhythms of Parliament's schedule---they could continue their work even as Parliament adjourned.
-On the other hand, the recommendations of royal commissioners were a further remove from actual legislation.
 Although by the mid-nineteenth century royal commissions sometimes offered model statutes, the legislation they advised still had to pass through the normal politicking and drafting processes of Parliament.[^15]
@@
 The first third of the code covered constitutional topics, specifying the jurisdiction of all state courts and the duties of all state officers (and liabilities for violating those duties).
-The code deregulated attorney compensation, introducing novel structures of retainers and contingency fees.[^19] It created summary procedures meant to accelerate debt collections while simultaneously carving out "homestead" exemptions from the sheriff's reach.[^20] The code concluded by defining who could be an attorney, a juror, and a witness, drawing racial and gendered distinctions over who could speak in court.[^21]
+The code deregulated attorney compensation, introducing novel structures of retainers and contingency fees.[^19] It created summary procedures meant to accelerate debt collection while simultaneously carving out "homestead" exemptions from the sheriff's reach.[^20] The code concluded by defining who could be an attorney, a juror, and a witness, drawing racial and gendered distinctions over who could speak in court.[^21]
 
@@
 Remedies were thus intimately connected to substantive law.
-For that reason, neither the French *code de procédure civile* (1806) nor Blackstone's or Bentham's writings conceived of remedies as purely procedural.[^22] By codifying remedies, Field invited continual expansion of the category of "procedure." As other states adopted the procedure code, they sometimes included other fields of law that seemed obviously "substantive" yet had such specific procedures or remedies that they were placed in a "code of procedure," including the law of wills, corporations, and mortgages.[^23] After all, argued procedural codifiers in Iowa, what did the famed Married Women's Property Acts offer besides procedural reform?
+For that reason, neither the French *code de procédure civile* (1806) nor Blackstone's and Bentham's writings conceived of remedies as purely procedural.[^22] By codifying remedies, Field invited continual expansion of the category of "procedure." As other states adopted the procedure code, they sometimes included other fields of law that seemed obviously "substantive" yet had such specific procedures or remedies that they were placed in a "code of procedure." Such fields included the law of wills, corporations, and mortgages.[^23] After all, argued procedural codifiers in Iowa, what did the famed Married Women's Property Acts offer besides procedural reform?
 These acts gave women *standing* to litigate in their own name and seek *remedies* in claims of property and contract, and they abolished mandatory rules of *joinder* (of husbands).
@@
 Even the shortest version of the Field Code was significantly longer than any other state statute before the Progressive legislation of the twentieth century.
-And unlike statutory compilations that sometimes took the name of a "code" but made no changes to existing law, the Field Code opened by abolishing the hallmarks of prior practice and instituting "hereafter" a new form of action with substantial revisions to basic matters of standing, remedy, and enforcement of civil judgments.[^27] In the states where it was imported, there was be no getting around the fact that the code introduced much new law, yet legislators were unable to read, critique, and amend the code within the brief period of a legislative session.
+Unlike statutory compilations that sometimes took the name of a "code" but made no changes to existing law, the Field Code opened by abolishing the hallmarks of prior practice and instituting "hereafter" a new form of action with substantial revisions to basic matters of standing, remedy, and enforcement of civil judgments.[^27] In the states where it was imported, there was no getting around the fact that the code introduced much new law, yet legislators were unable to read, critique, and amend the code within the brief period of a legislative session.
 "It is folly to undertake to pass a code in a sixty day session," wrote the *Montana Post*, "and the best way would be for the Assembly to select one from a State or Territory which would come near meeting our wants, and slide it through with the fewest changes possible."[^28] Sliding the code through eased the problem of time but exacerbated the problem of local sovereignty.
@@
 
-Curating a corpus to answer a specific question is an important difference from the way that digital history often describes itself.
+Curating a corpus to answer a specific question is an important difference from the way that digital history often describes its work.
 Speaking in broad terms, digital historical work---like all historical work---can begin either with a set of sources or with a question.
-Digital history is often conceived of as beginning with very large datasets such as the Google Books or Hathi Trust corpora.
+Computational digital history is often conceived of as beginning with very large datasets such as the Google Books or Hathi Trust corpora.
 These large corpora are sometimes called "big data"---though, it must be emphasized, almost never by digital historians who actually work with them---and are used as the basis of a "distant reading." We think that working with these large corpora is worthwhile because it is salutary for historians to have their research questions shaped by the broadest possible contexts.
 Nevertheless, it is not apparent that digital historians can readily move from these omnibus corpora to answering the specific research questions that animate various historical fields.
-In this article we demonstrate an alternative approach, which we might unimaginatively label "medium data." Although the amount of legislation that governed American civil practice is impressive---every state amended and re-enacted procedure statutes nearly every decade---a corpus of procedural legislation requires some computational sophistication but is far from needing the computational techniques derived for truly big data.
+In this article we demonstrate an alternative approach, which we might unimaginatively label "medium data." The amount of legislation that governed American civil practice is impressive, since every state amended and re-enacted procedure statutes nearly every decade.
+But while a corpus of procedural legislation requires some computational sophistication, it is far from needing the computational techniques derived for truly big data.
 We have gathered a large but narrowly constrained corpus centered on solving a well-defined research question.
@@
 The most important step we took in processing the files was to split each section of the code into its own text file.
-Codes varied in how they were organized, but they universally divided specific regulations into *sections* (or, on occasion, *articles*).
+Codes varied in how they were organized, but they all divided specific regulations into *sections* (or, on occasion, *articles*).
 Not only does the discursive form of these texts provide a handy organizational scheme for digital methods, but historically sections were also the way legislators borrowed their texts.
@@
 (Stephen Johnson Field, David Dudley Field's brother, was the lawyer who imported New York's code into California.[^33]) But the New York code is over 150,000 words long, whereas California's code was just over 50,000 words long.
-Those disparate lengths mean that comparing all of the California code to all of the New York code is a less meaningful comparison that than comparing each section in the California code to each section in the New York code, where matching sections will have a similar length.
+Those disparate lengths mean that comparing all of the California code to all of the New York code is less meaningful than comparing each section in the California code to each section in the New York code, where matching sections will have a similar length.
 
@@
 A common method for measuring the similarity of two documents involves dividing texts up into tokens of consecutive words (called n-grams) and calculating a Jaccard similarity score, defined as ratio between the number of tokens that the two document have in common to the total number of tokens that appear in both documents.
-We used five-word tokens and "shingled" them, meaning that for the New York sections above, the first token was "the distinction between actions at," the second token was "distinction between actions at law," and so on.
+We used five-word tokens and shingled them, meaning that for the New York sections above, the first token was "the distinction between actions at," the second token was "distinction between actions at law," and so on.
 These tokens each contain more meaning than a single word, yet because they are shingled they are robust to changes in the text or noisy OCR.
@@
 
-  : A subset of the section to section similarity matrix.
+  : A subset of the section-to-section similarity matrix.
 
-As we would expect the first respective sections (New York §554 and California §1) have a score of 0.14, which indicates that they are similar but have significant differences, while the second sections (New York §555 to California §2) have a much higher similarity score since only a few words were changed.
+As we would expect the first sections (New York § 554 and California § 1) have a score of 0.14, which indicates that they are similar but have significant differences, while the second sections (New York § 555 to California § 2) have a much higher similarity score of 0.41 since only a few words were changed.
 Just as important, when we compare the first section in New York to the second section in California, we get a score of 0; the two sections are nothing like each other.
@@
 While this is easy enough to conceptualize, such a matrix is actually quite large, containing about 4.8 billion comparisons.
-This would take an unreasonable amount of computation time, and most of these comparisons would be unnecessary, since each section has no relationship to most other sections.
-We therefore implemented the minhash/locality sensitive hashing (LSH) algorithm to detect pairs of possible matches quickly.This algorithm works by extracting a set number of random tokens from each document to create a document signature; this subset makes it possible to approximate the Jaccard similarity of two documents.
+This would take an unreasonable amount of computation time, and most of these comparisons would be unnecessary since each section has no relationship to most other sections.
+We therefore implemented the minhash/locality sensitive hashing algorithm to detect pairs of possible matches quickly.This algorithm works by extracting a set number of random tokens from each document to create a document signature; this subset makes it possible to approximate the Jaccard similarity of two documents.
 These signatures can then be used to identify each of the billions of possible pairs of sections as likely to be matches or not.
@@
 
-At the broadest scale of analysis, we aggregated the section-to-section borrowings into a summary of how many sections each code (or statute) borrowed from each other code.
+At the broadest scale of analysis, we aggregated the section-to-section borrowings into a summary of how many sections each code borrowed from each other code.
 We therefore can show the connections from one code to another.
@@
 
-The New York Field Codes, especially the finished draft of 1850, are central to the entire network.[^39] New York gave rise to different regional traditions within the procedural network.
+The New York Field Codes, especially the finished draft of 1850, were central to the entire network.[^39] New York gave rise to different regional traditions within the procedural network.
 Variations in the Field drafts meant that different states could borrow different versions of the Field Code.
@@
 In addition to the overview of the relationship between codes, we can also see more detail by visualizing the pattern of borrowings within each code.
-We have visualized where each section of a code was borrowed from to see how each code was put together.
+We have visualized the origin of each section of every code to see how each code was put together.
 To illustrate this, we will follow one branch of the Field Code network, beginning with the family started by California's 1850 and 1851 codes.
@@
 California's 1850 code, enacted in the period when California was entering the Union as a state, was borrowed almost entirely from New York's 1849 Field Code.
-The compiler Elisha Crosby did lift one significant section from the mixed civilian-common law code of Louisiana regulating when a judge could order a new trial.
+The compiler Elisha Crosby did lift one significant portion regulating when a judge could order a new trial from the mixed civilian/common law code of Louisiana .
 New trials were not provided for in the New York Code until the finished draft in 1850.
@@
 Indiana's 1852 code and Oregon's 1854 code provide the majority of the borrowings.
-Those two contiguous bands of borrowings correspond to regulations on judgement from Oregon and enforcement provisions from Indiana.
+The contiguous bands of borrowings correspond to regulations on judgement borrowed from Oregon and enforcement provisions borrowed from Indiana.
 This pattern likely came about because one of the Washington code commissioners, Edward Lander, was an Indiana appellate judge from 1850 to 1853, while another commissioner, William Strong, was a justice of the Oregon Supreme Court in the same years.
@@
 Like many of the last generation codes, the text of the procedure code had stabilized as a local manifestation of a regional tradition.
-The code was still genuinely a Field Code, with a great deal of similarity to the original New York Field Codes, but its specific form depended on the many edits and rearrangements that state code commissioners had made to the text.
+The code was still genuinely a Field Code, with a great deal of similarity to the original New York Field Codes, but its specific form depended on the many edits and rearrangements that code commissioners from several states had made to the text.
 
@@
 That algorithm finds an "exemplar" item which is most characteristic of the other items in the cluster.
-That assumption fits nicely with borrowings from the Field Code, where a single section (likely from the 1850 New York code) had many borrowings, but where there could also be innovative sections in other stages that might be more influential.[^43]
+That assumption fits nicely with borrowings from the Field Code, where a single section (likely from a Field Code) had many borrowings, but where there could also be innovative sections from other states that might be more influential.[^43]
 
@@
 Within each cluster, we organized the sections chronologically.
-We were thus able to see the development of the law from jurisdiction to jurisdiction.
+We were thus able to see the development of the law from jurisdiction to jurisdiction over time.
 This method provides historians with a way of noticing small changes in the wording and substance of the law.
@@
 This method of clustering, however, is a kind of algorithmic close reading.
-By deforming the texts---taking them out of the context of the codes and putting them in the context of their particular variations---we are able to pay attention to those variations.[^44]
+By deforming the texts---taking them out of the context of the codes and putting them into the context of their particular variations---we are able to pay attention to those variations.[^44]
 
-Take provisions regulating witness testimony.
+Take provisions regulating witness testimony as an example.
 At common law, parties and interested witnesses were not permitted to testify in their own causes.
@@
 The cluster of sections in the appendix documents how California's codifiers grafted earlier prohibitions from midwestern states into Field's Code.
-Many other codes then evidence a remarkable uniformity with California's text (which later changed only to add "Mongolian" to the list of races).
-Iowa's Code had a more minor influence, and Wyoming developed the only truly original section which made explicit that the exclusion was based on the racist assumption that non-white peoples were infantilized, a connection only implicit in other jurisdictions.
+Many other codes then evidenced a remarkable uniformity with California's text (which later changed only to add "Mongolian" to the list of races).
+Iowa's Code had a more minor influence, and Wyoming developed the only truly original section which made it explicit that the exclusion was based on the racist assumption that non-white peoples were infantilized, a connection only implicit in other jurisdictions.
 
@@
 No single section of the code announced its preference for creditors' rights; rather, the acceleration of creditors' remedies resulted from the combination of several sections.
-In New York's original enacted code from 1848, §107 required a defendant to answer the complaint within twenty days, instead of at the next court session (which in some cases could have been as far as three months away); §202 provided for default judgment as a matter of course, issued by a clerk without a judicial order if no adequate answer was received within the twenty days; §§128--133 abolished fictitious pleadings and required answers to state true facts verified by a defendant's oath, all so that no trial would delay the enforcement of uncontestable obligations; finally, the code abolished a traditional thirty-day waiting period between issue of judgment and commencement of execution.
+In New York's original enacted code from 1848, § 107 required a defendant to answer the complaint within twenty days, instead of at the next court session (which in some cases could have been as far as three months away); § 202 provided for default judgment as a matter of course, issued by a clerk without a judicial order if no adequate answer was received within the twenty days; §§ 128--133 abolished fictitious pleadings and required answers to state true facts verified by a defendant's oath, all so that no trial would delay the enforcement of uncontestable obligations; finally, the code abolished a traditional thirty-day waiting period between issue of judgment and commencement of execution.
 These provisions dealt with what merchants and capitalists perceived as an abuse of the common law system, where defendants in cases of debt could stretch out enforcement of debt collection for as long as two years.
-The Field code's summary judgment brought down the time of debt collection to a matter of weeks.
+The Field Code's summary judgment brought down the time of debt collection to a matter of weeks.
 The code traded the rhythms of agriculture for the rhythms of merchant finance.[^45]
@@
 
-In the last decade, scholars of Reconstruction have broadened the scope of their study to include both the South and the West as two sites in one "Greater Reconstruction." These studies have illustrated the ways that military conquest, rapid industrialization, and the resettlement and education of ethnic minorities developed similarly in each region, guided by economic elites in New York and political administrators in Washington.[^47] In tracing the legal aspects of this Greater Reconstruction, scholars have focused almost entirely on constitutional rights of citizenship and civil equality or the expansion of federal power.[^48] While the 1860s and 1870s were of course a transformative period in the history of civil rights and the creation of a national state, they were also the decades in which many local legal institutions and practices were transformed not by federal power but by state codification.
+In the last decade, scholars of Reconstruction have broadened the scope of their study to include both the South and the West as two sites in one "Greater Reconstruction." These studies have illustrated the ways that military conquest, rapid industrialization, and the resettlement and education of ethnic minorities developed similarly in each region, guided by economic elites in New York and political administrators in Washington.[^47] In tracing the legal aspects of this Greater Reconstruction, scholars have focused almost entirely on the expansion of federal power or constitutional rights of citizenship and civil equality.[^48] While the 1860s and 1870s were of course a transformative period in the history of civil rights and the creation of a national state, they were also the decades in which many local legal institutions and practices were transformed not by federal power but by state codification.
 Naomi Lamoreaux and John Joseph Wallis have recently argued that in the creation of a modern American economy, "the federal government played *no* role in this process until the Civil War, and even then it played only a bit part." The history of the Field Code's migration helps to substantiate this claim.
-While Lamoreaux and Wallis focus on the development of banking, transportation, and incorporation at the state level, it was the Procedure Code that provided the structure of civil remedies that protected these state institutions.
+While Lamoreaux and Wallis focus on the development of banking, transportation, and incorporation at the state level, it was the codes of civil procedure that provided the structure of civil remedies which protected these state institutions.
 And procedure codes were the creatures of state governance.[^49]
@@
 The states that adopted the Field Code were never forced to, and they had other options available to them.
-Southern states that drew more on the civilian code tradition such as Louisiana and Alabama offered other options for states desiring to reform common law practice.[^50] Illinois long retained the common law---in later decades lawyers called it "the Yellowstone Park of common law pleading." When Colorado was a territory it imported the Illinois common law to the West via statute, a full fourteen years before its legislature considered the Field Code.
+Southern states with a civilian code tradition such as Louisiana and Alabama offered other options for states desiring to reform common law practice.[^50] Illinois long retained the common law---in later decades lawyers called it "the Yellowstone Park of common law pleading." When Colorado was a territory it imported the Illinois common law to the West via statute, a full fourteen years before its legislature considered the Field Code.
 [^51]
@@
 The early Mormon settlers of Utah persistently avoided the mining frenzy as well as codification.
-By 1870, however, the territory's governor directed the legislature's attention to the recent Code of Nevada, a code "for a people whose interests in many respects are similar to our own." Of course, standing behind the Nevada Code was "the State of New York---a State which is an empire in itself and whose commercial transactions are far greater than those of any other State in the Union." By copying its code, Utah too could be "rewarded by equal advantages."[^52] Code proponents in Colorado similarly parried arguments that a code would be a "foreign" imposition by pointing to the fact that it has been "adopted twenty-nine years ago by the Empire state of the Union" and they promised that the code of the nation's uniquely commercial empire could bring wealth in its wake.[^53]
+By 1870, however, the territory's governor directed the legislature's attention to the recent Code of Nevada, a code "for a people whose interests in many respects are similar to our own." Of course, standing behind the Nevada Code was "the State of New York---a State which is an empire in itself and whose commercial transactions are far greater than those of any other State in the Union." By copying its code, Utah too could be "rewarded by equal advantages."[^52] Code proponents in Colorado similarly parried arguments that a code would be a "foreign" imposition by pointing to the fact that it has been "adopted twenty-nine years ago by the Empire state of the Union" and they promised that the code of the nation's commercial empire could bring wealth in its wake.[^53]
 
@@
 
-Receiving innumerable letters complaining that under the code, "no one will be benefited, except perhaps some Northern Capitalists," a North Carolina commissioner undertook an anonymous defense of the new Code in the *Weekly Standard*.
+Receiving innumerable letters complaining that under the code, "no one will be benefited, except perhaps some Northern Capitalists," a North Carolina commissioner undertook an anonymous defense of the new code in the *Weekly Standard*.
 He encouraged the bar to accommodate themselves to change, for "the New York system ...
@@
 The creditors' remedies in the code gave the codifiers their leading argument against criticisms rooted in the ideology of popular sovereignty.
-"There is no doubt but the people are in favor of anything that promises to hurry up that proverbially slow and blind old female called Justice, and they will go for the old code," one Colorado newspaper announced.[^59] New York's "code practice is the best in excellence," stated another, "and when I say *best* I do not mean best for lawyers only, but best for the people---the commonwealth."[^60] If the People favored economic progress, certainty of remedy, and efficiency in proceedings, then they favored the New York Code, no matter whether they understood or cared about technical rules of pleading and joinder.
-Thus, in their arguments the codifiers imagined themselves the champions of popular sovereignty, for it was they who accomplished what the People actually desired.
+"There is no doubt but the people are in favor of anything that promises to hurry up that proverbially slow and blind old female called Justice, and they will go for the old code," one Colorado newspaper announced.[^59] New York's "code practice is the best in excellence," stated another, "and when I say *best* I do not mean best for lawyers only, but best for the people---the commonwealth."[^60] If the people favored economic progress, certainty of remedy, and efficiency in proceedings, then they favored the New York code, no matter whether they understood or cared about technical rules of pleading and joinder.
+Thus, in their arguments the codifiers imagined themselves the champions of popular sovereignty, for it was they who accomplished what the people actually desired.
 
@@
 
-By framing addressing our historical questions to a sufficiently large but narrowly defined corpus of sources, we enjoyed a useful symbiosis of traditional and digital historical methods.
+By addressing our historical questions to a sufficiently large but narrowly defined corpus of sources, we enjoyed a useful symbiosis of traditional and digital historical methods.
 Our computational methods produced useful historical knowledge because they were carefully tailored to what we knew about the data from traditional historical work.
@@
 While we think that one of the most useful things about digital history is its ability to start with large corpora and then figure out what was interesting from the past, we have shown how digital history can also operate by starting with specific historical questions rather than particular sources.
-We have shown how a collection of methods from computer science, including minhash/locality-sensitive hashing, affinity propagation clustering, and network analysis, along with the concept of text deformance from literary history, can be used to good effect in tracking the changes in the law, as well as any other discursive field whose texts can be readily divided into sections.
+We have shown how a collection of methods from computer science, including minhash/locality-sensitive hashing, affinity propagation clustering, and network analysis, along with the concept of text deformance from literary studies, can be used to good effect in tracking the changes in the law, as well as any other discursive field whose texts can be readily divided into sections.
 Finally we have shown how it is possible to work on different scales, using network analysis, visualization, and algorithmic close reading, and thus to gain both a broad overview of the law's migration, as well as a highly detailed view of the changes in the law.
@@
 
-In the economically developing West and re-developing South, anxieties over the lack of capital---both among the bar as well as voters---joined with arguments of civilization and progress to spur many jurisdictions to copy the text of the code of New York, the Empire State of capital.
-The short time horizons of American lawmaking limited the options available for re-imagining or re-crafting what could become the law of remedies and legal practice.
-And in the economically underdeveloped parts of the country, time horizons could be short indeed.
+In the economically developing West and re-developing South, anxieties over the lack of capital---both among the bar as well as voters---joined with arguments about civilization and progress to spur many jurisdictions to copy the text of the code of New York, the Empire State of capital.
+The short legislative sessions of American lawmaking limited the options available for re-imagining or re-crafting what could become the law of remedies and legal practice.
+And in the economically underdeveloped parts of the country, periods of opportunity could be short indeed.
 Capital might quickly pass over one region and favor another, and each month more lawyers arrived hoping to make a start in a jurisdiction where economic progress was just about to take off.
@@
 Lawyers and judges, politicians and newspaper editors warred over whether codes that were drafted by commissioners and borrowed wholesale from beyond a jurisdiction's borders were actually democratic.
-Codifiers responded by transmuting democratic theory into support for a remedial code elected legislators had neither the time nor inclination to read.
+Codifiers responded by transmuting democratic theory into support for a remedial code that elected legislators had neither the time nor inclination to read.
 Popular support for commercial development was taken to indicate popular support for New York's civil remedies, especially the cheapened and accelerated collection of debts.
@@
 
-This sample cluster brings together sections that involve racial exclusions from witness testimony in civil trials, with commentary.
+This sample cluster brings together sections that involve race-based exclusions from witness testimony in civil trials, with commentary on the history of the variations.
 
-Disqualifying the testimony of racialized parties and witnesses was not new to the procedure codes.
+Disqualifying the testimony of non-white parties and witnesses was not new to the procedure codes.
 The following laws from midwestern states with large free black populations would be echoed in adaptations of the Field Code.
@@
 
-Racial qualifications were introduced to the Field Code tradition in California, first in Elisha Crosby’s draft of 1850, then in Stephen J.
+Racial disqualifications were introduced to the Field Code tradition in California, first in Elisha Crosby’s draft of 1850, then in Stephen J.
 Field’s draft of 1851.
@@
 Negroes, or persons having one half or more Negro blood, in an action or proceeding to which a white person is a party.
-           |
-CA 1868    | 394.
-The following persons shall not he witnesses: First.
-Those who are of unsound mind at the time of their production for examination.
-Second.
-Children under ten years of age, who, in the opinion of the court, appear incapable of receiving just impressions of the facts respecting which they are examined, or of relating them truly.
-Third.
-Mongolians, Chinese, or Indians, or persons having one-half or more of Indian blood, in an action or proceeding wherein a white person is a party.
-Fourth.
-Persons against whom judgment has been rendered upon a conviction for a felony, unless pardoned by the governor, or such judgment has been reversed on appeal.
            | 
@@
 Negroes, or persons having one-half or more negro blood, in an action or, proceeding to which a white person is a party.
+           |
+CA 1868    | 394.
+The following persons shall not he witnesses: First.
+Those who are of unsound mind at the time of their production for examination.
+Second.
+Children under ten years of age, who, in the opinion of the court, appear incapable of receiving just impressions of the facts respecting which they are examined, or of relating them truly.
+Third.
+Mongolians, Chinese, or Indians, or persons having one-half or more of Indian blood, in an action or proceeding wherein a white person is a party.
+Fourth.
+Persons against whom judgment has been rendered upon a conviction for a felony, unless pardoned by the governor, or such judgment has been reversed on appeal.
 
@@
 
-Iowa's Code began by defining competency purely in terms of understanding the legal oath, and in the same section it barred racialized testimony (even if racialized actors could understand the oath).
+Iowa's code began by defining competency purely in terms of understanding the legal oath, and in the same section it barred non-white testimony (even if non-white actors could understand the oath).
 Wyoming followed the same tack, but softened the racial bar by adopting the same standard used for children: only those adjudged incapable of perceiving and relating facts were barred from testifying.
@@
 
-States that did not borrow Field's Evidence Code nevertheless borrowed prohibitions of racialized testimony.
+States that did not borrow Field's evidence code nevertheless borrowed prohibitions of non-white testimony.
 Two distinct strands emerge in legislation from the Deep South as well as the Upper South and Midwest.

### 2016-06-29 article/article.Rmd
Fix the blankety blank footnotes

@@
 See Henry Martyn Field, *The Life of David Dudley Field* (1898); Philip J.
-Bergan, "David Dudley Field: A Lawyer's Life," in *The Fields and the Law* (New York: Federal Bar Council, 1986).
+Bergan, "David Dudley Field: A Lawyer's Life," in *The Fields and the Law* (Federal Bar Council, 1986).
 
@@
 [^6]: When law professors such as New York's David Graham Jr.
-(a collaborator on the Field Code) began to be appointed to university positions, the chair for instruction in legal practice or procedure carried this designation of "practice and pleadings." Today that field is described as "civil procedure" a field that grew out of David Dudley Field's codification, as described below.
+(a collaborator on the Field Code) began to be appointed to university positions, the chair for instruction in legal practice or procedure carried this designation of "practice and pleadings." Today that field is described as "civil procedure," a field that grew out of David Dudley Field's codification.
 The history of practice and procedure is a staple of general legal history.
-See Frederick Pollock and Frederick Maitland, *The History of English Law Before the Time of Edward I* (2d.
-ed., Cambridge, 1898), 2 vols.; Theodore Plucknett, *A Concise History of the Common Law* (5th ed.
-2010); Lawrence M.
-Friedman, *A History of American Law* (3d.
-ed.
-2005).
+See Frederick Pollock and Frederick Maitland, *The History of English Law Before the Time of Edward I*, 2 vols., 2nd ed.
+(Cambridge, 1898); Theodore Plucknett, *A Concise History of the Common Law*, 5th ed.
+(Liberty Fund, 2010); Lawrence M.
+Friedman, *A History of American Law*, 3rd ed.
+(Touchstone, 2005).
 Few book-length works have been dedicated to the subject, however.
-The exceptions are Robert Wyness Millar, *Civil Procedure of the Trial Court in Historical Perspective* (New York University School of Law 1952); Edward Purcell, *Litigation and Inequality: Federal Diversity Jurisdiction in Industrial America, 1870--1958* (Oxford 1992); John H.
-Langbein et al., *History of the Common Law: The Development of Anglo-American Legal Institutions* (Aspen 2009); and to some extent, William E.
-Nelson, *The Americanization of the Common Law: The Impact of Legal Change on Massachusetts Society, 1760--1830* (2d.
-ed., University of Georgia Press 1994).
+The exceptions are Robert Wyness Millar, *Civil Procedure of the Trial Court in Historical Perspective* (New York University School of Law 1952); Edward Purcell, *Litigation and Inequality: Federal Diversity Jurisdiction in Industrial America, 1870--1958* (Oxford, 1992); John H.
+Langbein et al., *History of the Common Law: The Development of Anglo-American Legal Institutions* (Aspen, 2009); and to some extent, William E.
+Nelson, *The Americanization of the Common Law: The Impact of Legal Change on Massachusetts Society, 1760--1830*, 2nd ed.
+(University of Georgia Press, 1994).
 
@@
 B.
-Simpson, "The Rise and Fall of the Legal Treatise: Legal Principles and the Forms of Legal Literature," in *Legal Theory and Legal History: Essays on the Common Law* (London: Hambledon Press, 1987), 273--320.
+Simpson, "The Rise and Fall of the Legal Treatise: Legal Principles and the Forms of Legal Literature," in *Legal Theory and Legal History: Essays on the Common Law* (Hambledon Press, 1987), 273--320.
 The most instructive treatises for New York practice in the 1840s were Oliver L.
 Barbour, *A Treatise on the Practice of the Court of Chancery* (1844); Alexander M.
-Burrill, *Treatise on the Practice of the Supreme Court of the State of New York* (1846), 2 vols.; David Graham, *A Treatise on on the Practice of the Supreme Court of the State of New York* (3d.
-ed.
-1847); David Graham, *A Treatise on the Organization and Jurisdiction of the Courts of Law and Equity in the State of New York* (1839); Claudius L.
+Burrill, *Treatise on the Practice of the Supreme Court of the State of New York*, 2 vols.
+(1846); David Graham, *A Treatise on on the Practice of the Supreme Court of the State of New York*, 3rd ed.
+(1847); David Graham, *A Treatise on the Organization and Jurisdiction of the Courts of Law and Equity in the State of New York* (1839); Claudius L.
 Monell, *A Treatise on the Practice of the Supreme Court of the State of New York* (1849); Joseph W.
@@
 Cook, *The American Codification Movement: A Study in Antebellum Legal Reform* (1983); Robert W.
-Gordon, "The American Codification Movement," 36 *Vanderbilt Law Review* 431 (1983); Maurice Eugen Lang, *Codification in the British Empire and America* (Lawbook Exchange 1924).
-On common theories of codification that transcended jurisdictional boundaries, see Csaba Varga, *Codification as a Socio-Historical Phenomenon* (Budapest, 2d.
-ed.
-2011 \[1991\]); Roger Berkowitz, *The Gift of Science: Leibniz and the Modern Legal Tradition* (Fordham 2010).
+Gordon, "The American Codification Movement," *Vanderbilt Law Review* 36 (1983): 431--458; Maurice Eugen Lang, *Codification in the British Empire and America* (Lawbook Exchange, 1924).
+On common theories of codification that transcended jurisdictional boundaries, see Csaba Varga, *Codification as a Socio-Historical Phenomenon*, 2nd ed.
+(Budapest, 2011 \[1991\]); Roger Berkowitz, *The Gift of Science: Leibniz and the Modern Legal Tradition* (Fordham, 2010).
 
@@
 See, for instance, Rabban, *Law's History*, 322--77; Parker, *Common Law, History, and Democracy*, 230--41; Lewis A.
-Grossman, "James Coolidge Carter and Mugwump Jurisprudence," *Law & History Review* 20 (2002).
+Grossman, "James Coolidge Carter and Mugwump Jurisprudence," *Law & History Review* 20, no.
+3 (2002): 577--629.
 These accounts follow Horwitz, however, in focusing on the few outspoken opponents of codification, rather than the elite lawyers who sponsored the procedure codes.
@@
 [^12]: James Fenimore Cooper, *The Ways of the Hour: A Tale* (1850), 84.
-For an analysis of Cooper's philosophy of law and his critique of the New York constitution, see Charles Hansford Adams, *"The Guardian of the Law": Authority and Identity in James Fenimore Cooper* (Penn State University Press (1990), 135--48.
-See also Marvin Meyers, *The Jacksonian Persuasion: Politics and Belief* (Stanford 1957), 57--100.
+For an analysis of Cooper's philosophy of law and his critique of the New York constitution, see Charles Hansford Adams, *"The Guardian of the Law": Authority and Identity in James Fenimore Cooper* (Penn State University Press, 1990), 135--48.
+See also Marvin Meyers, *The Jacksonian Persuasion: Politics and Belief* (Stanford, 1957), 57--100.
 
 [^13]: On the politics and reforms of the New York Convention of 1846, see Charles Z.
-Lincoln, *The Constitutional History of New York from the Beginning of the Colonial Period to the Year 1905* (Rochester 1905), 2:10--101; Charles McCurdy, *The Anti-Rent Era in New York Law and Politics, 1839--1865* (University of North Carolina 2001); Jed Shugerman, *The People's Courts: The Rise of Judicial Elections and Judicial Power in America* (Harvard University Press 2012).
+Lincoln, *The Constitutional History of New York from the Beginning of the Colonial Period to the Year 1905* (Rochester, 1905), 2:10--101; Charles McCurdy, *The Anti-Rent Era in New York Law and Politics, 1839--1865* (University of North Carolina, 2001); Jed Shugerman, *The People's Courts: The Rise of Judicial Elections and Judicial Power in America* (Harvard University Press, 2012).
 
-[^14]: Count Pierre François Réal to William Sampson, October 27, 1824, in Sampson's Discourse and Correspondence with Various Learned Jurists Upon the History of the Law (1826), 191; Maxwell Bloomfield, "William Sampson and the Codifiers: The Roots of American Legal Reform," 11 *American Journal of Legal History* 234 (1967); Walter J.
-Walsh, "William Sampson, a Republican Constitution, and the Conundrum of Orangeism on American Soil, 1824--1831," 5/7 *Radharc* 1 (2006); William Sampson, *Memoirs* (2d.
-ed., 1817).
+[^14]: Count Pierre François Réal to William Sampson, October 27, 1824, in Sampson's Discourse and Correspondence with Various Learned Jurists Upon the History of the Law (1826), 191; Maxwell Bloomfield, "William Sampson and the Codifiers: The Roots of American Legal Reform," *American Journal of Legal History* 11, no 3.
+(1967): 234--252; Walter J.
+Walsh, "William Sampson, a Republican Constitution, and the Conundrum of Orangeism on American Soil, 1824--1831," *Radharc* 5 (2006): 1--32; William Sampson, *Memoirs*, 2nd ed.
+(1817).
 On French-style codifications, see Robert B.
-Holtman, *The Napoleonic Revolution* (Louisiana State 1981); R.
+Holtman, *The Napoleonic Revolution* (Louisiana State, 1981); R.
 H.
 Kilbourne, *A History of the Louisiana Civil Code* (Paul M.
-Herbert Law Center 1987); Brian Young, *The Politics of Codification: The Lower Canadian Civil Code of 1866* (Osgoode Society 1994); John W.
-Cairns, *Codification, Transplants, and History: Law Reform in Louisiana (1808) and Quebec (1866)* (Talbot 2015); Roscoe Pound, "The French Civil Code and the Spirit of Nineteenth Century Law," 35 *Boston Law Review* 79 (1955).
+Herbert Law Center, 1987); Brian Young, *The Politics of Codification: The Lower Canadian Civil Code of 1866* (Osgoode Society, 1994); John W.
+Cairns, *Codification, Transplants, and History: Law Reform in Louisiana (1808) and Quebec (1866)* (Talbot, 2015); Roscoe Pound, "The French Civil Code and the Spirit of Nineteenth Century Law," *Boston University Law Review* 35 (1955): 79.
 
 [^15]: Thomas J.
-Lockwood, "A History of Royal Commissions," 5 *Osgoode Hall Law Journal* 172 (1967); Barbara Lauriat, "'The Examination of Everything': Royal Commissions in British Legal History," 31 *Statute Law Review* 24 (2010); Joanna Innes, *Inferior Politics: Social Problems and Social Policies in Eighteenth-century Britain* (Oxford 2009).
+Lockwood, "A History of Royal Commissions," *Osgoode Hall Law Journal* 5 (1967): 172; Barbara Lauriat, "'The Examination of Everything': Royal Commissions in British Legal History," *Statute Law Review* 31 (2010): 24; Joanna Innes, *Inferior Politics: Social Problems and Social Policies in Eighteenth-century Britain* (Oxford, 2009).
 
-[^16]: Second Report of the Commissioners on Practice and Pleading (New York 1849), 3--4.
-See also, First Report of the Commissioners on Practice and Pleadings (New York 1848), iii-iv; Third Report of the Commissioners on Practice and Pleadings (New York 1849), 3, Lillian Goldman Law Library Rare Books Collection; Final Report of the Commissioners on Practice and Pleadings, in Documents of the Assembly of the State of New York, 73d sess., vol.
+[^16]: Second Report of the Commissioners on Practice and Pleading (New York, 1849), 3--4.
+See also, First Report of the Commissioners on Practice and Pleadings (New York, 1848), iii-iv; Third Report of the Commissioners on Practice and Pleadings (New York, 1849), 3, Lillian Goldman Law Library Rare Books Collection; Final Report of the Commissioners on Practice and Pleadings, in Documents of the Assembly of the State of New York, 73d sess., vol.
 2, no.
-16 (New York 1850), viii.
+16 (New York, 1850), viii.
 
@@
 See Lobban, *The Common Law and English Jurisprudence*, 127--131, 146--151.
-As Amalia Kessler notes, *Bouvier's Law Dictionary* did not even define *civil procedure* until its 1897 edition, describing the term as "rather a modern one." Amalia Kessler, "Deciding Against Conciliation: The Nineteenth-Century Rejection of a European Transplant and the Rise of a Distinctively American Ideal of Adversarial Adjudication," 10 *Theoretical Inquiries in Law* 423 (2009), 481--482; *Bouvier's Law Dictionary* (1897), 2:764.
+As Amalia Kessler notes, *Bouvier's Law Dictionary* did not even define *civil procedure* until its 1897 edition, describing the term as "rather a modern one." Amalia Kessler, "Deciding Against Conciliation: The Nineteenth-Century Rejection of a European Transplant and the Rise of a Distinctively American Ideal of Adversarial Adjudication," *Theoretical Inquiries in Law* 10 (2009): 481--482; *Bouvier's Law Dictionary* (1897), 2:764.
 Before 1848, the term was largely restricted to French usage, and American remedial law had carried the typical designation---as it did both in Graham's treatise and professorial title---of "practice and pleadings," the name likewise given to the reform commission.
@@
 10.
-See also Peter Karsten, "Enabling the Poor to Have Their Day in Court: The Sanctioning of Contingency Fee Contracts, A History to 1940," 47 *DePaul Law Review* 231 (1998); Norman Spaulding, "The Luxury of the Law: The Codification Movement and the Right to Counsel," 73 *Fordham Law Review* 983 (2004) John Leubsdorf, "Toward a History of the American Rule on Attorney Fee Recovery," 47 *Law and Contemporary Problems* 9 (1984).
+See also Peter Karsten, "Enabling the Poor to Have Their Day in Court: The Sanctioning of Contingency Fee Contracts, A History to 1940," *DePaul Law Review* 47 (1998): 231; Norman Spaulding, "The Luxury of the Law: The Codification Movement and the Right to Counsel," *Fordham Law Review* 73 (2004): 983; John Leubsdorf, "Toward a History of the American Rule on Attorney Fee Recovery," *Law and Contemporary Problems* 47 (1984): 9.
 
@@
 On homestead exemptions, see Final Report of the Commissioners, 353--354, § 839; James W.
-Ely, "Homestead Exemption and Southern Legal Culture," in Sally Hadden & Patricia Minter eds., *Signposts: New Directions in Southern Legal History* (University of Georgia 2013), 289--314; Paul Goodman, "The Emergence of Homestead Exemption in the United States: Accommodation and Resistance to the Market Revolution, 1840--1880," 80 *Journal of American History* 470 (1993).
+Ely, "Homestead Exemption and Southern Legal Culture," in Sally Hadden & Patricia Minter eds., *Signposts: New Directions in Southern Legal History* (University of Georgia 2013), 289--314; Paul Goodman, "The Emergence of Homestead Exemption in the United States: Accommodation and Resistance to the Market Revolution, 1840--1880," *Journal of American History* 80, no.
+2 (1993): 470--498.
 
@@
 
-[^22]: On the French procedure code, see C.H.
+[^22]: On the French procedure code, see C.
+H.
 van Rhee, *European Traditions in Civil Procedure* (Antwerp 2005).
@@
 So long as the law of civil and criminal obligations and the law of property were sufficiently codified, a "natural procedure" arising from judicial discretion and flexibility would be superior to "technical" written rules.
-Later in his career Bentham produced the "Outlines of a Procedure Code" as a "provisional" remedy, but he insisted that a procedure code on its own could not be "invested with the form of law" without "reference to the codes of law, penal and non-penal, to which it has for its object and purpose the giving execution and effect." Although it spanned nearly 200 pages, Bentham's code favored general moral maxims over precise details, for instance: "On each occasion, have constant regard for all the several ends of justice; that is to say, minimize the sum, or the balance of evil." Jeremy Bentham, Principles of Judicial Procedure with the Outline of a Procedure Code, in John Bowring, ed., *Works of Jeremy Bentham* (2d.
-ed.
-1843 \[1839\]), 1--189, preface and 28, ch.
+Later in his career Bentham produced the "Outlines of a Procedure Code" as a "provisional" remedy, but he insisted that a procedure code on its own could not be "invested with the form of law" without "reference to the codes of law, penal and non-penal, to which it has for its object and purpose the giving execution and effect." Although it spanned nearly 200 pages, Bentham's code favored general moral maxims over precise details, for instance: "On each occasion, have constant regard for all the several ends of justice; that is to say, minimize the sum, or the balance of evil." Jeremy Bentham, Principles of Judicial Procedure with the Outline of a Procedure Code, in John Bowring, ed., *Works of Jeremy Bentham*, 2nd ed.
+(1843 \[1839\]), 1--189, preface and 28, ch.
 7 § 1.
@@
 3, no.
-47, (New York 1849), 2, 12--15.
+47 (New York, 1849), 2, 12--15.
 
@@
 
-[^29]: *The Miner's Express* (Dubuque), February 26, 1851.
+[^29]: *The Miner's Express* (Dubuque, IA), February 26, 1851.
 
-[^30]: Full citations to all of the codes that we used, plus links to electronic versions at the Hathi Trust, Google Books or other sources when available are available at Kellen Funk, *American Legislation Project* (2015--): <http://kellenfunk.org/legislation>.
+[^30]: For full citations to all of the codes that we used, plus links to electronic versions at the Hathi Trust, Google Books or other sources when available, see Kellen Funk, *American Legislation Project* (2015--): <http://kellenfunk.org/legislation>.
 
 [^31]: We have preferred to use the term "digital history" when referring to our own work, in part because the term "digital humanities" has largely come to refer to the work of digital literary and digital media scholars, but primarily because we wish to see digital scholars make disciplinary, rather than interdisciplinary contributions.
+We are working primarily in the field formerly known as humanities computing, but there are other forms of digital history such as digital public history or spatial history.
 On the role of disciplines and the importance of field specific argumentation, see, Stephen Robertson, "The Differences between Digital Humanities and Digital History," 289--307, and Cameron Blevins, "Digital History's Perpetual Future Tense," 308--324, both in *Debates in the Digital Humanities 2016*, ed.
@@
 On the uselessness of the term "big data," see Ted Underwood, "Against (Talking About) 'Big Data,'" *The Stone and the Shell*, blog post, 10 May 2013: <https://tedunderwood.com/2013/05/10/why-it-matters-that-we-dont-know-what-we-mean-by-big-data/>.
+For an overview of digital history projects involving text analysi, see the Roberston essay cited above.
 For an example of curating a corpus aimed at research questions, see Ted Underwood, Boris Capitanu, Peter Organisciak, Sayan Bhattacharyya, Loretta Auvil, Colleen Fallaw, J.
@@
 
-[^33]: William Wirt Blume, "Adoption in California of the Field Code of Civil Procedure: A Chapter in American Legal History," 17 *Hastings Law Journal* 701 (1966); Stephen J.
+[^33]: William Wirt Blume, "Adoption in California of the Field Code of Civil Procedure: A Chapter in American Legal History," *Hastings Law Journal* 17 (1966): 701; Stephen J.
 Field, *Personal Reminiscences of Early Days in California* (1893), 75--78.
@@
 [^36]: We filtered this matrix based on what we knew about the process of borrowing.
-We removed any match below a threshold that we determined by reading pairs of matches.
+We removed any match below a threshold that we determined by checking a sample of matches.
 Because Jaccard similarity scores are symmetric, we also removed anachronistic matches.
@@
 Furthermore, in chains of borrowing (e.g., NY1850 to CA1851 to CA1868 to CA1872 to MT1895) the latest section might have a high similarity to all of its ancestors, but it was in fact borrowed only from the most recent parent.
-We therefore filtered the similarity matrix to remove matches within the same code; anachronistic matches; spurious matches beneath a certain threshold.
+We therefore filtered the similarity matrix to remove matches within the same code, anachronistic matches, and spurious matches beneath a certain threshold.
 Then if a section had multiple matches, we kept the match from the chronologically closest code, giving preference to codes from the same state, unless there was a substantially closer match from a different code.
@@
 [^37]: We have released two repositories with all the code used for this project.
-Lincoln Mullen, "textreuse: Detect Text Reuse and Document Similarity," R package version 0.1.3 (2015--): <https://github.com/ropensci/textreuse>, includes the LSH and other algorithms that we used for general purpose application.
+Lincoln Mullen, "textreuse: Detect Text Reuse and Document Similarity," R package version 0.1.3 (2015--): <https://github.com/ropensci/textreuse>, includes our implementation of LSH and other algorithms suitable for use by other scholars.
 (This package was peer-reviewed by rOpenSci, a collective of academic developers who use the R programming language.) A second repository contains all of our code specific to the migration of the Field Code: <https://github.com/lmullen/civil-procedure-codes/>.
+These are the most essential software packages that we used, except for those cited elsewhere: R Core Team, "R: A language and environment for statistical computing," R Foundation for Statistical Computing, Vienna, Austria (2016): <https://www.R-project.org/>; Hadley Wickham and Romain Francois, "dplyr: A Grammar of Data Manipulation," R package version 0.4.3 (2016): <https://CRAN.R-project.org/package=dplyr>; Hadley Wickham and Winston Chang.
+"ggplot2: An Implementation of the Grammar of Graphics," R package version 2.1.0 (2016): <https://CRAN.R-project.org/package=ggplot2>; Hadley Wickham, "stringr: Simple, Consistent Wrappers for Common String Operations," R package version 1.0.0 (2016): <https://CRAN.R-project.org/package=stringr>; Hadley Wickham, “tidyr: Easily Tidy Data,” R package version 0.4.1 (2016): <https://CRAN.R-project.org/package=tidyr>;  Gabor Csardi and T.
+Nepusz, "The igraph Software Package for Complex Network Research," *InterJournal, Complex Systems* 1695 (2006): <http://igraph.org>.
 
-[^38]: Our attention to big and small scales is the main aim described in Shawn Graham, Ian Milligan, and Scott Weingart, *Exploring Big Historical Data: The Historian’s Macroscope* (Imperial College Press, 2015).
+[^38]: Attention to big and small scales is described in Shawn Graham, Ian Milligan, and Scott Weingart, *Exploring Big Historical Data: The Historian’s Macroscope* (Imperial College Press, 2015).
 
@@
 [^43]: Brendan J.
-Frey and Delbert Dueck, "Clustering by Passing Messages Between Data Points," *Science* 315 (2007): 972--976, doi: 10.1126/science.1136800; Ulrich Bodenhofer, Andreas Kothmeier, and Sepp Hochreiter, "APCluster: an R package for affinity propagation clustering," *Bioinformatics* 27 (2011): 2463--2464, doi:10.1093/bioinformatics/btr406.
+Frey and Delbert Dueck, "Clustering by Passing Messages Between Data Points," *Science* 315 (2007): 972--976, doi: 10.1126/science.1136800; Ulrich Bodenhofer, Andreas Kothmeier, and Sepp Hochreiter, "APCluster: An R package for Affinity Propagation Clustering," *Bioinformatics* 27 (2011): 2463--2464, doi:10.1093/bioinformatics/btr406.
 Even though the affinity propagation algorithm did not fully converge with our dataset, it did an adequate job clustering the documents.
@@
 
-[^44]: Samuels, Lisa, and Jerome McGann.
-"Deformance and Interpretation." *New Literary History* 30.1 (1999): 25--56; Mark Sample, "Notes toward a Deformed Humanities," blog post, 2 May 2012: <http://www.samplereality.com/2012/05/02/notes-towards-a-deformed-humanities/>; Ramsay, *Reading Machines*, 32--57.
+[^44]: Lisa Samuels and Jerome McGann, "Deformance and Interpretation" *New Literary History* 30, no.
+1 (1999): 25--56; Mark Sample, "Notes toward a Deformed Humanities," blog post, 2 May 2012: <http://www.samplereality.com/2012/05/02/notes-towards-a-deformed-humanities/>; Ramsay, *Reading Machines*, 32--57.
 
@@
 
-[^47]: Elliott West, "Reconstructing Race," 34 *Western Historical Quarterly* 6 (2003).
-See also Heather Cox Richardson, *West from Appomattox: The Reconstruction of America after the Civil War* (New Haven: Yale University Press, 2007); Sven Beckert, *Monied Metropolis: New York City and the Consolidation of the American Bourgeoisie, 1850--1896* (Harvard 2003); Mark Wahlgren Summers, *The Ordeal of the Reunion: A New History of Reconstruction* (Chapel Hill: University of North Carolina Press, 2014).
-The major application of the Greater Reconstruction idea to legal history has been Sarah Barringer Gordon, *The Mormon Question: Polygamy and Constitutional Conflict in Nineteenth-Century America* (Chapel Hill: University of North Carolina Press, 2003).
+[^47]: Elliott West, "Reconstructing Race," *Western Historical Quarterly* 34 (2003): 6.
+See also Heather Cox Richardson, *West from Appomattox: The Reconstruction of America after the Civil War* (Yale University Press, 2007); Sven Beckert, *Monied Metropolis: New York City and the Consolidation of the American Bourgeoisie, 1850--1896* (Harvard, 2003); Mark Wahlgren Summers, *The Ordeal of the Reunion: A New History of Reconstruction* (University of North Carolina Press, 2014).
+The major application of the Greater Reconstruction idea to legal history has been Sarah Barringer Gordon, *The Mormon Question: Polygamy and Constitutional Conflict in Nineteenth-Century America* (University of North Carolina Press, 2003).
 
 [^48]: See, for instance, Rogers Smith, *Civic Ideals: Conflicting Visions of Citizenship in U.S.
-History* (Yale 1999); Meg Jacobs, William J.
+History* (Yale, 1999); Meg Jacobs, William J.
 Novak, and Julian E.
-Zelizer, eds., *The Democratic Experiment: New Directions in American Political History* (Princeton 2003); Edward Purcell, *Litigation and Inequality: Federal Diversity Jurisdiction in Industrial America, 1870--1958* (Oxford 1992).
+Zelizer, eds., *The Democratic Experiment: New Directions in American Political History* (Princeton, 2003); Edward Purcell, *Litigation and Inequality: Federal Diversity Jurisdiction in Industrial America, 1870--1958* (Oxford, 1992).
 
-[^49]: Naomi Lamoreaux and John Joseph Wallis, "States, Not Nation: The Sources of Political and Economic Development in the Early United States," Paper Presented at the Economic History Workshop, Harvard University, March 4, 2016.
+[^49]: Naomi Lamoreaux and John Joseph Wallis, "States, Not Nation: The Sources of Political and Economic Development in the Early United States," paper presented at the Economic History Workshop, Harvard University, March 4, 2016.
 
@@
 [^57]: Gordon Morris Bakken, *Practicing Law in Frontier California* (Nebraska 1991), 51--54.
-The new western history ushered in by Patricia Nelson Limerick, *The Legacy of Conquest: The Unbroken Past of the American West* (Norton 1987) and Richard White, *"It's Your Misfortune and None of My Own": A History of the American West* (Oklahoma 1991) is now returning to issues of political economy.
-See Patricia Nelson Limerick, *A Ditch in Time: The City, the West, and Water* (Fulcrum 2012); Richard White, *Railroaded: The Transcontinentals and the Making of Modern America* (Norton 2011).
+The new western history ushered in by Patricia Nelson Limerick, *The Legacy of Conquest: The Unbroken Past of the American West* (Norton, 1987) and Richard White, *"It's Your Misfortune and None of My Own": A History of the American West* (Oklahoma, 1991) is now returning to issues of political economy.
+See Patricia Nelson Limerick, *A Ditch in Time: The City, the West, and Water* (Fulcrum, 2012); Richard White, *Railroaded: The Transcontinentals and the Making of Modern America* (Norton, 2011).
 
@@
 [^61]: See Gunther A.
-Weiss, "The Enchantment of Codification in the Common-Law World," 25 *Yale Journal of International Law* 435 (2000).
+Weiss, "The Enchantment of Codification in the Common-Law World," *Yale Journal of International Law* 25 (2000): 435.
 For a thorough study of the ideology of codification in India, see Robert A.
@@
 [^62]: See, for instance, James C.
-Carter's classic defense of the common law against codification, The Ideal and the Actual in the Law, Address to the American Bar Association, August 21, 1890, at 28 ("the legislature should never attempt to perform the function of the judge, that of simply ascertaining and declaring existing customs.
+Carter's classic defense of the common law against codification, "The Ideal and the Actual in the Law," Address to the American Bar Association, August 21, 1890, at 28 ("the legislature should never attempt to perform the function of the judge, that of simply ascertaining and declaring existing customs.
 This is the work of experts who can qualify themselves only by the devotion of their lives.").
 
-[^63]: See, for instance, "Note," 29 *Albany Law Journal* 141, 142 (1884); Millar, *Civil Procedure of the Trial Court*, 55--56.
+[^63]: See, for instance, "Note," *Albany Law Journal* 29 (1884): 141--42; Millar, *Civil Procedure of the Trial Court*, 55--56.
 
@@
 [^67]: See, for instance, the summary of the states-as-laboratories literature in Brian Galle & Joseph Leahy, "Laboratories of Democracy?
-Policy Innovation in Decentralized Governments," 58 *Emory Law Journal* 1333 (2009).
+Policy Innovation in Decentralized Governments," *Emory Law Journal* 58 (2009): 1333.
 
 [^68]: See Daniel Ernst, *Tocqueville's Nightmare: The Administrative State Emerges in America, 1900--1940* (Oxford: Oxford University Press, 2014); Jerry L.
-Mashaw, *Creating the Administrative Constitution: The Lost One Hundred Years of American Administrative Law* (Yale Law Library 2012); Gautham Rao, *National Duties: Custom Houses and the Making of the American State* (University of Chicago 2016).
+Mashaw, *Creating the Administrative Constitution: The Lost One Hundred Years of American Administrative Law* (Yale Law Library, 2012); Gautham Rao, *National Duties: Custom Houses and the Making of the American State* (University of Chicago, 2016).
 

### 2016-06-29 article/article.Rmd
Make text of the sections part of the article

@@
 The first pair is from the final draft of the New York Field Code.
-These sections completely abolished prior practice and began to rebuild the procedure system from the ground up:
+These sections completely abolished prior practice and began to rebuild the procedure system from the ground up (figure 3).
 
-> § 554.
-The distinction between actions at law and suits in equity, and the forms of all such actions and suits, heretofore existing, are abolished; and, there shall be in this state, hereafter, but one form of civil action, for the enforcement or protection of private rights and the redress or prevention of private wrongs, which shall be denominated a civil action.
-§ 555.
-In such action, the party complaining is known as the plaintiff, and the adverse party as the defendant.
+![Final Report of the Commissioners on Practice and Pleadings (New York, 1850), 225--25,  §§ 554--555.](NY1850-text.png)
 
-In the theory of Euro-American lawyers, California had no prior practice to abolish, so the code began more simply:
+In the theory of Euro-American lawyers, California had no prior practice to abolish, so the code began more simply (figure 4).
 
-> § 1.
-There shall be in this State but one form of Civil Action, for the enforcement or protection of private rights, and the redress or prevention of private wrongs.
-§2.
-In such action the party complaining shall be known as the plaintiff, and the adverse party as the defendant.
+![1851 California Laws 51 §§ 1--2.](CA1851-text.png)
 
@@
                                angle = 15)) + 
-  geom_node_point(aes(shape = as.factor(distance)), size = 5) +   
+  geom_node_point(aes(color = as.factor(distance)), size = 5) +   
   scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") +    

### 2016-06-29 article/article.Rmd
Kellen's changes to draft, shortens it quite a bit

@@
 At the opening of the first Nevada legislature in 1861, Territorial Governor James W.
-Nye, a former New York lawyer, instructed the assembly that they would have to forsake the Mormon statutes of Utah Territory from which Nevada had been carved.
-Those laws were ill adapted to "the mining interests" of the new territory, but "happily for us, a neighboring State whose interests are similar to ours, has established a code of laws" sufficiently attractive to "capital from abroad." That neighbor, of course, was California, and Nye urged that California's code of civil practice be enacted in Nevada, as far as it could "be made applicable."[^1] Territorial Senator William Morris Stewart, a famed silver-mining lawyer who would become the leading U.S.
-senator of Reconstruction, followed the instructions perhaps too well.
+Nye, a former New York lawyer, instructed the assembly that they would have to forsake their inherited Mormon statutes that were ill adapted to "the mining interests" of the new territory.
+"Happily for us, a neighboring State whose interests are similar to ours, has established a code of laws" sufficiently attractive to "capital from abroad." That neighbor was California, and Nye urged that California's "Practice Code" be enacted in Nevada, as far as it could "be made applicable."[^1] Territorial Senator William Morris Stewart, a famed mining lawyer who would lead the U.S.
+Senate during Reconstruction, followed the instructions perhaps too well.
 Stewart literally cut and pasted the latest *Wood's Digest* of the California Practice Act into the session bill, crossing out *state* and *California* and substituting *territory* and *Nevada* where necessary.
@@
 Even in the few hours he had to read it, Nye counted "many errors in the enrolling of it, numbering probably more than three hundred." Some errors were severe.
-Nevada's Organic Act specified the jurisdiction of the district courts and justices of the peace, but the code overwrote these limitations by copying California's arrangements.
-Error-riddled and unconstitutional as the bill was, Nye believed a civil practice code was a "universal necessity and public need," concluding that "without some legislation in providing a code of procedure in civil cases, it may be a matter of grave question whether your courts would be able to fulfill the purpose of their creation."[^2] Nye signed the code into law.
+The code overwrote the specific jurisdictional boundaries of Nevada’s Organic Act by copying California’s arrangements.
+Error-riddled and unconstitutional as the bill was, Nye believed a civil practice code was a "universal necessity and public need," doubting "whether your courts would be able to fulfill the purpose of their creation" without one.[^2] Nye signed the code into law.
 
-Nothing like this "universal necessity" for a code of practice existed when Nye began his legal career in New York in the 1840s; rather, it was one of the central developments of America law during the nineteenth-century.
-By the end of the nineteenth-century, thirty-one American states and territories had adapted the text of a New York code of civil procedure first promulgated in 1848.
-The code became known as the Field Code, after its chief draftsman David Dudley Field, a famed Manhattan trial lawyer.[^3] When Field's code appeared in the Colorado assembly in 1876, a Denver newspaper wryly commented, "The scissors and paste-pot we had heretofore confidently believed were implements peculiar to the newspaper sanctum." To the editor, the cut-and-paste code was not just a curiosity of legislative history.
+Nothing like this "universal necessity" existed when Nye began his legal career in New York in the 1840s; rather, it was one of the central developments of America law after the mid-nineteenth century.
+By 1900, thirty-one American states and territories had adapted the text of a New York code of civil procedure first promulgated in 1848.
+The code became known as the Field Code, after its chief draftsman David Dudley Field, a Manhattan trial lawyer.[^3] When Field's code appeared in the Colorado assembly in 1876, a Denver newspaper wryly commented, "The scissors and paste-pot we had heretofore confidently believed were implements peculiar to the newspaper sanctum." To the editor, the cut-and-paste code was not just a curiosity of legislative history.
 Rather, the extensive copying of Field's Code threatened the foundations of American popular sovereignty.
-"The bill is a long one; the assembly has not the time to devote to it and to give it the scrutiny that a measure of such importance demands," he explained.
-Blind approval "would be an injustice to themselves and a greater wrong and injustice to the people who have a right to demand that their public servants legislate for the public good." The code "has been 'assimilated,' as we are informed, 'to the character and requirements of our people,' whatever that may mean," but the editor feared the legislation was the product of "men who have the welfare of the 'dear people' at their tongue's end always, but never in their hearts."[^4]
+"The bill is a long one; the assembly has not the time to devote to it and to give it the scrutiny that a measure of such importance demands.” Blind approval "would be an injustice to themselves and a greater wrong and injustice to the people who have a right to demand that their public servants legislate for the public good." The code "has been 'assimilated,' as we are informed, 'to the character and requirements of our people,' whatever that may mean," but the editor feared the legislation was the product of "men who have the welfare of the 'dear people' at their tongue's end always, but never in their hearts."[^4]
 
 The migration of the Field Code was a central event in Anglo-American legal history, but no historian has traced the extensive borrowings of the Field text nor recognized the political furor that greeted the code outside New York.[^5] Every aspect of a civil justice system, from the rules granting access to courts, to lawyers, to remedies (whether damages, injunctions, or seizure of property) was covered by the code, making its New York-specific rules politically contentious both inside and outside the Empire State.
-As the Field Code migrated around the country, commentators in each jurisdiction raised the same complaint: how could legislation borrowed from another state represent the popular will and bests interests of *this* state?
+As the Field Code migrated around the country, commentators in each jurisdiction raised the same complaint: how could legislation borrowed from another state represent the popular will and best interests of *this* state?
 
@@
 Exploring these borrowings is a daunting task, however.
-Procedure codes were long, technical documents, and although each jurisdiction copied large swaths of text, each also modified the text along the way, sometimes with a simple *Nevada* for *California*, sometimes with more foundational changes to the remedial system.
+Procedure codes were long, technical documents, and although each jurisdiction copied large swaths of text, each also modified the text along the way, sometimes with a simple *Nevada* for *California*, sometimes with more foundational changes to civil remedies.
 Although Stewart's cut-and-paste code found its way into the archives, most draft legislation did not, and few codifiers explained in detail how they produced their texts.
-Traditional close reading or textual criticism of some 98,000 distinct sections of law comprising some 7.7 million words is simply not a feasible research task for a historian who wishes to track these borrowings.
+Traditional close reading or textual criticism of some 98,000 distinct sections of law comprising 7.7 million words is simply not a feasible research task for a historian who wishes to track these borrowings.
 
-Yet by turning to the digital analysis of texts, we have resolved this difficulty and tracked how states borrowed their codes of civil procedure from one another.
+Yet by turning to the digital analysis of texts, we have resolved this difficulty and tracked how states borrowed their codes of civil practice from one another.
 Within the corpus of legislation, algorithmic analysis of texts can reverse engineer and visualize what the archive revealed in figure 1: which texts were borrowed, which modified, and how extensively.
 Our method works especially well for legal texts, for reasons we will explain.
-However, scholars can extend this method to other kinds of curated collection of texts, from church hymns to medical treatises.
+However, scholars can extend this method to other curated collections of texts, from church hymns to medical treatises.
 
-The first contribution of this article is to demonstrate our methods as applied to a corpus of nineteenth-century state procedure codes.
+The first contribution of this article is to demonstrate our methods as applied to a corpus of nineteenth-century civil procedure codes.
 The second contribution is to integrate what we learned from the text analysis with the more conventional approaches of political and cultural history to explain why the migration of the Field Code mattered.
 On the national level the extent of legislative borrowing followed a pattern American historians have described as a "Greater Reconstruction" in which the former Confederate South and the Far West showed a remarkable kinship.
-Scholars have typically described Greater Reconstruction as a federal development, featuring the creation of national citizenship, a national economy, and a larger state apparatus centered in Washington, D.C.
+Scholars have typically described Greater Reconstruction as a federal development, featuring the creation of national citizenship, a national economy, and a larger federal apparatus centered in Washington, D.C.
 This article shows that Greater Reconstruction had its state-level dimensions as well.
@@
 
-## 1. The origin and migration of the Field Code
+## 1. The origin and political controversies of the Field Code
 
 Until 1848, civil remedies and trial practice in New York were largely governed by common law traditions loosely categorized as "practice and pleadings."[^6] To understand how to file a civil claim or to enforce a judgment, a lawyer had to consult ad hoc statutes from colonial times to the present as well as precedents reported from cases litigated at common law and chancery.
-By the 1840s, enterprising practitioners had collated these materials into a half dozen marketable treatises, but these remained works of private opinion---no court was bound to agree with the treatise writers as to the weight, relevance, or proper interpretation of a legal statement.[^7] The common law was accordingly known as "unwritten law" despite the proliferation of published texts, because the common law was not precisely determined until a particular case drawn from the messy facts of life demanded resolution.[^8] Statutes, on the other hand, were "written law," prescribing or reforming the rules even before a case put the precise question in issue.
+By the 1840s, enterprising practitioners had collated these materials into a half dozen marketable treatises, but these remained works of private opinion---no court was bound to agree with the treatise writers as to the weight, relevance, or proper interpretation of a legal statement.[^7] The common law was accordingly known as "unwritten law" despite the proliferation of published texts, because the common law was not precisely determined until a particular case demanded resolution.[^8] Statutes, on the other hand, were "written law," prescribing or reforming the rules even before a case put the precise question in issue.
 Within the realm of written law, codes were the ultimate statutes.[^9]
@@
 
-In New York, these codification debates came to a head at the 1846 constitutional convention, where "the conquerors took all," as the ambivalent Jacksonian James Fenimore Cooper complained.[^12] Law reformers abolished the court of chancery, made judges stand for popular election, and required the legislature to appoint a commission to reform the "practice and pleadings" of the civil courts.[^13]
+In New York, these codification debates came to a head at the 1846 constitutional convention, where "the conquerors took all," as the ambivalent Jacksonian James Fenimore Cooper complained.[^12] Law reformers abolished the court of chancery, made judges stand for popular election, and required the legislature to appoint commissioners to codify the law and reform the "practice and pleadings" of the civil courts.[^13]
 
@@
 Royal commissions had been employed since before the Revolution of 1688 to advise on a variety of matters.
-After the Revolution, royal commissions became disfavored while Parliament undertook many of the same functions through "committees of enquiry" to which only members of Parliament were appointed.
-By the nineteenth century, royal commissions again became common.
-Royal commissioners were usually not legislators.
-Although by the mid-nineteenth century royal commissions sometimes offered model statutes, the legislation they advised still had to pass through the normal politicking and drafting processes of Parliament.[^15]
+Although by the mid-nineteenth century royal commissions sometimes offered model statutes, Parliament maintained exclusive legislative prerogatives, forcing any commissioner-proposed legislation to pass through the normal politicking and drafting processes of Parliament.[^15]
 
@@
 Each time they reminded legislators that "public opinion had issued its mandate in the most imposing form" of a constitutional decree.
-The constitution, together with the legislative act appointing the commission, "gave the commissioners instructions so precise, as to leave them no discretion, if they had desired it, \[and\] promised them therefore in advance, so long as they obeyed those instructions, the concurrence and co-operation of all departments of the government."[^16] Although the theory of codification made it a democratic enterprise, in practice Field---an ardent Jacksonian---insisted the democratic legislature ought to defer to the expertise of the commissioners.
+The constitution, together with the legislative act appointing the commission, "gave the commissioners instructions so precise, as to leave them no discretion, if they had desired it, \[and\] promised them therefore in advance, so long as they obeyed those instructions, the concurrence and co-operation of all departments of the government."[^16] Although the theory of codification made it a democratic enterprise, in practice Jacksonians like Field insisted the democratic legislature ought to defer to the expertise of the commissioners.
 
@@
 
-Yet the scope of the procedure Code included far more than the "mere machinery" of a lawsuit.[^18] The final draft of the code, printed in 1850, spanned nearly 800 pages of 1,885 regulations.
+Yet the code's scope of "procedure" included far more than the "mere machinery" of a lawsuit.[^18] The final draft of the code, printed in 1850, spanned nearly 800 pages of 1,885 regulations.
 The first third of the code covered constitutional topics, specifying the jurisdiction of all state courts and the duties of all state officers (and liabilities for violating those duties).
@@
 Remedies were thus intimately connected to substantive law.
-For that reason, neither the French *code de procédure civile* (1806) nor Blackstone's and Bentham's writings conceived of remedies as purely procedural.[^22] By codifying remedies, Field invited continual expansion of the category of "procedure." As other states adopted the procedure code, they sometimes included other fields of law that seemed obviously "substantive" yet had such specific procedures or remedies that they were placed in a "code of procedure." Such fields included the law of wills, corporations, and mortgages.[^23] After all, argued procedural codifiers in Iowa, what did the famed Married Women's Property Acts offer besides procedural reform?
+For that reason, neither the French *code de procédure civile* (1806) nor Blackstone or Bentham's writings conceived of remedies as purely procedural.[^22] By codifying remedies, Field invited continual expansion of the category of "procedure." As other states adopted the procedure code, they sometimes included other fields of law that seemed obviously "substantive" yet had such specific procedures or remedies that they were placed in a "code of procedure." Such fields included the law of wills, corporations, and mortgages.[^23] And after all, argued procedural codifiers in Iowa, what did the famed Married Women's Property Acts offer besides procedural reform?
 These acts gave women *standing* to litigate in their own name and seek *remedies* in claims of property and contract, and they abolished mandatory rules of *joinder* (of husbands).
@@
 Despite Field's arguments that a mere procedure code was democratically unproblematic, his efforts were not entirely successful in New York.
-The commission submitted a draft of its main reforms in 1848, emphasizing that this first code was "but a report in part." New York's legislators enacted the partial code with little amendment, some legislators repeating Field's view that the constitution obligated them to accept the code.[^25] But when the commissioners submitted their final draft in 1849, the Assembly judiciary committee balked, directly disputing the commissioners' claims that procedure was merely the machinery of the law.
-They wrote that "provisions for rights and for the mode of pursuing remedies, insensibly run into each other," and observed that distinctions between substance and procedure were difficult to draw in practice.
-In fact, "the parts of a system of law are more dependent on each other, and run into and affect each other, infinitely more than any machine of human contrivance." They therefore suspected the commissioners' forthcoming code of criminal procedure would include all of the criminal law as well, "as they seem to understand practice and pleadings to include all the law upon a given subject." That being the case, the committee wondered whether they should "place in \[the commissioners\] a blind and implicit confidence that shall commit to their discretion the peace and property, the personal liberty and the lives of those who sent *us* here to make laws for them?"[^26]
+The commission submitted a draft of its main reforms in 1848, emphasizing that this first code was "but a report in part." New York's legislators enacted the partial code with little amendment, some legislators repeating Field's view that the constitution obligated them to accept the code.[^25] But when the commissioners submitted an extended draft in 1849, the Assembly judiciary committee balked, directly disputing the commissioners' claims that procedure was merely the machinery of the law.
+The "provisions for rights and for the mode of pursuing remedies, insensibly run into each other," the committee reported, complicating legal practice "infinitely more than any machine of human contrivance." They therefore suspected the commissioners' forthcoming code of criminal procedure would include all of the criminal law as well, "as they seem to understand practice and pleadings to include all the law upon a given subject." That being the case, the committee wondered whether they should "place in \[the commissioners\] a blind and implicit confidence that shall commit to their discretion the peace and property, the personal liberty and the lives of those who sent *us* here to make laws for them?"[^26]
 
@@
 The date shown is the date of the first enactment of a procedure code; most states subsequently revised their codes.
-Note that many southern states and western states came to adopt the Field Code during the period of Greater Reconstruction.
+Note that many southern states and western states came to adopt the Field Code during the Civil War and Reconstruction.
 By the end of the nineteenth-century, thirty-one jurisdictions (those displayed on the map, plus Alaska) had adopted a version of the Field Code.
@@
 Even the shortest version of the Field Code was significantly longer than any other state statute before the Progressive legislation of the twentieth century.
-Unlike statutory compilations that sometimes took the name of a "code" but made no changes to existing law, the Field Code opened by abolishing the hallmarks of prior practice and instituting "hereafter" a new form of action with substantial revisions to basic matters of standing, remedy, and enforcement of civil judgments.[^27] In the states where it was imported, there was no getting around the fact that the code introduced much new law, yet legislators were unable to read, critique, and amend the code within the brief period of a legislative session.
+Unlike statutory compilations that sometimes took the name of a "code" but made no changes to existing law, the Field Code opened by abolishing the hallmarks of prior practice and instituting "hereafter" a new form of action with substantial revisions to basic matters of civil remedies.[^27] In the states where it was imported, there was no getting around the fact that the code introduced much new law, yet legislators were unable to read, critique, and amend the code within the brief period of a legislative session.
 "It is folly to undertake to pass a code in a sixty day session," wrote the *Montana Post*, "and the best way would be for the Assembly to select one from a State or Territory which would come near meeting our wants, and slide it through with the fewest changes possible."[^28] Sliding the code through eased the problem of time but exacerbated the problem of local sovereignty.
@@
 How, then, did states and territories achieve a politically acceptable balance between efficiency and sovereignty, borrowing law for sake of time but endowing it with popular legitimacy in each locale?
-Quite apart from the technicalities of legal practice, the American federation of civil government into (depending on the year) more than thirty or forty separate state jurisdictions makes it hard to describe a phenomenon that was truly national despite its state-centered enactments.
+Quite apart from the technicalities of legal practice, the American federation of civil government into (depending on the year) more than thirty or forty separate jurisdictions makes it hard to describe a phenomenon that was truly national despite its state-centered enactments.
 It requires a sense of how much law was borrowed in each location and to what degree innovations were introduced.
@@
 
-To discover how the Field Code migrated to other jurisdictions, we compiled a corpus of relevant (or possibly relevant) laws, including separately bound codes of civil procedure as well as codes or regulations appearing as session laws and statutory compilations.
+To discover how the Field Code migrated to other jurisdictions, we compiled a corpus of potentially relevant laws, including separately bound codes of civil procedure as well as codes or statutes appearing within session laws and statutory compilations from around the Atlantic world.
 The corpus comprises 135 statutes from the nineteenth century, which amounts to 7.7 million words organized into 98,000 regulations.
-It includes the initial enactment of every code of civil procedure, as well as procedure statutes and re-enacted codes from states reputed to have been legally influential, but it does not include every known statute of American procedural law.
-While a comprehensive project may be illuminating in its own ways, our specific question of how New York legislation influenced other states permits a more curated corpus.[^30]
+It includes the initial enactment of every U.S.
+code of civil procedure, as well as procedure statutes and re-enacted codes from jurisdictions reputed to have been legally influential, including French and British codes.
+The corpus does not include every nineteenth-century statute of procedural law.
+While a comprehensive project may be illuminating in its own ways, our specific question of how New York legislation influenced other American jurisdictions permits a more curated corpus.[^30]
 
@@
 Speaking in broad terms, digital historical work---like all historical work---can begin either with a set of sources or with a question.
-Computational digital history is often conceived of as beginning with very large datasets such as the Google Books or Hathi Trust corpora.
-These large corpora are sometimes called "big data"---though, it must be emphasized, almost never by digital historians who actually work with them---and are used as the basis of a "distant reading." We think that working with these large corpora is worthwhile because it is salutary for historians to have their research questions shaped by the broadest possible contexts.
-Nevertheless, it is not apparent that digital historians can readily move from these omnibus corpora to answering the specific research questions that animate various historical fields.
+Computational digital history is often conceived of as beginning with sources, particularly with large datasets such as the Google Books or Hathi Trust corpora.
+These large corpora are sometimes called "big data"---though, it must be emphasized, almost never by digital historians who actually work with them---on which "distant reading" can be practiced.
+While it is salutary for historians to have their research questions shaped by the broadest possible contexts, it is not apparent that digital historians can readily move from these omnibus corpora to answering the specific research questions that animate various historical fields.
 In this article we demonstrate an alternative approach, which we might unimaginatively label "medium data." The amount of legislation that governed American civil practice is impressive, since every state amended and re-enacted procedure statutes nearly every decade.
-But while a corpus of procedural legislation requires some computational sophistication, it is far from needing the computational techniques derived for truly big data.
+But while a corpus of procedural legislation requires some computational sophistication, the techniques are far less complex than those derived for truly big data.
 We have gathered a large but narrowly constrained corpus centered on solving a well-defined research question.
@@
 For instance, we know that California's 1851 code was derived from New York's 1850 code.
-(Stephen Johnson Field, David Dudley Field's brother, was the lawyer who imported New York's code into California.[^33]) But the New York code is over 150,000 words long, whereas California's code was just over 50,000 words long.
+(Stephen J.
+Field, David Dudley's brother, was the lawyer who imported New York's code into California.[^33]) But the New York code is over 150,000 words long, whereas California's code was just over 50,000 words long.
 Those disparate lengths mean that comparing all of the California code to all of the New York code is less meaningful than comparing each section in the California code to each section in the New York code, where matching sections will have a similar length.
@@
 This would take an unreasonable amount of computation time, and most of these comparisons would be unnecessary since each section has no relationship to most other sections.
-We therefore implemented the minhash/locality sensitive hashing algorithm to detect pairs of possible matches quickly.This algorithm works by extracting a set number of random tokens from each document to create a document signature; this subset makes it possible to approximate the Jaccard similarity of two documents.
-These signatures can then be used to identify each of the billions of possible pairs of sections as likely to be matches or not.
-By setting parameters to the algorithm, one can control how sensitive the algorithm is in drawing the line between genuine and spurious matches.
-We then measured the actual Jaccard score for only those candidate pairs.[^35]
+We therefore implemented the minhash/locality sensitive hashing algorithm to detect pairs of possible matches quickly.
+Instead of comparing all tokens to one another, this algorithm samples tokens from each document to find probable matches, and then Jaccard scores can be calculated for only those probable matches (that is, many of the needless calculations that produce scores of zero get cut out).[^35]
 
@@
 Variations in the Field drafts meant that different states could borrow different versions of the Field Code.
-The 1850 New York code was the primary progenitor of several families of codes in California, Kentucky, Iowa, and Ohio, each of which in turn became major contributors to the law of neighboring states.
-The 1851 New York code became the progenitor of codes for Wisconsin, Florida, North Carolina, and South Carolina.
-Mississippi and Missouri borrowed from the New York 1849 code.
+Field’s 1850 draft---never actually enacted in New York---was the primary progenitor of several families of codes in California, Kentucky, Iowa, and Ohio, each of which in turn became major contributors to the law of neighboring states.
+The 1851 New York code---a small revision to the original 1848 code---became the progenitor of codes for Wisconsin, Florida, North Carolina, and South Carolina.
 While Field considered the 1850 version to be the definitive, ideal version of the code, all of the New York codes from 1848 to 1853 became models for other jurisdictions.
 In many cases, the commissions likely used whatever version of the code they had at hand.
-The Field Code was not a single volume on the shelf, but a series of volumes, any of which might be more accessible in different regions and in different years.
+The Field Code was not a single volume on the shelf, but a series of drafts, any of which might be more accessible in different regions and in different years.
 
 Even later New York codes can be considered a separate family.
-In 1876 a New York commission produced a new code attempting to consolidate all the statutory amendments subsequent to the 1851 Field Code.
-David Dudley Field was upset by the changes introduced in this revision, called the Throop Code.
-A count by a "friend" of Field's found that only three sentences of the Field Code had carried over word-for-word into the Throop Code.
-Nevertheless, many of the changes were purely formal, and Field speculated that these changes had been made only "so that \[the code\] should not appear to be the same thing as before."[^40] With respect to Mr.
-Field or his "friend," we found that the connection was between the Throop Code and the Field Code was somewhat stronger than he thought, and the Throop Code was indeed a descendant, if much revised, from the Field Code.
+In 1876 a New York commission produced a new code attempting to consolidate all the case law and statutory amendments subsequent to the 1851 Field Code.
+David Dudley Field was upset by the changes introduced in this revision.
+A count by a "friend" of Field's found that only three sentences of the Field Code had carried over word-for-word into the latest edition.
+With respect to Mr.
+Field or his "friend," we found that the connection between the codes somewhat stronger than he thought, although his conclusion that, textually, the 1876 code did "not appear to be the same thing as before," remains sound.[^40]
 
@@
 In addition to the overview of the relationship between codes, we can also see more detail by visualizing the pattern of borrowings within each code.
-We have visualized the origin of each section of every code to see how each code was put together.
 To illustrate this, we will follow one branch of the Field Code network, beginning with the family started by California's 1850 and 1851 codes.
@@
 California's 1850 code, enacted in the period when California was entering the Union as a state, was borrowed almost entirely from New York's 1849 Field Code.
-The compiler Elisha Crosby did lift one significant portion regulating when a judge could order a new trial from the mixed civilian/common law code of Louisiana .
+The compiler Elisha Crosby did lift one portion from the mixed civilian/common law code of Louisiana, the rules for ordering a new trial to revisit an earlier jury’s verdict.
 New trials were not provided for in the New York Code until the finished draft in 1850.
-Most of the sections that were not borrowed, as with many of the codes, have to do with parts that describe the system of courts or provide sample forms peculiar to that state.
+Most of the sections that were not borrowed, as with many of the codes, have to do with parts that describe the system of courts or provide sample forms of pleading or sheriff’s writs that were peculiar to each state.
 
@@
 
-When California revised its procedure code in 1851, for the most part it did not use its own code from the previous year as the basis.
-Rather, the bulk of the 1851 California code came from the updated model code Field completed for New York in 1850.
+When Stephen Field revised California’s code in 1851, he largely redrafted it from the updated code his brother David Dudley had completed for New York in 1850.
 This includes the portion of the code on new trials previously borrowed from Louisiana.[^42] The remainder of the code was borrowed from the 1850 California code.
-The bulk of the borrowings that come from California instead of directly from New York are at the beginning of the code, where the 1850 code had made amendments specific to California.
-(Many of the non-matching sections are tables of contents.) Thus California based the majority of its law of civil procedure entirely on New York's code not one, but twice.
-California made few to no innovations to the Field Code beyond a rearrangement of its provisions.
+(Many of the non-matching sections are tables of contents.) Thus California based the majority of its law of civil remedies entirely on New York's code not once, but twice.
+California made few to no innovations to the Field Code beyond a rearrangement of its provisions and their application to the new state’s particular system of courts.
 
@@
 The pattern of borrowings in the Washington 1855 code was a rather different case.
-The Washington code was definitely in the lineage of the 1851 California code, since it borrowed sections from both California directly and more often from Oregon, which was also derived from California.
+The Washington code was definitely in the lineage of the 1851 California code, since it borrowed sections from both California directly as well as from Oregon (which was also derived from California).
 Indiana's 1852 code and Oregon's 1854 code provide the majority of the borrowings.
@@
 While working on the Washington code, they must have each used the law (and the law books) that they knew best.
-As a second generation variation on a regional code, the Washington code drew from a variety of sources.
+As a second generation variation on a regional code, the Washington code drew from a variety of sources, even though all these sources basically agreed on the substance of the law.
 
@@
 
-Finally, we can consider the case of Washington's revised 1873 code as an example of one of the outermost leaves on the family tree of the Field Code.
-The bulk of this code was taken from the Washington 1855 code with only small amendments.
+Finally, we can examine one of the outermost leaves on the family tree of the Field Code in Washington’s revised code of 1873.
+The bulk of this code was taken from the early Washington code with only small amendments.
 The main exception was lengthy set of sections on probate drawn from California's 1872 code.
@@
 But since our fundamental unit of comparison is section to section, we can use a technique called clustering to group sections based on their similarity to one another, regardless of which code they come from.
-In this case, clustering groups sections of the law which have a high similarity because of their direct textual relationship and which thus share the same topic.
 There are innumerable clustering algorithms, but we used the affinity propagation clustering algorithm because its assumptions aligned with the characteristics of our problem.
@@
 The result was a set of approximately 2,900 clusters which contained at least five sections, though this probably overstates the number of innovative, *ur*-sections in the corpus.
-The biggest cluster, for instance, which concerned the use of affidavits in pleading, contained 103 sections.
+The biggest cluster, which concerned the use of affidavits in pleading, contained 103 sections.
 Within each cluster, we organized the sections chronologically.
@@
 At common law, parties and interested witnesses were not permitted to testify in their own causes.
-Field's Code reversed this rule, expanding witness competency as widely as possible: any person "having organs of sense" could now be admitted as a witness in New York, with only the insane and very young children exempted from the rule.
+Field's Code reversed this rule, expanding witness competency as widely as possible: any person "having organs of sense" was to be admitted as a witness in New York, with only the insane and very young children possibly exempted.
 As the code migrated West, however, legislators added racial exclusions to Field's list.
@@
 The Field Code's summary judgment brought down the time of debt collection to a matter of weeks.
-The code traded the rhythms of agriculture for the rhythms of merchant finance.[^45]
+The code thus traded the rhythms of agriculture for the rhythms of merchant finance.[^45]
 
@@
 
-## 4. Procedure codes and capitalism
+## 4. Procedure codes and American capitalism
 
-The near uniformity of creditors' remedies in Field Code states, as demonstrated by clustering, points out the close link between the rise of civil procedure and capitalism.
-Westerners and southerners commented on these features of the code or its connections to New York capital.
+The near uniformity of creditors' remedies in Field Code states, as demonstrated by clustering, points out the close link between the rise of modern American procedure and modern American capitalism.
+Westerners and southerners frequently commented on the seeming imperialism of the New York code and its connections to New York capital, but one must turn to the technical debates over procedure to find these anxieties.
 Twelve of the states and territories that copied the Field Code most closely did so during the Civil War and Reconstruction era---four states in the former Confederacy and eight jurisdictions in the Far West.[^46] As with other areas of postbellum history, it turns out one may learn a lot by holding the postbellum American South and American West together.
 
-In the last decade, scholars of Reconstruction have broadened the scope of their study to include both the South and the West as two sites in one "Greater Reconstruction." These studies have illustrated the ways that military conquest, rapid industrialization, and the resettlement and education of ethnic minorities developed similarly in each region, guided by economic elites in New York and political administrators in Washington.[^47] In tracing the legal aspects of this Greater Reconstruction, scholars have focused almost entirely on the expansion of federal power or constitutional rights of citizenship and civil equality.[^48] While the 1860s and 1870s were of course a transformative period in the history of civil rights and the creation of a national state, they were also the decades in which many local legal institutions and practices were transformed not by federal power but by state codification.
+In the last decade, scholars of Reconstruction have broadened the scope of their study to include both the South and the West as two sites in one "Greater Reconstruction." These studies have illustrated the ways that military conquest, rapid industrialization, and the resettlement and education of ethnic minorities developed similarly in each region, guided by and political elites in Washington.[^47] In tracing the legal aspects of this Greater Reconstruction, scholars have focused almost entirely on the expansion of federal power or constitutional rights of citizenship and civil equality.[^48] While the 1860s and 1870s were of course a transformative period in the history of civil rights and the creation of a national state, they were also the decades in which many local legal institutions and practices were transformed not by federal power but by state codification.
 Naomi Lamoreaux and John Joseph Wallis have recently argued that in the creation of a modern American economy, "the federal government played *no* role in this process until the Civil War, and even then it played only a bit part." The history of the Field Code's migration helps to substantiate this claim.
-While Lamoreaux and Wallis focus on the development of banking, transportation, and incorporation at the state level, it was the codes of civil procedure that provided the structure of civil remedies which protected these state institutions.
-And procedure codes were the creatures of state governance.[^49]
+While Lamoreaux and Wallis focus on the development of banking, transportation, and incorporation at the state level, it was the Procedure Code that structured civil remedies to protect these institutions.
+And procedure codes were creatures of the states.[^49]
 
-The states that adopted the Field Code were never forced to, and they had other options available to them.
-Southern states with a civilian code tradition such as Louisiana and Alabama offered other options for states desiring to reform common law practice.[^50] Illinois long retained the common law---in later decades lawyers called it "the Yellowstone Park of common law pleading." When Colorado was a territory it imported the Illinois common law to the West via statute, a full fourteen years before its legislature considered the Field Code.
-[^51]
+The states that adopted the Field Code had other options available to them.
+Southern states with a civilian code tradition such as Louisiana and Alabama offered alternative ways to reform common law practice.[^50] Illinois, on the other hand, long retained the common law---in later decades lawyers called it "the Yellowstone Park of common law pleading." When Colorado was a territory it imported Illinois common law via statute, a full seventeen years before its legislature considered the Field Code.[^51]
 
@@
 The early Mormon settlers of Utah persistently avoided the mining frenzy as well as codification.
-By 1870, however, the territory's governor directed the legislature's attention to the recent Code of Nevada, a code "for a people whose interests in many respects are similar to our own." Of course, standing behind the Nevada Code was "the State of New York---a State which is an empire in itself and whose commercial transactions are far greater than those of any other State in the Union." By copying its code, Utah too could be "rewarded by equal advantages."[^52] Code proponents in Colorado similarly parried arguments that a code would be a "foreign" imposition by pointing to the fact that it has been "adopted twenty-nine years ago by the Empire state of the Union" and they promised that the code of the nation's commercial empire could bring wealth in its wake.[^53]
+By 1870, however, the territory's governor directed the legislature's attention to the recent Code of Nevada, a code "for a people whose interests in many respects are similar to our own." Of course, standing behind the Nevada Code was "the State of New York---a State which is an empire in itself and whose commercial transactions are far greater than those of any other State in the Union." By copying its code, Utah too could be "rewarded by equal advantages."[^52] Code proponents in Colorado similarly pointed to the fact that the code had been “adopted twenty-nine years ago by the Empire state of the Union,” and they too hoped that the code of the nation’s commercial empire brought wealth in its wake.[^53]
 
@@
 If we had had this code years ago, Colorado would now have a larger amount of California capital in her mines."[^54] Codifiers argued that, in attracting capital, procedure was at least as important as the substantive rules of property and contract, because procedure secured the remedies that actually protected investments.
-"Men of capital and enterprise will not make investments and devote their time and energies to those works of internal improvement so necessary for the speedy development of our natural resources, and for the settlement and building up the country," Nebraska's governor reasoned, "unless ample protection is afforded them, by legal enactment, for the capital invested and labor employed." And he therefore urged swift passage of the Field Code.[^55]
+"Men of capital and enterprise will not make investments and devote their time and energies to those works of internal improvement," Nebraska's governor reasoned, "unless ample protection is afforded them, by legal enactment, for the capital invested and labor employed." He therefore urged swift passage of the Field Code.[^55]
 
@@
 He encouraged the bar to accommodate themselves to change, for "the New York system ...
-bids fair to become national." Supposedly offering an overview of the code, the articles were almost entirely about credit.
+bids fair to become national." Purporting to give an overview of the code, the articles were almost entirely about credit.
 "How can we create credit?
@@
 by law, and by law alone.
-Let the law enforce punctuality; let the people of North Carolina learn that the great law of business is, that 'time is of the essence of the contract,' and incur no debt that they do not expect to meet at maturity." Under the more certain and speedy remedies of the code, "we may expect that the secret hoards of the frugal among ourselves will be offered to loan, and even that the vaults of the banks of New-York ...
+Let the law enforce punctuality; let the people of North Carolina learn that the great law of business is, that 'time is of the essence of the contract.'" Under the more certain and speedy remedies of the code, "we may expect that ...
+even that the vaults of the banks of New-York ...
 will be open to our industry."[^56]
@@
 The creditors' remedies in the code gave the codifiers their leading argument against criticisms rooted in the ideology of popular sovereignty.
-"There is no doubt but the people are in favor of anything that promises to hurry up that proverbially slow and blind old female called Justice, and they will go for the old code," one Colorado newspaper announced.[^59] New York's "code practice is the best in excellence," stated another, "and when I say *best* I do not mean best for lawyers only, but best for the people---the commonwealth."[^60] If the people favored economic progress, certainty of remedy, and efficiency in proceedings, then they favored the New York code, no matter whether they understood or cared about technical rules of pleading and joinder.
+"There is no doubt but the people are in favor of anything that promises to hurry up ...
+Justice, and they will go for the old code," one Colorado newspaper announced.[^59] New York's "code practice is the best in excellence," stated another, "and when I say *best* I do not mean best for lawyers only, but best for the people---the commonwealth."[^60] If the people favored economic progress, certainty of remedy, and efficiency in proceedings, then they favored the New York code, no matter whether they understood or cared about technical rules of pleading and remedies.
 Thus, in their arguments the codifiers imagined themselves the champions of popular sovereignty, for it was they who accomplished what the people actually desired.
@@
 Thus by the end of Reconstruction, New York's domestic empire of capital and creditors' remedies bore a remarkable resemblance to the international empire administered by England.
-Both jurisdictions, while reforming the practice of law, largely rejected codification within their own borders but encouraged it among their economic dependents.
-The English commissioned a full codification of law for India and colonies in Singapore, while further codifications produced by Field in New York covering civil and penal law were adopted in California and other western jurisdictions.[^61] In both places, leading arguments against codification carried a civilizational logic of empire: advanced societies could not codify their law, for to do so would be to freeze the progress of legal science.
+Both jurisdictions, while reforming the practice of law, remained ambivalent about codification within their own borders but encouraged it among their economic dependents.
+The English commissioned codes for India and Singapore, while Field’s additional codes covering New York’s civil and penal law---ignored in his home state---were adopted in California and other western jurisdictions.[^61] In both England and New York, leading arguments against codification carried a civilizational logic of empire: advanced metropoles could not codify their law, for to do so would be to freeze the progress of legal science.
 What appeared to some to be a hopeless mass of confusion was to common law defenders the sign of true legal sophistication.
-Science was, after all, sophisticated.[^62] The Throop Code came in for censure, both in its first year and in following decades, precisely for trying to capture all the sophistication of the New York legal system within an unwieldy 3,300 rules.[^63] Codification, however, could help developing societies along law's frontier take a progressive leap forward.
+Science was, after all, complex.[^62] The later editions of the New York Procedure Code came in for censure precisely for trying to capture all the sophistication of the New York legal system within an unwieldy 3,300 rules.[^63] Codification, however, could help developing societies along law's frontier take a progressive leap forward.
 As India's chief codifier Thomas Macaulay explained, codification "cannot be well performed in an age of barbarism," but also "cannot without great difficulty be performed in an age of freedom." As India balanced between the two, however, "it is the work which especially belongs to a government like that of India---to an enlightened and paternal despotism."[^64]
@@
 In America, Macaulay's tool of enlightened despotism spread with the anxiety that capital from the nation's economic center would remain scarce without a code of remedies that, if not in fact the law of New York, was at least prescribed by New York lawyers and their corporate clients.
-In the two most populous and commercially advanced western states, Texas and Illinois, the need for New York capital failed to move state legislators to adopt the code at the expense of popular sovereignty (although there were concerted efforts in both jurisdictions).[^65] Lacking the self-sufficiency of those two jurisdictions, the other states of the Greater Reconstruction in America adopted a foreign code, but lawyers, legislators, and their supporters claimed the endorsement of popular sovereignty in doing so.
+In the two most populous and commercially advanced western states, Texas and Illinois, the need for New York capital failed to move state legislators to adopt the code at the expense of popular sovereignty (despite concerted efforts in both jurisdictions).[^65] Lacking the self-sufficiency of those two jurisdictions, the other states of Greater Reconstruction in America adopted a foreign code, but lawyers, legislators, and their supporters claimed the endorsement of popular sovereignty in doing so.
 Even in North Carolina, whose Democratic newspapers daily called for the repeal "this child of the carpet baggers," Republican editors proclaimed that "the movement" towards procedural codification "comes from the people, from the instinctive logic by which an unprejudiced mind grasps the advantages of the system."[^66]
@@
 
-The history of codification on the American periphery troubles cherished notions of American federalism.
-On the one hand, those suspicious of centralized power and critical of national governance since the New Deal have relied on narratives that tout the equality of sovereign states to set their own policies, foster local diversity, and "experiment" with legislative solutions to local issues.[^67] But the history of legal practice and civil remedies is one in which the localism fostered by common law practice rapidly gave way to uniform regulations transmitted by a network of New York lawyers without the slightest interference of the federal government.
-On the other hand, scholars who support the legitimacy of New Deal governance have recently produced an abundant literature unearthing a long tradition of "administrative" law at the state level well before the twentieth century.
-These accounts have focused on administrative adjudication or discretionary regulation within a narrow domain, such as customs houses.[^68] These histories have so far neglected the most widespread and significant instance of nineteenth-century administrative lawmaking in America---the spread of the Field Code through extra-legislative commissions.
-While these histories have sought to demonstrate that Americans from early on could be quite comfortable with administrative law and accepted it as a normal part of the constitutional order, this chapter has shown how lawmaking by commission generated significant political controversy and raised grave questions about popular sovereignty under such delegations, questions that over time were merely dodged rather than answered.
+The history of codification on the American periphery challenges foundational assumptions about American federalism.
+Scholars commonly speak of regulating at “the state level” imagining an equality between state sovereignties that exists in tension only with “the federal level.” But the history of legal practice and civil remedies is one in which the localism fostered by common law practice rapidly gave way to uniform regulations promulgated by New York trial lawyers without the slightest interference of the federal government.[^67] The history of the Code also has important implications for recent scholarship seeking to unearth a long tradition of “administrative law” among the states before the twentieth century.
+These accounts have largely focused on administrative adjudication or discretionary regulation within a narrow domain, such as customs houses, but have so far neglected the most widespread and significant instance of nineteenth-century administrative lawmaking in America---the spread of remedial codes through extra-legislative commissions.[^68] While these histories have sought to demonstrate that nineteenth-century Americans could be quite comfortable with administrative law, accepting it as a normal part of the constitutional order, this chapter has shown how lawmaking by commission generated significant political controversy and raised grave questions about popular sovereignty that over time were merely dodged rather than answered.
 
@@
 
-[^67]: See, for instance, the summary of the states-as-laboratories literature in Brian Galle & Joseph Leahy, "Laboratories of Democracy?
-Policy Innovation in Decentralized Governments," *Emory Law Journal* 58 (2009): 1333.
+[^67]: The equality of the states is a foundational assumption in the much-criticized idea of the states as laboratories for regulatory experimentation.
+The states-as-laboratories idea emerged from *New State Ice Co.
+v.
+Liebmann*, 285 U.S.
+262, 311 (1932) (Brandeis, J., dissenting).
+See James A.
+Gardner, “The ‘States-as-Laboratories’ Metaphor in State Constitutional Law,” *Valparaiso University Law Review* 30 (1996), 475.
+For a collection of refutations, see Brian Galle & Joseph Leahy, “Laboratories of Democracy?
+Policy Innovation in Decentralized Governments,” *Emory Law Journal* 58 (2009), 1333.
+Even as federalism scholars vigorously refute the idea of states as “laboratories” for regulative experimentation, they continually pose “the federal” to “the state” level, with an assumed equality among the numerous sovereignties in the latter category.
+See, for instance, James E.
+Fleming & Jacob T.
+Levy, eds., *Federalism and Subsidiarity* (NYU 2014); Heather Gerken, *Beyond Sovereignty, Beyond Autonomy: A Nationalist’s View of Federalism’s Future* (forthcoming).
 

### 2016-06-29 article/article.Rmd
Fix some footnotes

@@
 
-[^5]: Roscoe Pound, "David Dudley Field: An Appraisal," and Alison Reppy, "The Field Codification Concept," in Alison Reppy, ed., *David Dudley Field: Centenary Essays* (New York University School of Law, 1949); Stephen Subrin, "David Dudley Field and the Field Code: A Historical Analysis of an Earlier Procedural Vision," 6 *Law & Hist.
-Rev*.
-311 (1988); Robert G.
-Bone, "Mapping the Boundaries of a Dispute: Conceptions of Ideal Lawsuit Structure from the Field Code to the Federal Rules," 89 *Colum.
-L.
-Rev*.
-1 (1989).
+[^5]: Roscoe Pound, "David Dudley Field: An Appraisal," and Alison Reppy, "The Field Codification Concept," in Alison Reppy, ed., *David Dudley Field: Centenary Essays* (New York University School of Law, 1949); Stephen Subrin, "David Dudley Field and the Field Code: A Historical Analysis of an Earlier Procedural Vision," *Law and History Review* 6 (1988): 311--373; Robert G.
+Bone, "Mapping the Boundaries of a Dispute: Conceptions of Ideal Lawsuit Structure from the Field Code to the Federal Rules," *Columbia Law Review* 89 (1989): 1--118.
 See also the literature on procedure and codification cited below.

### 2016-06-29 article/article.Rmd
Better image of Stewart bill
Add page count

@@
 
-![Detail from Council Bill 21, First Territorial Legislative Session (1861), Nevada State Library, Archives and Public Records.](morris-bill.jpg)
+![Detail from Council Bill 21, First Territorial Legislative Session (1861), Nevada State Library, Archives and Public Records.](CB021-1861.jpg)
 
@@
 Although Stewart's cut-and-paste code found its way into the archives, most draft legislation did not, and few codifiers explained in detail how they produced their texts.
-Traditional close reading or textual criticism of some 98,000 distinct sections of law comprising 7.7 million words is simply not a feasible research task for a historian who wishes to track these borrowings.
+Traditional close reading or textual criticism of some 98,000 distinct sections of law across 20,000 pages comprising 7.7 million words is simply not a feasible research task for a historian who wishes to track these borrowings.
 

### 2016-06-29 article/article.Rmd
Fix citations to legislation

@@
 
-[^30]: For full citations to all of the codes that we used, plus links to electronic versions at the Hathi Trust, Google Books or other sources when available, see Kellen Funk, *American Legislation Project* (2015--): <http://kellenfunk.org/legislation>.
+[^30]: For full citations to all of the codes that we used, plus links to electronic versions at the Hathi Trust, Google Books or other sources when available, see Kellen Funk, "American Civil Procedure: Law on the Books" (2015--16): <http://kellenfunk.org/civil-procedure/procedure-law/>.
 

### 2016-07-28 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Change title

--- 2016-06-29 article/article.Rmd
@@
     pandoc_args: ["--smart"]
-title: The Spine of American Legal Practice
+title: "The Spine of American Law: Digital History Methods and U.S. Legal Practice"
 ---

### 2016-07-28 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Thomas citation

@@
 Gold and Lauren F.
-Klein (Minneapolis: University of Minnesota Press, 2016).
+Klein (Minneapolis: University of Minnesota Press, 2016); William G.
+Thomas III, "The Promise of the Digital Humanities and the Contested Nature of Digital Scholarship," in *A New Companion to the Digital Humanities*, edited by Susan Schreibman, Ray Siemens, and John Unsworth (Malden, MA: Wiley Blackwell, 2016), 524--37.
 Nevertheless, digital text analysis in the humanities has mostly been published by literary scholars, including Stephen Ramsay, *Reading Machines: Toward an Algorithmic Criticism* (Urbana: University of Illinois Press, 2011); Franco Moretti, *Distant Reading* (New York: Verso, 2013); Matthew L.

### 2016-07-28 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Context of codification

@@
 Law was to be made by democratically responsible legislators in terse, unambiguous statements, not discovered through application and analogy in particular cases by the judges.
-Debates over codification thus ranged from the metaphysics of law to political theories of institutional competency and the separation of powers.[^11]
+Debates over codification thus ranged from the metaphysics of law to political theories of institutional competency and the separation of powers.[^11] Codification remained a major interest of the American bar across the nineteenth century.
+When the intellectual historian Perry Miller developed a reader surveying The Legal Mind in America, codification was its central theme, as Miller argued it was the only intellectual topic that attracted lawyers away from their practices long enough to debate.[^112] The importance of codification extended far beyond the United States.
+Napoleonic France promulgated a series of codes in the early nineteenth century, Germans debated the wisdom of codification after Napoleon’s fall, and in the 1860s the British imposed codes on their colonies in India and Singapore.
+Many American lawyers followed the international development of these codes with interest, viewing codification as the leading edge of modern legal science.[^113]
 
@@
 [^10]: Friedman, *A History of American Law*, 302.
-When the intellectual historian Perry Miller developed a reader surveying *The Legal Mind in America*, codification was its only central theme, as Miller argued it was the one intellectual topic that attracted lawyers away from their practices long enough to debate.
-Perry Miller, ed., *The Legal Mind in America: From Independence to the Civil War* (Anchor 1962).
 See also Charles M.
@@
 Gordon, "The American Codification Movement," *Vanderbilt Law Review* 36 (1983): 431--458; Maurice Eugen Lang, *Codification in the British Empire and America* (Lawbook Exchange, 1924).
-On common theories of codification that transcended jurisdictional boundaries, see Csaba Varga, *Codification as a Socio-Historical Phenomenon*, 2nd ed.
-(Budapest, 2011 \[1991\]); Roger Berkowitz, *The Gift of Science: Leibniz and the Modern Legal Tradition* (Fordham, 2010).
 
@@
 Among the latter group could be found some of the most devout theorists of laissez faire economics in nineteenth-century America, including David Dudley Field and his brother, the Supreme Court Justice Stephen Johnson Field.
+
+[^112]: Perry Miller, ed., *The Legal Mind in America: From Independence to the Civil War* (Anchor 1962).
+
+[^113]: See James Q.
+Whitman, *The Legacy of Roman Law in the German Romantic Era: Historical Vision and Legal Change* (Princeton, 1990); Gunther A.
+Weiss, "The Enchantment of Codification in the Common-Law World, *Yale Journal of International Law* 25 (2000): 435; Maurice Eugen Lang, *Codification in the British Empire and America* (Lawbook Exchange, 1924); Jean-Louis Halperin, *The French Civil Code* (Austin: University of Texas Press, 2006); Robert B.
+Holtman, *The Napoleonic Revolution* (Baton Rouge: Louisiana State University Press, 1981); R.
+H.
+Kilbourne, *A History of the Louisiana Civil Code* (Paul M.
+Herbert Law Center, 1987); Brian Young, *The Politics of Codification: The Lower Canadian Civil Code of 1866* (Osgoode Society, 1994); John W.
+Cairns, *Codification, Transplants, and History: Law Reform in Louisiana (1808) and Quebec (1866)* (Clark, NJ: Talbot, 2015); Roscoe Pound, "The French Civil Code and the Spirit of Nineteenth Century Law," *Boston Law Review* 35 (1955): 79.
+On common theories of codification that transcended jurisdictional boundaries, see Csaba Varga, *Codification as a Socio-Historical Phenomenon*, 2nd ed.
+(Budapest: Akadémiai Kiadó, 2011 [1991]); Roger Berkowitz, *The Gift of Science: Leibniz and the Modern Legal Tradition* (New York: Fordham University Press, 2010).
 

### 2016-07-28 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Break national into its own period

@@
 Debates over codification thus ranged from the metaphysics of law to political theories of institutional competency and the separation of powers.[^11] Codification remained a major interest of the American bar across the nineteenth century.
-When the intellectual historian Perry Miller developed a reader surveying The Legal Mind in America, codification was its central theme, as Miller argued it was the only intellectual topic that attracted lawyers away from their practices long enough to debate.[^112] The importance of codification extended far beyond the United States.
+When the intellectual historian Perry Miller developed a reader surveying The Legal Mind in America, codification was its central theme, as Miller argued it was the only intellectual topic that attracted lawyers away from their practices long enough to debate.[^112]
+
+The importance of codification extended far beyond the United States.
 Napoleonic France promulgated a series of codes in the early nineteenth century, Germans debated the wisdom of codification after Napoleon’s fall, and in the 1860s the British imposed codes on their colonies in India and Singapore.

### 2016-07-28 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Remove author identifier in a meaningless gesture towards double blind peer review

@@
 author:
-- Kellen Funk
-- Lincoln Mullen
 fontfamily:

### 2016-07-28 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Paragraph on digital textual analysis

@@
 Our method works especially well for legal texts, for reasons we will explain.
-However, scholars can extend this method to other curated collections of texts, from church hymns to medical treatises.
+
+The computational analysis of texts is a method which historians can use across the discipline to study many topics.
+We have used text analysis---specifically, methods to detect text reuse---to show how law migrates through borrowings, just as scholars on the *Viral Texts* team have demonstrated how newspaper articles were reprinted in the nineteenth-century United States.[^100] While we have developed a method that discovers borrowings of exact words and phrasings, other forms of digital text analysis can track the diffusion of concepts.
+Making due allowance for the specific historical questions and sources at hand, computational text analysis is broadly applicable to historical problem that involves the spread of words or ideas.
+The specific method that we outline could be extended beyond codes of civil procedure to legal statutes or treatises.
+Yet it could also be used, for instance, to track the spread of hymns in collections of hymnbooks in religious history, or the reuse of sections of medical textbooks in the history of science.
+Since historians by and large work with textual sources and increasingly with digitized texts, computational text analysis should become a part of the historian's toolbox.
+Lara Putnam has recently described the importance of "digitization and OCR, which make words above all available" for historians to search and read, while observing that "computational tools can discipline our term-searching if we ask them to."[^101] Historians have been slow to take up text analysis even as the aid to more traditional reading that Putnam recommends.
+Yet as we demonstrate in this article, such methods can reveal patterns inaccessible to the traditional historian.[^102]
 
@@
 
+[^100]: Ryan Cordell and David A.
+Smith, *Viral Texts: Mapping Networks of Reprinting in 19th-Century Newspapers and Magazines*, NULab for Texts Maps and Networks, Northeastern University (2012--): <http://viraltexts.org>.
+
+[^101]: Lara Putnam, "The Transnational and the Text-Searchable: Digitized Sources and the Shadows They Cast," *American Historical Review* 121, no. 2 (2016): 399--400.
+
+[^102]: Only a few historians have used computational text analysis, including Cameron Blevins, “Space, Nation, and the Triumph of Region: A View of the World from Houston,” *Journal of American History* 101, no.
+1 (June 1, 2014): 122–47, doi:10.1093/jahist/jau184; Benjamin M.
+Schmidt, *Sapping Attention* (blog): <http://sappingattention.blogspot.com/>; Sharon Block, "Doing More with Digitization: An Introduction to Topic Modeling of Early American Sources," *Common-Place* 6, no.
+2 (January 2006): <http://www.common-place.org/vol-06/no-02/tales/>; Dan Cohen, Frederick Gibbs, Tim Hitchcock, Geoffrey Rockwell, et al., "Data Mining with Criminal Intent," white paper, 31 August 2011, <http://criminalintent.org>; Robert K.
+Nelson, "Mining the Dispatch, website, Digital Scholarship Lab, University of Richmond, <http://dsl.richmond.edu/dispatch/>; Dan Cohen, "Searching for the Victorians," 4 October 2010: <http://www.dancohen.org/2010/10/04/searching-for-the-victorians/>; Micki Kaufmann, *"Everything on Paper Will Be Used Against Me:" Quantifying Kissinger*, digital project (2012--16): <http://blog.quantifyingkissinger.com/>; E.
+Thomas Ewing, Samah Gad, Bernice L.
+Hausman, Kathleen Kerr, Bruce Pencek, and Naren Ramakrishnan, "An Epidemiology of Information: Datamining the 1918 Flu Pandemic," project research report (2 April 2014): <http://vtechworks.lib.vt.edu/bitstream/handle/10919/46991/An%20Epidemiology%20of%20Information%20Project%20Research%20Report_Final.pdf?sequence=1>; Michelle Moravec, "'Under this name she is fitly described': A Digital History of Gender in the History of Woman Suffrage" (March 2015): <http://womhist.alexanderstreet.com/moravec-full.html>.
+
 [^7]: For the rise of treatises in America generally, see G.
@@
 Nevertheless, digital text analysis in the humanities has mostly been published by literary scholars, including Stephen Ramsay, *Reading Machines: Toward an Algorithmic Criticism* (Urbana: University of Illinois Press, 2011); Franco Moretti, *Distant Reading* (New York: Verso, 2013); Matthew L.
-Jockers, *Macroanalysis: Digital Methods and Literary History* (Urbana: University of Illinois Press, 2013); Ted Underwood, *Why Literary Periods Mattered: Historical Contrast and the Prestige of English Studies* (Stanford: Stanford University Press, 2013); Ryan Cordell and David A.
-Smith, *Viral Texts: Mapping Networks of Reprinting in 19th-Century Newspapers and Magazines*, NULab for Texts Maps and Networks, Northeastern University (2012--): <http://viraltexts.org>.
+Jockers, *Macroanalysis: Digital Methods and Literary History* (Urbana: University of Illinois Press, 2013); Ted Underwood, *Why Literary Periods Mattered: Historical Contrast and the Prestige of English Studies* (Stanford: Stanford University Press, 2013).
 Related but less well regarded by humanities scholars is work in "culturomics": see Jean-Baptiste Michel et al., "Quantitative Analysis of Culture Using Millions of Digitized Books", *Science* 331, no.

### 2016-07-28 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Response to Jason's comments

@@
 
-Curating a corpus to answer a specific question is an important difference from the way that digital history often describes its work.
-Speaking in broad terms, digital historical work---like all historical work---can begin either with a set of sources or with a question.
-Computational digital history is often conceived of as beginning with sources, particularly with large datasets such as the Google Books or Hathi Trust corpora.
-These large corpora are sometimes called "big data"---though, it must be emphasized, almost never by digital historians who actually work with them---on which "distant reading" can be practiced.
+Curating a corpus to answer a specific question is one of two ways in which digital history can proceed.
+To quote Jason Heppler, digital history--like all historical work---can begin either "with a corpus looking for a question, or a question looking for a corpus." Computational text analysis in digital history is often conceived of as beginning with sources, particularly with large datasets such as the Google Books or Hathi Trust corpora.
+These large corpora are sometimes called "big data"---though it must be emphasized almost never by digital historians who actually work with them---on which "distant reading" can be practiced.
 While it is salutary for historians to have their research questions shaped by the broadest possible contexts, it is not apparent that digital historians can readily move from these omnibus corpora to answering the specific research questions that animate various historical fields.
@@
 But while a corpus of procedural legislation requires some computational sophistication, the techniques are far less complex than those derived for truly big data.
-We have gathered a large but narrowly constrained corpus centered on solving a well-defined research question.
-This corpus is large enough that digital historical methods provide results that a scholar could not obtain through traditional methods, but sufficiently circumscribed so as to directly address a discipline- and field-specific question.[^31]
+We have gathered a large but narrowly constrained corpus centered on solving a well-defined research question.[^310] This corpus is large enough that digital historical methods provide results that a scholar could not obtain through traditional methods, but sufficiently circumscribed so as to directly address a discipline- and field-specific question.[^31]
+
+[^310]: Our approach draws on an earlier generation of digital history which collected sources, as exemplified in *The Valley of the Shadow* project: William G.
+Thomas III and Edward L.
+Ayers, "The Differences Slavery Made: A Close Analysis of Two American Communities," *The American Historical Review* 108, no.
+5 (December 1, 2003): 1299–1307, doi:10.1086/587017.
+See also Dan Cohen and Roy Rosenzweig, *Digital History: A Guide to Gathering, Preserving, and Presenting the Past on the Web* (Philadelphia: University of Pennsylvania Press, 2005), ch.
+6, digital edition hosted at Roy Rosenzweig Center for History and New Media, George Mason University: <http://chnm.gmu.edu/digitalhistory/>.
 

### 2016-07-28 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Title again

@@
     pandoc_args: ["--smart"]
-title: "The Spine of American Law: Digital History Methods and U.S. Legal Practice"
+title: "The Spine of American Law: Digital Text Analysis and U.S. Legal Practice"
 ---

### 2016-07-29 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Typos and minor changes

@@
 The French government under Napoleon had appointed five-member commissions to codify the law of France.
-When the New York law reformer William Sampson called for codification in a widely noted address to the New York historical society, one of the members of the French commission was living in exile in upstate New York at the time and wrote to Sampson to advise him on the mechanics of codification: "Let four or five good heads be united in a commission, to frame in silence the project of a code.
+When the New York law reformer William Sampson called for codification in a widely noted address to the New-York Historical Society, one of the members of the French commission living in exile in upstate New York wrote to Sampson.
+He advised Sampson on the mechanics of codification: "Let four or five good heads be united in a commission, to frame in silence the project of a code.
 It is not so difficult a task.
@@
 Note that many southern states and western states came to adopt the Field Code during the Civil War and Reconstruction.
-By the end of the nineteenth-century, thirty-one jurisdictions (those displayed on the map, plus Alaska) had adopted a version of the Field Code.
+By the end of the nineteenth century, thirty-one jurisdictions (those displayed on the map, plus Alaska) had adopted a version of the Field Code.
 Data adapted from Charles McGuffey Hepburn, *The Historical Development of Code Pleading in America and England* (1897).](field-code-states-map.jpeg)
@@
 In the two most populous and commercially advanced western states, Texas and Illinois, the need for New York capital failed to move state legislators to adopt the code at the expense of popular sovereignty (despite concerted efforts in both jurisdictions).[^65] Lacking the self-sufficiency of those two jurisdictions, the other states of Greater Reconstruction in America adopted a foreign code, but lawyers, legislators, and their supporters claimed the endorsement of popular sovereignty in doing so.
-Even in North Carolina, whose Democratic newspapers daily called for the repeal "this child of the carpet baggers," Republican editors proclaimed that "the movement" towards procedural codification "comes from the people, from the instinctive logic by which an unprejudiced mind grasps the advantages of the system."[^66]
+Even in North Carolina, whose Democratic newspapers daily called for the repeal of "this child of the carpet baggers," Republican editors proclaimed that "the movement" towards procedural codification "comes from the people, from the instinctive logic by which an unprejudiced mind grasps the advantages of the system."[^66]
 
@@
 
-By addressing our historical questions to a sufficiently large but narrowly defined corpus of sources, we enjoyed a useful symbiosis of traditional and digital historical methods.
+By addressing our historical questions to a sufficiently large but narrowly defined corpus of sources, we benefited from a useful symbiosis of traditional and digital historical methods.
 Our computational methods produced useful historical knowledge because they were carefully tailored to what we knew about the data from traditional historical work.

### 2016-08-13 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Metadata at top of article

@@
 ---
-author:
 fontfamily:
@@
 fontsize: 12pt
+geometry:
+- "margin=1in"
 output:
@@
     number_sections: False
+    template: article-template.tex
   word_document: 
@@
     pandoc_args: ["--smart"]
-title: "The Spine of American Law: Digital Text Analysis and U.S. Legal Practice"
+title: |
+       | The Spine of American Law\: 
+       | Digital Text Analysis and U.S. Legal Practice
+author: 
+- name: Kellen Funk
+  affiliation: Princeton University
+  email: kfunk@princeton.edu
+- name: Lincoln Mullen
+  affiliation: George Mason University
+  email: lincoln@lincolnmullen.com
 ---
@@
 ```
+
+*This article is currently under peer review at the American Historical Review.*
+
+\
 

### 2016-08-13 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Move footnote for text flow problem

@@
 Yet by turning to the digital analysis of texts, we have resolved this difficulty and tracked how states borrowed their codes of civil practice from one another.
-Within the corpus of legislation, algorithmic analysis of texts can reverse engineer and visualize what the archive revealed in figure 1: which texts were borrowed, which modified, and how extensively.
-Our method works especially well for legal texts, for reasons we will explain.
+Within the corpus of legislation, algorithmic analysis of texts can reverse engineer and visualize what the archive revealed in figure 1: which texts were borrowed, which modified, and how extensively.[^37] Our method works especially well for legal texts, for reasons we will explain.
 
@@
 The result was a matrix of similarity scores, with over 45,000 genuine matches.
-For each section in the corpus, after making some adjustments to remove anachronisms and spurious matches, we were able to identify the section from which it was most likely borrowed.[^36] In other words, we had traced the work of the commissioners' scissors and paste-pots through the course of their codes.[^37]
+For each section in the corpus, after making some adjustments to remove anachronisms and spurious matches, we were able to identify the section from which it was most likely borrowed.[^36] In other words, we had traced the work of the commissioners' scissors and paste-pots through the course of their codes.
 

### 2017-05-16 scripts/clean-text.R
Specify column types for read_csv

@@ -12,7 +12,9 @@ text <- read_file(in_file)
 # Corrections in this file are literal substrings, not patterns. E.g. "adjoum"
 # should be corrected to "adourn" in both the word "adjourn" and the word
 # "adjournment".
-corrections <- read_csv("scripts/ocr-corrections.csv")
+corrections <- read_csv("scripts/ocr-corrections.csv",
+                        col_types = cols(pattern = col_character(),
+                                         replacement = col_character()))
 
 cleaned <- text %>%
   stri_replace_all_fixed(corrections$pattern, corrections$replacement,

### 2017-05-16 scripts/split-code.R
Add certain codes to sectioning rules
Fixes #37

@@ -1,8 +1,7 @@
 # Split a code into chunks
-library("readr")
-library("stringr")
+library(readr)
+library(stringr)
 
-dir.create("legal-codes-split", showWarnings = FALSE)
 args <- commandArgs(trailingOnly = TRUE)
 in_file <- args[1]
 stem <- in_file %>%
@@ -10,20 +9,58 @@ stem <- in_file %>%
   str_replace("\\.txt", "")
 out_file_stem <- str_c("legal-codes-split/", stem)
 doc <- read_file(in_file)
-doc <- str_c(doc, collapse = "\n")
 
-# Use pattern_clean on files we have cleaned up; otherwise use pattern_fuzzy. We will assume that a file has been cleaned up unless it matches a black list.
+# Use pattern_clean on files we have cleaned up; otherwise use pattern_fuzzy. We
+# will assume that a file has been cleaned up unless it matches a black list.
 pattern_fuzzy <- regex("(\n§((\\s+)?)\\d+((\\.)?)|\n\\$((\\s+)?)\\d+((\\.)?)|\nchapter|\ntitle|\narticle|\nSUBDIVISION|\nt i t l e|\nRULE \\w+\\.|\n\\d{1,}\\.|\nSEC((\\.)?)\\s+\\d+((\\.)?)|\nSECTION((\\.)?)\\s+\\d+((\\.)?)|\nSECT((\\.)?)\\s+\\d+((\\.)?)|\n8EC((\\.)?)\\s+\\d+((\\.)?)|\nSE0((\\.)?)\\s+\\d+((\\.)?)|\nSEO((\\.)?)\\s+\\d+((\\.)?)|\nS((\\.)?)\\s+\\d+((\\.)?)|\nSEQ((\\.)?)\\s+\\d+((\\.)?)|\nArt((\\.)?)\\s+\\d+((\\.)?)|\nAn((\\.)?)\\s+\\d+((\\.)?)|\nAm((\\.)?)\\s+\\d+((\\.)?)|\nSec\\.\n\\d+\\.)", ignore_case = TRUE)
 pattern_clean <- regex("(\ntitle|\nchapter|\narticle\n|\nsection|\ndivision|\nsubdivision|\n§|\nSec\\.)", ignore_case = TRUE)
 
-uncleaned_files <- c("BI1859", "CA1868short", "CO1858", "CT1854", "CT1879",
-                     "CT1879extended", "DE1852", "FL1847", "FL1892", "FR1806",
[…]

### 2017-05-16 scripts/corpus-lsh.R
Fix writing out matches as CSVs

@@ -1,8 +1,7 @@
-library("readr")
-library("plyr")
-library("dplyr")
-library("stringr")
-library("textreuse")
+suppressPackageStartupMessages(library(readr))
+suppressPackageStartupMessages(library(dplyr))
+suppressPackageStartupMessages(library(stringr))
+suppressPackageStartupMessages(library(textreuse))
 source("R/helper.R")
 source("R/section-matches.R")
 options("mc.cores" = 8L)
@@ -50,13 +49,14 @@ best_matches <- data_frame(borrower_section = names(sections)) %>%
          match_state = extract_state(match_section)) %>%
   arrange(borrower_section, match_section)
 
-split_matches <- dlply(best_matches, "borrower_code", identity)
+split_matches <- plyr::dlply(best_matches, "borrower_code", identity)
 
 summary_matches <- summarize_borrowings(best_matches)
 
 save(sections, buckets, scores, all_matches, best_matches, summary_matches,
      file = "cache/corpus-lsh.rda")
 
+dir.create("out", showWarnings = FALSE)
 dir.create("out/matches", showWarnings = FALSE)
 write_csv(all_matches, "out/matches/all_matches.csv")
 write_csv(best_matches, "out/matches/best_matches.csv")

### 2017-05-16 scripts/network-graphs.R
No package startup messages

@@ -1,8 +1,8 @@
-library(dplyr)
-library(igraph)
-library(ggplot2)
-library(ggraph)
-library(stringr)
+suppressPackageStartupMessages(library(dplyr))
+suppressPackageStartupMessages(library(igraph))
+suppressPackageStartupMessages(library(ggplot2))
+suppressPackageStartupMessages(library(ggraph))
+suppressPackageStartupMessages(library(stringr))
 load("cache/corpus-lsh.rda")
 source("R/helper.R")
 set.seed(82892)

### 2017-05-16 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Remove peer review notice
Adjust the network graph
Fixes #40

@@
 set.seed(82893)
+dir.create("../out/figures", recursive = TRUE, showWarnings = FALSE)
 ```
-
-*This article is currently under peer review at the American Historical Review.*
 
@@
 
-```{r code-to-code-network, fig.width=6.5, fig.height=7, fig.cap = "The structure of borrowings among nineteenth-century codes of civil procedure.
+```{r code-to-code-network, fig.width=10, fig.height=7, fig.cap = "The structure of borrowings among nineteenth-century codes of civil procedure.
 Note that several versions of New York's Field Code were at the center of the network, while other states such as California and Ohio became centers of regional variations on the Field Code.
@@
 set.seed(3728)
-ggraph(codes_g, "igraph", algorithm = "nicely") +
+network_g <- ggraph(codes_g, "igraph", algorithm = "nicely") +
   geom_edge_fan(aes(edge_width = sections_borrowed, 
@@
   scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") +    
-  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +   
-  scale_color_discrete("Distance from a Field Code") +
+  scale_edge_alpha(range = c(0.4, 0.5), guide = "none") +   
+  scale_color_manual(name = "Distance from a Field Code",
+                     values = c("0" = "#88419d",
+                                "1" = "#1d91c0",
+                                "2" = "#41b6c4",
+                                "3" = "#7fcdbb",
+                                "4" = "#c7e9b4",
+                                "5" = "#edf8b1",
+                                "6" = "#ffffd9",
+                                "Inf" = "#dfc27d")) +
   ggforce::theme_no_axes() +  
-  geom_node_text(aes(label = name), size = 3, family = "Palatino") +
+  geom_node_text(aes(label = name), size = 4, family = "Palatino") +
   labs(title = "The migration of the Field Code",
@@
         plot.title = element_text(face = "bold"))
+print(network_g)
+ggsave("../out/figures/02-network-graph.svg", network_g, width = 10, height = 7)
+ggsave("../out/figures/02-network-graph.pdf", network_g, width = 10, height = 7)
 ```
@@
 ```{r ca1850-borrowings, fig.height=3, fig.align="center"}
-spectrogram("CA1850", best_matches, white_list = c("LA1844", "NY1829", "NY1849",
+spec_CA1850 <- spectrogram("CA1850", best_matches, white_list = c("LA1844", "NY1829", "NY1849",
                                                    "NY1848"), base_size = 10)
+print(spec_CA1850)
+ggsave("../out/figures/03-spec_CA1850.svg", spec_CA1850, width = 7, height = 3)
+ggsave("../out/figures/03-spec_CA1850.pdf", spec_CA1850, width = 7, height = 3)
 ```
@@
 ```{r CA1851-borrowings, fig.height=3.5, fig.align="center"}
-spectrogram("CA1851", best_matches, white_list = 3, base_size = 10)
+spec_CA1851 <- spectrogram("CA1851", best_matches, white_list = 3, base_size = 10)
+print(spec_CA1851)
+ggsave("../out/figures/04-spec_CA1851.svg", spec_CA1851, width = 7, height = 3.5)
+ggsave("../out/figures/04-spec_CA1851.pdf", spec_CA1851, width = 7, height = 3.5)
 ```
@@
 ```{r WA1855-borrowings, fig.height=4.5, fig.align="center"}
-spectrogram("WA1855", best_matches, white_list = c("CA1850", "CA1851", "IN1852",
+spec_WA1855 <- spectrogram("WA1855", best_matches, white_list = c("CA1850", "CA1851", "IN1852",
                                                    "NY1853", "OR1854", "WI1849"),
             base_size = 10)
+print(spec_WA1855)
+ggsave("../out/figures/05-spec_WA1855.svg", spec_WA1855, width = 7, height = 4.5)
+ggsave("../out/figures/05-spec_WA1855.pdf", spec_WA1855, width = 7, height = 4.5)
 ```
@@
 ```{r WA1873-borrowings, fig.height=4.5, fig.align="center"}
-spectrogram("WA1873", best_matches, base_size = 10)
+spec_WA1873 <- spectrogram("WA1873", best_matches, base_size = 10)
+print(spec_WA1873)
+ggsave("../out/figures/06-spec_WA1873.svg", spec_WA1873, width = 7, height = 4.5)
+ggsave("../out/figures/06-spec_WA1873.pdf", spec_WA1873, width = 7, height = 4.5)
 ```

### 2017-05-16 scripts/network-graphs.R

@@ -32,15 +32,20 @@ edges_n <- summary_matches %>%
 
 codes_g <- graph_from_data_frame(edges_n, directed = TRUE)
 
+the_field_codes <- c("NY1848", "NY1849", "NY1850", "NY1851", "NY1853")
+
+is_field_code <- function(x) {
+  ifelse(x %in% the_field_codes, TRUE, FALSE)
+}
 
 node_distances <- distances(codes_g,
                             mode = "out",
-                            to = c("NY1848", "NY1849", "NY1850",
-                                   "NY1851", "NY1853"),
+                            to = the_field_codes,
                             algorithm = "unweighted") %>%
                     apply(1, min, na.rm = TRUE)
 nodes_n <- data_frame(name = names(node_distances),
-                      distance = node_distances)
+                      distance = node_distances,
+                      field_code = is_field_code(name))
 
 codes_g <- graph_from_data_frame(edges_n, directed = TRUE, vertices = nodes_n)
 

### 2017-07-13 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Moving things around

@@
 print(network_g)
-ggsave("../out/figures/02-network-graph.svg", network_g, width = 10, height = 7)
-ggsave("../out/figures/02-network-graph.pdf", network_g, width = 10, height = 7)
+ggsave("../out/figures/figure-05.svg", network_g, width = 10, height = 7)
+ggsave("../out/figures/figure-05.pdf", network_g, width = 10, height = 7)
+ggsave("../out/figures/figure-05.png", network_g, width = 10, height = 7)
 ```
@@
 print(spec_CA1850)
-ggsave("../out/figures/03-spec_CA1850.svg", spec_CA1850, width = 7, height = 3)
-ggsave("../out/figures/03-spec_CA1850.pdf", spec_CA1850, width = 7, height = 3)
+ggsave("../out/figures/figure-06.svg", spec_CA1850, width = 7, height = 3)
+ggsave("../out/figures/figure-06.pdf", spec_CA1850, width = 7, height = 3)
+ggsave("../out/figures/figure-06.png", spec_CA1850, width = 7, height = 3)
 ```
@@
 print(spec_CA1851)
-ggsave("../out/figures/04-spec_CA1851.svg", spec_CA1851, width = 7, height = 3.5)
-ggsave("../out/figures/04-spec_CA1851.pdf", spec_CA1851, width = 7, height = 3.5)
+ggsave("../out/figures/figure-07.svg", spec_CA1851, width = 7, height = 3.5)
+ggsave("../out/figures/figure-07.pdf", spec_CA1851, width = 7, height = 3.5)
+ggsave("../out/figures/figure-07.png", spec_CA1851, width = 7, height = 3.5)
 ```
@@
 print(spec_WA1855)
-ggsave("../out/figures/05-spec_WA1855.svg", spec_WA1855, width = 7, height = 4.5)
-ggsave("../out/figures/05-spec_WA1855.pdf", spec_WA1855, width = 7, height = 4.5)
+ggsave("../out/figures/figure-08.svg", spec_WA1855, width = 7, height = 4.5)
+ggsave("../out/figures/figure-08.pdf", spec_WA1855, width = 7, height = 4.5)
+ggsave("../out/figures/figure-08.png", spec_WA1855, width = 7, height = 4.5)
 ```
@@
 print(spec_WA1873)
-ggsave("../out/figures/06-spec_WA1873.svg", spec_WA1873, width = 7, height = 4.5)
-ggsave("../out/figures/06-spec_WA1873.pdf", spec_WA1873, width = 7, height = 4.5)
+ggsave("../out/figures/figure-09.svg", spec_WA1873, width = 7, height = 4.5)
+ggsave("../out/figures/figure-09.pdf", spec_WA1873, width = 7, height = 4.5)
+ggsave("../out/figures/figure-09.png", spec_WA1873, width = 7, height = 4.5)
 ```

### 2017-07-13 index.Rmd
Update with link to preprint

@@
 It is a collaboration between [Kellen Funk](http://kellenfunk.org/) and [Lincoln Mullen](http://lincolnmullen.com).
-This [working paper](talks/dh-working-group/Funk-Mullen.Migration-Field-Code.working-paper.pdf) has the most up-to-date summary of what we are doing.
+You can read a [preprint of our article](https://osf.io/preprints/socarxiv/w8un4/) accepted for publication in the *American Historical Review*.
+This older [working paper](https://osf.io/preprints/socarxiv/nfg92/) describes our method.
 

### 2017-11-16 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Revisions towards the final version

--- 2016-08-13 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
@@
 set.seed(82893)
+dir.create("../out/figures", recursive = TRUE, showWarnings = FALSE)
+bw <- TRUE
 ```
-
-*This article is currently under peer review at the American Historical Review.*
 
@@
 
-```{r code-to-code-network, fig.width=6.5, fig.height=7, fig.cap = "The structure of borrowings among nineteenth-century codes of civil procedure.
+```{r code-to-code-network, fig.width=17.5, fig.height=12.5, fig.cap = "The structure of borrowings among nineteenth-century codes of civil procedure.
 Note that several versions of New York's Field Code were at the center of the network, while other states such as California and Ohio became centers of regional variations on the Field Code.
@@
                                angle = 15)) +
-  geom_node_point(aes(color = as.factor(distance)), size = 5) +   
+  geom_node_point(aes(color = as.factor(distance)), size = 6) +   
   scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") +    
-  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +   
-  scale_color_discrete("Distance from a Field Code") +
+  scale_edge_alpha(range = c(0.5, 0.5), guide = "none") +   
+  scale_color_manual(name = "Distance from a Field Code",
+                     values = c("0" = "#ff0000",
+                                "1" = "#1d91c0",
+                                "2" = "#41b6c4",
+                                "3" = "#7fcdbb",
+                                "4" = "#c7e9b4",
+                                "5" = "#edf8b1",
+                                "6" = "#ffffd9",
+                                "Inf" = "#dfc27d")) +
   ggforce::theme_no_axes() +  
-  geom_node_text(aes(label = name), size = 3, family = "Palatino") +
+  geom_node_text(aes(label = name), size = 5, family = "Palatino") +
   labs(title = "The migration of the Field Code",
@@
         text = element_text(family = "Palatino"),
-        legend.title = element_text(size = 10),
-        legend.text = element_text(size = 8),
-        plot.title = element_text(face = "bold"))
+        legend.title = element_text(size = 18),
+        legend.text = element_text(size = 15),
+        plot.title = element_text(size = 22, face = "bold"),
+        plot.subtitle = element_text(size = 18))
+print(network_g)
+ggsave("../out/figures/figure-05.svg", network_g, width = 17.5, height = 12.25)
+ggsave("../out/figures/figure-05.pdf", network_g, width = 17.5, height = 12.25)
+ggsave("../out/figures/figure-05.png", network_g, width = 17.5, height = 12.25)
 ```
@@
 
-```{r ca1850-borrowings, fig.height=3, fig.align="center"}
-spectrogram("CA1850", best_matches, white_list = c("LA1844", "NY1829", "NY1849",
-                                                   "NY1848"), base_size = 10)
+```{r CA1850-borrowings, fig.height=3, fig.align="center"}
+spec_CA1850 <- spectrogram("CA1850", best_matches, 
+                           white_list = c("LA1844", "NY1829", "NY1849", "NY1848"),
+                           base_size = 10)
+spec_CA1850_bw <- spectrogram("CA1850", best_matches, 
+                              white_list = c("LA1844", "NY1829", "NY1849", "NY1848"),
+                              base_size = 10, bw = TRUE)
+if (!bw) {
+  print(spec_CA1850) 
+} else {
+  print(spec_CA1850_bw)
+} 
+ggsave("../out/figures/figure-06.svg", spec_CA1850, width = 7, height = 3)
+ggsave("../out/figures/figure-06.pdf", spec_CA1850, width = 7, height = 3)
+ggsave("../out/figures/figure-06.png", spec_CA1850, width = 7, height = 3)
+ggsave("../out/figures/figure-06-bw.svg", spec_CA1850_bw, width = 7, height = 3)
+ggsave("../out/figures/figure-06-bw.pdf", spec_CA1850_bw, width = 7, height = 3)
+ggsave("../out/figures/figure-06-bw.png", spec_CA1850_bw, width = 7, height = 3)
 ```
@@
 ```{r CA1851-borrowings, fig.height=3.5, fig.align="center"}
-spectrogram("CA1851", best_matches, white_list = 3, base_size = 10)
+spec_CA1851 <- spectrogram("CA1851", best_matches, 
+                           white_list = 3, base_size = 10)
+spec_CA1851_bw <- spectrogram("CA1851", best_matches, 
+                              white_list = 3, base_size = 10, bw = TRUE)
+if (!bw) {
+  print(spec_CA1851) 
+} else {
+  print(spec_CA1851_bw)
+} 
+ggsave("../out/figures/figure-07.svg", spec_CA1851, width = 7, height = 3.5)
+ggsave("../out/figures/figure-07.pdf", spec_CA1851, width = 7, height = 3.5)
+ggsave("../out/figures/figure-07.png", spec_CA1851, width = 7, height = 3.5)
+ggsave("../out/figures/figure-07-bw.svg", spec_CA1851_bw, width = 7, height = 3.5)
+ggsave("../out/figures/figure-07-bw.pdf", spec_CA1851_bw, width = 7, height = 3.5)
+ggsave("../out/figures/figure-07-bw.png", spec_CA1851_bw, width = 7, height = 3.5)
 ```
@@
 ```{r WA1855-borrowings, fig.height=4.5, fig.align="center"}
-spectrogram("WA1855", best_matches, white_list = c("CA1850", "CA1851", "IN1852",
-                                                   "NY1853", "OR1854", "WI1849"),
+spec_WA1855 <- spectrogram("WA1855", best_matches, 
+                           white_list = c("CA1850", "CA1851", "IN1852", 
+                                          "OR1854"),
                            base_size = 10)
+spec_WA1855_bw <- spectrogram("WA1855", best_matches, 
+                              white_list = c("CA1850", "CA1851", "IN1852", 
+                                             "OR1854"),
+                              base_size = 10, bw = TRUE)
+if (!bw) {
+  print(spec_WA1855) 
+} else {
+  print(spec_WA1855_bw)
+} 
+ggsave("../out/figures/figure-08.svg", spec_WA1855, width = 7, height = 4.5)
+ggsave("../out/figures/figure-08.pdf", spec_WA1855, width = 7, height = 4.5)
+ggsave("../out/figures/figure-08.png", spec_WA1855, width = 7, height = 4.5)
+ggsave("../out/figures/figure-08-bw.svg", spec_WA1855_bw, width = 7, height = 4.5)
+ggsave("../out/figures/figure-08-bw.pdf", spec_WA1855_bw, width = 7, height = 4.5)
+ggsave("../out/figures/figure-08-bw.png", spec_WA1855_bw, width = 7, height = 4.5)
 ```
@@
 ```{r WA1873-borrowings, fig.height=4.5, fig.align="center"}
-spectrogram("WA1873", best_matches, base_size = 10)
+spec_WA1873 <- spectrogram("WA1873", 
+                           white_list = c("CA1872", "IN1852", "WA1855"),
+                           best_matches, base_size = 10)
+spec_WA1873_bw <- spectrogram("WA1873", best_matches,
+                              white_list = c("CA1872", "IN1852", "WA1855"),
+                              base_size = 10, bw = TRUE)
+if (!bw) {
+  print(spec_WA1873) 
+} else {
+  print(spec_WA1873_bw)
+} 
+ggsave("../out/figures/figure-09.svg", spec_WA1873, width = 7, height = 4.5)
+ggsave("../out/figures/figure-09.pdf", spec_WA1873, width = 7, height = 4.5)
+ggsave("../out/figures/figure-09.png", spec_WA1873, width = 7, height = 4.5)
+ggsave("../out/figures/figure-09-bw.svg", spec_WA1873_bw, width = 7, height = 4.5)
+ggsave("../out/figures/figure-09-bw.pdf", spec_WA1873_bw, width = 7, height = 4.5)
+ggsave("../out/figures/figure-09-bw.png", spec_WA1873_bw, width = 7, height = 4.5)
 ```

### 2017-11-16 R/spectrogram.R

@@ -4,7 +4,7 @@
 spectrogram <- function(code, matches_df, num_cols = 50,
                         white_list = NULL, title = NULL,
                         base_size = 12, base_family = "",
-                        legend_size = 0.5) {
+                        legend_size = 0.5, bw = FALSE) {
   require(dplyr)
   require(stringr)
   require(ggplot2)
@@ -37,7 +37,7 @@ spectrogram <- function(code, matches_df, num_cols = 50,
     title <- str_c("Borrowed sections in ", code)
 
   # Make the plot
-  matches_df %>%
+  the_plot <- matches_df %>%
   ggplot(aes(x = column, y = -row, fill = match_code)) +
   geom_tile(color = "lightgray") +
   theme_minimal(base_size = base_size, base_family = base_family) +
@@ -51,8 +51,30 @@ spectrogram <- function(code, matches_df, num_cols = 50,
         panel.background = element_blank(), panel.grid = element_blank(),
         legend.key.size = unit(legend_size, "cm"),
         plot.margin = unit(c(0, 0, 0, 0), "cm"),
-        plot.title = element_text(hjust = 0.5)) +
-  scale_fill_manual(na.value = "white",
+        plot.title = element_text(hjust = 0.5))
+  if (bw) {
+    # the_plot <- the_plot + scale_fill_brewer(type = "qual", palette = "Set3")
+    # the_plot <- the_plot + scale_fill_brewer(type = "seq", palette = "Greys",
+    #                                          direction = -1)
+    the_plot <- the_plot + scale_fill_manual(na.value = "white",
+                    values = c(
+                        CA1850 = "#969696",
+                        CA1851 = "#BDBDBD",
+                        CA1872 = "#BDBDBD",
+                        IN1852 = "#252525",
+                        LA1844 = "#969696",
+                        NY1829 = "#BDBDBD",
+                        NY1848 = "#636363",
+                        NY1849 = "#252525",
+                        NY1850 = "#252525",
+                        OR1854 = "#636363",
+                        OR1862 = "#BDBDBD",
+                        WA1855 = "#636363",
+                        WI1849 = "#D9D9D9",
+                        Other = "#F7F7F7"
+                        ))
+  } else {
+    the_plot <- the_plot + scale_fill_manual(na.value = "white",
                     values = c(
                       AZ1865 = "lightpink3",
                       AZ1887 = "lightpink3",
[…]

### 2017-11-16 scripts/network-graphs.R

@@ -32,7 +32,8 @@ edges_n <- summary_matches %>%
 
 codes_g <- graph_from_data_frame(edges_n, directed = TRUE)
 
-the_field_codes <- c("NY1848", "NY1849", "NY1850", "NY1851", "NY1853")
+the_field_codes <- c("NY1848", "NY1849", "NY1850", "NY1851", "NY1853",
+                     "NY1864", "NY1873")
 
 is_field_code <- function(x) {
   ifelse(x %in% the_field_codes, TRUE, FALSE)

### 2017-11-16 scripts/state-network.R
State network graph

@@ -1,0 +1,37 @@
+library(tidyverse)
+library(igraph)
+library(ggraph)
+
+load("cache/corpus-lsh.rda")
+load("cache/network-graphs.rda")
+
+set.seed(7833)
+network_g <- ggraph(states_g, "igraph", algorithm = "nicely") +
+  geom_edge_fan(aes(edge_width = sections_borrowed,
+                    alpha = sections_borrowed),
+                arrow = arrow(type = "closed", ends = "first",
+                              length = unit(0.3, "inches"),
+                               angle = 25)) +
+  geom_node_point(aes(color = as.factor(region)), size = 9) +
+  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") +
+  scale_edge_alpha(range = c(0.5, 0.5), guide = "none") +
+  # scale_color_manual(name = "Region",
+  #                    values = c("New York" = "#ff0000",
+  #                               "Midwest" = "#1d91c0",
+  #                               "South" = "#41b6c4",
+  #                               "West" = "#7fcdbb",
+  #                               "New England" = "#c7e9b4")) +
+  scale_color_brewer(name = "Region", palette = "Set3") +
+  ggforce::theme_no_axes() +
+  geom_node_text(aes(label = name), size = 6, family = "Palatino") +
+  labs(title = "The migration of the Field Code",
+       subtitle = "States connected by legislative borrowings of civil procedure") +
+  theme(legend.position = "bottom",
+        panel.border = element_blank(),
+        text = element_text(family = "Palatino"),
+        legend.title = element_text(size = 18),
+        legend.text = element_text(size = 15),
+        plot.title = element_text(size = 22, face = "bold"),
+        plot.subtitle = element_text(size = 18))
+print(network_g)
+ggsave("out/state-network.svg", network_g, width = 12, height = 6.75)

### 2018-01-03 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
Revised figures

@@
   scale_color_manual(name = "Distance from a Field Code",
-                     values = c("0" = "#ff0000",
-                                "1" = "#1d91c0",
-                                "2" = "#41b6c4",
-                                "3" = "#7fcdbb",
-                                "4" = "#c7e9b4",
-                                "5" = "#edf8b1",
-                                "6" = "#ffffd9",
-                                "Inf" = "#dfc27d")) +
+                     values = c("Field code" = "#e41a1c",
+                                "Original borrower" = "#377eb8",
+                                "Subsequent borrower" = "#4daf4a",
+                                "Independent" = "#984ea3"
+                                # "3" = "#7fcdbb",
+                                # "4" = "#c7e9b4",
+                                # "5" = "#edf8b1",
+                                # "6" = "#ffffd9",
+                                # "Inf" = "#dfc27d"
+                                )) +
   ggforce::theme_no_axes() +  
@@
 ```{r CA1850-borrowings, fig.height=3, fig.align="center"}
-spec_CA1850 <- spectrogram("CA1850", best_matches, 
-                           white_list = c("LA1844", "NY1829", "NY1849", "NY1848"),
+best_matches_combine_ny <- best_matches %>% 
+  mutate(match_code = ifelse(match_code == "NY1848" | match_code == "NY1849",
+                             "NY1848-49",
+                             match_code))
+spec_CA1850 <- spectrogram("CA1850", best_matches_combine_ny, 
+                           white_list = c("LA1844", "NY1848-49"),
                            base_size = 10)
-spec_CA1850_bw <- spectrogram("CA1850", best_matches, 
-                              white_list = c("LA1844", "NY1829", "NY1849", "NY1848"),
+spec_CA1850_bw <- spectrogram("CA1850", best_matches_combine_ny, 
+                              white_list = c("LA1844", "NY1848-49"),
                               base_size = 10, bw = TRUE)
@@
 ```{r CA1851-borrowings, fig.height=3.5, fig.align="center"}
-spec_CA1851 <- spectrogram("CA1851", best_matches, 
+best_matches_ca1851 <- best_matches %>% 
+    mutate(match_code = ifelse(match_code == "NY1848" | match_code == "NY1849" | match_code == "NY1850",
+                             "NY1848-50",
+                             match_code))
+spec_CA1851 <- spectrogram("CA1851", best_matches_ca1851, 
                            white_list = 3, base_size = 10)
-spec_CA1851_bw <- spectrogram("CA1851", best_matches, 
+spec_CA1851_bw <- spectrogram("CA1851", best_matches_ca1851, 
                               white_list = 3, base_size = 10, bw = TRUE)
@@
 ```{r WA1855-borrowings, fig.height=4.5, fig.align="center"}
-spec_WA1855 <- spectrogram("WA1855", best_matches, 
-                           white_list = c("CA1850", "CA1851", "IN1852", 
+best_matches_wa1855 <- best_matches %>% 
+  mutate(match_code = ifelse(match_code == "CA1850" | match_code == "CA1851",
+                             "CA1850-51",
+                             match_code))
+
+spec_WA1855 <- spectrogram("WA1855", best_matches_wa1855, 
+                           white_list = c("CA1850-51", "IN1852", 
                                           "OR1854"),
                            base_size = 10)
-spec_WA1855_bw <- spectrogram("WA1855", best_matches, 
-                              white_list = c("CA1850", "CA1851", "IN1852", 
+spec_WA1855_bw <- spectrogram("WA1855", best_matches_wa1855, 
+                              white_list = c("CA1850-51", "IN1852", 
                                              "OR1854"),

### 2018-01-03 R/spectrogram.R

@@ -58,20 +58,16 @@ spectrogram <- function(code, matches_df, num_cols = 50,
     #                                          direction = -1)
     the_plot <- the_plot + scale_fill_manual(na.value = "white",
                     values = c(
-                        CA1850 = "#969696",
-                        CA1851 = "#BDBDBD",
-                        CA1872 = "#BDBDBD",
-                        IN1852 = "#252525",
-                        LA1844 = "#969696",
-                        NY1829 = "#BDBDBD",
-                        NY1848 = "#636363",
-                        NY1849 = "#252525",
-                        NY1850 = "#252525",
-                        OR1854 = "#636363",
-                        OR1862 = "#BDBDBD",
-                        WA1855 = "#636363",
-                        WI1849 = "#D9D9D9",
-                        Other = "#F7F7F7"
+                        `NY1848-49` = "#404040",
+                        `NY1848-50` = "#404040",
+                        CA1850 = "#808080",
+                        LA1844 = "#808080",
+                        IN1852 = "#404040",
+                        OR1854 = "#000000",
+                        `CA1850-51` = "#808080",
+                        WA1855 = "#000000",
+                        CA1872 = "#808080",
+                        Other = "#C0C0C0"
                         ))
   } else {
     the_plot <- the_plot + scale_fill_manual(na.value = "white",
@@ -80,6 +76,7 @@ spectrogram <- function(code, matches_df, num_cols = 50,
                       AZ1887 = "lightpink3",
                       CA1850 = "indianred4",
                       CA1851 = "firebrick2",
+                      `CA1850-51` = "indianred4",
                       CA1858 = "firebrick3",
                       CA1868 = "indianred1",
                       CA1872 = "darkred",
@@ -101,6 +98,8 @@ spectrogram <- function(code, matches_df, num_cols = 50,
                       NY1829 = "darkorchid1",
                       NY1848 = "darkorange",
                       NY1849 = "goldenrod1",
+                      `NY1848-49` = "darkorange",
+                      `NY1848-50` = "darkorange",
                       NY1850 = "peru",
                       NY1851 = "goldenrod4",
                       NY1853 = "tan4",
@@ -108,9 +107,9 @@ spectrogram <- function(code, matches_df, num_cols = 50,
                       NY1879 = "mediumpurple1",
                       OR1854 = "chocolate1",
                       OR1862 = "chocolate1",
-                      Other  = "lightgray",
+                      Other  = "gray",
[…]

### 2018-01-03 scripts/network-graphs.R

@@ -44,7 +44,17 @@ node_distances <- distances(codes_g,
                             to = the_field_codes,
                             algorithm = "unweighted") %>%
                     apply(1, min, na.rm = TRUE)
-nodes_n <- data_frame(name = names(node_distances),
+# Change labels of field codes
+code_names <- names(node_distances)
+node_distances <- ifelse(is.infinite(node_distances), NA_integer_, node_distances)
+node_distances <- ifelse(node_distances >= 2, 2, node_distances)
+node_distances <- as.character(node_distances)
+node_distances <- ifelse(node_distances == "0", "Field code",
+                         ifelse(node_distances == "1", "Original borrower",
+                         ifelse(node_distances == "2", "Subsequent borrower",
+                         node_distances)))
+node_distances <- ifelse(is.na(node_distances), "Independent", node_distances)
+nodes_n <- data_frame(name = code_names,
                       distance = node_distances,
                       field_code = is_field_code(name))
 

### 2018-01-08 scripts/split-code.R
Rename some things for the compendium

@@ -7,7 +7,7 @@ in_file <- args[1]
 stem <- in_file %>%
   basename() %>%
   str_replace("\\.txt", "")
-out_file_stem <- str_c("legal-codes-split/", stem)
+out_file_stem <- str_c("procedure-code-sections/", stem)
 doc <- read_file(in_file)
 
 # Use pattern_clean on files we have cleaned up; otherwise use pattern_fuzzy. We

### 2018-01-08 notebooks/031-count-sections.Rmd
Move notebooks into a single directory

--- 2015-12-02 031-count-sections.Rmd
@@
 ---
-title: "Number of actual sections"
+title: "Count number of sections in corpus"
 author: "Lincoln Mullen"
-date: "December 2, 2015"
 ---
@@
 library("knitr")
+load("cache/corpus-lsh.rda")
 code_files <- Sys.glob("legal-codes/*")
@@
 
-A section is a line with `§` or `SEC.` at the very beginning.
+The number of sectioned files on disk.
+
+```{r}
+Sys.glob("legal-codes-sp")
+```
+
+An alternative way of counting. A section is a line with `§` or `SEC.` at the very beginning.
 

### 2018-01-08 notebooks/101-visualizations-for-article.Rmd
Move notebooks into a single directory

--- 2016-05-26 101-visualizations-for-article.Rmd
@@
 ```
+
+```{r NY-most-borrowed, fig.height=8}
+all_NY1850 <- data_frame(borrower_code = "NY1850",
+                         borrower_section = all_matches %>% 
+                           filter(borrower_code == "NY1850") %>% 
+                           `$`("borrower_section") %>%
+                           unique() %>%
+                           sort()
+                        )
+
+NY1850_match_counts <- all_matches %>% 
+  filter(match_code == "NY1850",
+         borrower_year > 1850,
+         score >= 0.1) %>% 
+  count(match_section)
+
+left_join(all_NY1850, NY1850_match_counts, 
+          by = c("borrower_section" = "match_section")) %>% 
+  select(section = borrower_section, n) %>% 
+  mutate(n = ifelse(n < 6, NA, n)) %>% 
+  mutate(n = cut(n, c(seq(0, 40, 5), 85))) %>% 
+  mutate(.,
+         column = col_vector(nrow(.), 50),
+         row = row_vector(nrow(.), 50)) %>% 
+  ggplot(aes(x = column, y = -row, fill = n)) +
+  geom_tile(color = "lightgray") +
+  scale_fill_brewer(palette = "YlOrBr", na.value = "white", 
+                    labels = c("6-10", "11-15", "16-20", "21-25", "26-30",
+                               "31-35", "36-40", "40+")) +
+  labs(x = NULL, y = NULL, fill = "Number of times borrowed") + 
+  coord_equal() + 
+  theme_minimal() + 
+  theme(legend.position = "bottom",
+      axis.ticks = element_blank(),
+      axis.line = element_blank(), axis.text = element_blank(),
+      panel.background = element_blank(), panel.grid = element_blank(),
+      legend.key.size = unit(0.5, "cm"),
+      plot.margin = unit(c(0, 0, 0, 0), "cm"),
+      plot.title = element_text(hjust = 0.5)) +
+  ggtitle("Most frequently borrowed sections in NY1850")
+
+```

### 2018-01-08 notebooks/102-clustering.Rmd
Move notebooks into a single directory

--- 2015-12-01 102-clustering.Rmd
@@
 ---
-title: "Sparse matrix of comparisons"
+title: "Cluster the documents"
 author: "Lincoln Mullen"
@@
 ---
+
+We are going to create clusters of our documents using the affinity propagration algorithm.
 
@@
 library("textreuse")
-source("R/extract-date.R")
-source("R/extract_code_names.R")
-cache_lsh <- "cache/lsh-sections.rda"
-load(file = cache_lsh)
-cache_corpus <- "cache/corpus-sections-minash-n120-seed623.rda"
-load(file = cache_corpus)
+source("R/helper.R")
+load("cache/corpus-lsh.rda")
 ```
@@
 ```{r}
-scores <- section_scores %>% 
+scores_clustering <- scores %>% 
   filter(score >= 0.1)
-scores
-nrow(scores)
+scores_clustering
+nrow(scores_clustering)
 ```
@@
 ```{r}
-section_names <- lsh_subset(scores)
+section_names <- lsh_subset(scores_clustering)
 head(section_names, 10)
@@
 lookup
-scores <- scores %>% 
+scores_clustering <- scores_clustering %>% 
   left_join(lookup, by = c("a" = "section_names")) %>% 
   left_join(lookup, by = c("b" = "section_names")) 
-scores
+scores_clustering
 ```
@@
 n <- length(section_names)
-m <- sparseMatrix(i = scores$index.x, j = scores$index.y, x = scores$score,
+m <- sparseMatrix(i = scores_clustering$index.x,
+                  j = scores_clustering$index.y,
+                  x = scores_clustering$score,
                   dims = c(n, n), symmetric = TRUE)
@@
 ```{r}
-write_csv(clusters_df, "out/clusters.csv")
+dir.create("out/clusters")
+write_csv(clusters_df, "out/clusters/clusters.csv")
 ```
@@
 ```{r, message=FALSE}
+unlink("clusters", recursive = TRUE)
 dir.create("clusters", showWarnings = FALSE)

### 2018-01-08 notebooks/104-network-graphs-in-ggraph.Rmd
Move notebooks into a single directory

--- 2016-05-27 104-network-graphs-in-ggraph.Rmd
@@
 ```{r}
+set.seed(473)
 ggraph(states_g, "igraph", algorithm = "nicely") +
-  geom_edge_fan(aes(edge_width = sections_borrowed, 
-                    alpha = sections_borrowed),
-                arrow = arrow(type = "closed", ends = "first",
+  geom_edge_fan2(aes(edge_width = sections_borrowed, 
+                    alpha = 0.9),
+                arrow = arrow(type = "open", ends = "first",
                               length = unit(0.20, "inches"),
                               angle = 15)) +
-  geom_node_point(size = 6, alpha = 0.75, aes(color = region)) +
-  geom_node_text(aes(label = name)) +
+  # geom_node_point(size = 6, alpha = 0.15) +
+  geom_node_text(aes(label = name), size = 5) +
   scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") + 

### 2018-01-08 notebooks/105-most-borrowed-sections.Rmd
Move notebooks into a single directory

--- 2016-02-19 105-most-borrowed-sections.Rmd
@@
       mutate(match_code = "All codes",
+             n = ifelse(n == 1, NA, n),
              score = scales::rescale(n, from = c(0, max(n, na.rm = TRUE)))) %>% 
@@
 borrowings_spectrogram("CA1851")
-
 ```

### 2018-01-08 notebooks/107-test-values-of-n-k.Rmd
Move notebooks into a single directory

--- 2016-03-16 107-test-values-of-n-k.Rmd
@@
   filter(control < 0.02,
-         WA > 0.01) 
+         WA >= 0.009) 
 valid_params %>% 
@@
   spread(cf, score) %>% 
-  filter(WA > 0.01) %>% 
+  filter(WA >= 0.009) %>% 
   ggplot(aes(x = control, label = paste0("n:", n, ",k:", k))) +

### 2018-01-08 notebooks/108-mapping.Rmd
Move notebooks into a single directory

--- 2016-03-21 108-mapping.Rmd
@@
 ```
-
-Make
 
@@
 ```{r}
+regions <- read_csv("regions.csv")
 ny_codes <- c("NY1848", "NY1849", "NY1850", "NY1851", "NY1853")
+ca_codes <- c("CA1850", "CA1851", "CA1858", "CA1868", "CA1872")
+ia_codes <- c("IA1851", "IA1859")
+mo_codes <- c("MO1849", "MO1856", "MO1879")
+ky_codes <- c("KY1851", "KY1854")
+oh_codes <- c("OH1853", "OH1879")
+searched_for_codes <- oh_codes
+
 map_matches <- all_matches %>% 
-  filter(xor(borrower_code %in% ny_codes, match_code %in% ny_codes))
+  filter(xor(borrower_code %in% searched_for_codes,
+             match_code %in% searched_for_codes))
 
 map_matches_ny_borrower <- map_matches %>% 
-  filter(borrower_code %in% ny_codes) %>% 
+  filter(borrower_code %in% searched_for_codes) %>% 
   select(-borrower_state) %>% 
@@
 map_matches_not_ny <- map_matches %>% 
-  filter(!(borrower_code %in% ny_codes)) %>% 
+  filter(!(borrower_code %in% searched_for_codes)) %>% 
   select(borrower_section, match_section, score)
@@
 
-map_summary <- map_matches %>% 
-  filter(borrower_code %in% list2) %>% # Just the codes Kellen picked
-  group_by(borrower_state) %>% 
-  summarize(score = mean(score)) %>% 
-  arrange(desc(score))
+# map_summary <-
 
-intervals <- classIntervals(map_summary$score, n = 5, style = "jenks")
-map_summary$score <- cut(map_summary$score, breaks = intervals$brks)
+  map_matches %>% 
+  # filter(borrower_code %in% list2) %>% # Just the codes Kellen picked
+  mutate(borrower_code = extract_code_names(borrower_section)) %>% 
+  mutate(borrower_state = extract_state(borrower_code)) %>% 
+  mutate(borrower_year = extract_date(borrower_year)) %>% 
+  filter(score != 0) %>% 
+  group_by(borrower_code) %>% 
+  summarize(score = mean(score),
+            n = n()) %>% 
+  arrange(borrower_code) %>% 
+  # mutate(state = extract_state(borrower_code)) %>% 
+  #   left_join(regions) %>% 
+  #   ggplot(aes(x = n, y = score, color = region)) +
+  #   geom_point() +
+  #   ggtitle("Number of sections borrowed from NY vs average similarity of borrowing")
+  write_csv("out/summary-all-codes-with-matches-to-oh.csv")
+
+# intervals <- classIntervals(map_summary$score, n = 5, style = "jenks")
+# map_summary$score <- cut(map_summary$score, breaks = intervals$brks)
 ```
@@
                color = "black", size = 0.25) +
-  scale_fill_manual("Avg. dissimilarity score", values = brewer.pal(5, "YlGn")) +
+  scale_fill_manual("Avg. similarity score", values = brewer.pal(5, "YlGn")) +
   coord_map("albers", lat0=30, lat1=40) +
   theme_classic() +
-  labs(title = "Strength of borrowings from Field Code (List 2)",
+  labs(title = "Strength of borrowings from Field Code (All codes)",
        x = NULL, y = NULL) +

### 2018-01-08 article/Funk-Mullen.Spine-of-American-Law.Rmd
Re-run article PDF code

--- 2018-01-03 article/Funk-Mullen.Spine-of-Legal-Practice.Rmd
@@
     fig_caption: True
-    md_extensions: '-tex_math_single_backslash'
+    md_extensions: '-tex_math_single_backslash+smart'
     number_sections: False
     template: article-template.tex
-  word_document: 
-    fig_caption: True
-    md_extensions: '-tex_math_single_backslash'
-    pandoc_args: ["--smart"]
 title: |
@@
 dir.create("../out/figures", recursive = TRUE, showWarnings = FALSE)
-bw <- TRUE
+bw <- FALSE
 ```

### 2018-01-09 article/Funk-Mullen.Spine-of-American-Law.Rmd

@@
 library(textreuse)
+library(svglite)
 source("../R/helper.R")

### 2018-01-09 scripts/corpus-lsh.R
Fix changed directory name

@@ -10,7 +10,7 @@ h <- 120
 b <- 60
 minhash <- minhash_generator(n = h, seed = 623)
 
-sections <- TextReuseCorpus(dir = "legal-codes-split",
+sections <- TextReuseCorpus(dir = "procedure-code-sections",
                             tokenizer = tokenize_ngrams, n = 5,
                             keep_tokens = FALSE,
                             minhash_func = minhash)

### 2018-07-28 notebooks/101-visualizations-for-article.Rmd
Change knitr working directory
Redo NY 1850 most borrowed chart

--- 2016-05-26 101-visualizations-for-article.Rmd
@@
 knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+knitr::opts_knit$set(root.dir = normalizePath(".."))
 ```
@@
 ```
+
+This makes a spectrogram not of which sections in NY 1850 did the borrowing, but of which sections were borrowed the most.
+
+```{r NY-most-borrowed, fig.height=8}
+all_NY1850 <- data_frame(borrower_code = "NY1850",
+                         borrower_section = all_matches %>% 
+                           filter(borrower_code == "NY1850") %>% 
+                           pull(borrower_section) %>%
+                           unique() %>%
+                           sort()
+                        )
+
+NY1850_match_counts <- all_matches %>% 
+  filter(match_code == "NY1850",
+         borrower_year > 1850,
+         score >= 0.1) %>% 
+  count(match_section)
+
+NY1850_for_plotting <- left_join(all_NY1850, NY1850_match_counts, 
+          by = c("borrower_section" = "match_section")) 
+max_n <- NY1850_for_plotting$n %>% max(na.rm = TRUE)
+
+NY1850_for_plotting %>% 
+  # select(section = borrower_section, n) %>% 
+  mutate(n = ifelse(n < 2, NA, n)) %>% 
+  # mutate(n = cut(n, c(seq(0, 40, 5), 85))) %>% View
+  mutate(n = cut(n, c(seq(0, 80, 10), max_n))) %>% 
+  mutate(.,
+         column = col_vector(nrow(.), 50),
+         row = row_vector(nrow(.), 50)) %>% 
+  ggplot(aes(x = column, y = -row, fill = n)) +
+  geom_tile(color = "lightgray") +
+  scale_fill_brewer(palette = "YlOrBr", na.value = "white", 
+                    labels = c("2-10", "11-20", "21-30", "31-40", "41-50",
+                               "51-60", "61-70", "71-80", "80+", "")) +
+  labs(x = NULL, y = NULL, fill = "Number of similar sections in subsequent codes") + 
+  coord_equal() + 
+  theme_minimal() + 
+  theme(legend.position = "bottom",
+      axis.ticks = element_blank(),
+      axis.line = element_blank(), axis.text = element_blank(),
+      panel.background = element_blank(), panel.grid = element_blank(),
+      legend.key.size = unit(0.5, "cm"),
+      plot.margin = unit(c(0, 0, 0, 0), "cm"),
+      plot.title = element_text(hjust = 0.5)) +
+  labs(title = "Most influential sections in NY1850")
+```

### 2018-07-28 notebooks/101-visualizations-for-article.Rmd
Adjust NY1850 most borrowed

@@
                                "51-60", "61-70", "71-80", "80+", "")) +
-  labs(x = NULL, y = NULL, fill = "Number of similar sections in subsequent codes") + 
+  labs(x = NULL, y = NULL, fill = "Number of similar sections\nin subsequent codes") + 
   coord_equal() + 
@@
       legend.key.size = unit(0.5, "cm"),
-      plot.margin = unit(c(0, 0, 0, 0), "cm"),
+      plot.margin = unit(c(0.0, 0.0, 0.0, 0.0), "cm"),
       plot.title = element_text(hjust = 0.5)) +
   labs(title = "Most influential sections in NY1850")
+ggsave("out/diss/NY1850-most-borrowed.png", width = 6.5, height = 7.5)
 ```
